### 2016-10-19 paper.tex
update

\documentclass{llncs}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{color,graphicx,epstopdf,changepage,amsmath,multirow}

\SetAlgoCaptionSeparator{.\space}
\renewcommand\AlCapFnt{\normalfont\scshape}
\setlength{\algomargin}{0.7cm}

\title{A Novel Comprehensive Quality Evaluation Model in Automated Semantic Web Service Composition}

\author{Chen Wang, Hui Ma, and Aaron Chen}
\institute{School of Engineering and Computer Science,
\\Victoria University of Wellington, New Zealand \\
\email{\{Chen.Wang, Hui.Ma, and Aaron.Chen\}@ecs.vuw.ac.nz }}

\makeatletter
\usepackage[pdfauthor={\@author}, pdftitle={\@title}]{hyperref}
\makeatother

\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}}

\begin{document}

\maketitle

\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major governance challenges faced by researchers, and Semantic matchmaking is to discover interoperable web services, which demands a rich “machine understanding” language such as OWL-S (Web Ontology language for Web Services), WSML (Web Service Modeling language, SAWSDL (Semantic Annotations for WSDL and XML Schema). This interaction enables us to pair service functionalities through language understanding and reasoning. An optimisation problem is the another challenge with consideration in non-functional attributes, such as quality of service (QoS). Nowadays, many scholars have looked into optimisation problems in QoS-awareness web service composition applying AI planning and Evolution Computing techniques. However, it is not sufficient without considering good balancing between functional and nonfunctional quality in most scenarios. Therefore, the consideration in these two quality dimensions is a must, so that a comprehensive quality evaluation model is proposed to deal with finding optimised semantic web service composition solution. This paper develops a more applicable approach dealing with a comprehensive quality ---semantic matchmaking and QoS optimisation for automated semantic web service composition.
\end{abstract}

\section{Introduction}\label{introduction}
Service-oriented computing (SOC) is a novel computing paradigm that employs services as fundamental elements to achieve agile development of cost-efficient and integratable enterprise applications in heterogeneous environments \cite{papazoglou2003service}. Service Oriented Architecture (SOA) could abstractly realise service-oriented paradigm of computing, this accomplishment has been contributing to reuse of software components, from the concept of functions to units and from units to services during the development in SOA \cite{booth2004web}. One of the most typical realisations of SOA is \textit{web service}, which designated as ``modular, self-describing, self-contained applications that are available on the Internet'' \cite{curbera2001web}. Several standards play a significant role in registering, enquiring and grounding web services, such as UDDI, WSDL and SOAP \cite{fensel2011semantic}.

\textit{Web service composition} pertains to a combination of several web services to provide a value-added composite service that accommodates customers' arbitrarily complex requirements. This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems - diverse platforms and programming languages \cite{casati2001technologies}. Due to an increase in a large-scale alignment of enterprise applications, the number of Web services has increased dramatically and unprecedentedly, which cause an immense redundancy in functionality in a huge searching space. Therefore, manual service and semi-automated web service composition are considered to be lower efficiency while automated web service composition is considered to be less human intervention, less time consumption, and high productivity.

Two most notable challenges for web service composition are ensuring interoperability of services and QoS optimisation \cite{fensel2011semantic}. Interoperability of web services is one challenge in the dimensions of syntactic and semantics \cite{fensel2011semantic}. The syntactic dimension has achieved success through the use of XML standards (such as $WSDL$, $SOAP$), the semantics dimension, on the other hand, demands further research. Adding semantics given by ontologies \cite{o2005review} enables web service to understand and reason with each other. Historically, there are many ontologies languages and formats for semantic service descriptions, such as OWL-S \cite{martin2004owl}, WSML \cite{fensel2006enabling}, and SAWSDL \cite{lausen2007semantic}, The logical characteristics in reasoning makes ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments. The second challenge is to find optimised solutions to Quality of Service ($QoS$) over the composite web service. This problems give birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements \cite {sahai2002automated} manifesting a collection of SLA rules and policies for supporting QoS-based composition.

Existing works on service composition are often addressed regarding one of the above challenges. One group optimises the quality of compositions under a pre-defined abstract workflow, which is considered to be a \textit{semi-automated Web service composition} approach. Another group attempts to generate a composite plan automatically in discovering and selecting suitable web services, which are deemed to be an NP-hard problem \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition. Its benefits are presented in eliminating conflicts at the semantic level of web service composition. In the last few years, substantial work has been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}. Howevever, few works have addressed an automatic semantic web service composition approach, which optimise both QoS and quality of semantic matchmatching as optimised web service composition sollutions. For example, customers prefer the highest quality of service solution associated with the acceptable semantic matchmatching quality.

The overall goal of this paper is to develop an comprehensive evaluation model in  automated semantic web service composition that satisfactorily optimises both functional and non-functional requirements. Particularly, this project considers a semantic matchmaking quality extension to QoS awareness and a few structural constructs(sequence and parallel) for building optimised composition solution using Particle Swarm Optimisation. We aim to provide a more general and applicable way to measure semantic matchmaking in automated semantic web service composition and contribute to the state-of-the-art in this field. Three objectives of this work are accomplished as follows:

\begin{enumerate}
 \item To address semantic matchmaking quality with considering different matching types associated with corresponding semantic similarity, which is demonstrated as a comprehensive quality --- a more general and applicable evaluation method utilising semantic information of service descriptions in this paper.

 \item To apply PSO for sorting an optimised service queue as a indirect representation of web service composition with consideration in optimising the comprehensive quality, this indirect representation is decoded using graph building algorithm to generate a service composite solution.

 \item To evaluate the performance of proposed approaches, we utilise the datasets from Web Services Challenge 2009 (WSC'09) \cite{kona2009wsc}.
\end{enumerate}

The remains of this paper are composed as the following: Sect. \ref{background} provides the knowledge background on the semantic web service composition, including a literature review; Sect. \ref{qswsc_approach} represents the an Introduction of of semantic automated web service composition approach, and the comprehensive quality evaluation model; Sect. \ref{experiment_design} describes the experiments conducted to test the effectiveness of proposed model; Sect. \ref{results_analysis} presents the results and analysis of these experiments; Sect. \ref{conclusion} is the paper conclusion.

\section{Background}\label{background}

\subsection{Problem Description}\label{problemDes}

The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as composite goal: $G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$. This overall composite goal is demonstrated in two parts. One part is that a given input or input set to get the desired output or output set, it typically refers to a statement in functional requirement ; another part specify the overall acceptable composite quality, which covers aspects in non-functionality. To accomplish the first half goal, two stages are involved in the investigation of this paper : services discovery and service selection. Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from Service Repository: $S \{S_{1}, S_{2},..., S_{n} \}$ with the given Task until the desired output found. It results in more than one solutions without considering optimisation; Service selection is to select web services to reach global best quality($T_{QoS}$). We are aiming to optimise a combined objective function involving both functional and non-functional concerns. Particularly in this paper, two challenges mentioned in Sect. \ref{introduction} are addressed in semantic web composite approach. First, the inputs of each service could be semantically matched by predecessor services in the composition. Second, optimisation in QoS would not be sufficient in many scenarios to make a good decision, if customers are looking for a trade off either in better service quality with counteroffer in QoS or better QoS with less strict functional matchmaking quality.

\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
The semantic service matchmaking aims to discover appropriate services from service repository relevant to a customer's functional request defined by the Goal. A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$ with both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Tax\}$. The web service discovery process is to discovery the services an input-output concept matchmaking according to the Taxonomy(Tax) within an ontology (O). To measure the quality of semantic matchmaking, different matching levels that are typically considered in the literature \cite{paolucci2002semantic}. We defined two web services associated with parameters in a particular domain: $S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S2$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$ defined in.

\begin{itemize}
\item \textit{Exact} ($\equiv$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Exact match ($ S_{output} \in S_{1} \equiv S_{input}S_{2}$), if  Concept $C_{2}$ and Concept $C_{3}$ are equivalent.
\item \textit{Plugin} ($\sqsubseteq$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Plugin match ($S_{output} \in S_{1} \sqsubseteq S_{input} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of Concept $C_{3}$.
\item \textit{Subsume} ($\sqsupseteq$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Subsume matched($S_{output} \in S_{1} \sqsupseteq S_{input} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of  Concept $C_{3}$.
\item \textit{Fail} ($\perp$). Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are not matched (Fail) ($S_{output} \in S_{1} \perp S_{input} \in S_{2}$), if none of the previous matches discovered.
\end{itemize}

Note that, to find relevant services to automatically form suitable and applicable service compositions for a given goal, we consider Exact, Plugin and Fail match types in our paper. Therefore, these three robust and valid matches will be used to discover web service candidate for a service composition.

\subsection{Quality of Service and Composition Constructs}\label{web service selection}
Currently, most of the optimisation problems \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} in web service composition are focusing on QoS optimisation, which covers aspects in non-functional requirements. This problem have been explored in optimising both single objective and multi-objectives in QoS. Ideally, customers prefer lowest execution cost with highest response time and reliability. According to \cite{zeng2003quality}, four most often considered QoS parameters are as following:
\begin{itemize}
\item \textit{Response time} ($T$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.
\item \textit{Cost} ($C$) is the amount of money that a service requester has to pay for executing the web service
\item \textit{Reliability} ($R$) is the probability that a request is correctly responded within the maximum expected time frame.
\item \textit{Availability} ($A$) is the probability that a web service is accessible.
\end{itemize}
The aggregation value of QoS attributes for web services composition varies with respect to different constructs, which explains how services associated with each other \cite{zeng2003quality}. Here we consider two composite constructs: sequence and parallel are used in building the composite flow, which are described as follows:

\begin{figure}[h]
\centerline{
\fbox{
\begin{tabular}{p{0.6\linewidth}}
\space\hfill\includegraphics[width=2in]{sequence.pdf}\hfill\space\\[0.2cm]
$T=\sum\limits^m_{n=1}t_n$ \hfill $C=\sum\limits^m_{n=1}c_n$ \hfill
$A=\prod\limits^m_{n=1}a_n$ \hfill $R=\prod\limits^m_{n=1}r_n$
\end{tabular}}}
\caption{Sequence construct and calculation of its QoS properties
\cite{yu2013adaptive}.}
\label{sequence}
%\end{figure}
\vspace{0.3cm}
%\begin{figure}
\centerline{
\fbox{
\begin{tabular}{p{0.6\linewidth}}
\space\hfill\includegraphics[width=1.4in]{parallel.pdf}\hfill\space\\[0.2cm]
\space\hfill$T=MAX\{t_n|n\in\{1,\ldots,m\}\}$\hfill\space\\[0.2cm]
$C=\sum\limits^m_{n=1}c_n$ \hfill $A=\prod\limits^m_{n=1}a_n$ \hfill
$R=\prod\limits^m_{n=1}r_n$
\end{tabular}}}
\caption{Parallel construct and calculation of its QoS properties
\cite{yu2013adaptive}.}
\label{parallel}
\end{figure}

\subsubsection{Sequence construct}
The composite web service executes each atomic service associated with a sequence construct in a definite sequence order. The aggregation value for total time ($T$) and total cost ($C$) is the sum of time and cost of web services involved respectively. The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory. This construct is shown in Figure \ref{sequence}.
\subsubsection{Parallel construct}
Web services in a parallel construct are executed in the meantime. The QoS aggregation value in total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is delimited by the maximum time consumed path in the service composite solution. This construct is presented in Figure \ref{parallel}.

\subsection{Related Work}
\textbf{Semantic web service matchmaking}. Substantial work \cite{bansal2016generalized,mier2015integrated} on semantic web service composition focus particularly on functional requirements and negect non-functional requirements. This approach utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output concepts of web services to ensure a semantic matchmaking. Since semantic descriptions are introduced into web service, which is expressed in ontologies, the semantic matchmaking is to considered to seek similarity of parameters (i.e., input and output) of web services and pair a mapping between two knowledge representations encoded utilising the same ontology \cite{lecue2006formal}. In \cite{shet2012new}, the author surveyed three approaches the similarity measures using taxonomies: one is based on nodes, in which similarity is determined by the information content of the nodes; one is entirely based on edge, where concept distance in a hierarchy structure is evaluated,  and the hybrid approach that combines the previous two methods. A new similarity measure based on edge counting is introduced in a Ontology in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}. Neighbourhood concepts are considered in their model in Formular \ref{equation1}, where $\lambda$ = 1 (default value as 0).

\begin{equation}
q(s_ {similarity}){=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
\label{equation1}
\end{equation}

In \cite{lecue2009optimizing}, web services are connected as an semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, which apply one possible measure for similarity degree on nodes information demonstrated as Common Description rate of a semantic link in Formula \ref{equation2}. Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$and Least Subsume $lcs(Out_{s_i},In_{s_j})$. They chained the web service in five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint. The quality of the semantic link is estimated as quality criteria $q_{m}$(i.e. either 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection)) associated with their corresponding quality of vector $q_{cd}$ \ref{equation2}. The model is defined as follows.
\begin{equation}
\label{equation2}
q(sl{_{i,j}}) \stackrel{.}{=} (q_{mt}(sl_{i,j}), \  q_{cd}(sl_{i,j}))
\end{equation}
\begin{equation}
q_{cd}(sl{_{i,j}})={=} \frac{|lcs(Out_{s_i},In_{s_j})|}{|In_{s_{x}} \setminus Out_{s{_y}} \stackrel{.}| +|lcs(Out_{s_i},In_{s_j})| }
 \label{equation3}
\end{equation}

However, the weakness of this approach for semantic link quality is that calculating Extra Description and Least Subsume of out-input request requires well and complete defined DL in knowledge representation in the different domains, which makes it nearly impossible to be widely applied to semantic matchmaking measures in today's' web services application. Additionally, in their semi-auto workflow approach, they do not consider data-flow compatible and automated service composition.

\textbf{QoS-aware EC approaches}.
Evolution Computing techniques are considered to be more effective for solving globally optimisation problem. Genetic Programming (GP) approaches \cite{da2015graphevol,da2016particle} are typical EC techniques widely applied to fully automated web service composition, which utilises a tree representation that service as the terminal nodes, and composite constructs as the functional nodes. The crossover and mutation process reproduce various individuals with ensuring correctness of structure. In \cite{yu2013adaptive}, the author optimises the quality of the overall composition by a complex fitness function, which is also liable for correctness in functionality through penalising solutions. To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, this approach is to find a optimised web service queue in the way of searching best location using PSO for optimised QoS, that service queue is involved in building a graph representation of web service composition later. However, the neglecting of leveraging the semantic difference between composite service output and customers' request could lead to the lower quality of functionality matchmaking with best quality of service in QoS-awaren web service composite paper \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph}. For example, a client asks for a particular AI textbook while output of the composte web service provides a general book. In this scenario, the output is a too broad consequences that have no meaning for the customers, even though web services are selected for a excellent composite QoS consideration. Therefore, we fill the gap to provide a more applicable approach to evaluate an overall quality in this paper.

\section{QoS-aware Semantic Autoamted Web Serivce Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
On the support of the representation of our solution, in this section, we introduce our evaluation model in a graph-based representation for QoS-aware automatic semantic web service composition utilising PSO, which is considered to be simple and efficient without penalising and repairing comparing to GP \cite{da2014graph}. Fig. \ref{overview} shows the overview of our approach with the several steps included. The composite process is triggered by a composite goal defined in Subection \ref{problemDes}, which demonstrate customers requirements in terms of functional and non-functional requirement. The previous one is well defined as an overall input-output requirement, and the later one is the users' accepted quality of service. Those requirements are initially used to discover all relevant web services and their relationship in semantic matchmaking to get prepared for building graph representations. The second step of selecting relevant web services contributes to shrink the size of participated web services for dimensions of particles involved in future optimised problem. In the third step, a service composition graph randomly built up with considering the QoS and matchmaking quality. This graph building is interleaved with semantic matchmaking for services. The output of one service and its associated input of another service is calculated in the matchmaking phase where semantic matchmaking quality are measured which will be explained in Subsection \ref{qulityModel}. The further optimization of service composition solution is performed over the PSO in Section \ref{pso_algorithm}, which is used to find optimised particle locations mapped back to web service for service-graph building. This approach \cite{da2016particle} is an indirect representation of web service composition that constructing a graph-based composite service composition.

\subsection{QoS-aware Semantic Web Service Composition algorithm} \label{pso_algorithm}
\begin{algorithm}[!htb]
 \setlength\hsize{0.9\linewidth}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \let\oldnl\nl% Store \nl in \oldnl
\newcommand{\nonl}{\renewcommand{\nl}{\let\nl\oldnl}}
 \LinesNumbered
	\textbf{1.} Randomly initialise each particle in the swarm.\\
	\nonl \While {max. iterations not met}{
		\ForAll{particles in the swarm}{
			\textbf{2.} Sort partcile's postion vector as a service queue in ascending order\\
			\textbf{3.} Initialise OutputSet with Task Input\\
			\textbf{4.} Initialise a graph with a startNode associated with Task Input as its output\\
			\nonl \While {max. OutputSet not contains Task Input}{
				\textbf{5.} Get web service from service queue\\
				\If{All inputs of current web service satisfied with output from outputSet}{
					\textbf{6.} Create and connect service edge associated with matchmaking quality to graph.\\
					\textbf{7.} Create and connect node(current web serivce) to graph.\\
					\textbf{8.} Remove current web service fromt the queue.\\
					\textbf{9.} Update OutputSet with outputs current web service.\\
				}
				\textbf{10.} Get next web service from service queue\\
			}
			\textbf{11.} Connect endNode the graph\\
			\textbf{12.} Remove dangle services from the graph\\
			\textbf{13.} Remove dangle edges\\
			\textbf{14.} Aggregation of semantic matchmaking and QoS\\
			\textbf{15.} Calculate the particle's fitness.\\
			\Indp $fitness_i = w_1SDst + w_2A_i + w_3R_i + w_4(1 - T_i) + w_5(1 - C_i)$ where $\sum_{i=1}^{5} w_i = 1$ \\
			\eIf{fitness value better than pBest}{
				\textbf{16.} Assign current fitness as new pBest.\\
			}{
				\textbf{17.} Keep previous pBest.\\
			}		
		}
		\textbf{18.} Assign best particle's pBest value to gBest, if better than gBest.\\
		\textbf{19.} Calculate the velocity of each particle according to the equation:\\
		\Indp $v_{id} = v_{id} + c_1 * rand() * (p_{id} - x_{id}) + c_2 * rand() * (p_{gd} - x_{id})$\\
		\Indm \textbf{19.} Update the position of each particle according to the equation:\\
		\Indp $x_{id} = x_{id} + v_{id}$\\
	}

 \caption{Steps of graph-based PSO optimisation technique.}
\label{psoSteps}
\end{algorithm}
The overall algorithm investigated here is a combination of a simple forward decoding PSO \cite{da2016particle} and a graph-building technique \cite{blum1997fast} with our comprehensive quality evaluation model. The idea of that is to translate the particle location into a service queue as an indirect representation of service composition graph, finding the best fitness of the composite service solution is to figure out the optimised location of the particle. In PSO, the dimension of the particle is set up as the same as the number of relevant web services shrunk from serivce repository, and all of them are mapped to the particle location, put in a service queue and sorted in ascending order. The second method is to decode a corresponding graph built from that service queue. and it is a forward graph-building technique from a start node to the end node, we select and connect web services to startNode if this web service can satisfy the given Task input initialised in a Output Set, and this Output Set is updated after adding web service to the graph, later on, we services are keeping being selected and added if its added services' outputs in the Output Set could be satisfied, if the any outputs in the Output Set meets the Task's requriment, we end up graph building. In addition, dangle services and edges shoud be removed. At last, fitness value can be calculated by the construct-based aggregation.

\subsection{Semantic matchmaking}
The semantic matchmaking is achieved by utilising semantic annotation with OWL and MECE ontologies \cite{bleul2008self} with OWL and XWL format respectively. In OWL,  the semantics specifies the both concepts and individuals in forms of classes and instances but limited to taxonomies. The semantic concepts are expressed with the their statements and relationship in RDFs (such as subClassOf ), and the semantic individuals are related to the input and output parameters of web services. The MECE is an extensive annotation to WSDL files, which defines the each parameter of services associated with their semantic individuals. The overall matchingmaking process is demonstrated in Figure \ref{matchmaking}.

\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=10cm]{matchmaking.pdf}}}
 \caption{Semantic matchmaking.}
 \label{matchmaking}
\end{figure}

The semantic matchmaking transfer a function match (OutputS1, InputS2 ) to a pair of concept match (C2, C3) for the two web services defined in Section \ref{semantic Web service Discovery}. The matching mechanism attempts to determine whether correct match criteria between the source concepts of C1 and the target concepts of C2, and the quality of semantic matchmaking for the two its reasoning is also calculated in the quality model in the following Section ref{qulityModel}. The advantage of utilising semantic matchmaking is to enable a reasonable connection between two web services from different service providers to find more service solutions with better QoS.

\subsection{Comprehensive quality model and aggregation matrix}\label{qulityModel}
In this paper, we proposed a semantic matchmaking model to evaluate the semantic quality of two matched web services. Then we fill the gap of current prevailing QoS-aware optimisation consideration in the fully automated composition approach, which has not considered the quality of matchmaking for service selection.

\textbf{Semantic matchmaking model}. Due to the discretizational characteristics of different match types, the match type quality is driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}, so that match type is considered to be one factor for the semantic quality. Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, a taxonomy based measurement for ontology matching, In our paper, it could be used to estimate the parameter concepts similarity between the output and input request for selecting the highest semantic-closeness web services. Therefore, given the quality match type and the similarity of two parameters, the semantic matchmaking quality is defined as Equation \ref{equation4}.$q(s_ {matchType})$ is set up as the same as the quality of the semantic link in literature \cite{lecue2009optimizing} (i.e. either 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection)), and $q(s_ {similarity})$ is Equation \ref{equation1}.

\begin{equation}
\label{equation4}
q_{smq} \stackrel{.}{=} (q(s_ {matchType}), \  q(s_ {similarity}))
\end{equation}

\textbf{Comprehensive quality model}. Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional attributes of composite web service. The non-functional properties typically refer to availability, reliability, cost and response time, which are given by service providers. Consequently, the comprehensive quality model integrated the semantic matchmaking quality and quality of service in Equation \ref{equation5}, which could be broken down into Equation \ref{equation6}.

\begin{equation}
\label{equation5}
q_{cq} \stackrel{.}{=} (q(s_ {smq}), \  q(s_ {QoS}))
\end{equation}
\begin{equation}
\label{equation6}
q_{cq} \stackrel{.}{=} (q(s_ {mt}), \  q(s_ {s}), \  q(s_{a}),\  q(s_{r}),\  q(s_{c}),\  q(s_{t}))
\end{equation}

\textbf{Quality aggregate matrix}.The quality aggregation is defined based on the constructs of composite web services on the criteria of functional and non-functional properties. Typically, two web services are connected by more than one parameter-related concepts. In details, edge-level quality aggregation is determined by the mean of parameter-related concept quality in both semantic match type and similarity respectively, and construct-level quality is further calculated based on the edege-level quality aggregation following the rules in Table \ref{table1}, which is the quality aggregate matrix for semantic web service composition. The calculation of QoS aggregation is similar to \cite{cardoso2004quality} while semantic matchmaking aggregation is adopted from \cite{lecue2009optimizing}.

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\centering
\caption{Quality aggregate matrix for semanic web service composition}
\label{table1}
\begin{tabular}{|c|c|c|c|l|}
\hline
\multicolumn{3}{|c|}{Composition Construct}                                      & Sequence                             & Parallel \\ \hline
\multirow{5}{*}{QualityFactors} & \multirow{2}{*}{Functional}    & $Q(s_ {mt})$  &$\prod_{n=1}^{m} q(s_ {mt})$          &  $\prod_{n=1}^{m} q(s_ {mt})$ \\ \cline{3-5}
                                &                                & $Q(s_ {s})$  & $(\sum_{n=1}^m q(s_ {s}))/m$        &  $(\sum_{n=1}^m q(s_ {s}))/m$  \\ \cline{2-5}   
                                & \multirow{4}{*}{NonFunctional} & $Q(s_{a})$    & $\prod_{n=1}^{m} q(s_a)$             &  $\prod_{n=1}^{m} q(s_a)$ \\ \cline{3-5} 
                                &                                & $Q(s_{r})$    & $\prod_{n=1}^{m} q(s_r)$             &  $\prod_{n=1}^{m} q(s_r)$ \\ \cline{3-5} 
                                &                                & $Q(s_{c})$    & $\sum_{n=1}^m q(s_ {c})$             &  $\sum_{n=1}^m q(s_ {c})$ \\ \cline{3-5} 
                                &                                & $Q(s_{t})$    & $\sum_{n=1}^m q(s_ {t})$             &  $max(q(s_ {t}))$ \\ \hline
\end{tabular}
\end{table}

\subsection{Fitness Calculation}
The fitness value is calculated from the aggregate value of quality components involved in a graph-based service composition. A weighted sum of those components is utilised in the fitness function \ref{equation7}, in which fitness value of 1 means the best overall quality and 0 means the worst. In addtion, aggregate value of each parameters must be normalised between 0 and 1. In details, $MT$, $S$, $A$, and $R$ are calculated in Formula \ref{equation8} while $T$ and $C$ are calculated in Formula \ref{equation9}.

\begin{equation}
\label{equation7}
fitness_i = w_1MT + w_2S + w_3A_i + w_4R_i + w_5(1 - T_i) + w_6(1 - C_i)
\end{equation}

\noindent where $\sum_{i=1}^{6} w_i = 1$
\\\\
\begin{equation}
\label{equation8}
normalise(MT, S, A, or R) = 
\begin{cases}
	\frac{value - min}{max - min} & \text{ if }max - min \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}

\begin{equation}
\label{equation9}
normalise(T or C) = 
\begin{cases}
	\frac{max - value}{max - min} & \text{ if }max - min \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}

\section{Experiment Design}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design. The objective of the evaluation are: 1) measure the effectiveness of the proposed comprehensive quality model in automated semantic web service composition approach, and explore the impact of the semantic matchmaking that contributes to overall composition quality. 2) compare the optimised sollutions with using comprehensive evaluation model with using QoS-aware evaluation model to reveal the advantages of our novel method.

We utilise the web service challenge 2009 (WSC’09) web service data sets to perform a standard evaluation. Compared to previous web service challenge dataset, WSC'09 is evolved with OWL for providing richer semantics. With an incremental number in concept, individuals and web services in each dataset, it is a proper dataset for the scalability measures in our defined quality evaluation model.Table 1 presents the features of the WSC’09 dataset. The number of concepts, individuals in the ontology and services of each data set is shown in the second, third, fourth column respectively. Also, we extend the all the datasets with QoS attributes from service providers to perform a comprehensive quality evaluation. 
\begin{table}[]
\centering
\caption{features of the WSC'09 datasets}
\label{wsc09datasetTable}
\begin{tabular}{|l|l|l|l|}
\hline
\multicolumn{1}{|c|}{Dataset} & No.Concept & No.Individual & No.Service \\ \hline
WSC'09 01                     & 1578       &3102           &572      \\ \hline
WSC'09 02                     & 12388      &24815          &4129      \\ \hline
WSC'09 03                     & 18573      &37316          &8138      \\ \hline
WSC'09 04                     & 18673      &37324          &8301      \\ \hline
\end{tabular}
\end{table}

We run the experiment under computing grid comprising of almost 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine. Experimentation was done using the composite service approach explained in Section \ref{qswsc_approach}, and evaluated in the comprehensive quality model introduced in Section \ref{qulityModel}. The parameters were chosen based on general settings from \cite{shi2001particle}, In PSO approach, 30 particles evolved in 100 generations in the searching space, in which problem dimension's size equals to the relevant service size shown in graph. we run 30 times independently for each dataset. In addition, weights setting are more flexible defined by users' preferences. Simplely, we configure weights of fitness function as same leverage for balancing functional side and nonfunctional side. Therefore, W1 and W2 are equals to 0.1 and 0.4 entirety 0.5,  and W3, W4, W5, W6 are all set to 0.125 summed 0.5.

\section{Results and Analysis}\label{results_analysis}
\subsection{Convergence Test}\label{convergenceTest}
The purpose of our experiment is to expose the results of our proposed approach are optimised comprehensive quality for web service challenge tasks utilising datasets from WSC’09. To study an overall effectiveness of evaluation model and investigate the impacts of all involved components that are contributing the weighted sum fitness functional. We analysis all the performance of these components in the whole evolutionary process in Figure \ref{exp_fitnessvalue}, in which the three tasks' experiment results are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average quality of service for generation 0-99 with optimum.
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{convergency.pdf}}}
 \caption{Average fitness, Average MatchType quality, Average Similarity quality and Average QoS per generation with comprehensive quality optimum}
 \label{exp_fitnessvalue}
\end{figure}

Firstly, the average fitness value over 100 generations is calculated by the average best fitness so far found per generation over 30 independent runs. The marked value plotted in the first group of the figure ranges from 0 to 1, and it is considered to be more optimised if its value is closer to value 1. We can see that there is a significant increase in the fitness value between generation 0 and generation 15-25, the remained generation continues to perform a very slight improvement in the fitness value and reach a plateau with no further changes. Furthermore, it is a common feature in three tasks’ average fitness graph. Also, there is a fast convergence of the population can be observed. That is simply because of many repetitive solutions as the indirect web service composition representation, although it is a large search space.

We also investigate the variation in functional quality part including two subfactors --- average matchType quality and average similarity quality from generation 0 to 99 in second and third groups in Figure \ref{exp_fitnessvalue}.  In these groups,  both the average matchType quality and average similarity quality are the average value corresponding to the average best fitness so far found,  and further calculated their mean over 30 independent runs respectively. The dominant tendency of the marked value representing a similar characteristic compared to the average fitness value group trend. However, there are some slight fluctuations over the generations, and it could be reasonably treated as a typical situation that theoretically single objective function prevents selecting the lowest semantic matchmaking quality without granting for the excellent, yet the combination of all the influential functional quality part evolved towards an optimised solution.

Lastly, It is interesting to look at the average QoS per generation for the 30 independent runs if the behaviour of functional part performance is towards a higher value, where QoS is the value corresponding to the best fitness so far found in each generation. We construct the results in the fourth groups in Figure \ref{exp_fitnessvalue}. It is obviously that the overall trend of QoS moves upward in three tasks, and reach almost constant later on. Luckiely, we reach a very good state for QoS value, because we don't see too much trade-off from QoS regarding the improvement in functional quality part.

\subsection{Comparision Test}\label{comparisionTest}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=8cm]{wscs.pdf}}}
 \caption{Example composition solutions for problem1 WSC'09.}
 \label{wscs}
\end{figure}
We defined our optimised web service composition as $WSC = (V, E)Graph$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of service connections as edges associated matchType quality and semantic similarity quality: $E = {e_{1}, e_{2},... e_{n}}$ where $e1$ is define as $(S_{1},S_{2})={q_{mt}, q_{s}}$. Here we provide an uncomplicated example of the web service composition solution to problem1, which can be described in the Figure \ref{wscs}. The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, $q_{mt}$ and $q_{s}$) are calcuated for all edges ${e_{1}, e_{2},... e_{n}}$, and further aggregateed in $Q_{mt}$ and $Q_{s}$ respectively.In addtion, $Q_{QoS}$ is calcuated the all the non-functional attributes of $V$ using aggregation rules defined before.

After well-defined solutions are discussed, we will look at $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ using  black-box testing for sollution comparision, where these components in both comprehensive quality evaluation approach and traditional QoS-ware one \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} are compared to reveal how good our evaluation mode is. In a decision table \ref{decisionTable}, these two models are interpreted as a rule set considering three different conditions (three independent tasks) associated with three corresponding sollutions. In each sollution, we compare $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$, where $Q_{QoS}$ is normalised to make them comparable from 0 to 1 in our method. From the table below.

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\footnotesize
\centering
\caption{Quality of two evaluation model in a decision table}
\label{decisionTable}
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{\multirow{2}{*}{}}                              & Rule 1               & Rule 2                           \\ \cline{3-4} 
\multicolumn{2}{|c|}{}                                               & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
\multirow{3}{*}{Condition}            & dataset1             & $\surd$              & $\surd$                            \\ \cline{2-4} 
                                      & dataset2             & $\surd$              & $\surd$                            \\ \cline{2-4} 
                                      & dataset3             & $\surd$              & $\surd$                            \\ \hline
\multirow{3}{*}{\shortstack{Task1\\Optimised sollution}}  &$Q_{mt}$                      & .232635              & .232635                          \\ \cline{2-4} 
                                      &$Q_{s}$                       & .903572              & .903572                          \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .578577              & .578577                          \\ \hline
\multirow{3}{*}{\shortstack{Task2\\Optimised sollution}}  &$Q_{mt}$                      & .001828              & .000851$\downarrow$               \\ \cline{2-4} 
                                      &$Q_{s}$                       & .917172              & .938840$\uparrow$                 \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .480251              & .473002$\downarrow$               \\ \hline
\multirow{3}{*}{\shortstack{Task3\\Optimised sollution}}  &$Q_{mt}$                      & .191188              & .247836$\uparrow$                  \\ \cline{2-4} 
                                      &$Q_{s}$                       & .951509              & .973723$\uparrow$                  \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .493927              & .491538$\downarrow$                         \\ \hline
\end{tabular}
\end{table}
From the table \ref{decisionTable}, Task 1 represents the same solution that can be observed in values of  $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$ using the smallest dataset size with the lowest complexity of ontologies and valid solutions. However, we can recognise trade-offs in task2 and task3 using our evaluation model, where a 0.021668 increase and a 0.00098 decrease in similarity quality and matchType quality with weights 0.4 and 0.1 respectively so that it is still considered to be an improvement in functional quality part with a trade-off value 0.007249 in QoS. In task3, the benefit of functional part quality is clearer with an increase in both similarity quality and matchType quality of 0.056648 and 0.078862 while a slight decrease in QoS.  In conclusion, we can perceive that our evaluation could find out better functional quality with a reasonable trade off in QoS.

\section{Conclusion}\label{conclusion}
This work introduced a more applicable and simpler evaluation model for semantic automated web service composition that relies on semantic matchmaking quality extension to QoS-aware consideration. The key idea of these evaluation model is to consider the quality of semantic matchmaking corresponding to different matchmaking types, which is simply achieved by applying the similarity measures in parameter-related concepts, and those web services are involved in further selection for dealing optimised problems. Also, the effectiveness of our model is also proved to be able to obtain a better-optimised solution in better functional quality with a reasonable trade-off in QoS. Future works in this area should investigate in multi-objective optimisation as well as consider improving efficiency in the functional quality calculation.
\bibliographystyle{splncs03}
\bibliography{bibliography}

\end{document}

### 2016-10-20 paper.tex
update

@@
 \textbf{Semantic web service matchmaking}.
-Substantial work \cite{bansal2016generalized,mier2015integrated} on semantic web service composition focus particularly on functional requirements and negect non-functional requirements.
+Substantial work \cite{bansal2016generalized,mier2015integrated} on semantic web service composition focused mainly on functional requirements and negect non-functional requirements.
 This approach utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output concepts of web services to ensure a semantic matchmaking.
-Since semantic descriptions are introduced into web service, which is expressed in ontologies, the semantic matchmaking is to considered to seek similarity of parameters (i.e., input and output) of web services and pair a mapping between two knowledge representations encoded utilising the same ontology \cite{lecue2006formal}.
+Since semantic descriptions are introduced into web service, which is expressed in ontologies, the semantic matchmaking is to considered be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and pairing a mapping between two knowledge representations encoded utilising the ontology \cite{lecue2006formal}.
 In \cite{shet2012new}, the author surveyed three approaches the similarity measures using taxonomies: one is based on nodes, in which similarity is determined by the information content of the nodes; one is entirely based on edge, where concept distance in a hierarchy structure is evaluated,  and the hybrid approach that combines the previous two methods.
@@
 
-In \cite{lecue2009optimizing}, web services are connected as an semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, which apply one possible measure for similarity degree on nodes information demonstrated as Common Description rate of a semantic link in Formula \ref{equation2}.
-Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$and Least Subsume $lcs(Out_{s_i},In_{s_j})$.
-They chained the web service in five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint.
-The quality of the semantic link is estimated as quality criteria $q_{m}$(i.e.
-either 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection)) associated with their corresponding quality of vector $q_{cd}$ \ref{equation2}.
-The model is defined as follows.
-\begin{equation}
-\label{equation2}
-q(sl{_{i,j}}) \stackrel{.}{=} (q_{mt}(sl_{i,j}), \  q_{cd}(sl_{i,j}))
-\end{equation}
+In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, which utilise one possible measure for the degree of similarity using Common Description rate of a semantic link in Formula \ref{equation2}.
+And Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are also required to be pre-calculated in Formula \ref{equation2}.
+They chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint.
+Therefore, the quality of the semantic link is estimated as quality criteria $q_{m}$, either 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection) associated with their corresponding quality of vector $q_{cd}$ defined as Formula \ref{equation3}.
+
 \begin{equation}
 q_{cd}(sl{_{i,j}})={=} \frac{|lcs(Out_{s_i},In_{s_j})|}{|In_{s_{x}} \setminus Out_{s{_y}} \stackrel{.}| +|lcs(Out_{s_i},In_{s_j})| }
- \label{equation3}
+ \label{equation2}
 \end{equation}
 
-However, the weakness of this approach for semantic link quality is that calculating Extra Description and Least Subsume of out-input request requires well and complete defined DL in knowledge representation in the different domains, which makes it nearly impossible to be widely applied to semantic matchmaking measures in today's' web services application.
-Additionally, in their semi-auto workflow approach, they do not consider data-flow compatible and automated service composition.
+\begin{equation}
+\label{equation3}
+q(sl{_{i,j}}) \stackrel{.}{=} (q_{mt}(sl_{i,j}), q_{cd}(sl_{i,j}))
+\end{equation}
+
+However, the weakness of this approach for semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined DL in the knowledge representation system.
+for example, both service profiles definition described in OWL-S, and their related class, class axioms and properties defined in OWL2 are needed.
+This makes it nearly impossible to measure semantic matchmaking quality in most semantic web services applications.
+Additionally, a semi-automated service composition approach is considered by the author, rather than a fully automated method.
+Therefore, we introduce a more applicable evaluation model in a full automated semantic web service composition.
 
 \textbf{QoS-aware EC approaches}.
-Evolution Computing techniques are considered to be more effective for solving globally optimisation problem.
-Genetic Programming (GP) approaches \cite{da2015graphevol,da2016particle} are typical EC techniques widely applied to fully automated web service composition, which utilises a tree representation that service as the terminal nodes, and composite constructs as the functional nodes.
-The crossover and mutation process reproduce various individuals with ensuring correctness of structure.
-In \cite{yu2013adaptive}, the author optimises the quality of the overall composition by a complex fitness function, which is also liable for correctness in functionality through penalising solutions.
-To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, this approach is to find a optimised web service queue in the way of searching best location using PSO for optimised QoS, that service queue is involved in building a graph representation of web service composition later.
-However, the neglecting of leveraging the semantic difference between composite service output and customers' request could lead to the lower quality of functionality matchmaking with best quality of service in QoS-awaren web service composite paper \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph}.
-For example, a client asks for a particular AI textbook while output of the composte web service provides a general book.
-In this scenario, the output is a too broad consequences that have no meaning for the customers, even though web services are selected for a excellent composite QoS consideration.
-Therefore, we fill the gap to provide a more applicable approach to evaluate an overall quality in this paper.
+Evolution Computing techniques are widely used to solve optimisation problem.
+Genetic Programming (GP) \cite{da2015graphevol,da2016particle} is typical EC techniques to solve automated web service composition.
+GP-based approach utilises tree representations, on which service as represented as terminal nodes, and composite constructs as the functional nodes.
+The crossover and mutation operations reproduce various individuals while ensuring correctness of structure.
+In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by a fitness function, which is also liable for correctness in functionality through penalising infeasible solutions.
+To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is looked for using PSO considering optimising QoS for building up service queue, then the web services in this service queue are selected to build up a graph representation of web service composition.
+However, the composite solution does not distinguish different match types and the degree of matching, which could lead to the data returned by the selected service that we think may be too general.
+In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the data requested by users.
+In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS.
+Therefore, we fill the gap by considering different matching types and their similarity when evaluate an overall quality of composite service.
 
-\section{QoS-aware Semantic Autoamted Web Serivce Composition}\label{qswsc_approach}
+\section{QoS-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
 \begin{figure}[h]
@@
 \end{figure}
-On the support of the representation of our solution, in this section, we introduce our evaluation model in a graph-based representation for QoS-aware automatic semantic web service composition utilising PSO, which is considered to be simple and efficient without penalising and repairing comparing to GP \cite{da2014graph}.
+In this paper, we model automated QoS-ware semantic service composition with graphs.
+PSO has shown its efficiency in solving combinatorial optimisation problems.
+Therefore, we will propose a PSO based approach, which is considered to be simple and efficient without penalising and repairing comparing to GP \cite{da2014graph}.
 Fig.
 \ref{overview} shows the overview of our approach with the several steps included.
-The composite process is triggered by a composite goal defined in Subection \ref{problemDes}, which demonstrate customers requirements in terms of functional and non-functional requirement.
-The previous one is well defined as an overall input-output requirement, and the later one is the users' accepted quality of service.
-Those requirements are initially used to discover all relevant web services and their relationship in semantic matchmaking to get prepared for building graph representations.
-The second step of selecting relevant web services contributes to shrink the size of participated web services for dimensions of particles involved in future optimised problem.
+The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which demonstrate customers requirements in terms of functional and non-functional requirement.
+The previous functional one is defined as $F(T_{Input}, T_{Output})$ , and the later nonfunctional one is the users' accepted level of QoS.
+Those requirements are initially used to discover all relevant web services and their relationship in semantic matchmaking to get prepared for designing service composition via building graphs.
+The second step selects relevant web services related to services request.
+This leads to a shrunken service repository that is used by PSO-based algorithm.
 In the third step, a service composition graph randomly built up with considering the QoS and matchmaking quality.
@@
 The output of one service and its associated input of another service is calculated in the matchmaking phase where semantic matchmaking quality are measured which will be explained in Subsection \ref{qulityModel}.
-The further optimization of service composition solution is performed over the PSO in Section \ref{pso_algorithm}, which is used to find optimised particle locations mapped back to web service for service-graph building.
+The further optimisation of service composition solution is performed over the PSO in Section \ref{pso_algorithm}, which is used to find optimised particle locations mapped back to web service for service-graph building.
 This approach \cite{da2016particle} is an indirect representation of web service composition that constructing a graph-based composite service composition.
@@
 		\ForAll{particles in the swarm}{
-			\textbf{2.} Sort partcile's postion vector as a service queue in ascending order\\
+			\textbf{2.} Sort particle's position vector as a service queue in ascending order\\
 			\textbf{3.} Initialise OutputSet with Task Input\\
@@
 					\textbf{6.} Create and connect service edge associated with matchmaking quality to graph.\\
-					\textbf{7.} Create and connect node(current web serivce) to graph.\\
-					\textbf{8.} Remove current web service fromt the queue.\\
+					\textbf{7.} Create and connect node(current web service) to graph.\\
+					\textbf{8.} Remove current web service from the queue.\\
 					\textbf{9.} Update OutputSet with outputs current web service.\\
@@
 The overall algorithm investigated here is a combination of a simple forward decoding PSO \cite{da2016particle} and a graph-building technique \cite{blum1997fast} with our comprehensive quality evaluation model.
-The idea of that is to translate the particle location into a service queue as an indirect representation of service composition graph, finding the best fitness of the composite service solution is to figure out the optimised location of the particle.
-In PSO, the dimension of the particle is set up as the same as the number of relevant web services shrunk from serivce repository, and all of them are mapped to the particle location, put in a service queue and sorted in ascending order.
-The second method is to decode a corresponding graph built from that service queue.
-and it is a forward graph-building technique from a start node to the end node, we select and connect web services to startNode if this web service can satisfy the given Task input initialised in a Output Set, and this Output Set is updated after adding web service to the graph, later on, we services are keeping being selected and added if its added services' outputs in the Output Set could be satisfied, if the any outputs in the Output Set meets the Task's requriment, we end up graph building.
-In addition, dangle services and edges shoud be removed.
+The idea is to translate the particle location into a service queue as an indirect representation of service composition graph, finding the best fitness of the composite service solution is to discover the optimised location of the particle.
+In PSO, the dimension of the particle is set up as the same as the number of relevant web services in the shrunken service repository, each of which is mapped to a location in a particle, put services in a queue and sort in ascending order.
+The second method is to decode a corresponding graph built from that service queue using a forward graph-building technique from a start node to the end node.
+We select and connect web services to the startNode if this web service can satisfy the given Task input, and an Output Set is initialised and kept updating with outputs from new added web services in the graph, later on, we services are keeping being selected and added if services' inputs could be satisfied by any output in the Output Set, if the Output Set contains the Task's required outputs, we end up graph building.
+In addition, dangle service nodes and edges should be removed.
 At last, fitness value can be calculated by the construct-based aggregation.
@@
 The semantic matchmaking is achieved by utilising semantic annotation with OWL and MECE ontologies \cite{bleul2008self} with OWL and XWL format respectively.
-In OWL,  the semantics specifies the both concepts and individuals in forms of classes and instances but limited to taxonomies.
+In OWL, semantics specifies the both concepts and individuals in the forms of classes and instances but limited to taxonomies.
 The semantic concepts are expressed with the their statements and relationship in RDFs (such as subClassOf ), and the semantic individuals are related to the input and output parameters of web services.
 The MECE is an extensive annotation to WSDL files, which defines the each parameter of services associated with their semantic individuals.
-The overall matchingmaking process is demonstrated in Figure \ref{matchmaking}.
+The overall matching making process is demonstrated in Figure \ref{matchmaking}.
 
@@
 
-The semantic matchmaking transfer a function match (OutputS1, InputS2 ) to a pair of concept match (C2, C3) for the two web services defined in Section \ref{semantic Web service Discovery}.
+The semantic matchmaking transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match: $match(C_{2}, C_{3})$ defined in Section \ref{semantic Web service Discovery}.
 The matching mechanism attempts to determine whether correct match criteria between the source concepts of C1 and the target concepts of C2, and the quality of semantic matchmaking for the two its reasoning is also calculated in the quality model in the following Section ref{qulityModel}.
@@
 \subsection{Comprehensive quality model and aggregation matrix}\label{qulityModel}
-In this paper, we proposed a semantic matchmaking model to evaluate the semantic quality of two matched web services.
-Then we fill the gap of current prevailing QoS-aware optimisation consideration in the fully automated composition approach, which has not considered the quality of matchmaking for service selection.
+In this paper, we propose a semantic matchmaking model to evaluate the semantic quality of two matched web services, this fill the gap of current prevailing QoS-aware optimisation consideration in the fully automated composition approaches, which has not considered the quality of matchmaking for service selection.
 
 \textbf{Semantic matchmaking model}.
-Due to the discretizational characteristics of different match types, the match type quality is driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}, so that match type is considered to be one factor for the semantic quality.
-Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, a taxonomy based measurement for ontology matching, In our paper, it could be used to estimate the parameter concepts similarity between the output and input request for selecting the highest semantic-closeness web services.
+Due to the discretisational characteristics of different match types, which is driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}, so that match type is considered to be one factor for the semantic quality.
+Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, a taxonomy based measurement for ontology matching, In this paper, it could be used to estimate the parameter concepts similarity between the output and input of a request for selecting web services with close semantic matching.
 Therefore, given the quality match type and the similarity of two parameters, the semantic matchmaking quality is defined as Equation \ref{equation4}.$q(s_ {matchType})$ is set up as the same as the quality of the semantic link in literature \cite{lecue2009optimizing} (i.e.
@@
 \textbf{Comprehensive quality model}.
-Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional attributes of composite web service.
+Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional reguirements of composite web service.
 The non-functional properties typically refer to availability, reliability, cost and response time, which are given by service providers.
@@
 Typically, two web services are connected by more than one parameter-related concepts.
-In details, edge-level quality aggregation is determined by the mean of parameter-related concept quality in both semantic match type and similarity respectively, and construct-level quality is further calculated based on the edege-level quality aggregation following the rules in Table \ref{table1}, which is the quality aggregate matrix for semantic web service composition.
+In details, edge-level quality aggregation is determined by the mean of parameter-related concept quality in both semantic match type and similarity respectively, and construct-level quality is further calculated based on the edge-level quality aggregation following the rules in Table \ref{table1}, which is the quality aggregate matrix for semantic web service composition.
 The calculation of QoS aggregation is similar to \cite{cardoso2004quality} while semantic matchmaking aggregation is adopted from \cite{lecue2009optimizing}.
@@
 A weighted sum of those components is utilised in the fitness function \ref{equation7}, in which fitness value of 1 means the best overall quality and 0 means the worst.
-In addtion, aggregate value of each parameters must be normalised between 0 and 1.
-In details, $MT$, $S$, $A$, and $R$ are calculated in Formula \ref{equation8} while $T$ and $C$ are calculated in Formula \ref{equation9}.
+In addition, aggregate value of each parameters must be normalised between 0 and 1.
+In details, $MT$, $S$, $A$, $R$, $T$, and $C$ are normalised in Formula \ref{equation8}.
 
@@
 \label{equation7}
-fitness_i = w_1MT + w_2S + w_3A_i + w_4R_i + w_5(1 - T_i) + w_6(1 - C_i)
+Fitness = w_1MT + w_2S + w_3A + w_4R + w_5(1 - T) + w_6(1 - C)
 \end{equation}
@@
 \label{equation8}
-normalise(MT, S, A, or R) = 
+N(Q_{k}) = 
 \begin{cases}
 	\frac{value - min}{max - min} & \text{ if }max - min \neq 0.\\
-	1 & \mathrm{ otherwise}.
-\end{cases}
-\end{equation}
-
-\begin{equation}
-\label{equation9}
-normalise(T or C) = 
-\begin{cases}
-	\frac{max - value}{max - min} & \text{ if }max - min \neq 0.\\
 	1 & \mathrm{ otherwise}.
@@
 The objective of the evaluation are: 1) measure the effectiveness of the proposed comprehensive quality model in automated semantic web service composition approach, and explore the impact of the semantic matchmaking that contributes to overall composition quality.
-2) compare the optimised sollutions with using comprehensive evaluation model with using QoS-aware evaluation model to reveal the advantages of our novel method.
+2) compare the optimised solutions with using comprehensive evaluation model with using QoS-aware evaluation model to reveal the advantages of our novel method.
 
@@
 In addition, weights setting are more flexible defined by users' preferences.
-Simplely, we configure weights of fitness function as same leverage for balancing functional side and nonfunctional side.
+Simply, we configure weights of fitness function as same leverage for balancing functional side and nonfunctional side.
 Therefore, W1 and W2 are equals to 0.1 and 0.4 entirety 0.5,  and W3, W4, W5, W6 are all set to 0.125 summed 0.5.
@@
 
-We also investigate the variation in functional quality part including two subfactors --- average matchType quality and average similarity quality from generation 0 to 99 in second and third groups in Figure \ref{exp_fitnessvalue}.
+We also investigate the variation in functional quality part including two sub factors --- average matchType quality and average similarity quality from generation 0 to 99 in second and third groups in Figure \ref{exp_fitnessvalue}.
 In these groups,  both the average matchType quality and average similarity quality are the average value corresponding to the average best fitness so far found,  and further calculated their mean over 30 independent runs respectively.

### 2016-10-20 paper.tex
update

@@
 
-The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as composite goal: $G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$.
+The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$.
 This overall composite goal is demonstrated in two parts.
@@
 
-\subsection{Related Work}
+\subsection{Related Work} \label{relatedWork}
 \textbf{Semantic web service matchmaking}.
@@
 Fig.
-\ref{overview} shows the overview of our approach with the several steps included.
-The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which demonstrate customers requirements in terms of functional and non-functional requirement.
+\ref{overview} shows the overview of our approach with the five steps included.
+Step 1:The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements in terms of functional and non-functional requirement.
 The previous functional one is defined as $F(T_{Input}, T_{Output})$ , and the later nonfunctional one is the users' accepted level of QoS.
-Those requirements are initially used to discover all relevant web services and their relationship in semantic matchmaking to get prepared for designing service composition via building graphs.
-The second step selects relevant web services related to services request.
+Step 2: Those requirements are initially used to discover all relevant web services and their relationship in semantic matchmaking to get prepared for designing service composition via building graphs.
+This step selects relevant web services related to services request.
 This leads to a shrunken service repository that is used by PSO-based algorithm.
-In the third step, a service composition graph randomly built up with considering the QoS and matchmaking quality.
+Step 3: a service composition graph is randomly built up with considering the QoS and matchmaking quality.
 This graph building is interleaved with semantic matchmaking for services.
-The output of one service and its associated input of another service is calculated in the matchmaking phase where semantic matchmaking quality are measured which will be explained in Subsection \ref{qulityModel}.
-The further optimisation of service composition solution is performed over the PSO in Section \ref{pso_algorithm}, which is used to find optimised particle locations mapped back to web service for service-graph building.
+The output of one service and its associated input of another service is calculated in the matchmaking phase where semantic matchmaking quality are measured which will be explained in Subsection \ref{qualityModel}.
+Step 4,5: The optimisation of service composition solution is performed over the PSO in Section \ref{pso_algorithm}, which is used to find optimised particle locations mapped back to web service for service-graph building.
 This approach \cite{da2016particle} is an indirect representation of web service composition that constructing a graph-based composite service composition.
@@
 \end{algorithm}
-The overall algorithm investigated here is a combination of a simple forward decoding PSO \cite{da2016particle} and a graph-building technique \cite{blum1997fast} with our comprehensive quality evaluation model.
+The overall algorithm investigated here is a combination of a simple forward decoding PSO \cite{da2016particle} with our comprehensive quality evaluation model.
 The idea is to translate the particle location into a service queue as an indirect representation of service composition graph, finding the best fitness of the composite service solution is to discover the optimised location of the particle.
 In PSO, the dimension of the particle is set up as the same as the number of relevant web services in the shrunken service repository, each of which is mapped to a location in a particle, put services in a queue and sort in ascending order.
-The second method is to decode a corresponding graph built from that service queue using a forward graph-building technique from a start node to the end node.
+Later on, we decode a corresponding graph built from that service queue using a forward graph-building technique from a start node to the end node.
 We select and connect web services to the startNode if this web service can satisfy the given Task input, and an Output Set is initialised and kept updating with outputs from new added web services in the graph, later on, we services are keeping being selected and added if services' inputs could be satisfied by any output in the Output Set, if the Output Set contains the Task's required outputs, we end up graph building.
@@
 \subsection{Semantic matchmaking}
-The semantic matchmaking is achieved by utilising semantic annotation with OWL and MECE ontologies \cite{bleul2008self} with OWL and XWL format respectively.
+The semantic matchmaking is achieved by utilising semantic annotation with OWL and OWL-S.
+In this paper, we use MECE ontologies \cite{bleul2008self} XWL format, which could be considered to be an alternative form of ontology for services.
 In OWL, semantics specifies the both concepts and individuals in the forms of classes and instances but limited to taxonomies.
@@
 The semantic matchmaking transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match: $match(C_{2}, C_{3})$ defined in Section \ref{semantic Web service Discovery}.
-The matching mechanism attempts to determine whether correct match criteria between the source concepts of C1 and the target concepts of C2, and the quality of semantic matchmaking for the two its reasoning is also calculated in the quality model in the following Section ref{qulityModel}.
-The advantage of utilising semantic matchmaking is to enable a reasonable connection between two web services from different service providers to find more service solutions with better QoS.
+The matching mechanism attempts to determine whether correct match criteria between the source concepts of C1 and the target concepts of C2, and the quality of semantic matchmaking for these two concepts is calculated in the quality model in subSection \ref{qualityModel}.
+The advantage of utilising semantic matchmaking quality is to find a more closely requested service output with acceptable level of QoS.
 
-\subsection{Comprehensive quality model and aggregation matrix}\label{qulityModel}
-In this paper, we propose a semantic matchmaking model to evaluate the semantic quality of two matched web services, this fill the gap of current prevailing QoS-aware optimisation consideration in the fully automated composition approaches, which has not considered the quality of matchmaking for service selection.
+\subsection{Comprehensive quality model and aggregation matrix}\label{qualityModel}
+In this paper, we propose a semantic matchmaking model to evaluate the semantic quality of two matched web services, this fill the gaps in subsection \ref{relatedWork} of current prevailing QoS-aware optimisation, where quality of matchmaking for service selection are not considered.
 
 \textbf{Semantic matchmaking model}.
-Due to the discretisational characteristics of different match types, which is driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}, so that match type is considered to be one factor for the semantic quality.
+Due to the discretisational characteristics of different match types, which is driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}.
+Match type is considered to be one factor for the semantic quality.
 Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, a taxonomy based measurement for ontology matching, In this paper, it could be used to estimate the parameter concepts similarity between the output and input of a request for selecting web services with close semantic matching.
-Therefore, given the quality match type and the similarity of two parameters, the semantic matchmaking quality is defined as Equation \ref{equation4}.$q(s_ {matchType})$ is set up as the same as the quality of the semantic link in literature \cite{lecue2009optimizing} (i.e.
-either 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection)), and $q(s_ {similarity})$ is Equation \ref{equation1}.
+Therefore, given the quality match type and the similarity of two parameters, the semantic matchmaking quality is defined as Formula \ref{equation4}, where $q(s_ {matchType})$ is set up as the same as the quality of the semantic link in literature \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection) while $q(s_ {similarity})$ is calculated utilising formula \ref{equation1} in subsection \ref{relatedWork}.
 
@@
 \textbf{Comprehensive quality model}.
-Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional reguirements of composite web service.
-The non-functional properties typically refer to availability, reliability, cost and response time, which are given by service providers.
-Consequently, the comprehensive quality model integrated the semantic matchmaking quality and quality of service in Equation \ref{equation5}, which could be broken down into Equation \ref{equation6}.
+Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional requirements of composite web services.
+The non-functional properties typically refer previously discussed QoS, which are given by service providers.
+Consequently, the comprehensive quality model integrated the semantic matchmaking quality $q(s_{smq})$ in Formula \ref{equation5}, which could be further broken down into Formula \ref{equation6}.
 
@@
 \textbf{Quality aggregate matrix}.The quality aggregation is defined based on the constructs of composite web services on the criteria of functional and non-functional properties.
-Typically, two web services are connected by more than one parameter-related concepts.
-In details, edge-level quality aggregation is determined by the mean of parameter-related concept quality in both semantic match type and similarity respectively, and construct-level quality is further calculated based on the edge-level quality aggregation following the rules in Table \ref{table1}, which is the quality aggregate matrix for semantic web service composition.
-The calculation of QoS aggregation is similar to \cite{cardoso2004quality} while semantic matchmaking aggregation is adopted from \cite{lecue2009optimizing}.
+Typically, web services could have more than one concept-related parameters.
+Regarding semantic matchmaking part, edge-level quality aggregation is determined by the mean of concept-related parameter quality in both semantic match type and similarity respectively, and construct-level quality is further calculated based on the edge-level quality aggregation following the rules in Table \ref{table1}, which is the quality aggregate matrix for semantic web service composition.
+Semantic matchmaking aggregation considers two different factor aggregations: the matching type quality aggregation is calculated by the product function of involved edge-level matching type value, and the similarity quality average value of all edge-level similarity quality.
+The nonfunctional (QoS) aggregation calculation is same to \cite{cardoso2004quality}.
 
@@
 \centering
-\caption{Quality aggregate matrix for semanic web service composition}
+\caption{Quality aggregate matrix for semantic web service composition}
 \label{table1}
@@
 We run the experiment under computing grid comprising of almost 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine.
-Experimentation was done using the composite service approach explained in Section \ref{qswsc_approach}, and evaluated in the comprehensive quality model introduced in Section \ref{qulityModel}.
+Experimentation was done using the composite service approach explained in Section \ref{qswsc_approach}, and evaluated in the comprehensive quality model introduced in Section \ref{qualityModel}.
 The parameters were chosen based on general settings from \cite{shi2001particle}, In PSO approach, 30 particles evolved in 100 generations in the searching space, in which problem dimension's size equals to the relevant service size shown in graph.

### 2016-10-20 paper.tex
update

@@
 
- \item To evaluate the performance of proposed approaches, we utilise the datasets from Web Services Challenge 2009 (WSC'09) \cite{kona2009wsc}.
+ \item To evaluate the performance of proposed approaches, we utilise the datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
 \end{enumerate}
@@
 A weighted sum of those components is utilised in the fitness function \ref{equation7}, in which fitness value of 1 means the best overall quality and 0 means the worst.
-In addition, aggregate value of each parameters must be normalised between 0 and 1.
-In details, $MT$, $S$, $A$, $R$, $T$, and $C$ are normalised in Formula \ref{equation8}.
+As the sum of all the function weights (w1 to w6) is equal to 1, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised ranging from 0 to 1 so that the overall result falls within 0 to 1.
+Also, the lowest T and C value represent the best quality so that the objective function is offset using $(1 - T)$ and $(1 - C)$.
 
@@
 \noindent where $\sum_{i=1}^{6} w_i = 1$
-\\\\
-\begin{equation}
-\label{equation8}
-N(Q_{k}) = 
-\begin{cases}
-	\frac{value - min}{max - min} & \text{ if }max - min \neq 0.\\
-	1 & \mathrm{ otherwise}.
-\end{cases}
-\end{equation}
 
@@
 In this section, a quantitative evaluation approach is adopted in our experiment design.
-The objective of the evaluation are: 1) measure the effectiveness of the proposed comprehensive quality model in automated semantic web service composition approach, and explore the impact of the semantic matchmaking that contributes to overall composition quality.
-2) compare the optimised solutions with using comprehensive evaluation model with using QoS-aware evaluation model to reveal the advantages of our novel method.
+The objectives of the evaluation are to measure the effectiveness of the proposed comprehensive quality model in automated semantic web service composition approach, and to explore the impact of the semantic matchmaking that contributes to overall composition quality, and to compare solutions generated by QoS-ware approach with our method.
 
-We utilise the web service challenge 2009 (WSC’09) web service data sets to perform a standard evaluation.
-Compared to previous web service challenge dataset, WSC'09 is evolved with OWL for providing richer semantics.
-With an incremental number in concept, individuals and web services in each dataset, it is a proper dataset for the scalability measures in our defined quality evaluation model.Table 1 presents the features of the WSC’09 dataset.
+We utilise benchmark dataset web service challenge 2009 (WSC09) \cite{kona2009wsc} web service data sets to perform a standard evaluation.
+WSC09 designed OWL for providing richer semantics consisting tasks with variable size.
+With an incremental number in concept, individuals and web services in each dataset, it is a proper dataset for the scalability measures in our defined quality evaluation model.
+Table \ref{wsc09datasetTable} presents the features of the WSC’09 dataset.
 The number of concepts, individuals in the ontology and services of each data set is shown in the second, third, fourth column respectively.
-Also, we extend the all the datasets with QoS attributes from service providers to perform a comprehensive quality evaluation.
+Also, we extend all the datasets with QoS attributes from service providers to perform a comprehensive quality evaluation.
 \begin{table}[]
 \centering
-\caption{features of the WSC'09 datasets}
+\caption{Features of the WSC09 datasets}
 \label{wsc09datasetTable}
@@
 \multicolumn{1}{|c|}{Dataset} & No.Concept & No.Individual & No.Service \\ \hline
-WSC'09 01                     & 1578       &3102           &572      \\ \hline
-WSC'09 02                     & 12388      &24815          &4129      \\ \hline
-WSC'09 03                     & 18573      &37316          &8138      \\ \hline
-WSC'09 04                     & 18673      &37324          &8301      \\ \hline
+WSC09 01                     & 1578       &3102           &572      \\ \hline
+WSC09 02                     & 12388      &24815          &4129      \\ \hline
+WSC09 03                     & 18573      &37316          &8138      \\ \hline
+WSC09 04                     & 18673      &37324          &8301      \\ \hline
+WSC09 05                     & 31044      &62132          &15211    \\ \hline
 \end{tabular}
@@
 We run the experiment under computing grid comprising of almost 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine.
-Experimentation was done using the composite service approach explained in Section \ref{qswsc_approach}, and evaluated in the comprehensive quality model introduced in Section \ref{qualityModel}.
-The parameters were chosen based on general settings from \cite{shi2001particle}, In PSO approach, 30 particles evolved in 100 generations in the searching space, in which problem dimension's size equals to the relevant service size shown in graph.
+Experimentation was done using the approach explained in Section \ref{qswsc_approach}, and evaluated in the comprehensive quality model introduced in Subsection \ref{qualityModel}.
+The parameters were chosen based on general settings from \cite{shi2001particle} for our PSO-based approach, 30 particles evolved in 100 generations in the searching space, in which problem dimension's size equals to the relevant service size shown in graph.
 we run 30 times independently for each dataset.
-In addition, weights setting are more flexible defined by users' preferences.
-Simply, we configure weights of fitness function as same leverage for balancing functional side and nonfunctional side.
-Therefore, W1 and W2 are equals to 0.1 and 0.4 entirety 0.5,  and W3, W4, W5, W6 are all set to 0.125 summed 0.5.
+In addition, weights setting are flexibly defined by users' preferences.
+As part of their requirement, we configure weights of fitness function as the same to properly balance functional side and nonfunctional side.
+Therefore, $w_{1}$ and $w_{2}$ are equals to 0.1 and 0.4,  and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly.
 
@@
 \subsection{Convergence Test}\label{convergenceTest}
-The purpose of our experiment is to expose the results of our proposed approach are optimised comprehensive quality for web service challenge tasks utilising datasets from WSC’09.
-To study an overall effectiveness of evaluation model and investigate the impacts of all involved components that are contributing the weighted sum fitness functional.
-We analysis all the performance of these components in the whole evolutionary process in Figure \ref{exp_fitnessvalue}, in which the three tasks' experiment results are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average quality of service for generation 0-99 with optimum.
+To analysis the effectiveness of our approach, we explore the convergency rate of the proposed method in this section.
+We show the convergency of five tasks in WSC09.
+To further study an overall effectiveness of evaluation model and investigate the impacts of all involved components in the fitness function.
+We analysis all the performance of these components in the whole evolutionary process in Figure \ref{exp_fitnessvalue}, in which the five tasks' experiment results are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average quality of service for generation 0-99 with optimum.
 \begin{figure}[h]
@@
 \includegraphics[width=12cm]{convergency.pdf}}}
- \caption{Average fitness, Average MatchType quality, Average Similarity quality and Average QoS per generation with comprehensive quality optimum}
+ \caption{Average Fitness, Average MatchType Quality, Average Similarity quality and Average QoS per generation with comprehensive quality optimum}
  \label{exp_fitnessvalue}
@@
 It is obviously that the overall trend of QoS moves upward in three tasks, and reach almost constant later on.
-Luckiely, we reach a very good state for QoS value, because we don't see too much trade-off from QoS regarding the improvement in functional quality part.
+Luckily, we reach a very good state for QoS value, because we don't see too much trade-off from QoS regarding the improvement in functional quality part.
 
@@
 The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections.
-Besides that, $q_{mt}$ and $q_{s}$) are calcuated for all edges ${e_{1}, e_{2},...
-e_{n}}$, and further aggregateed in $Q_{mt}$ and $Q_{s}$ respectively.In addtion, $Q_{QoS}$ is calcuated the all the non-functional attributes of $V$ using aggregation rules defined before.
+Besides that, $q_{mt}$ and $q_{s}$) are calculated for all edges ${e_{1}, e_{2},...
+e_{n}}$, and further aggregated in $Q_{mt}$ and $Q_{s}$ respectively.In addtion, $Q_{QoS}$ is calculated the all the non-functional attributes of $V$ using aggregation rules defined before.
 
-After well-defined solutions are discussed, we will look at $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ using  black-box testing for sollution comparision, where these components in both comprehensive quality evaluation approach and traditional QoS-ware one \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} are compared to reveal how good our evaluation mode is.
-In a decision table \ref{decisionTable}, these two models are interpreted as a rule set considering three different conditions (three independent tasks) associated with three corresponding sollutions.
-In each sollution, we compare $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$, where $Q_{QoS}$ is normalised to make them comparable from 0 to 1 in our method.
+After well-defined solutions are discussed, we will look at $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ using  black-box testing for solution comparision, where these components in both comprehensive quality evaluation approach and traditional QoS-ware one \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} are compared to reveal how good our evaluation mode is.
+In a decision table \ref{decisionTable}, these two models are interpreted as a rule set considering three different conditions (three independent tasks) associated with three corresponding solutions.
+In each solution, we compare $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$, where $Q_{QoS}$ is normalised to make them comparable from 0 to 1 in our method.
 From the table below.
@@
                                       & dataset3             & $\surd$              & $\surd$                            \\ \hline
-\multirow{3}{*}{\shortstack{Task1\\Optimised sollution}}  &$Q_{mt}$                      & .232635              & .232635                          \\ \cline{2-4} 
+\multirow{3}{*}{\shortstack{Task1\\Optimised solution}}  &$Q_{mt}$                      & .232635              & .232635                          \\ \cline{2-4} 
                                       &$Q_{s}$                       & .903572              & .903572                          \\ \cline{2-4}
                                       &$Q_{QoS}$                     & .578577              & .578577                          \\ \hline
-\multirow{3}{*}{\shortstack{Task2\\Optimised sollution}}  &$Q_{mt}$                      & .001828              & .000851$\downarrow$               \\ \cline{2-4} 
+\multirow{3}{*}{\shortstack{Task2\\Optimised solution}}  &$Q_{mt}$                      & .001828              & .000851$\downarrow$               \\ \cline{2-4} 
                                       &$Q_{s}$                       & .917172              & .938840$\uparrow$                 \\ \cline{2-4}
                                       &$Q_{QoS}$                     & .480251              & .473002$\downarrow$               \\ \hline
-\multirow{3}{*}{\shortstack{Task3\\Optimised sollution}}  &$Q_{mt}$                      & .191188              & .247836$\uparrow$                  \\ \cline{2-4} 
+\multirow{3}{*}{\shortstack{Task3\\Optimised solution}}  &$Q_{mt}$                      & .191188              & .247836$\uparrow$                  \\ \cline{2-4} 
                                       &$Q_{s}$                       & .951509              & .973723$\uparrow$                  \\ \cline{2-4}

### 2016-10-21 paper.tex
update

@@
                                       &$Q_{QoS}$                     & .493927              & .491538$\downarrow$                 \\ \hline
+\multirow{3}{*}{\shortstack{Task4\\Optimised solution}}  &$Q_{mt}$   & .919678              & .943406$\uparrow$                  \\ \cline{2-4} 
+                                      &$Q_{s}$                       & .000000              & .000009$\uparrow$                  \\ \cline{2-4}
+                                      &$Q_{QoS}$                     & .480818              & .472485$\downarrow$                 \\ \hline
+\multirow{3}{*}{\shortstack{Task5\\Optimised solution}}  &$Q_{mt}$   & .000094              & .000109$\uparrow$                  \\ \cline{2-4} 
+                                      &$Q_{s}$                       & .927476              & .930975$\uparrow$                  \\ \cline{2-4}
+                                      &$Q_{QoS}$                     & .476236              & .475128$\downarrow$                 \\ \hline                                                   
 \end{tabular}

### 2016-10-21 paper.tex
update

@@
 Firstly, the average fitness value over 100 generations is calculated by the average best fitness so far found per generation over 30 independent runs.
-The marked value plotted in the first group of the figure ranges from 0 to 1, and it is considered to be more optimised if its value is closer to value 1.
-We can see that there is a significant increase in the fitness value between generation 0 and generation 15-25, the remained generation continues to perform a very slight improvement in the fitness value and reach a plateau with no further changes.
-Furthermore, it is a common feature in three tasks’ average fitness graph.
-Also, there is a fast convergence of the population can be observed.
-That is simply because of many repetitive solutions as the indirect web service composition representation, although it is a large search space.
+The value plotted in the first column group of figure \ref{exp_fitnessvalue} ranges from 0 to 1, and it is considered to be more optimised if its value is closer to value 1.
+We can see that there is a significant increase in the fitness value (avg) with optimum between generation 0 and generation 15-25, the remained generation continues to produce a steady but moderate improvement in the fitness value and eventually reach a plateau with no further changes.
+The same behaviour is observed over the rest tasks.
+Also, there is a fast convergence of the fitness value can be observed.
+That is simply because of many repetitive solutions as the indirect web service composition representation in a large search space.
 
-We also investigate the variation in functional quality part including two sub factors --- average matchType quality and average similarity quality from generation 0 to 99 in second and third groups in Figure \ref{exp_fitnessvalue}.
-In these groups,  both the average matchType quality and average similarity quality are the average value corresponding to the average best fitness so far found,  and further calculated their mean over 30 independent runs respectively.
+We also investigate the variation in functional quality part including two sub factors --- average matchType quality and average similarity quality from generation 0 to 99 in second and third column groups in Figure \ref{exp_fitnessvalue}.
+In these groups,  both the average matchType quality and average similarity quality are the average value corresponding to the average best fitness so far found plotted in the first column group,  and further calculated their mean over 30 independent runs respectively.
 The dominant tendency of the marked value representing a similar characteristic compared to the average fitness value group trend.
-However, there are some slight fluctuations over the generations, and it could be reasonably treated as a typical situation that theoretically single objective function prevents selecting the lowest semantic matchmaking quality without granting for the excellent, yet the combination of all the influential functional quality part evolved towards an optimised solution.
+However, there are some slight fluctuations over the generations, and it could be reasonably treated as a typical situation that theoretically single objective function prevents selecting the lowest semantic matchmaking quality without granting for the excellent.
 
 Lastly, It is interesting to look at the average QoS per generation for the 30 independent runs if the behaviour of functional part performance is towards a higher value, where QoS is the value corresponding to the best fitness so far found in each generation.
-We construct the results in the fourth groups in Figure \ref{exp_fitnessvalue}.
-It is obviously that the overall trend of QoS moves upward in three tasks, and reach almost constant later on.
-Luckily, we reach a very good state for QoS value, because we don't see too much trade-off from QoS regarding the improvement in functional quality part.
+We construct the results in the fourth column group in Figure \ref{exp_fitnessvalue}.
+It is obvious that the overall trend of QoS moves upward to a high constant level in five independent tasks.
+Additionally, QoS (avg) with optimum have evolved towards an overall excellent state, because we don't see too much trade-off from QoS regarding the improvement in functional quality part.
 
@@
 e_{n}}$ where $e1$ is define as $(S_{1},S_{2})={q_{mt}, q_{s}}$.
-Here we provide an uncomplicated example of the web service composition solution to problem1, which can be described in the Figure \ref{wscs}.
+Here we provide an example of the web service composition solution to task 1, which can be described in the Figure \ref{wscs}.
 The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections.
 Besides that, $q_{mt}$ and $q_{s}$) are calculated for all edges ${e_{1}, e_{2},...
-e_{n}}$, and further aggregated in $Q_{mt}$ and $Q_{s}$ respectively.In addtion, $Q_{QoS}$ is calculated the all the non-functional attributes of $V$ using aggregation rules defined before.
+e_{n}}$, and further aggregated in $Q_{mt}$ and $Q_{s}$ respectively.In addtion, $Q_{QoS}$ is calculated by all the non-functional attributes of $V$ using aggregation rules defined before.This standard solution model helps us to make better comparison for evaluating the results from different approaches.
 
-After well-defined solutions are discussed, we will look at $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ using  black-box testing for solution comparision, where these components in both comprehensive quality evaluation approach and traditional QoS-ware one \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} are compared to reveal how good our evaluation mode is.
-In a decision table \ref{decisionTable}, these two models are interpreted as a rule set considering three different conditions (three independent tasks) associated with three corresponding solutions.
+After a well-defined solution is discussed, we will look at $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ defined in the solution model using  black-box testing for solution comparison, where these components in both comprehensive quality evaluation approach and traditional QoS-ware one \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} are compared to reveal how good our evaluation mode is.
+In a decision table \ref{decisionTable}, these two models are interpreted as a rule set considering five different conditions (five independent tasks) associated with three corresponding solutions.
 In each solution, we compare $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$, where $Q_{QoS}$ is normalised to make them comparable from 0 to 1 in our method.

### 2016-10-21 paper.tex
update

@@
 This approach \cite{da2016particle} is an indirect representation of web service composition that constructing a graph-based composite service composition.
-
-\subsection{QoS-aware Semantic Web Service Composition algorithm} \label{pso_algorithm}
-\begin{algorithm}[!htb]
- \setlength\hsize{0.9\linewidth}
- \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
- \let\oldnl\nl% Store \nl in \oldnl
-\newcommand{\nonl}{\renewcommand{\nl}{\let\nl\oldnl}}
- \LinesNumbered
-	\textbf{1.} Randomly initialise each particle in the swarm.\\
-	\nonl \While {max. iterations not met}{
-		\ForAll{particles in the swarm}{
-			\textbf{2.} Sort particle's position vector as a service queue in ascending order\\
-			\textbf{3.} Initialise OutputSet with Task Input\\
-			\textbf{4.} Initialise a graph with a startNode associated with Task Input as its output\\
-			\nonl \While {max. OutputSet not contains Task Input}{
-				\textbf{5.} Get web service from service queue\\
-				\If{All inputs of current web service satisfied with output from outputSet}{
-					\textbf{6.} Create and connect service edge associated with matchmaking quality to graph.\\
-					\textbf{7.} Create and connect node(current web service) to graph.\\
-					\textbf{8.} Remove current web service from the queue.\\
-					\textbf{9.} Update OutputSet with outputs current web service.\\
-				}
-				\textbf{10.} Get next web service from service queue\\
-			}
-			\textbf{11.} Connect endNode the graph\\
-			\textbf{12.} Remove dangle services from the graph\\
-			\textbf{13.} Remove dangle edges\\
-			\textbf{14.} Aggregation of semantic matchmaking and QoS\\
-			\textbf{15.} Calculate the particle's fitness.\\
-			\Indp $fitness_i = w_1SDst + w_2A_i + w_3R_i + w_4(1 - T_i) + w_5(1 - C_i)$ where $\sum_{i=1}^{5} w_i = 1$ \\
-			\eIf{fitness value better than pBest}{
-				\textbf{16.} Assign current fitness as new pBest.\\
-			}{
-				\textbf{17.} Keep previous pBest.\\
-			}		
-		}
-		\textbf{18.} Assign best particle's pBest value to gBest, if better than gBest.\\
-		\textbf{19.} Calculate the velocity of each particle according to the equation:\\
-		\Indp $v_{id} = v_{id} + c_1 * rand() * (p_{id} - x_{id}) + c_2 * rand() * (p_{gd} - x_{id})$\\
-		\Indm \textbf{19.} Update the position of each particle according to the equation:\\
-		\Indp $x_{id} = x_{id} + v_{id}$\\
-	}
-
- \caption{Steps of graph-based PSO optimisation technique.}
-\label{psoSteps}
-\end{algorithm}
-The overall algorithm investigated here is a combination of a simple forward decoding PSO \cite{da2016particle} with our comprehensive quality evaluation model.
-The idea is to translate the particle location into a service queue as an indirect representation of service composition graph, finding the best fitness of the composite service solution is to discover the optimised location of the particle.
-In PSO, the dimension of the particle is set up as the same as the number of relevant web services in the shrunken service repository, each of which is mapped to a location in a particle, put services in a queue and sort in ascending order.
-Later on, we decode a corresponding graph built from that service queue using a forward graph-building technique from a start node to the end node.
-We select and connect web services to the startNode if this web service can satisfy the given Task input, and an Output Set is initialised and kept updating with outputs from new added web services in the graph, later on, we services are keeping being selected and added if services' inputs could be satisfied by any output in the Output Set, if the Output Set contains the Task's required outputs, we end up graph building.
-In addition, dangle service nodes and edges should be removed.
-At last, fitness value can be calculated by the construct-based aggregation.
-
 \subsection{Semantic matchmaking}
@@
 
+\subsection{QoS-aware Semantic Web Service Composition algorithm} \label{pso_algorithm}
+\begin{algorithm}[!htb]
+ \setlength\hsize{0.9\linewidth}
+ \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
+ \let\oldnl\nl% Store \nl in \oldnl
+\newcommand{\nonl}{\renewcommand{\nl}{\let\nl\oldnl}}
+\textbf{Input}: I, O \\
+\textbf{Output}: G \\
+ \LinesNumbered
+	\textbf{1.} Randomly initialise each particle in the swarm.\\
+	\nonl \While {max. iterations not met}{
+		\ForAll{particles in the swarm}{
+			\textbf{2.} Sort particle's position vector as a service queue in ascending order\\
+			\textbf{3.} Initialise OutputSet with Task Input: I\\
+			\textbf{4.} Initialise a graph G with a startNode\\
+			\nonl \While {max. OutputSet not contains Task Output: O}{
+				\textbf{5.} Get web service from service queue\\
+				\If{All inputs of current web service satisfied with output from outputSet}{
+					\textbf{6.} Create and connect service edge associated with matchmaking quality to graph.\\
+					\textbf{7.} Create and connect node(current web service) to graph.\\
+					\textbf{8.} Remove current web service from the queue.\\
+					\textbf{9.} Update OutputSet with outputs current web service.\\
+				}
+				\textbf{10.} Get next web service from service queue\\
+			}
+			\textbf{11.} Connect endNode the graph G\\
+			\textbf{12.} Remove dangle services from the graph G\\
+			\textbf{13.} Remove dangle edges from graph G\\
+			\textbf{14.} Aggregation of semantic matchmaking and QoS\\
+			\textbf{15.} Calculate the particle's fitness.\\
+			\eIf{fitness value better than pBest}{
+				\textbf{16.} Assign current fitness as new pBest.\\
+			}{
+				\textbf{17.} Keep previous pBest.\\
+			}		
+		}
+		\textbf{18.} Assign best particle's pBest value to gBest, if better than gBest.\\
+		\textbf{19.} Calculate the velocity of each particle according to the equation:\\
+		\textbf{19.} Update the position of each particle according to the equation:\\
+	}
+
+ \caption{Steps of graph-based PSO optimisation technique.}
+\label{psoSteps}
+\end{algorithm}
+The overall algorithm investigated here is a combination of a simple forward decoding PSO \cite{da2016particle} with our comprehensive quality evaluation model.
+The idea is to translate the particle location into a service queue as an indirect representation of service composition graph, finding the best fitness of the composite service solution is to discover the optimised location of the particle.
+In PSO, the dimension of the particle is set up as the same as the number of relevant web services in the shrunken service repository, each of which is mapped to a location in a particle, put services in a queue and sort in ascending order.
+Later on, we decode a corresponding graph built from that service queue using a forward graph-building technique from a start node to the end node.
+We select and connect web services to the startNode if this web service can satisfy the given Task input, and an Output Set is initialised and kept updating with outputs from new added web services in the graph, later on, we services are keeping being selected and added if services' inputs could be satisfied by any output in the Output Set, if the Output Set contains the Task's required outputs, we end up graph building.
+In addition, dangle service nodes and edges should be removed.
+At last, fitness value can be calculated by the construct-based aggregation.
+
 \section{Experiment Design}\label{experiment_design}
@@
 After a well-defined solution is discussed, we will look at $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ defined in the solution model using black-box testing for solution comparison, where these components in both comprehensive quality evaluation approach and traditional QoS-ware one \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} are compared to reveal how good our evaluation mode is.
-In a decision table \ref{decisionTable}, these two models are interpreted as a rule set considering five different conditions (five independent tasks) associated with three corresponding solutions.
-In each solution, we compare $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$, where $Q_{QoS}$ is normalised to make them comparable from 0 to 1 in our method.
-From the table below.
+In a decision table \ref{decisionTable}, optimised solution using these two evaluation models are compared under five independent tasks in WSC09 dataset.
+In each task solution, we compare $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$, where $Q_{QoS}$ is normalised to make them comparable from 0 to 1 in our method.
 
@@
 \hline
-\multicolumn{2}{|c|}{\multirow{2}{*}{}}                              & Rule 1               & Rule 2                           \\ \cline{3-4} 
+\multicolumn{2}{|c|}{\multirow{2}{*}{}}                              &Approach 1           &Approach 2                           \\ \cline{3-4} 
 \multicolumn{2}{|c|}{}                                               & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
@@
 \end{table}
-From the table \ref{decisionTable}, Task 1 represents the same solution that can be observed in values of  $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$ using the smallest dataset size with the lowest complexity of ontologies and valid solutions.
-However, we can recognise trade-offs in task2 and task3 using our evaluation model, where a 0.021668 increase and a 0.00098 decrease in similarity quality and matchType quality with weights 0.4 and 0.1 respectively so that it is still considered to be an improvement in functional quality part with a trade-off value 0.007249 in QoS.
+From the table \ref{decisionTable}, Task 1 represents the same solution that can be observed in values of  $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$ using the smallest dataset size with the lowest size of ontologies.
+However, we can recognise trade-offs in task2 and task3 using our evaluation model, where a 0.021668 increase and a 0.00098 decrease in similarity quality and matchType quality with weights 0.4 and 0.1 respectively so that solution to task 2 is still considered to be an improvement in functional quality part with a trade-off value 0.007249 in QoS.
 In task3, the benefit of functional part quality is clearer with an increase in both similarity quality and matchType quality of 0.056648 and 0.078862 while a slight decrease in QoS.
+later on, the performance is the same in task 4 and task 5.
 In conclusion, we can perceive that our evaluation could find out better functional quality with a reasonable trade off in QoS.

### 2016-10-21 paper.tex
update

@@
 
-\title{A Novel Comprehensive Quality Evaluation Model in Automated Semantic Web Service Composition}
+\title{Comprehensive Quality Awareness Automated Semantic Web Service Composition}
 
@@
 Semantic web service composition has been a prevailing research area in recent years.
-There are two major governance challenges faced by researchers, and Semantic matchmaking is to discover interoperable web services, which demands a rich “machine understanding” language such as OWL-S (Web Ontology language for Web Services), WSML (Web Service Modeling language, SAWSDL (Semantic Annotations for WSDL and XML Schema).
+There are two major governance challenges faced by researchers, one is semantic matchmaking for discovering interoperable web services, which demands a rich “machine understanding” language such as OWL-S (Web Ontology language for Web Services), WSML (Web Service Modeling language, SAWSDL (Semantic Annotations for WSDL and XML Schema).
 This interaction enables us to pair service functionalities through language understanding and reasoning.
-An optimisation problem is the another challenge with consideration in non-functional attributes, such as quality of service (QoS).
-Nowadays, many scholars have looked into optimisation problems in QoS-awareness web service composition applying AI planning and Evolution Computing techniques.
+An optimisation problem is another challenge, many scholars have looked into the nonfunctional optimisation problems in QoS-awareness web service composition applying AI planning and Evolution Computing techniques.
 However, it is not sufficient without considering good balancing between functional and nonfunctional quality in most scenarios.
-Therefore, the consideration in these two quality dimensions is a must, so that a comprehensive quality evaluation model is proposed to deal with finding optimised semantic web service composition solution.
-This paper develops a more applicable approach dealing with a comprehensive quality ---semantic matchmaking and QoS optimisation for automated semantic web service composition.
+Therefore, the consideration in these two quality dimensions is a must, so that comprehensive quality  awareness semantic web service composition is proposed to deal with optimising composition solution.
+This paper develops a more applicable approach for comprehensive quality in semantic matchmaking and QoS optimisation for automated semantic web service composition.
 \end{abstract}
@@
 Service-oriented computing (SOC) is a novel computing paradigm that employs services as fundamental elements to achieve agile development of cost-efficient and integratable enterprise applications in heterogeneous environments \cite{papazoglou2003service}.
-Service Oriented Architecture (SOA) could abstractly realise service-oriented paradigm of computing, this accomplishment has been contributing to reuse of software components, from the concept of functions to units and from units to services during the development in SOA \cite{booth2004web}.
+Service Oriented Architecture (SOA) could abstractly realise service-oriented paradigm of computing, this accomplishment has been contributing to reuse of software components, from functions to units and from units to services during the development in SOA \cite{booth2004web}.
 One of the most typical realisations of SOA is \textit{web service}, which designated as ``modular, self-describing, self-contained applications that are available on the Internet'' \cite{curbera2001web}.
-Several standards play a significant role in registering, enquiring and grounding web services, such as UDDI, WSDL and SOAP \cite{fensel2011semantic}.
+And several standards play a significant role in registering, enquiring and grounding web services, such as UDDI, WSDL and SOAP \cite{fensel2011semantic}.
 
-\textit{Web service composition} pertains to a combination of several web services to provide a value-added composite service that accommodates customers' arbitrarily complex requirements.
+\textit{Web service composition} pertains to a combination of several web services to provide a value --- added composite service that accommodates customers' arbitrarily complex requirements.
 This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems - diverse platforms and programming languages \cite{casati2001technologies}.
 Due to an increase in a large-scale alignment of enterprise applications, the number of Web services has increased dramatically and unprecedentedly, which cause an immense redundancy in functionality in a huge searching space.
-Therefore, manual service and semi-automated web service composition are considered to be lower efficiency while automated web service composition is considered to be less human intervention, less time consumption, and high productivity.
+Therefore, manual service and semi-automated web service composition are considered to be less efficient while automated web service composition is deemed to be less human intervention, less time consumption, and high productivity.
 
@@
 The syntactic dimension has achieved success through the use of XML standards (such as $WSDL$, $SOAP$), the semantics dimension, on the other hand, demands further research.
-Adding semantics given by ontologies \cite{o2005review} enables web service to understand and reason with each other.
+Those semantics given by ontologies \cite{o2005review} enables web service to understand and reason with each other.
 Historically, there are many ontologies languages and formats for semantic service descriptions, such as OWL-S \cite{martin2004owl}, WSML \cite{fensel2006enabling}, and SAWSDL \cite{lausen2007semantic}, The logical characteristics in reasoning makes ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments.
@@
 
-Existing works on service composition are often addressed regarding one of the above challenges.
+Existing works on service composition are often addressed regarding the above challenges.
 One group optimises the quality of compositions under a pre-defined abstract workflow, which is considered to be a \textit{semi-automated Web service composition} approach.
@@
 In the last few years, substantial work has been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}.
-Howevever, few works have addressed an automatic semantic web service composition approach, which optimise both QoS and quality of semantic matchmatching as optimised web service composition sollutions.
-For example, customers prefer the highest quality of service solution associated with the acceptable semantic matchmatching quality.
+However, few works have addressed an automatic semantic web service composition approach, which optimise both QoS and quality of semantic match matching as web service composition solution.
+For example, customers prefer the highest quality of service solution associated with the acceptable semantic match matching quality.
 
-The overall goal of this paper is to develop an comprehensive evaluation model in  automated semantic web service composition that satisfactorily optimises both functional and non-functional requirements.
-Particularly, this project considers a semantic matchmaking quality extension to QoS awareness and a few structural constructs(sequence and parallel) for building optimised composition solution using Particle Swarm Optimisation.
+The overall goal of this paper is to develop an comprehensive quality awareness automated semantic web service composition that satisfactorily optimises both functional and non-functional requirements.
+Particularly, this project considers a semantic matchmaking quality extension to QoS awareness and a few structural constructs (sequence and parallel) for building optimised composition solution using Particle Swarm Optimisation.
 We aim to provide a more general and applicable way to measure semantic matchmaking in automated semantic web service composition and contribute to the state-of-the-art in this field.
@@
 \begin{enumerate}
- \item To address semantic matchmaking quality with considering different matching types associated with corresponding semantic similarity, which is demonstrated as a comprehensive quality --- a more general and applicable evaluation method utilising semantic information of service descriptions in this paper.
+ \item To address semantic matchmaking quality in considering different matching types associated with corresponding semantic similarity, which is demonstrated in a comprehensive quality integrated with QoS --- a more general and applicable evaluation model utilising semantic information of web services in this paper.
 
- \item To apply PSO for sorting an optimised service queue as a indirect representation of web service composition with consideration in optimising the comprehensive quality, this indirect representation is decoded using graph building algorithm to generate a service composite solution.
+ \item To apply PSO for sorting out an optimised service queue as a indirect representation of web service composition with consideration in comprehensive quality, and this service queue is decoded using graph building algorithm to generate optimised comprehensive quality awareness   composite solution.
 
- \item To evaluate the performance of proposed approaches, we utilise the datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
+ \item To Compare the performance of comprehensive quality awareness service composition with the QoS-awareness utilising the benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
 \end{enumerate}
@@
 This overall composite goal is demonstrated in two parts.
-One part is that a given input or input set to get the desired output or output set, it typically refers to a statement in functional requirement ; another part specify the overall acceptable composite quality, which covers aspects in non-functionality.
-To accomplish the first half goal, two stages are involved in the investigation of this paper : services discovery and service selection.
-Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from Service Repository: $S \{S_{1}, S_{2},..., S_{n} \}$ with the given Task until the desired output found.
-It results in more than one solutions without considering optimisation; Service selection is to select web services to reach global best quality($T_{QoS}$).
-We are aiming to optimise a combined objective function involving both functional and non-functional concerns.
-Particularly in this paper, two challenges mentioned in Sect.
-\ref{introduction} are addressed in semantic web composite approach.
-First, the inputs of each service could be semantically matched by predecessor services in the composition.
-Second, optimisation in QoS would not be sufficient in many scenarios to make a good decision, if customers are looking for a trade off either in better service quality with counteroffer in QoS or better QoS with less strict functional matchmaking quality.
+The first functional part is  a given task input or input set to get the desired Task output or output set, it typically refers to a statement of user's functional requirement; another nonfunctional part specifies the acceptable composite quality of service.
+To accomplish the composte goal, two stages are involved: services discovery and service selection.
+Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from Service Repository: $S \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$, and updated $T_{Input}$ with found services output, which is used to further discovery more related services until the desired $T_{Output}$ found.
+It normally results in more than one solutions.
+Service selection is to select one of those composite solution considering closest QoS to $T_{QoS}$.
+To ensure the composite solution returns exact the same or very close $T_{Output}$, we consider a comprehensive quality in both discovery and selection stages, where two challenges mentioned in Sect.
+\ref{introduction} are also addressed in Sect.
+\ref{qswsc_approach},
 
@@
 A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$ with both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Tax\}$.
-The web service discovery process is to discovery the services an input-output concept matchmaking according to the Taxonomy(Tax) within an ontology (O).
-To measure the quality of semantic matchmaking, different matching levels that are typically considered in the literature \cite{paolucci2002semantic}.
-We defined two web services associated with parameters in a particular domain: $S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S2$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$ defined in.
+The web service matching process is to pair the two services' output and input concepts according to the Taxonomy(Tax) within an ontology (O).
+To measure the quality of semantic matchmaking, different matching levels that are typically considered in the literature \cite{paolucci2002semantic}: We defined two web services associated with parameters in a particular domain: $S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S2$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$ defined in.
 
@@
 Note that, to find relevant services to automatically form suitable and applicable service compositions for a given goal, we consider Exact, Plugin and Fail match types in our paper.
-Therefore, these three robust and valid matches will be used to discover web service candidate for a service composition.
+Therefore, these three robust and valid matches will be used to discover web service candidates for a service composition.
 
-\subsection{Quality of Service and Composition Constructs}\label{web service selection}
+\subsection{Quality of Service and Composition Constructs}\label{Quality of Service and Composition Constructs}
 Currently, most of the optimisation problems \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} in web service composition are focusing on QoS optimisation, which covers aspects in non-functional requirements.
-This problem have been explored in optimising both single objective and multi-objectives in QoS.
+This problem have been explored in both single objective and multi-objectives optimisation.
 Ideally, customers prefer lowest execution cost with highest response time and reliability.
-According to \cite{zeng2003quality}, four most often considered QoS parameters are as following:
+According to \cite{zeng2003quality}, four most often considered QoS parameters are as follows:
 \begin{itemize}
@@
 The aggregation value of QoS attributes for web services composition varies with respect to different constructs, which explains how services associated with each other \cite{zeng2003quality}.
-Here we consider two composite constructs: sequence and parallel are used in building the composite flow, which are described as follows:
+Here we consider two composite constructs: both sequence and parallel construts are used in building the composite flow, which are described as follows:
 
@@
 \textbf{Semantic web service matchmaking}.
-Substantial work \cite{bansal2016generalized,mier2015integrated} on semantic web service composition focused mainly on functional requirements and negect non-functional requirements.
-This approach utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output concepts of web services to ensure a semantic matchmaking.
-Since semantic descriptions are introduced into web service, which is expressed in ontologies, the semantic matchmaking is to considered be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and pairing a mapping between two knowledge representations encoded utilising the ontology \cite{lecue2006formal}.
-In \cite{shet2012new}, the author surveyed three approaches the similarity measures using taxonomies: one is based on nodes, in which similarity is determined by the information content of the nodes; one is entirely based on edge, where concept distance in a hierarchy structure is evaluated,  and the hybrid approach that combines the previous two methods.
-A new similarity measure based on edge counting is introduced in a Ontology in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}.
-Neighbourhood concepts are considered in their model in Formular \ref{equation1}, where $\lambda$ = 1 (default value as 0).
+Substantial work \cite{bansal2016generalized,mier2015integrated} on semantic web service composition focused mainly on functional requirements while neglecting non-functional requirements.
+Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output concepts of web services to ensure a semantic matchmaking.
+Since semantic descriptions are introduced into web service, the semantic matchmaking is to considered be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and pairing a mapping between two knowledge representations encoded utilising the ontology \cite{lecue2006formal}.
+In \cite{shet2012new}, the author surveyed three approaches to the similarity measures using taxonomies: one is based on nodes, in which similarity is determined by the information content of the nodes; one is entirely based on edge, where concept distance in a hierarchy structure is evaluated,  and the hybrid approach that combines the previous two methods.
+A new similarity measure based on edge counting in a taxonomy is introduced in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}.
+Neighbourhood concepts are considered in their model in Formular \ref{equation1}, when $\lambda$ = 1 (default value as 0).
 
@@
 They chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint.
-Therefore, the quality of the semantic link is estimated as quality criteria $q_{m}$, either 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection) associated with their corresponding quality of vector $q_{cd}$ defined as Formula \ref{equation3}.
+Therefore, the quality of the semantic link is estimated as quality criteria $q_{m}$ associated with their corresponding quality of vector $q_{cd}$ defined as Formula \ref{equation3}.
 
@@
 Additionally, a semi-automated service composition approach is considered by the author, rather than a fully automated method.
-Therefore, we introduce a more applicable evaluation model in a full automated semantic web service composition.
+Therefore, we introduce a more applicable comprehensive quality model in a full automated semantic web service composition.
 
@@
 Genetic Programming (GP) \cite{da2015graphevol,da2016particle} is typical EC techniques to solve automated web service composition.
-GP-based approach utilises tree representations, on which service as represented as terminal nodes, and composite constructs as the functional nodes.
+GP-based approach utilises tree representations, on which service and constructs as represented as terminal nodes and functional nodes respectively.
 The crossover and mutation operations reproduce various individuals while ensuring correctness of structure.
 In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by a fitness function, which is also liable for correctness in functionality through penalising infeasible solutions.
-To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is looked for using PSO considering optimising QoS for building up service queue, then the web services in this service queue are selected to build up a graph representation of web service composition.
+To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is searched using PSO considering optimising QoS for building up service queue, then the web services in this service queue are selected to build up a graph representation of web service composition.
 However, the composite solution does not distinguish different match types and the degree of matching, which could lead to the data returned by the selected service that we think may be too general.
@@
 \end{figure}
-In this paper, we model automated QoS-ware semantic service composition with graphs.
+In this paper, we model comprehensive quality awareness automated semantic service composition with graphs.
 PSO has shown its efficiency in solving combinatorial optimisation problems.
@@
 \ref{overview} shows the overview of our approach with the five steps included.
-Step 1:The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements in terms of functional and non-functional requirement.
-The previous functional one is defined as $F(T_{Input}, T_{Output})$ , and the later nonfunctional one is the users' accepted level of QoS.
-Step 2: Those requirements are initially used to discover all relevant web services and their relationship in semantic matchmaking to get prepared for designing service composition via building graphs.
-This step selects relevant web services related to services request.
-This leads to a shrunken service repository that is used by PSO-based algorithm.
-Step 3: a service composition graph is randomly built up with considering the QoS and matchmaking quality.
-This graph building is interleaved with semantic matchmaking for services.
-The output of one service and its associated input of another service is calculated in the matchmaking phase where semantic matchmaking quality are measured which will be explained in Subsection \ref{qualityModel}.
-Step 4,5: The optimisation of service composition solution is performed over the PSO in Section \ref{pso_algorithm}, which is used to find optimised particle locations mapped back to web service for service-graph building.
-This approach \cite{da2016particle} is an indirect representation of web service composition that constructing a graph-based composite service composition.
+Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements in functional and non-functional parts.
+The first functional one is defined as $F(T_{Input}, T_{Output})$ , and the second nonfunctional one is the users' accepted level of QoS.
+Step 2: Those requirements are initially used to discover all relevant web services, which leads to a shrunken service repository that is used by PSO as a searching space.
+Step 3: a service composition graph is randomly built up interleaving with semantic matchmaking, where web services are discovered and connected with calculation of matchmaking quality, which will be explained in Subsect.
+\ref{qualityModel}.
+Step 4,5: The selection of web service is performed over the PSO in subSect.
+\ref{pso_algorithm}, which is used to find global best particle location mapped back to a service queue for a graph building.
+This approach \cite{da2016particle} is an indirect representation of web service composition using PSO.
 \subsection{Semantic matchmaking}

### 2016-10-23 paper.tex
update

@@
 However, it is not sufficient without considering good balancing between functional and nonfunctional quality in most scenarios.
-Therefore, the consideration in these two quality dimensions is a must, so that comprehensive quality  awareness semantic web service composition is proposed to deal with optimising composition solution.
-This paper develops a more applicable approach for comprehensive quality in semantic matchmaking and QoS optimisation for automated semantic web service composition.
+Therefore, the consideration in these two quality dimensions is a must, so that comprehensive quality  awareness semantic web service composition is proposed to deal with optimisation problems.
+This paper develops a more applicable approach for comprehensive quality in both semantic matchmaking and QoS optimisation for automated semantic web service composition.
 \end{abstract}
@@
 Service-oriented computing (SOC) is a novel computing paradigm that employs services as fundamental elements to achieve agile development of cost-efficient and integratable enterprise applications in heterogeneous environments \cite{papazoglou2003service}.
-Service Oriented Architecture (SOA) could abstractly realise service-oriented paradigm of computing, this accomplishment has been contributing to reuse of software components, from functions to units and from units to services during the development in SOA \cite{booth2004web}.
+Service Oriented Architecture (SOA) could abstractly realise service-oriented paradigm of computing, this accomplishment has been contributing to reuse of software components, from functions to units, and from units to services during the development in SOA \cite{booth2004web}.
 One of the most typical realisations of SOA is \textit{web service}, which designated as ``modular, self-describing, self-contained applications that are available on the Internet'' \cite{curbera2001web}.
@@
 
-\textit{Web service composition} pertains to a combination of several web services to provide a value --- added composite service that accommodates customers' arbitrarily complex requirements.
+\textit{Web service composition} pertains to a combination of several web services to provide a value-added composite service that accommodates customers' arbitrarily complex requirements.
 This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems - diverse platforms and programming languages \cite{casati2001technologies}.
 Due to an increase in a large-scale alignment of enterprise applications, the number of Web services has increased dramatically and unprecedentedly, which cause an immense redundancy in functionality in a huge searching space.
-Therefore, manual service and semi-automated web service composition are considered to be less efficient while automated web service composition is deemed to be less human intervention, less time consumption, and high productivity.
+Therefore, manual and semi-automated web service composition are considered to be less efficient while automated web service composition is deemed to be less human intervention, less time consumption, and high productivity.
 
@@
 \textit{Semantic web services composition} is distinguished from the syntactic service composition.
-Its benefits are presented in eliminating conflicts at the semantic level of web service composition.
+Its benefits are presented in eliminating conflicts by the semantic level of web service composition.
 In the last few years, substantial work has been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}.
-However, few works have addressed an automatic semantic web service composition approach, which optimise both QoS and quality of semantic match matching as web service composition solution.
+However, few works have addressed an automatic semantic web service composition approach, which optimise both QoS and quality of semantic match making as web service composition solutions.
 For example, customers prefer the highest quality of service solution associated with the acceptable semantic match matching quality.
@@
 \begin{enumerate}
- \item To address semantic matchmaking quality in considering different matching types associated with corresponding semantic similarity, which is demonstrated in a comprehensive quality integrated with QoS --- a more general and applicable evaluation model utilising semantic information of web services in this paper.
+ \item To address semantic matchmaking quality in considering different matching types associated with corresponding semantic similarity, which is demonstrated in a comprehensive quality approach with QoS.
+This approach is consider to be a more general and applicable way of finding an optimised solution in semantic web service composition.
 
- \item To apply PSO for sorting out an optimised service queue as a indirect representation of web service composition with consideration in comprehensive quality, and this service queue is decoded using graph building algorithm to generate optimised comprehensive quality awareness   composite solution.
+ \item To apply PSO for sorting out an optimised service queue as a indirect representation of web service composition with consideration of comprehensive quality, and this service queue is further decoded using graph building algorithm to generate optimised comprehensive quality awareness solution.
 
- \item To Compare the performance of comprehensive quality awareness service composition with the QoS-awareness utilising the benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
+ \item To Compare the performance of comprehensive quality awareness service composition with the QoS-awareness, we utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
 \end{enumerate}
@@
 \ref{background} provides the knowledge background on the semantic web service composition, including a literature review; Sect.
-\ref{qswsc_approach} represents the an Introduction of of semantic automated web service composition approach, and the comprehensive quality evaluation model; Sect.
+\ref{qswsc_approach} represents the an overview of comprehensive quality awareness semantic automated web service composition consisting of comprehensive quality evaluation model and the whole implementation algorithm; Sect.
 \ref{experiment_design} describes the experiments conducted to test the effectiveness of proposed model; Sect.
@@
 This overall composite goal is demonstrated in two parts.
-The first functional part is  a given task input or input set to get the desired Task output or output set, it typically refers to a statement of user's functional requirement; another nonfunctional part specifies the acceptable composite quality of service.
+The first functional part is  a given task input or input set to get the desired Task output or output set, it typically refers to users' functional requirement; another nonfunctional part specifies the acceptable composite quality of service.
 To accomplish the composte goal, two stages are involved: services discovery and service selection.
-Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from Service Repository: $S \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$, and updated $T_{Input}$ with found services output, which is used to further discovery more related services until the desired $T_{Output}$ found.
+Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from Service Repository: $S \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$, and updated a output set: $Output Set(T_{input}, S_{output} \in S_1,...,S_{output} \in S_{n-k})$ with found services output.
+The Output Set is used to further discovery all related services until the desired $T_{Output}$ found in the updated Output Set.
 It normally results in more than one solutions.
@@
 A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$ with both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Tax\}$.
-The web service matching process is to pair the two services' output and input concepts according to the Taxonomy(Tax) within an ontology (O).
-To measure the quality of semantic matchmaking, different matching levels that are typically considered in the literature \cite{paolucci2002semantic}: We defined two web services associated with parameters in a particular domain: $S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S2$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$ defined in.
+The web service matching process is to pair the output and input concepts of two services according to the Taxonomy(Tax) within an ontology (O).
+To measure the quality of semantic matchmaking, different matching levels that are typically considered in the literature \cite{paolucci2002semantic}: We defined two web services associated with parameters in a particular domain.
+$S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S2$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$ are defined in.
 
@@
 Note that, to find relevant services to automatically form suitable and applicable service compositions for a given goal, we consider Exact, Plugin and Fail match types in our paper.
-Therefore, these three robust and valid matches will be used to discover web service candidates for a service composition.
+Therefore, these three robust matches will be used to discover web service candidates for service composition.
 
 \subsection{Quality of Service and Composition Constructs}\label{Quality of Service and Composition Constructs}
-Currently, most of the optimisation problems \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} in web service composition are focusing on QoS optimisation, which covers aspects in non-functional requirements.
+Currently, most of the optimisation problems \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} in web service composition are focusing on QoS, which covers aspects in non-functional requirements.
 This problem have been explored in both single objective and multi-objectives optimisation.
@@
 Web services in a parallel construct are executed in the meantime.
-The QoS aggregation value in total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is delimited by the maximum time consumed path in the service composite solution.
+The QoS aggregation value in total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is delimited by the maximum time consumed path in the composite flow of the solution.
 This construct is presented in Figure \ref{parallel}.
@@
 Substantial work \cite{bansal2016generalized,mier2015integrated} on semantic web service composition focused mainly on functional requirements while neglecting non-functional requirements.
-Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output concepts of web services to ensure a semantic matchmaking.
-Since semantic descriptions are introduced into web service, the semantic matchmaking is to considered be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and pairing a mapping between two knowledge representations encoded utilising the ontology \cite{lecue2006formal}.
+Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output parameter concepts of web services to ensure a semantic matchmaking.
+It is to considered be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and pairing a mapping between two knowledge representations encoded utilising the ontology \cite{lecue2006formal}.
+
 In \cite{shet2012new}, the author surveyed three approaches to the similarity measures using taxonomies: one is based on nodes, in which similarity is determined by the information content of the nodes; one is entirely based on edge, where concept distance in a hierarchy structure is evaluated,  and the hybrid approach that combines the previous two methods.
@@
 
-In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, which utilise one possible measure for the degree of similarity using Common Description rate of a semantic link in Formula \ref{equation2}.
-And Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are also required to be pre-calculated in Formula \ref{equation2}.
-They chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint.
+In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, the auther utilise one possible measure for the degree of similarity using Common Description rate of a semantic link in Formula \ref{equation2}, where Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are required to be pre-calculated.
+They also chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint.
 Therefore, the quality of the semantic link is estimated as quality criteria $q_{m}$ associated with their corresponding quality of vector $q_{cd}$ defined as Formula \ref{equation3}.
@@
 
-However, the weakness of this approach for semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined DL in the knowledge representation system.
-for example, both service profiles definition described in OWL-S, and their related class, class axioms and properties defined in OWL2 are needed.
+However, the weakness of this approach for semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined ontology in the knowledge representation system.
+for example, we may need service profiles definition described in OWL-S, and their related class, class axioms and properties defined in OWL2.
 This makes it nearly impossible to measure semantic matchmaking quality in most semantic web services applications.
 Additionally, a semi-automated service composition approach is considered by the author, rather than a fully automated method.
-Therefore, we introduce a more applicable comprehensive quality model in a full automated semantic web service composition.
+Therefore, we introduce a more applicable comprehensive quality model in a fully automated approach.
 
@@
 Genetic Programming (GP) \cite{da2015graphevol,da2016particle} is typical EC techniques to solve automated web service composition.
-GP-based approach utilises tree representations, on which service and constructs as represented as terminal nodes and functional nodes respectively.
+This GP-based approach utilises tree representations, on which service and constructs as represented as terminal nodes and functional nodes respectively.
 The crossover and mutation operations reproduce various individuals while ensuring correctness of structure.
-In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by a fitness function, which is also liable for correctness in functionality through penalising infeasible solutions.
-To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is searched using PSO considering optimising QoS for building up service queue, then the web services in this service queue are selected to build up a graph representation of web service composition.
-However, the composite solution does not distinguish different match types and the degree of matching, which could lead to the data returned by the selected service that we think may be too general.
-In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the data requested by users.
+In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions.
+To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is searched using PSO considering optimising QoS for building up service queue, then web services in this service queue are selected to build up a graph representation of the solution.
+However, this solution does not distinguish different match types and the degree of matching, which could lead to the data returned by the selected service that we think may be too general.
+In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the outputs requested by users.
 In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS.
@@
 PSO has shown its efficiency in solving combinatorial optimisation problems.
-Therefore, we will propose a PSO based approach, which is considered to be simple and efficient without penalising and repairing comparing to GP \cite{da2014graph}.
+Therefore, we will propose a PSO-based approach, which is considered to be simple and efficient without penalising or repairing comparing to GP \cite{da2014graph}.
 Fig.
@@
 Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements in functional and non-functional parts.
-The first functional one is defined as $F(T_{Input}, T_{Output})$ , and the second nonfunctional one is the users' accepted level of QoS.
-Step 2: Those requirements are initially used to discover all relevant web services, which leads to a shrunken service repository that is used by PSO as a searching space.
-Step 3: a service composition graph is randomly built up interleaving with semantic matchmaking, where web services are discovered and connected with calculation of matchmaking quality, which will be explained in Subsect.
+The first functional one is defined as $F(T_{Input}, T_{Output})$ , and the second nonfunctional one is users' accepted level of QoS.
+Step 2: Those requirements are initially used to discover all relevant web services, which leads to a shrunken service repository that further used by PSO as a searching space.
+Step 3: a service composition graph is randomly built up interleaving with semantic matchmaking process, where web services are discovered and connected with calculation of matchmaking quality that will be explained in Subsect.
 \ref{qualityModel}.
 Step 4,5: The selection of web service is performed over the PSO in subSect.
-\ref{pso_algorithm}, which is used to find global best particle location mapped back to a service queue for a graph building.
+\ref{pso_algorithm}, which is used to find global best particle location mapped back to a service queue for building a graph.
 This approach \cite{da2016particle} is an indirect representation of web service composition using PSO.
@@
 In this paper, we use MECE ontologies \cite{bleul2008self} XWL format, which could be considered to be an alternative form of ontology for services.
-In OWL, semantics specifies the both concepts and individuals in the forms of classes and instances but limited to taxonomies.
-The semantic concepts are expressed with the their statements and relationship in RDFs (such as subClassOf ), and the semantic individuals are related to the input and output parameters of web services.
+In OWL, semantics specifies the both concepts and individuals in the forms of classes and instances wherer semantic concepts are expressed with the their statements and relationship in RDFs (such as subClassOf ), and the semantic individuals are related to the input and output parameters of web services.
 The MECE is an extensive annotation to WSDL files, which defines the each parameter of services associated with their semantic individuals.
@@
 The matching mechanism attempts to determine whether correct match criteria between the source concepts of C1 and the target concepts of C2, and the quality of semantic matchmaking for these two concepts is calculated in the quality model in subSection \ref{qualityModel}.
-The advantage of utilising semantic matchmaking quality is to find a more closely requested service output with acceptable level of QoS.
+The advantage of semantic matchmaking quality is to find a more closely requested service output with acceptable level of QoS.
 
 \subsection{Comprehensive quality model and aggregation matrix}\label{qualityModel}
-In this paper, we propose a semantic matchmaking model to evaluate the semantic quality of two matched web services, this fill the gaps in subsection \ref{relatedWork} of current prevailing QoS-aware optimisation, where quality of matchmaking for service selection are not considered.
+In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition, this overcome the disadvantages of current prevailing QoS-aware optimisation, in which quality of matchmaking for service selection are not considered.
 
 \textbf{Semantic matchmaking model}.
-Due to the discretisational characteristics of different match types, which is driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}.
+Due to the discretisational characteristics of different match types driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}.
 Match type is considered to be one factor for the semantic quality.
-Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, a taxonomy based measurement for ontology matching, In this paper, it could be used to estimate the parameter concepts similarity between the output and input of a request for selecting web services with close semantic matching.
-Therefore, given the quality match type and the similarity of two parameters, the semantic matchmaking quality is defined as Formula \ref{equation4}, where $q(s_ {matchType})$ is set up as the same as the quality of the semantic link in literature \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection) while $q(s_ {similarity})$ is calculated utilising formula \ref{equation1} in subsection \ref{relatedWork}.
+Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, a taxonomy based measurement for ontology matching, In this paper, it could be used to estimate the parameter concepts similarity between the given output and available input for selecting web services with close semantic matching.
+Therefore, given the quality match type and the similarity of two parameters, the semantic matchmaking quality is defined as Formula \ref{equation4}, where the value of $q(s_ {matchType})$ is set up as the same as the quality of the semantic link in literature \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection) while $q(s_ {similarity})$ is calculated utilising formula \ref{equation1} in subsection \ref{relatedWork}.
 
@@
 \label{equation4}
-q_{smq} \stackrel{.}{=} (q(s_ {matchType}), \  q(s_ {similarity}))
+q_{sm} \stackrel{.}{=} (q(s_ {matchType}), \  q(s_ {similarity}))
 \end{equation}
@@
 \textbf{Comprehensive quality model}.
-Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional requirements of composite web services.
+Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional requirements of composite goal.
 The non-functional properties typically refer previously discussed QoS, which are given by service providers.
@@
 \label{equation5}
-q_{cq} \stackrel{.}{=} (q(s_ {smq}), \  q(s_ {QoS}))
+q_{cq} \stackrel{.}{=} (q(s_ {sm}), \  q(s_ {QoS}))
 \end{equation}
@@
 \textbf{Quality aggregate matrix}.The quality aggregation is defined based on the constructs of composite web services on the criteria of functional and non-functional properties.
-Typically, web services could have more than one concept-related parameters.
-Regarding semantic matchmaking part, edge-level quality aggregation is determined by the mean of concept-related parameter quality in both semantic match type and similarity respectively, and construct-level quality is further calculated based on the edge-level quality aggregation following the rules in Table \ref{table1}, which is the quality aggregate matrix for semantic web service composition.
-Semantic matchmaking aggregation considers two different factor aggregations: the matching type quality aggregation is calculated by the product function of involved edge-level matching type value, and the similarity quality average value of all edge-level similarity quality.
-The nonfunctional (QoS) aggregation calculation is same to \cite{cardoso2004quality}.
+Generally, web services could have more than one concept-related parameters.
+In semantic matchmaking process, two levels of quality aggregation are considered --- edge level and construct level.
+At edge level, the edge-level quality aggregation is determined by the mean of concept-related parameter quality in both $q(s_{mt})$ and $q(s_{s})$ respectively.
+Meanwhile, the construct-level quality is further calculated based on the constructs following the rules in Table \ref{table1}, which is a quality aggregate matrix for semantic web service composition.
+Both the $Q(s_{mt})$ and $Q(s_{s})$ are considered by calculating the product function of involved edge-level $q(s_{mt})$, and $q(s_{s})$ respectively.
+The QoS aggregation $Q(q_{QoS})$ calculation is same to \cite{cardoso2004quality}.
 
@@
 A weighted sum of those components is utilised in the fitness function \ref{equation7}, in which fitness value of 1 means the best overall quality and 0 means the worst.
-As the sum of all the function weights (w1 to w6) is equal to 1, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised ranging from 0 to 1 so that the overall result falls within 0 to 1.
+As the sum of all the function weights (w1 to w6) is equal to 1, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the fitness value result falls within 0 to 1.
 Also, the lowest T and C value represent the best quality so that the objective function is offset using $(1 - T)$ and $(1 - C)$.
@@
 			\textbf{2.} Sort particle's position vector as a service queue in ascending order\\
-			\textbf{3.} Initialise OutputSet with Task Input: I\\
+			\textbf{3.} Initialise OutputSet with Task Input $\leftarrow I$ \\
 			\textbf{4.} Initialise a graph G with a startNode\\
-			\nonl \While {max. OutputSet not contains Task Output: O}{
+			\nonl \While {max. OutputSet not contains Task Output $\leftarrow O$}{
 				\textbf{5.} Get web service from service queue\\
@@
 	}
+		\textbf{20.} return Graph in the last iteration $ \rightarrow G$.\\
 
@@
 The overall algorithm investigated here is a combination of a simple forward decoding PSO \cite{da2016particle} with our comprehensive quality evaluation model.
-The idea is to translate the particle location into a service queue as an indirect representation of service composition graph, finding the best fitness of the composite service solution is to discover the optimised location of the particle.
+The idea is to translate the particle location into a service queue as an indirect representation of service composition graph, so finding the best fitness of the composite service solution is to discover the optimised location of the particle.
 In PSO, the dimension of the particle is set up as the same as the number of relevant web services in the shrunken service repository, each of which is mapped to a location in a particle, put services in a queue and sort in ascending order.
 Later on, we decode a corresponding graph built from that service queue using a forward graph-building technique from a start node to the end node.
-We select and connect web services to the startNode if this web service can satisfy the given Task input, and an Output Set is initialised and kept updating with outputs from new added web services in the graph, later on, we services are keeping being selected and added if services' inputs could be satisfied by any output in the Output Set, if the Output Set contains the Task's required outputs, we end up graph building.
+We select and connect web services to the startNode if this web service can satisfy the given Task input, and an Output Set is initialised and kept being updated using outputs from new-added web services in the graph, later on, we services are keeping being selected and added if services' inputs could be satisfied by any output in the Output Set, if the Output Set contains the Task's required outputs, we end up graph building.
 In addition, dangle service nodes and edges should be removed.
-At last, fitness value can be calculated by the construct-based aggregation.
+The particle's fitness value can be calculated by the graph-based composition solution.
+In the evolutionary process, pBest and gBest value are assigned and updated in each generation while swarm's position is updated.
+Finally, we return the graph G built in the last iteration as the optimised solution.
 

### 2016-10-24 paper.tex
update

@@
 This interaction enables us to pair service functionalities through language understanding and reasoning.
-An optimisation problem is another challenge, many scholars have looked into the nonfunctional optimisation problems in QoS-awareness web service composition applying AI planning and Evolution Computing techniques.
-However, it is not sufficient without considering good balancing between functional and nonfunctional quality in most scenarios.
+Optimisation problems are another challenge, many scholars have looked into the nonfunctional optimisation problems in QoS-awareness web service composition applying AI planning and Evolution Computing techniques.
+However, it is not sufficient without considering good balance between functional and nonfunctional quality in most scenarios.
 Therefore, the consideration in these two quality dimensions is a must, so that comprehensive quality  awareness semantic web service composition is proposed to deal with optimisation problems.
-This paper develops a more applicable approach for comprehensive quality in both semantic matchmaking and QoS optimisation for automated semantic web service composition.
+This paper develops a more applicable approach for measuring comprehensive quality in both semantic matchmaking and QoS optimisation for automated semantic web service composition.
 \end{abstract}
@@
 \textit{Web service composition} pertains to a combination of several web services to provide a value-added composite service that accommodates customers' arbitrarily complex requirements.
-This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems - diverse platforms and programming languages \cite{casati2001technologies}.
+This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems --- diverse platforms and programming languages \cite{casati2001technologies}.
 Due to an increase in a large-scale alignment of enterprise applications, the number of Web services has increased dramatically and unprecedentedly, which cause an immense redundancy in functionality in a huge searching space.
@@
 The syntactic dimension has achieved success through the use of XML standards (such as $WSDL$, $SOAP$), the semantics dimension, on the other hand, demands further research.
-Those semantics given by ontologies \cite{o2005review} enables web service to understand and reason with each other.
+This semantics given by ontologies \cite{o2005review} enables web service to understand and reason with each other.
 Historically, there are many ontologies languages and formats for semantic service descriptions, such as OWL-S \cite{martin2004owl}, WSML \cite{fensel2006enabling}, and SAWSDL \cite{lausen2007semantic}, The logical characteristics in reasoning makes ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments.
@@
 \textit{Semantic web services composition} is distinguished from the syntactic service composition.
-Its benefits are presented in eliminating conflicts by the semantic level of web service composition.
+Its benefits are presented in eliminating conflicts by the semantic level of web services.
 In the last few years, substantial work has been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}.
@@
 The overall goal of this paper is to develop an comprehensive quality awareness automated semantic web service composition that satisfactorily optimises both functional and non-functional requirements.
-Particularly, this project considers a semantic matchmaking quality extension to QoS awareness and a few structural constructs (sequence and parallel) for building optimised composition solution using Particle Swarm Optimisation.
+Particularly, this project considers a semantic matchmaking quality extension to QoS awareness and two structural constructs (sequence and parallel) for building optimised composition solution using Particle Swarm Optimisation.
 We aim to provide a more general and applicable way to measure semantic matchmaking in automated semantic web service composition and contribute to the state-of-the-art in this field.
@@
 
- \item To apply PSO for sorting out an optimised service queue as a indirect representation of web service composition with consideration of comprehensive quality, and this service queue is further decoded using graph building algorithm to generate optimised comprehensive quality awareness solution.
+ \item To apply PSO for implementing comprehensive awareness automated semantic web service composition.
+PSO sorts out an optimised service queue as a indirect representation of web service composition with consideration of comprehensive quality, and this service queue is further decoded using graph building algorithm to generate a final solution.
 
- \item To Compare the performance of comprehensive quality awareness service composition with the QoS-awareness, we utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
+ \item To explore the performance of comprehensive quality awareness semantic web service composition, we utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
 \end{enumerate}
@@
 \ref{experiment_design} describes the experiments conducted to test the effectiveness of proposed model; Sect.
-\ref{results_analysis} presents the results and analysis of these experiments; Sect.
+\ref{results_analysis} presents the results and analysis of the experiment; Sect.
 \ref{conclusion} is the paper conclusion.
@@
 
-The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$.
+The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as a composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$.
 This overall composite goal is demonstrated in two parts.
-The first functional part is  a given task input or input set to get the desired Task output or output set, it typically refers to users' functional requirement; another nonfunctional part specifies the acceptable composite quality of service.
-To accomplish the composte goal, two stages are involved: services discovery and service selection.
-Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from Service Repository: $S \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$, and updated a output set: $Output Set(T_{input}, S_{output} \in S_1,...,S_{output} \in S_{n-k})$ with found services output.
-The Output Set is used to further discovery all related services until the desired $T_{Output}$ found in the updated Output Set.
-It normally results in more than one solutions.
-Service selection is to select one of those composite solution considering closest QoS to $T_{QoS}$.
+The first functional part is a given task input or input set to get the desired Task output or output set, it typically refers to users' functional requirement; another nonfunctional part specifies the acceptable level of composite quality of service.
+To accomplish the composite goal, two stages are involved: services discovery and service selection.
+Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from Service Repository: $S \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$.
+Meanwhile, a output set is initialised and updated with found services output, which could be denoted as  $Output Set(T_{input}, S_{output} \in S_1,...,S_{output} \in S_{n-k})$.
+The Output Set is used to discovery all related services until the desired $T_{Output}$ found in the updated Output Set.
+The discovery process normally results in more than one solutions.
+Service selection is to select one of those composite solution considering the closest QoS to $T_{QoS}$.
 To ensure the composite solution returns exact the same or very close $T_{Output}$, we consider a comprehensive quality in both discovery and selection stages, where two challenges mentioned in Sect.
@@
 \subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
-The semantic service matchmaking aims to discover appropriate services from service repository relevant to a customer's functional request defined by the Goal.
+The semantic service matchmaking aims to discover appropriate services from service repository relevant to a customer's functional requests.
 A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$ with both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Tax\}$.
@@
 This GP-based approach utilises tree representations, on which service and constructs as represented as terminal nodes and functional nodes respectively.
-The crossover and mutation operations reproduce various individuals while ensuring correctness of structure.
+The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure.
 In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions.
 To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is searched using PSO considering optimising QoS for building up service queue, then web services in this service queue are selected to build up a graph representation of the solution.
-However, this solution does not distinguish different match types and the degree of matching, which could lead to the data returned by the selected service that we think may be too general.
+However, this solution does not distinguish different matching types and parameter similarity, which could lead to the outputs returned by the selected service that we think may be too general.
 In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the outputs requested by users.
 In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS.
-Therefore, we fill the gap by considering different matching types and their similarity when evaluate an overall quality of composite service.
+Therefore, we fill the gap by considering different matching types and the similarity when evaluate an overall quality of web service composition.
 
@@
 Step 2: Those requirements are initially used to discover all relevant web services, which leads to a shrunken service repository that further used by PSO as a searching space.
-Step 3: a service composition graph is randomly built up interleaving with semantic matchmaking process, where web services are discovered and connected with calculation of matchmaking quality that will be explained in Subsect.
+Step 3: a graph representation is randomly built up interleaving with semantic matchmaking process, where web services are discovered and connected while calculating matchmaking quality that will be explained in Subsect.
 \ref{qualityModel}.
-Step 4,5: The selection of web service is performed over the PSO in subSect.
-\ref{pso_algorithm}, which is used to find global best particle location mapped back to a service queue for building a graph.
+Step 4,5: The selection of web services is performed over the PSO algorithm in subSect.
+\ref{pso_algorithm}, which is used to find best particle location mapped back to a service queue for building graph solutions considering comprehensive quality.
 This approach \cite{da2016particle} is an indirect representation of web service composition using PSO.
 \subsection{Semantic matchmaking}
+
+The semantic matchmaking transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match: $match(C_{2}, C_{3})$ defined in Section \ref{semantic Web service Discovery}.
+The matching mechanism attempts to determine whether correct match criteria between the source concepts of C1 and the target concepts of C2, and the quality of semantic matchmaking for these two concepts is calculated in the quality model in subSection \ref{qualityModel}.
+The advantage of semantic matchmaking quality is to find a more closely requested service output with acceptable level of QoS.
+
 The semantic matchmaking is achieved by utilising semantic annotation with OWL and OWL-S.
-In this paper, we use MECE ontologies \cite{bleul2008self} XWL format, which could be considered to be an alternative form of ontology for services.
-In OWL, semantics specifies the both concepts and individuals in the forms of classes and instances wherer semantic concepts are expressed with the their statements and relationship in RDFs (such as subClassOf ), and the semantic individuals are related to the input and output parameters of web services.
+In this paper, we use MECE ontologies \cite{bleul2008self}, which could be considered to be an alternative form of ontology for services.
+In ontology, semantics specifies the both concepts and individuals in the terms of classes and instances wherer semantic concepts are expressed with the their statements and relationship in RDFs (such as subClassOf ), and the semantic individuals are related to the input and output parameters of web services.
 The MECE is an extensive annotation to WSDL files, which defines the each parameter of services associated with their semantic individuals.
@@
 
-The semantic matchmaking transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match: $match(C_{2}, C_{3})$ defined in Section \ref{semantic Web service Discovery}.
-The matching mechanism attempts to determine whether correct match criteria between the source concepts of C1 and the target concepts of C2, and the quality of semantic matchmaking for these two concepts is calculated in the quality model in subSection \ref{qualityModel}.
-The advantage of semantic matchmaking quality is to find a more closely requested service output with acceptable level of QoS.
-
 \subsection{Comprehensive quality model and aggregation matrix}\label{qualityModel}
-In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition, this overcome the disadvantages of current prevailing QoS-aware optimisation, in which quality of matchmaking for service selection are not considered.
+In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition.
+This model overcome the disadvantages of current prevailing QoS-aware optimisation, in which quality of semantic matchmaking are not considered.
 
@@
 Due to the discretisational characteristics of different match types driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}.
-Match type is considered to be one factor for the semantic quality.
-Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, a taxonomy based measurement for ontology matching, In this paper, it could be used to estimate the parameter concepts similarity between the given output and available input for selecting web services with close semantic matching.
+Match type is considered to be one factor for the semantic matchmaking quality.
+Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new} --- a taxonomy-based measurement for ontology matching.
+In this paper, it could be used to estimate the parameter concepts similarity between the given output and available input for selecting web services.
 Therefore, given the quality match type and the similarity of two parameters, the semantic matchmaking quality is defined as Formula \ref{equation4}, where the value of $q(s_ {matchType})$ is set up as the same as the quality of the semantic link in literature \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection) while $q(s_ {similarity})$ is calculated utilising formula \ref{equation1} in subsection \ref{relatedWork}.
@@
 Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional requirements of composite goal.
-The non-functional properties typically refer previously discussed QoS, which are given by service providers.
-Consequently, the comprehensive quality model integrated the semantic matchmaking quality $q(s_{smq})$ in Formula \ref{equation5}, which could be further broken down into Formula \ref{equation6}.
+The non-functional properties typically refers to previously discussed QoS, which are given by service providers.
+Consequently, the comprehensive quality model integrated the semantic matchmaking quality $q(s_{sm})$ in Formula \ref{equation5}, which could be further broken down into Formula \ref{equation6}.
 
@@
 In semantic matchmaking process, two levels of quality aggregation are considered --- edge level and construct level.
-At edge level, the edge-level quality aggregation is determined by the mean of concept-related parameter quality in both $q(s_{mt})$ and $q(s_{s})$ respectively.
-Meanwhile, the construct-level quality is further calculated based on the constructs following the rules in Table \ref{table1}, which is a quality aggregate matrix for semantic web service composition.
-Both the $Q(s_{mt})$ and $Q(s_{s})$ are considered by calculating the product function of involved edge-level $q(s_{mt})$, and $q(s_{s})$ respectively.
+At edge level, the edge-level quality aggregation is determined by the mean value of concept-related parameter quality in $q(s_{mt})$ and $q(s_{s})$ respectively.
+Meanwhile, the construct-level quality is further calculated based on the constructs following the rules in Table \ref{table1} --- a quality aggregate matrix for semantic web service composition.
+Both the $Q(s_{mt})$ and $Q(s_{s})$ are considered by calculating the product function of involved edge-level $q(s_{mt})$, and mean function of edge-level $q(s_{s})$ respectively.
 The QoS aggregation $Q(q_{QoS})$ calculation is same to \cite{cardoso2004quality}.
@@
 \subsection{Fitness Calculation}
-The fitness value is calculated from the aggregate value of quality components involved in a graph-based service composition.
-A weighted sum of those components is utilised in the fitness function \ref{equation7}, in which fitness value of 1 means the best overall quality and 0 means the worst.
-As the sum of all the function weights (w1 to w6) is equal to 1, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the fitness value result falls within 0 to 1.
-Also, the lowest T and C value represent the best quality so that the objective function is offset using $(1 - T)$ and $(1 - C)$.
+The fitness value is calculated from the aggregated value of quality components involved in a graph-based service composition.
+A weighted sum of those components is utilised in the fitness function \ref{equation7}, in which fitness value of 1 means the best comprehensive quality and 0 means the worst.
+As the sum of all the function weights (w1 to w6) is equal to 1, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the fitness value falls within 0 to 1.
+Also, the lowest T and C value represent the best conponent quality so that the objective function is offset using $(1 - T)$ and $(1 - C)$.
 
@@
 \end{algorithm}
-The overall algorithm investigated here is a combination of a simple forward decoding PSO \cite{da2016particle} with our comprehensive quality evaluation model.
-The idea is to translate the particle location into a service queue as an indirect representation of service composition graph, so finding the best fitness of the composite service solution is to discover the optimised location of the particle.
-In PSO, the dimension of the particle is set up as the same as the number of relevant web services in the shrunken service repository, each of which is mapped to a location in a particle, put services in a queue and sort in ascending order.
-Later on, we decode a corresponding graph built from that service queue using a forward graph-building technique from a start node to the end node.
-We select and connect web services to the startNode if this web service can satisfy the given Task input, and an Output Set is initialised and kept being updated using outputs from new-added web services in the graph, later on, we services are keeping being selected and added if services' inputs could be satisfied by any output in the Output Set, if the Output Set contains the Task's required outputs, we end up graph building.
+The overall algorithm investigated here is a simple forward decoding PSO \cite{da2016particle} with our comprehensive quality evaluation model.
+The idea is to translate the particle location into a service queue as an indirect representation of graph-based service composition, so finding the best fitness of the composite service solution is to discover the optimised location of the particle.
+In PSO, the dimension of the particle is set up as the same as the number of relevant web services in the shrunken service repository, and all the services index is mapped to the location in a particle, and we put services in a queue in ascending order, from which we decode a corresponding graph using a forward graph-building technique.
+The particle's fitness value can be calculated based on that built graph.
+During the evolutionary process, pBest and gBest value are assigned and updated in each generation with new-updated particles' position while graph-based solutions are generated at the same time.
+eventually, we return the graph built from the last generation as an optimised solution.
+In the forward graph building algorithm.
+We select and connect web services to the startNode from the service queue if the web service can satisfy the given $T_{input}$.
+Meanwhile, an Output Set is initialised and kept being updated using outputs from the new-added web services in the graph, later on, more services are connected if services' inputs could be satisfied by any output in the Output Set.
+At last, The end node is connected if the updated Output Set contains the $T_{output}$.
 In addition, dangle service nodes and edges should be removed.
-The particle's fitness value can be calculated by the graph-based composition solution.
-In the evolutionary process, pBest and gBest value are assigned and updated in each generation while swarm's position is updated.
-Finally, we return the graph G built in the last iteration as the optimised solution.
 
@@
 In this section, a quantitative evaluation approach is adopted in our experiment design.
-The objectives of the evaluation are to measure the effectiveness of the proposed comprehensive quality model in automated semantic web service composition approach, and to explore the impact of the semantic matchmaking that contributes to overall composition quality, and to compare solutions generated by QoS-ware approach with our method.
+The objectives of the evaluation are to measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach, and to explore the impacts of the semantic matchmaking that contributes to overall composition quality, and to compare solutions generated by QoS-ware approach with our method.
 
-We utilise benchmark dataset web service challenge 2009 (WSC09) \cite{kona2009wsc} web service data sets to perform a standard evaluation.
-WSC09 designed OWL for providing richer semantics consisting tasks with variable size.
-With an incremental number in concept, individuals and web services in each dataset, it is a proper dataset for the scalability measures in our defined quality evaluation model.
+We utilise benchmark dataset web service challenge 2009 (WSC09) \cite{kona2009wsc} to perform a standard evaluation.
+WSC09 provides problems,  WSDL+MECE, taxonomy files in formats of xml, xml, and owl respectively, where five tasks consisted in with variable size in both services, and ontologies.
+Therefore, it is a proper dataset for the scalability measures in our defined quality evaluation model.
 Table \ref{wsc09datasetTable} presents the features of the WSC’09 dataset.
-The number of concepts, individuals in the ontology and services of each data set is shown in the second, third, fourth column respectively.
+The number of concepts, individuals in the ontology and services in each data set is shown in the second, third, fourth column respectively.
 Also, we extend all the datasets with QoS attributes from service providers to perform a comprehensive quality evaluation.
@@
 In addition, weights setting are flexibly defined by users' preferences.
-As part of their requirement, we configure weights of fitness function as the same to properly balance functional side and nonfunctional side.
+As part of their requirement, we configure weights of fitness function to properly balance functional side and nonfunctional side.
 Therefore, $w_{1}$ and $w_{2}$ are equals to 0.1 and 0.4,  and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly.
@@
 \subsection{Convergence Test}\label{convergenceTest}
-To analysis the effectiveness of our approach, we explore the convergency rate of the proposed method in this section.
-We show the convergency of five tasks in WSC09.
-To further study an overall effectiveness of evaluation model and investigate the impacts of all involved components in the fitness function.
-We analysis all the performance of these components in the whole evolutionary process in Figure \ref{exp_fitnessvalue}, in which the five tasks' experiment results are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average quality of service for generation 0-99 with optimum.
+
 \begin{figure}[h]
@@
 
-Firstly, the average fitness value over 100 generations is calculated by the average best fitness so far found per generation over 30 independent runs.
-The value plotted in the first column group of figure \ref{exp_fitnessvalue} ranges from 0 to 1, and it is considered to be more optimised if its value is closer to value 1.
+To analysis the effectiveness of our approach, we explore the convergency rate of the proposed method in this section to investigate the convergency of five tasks in WSC09.
+To further study an overall effectiveness of evaluation model and impacts of all involved components in the fitness function.
+We analysis all the performances of these components in the whole evolutionary process in Figure \ref{exp_fitnessvalue}, in which the five tasks' experiment results are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average QoS for generation 0-99 with optimum.
+
+Firstly, the average fitness value with optimum is calculated by the average value of best fitness found in each generation over 30 independent runs.
+The value plotted in the first column group ranges from 0 to 1 in figure \ref{exp_fitnessvalue}, and it is considered to be more optimised if its value is closer to value 1.
 We can see that there is a significant increase in the fitness value (avg) with optimum between generation 0 and generation 15-25, the remained generation continues to produce a steady but moderate improvement in the fitness value and eventually reach a plateau with no further changes.
 The same behaviour is observed over the rest tasks.
-Also, there is a fast convergence of the fitness value can be observed.
-That is simply because of many repetitive solutions as the indirect web service composition representation in a large search space.
+Also, there is a fast convergence of the fitness value that be observed.
+That is simply because of many repetitive solutions in the indirect web service composition representations in the search space.
 
-We also investigate the variation in functional quality part including two sub factors --- average matchType quality and average similarity quality from generation 0 to 99 in second and third column groups in Figure \ref{exp_fitnessvalue}.
-In these groups,  both the average matchType quality and average similarity quality are the average value corresponding to the average best fitness so far found plotted in the first column group,  and further calculated their mean over 30 independent runs respectively.
-The dominant tendency of the marked value representing a similar characteristic compared to the average fitness value group trend.
-However, there are some slight fluctuations over the generations, and it could be reasonably treated as a typical situation that theoretically single objective function prevents selecting the lowest semantic matchmaking quality without granting for the excellent.
+We also investigate the variation of two factors consisted in the functional quality part --- average matchType quality with optimum and average similarity quality with optimum from generation 0 to 99 in second and third column groups of Figure \ref{exp_fitnessvalue}.
+In these groups,  both the average matchType quality with optimum and average similarity quality with optimum are the mean value corresponding to the best fitness value found in each generation over 30 independent runs.
+The dominant tendency of the marked value representing a similar characteristic compared to the average fitness value group trend in five tasks.
+However, there are some slight fluctuations over the generations, it due to the single objective fitness function that prevents selecting the worst component quality without granting for the best.
 
-Lastly, It is interesting to look at the average QoS per generation for the 30 independent runs if the behaviour of functional part performance is towards a higher value, where QoS is the value corresponding to the best fitness so far found in each generation.
-We construct the results in the fourth column group in Figure \ref{exp_fitnessvalue}.
+Lastly, It is interesting to look at the average QoS per generation for the 30 independent runs when the behaviour of functional quality moves upward.
+Here average QoS with optimum is also the value corresponding to the fitness value with optimum in each generation, and we display the results in the fourth column group in Figure \ref{exp_fitnessvalue}.
 It is obvious that the overall trend of QoS moves upward to a high constant level in five independent tasks.
-Additionally, QoS (avg) with optimum have evolved towards an overall excellent state, because we don't see too much trade-off from QoS regarding the improvement in functional quality part.
+Additionally, we don't see too much trade-off from the QoS.
 
@@
 \end{figure}
-We defined our optimised web service composition as $WSC = (V, E)Graph$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of service connections as edges associated matchType quality and semantic similarity quality: $E = {e_{1}, e_{2},...
+We defined our optimised web service composition as $WSC = (V, E)Graph$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of service connections as edges associated with two values of matchType quality and semantic similarity quality: $E = {e_{1}, e_{2},...
 e_{n}}$ where $e1$ is define as $(S_{1},S_{2})={q_{mt}, q_{s}}$.
@@
 The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections.
-Besides that, $q_{mt}$ and $q_{s}$) are calculated for all edges ${e_{1}, e_{2},...
-e_{n}}$, and further aggregated in $Q_{mt}$ and $Q_{s}$ respectively.In addtion, $Q_{QoS}$ is calculated by all the non-functional attributes of $V$ using aggregation rules defined before.This standard solution model helps us to make better comparison for evaluating the results from different approaches.
+Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},...
+e_{n}}$, and further aggregated in $Q_{mt}$ and $Q_{s}$ respectively.
+In addition, $Q_{QoS}$ is calculated by all the non-functional attributes of $V$ using aggregation rules defined before.
+The demonstration of the solution is to make better comparison of results using the same solution model from different approaches .
 
-After a well-defined solution is discussed, we will look at $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ defined in the solution model using black-box testing for solution comparison, where these components in both comprehensive quality evaluation approach and traditional QoS-ware one \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} are compared to reveal how good our evaluation mode is.
-In a decision table \ref{decisionTable}, optimised solution using these two evaluation models are compared under five independent tasks in WSC09 dataset.
-In each task solution, we compare $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$, where $Q_{QoS}$ is normalised to make them comparable from 0 to 1 in our method.
+Now we look at $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ defined in the solution model using black-box testing for the comparison, where the comprehensive quality awareness approach and QoS awareness approach \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} are compared to reveal how good our evaluation mode is in a decision table shown in Table \ref{decisionTable}.
+Solutions to five tasks are compared using two evaluation models in WSC09.
+In each task, we compare $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$, and $Q_{QoS}$ is normalised to make it comparable to another method in our comprehensive awareness approach
 
@@
 \end{table}
-From the table \ref{decisionTable}, Task 1 represents the same solution that can be observed in values of  $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$ using the smallest dataset size with the lowest size of ontologies.
-However, we can recognise trade-offs in task2 and task3 using our evaluation model, where a 0.021668 increase and a 0.00098 decrease in similarity quality and matchType quality with weights 0.4 and 0.1 respectively so that solution to task 2 is still considered to be an improvement in functional quality part with a trade-off value 0.007249 in QoS.
-In task3, the benefit of functional part quality is clearer with an increase in both similarity quality and matchType quality of 0.056648 and 0.078862 while a slight decrease in QoS.
-later on, the performance is the same in task 4 and task 5.
+In Table \ref{decisionTable}, Task 1 represents the same solution using different methods where the values of $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$ are all the same.
+It is due to the size of dataset 01 is very small in both available services and ontologies.
+However, As the size of dataset increase, we can recognise a trade-offs in task 2 using our evaluation approach, where a 0.021668 increase in similarity quality and a 0.00098 decrease in matchType quality with weights 0.4 and 0.1 respectively so that solution to task 2 is still considered to be an improvement in the functional quality part while a decrease value of 0.007249 in QoS.
+In task 3, the benefit of functional part quality is clearer with an increase value of 0.056648 and 0.078862 in  similarity quality and matchType quality respectively while a slight decrease in QoS.
+later on, the rest tasks perform the same behaviour in $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$ as task 3.
 In conclusion, we can perceive that our evaluation could find out better functional quality with a reasonable trade off in QoS.
@@
 \section{Conclusion}\label{conclusion}
-This work introduced a more applicable and simpler evaluation model for semantic automated web service composition that relies on semantic matchmaking quality extension to QoS-aware consideration.
-The key idea of these evaluation model is to consider the quality of semantic matchmaking corresponding to different matchmaking types, which is simply achieved by applying the similarity measures in parameter-related concepts, and those web services are involved in further selection for dealing optimised problems.
-Also, the effectiveness of our model is also proved to be able to obtain a better-optimised solution in better functional quality with a reasonable trade-off in QoS.
-Future works in this area should investigate in multi-objective optimisation as well as consider improving efficiency in the functional quality calculation.
+This work introduced a more applicable and simpler evaluation model for comprehensive quality awareness semantic automated web service composition that relies on semantic matchmaking quality extension to QoS-aware consideration.
+The key idea of these evaluation model is to consider the quality of semantic matchmaking corresponding to different matchmaking types.
+Also, the effectiveness of our model is also proved to obtain better functional quality with a reasonable trade-off in QoS.
+Future works in this area should investigate more reasonable matching types, explore the comprehensive quality in multi-objective approach, and improve efficiency in the functional quality calculation.
 \bibliographystyle{splncs03}

### 2016-10-30 paper.tex
update

@@
 
-\title{Comprehensive Quality Awareness Automated Semantic Web Service Composition}
+\title{Comprehensive quality - aware Automated Semantic Web Service Composition}
 
@@
 Semantic web service composition has been a prevailing research area in recent years.
-There are two major governance challenges faced by researchers, one is semantic matchmaking for discovering interoperable web services, which demands a rich “machine understanding” language such as OWL-S (Web Ontology language for Web Services), WSML (Web Service Modeling language, SAWSDL (Semantic Annotations for WSDL and XML Schema).
-This interaction enables us to pair service functionalities through language understanding and reasoning.
-Optimisation problems are another challenge, many scholars have looked into the nonfunctional optimisation problems in QoS-awareness web service composition applying AI planning and Evolution Computing techniques.
+There are two major governance challenges faced by researchers.
+One is semantic matchmaking for discovering interoperable web services, which demands a rich “machine understanding” language such as OWL-S (Web Ontology language for Web Services), WSML (Web Service Modeling language, SAWSDL (Semantic Annotations for WSDL and XML Schema).
+This interaction of web services enables us to pair service functionalities through understanding and reasoning those semantic descriptions.
+Optimisation problems are another challenge.
+Many scholars have looked into nonfunctional optimisation problems in QoS-aware web service composition applying AI planning and Evolution Computing techniques.
 However, it is not sufficient without considering good balance between functional and nonfunctional quality in most scenarios.
-Therefore, the consideration in these two quality dimensions is a must, so that comprehensive quality  awareness semantic web service composition is proposed to deal with optimisation problems.
-This paper develops a more applicable approach for measuring comprehensive quality in both semantic matchmaking and QoS optimisation for automated semantic web service composition.
+Therefore, the consideration in these two quality dimensions is a must, so that service composition needs to deal with optimisation problems in both quality of semantic matchmaking and QoS.
+This paper develops a more applicable way for measuring a proposed comprehensive quality model in both semantic matchmaking and QoS for automated semantic web service composition.
 \end{abstract}
@@
 Service-oriented computing (SOC) is a novel computing paradigm that employs services as fundamental elements to achieve agile development of cost-efficient and integratable enterprise applications in heterogeneous environments \cite{papazoglou2003service}.
-Service Oriented Architecture (SOA) could abstractly realise service-oriented paradigm of computing, this accomplishment has been contributing to reuse of software components, from functions to units, and from units to services during the development in SOA \cite{booth2004web}.
-One of the most typical realisations of SOA is \textit{web service}, which designated as ``modular, self-describing, self-contained applications that are available on the Internet'' \cite{curbera2001web}.
-And several standards play a significant role in registering, enquiring and grounding web services, such as UDDI, WSDL and SOAP \cite{fensel2011semantic}.
+Service Oriented Architecture (SOA) could abstractly realise service-oriented paradigm of computing.
+This accomplishment has been contributing to the reuse of software components, from functions to units, and from units to services during the development in SOA \cite{booth2004web}.
+One of the most typical realisations of SOA is \textit{web service}, which is designated as ``modular, self-describing, self-contained applications that are available on the Internet'' \cite{curbera2001web}.
+Several standards play a significant role in registering, enquiring and grounding web services including particularly UDDI, WSDL and SOAP \cite{fensel2011semantic}.
 
-\textit{Web service composition} pertains to a combination of several web services to provide a value-added composite service that accommodates customers' arbitrarily complex requirements.
-This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems --- diverse platforms and programming languages \cite{casati2001technologies}.
-Due to an increase in a large-scale alignment of enterprise applications, the number of Web services has increased dramatically and unprecedentedly, which cause an immense redundancy in functionality in a huge searching space.
+\textit{Web service composition} pertains to a combination of multiple web services to provide a value-added composite service that accommodates customers' arbitrarily complex requirements.
+This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems.
+Due to the increase in the number of large-scale enterprise applications, the number of Web services has increased dramatically and unprecedentedly, which cause an immense redundancy in functionality in a huge searching space.
 Therefore, manual and semi-automated web service composition are considered to be less efficient while automated web service composition is deemed to be less human intervention, less time consumption, and high productivity.
 
-Two most notable challenges for web service composition are ensuring interoperability of services and QoS optimisation \cite{fensel2011semantic}.
-Interoperability of web services is one challenge in the dimensions of syntactic and semantics \cite{fensel2011semantic}.
-The syntactic dimension has achieved success through the use of XML standards (such as $WSDL$, $SOAP$), the semantics dimension, on the other hand, demands further research.
-This semantics given by ontologies \cite{o2005review} enables web service to understand and reason with each other.
-Historically, there are many ontologies languages and formats for semantic service descriptions, such as OWL-S \cite{martin2004owl}, WSML \cite{fensel2006enabling}, and SAWSDL \cite{lausen2007semantic}, The logical characteristics in reasoning makes ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments.
-The second challenge is to find optimised solutions to Quality of Service ($QoS$) over the composite web service.
+Two most notable challenges for web service composition are $(1)$ ensuring interoperability of services and $(2)$ achieving QoS optimisation \cite{fensel2011semantic}.
+\textit{Interoperability} of web services presents challenge $(1)$ in the dimensions of syntactic and semantics \cite{fensel2011semantic}.
+The syntactic dimension is covered the XML-based technologies (such as $WSDL$, $SOAP$).
+The semantics aspect, on the other hand, demands further research.
+Through semantics given by ontologies \cite{o2005review}, web services understand and better collaborate with each other.
+Historically, there are many ontologies languages and formats for semantic service descriptions, such as OWL-S \cite{martin2004owl}, WSML \cite{fensel2006enabling}, and SAWSDL \cite{lausen2007semantic}.
+The logical characteristics in reasoning makes ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments.
+The second challenge $(2)$ is related to finding \textit{optimised solutions} to Quality of Service ($QoS$) over composite web services.
 This problems give birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements \cite {sahai2002automated} manifesting a collection of SLA rules and policies for supporting QoS-based composition.
 
-Existing works on service composition are often addressed regarding the above challenges.
+Existing works on service composition focus mainly addressing two challenges above.
 One group optimises the quality of compositions under a pre-defined abstract workflow, which is considered to be a \textit{semi-automated Web service composition} approach.
-Another group attempts to generate a composite plan automatically in discovering and selecting suitable web services, which are deemed to be an NP-hard problem \cite{moghaddam2014service}.
+Another group attempts to generate a composite plan automatically in discovering and selecting suitable web services, which are deemed to NP-hard \cite{moghaddam2014service}.
 \textit{Semantic web services composition} is distinguished from the syntactic service composition.
 Its benefits are presented in eliminating conflicts by the semantic level of web services.
-In the last few years, substantial work has been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}.
-However, few works have addressed an automatic semantic web service composition approach, which optimise both QoS and quality of semantic match making as web service composition solutions.
-For example, customers prefer the highest quality of service solution associated with the acceptable semantic match matching quality.
+In the past few years, substantial works have been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}.
+However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously.
+However, customers often prefer a service composition that matches their requirement most with highest QoS.
 
-The overall goal of this paper is to develop an comprehensive quality awareness automated semantic web service composition that satisfactorily optimises both functional and non-functional requirements.
-Particularly, this project considers a semantic matchmaking quality extension to QoS awareness and two structural constructs (sequence and parallel) for building optimised composition solution using Particle Swarm Optimisation.
-We aim to provide a more general and applicable way to measure semantic matchmaking in automated semantic web service composition and contribute to the state-of-the-art in this field.
-Three objectives of this work are accomplished as follows:
+The overall goal of this paper is to \textit{develop an comprehensive quality-aware automated semantic web service composition that satisfactorily optimises both functional and non-functional requirements}.
+Particularly, this paper considers the quality of semantic matchmaking quality and QoS and two structural constructs (sequence and parallel) for building optimised composition solution using Particle Swarm Optimisation (PSO).
+We aim to provide a more applicable and adaptive way to measure semantic matchmaking in automated semantic web service composition.
+We will achieve three objectives in this work as follows:
 
 \begin{enumerate}
- \item To address semantic matchmaking quality in considering different matching types associated with corresponding semantic similarity, which is demonstrated in a comprehensive quality approach with QoS.
-This approach is consider to be a more general and applicable way of finding an optimised solution in semantic web service composition.
+ \item To propose a comprehensive quality model that address QoS and semantic matchmaking quality in considering different matching types associated with corresponding semantic similarity.
+This approach is consider to be a more applicable and adaptive way of finding an optimised solution in semantic web service composition.
 
- \item To apply PSO for implementing comprehensive awareness automated semantic web service composition.
-PSO sorts out an optimised service queue as a indirect representation of web service composition with consideration of comprehensive quality, and this service queue is further decoded using graph building algorithm to generate a final solution.
+ \item To propose a PSO-based service composition model that utilise the proposed quality model.
+In PSO, each particle represent a weighted graph sorts out an optimised service queue as an indirect representation of web service composition with the consideration of comprehensive quality, and this service queue is further decoded using a graph building algorithm to generate a final solution.
 
- \item To explore the performance of comprehensive quality awareness semantic web service composition, we utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
+ \item To evaluate the performance of comprehensive quality awareness semantic web service composition by utilising benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
 \end{enumerate}
 
-The remains of this paper are composed as the following: Sect.
-\ref{background} provides the knowledge background on the semantic web service composition, including a literature review; Sect.
-\ref{qswsc_approach} represents the an overview of comprehensive quality awareness semantic automated web service composition consisting of comprehensive quality evaluation model and the whole implementation algorithm; Sect.
+The remains of this paper are organized as the following: Sect.
+\ref{background} provides the background on the semantic web service composition, and related works; Sect.
+\ref{qswsc_approach} presents an overview of comprehensive quality awareness semantic automated web service composition consisting of comprehensive quality evaluation model and PSO-based service composition algorithm; Sect.
 \ref{experiment_design} describes the experiments conducted to test the effectiveness of proposed model; Sect.
@@
 \ref{introduction} are also addressed in Sect.
-\ref{qswsc_approach},
+\ref{qswsc_approach}.
 

### 2016-10-30 paper.tex
update

@@
  \item To propose a PSO-based service composition model that utilise the proposed quality model.
-In PSO, each particle represent a weighted graph sorts out an optimised service queue as an indirect representation of web service composition with the consideration of comprehensive quality, and this service queue is further decoded using a graph building algorithm to generate a final solution.
+In PSO, weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively represent the solutions of semantic web service composition as particles, which are decoded from an optimised service queue with the consideration of comprehensive quality.
 
@@
 
-The remains of this paper are organized as the following: Sect.
+The remains of this paper are organised as the following: Sect.
 \ref{background} provides the background on the semantic web service composition, and related works; Sect.
-\ref{qswsc_approach} presents an overview of comprehensive quality awareness semantic automated web service composition consisting of comprehensive quality evaluation model and PSO-based service composition algorithm; Sect.
+\ref{qswsc_approach} presents an overview of comprehensive quality-aware semantic automated web service composition consisting of comprehensive quality evaluation model and PSO-based service composition algorithm; Sect.
 \ref{experiment_design} describes the experiments conducted to test the effectiveness of proposed model; Sect.
-\ref{results_analysis} presents the results and analysis of the experiment; Sect.
-\ref{conclusion} is the paper conclusion.
+\ref{results_analysis} presents and analyses the experiment; Sect.
+\ref{conclusion} concludes our work.
 
@@
 This overall composite goal is demonstrated in two parts.
-The first functional part is a given task input or input set to get the desired Task output or output set, it typically refers to users' functional requirement; another nonfunctional part specifies the acceptable level of composite quality of service.
+The first functional part is a given task input or input set to get the desired Task output or output set.
+It typically refers to users' functional requirement.
+Another nonfunctional part specifies the acceptable level of composite quality of service.
 To accomplish the composite goal, two stages are involved: services discovery and service selection.
-Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from Service Repository: $S \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$.
-Meanwhile, a output set is initialised and updated with found services output, which could be denoted as  $Output Set(T_{input}, S_{output} \in S_1,...,S_{output} \in S_{n-k})$.
-The Output Set is used to discovery all related services until the desired $T_{Output}$ found in the updated Output Set.
-The discovery process normally results in more than one solutions.
-Service selection is to select one of those composite solution considering the closest QoS to $T_{QoS}$.
-To ensure the composite solution returns exact the same or very close $T_{Output}$, we consider a comprehensive quality in both discovery and selection stages, where two challenges mentioned in Sect.
+Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from a Service Repository: $S =  \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$.
+If no atomic web service could satisfy the composite goal, a combination of web services will be found concretely to meet $Comp.G$.
+Firstly, a output set is initialised and updated with found services output, which could be denoted as $Output Set(T_{input}, S_{output} \in S_1,...,S_{output} \in S_{n-k})$.
+The Output set is used to discover all related services until the desired $T_{Output}$ found in the updated Output Set.
+The discovery process normally results in more than one service compositions.
+Therefore, Service selection is to select one of those composite solutions considering the best QoS according to $T_{QoS}$.
+To ensure the composite solution returns the desired $Comp.G$, we consider a comprehensive quality model defined in \ref{qualityModel} for service discovery and selection, where challenges $(1)$ and $(2)$ mentioned in Sect.
 \ref{introduction} are also addressed in Sect.
@@
 The semantic service matchmaking aims to discover appropriate services from service repository relevant to a customer's functional requests.
-A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$ with both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Tax\}$.
-The web service matching process is to pair the output and input concepts of two services according to the Taxonomy(Tax) within an ontology (O).
-To measure the quality of semantic matchmaking, different matching levels that are typically considered in the literature \cite{paolucci2002semantic}: We defined two web services associated with parameters in a particular domain.
-$S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S2$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$ are defined in.
+A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$ with both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Taxonomy\}$.
+A web service matching process is to match the output and input concepts of two services according to the Taxonomy within an Ontology (O).
+To measure the quality of semantic matchmaking, different matching levels are typically considered in the literature \cite{paolucci2002semantic}.
+To understand these levels, let us define two web services associated with parameters in a particular domain.
+$S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S_{2}$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$.
+The matching levels to be considered are:
 
@@
 \item \textit{Exact} ($\equiv$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Exact match ($ S_{output} \in S_{1} \equiv S_{input}S_{2}$), if  Concept $C_{2}$ and Concept $C_{3}$ are equivalent.
-\item \textit{Plugin} ($\sqsubseteq$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Plugin match ($S_{output} \in S_{1} \sqsubseteq S_{input} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of Concept $C_{3}$.
-\item \textit{Subsume} ($\sqsupseteq$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Subsume matched($S_{output} \in S_{1} \sqsupseteq S_{input} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of  Concept $C_{3}$.
+\item \textit{Plugin} ($\sqsubseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Plugin match ($S_{output} \in S_{1} \sqsubseteq_{n} S_{input} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of children concepts ($n=1$ stands for direct children).
+\item \textit{Subsume} ($\sqsupseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Subsume matched($S_{output} \in S_{1} \sqsupseteq_{n} S_{input} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of  Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of parent concepts ($n=1$ stands for direct parent).
 \item \textit{Fail} ($\perp$).
@@
 
-Note that, to find relevant services to automatically form suitable and applicable service compositions for a given goal, we consider Exact, Plugin and Fail match types in our paper.
-Therefore, these three robust matches will be used to discover web service candidates for service composition.
+Note that, to find relevant services for service compositions according to a given goal, we consider Exact, Plugin, Subsume and Fail match types in our paper.
+Therefore, these matches will be used to discover web service candidates for service composition with consideration of the threshold $\alpha$ to enhance the accuracy and efficiency in our proposed the comprehensive quality-aware model in Sect.\ref{semantic_matchmaking}
 
@@
 Currently, most of the optimisation problems \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} in web service composition are focusing on QoS, which covers aspects in non-functional requirements.
-This problem have been explored in both single objective and multi-objectives optimisation.
-Ideally, customers prefer lowest execution cost with highest response time and reliability.
+This problem has been explored in both single objective and multi-objectives optimisation problems.
+Customers prefer lowest execution cost with highest response time and reliability so that it could be involved as a single objective optimisation problem while cost and reliability of web service are two conflicting objectives that could be optimised simultaneously in multi-objective problem.
 According to \cite{zeng2003quality}, four most often considered QoS parameters are as follows:
@@
 \end{itemize}
-The aggregation value of QoS attributes for web services composition varies with respect to different constructs, which explains how services associated with each other \cite{zeng2003quality}.
-Here we consider two composite constructs: both sequence and parallel construts are used in building the composite flow, which are described as follows:
+The aggregation value of QoS attributes for web services composition varies with respect to different constructs, which explains how services associated with each other in a service composition \cite{zeng2003quality}.
+Here we consider two composite constructs: sequence and parallel constructs, in building the composite flow.
+The QoS calculation models are described as follows:
 
@@
 The composite web service executes each atomic service associated with a sequence construct in a definite sequence order.
-The aggregation value for total time ($T$) and total cost ($C$) is the sum of time and cost of web services involved respectively.
+The aggregation value for total time ($T$) and total cost ($C$) is as the sum of time and cost of web services involved respectively.
 The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory.
@@
 Web services in a parallel construct are executed in the meantime.
-The QoS aggregation value in total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is delimited by the maximum time consumed path in the composite flow of the solution.
+The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is delimited by the maximum time consumed path in the composite flow of the solution.
 This construct is presented in Figure \ref{parallel}.
@@
 This approach \cite{da2016particle} is an indirect representation of web service composition using PSO.
-\subsection{Semantic matchmaking}
+\subsection{Semantic matchmaking} \label{semantic_matchmaking}
 

### 2016-10-31 paper.tex
update

@@
 \textbf{Semantic web service matchmaking}.
-Substantial work \cite{bansal2016generalized,mier2015integrated} on semantic web service composition focused mainly on functional requirements while neglecting non-functional requirements.
+Substantial work \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} on web service composition focused mainly on non-functional requirements consistently neglecting functional requirements.
+However few researchers addressed both addressed both of them at the same time in web service composition.
+To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing} are the papers could be found so far.
 Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output parameter concepts of web services to ensure a semantic matchmaking.
-It is to considered be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and pairing a mapping between two knowledge representations encoded utilising the ontology \cite{lecue2006formal}.
+It is considered be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and mapping between two knowledge representations encoded utilising the ontology \cite{lecue2006formal}.
 
-In \cite{shet2012new}, the author surveyed three approaches to the similarity measures using taxonomies: one is based on nodes, in which similarity is determined by the information content of the nodes; one is entirely based on edge, where concept distance in a hierarchy structure is evaluated,  and the hybrid approach that combines the previous two methods.
-A new similarity measure based on edge counting in a taxonomy is introduced in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}.
-Neighbourhood concepts are considered in their model in Formular \ref{equation1}, when $\lambda$ = 1 (default value as 0).
+In \cite{shet2012new}, three approaches are surveyed three approaches regarding the similarity measures using taxonomies: $(1)$ The first one is based on nodes, in which similarity is determined by the information content of the nodes; $(2)$ the second is entirely based on edge, where concept distance in a hierarchy structure is evaluated, and $(3)$ the hybrid approach features a combination of $(1)$ and $(2)$.
+A new similarity measure based on edge counting in taxonomy is introduced in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}.
+Neighbourhood concepts are considered in their model in Formula \ref{equation1}, when $\lambda$ = 1 (default value as 0).
 
@@
 
-In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, the auther utilise one possible measure for the degree of similarity using Common Description rate of a semantic link in Formula \ref{equation2}, where Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are required to be pre-calculated.
+In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, one possible measure is applied for the degree of similarity using Common Description rate of a semantic link in Formula \ref{equation2}, where Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are required to be pre-calculated.
 They also chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint.
@@
 
-However, the weakness of this approach for semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined ontology in the knowledge representation system.
-for example, we may need service profiles definition described in OWL-S, and their related class, class axioms and properties defined in OWL2.
-This makes it nearly impossible to measure semantic matchmaking quality in most semantic web services applications.
-Additionally, a semi-automated service composition approach is considered by the author, rather than a fully automated method.
+However, the weakness of semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined ontology in class, class axioms and properties in OWL2.
+This makes it difficult to measure semantic matchmaking quality in most semantic web services applications.
+Additionally, a semi-automated service composition approach is considered, rather than a fully automated method.
+And only cost and time are considered in the optimised problems.
 Therefore, we introduce a more applicable comprehensive quality model in a fully automated approach.
+
+In \cite{fanjiang2014semantic}, it covers the concerns in both functional and non-functional requirements in design time of semantic-based automatic service composition, where a GA-based approach with four unusual independent fitness functions are designed to solve the problems with these concerns.
+In details, a sequence of fitness functions are used in the binary selection of chromosome, rather than a single objective consisting of both functional and non-functional quality.
+Apart from that, match types are ignored in their quality evaluation of semantic matching.
 
@@
 Evolution Computing techniques are widely used to solve optimisation problem.
-Genetic Programming (GP) \cite{da2015graphevol,da2016particle} is typical EC techniques to solve automated web service composition.
+Genetic Programming (GP) \cite{da2016particle,da2015graphevol} is a typical EC technique to solve automated web service composition.
 This GP-based approach utilises tree representations, on which service and constructs as represented as terminal nodes and functional nodes respectively.
 The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure.
-In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions.
+In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions.
 To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is searched using PSO considering optimising QoS for building up service queue, then web services in this service queue are selected to build up a graph representation of the solution.
@@
 In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS.
-Therefore, we fill the gap by considering different matching types and the similarity when evaluate an overall quality of web service composition.
+Therefore, we fill the gap by considering different matching types and the similarity when evaluate an overall quality of web service composition and utilising a weighed graph representation as the particles in the PSO.
 

### 2016-10-31 paper.tex
update

@@
 However, the weakness of semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined ontology in class, class axioms and properties in OWL2.
-This makes it difficult to measure semantic matchmaking quality in most semantic web services applications.
-Additionally, a semi-automated service composition approach is considered, rather than a fully automated method.
-And only cost and time are considered in the optimised problems.
+This makes it difficult to measure semantic matchmaking quality in most semantic web services applications, as it takes unpredictable cost and time for the domain experts to establish required ontology.
+Additionally, a semi-automated service composition approach is considered in their paper, rather than a fully automated method.
+In QoS, only cost and time are considered in the optimised problems.
 Therefore, we introduce a more applicable comprehensive quality model in a fully automated approach.
@@
 In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions.
+
 To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is searched using PSO considering optimising QoS for building up service queue, then web services in this service queue are selected to build up a graph representation of the solution.
@@
 In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS.
-Therefore, we fill the gap by considering different matching types and the similarity when evaluate an overall quality of web service composition and utilising a weighed graph representation as the particles in the PSO.
+Therefore, we fill the gap by considering different matching types and the similarity when evaluate an overall quality of web service composition and utilising weighed graphs as different particle representations from \cite{da2016particle}.
 

### 2016-10-31 paper.tex
update

@@
 This approach \cite{da2016particle} is an indirect representation of web service composition using PSO.
+
 \subsection{Semantic matchmaking} \label{semantic_matchmaking}
-
-The semantic matchmaking transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match: $match(C_{2}, C_{3})$ defined in Section \ref{semantic Web service Discovery}.
-The matching mechanism attempts to determine whether correct match criteria between the source concepts of C1 and the target concepts of C2, and the quality of semantic matchmaking for these two concepts is calculated in the quality model in subSection \ref{qualityModel}.
+To perform semantic matchmaking transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match in \ref{semantic Web service Discovery}.
+The matching process attempts to determine semantic matching between the source concepts of $C_{1}$ and the target concepts of $C_{2}$ calculated in the quality model in subSection \ref{qualityModel}.
 The advantage of semantic matchmaking quality is to find a more closely requested service output with acceptable level of QoS.
@@
 The overall matching making process is demonstrated in Figure \ref{matchmaking}.
+
+\subsection{Ontology-based Index Cache}
+In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively.
+To effectively construct weighted graphs, we pre-calculate semantic matchmaking quality and mark the input-parameter concepts with a set of services.
+The key idea of the index is to create a mapping from the output-related concepts to matched input-related services while considering different levels of match types.
+Furthermore, the repository size could also be reduced by considering users' predefined acceptable semantic matching quality, which eliminates the influence of low composition accuracy.
+The service repository size is further reduced to the available output parameter concepts are input-relevant and more than the threshold.
+
+This implementation contributes to less time and constant time for weighted graph building.
 

### 2016-10-31 paper.tex
update

@@
 \subsection{Semantic matchmaking} \label{semantic_matchmaking}
-To perform semantic matchmaking transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match in \ref{semantic Web service Discovery}.
+To perform semantic matchmaking, we transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match in \ref{semantic Web service Discovery}.
 The matching process attempts to determine semantic matching between the source concepts of $C_{1}$ and the target concepts of $C_{2}$ calculated in the quality model in subSection \ref{qualityModel}.
-The advantage of semantic matchmaking quality is to find a more closely requested service output with acceptable level of QoS.
+The purpose of semantic matchmaking quality is to find more component services that satisfies the quality of QoS.
 
-The semantic matchmaking is achieved by utilising semantic annotation with OWL and OWL-S.
-In this paper, we use MECE ontologies \cite{bleul2008self}, which could be considered to be an alternative form of ontology for services.
-In ontology, semantics specifies the both concepts and individuals in the terms of classes and instances wherer semantic concepts are expressed with the their statements and relationship in RDFs (such as subClassOf ), and the semantic individuals are related to the input and output parameters of web services.
-The MECE is an extensive annotation to WSDL files, which defines the each parameter of services associated with their semantic individuals.
+The semantic matchmaking is typically achieved by utilising OWL2 and OWL-S.
+In this paper, we use MECE (Mediation Contract Extension) \cite{bleul2008self} and OWL-DL, MECE is considered to be an alternative semantic annotation for WSDL.
+MECE defines the service-related inputs and outputs with parameter-related concepts.
+OWL-DL is a sublanguage of OWL from extension of RDF.
+which specifies semantic information of concepts involved in MECE.
 The overall matching making process is demonstrated in Figure \ref{matchmaking}.
 
-\subsection{Ontology-based Index Cache}
+\subsection{Ontology-based Index Cached Optimisation}
 In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively.
@@
 Furthermore, the repository size could also be reduced by considering users' predefined acceptable semantic matching quality, which eliminates the influence of low composition accuracy.
-The service repository size is further reduced to the available output parameter concepts are input-relevant and more than the threshold.
+The service repository size is further reduced to the available output parameter concepts are input-relevant and more than the threshold $\alpha$.
 

### 2016-10-31 paper.tex
up

@@
 \end{figure}
-In this paper, we model comprehensive quality awareness automated semantic service composition with graphs.
+In this paper, we propose a comprehensive quality model for automated semantic service composition, and optimise both the quality of semantic matchmaking and QoS.
 PSO has shown its efficiency in solving combinatorial optimisation problems.
-Therefore, we will propose a PSO-based approach, which is considered to be simple and efficient without penalising or repairing comparing to GP \cite{da2014graph}.
-Fig.
-\ref{overview} shows the overview of our approach with the five steps included.
-Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements in functional and non-functional parts.
-The first functional one is defined as $F(T_{Input}, T_{Output})$ , and the second nonfunctional one is users' accepted level of QoS.
-Step 2: Those requirements are initially used to discover all relevant web services, which leads to a shrunken service repository that further used by PSO as a searching space.
-Step 3: a graph representation is randomly built up interleaving with semantic matchmaking process, where web services are discovered and connected while calculating matchmaking quality that will be explained in Subsect.
+Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing comparing to GP \cite{da2014graph}.Fig.
+\ref{overview} shows the overview of our approach with five steps.
+Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional.
+A functional requirement is defined as $F(T_{Input}, T_{Output})$ , and a nonfunctional one is users' accepted level of QoS.
+Step 2: Those requirements are used to discover all relevant web services, which leads to a shrunken service repository that further used by PSO as a searching space.
+Step 3: a weighted graph representation is randomly built up interleaving with semantic matchmaking process, where web services are discovered and connected while calculating matchmaking quality that will be explained in Subsect.
 \ref{qualityModel}.
-Step 4,5: The selection of web services is performed over the PSO algorithm in subSect.
-\ref{pso_algorithm}, which is used to find best particle location mapped back to a service queue for building graph solutions considering comprehensive quality.
-This approach \cite{da2016particle} is an indirect representation of web service composition using PSO.
+Step 4,5: The selection of web services performs PSO algorithm in Sect.
+\ref{pso_algorithm} to find best particle location.
+This approach is different from \cite{da2016particle}.
+Here we use weighted graphs as particle presentation while considering a comprehensive quality.
 

### 2016-11-01 paper.tex
update

@@
  \item To propose a comprehensive quality model that address QoS and semantic matchmaking quality in considering different matching types associated with corresponding semantic similarity.
-This approach is consider to be a more applicable and adaptive way of finding an optimised solution in semantic web service composition.
+This approach is consider to be a more applicable and effective way of finding an optimised solution in semantic web service composition.
 
  \item To propose a PSO-based service composition model that utilise the proposed quality model.
-In PSO, weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively represent the solutions of semantic web service composition as particles, which are decoded from an optimised service queue with the consideration of comprehensive quality.
+In PSO, weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively represent the solutions of semantic web service composition as particles in the searching space, which are decoded from an optimised service queue with the consideration of comprehensive quality.
 
@@
 
-\section{Background}\label{background}
+\section{Related Work} \label{relatedWork}
+\textbf{Semantic web service matchmaking}.
+Substantial work \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} on web service composition focused mainly on non-functional requirements consistently neglecting functional requirements.
+However few researchers addressed both addressed both of them at the same time in web service composition.
+To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing} are the papers could be found so far.
+Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output parameter concepts of web services to ensure a semantic matchmaking.
+It is considered be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and mapping between two knowledge representations encoded utilising the ontology \cite{lecue2006formal}.
 
-\subsection{Problem Description}\label{problemDes}
+In \cite{shet2012new}, three approaches are surveyed three approaches regarding the similarity measures using taxonomies: $(1)$ The first one is based on nodes, in which similarity is determined by the information content of the nodes; $(2)$ the second is entirely based on edge, where concept distance in a hierarchy structure is evaluated, and $(3)$ the hybrid approach features a combination of $(1)$ and $(2)$.
+A new similarity measure based on edge counting in taxonomy is introduced in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}.
+Neighbourhood concepts are considered in their model when $\lambda$ = 1 (default value as 0).
+
+In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, one possible measure is applied for the degree of similarity using Common Description rate of a semantic link, where Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are required to be pre-calculated.
+They also chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint.
+Therefore, the quality of the semantic link is estimated as quality criteria $q_{m}$ associated with their corresponding quality of vector $q_{cd}$.
+
+However, the weakness of semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined ontology in class, class axioms and properties in OWL2.
+This makes it difficult to measure semantic matchmaking quality in most semantic web services applications, as it takes unpredictable cost and time for the domain experts to establish required ontology.
+Additionally, a semi-automated service composition approach is considered in their paper, rather than a fully automated method.
+In QoS, only cost and time are considered in the optimised problems.
+Therefore, we introduce a more applicable comprehensive quality model in a fully automated approach.
+
+In \cite{fanjiang2014semantic}, it covers the concerns in both functional and non-functional requirements in design time of semantic-based automatic service composition, where a GA-based approach with four unusual independent fitness functions are designed to solve the problems with these concerns.
+In details, a sequence of fitness functions are used in the binary selection of chromosomes, rather than a single objective consisting of both functional and non-functional quality.
+Apart from that, match types are ignored in their quality evaluation of semantic matching.
+
+\textbf{QoS-aware EC approaches}.
+Evolution Computing techniques are widely used to solve optimisation problem.
+Genetic Programming (GP) \cite{da2016particle,da2015graphevol} is a typical EC technique to solve automated web service composition.
+This GP-based approach utilises tree representations, on which service and constructs as represented as terminal nodes and functional nodes respectively.
+The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure.
+In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions.
+
+To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}.
+A general graph is used as representation as particles in their PSO algorithm considering QoS optimisation.
+However, this solution does not distinguish different matching types and parameter similarity, which could lead to the outputs returned by the selected service that we think may be too general.
+In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the outputs requested by users.
+In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS.
+Therefore, we fill the gap by considering different matching types and the similarity when evaluate an overall quality of web service composition and utilising weighed graphs as different particle representations from \cite{da2016particle}.
+
+\section{Problem Description}\label{problemDes}
 
@@
 If no atomic web service could satisfy the composite goal, a combination of web services will be found concretely to meet $Comp.G$.
-Firstly, a output set is initialised and updated with found services output, which could be denoted as $Output Set(T_{input}, S_{output} \in S_1,...,S_{output} \in S_{n-k})$.
-The Output set is used to discover all related services until the desired $T_{Output}$ found in the updated Output Set.
-The discovery process normally results in more than one service compositions.
-Therefore, Service selection is to select one of those composite solutions considering the best QoS according to $T_{QoS}$.
-To ensure the composite solution returns the desired $Comp.G$, we consider a comprehensive quality model defined in \ref{qualityModel} for service discovery and selection, where challenges $(1)$ and $(2)$ mentioned in Sect.
+To ensure the composite solution returns the desired $Comp.G$, we consider a comprehensive quality model for service discovery and selection, where challenges $(1)$ and $(2)$ mentioned in Sect.
 \ref{introduction} are also addressed in Sect.
@@
 Note that, to find relevant services for service compositions according to a given goal, we consider Exact, Plugin, Subsume and Fail match types in our paper.
-Therefore, these matches will be used to discover web service candidates for service composition with consideration of the threshold $\alpha$ to enhance the accuracy and efficiency in our proposed the comprehensive quality-aware model in Sect.\ref{semantic_matchmaking}
+Therefore, these matches will be used to discover web service candidates for service composition in our proposed the comprehensive quality-aware model in Sect.\ref{semantic_matchmaking}
 
@@
 
-\subsection{Related Work} \label{relatedWork}
-\textbf{Semantic web service matchmaking}.
-Substantial work \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} on web service composition focused mainly on non-functional requirements consistently neglecting functional requirements.
-However few researchers addressed both addressed both of them at the same time in web service composition.
-To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing} are the papers could be found so far.
-Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output parameter concepts of web services to ensure a semantic matchmaking.
-It is considered be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and mapping between two knowledge representations encoded utilising the ontology \cite{lecue2006formal}.
-
-In \cite{shet2012new}, three approaches are surveyed three approaches regarding the similarity measures using taxonomies: $(1)$ The first one is based on nodes, in which similarity is determined by the information content of the nodes; $(2)$ the second is entirely based on edge, where concept distance in a hierarchy structure is evaluated, and $(3)$ the hybrid approach features a combination of $(1)$ and $(2)$.
-A new similarity measure based on edge counting in taxonomy is introduced in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}.
-Neighbourhood concepts are considered in their model in Formula \ref{equation1}, when $\lambda$ = 1 (default value as 0).
-
-\begin{equation}
-q(s_ {similarity}){=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
-\label{equation1}
-\end{equation}
-
-In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, one possible measure is applied for the degree of similarity using Common Description rate of a semantic link in Formula \ref{equation2}, where Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are required to be pre-calculated.
-They also chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint.
-Therefore, the quality of the semantic link is estimated as quality criteria $q_{m}$ associated with their corresponding quality of vector $q_{cd}$ defined as Formula \ref{equation3}.
-
-\begin{equation}
-q_{cd}(sl{_{i,j}})={=} \frac{|lcs(Out_{s_i},In_{s_j})|}{|In_{s_{x}} \setminus Out_{s{_y}} \stackrel{.}| +|lcs(Out_{s_i},In_{s_j})| }
- \label{equation2}
-\end{equation}
-
-\begin{equation}
-\label{equation3}
-q(sl{_{i,j}}) \stackrel{.}{=} (q_{mt}(sl_{i,j}), q_{cd}(sl_{i,j}))
-\end{equation}
-
-However, the weakness of semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined ontology in class, class axioms and properties in OWL2.
-This makes it difficult to measure semantic matchmaking quality in most semantic web services applications, as it takes unpredictable cost and time for the domain experts to establish required ontology.
-Additionally, a semi-automated service composition approach is considered in their paper, rather than a fully automated method.
-In QoS, only cost and time are considered in the optimised problems.
-Therefore, we introduce a more applicable comprehensive quality model in a fully automated approach.
-
-In \cite{fanjiang2014semantic}, it covers the concerns in both functional and non-functional requirements in design time of semantic-based automatic service composition, where a GA-based approach with four unusual independent fitness functions are designed to solve the problems with these concerns.
-In details, a sequence of fitness functions are used in the binary selection of chromosome, rather than a single objective consisting of both functional and non-functional quality.
-Apart from that, match types are ignored in their quality evaluation of semantic matching.
-
-\textbf{QoS-aware EC approaches}.
-Evolution Computing techniques are widely used to solve optimisation problem.
-Genetic Programming (GP) \cite{da2016particle,da2015graphevol} is a typical EC technique to solve automated web service composition.
-This GP-based approach utilises tree representations, on which service and constructs as represented as terminal nodes and functional nodes respectively.
-The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure.
-In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions.
-
-To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is searched using PSO considering optimising QoS for building up service queue, then web services in this service queue are selected to build up a graph representation of the solution.
-However, this solution does not distinguish different matching types and parameter similarity, which could lead to the outputs returned by the selected service that we think may be too general.
-In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the outputs requested by users.
-In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS.
-Therefore, we fill the gap by considering different matching types and the similarity when evaluate an overall quality of web service composition and utilising weighed graphs as different particle representations from \cite{da2016particle}.
-
 \section{QoS-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
@@
 PSO has shown its efficiency in solving combinatorial optimisation problems.
-Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing comparing to GP \cite{da2014graph}.Fig.
+Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing comparing to GP \cite{da2014graph}.
+Fig.
 \ref{overview} shows the overview of our approach with five steps.
@@
 Step 2: Those requirements are used to discover all relevant web services, which leads to a shrunken service repository that further used by PSO as a searching space.
-Step 3: a weighted graph representation is randomly built up interleaving with semantic matchmaking process, where web services are discovered and connected while calculating matchmaking quality that will be explained in Subsect.
-\ref{qualityModel}.
+Step 3: A weighted graph representation is randomly built up interleaving with semantic matchmaking process, where web services are discovered as graph vertices while edges are assigned with semantic matchmaking quality as weights.
 Step 4,5: The selection of web services performs PSO algorithm in Sect.
 \ref{pso_algorithm} to find best particle location.
-This approach is different from \cite{da2016particle}.
-Here we use weighted graphs as particle presentation while considering a comprehensive quality.
+Overall, this approach is different from \cite{da2016particle}, as we use weighted graphs as particle presentation while considering a comprehensive quality.
 
@@
 To perform semantic matchmaking, we transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match in \ref{semantic Web service Discovery}.
-The matching process attempts to determine semantic matching between the source concepts of $C_{1}$ and the target concepts of $C_{2}$ calculated in the quality model in subSection \ref{qualityModel}.
-The purpose of semantic matchmaking quality is to find more component services that satisfies the quality of QoS.
+The matching process attempts to determine semantic matching between the source concepts of $C_{1}$ and the target concepts of $C_{2}$.
+Meanwhile, the quality of matched concepts are calculated in the mode model in subSection \ref{qualityModel}.
+The purpose of semantic matchmaking is to find more component services that could also potentially satisfies the quality of QoS with considering its functional quality.
 
@@
 which specifies semantic information of concepts involved in MECE.
-The overall matching making process is demonstrated in Figure \ref{matchmaking}.
-
-\subsection{Ontology-based Index Cached Optimisation}
-In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively.
-To effectively construct weighted graphs, we pre-calculate semantic matchmaking quality and mark the input-parameter concepts with a set of services.
-The key idea of the index is to create a mapping from the output-related concepts to matched input-related services while considering different levels of match types.
-Furthermore, the repository size could also be reduced by considering users' predefined acceptable semantic matching quality, which eliminates the influence of low composition accuracy.
-The service repository size is further reduced to the available output parameter concepts are input-relevant and more than the threshold $\alpha$.
-
-This implementation contributes to less time and constant time for weighted graph building.
-
-\begin{figure}[h]
-\centerline{
-\fbox{
-\includegraphics[width=10cm]{matchmaking.pdf}}}
- \caption{Semantic matchmaking.}
- \label{matchmaking}
-\end{figure}
 
@@
 In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition.
-This model overcome the disadvantages of current prevailing QoS-aware optimisation, in which quality of semantic matchmaking are not considered.
+This model overcome the disadvantages of current prevailing QoS-aware optimisation, in which quality of semantic matchmaking are not considered \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive}.
 
@@
 Due to the discretisational characteristics of different match types driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}.
-Match type is considered to be one factor for the semantic matchmaking quality.
-Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new} --- a taxonomy-based measurement for ontology matching.
-In this paper, it could be used to estimate the parameter concepts similarity between the given output and available input for selecting web services.
+Match types are considered to be one factor for the semantic matchmaking quality.
+Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, which is a taxonomy-based measurement for ontology matching.
+This formula \ref{equation1} is used to estimate the similarity between output-related concept and input-related concept for selecting web services.
 Therefore, given the quality match type and the similarity of two parameters, the semantic matchmaking quality is defined as Formula \ref{equation4}, where the value of $q(s_ {matchType})$ is set up as the same as the quality of the semantic link in literature \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection) while $q(s_ {similarity})$ is calculated utilising formula \ref{equation1} in subsection \ref{relatedWork}.
+\begin{equation}
+q(s_ {similarity}){=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
+\label{equation1}
+\end{equation}
 
@@
 In addition, dangle service nodes and edges should be removed.
+
+Firstly, a output set is initialised and updated with found services output, which could be denoted as $Output Set(T_{input}, S_{output} \in S_1,...,S_{output} \in S_{n-k})$.
+The Output set is used to discover all related services until the desired $T_{Output}$ found in the updated Output Set.
+The discovery process normally results in more than one service compositions.
+Therefore, Service selection is to select one of those composite solutions considering the best QoS according to $T_{QoS}$
 

### 2016-11-01 paper.tex
update
update

@@
 \textbf{Semantic matchmaking model}.
-Due to the discretisational characteristics of different match types driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}.
-Match types are considered to be one factor for the semantic matchmaking quality.
+Due to the discretisational characteristics of different match types driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}, match types are considered to be one factor for the semantic matchmaking quality.
 Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, which is a taxonomy-based measurement for ontology matching.
-This formula \ref{equation1} is used to estimate the similarity between output-related concept and input-related concept for selecting web services.
-Therefore, given the quality match type and the similarity of two parameters, the semantic matchmaking quality is defined as Formula \ref{equation4}, where the value of $q(s_ {matchType})$ is set up as the same as the quality of the semantic link in literature \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection) while $q(s_ {similarity})$ is calculated utilising formula \ref{equation1} in subsection \ref{relatedWork}.
+This formula \ref{equation1} is used to estimate the similarity between parameter-related output concept and parameter-related input concept for selecting web services.
+Therefore, given the quality match type and the similarity of two parameters-related concepts, the semantic matchmaking quality of matched parameters is defined by Formula \ref{equation2}, where the value of $q(p_ {matchType})$ is set up as the same as the quality of the semantic link in \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).
+
 \begin{equation}
-q(s_ {similarity}){=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
+q(p_ {s}){=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
 \label{equation1}
@@
 \begin{equation}
-\label{equation4}
-q_{sm} \stackrel{.}{=} (q(s_ {matchType}), \  q(s_ {similarity}))
+\label{equation2}
+q(p_{sm}) \stackrel{.}{=} (q(p_ {mt}), \  q(p_ {s}))
+\end{equation}
+
+Further more, edges represent services connections in our weighted graph presentations, where assigned weight value $q(e_{sm})$ is considered to be semantic matching quality on edge level according to parameter aggregations.
+The weight value $q(e_{sm})$ is defined in \ref{equation3}, where $q(e_ {matchType})$ and $q(e_ {similarity})$ are the mean value of concept-related parameters quality in $q(p_{mt})$ and $q(p_{s})$ respectively.
+
+\begin{equation}
+\label{equation3}
+q(e_{sm}) \stackrel{.}{=} (q(e_ {mt}), \  q(e_ {s}))
 \end{equation}
@@
 \textbf{Comprehensive quality model}.
-Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional requirements of composite goal.
-The non-functional properties typically refers to previously discussed QoS, which are given by service providers.
-Consequently, the comprehensive quality model integrated the semantic matchmaking quality $q(s_{sm})$ in Formula \ref{equation5}, which could be further broken down into Formula \ref{equation6}.
-
+Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional requirements of a goal.
+The comprehensive quality of our service composition representation refers to QoS of service vertices and Semantic matching quality of Edges in weighted graphs.
+Consequently, the comprehensive quality model is defined in Formula \ref{equation4}, which could be further broken down into Formula \ref{equation5}.
+\begin{equation}
+\label{equation4}
+q_{cq} \stackrel{.}{=} (q(e_ {sm}), \  q(v_ {QoS}))
+\end{equation}
 \begin{equation}
 \label{equation5}
-q_{cq} \stackrel{.}{=} (q(s_ {sm}), \  q(s_ {QoS}))
-\end{equation}
-\begin{equation}
-\label{equation6}
-q_{cq} \stackrel{.}{=} (q(s_ {mt}), \  q(s_ {s}), \  q(s_{a}),\  q(s_{r}),\  q(s_{c}),\  q(s_{t}))
+q_{cq} \stackrel{.}{=} (q(e_ {mt}), \  q(e_ {s}), \  q(v_{a}),\  q(v_{r}),\  q(v_{c}),\  q(v_{t}))
 \end{equation}
 
-\textbf{Quality aggregate matrix}.The quality aggregation is defined based on the constructs of composite web services on the criteria of functional and non-functional properties.
-Generally, web services could have more than one concept-related parameters.
-In semantic matchmaking process, two levels of quality aggregation are considered --- edge level and construct level.
-At edge level, the edge-level quality aggregation is determined by the mean value of concept-related parameter quality in $q(s_{mt})$ and $q(s_{s})$ respectively.
-Meanwhile, the construct-level quality is further calculated based on the constructs following the rules in Table \ref{table1} --- a quality aggregate matrix for semantic web service composition.
+\textbf{Quality aggregate matrix}.
+The quality aggregation is defined based on the constructs of composite web services on the criteria of functional and non-functional properties.
+The quality on construct level is further calculated following the rules in Table \ref{table1} --- a quality aggregate matrix for semantic web service composition.
 Both the $Q(s_{mt})$ and $Q(s_{s})$ are considered by calculating the product function of involved edge-level $q(s_{mt})$, and mean function of edge-level $q(s_{s})$ respectively.
@@
 \multicolumn{3}{|c|}{Composition Construct}                                      & Sequence                             & Parallel \\ \hline
-\multirow{5}{*}{QualityFactors} & \multirow{2}{*}{Functional}    & $Q(s_ {mt})$  &$\prod_{n=1}^{m} q(s_ {mt})$          &  $\prod_{n=1}^{m} q(s_ {mt})$ \\ \cline{3-5}
-                                &                                & $Q(s_ {s})$  & $(\sum_{n=1}^m q(s_ {s}))/m$        &  $(\sum_{n=1}^m q(s_ {s}))/m$  \\ \cline{2-5}   
-                                & \multirow{4}{*}{NonFunctional} & $Q(s_{a})$    & $\prod_{n=1}^{m} q(s_a)$             &  $\prod_{n=1}^{m} q(s_a)$ \\ \cline{3-5} 
-                                &                                & $Q(s_{r})$    & $\prod_{n=1}^{m} q(s_r)$             &  $\prod_{n=1}^{m} q(s_r)$ \\ \cline{3-5} 
-                                &                                & $Q(s_{c})$    & $\sum_{n=1}^m q(s_ {c})$             &  $\sum_{n=1}^m q(s_ {c})$ \\ \cline{3-5} 
-                                &                                & $Q(s_{t})$    & $\sum_{n=1}^m q(s_ {t})$             &  $max(q(s_ {t}))$ \\ \hline
+\multirow{5}{*}{QualityFactors} & \multirow{2}{*}{Functional}    & $Q(e_ {mt})$  &$\prod_{n=1}^{m} q(e_ {mt})$          &  $\prod_{n=1}^{m} q(e_ {mt})$ \\ \cline{3-5}
+                                &                                & $Q(e_ {s})$  & $(\sum_{n=1}^m q(e_ {s}))/m$        &  $(\sum_{n=1}^m q(e_ {s}))/m$  \\ \cline{2-5}   
+                                & \multirow{4}{*}{NonFunctional} & $Q(v_{a})$    & $\prod_{n=1}^{m} q(v_a)$             &  $\prod_{n=1}^{m} q(v_a)$ \\ \cline{3-5} 
+                                &                                & $Q(v_{r})$    & $\prod_{n=1}^{m} q(v_r)$             &  $\prod_{n=1}^{m} q(v_r)$ \\ \cline{3-5} 
+                                &                                & $Q(v_{c})$    & $\sum_{n=1}^m q(v_ {c})$             &  $\sum_{n=1}^m q(v_ {c})$ \\ \cline{3-5} 
+                                &                                & $Q(v_{t})$    & $\sum_{n=1}^m q(v_ {t})$             &  $max(q(v_ {t}))$ \\ \hline
 \end{tabular}

### 2016-11-02 paper.tex
update

@@
 
-The semantic matchmaking is typically achieved by utilising OWL2 and OWL-S.
+The semantic matchmaking is achieved by utilising OWL2 and OWL-S or other semantic markup languages for web services.
 In this paper, we use MECE (Mediation Contract Extension) \cite{bleul2008self} and OWL-DL, MECE is considered to be an alternative semantic annotation for WSDL.
@@
 The quality aggregation is defined based on the constructs of composite web services on the criteria of functional and non-functional properties.
-The quality on construct level is further calculated following the rules in Table \ref{table1} --- a quality aggregate matrix for semantic web service composition.
-Both the $Q(s_{mt})$ and $Q(s_{s})$ are considered by calculating the product function of involved edge-level $q(s_{mt})$, and mean function of edge-level $q(s_{s})$ respectively.
-The QoS aggregation $Q(q_{QoS})$ calculation is same to \cite{cardoso2004quality}.
+The quality on construct level is further calculated and by following the rules summarised in Table \ref{table1}.
 
@@
 \subsection{Fitness Calculation}
-The fitness value is calculated from the aggregated value of quality components involved in a graph-based service composition.
-A weighted sum of those components is utilised in the fitness function \ref{equation7}, in which fitness value of 1 means the best comprehensive quality and 0 means the worst.
-As the sum of all the function weights (w1 to w6) is equal to 1, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the fitness value falls within 0 to 1.
-Also, the lowest T and C value represent the best conponent quality so that the objective function is offset using $(1 - T)$ and $(1 - C)$.
+The fitness value of a service composition solution is a weighted sum of all the quality components discussed previously shown in Formula \ref{equation6}, in which fitness value of 1 means the best comprehensive quality and 0 means the worst.
+As the sum of all the components' weights ($w_1$ to $w_6$) equals to 1, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the fitness value falls within the range from 0 to 1.
+Also, the lowest T and C value represent the best component quality so that the objective function can be offset using $(1 - T)$ and $(1 - C)$.
 
 \begin{equation}
-\label{equation7}
+\label{equation6}
 Fitness = w_1MT + w_2S + w_3A + w_4R + w_5(1 - T) + w_6(1 - C)
 \end{equation}
-
 \noindent where $\sum_{i=1}^{6} w_i = 1$
 
-\subsection{QoS-aware Semantic Web Service Composition algorithm} \label{pso_algorithm}
+\subsection{QoS-aware Semantic Web Service Composition Algorithm} \label{pso_algorithm}
+
 \begin{algorithm}[!htb]
@@
 \newcommand{\nonl}{\renewcommand{\nl}{\let\nl\oldnl}}
-\textbf{Input}: I, O \\
-\textbf{Output}: G \\
  \LinesNumbered
-	\textbf{1.} Randomly initialise each particle in the swarm.\\
+ 	\textbf{1.} Map each relevant service to an index in the particle's position vector.\\
+	\textbf{2.} Randomly initialise each particle in the swarm.\\
 	\nonl \While {max. iterations not met}{
 		\ForAll{particles in the swarm}{
-			\textbf{2.} Sort particle's position vector as a service queue in ascending order\\
-			\textbf{3.} Initialise OutputSet with Task Input $\leftarrow I$ \\
-			\textbf{4.} Initialise a graph G with a startNode\\
-			\nonl \While {max. OutputSet not contains Task Output $\leftarrow O$}{
-				\textbf{5.} Get web service from service queue\\
-				\If{All inputs of current web service satisfied with output from outputSet}{
-					\textbf{6.} Create and connect service edge associated with matchmaking quality to graph.\\
-					\textbf{7.} Create and connect node(current web service) to graph.\\
-					\textbf{8.} Remove current web service from the queue.\\
-					\textbf{9.} Update OutputSet with outputs current web service.\\
-				}
-				\textbf{10.} Get next web service from service queue\\
-			}
-			\textbf{11.} Connect endNode the graph G\\
-			\textbf{12.} Remove dangle services from the graph G\\
-			\textbf{13.} Remove dangle edges from graph G\\
-			\textbf{14.} Aggregation of semantic matchmaking and QoS\\
-			\textbf{15.} Calculate the particle's fitness.\\
+		    \textbf{3.} Create queue of services using the particle's position vector.\\
+			\textcolor{blue}{\textbf{4.} Build a weighted graph using the queue.}\\
+			\textcolor{blue}{\textbf{5.} Calculate the fitness of the weighted graph.}\\
 			\eIf{fitness value better than pBest}{
-				\textbf{16.} Assign current fitness as new pBest.\\
+				\textbf{6a.} Assign current fitness as new pBest.\\
 			}{
-				\textbf{17.} Keep previous pBest.\\
+				\textbf{6b.} Keep previous pBest.\\
 			}		
 		}
-		\textbf{18.} Assign best particle's pBest value to gBest, if better than gBest.\\
-		\textbf{19.} Calculate the velocity of each particle according to the equation:\\
-		\textbf{19.} Update the position of each particle according to the equation:\\
+		\textbf{7.} Assign best particle's pBest value to gBest, if better than gBest.\\
+		\textbf{8.} Calculate the velocity of each particle according to the equation:\\
+		\Indp $v_{id} = v_{id} + c_1 * rand() * (p_{id} - x_{id}) + c_2 * rand() * (p_{gd} - x_{id})$\\
+		\Indm \textbf{9.} Update the position of each particle according to the equation:\\
+		\Indp $x_{id} = x_{id} + v_{id}$\\
 	}
-		\textbf{20.} return Graph in the last iteration $ \rightarrow G$.\\
 
- \caption{Steps of graph-based PSO optimisation technique.}
-\label{psoSteps}
+ \caption{Steps of the PSO-based Web service composition technique.}
+\label{novelSteps}
 \end{algorithm}
-The overall algorithm investigated here is a simple forward decoding PSO \cite{da2016particle} with our comprehensive quality evaluation model.
-The idea is to translate the particle location into a service queue as an indirect representation of graph-based service composition, so finding the best fitness of the composite service solution is to discover the optimised location of the particle.
-In PSO, the dimension of the particle is set up as the same as the number of relevant web services in the shrunken service repository, and all the services index is mapped to the location in a particle, and we put services in a queue in ascending order, from which we decode a corresponding graph using a forward graph-building technique.
-The particle's fitness value can be calculated based on that built graph.
-During the evolutionary process, pBest and gBest value are assigned and updated in each generation with new-updated particles' position while graph-based solutions are generated at the same time.
-eventually, we return the graph built from the last generation as an optimised solution.
-In the forward graph building algorithm.
-We select and connect web services to the startNode from the service queue if the web service can satisfy the given $T_{input}$.
+
+\begin{algorithm}[!htb]
+ \setlength\hsize{0.9\linewidth}
+ \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
+ \SetKwFunction{connectNode}{connectNode}\SetKwFunction{findCands}{findCands}\SetKwFunction{removeDangling}{removeDangling}
+ \LinesNumbered
+ \SetNlSty{}{}{:}
+ \Input{$I$, $O$, $queue$}
+ \Output{composition weighted graph $WG$}
+ Create $start$ vertex with outputs $I$ and $end$ vertex with inputs $O$\;
+ Create graph $WG$ containing the $start$ vertex\;
+ Create available outputs set containing $start$ outputs\;
+ \While{available outputs do not satisfy $end$ inputs}{
+ Get next candidate from queue\;
+ \If{candidate inputs are satisfied by available outputs}{
+ \textcolor{blue}{Create edge assigned with weight\;}
+ \textcolor{blue}{Connect vertex to graph with the edge\;}
+ Remove it from queue and go back to the queue's beginning\;
+ }}
+ Connect end vetex\;
+ Remove dangling vertices from graph $WG$\;
+ Remove dangling edges from graph $WG$
+ \KwRet $WG$\;
+ \caption{Create a composition weighted graph from a queue}
+\label{graph_building}
+\end{algorithm}
+
+The overall algorithm investigated here is a PSO-based web service composition algorithm \ref{novelSteps} from   \cite{da2016particle} with a different decoded algorithm \ref{graph_building} to generate a composition weighted graph from a queue.
+In the first algorithm, the idea is to translate the particle location into a service queue as an indirect representation of composition weighted graph, so finding the best fitness of the composite service solution is to discover the optimised location of the particle.
+In PSO, the dimension of the particle is set up as the same as the number of relevant web services, and all the services index is mapped to the location in a particle, and we put services in a queue in ascending order, from which we decode a weighted graph using Algorithm \ref{graph_building}.
+We select and connect web services to the start Vetex from the service queue if the web service can satisfy the given $T_{input}$.
 Meanwhile, an Output Set is initialised and kept being updated using outputs from the new-added web services in the graph, later on, more services are connected if services' inputs could be satisfied by any output in the Output Set.
-At last, The end node is connected if the updated Output Set contains the $T_{output}$.
+At last, The end vetex is connected if the updated Output Set contains the $T_{output}$.
 In addition, dangle service nodes and edges should be removed.
-
-Firstly, a output set is initialised and updated with found services output, which could be denoted as $Output Set(T_{input}, S_{output} \in S_1,...,S_{output} \in S_{n-k})$.
-The Output set is used to discover all related services until the desired $T_{Output}$ found in the updated Output Set.
-The discovery process normally results in more than one service compositions.
-Therefore, Service selection is to select one of those composite solutions considering the best QoS according to $T_{QoS}$
 

### 2016-11-02 paper.tex
update

@@
 As the sum of all the components' weights ($w_1$ to $w_6$) equals to 1, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the fitness value falls within the range from 0 to 1.
-Also, the lowest T and C value represent the best component quality so that the objective function can be offset using $(1 - T)$ and $(1 - C)$.
+Also, the lowest T and C value represent the best component quality so that the objective function can be offset using $(1 - T)$ and $(1 - C)$ using normalisation formula \ref{equation8}, and normalisation formula \ref{equation7} is for the rest components.
+Therefore, the whole problem is treated as a maximisation problem.
 
@@
 \noindent where $\sum_{i=1}^{6} w_i = 1$
+\\\\
+\begin{equation}
+\label{equation7}
+normalise(value) = 
+\begin{cases}
+	\frac{value - min}{max - min} & \text{ if }max - min \neq 0.\\
+	1 & \mathrm{ otherwise}.
+\end{cases}
+\end{equation}
+\begin{equation}
+\label{equation8}
+normalise(value) = 
+\begin{cases}
+	\frac{max - value}{max - min} & \text{ if }max - min \neq 0.\\
+	1 & \mathrm{ otherwise}.
+\end{cases}
+\end{equation}
 
@@
 The overall algorithm investigated here is a PSO-based web service composition algorithm \ref{novelSteps} from   \cite{da2016particle} with a different decoded algorithm \ref{graph_building} to generate a composition weighted graph from a queue.
-In the first algorithm, the idea is to translate the particle location into a service queue as an indirect representation of composition weighted graph, so finding the best fitness of the composite service solution is to discover the optimised location of the particle.
-In PSO, the dimension of the particle is set up as the same as the number of relevant web services, and all the services index is mapped to the location in a particle, and we put services in a queue in ascending order, from which we decode a weighted graph using Algorithm \ref{graph_building}.
-We select and connect web services to the start Vetex from the service queue if the web service can satisfy the given $T_{input}$.
-Meanwhile, an Output Set is initialised and kept being updated using outputs from the new-added web services in the graph, later on, more services are connected if services' inputs could be satisfied by any output in the Output Set.
-At last, The end vetex is connected if the updated Output Set contains the $T_{output}$.
-In addition, dangle service nodes and edges should be removed.
+In the first algorithm, the idea is to translate the particle location into a service queue as an indirect representation of composition weighted graph, so finding the best fitness of the composite weighted graph is to discover the optimised location of the particle in the search space.
+In PSO, the dimension of the particle is set up as the same number as relevant web services, and the index of services is mapped to the location vectors in a particle, and we put services in a queue in ascending order, from which we decode a weighted graph using Algorithm \ref{graph_building}.
+We select and connect  service vertex to the start vertex from the service queue if the web service can satisfy the output of start vertex.
+Meanwhile, an Output Set is initialised and kept being updated using outputs from the new-added service vertex in the weighted graph, later on, more services vertex are connected with edges if services' inputs could be satisfied by any output in the Output Set.
+At last, The end vertex is connected if the updated Output Set contains all end inputs.
+In addition, dangling service vertex and edges should be removed.
 
@@
 In this section, a quantitative evaluation approach is adopted in our experiment design.
-The objectives of the evaluation are to measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach, and to explore the impacts of the semantic matchmaking that contributes to overall composition quality, and to compare solutions generated by QoS-ware approach with our method.
+The objectives of the evaluation are $(1)$ to measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach, $(2)$ to explore the impacts of the semantic matchmaking that contributes to overall composition quality, and $(3)$ to compare solutions generated by QoS-ware approach with our method.
 
-We utilise benchmark dataset web service challenge 2009 (WSC09) \cite{kona2009wsc} to perform a standard evaluation.
-WSC09 provides problems,  WSDL+MECE, taxonomy files in formats of xml, xml, and owl respectively, where five tasks consisted in with variable size in both services, and ontologies.
+We utilise benchmark dataset web service challenge 2009 (WSC09) \cite{kona2009wsc} to perform a evaluation.
+WSC09 provides problems where five tasks consisted in with variable size in both services, and ontologies.
 Therefore, it is a proper dataset for the scalability measures in our defined quality evaluation model.
@@
 The number of concepts, individuals in the ontology and services in each data set is shown in the second, third, fourth column respectively.
-Also, we extend all the datasets with QoS attributes from service providers to perform a comprehensive quality evaluation.
+Also, we extend all the datasets with QoS attributes from service providers to enable our evaluation.
 \begin{table}[]
@@
 We run the experiment under computing grid comprising of almost 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine.
-Experimentation was done using the approach explained in Section \ref{qswsc_approach}, and evaluated in the comprehensive quality model introduced in Subsection \ref{qualityModel}.
-The parameters were chosen based on general settings from \cite{shi2001particle} for our PSO-based approach, 30 particles evolved in 100 generations in the searching space, in which problem dimension's size equals to the relevant service size shown in graph.
-we run 30 times independently for each dataset.
-In addition, weights setting are flexibly defined by users' preferences.
-As part of their requirement, we configure weights of fitness function to properly balance functional side and nonfunctional side.
+Experimentation is done using the approach explained in Section \ref{qswsc_approach}, and evaluated in the comprehensive quality model introduced in Subsection \ref{qualityModel}.
+The parameters were chosen based on general settings from \cite{shi2001particle} for our PSO-based approach, 30 particles evolved in 100 generations in the searching space, in which problem dimension's size equals to the number of relevant services in service repository.
+We run 30 times independently for each dataset.
+In addition, weight settings are flexibly defined by users' preferences.
+As part of their requirement, we configure weight of fitness function to properly balance functional side and nonfunctional side.
 Therefore, $w_{1}$ and $w_{2}$ are equals to 0.1 and 0.4,  and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly.
@@
 \section{Results and Analysis}\label{results_analysis}
-\subsection{Convergence Test}\label{convergenceTest}
-
-\begin{figure}[h]
-\centerline{
-\fbox{
-\includegraphics[width=12cm]{convergency.pdf}}}
- \caption{Average Fitness, Average MatchType Quality, Average Similarity quality and Average QoS per generation with comprehensive quality optimum}
- \label{exp_fitnessvalue}
-\end{figure}
-
-To analysis the effectiveness of our approach, we explore the convergency rate of the proposed method in this section to investigate the convergency of five tasks in WSC09.
-To further study an overall effectiveness of evaluation model and impacts of all involved components in the fitness function.
-We analysis all the performances of these components in the whole evolutionary process in Figure \ref{exp_fitnessvalue}, in which the five tasks' experiment results are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average QoS for generation 0-99 with optimum.
-
-Firstly, the average fitness value with optimum is calculated by the average value of best fitness found in each generation over 30 independent runs.
-The value plotted in the first column group ranges from 0 to 1 in figure \ref{exp_fitnessvalue}, and it is considered to be more optimised if its value is closer to value 1.
-We can see that there is a significant increase in the fitness value (avg) with optimum between generation 0 and generation 15-25, the remained generation continues to produce a steady but moderate improvement in the fitness value and eventually reach a plateau with no further changes.
-The same behaviour is observed over the rest tasks.
-Also, there is a fast convergence of the fitness value that be observed.
-That is simply because of many repetitive solutions in the indirect web service composition representations in the search space.
-
-We also investigate the variation of two factors consisted in the functional quality part --- average matchType quality with optimum and average similarity quality with optimum from generation 0 to 99 in second and third column groups of Figure \ref{exp_fitnessvalue}.
-In these groups,  both the average matchType quality with optimum and average similarity quality with optimum are the mean value corresponding to the best fitness value found in each generation over 30 independent runs.
-The dominant tendency of the marked value representing a similar characteristic compared to the average fitness value group trend in five tasks.
-However, there are some slight fluctuations over the generations, it due to the single objective fitness function that prevents selecting the worst component quality without granting for the best.
-
-Lastly, It is interesting to look at the average QoS per generation for the 30 independent runs when the behaviour of functional quality moves upward.
-Here average QoS with optimum is also the value corresponding to the fitness value with optimum in each generation, and we display the results in the fourth column group in Figure \ref{exp_fitnessvalue}.
-It is obvious that the overall trend of QoS moves upward to a high constant level in five independent tasks.
-Additionally, we don't see too much trade-off from the QoS.
-
 \subsection{Comparision Test}\label{comparisionTest}
@@
 
+\subsection{Convergence Test}\label{convergenceTest}
+
+\begin{figure}[h]
+\centerline{
+\fbox{
+\includegraphics[width=12cm]{convergency.pdf}}}
+ \caption{Average Fitness, Average MatchType Quality, Average Similarity quality and Average QoS per generation with comprehensive quality optimum}
+ \label{exp_fitnessvalue}
+\end{figure}
+
+To analysis the effectiveness of our approach, we explore the convergency rate of the proposed method in this section to investigate the convergency of five tasks in WSC09.
+To further study an overall effectiveness of evaluation model and impacts of all involved components in the fitness function.
+We analysis all the performances of these components in the whole evolutionary process in Figure \ref{exp_fitnessvalue}, in which the five tasks' experiment results are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average QoS for generation 0-99 with optimum.
+
+Firstly, the average fitness value with optimum is calculated by the average value of best fitness found in each generation over 30 independent runs.
+The value plotted in the first column group ranges from 0 to 1 in figure \ref{exp_fitnessvalue}, and it is considered to be more optimised if its value is closer to value 1.
+We can see that there is a significant increase in the fitness value (avg) with optimum between generation 0 and generation 15-25, the remained generation continues to produce a steady but moderate improvement in the fitness value and eventually reach a plateau with no further changes.
+The same behaviour is observed over the rest tasks.
+Also, there is a fast convergence of the fitness value that be observed.
+That is simply because of many repetitive solutions in the indirect web service composition representations in the search space.
+
+We also investigate the variation of two factors consisted in the functional quality part --- average matchType quality with optimum and average similarity quality with optimum from generation 0 to 99 in second and third column groups of Figure \ref{exp_fitnessvalue}.
+In these groups,  both the average matchType quality with optimum and average similarity quality with optimum are the mean value corresponding to the best fitness value found in each generation over 30 independent runs.
+The dominant tendency of the marked value representing a similar characteristic compared to the average fitness value group trend in five tasks.
+However, there are some slight fluctuations over the generations, it due to the single objective fitness function that prevents selecting the worst component quality without granting for the best.
+
+Lastly, It is interesting to look at the average QoS per generation for the 30 independent runs when the behaviour of functional quality moves upward.
+Here average QoS with optimum is also the value corresponding to the fitness value with optimum in each generation, and we display the results in the fourth column group in Figure \ref{exp_fitnessvalue}.
+It is obvious that the overall trend of QoS moves upward to a high constant level in five independent tasks.
+Additionally, we don't see too much trade-off from the QoS.
+
 \section{Conclusion}\label{conclusion}

### 2016-11-02 paper.tex
update

@@
  \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
- \SetKwFunction{connectNode}{connectNode}\SetKwFunction{findCands}{findCands}\SetKwFunction{removeDangling}{removeDangling}
- \LinesNumbered
- \SetNlSty{}{}{:}
+ \let\oldnl\nl% Store \nl in \oldnl
+\newcommand{\nonl}{\renewcommand{\nl}{\let\nl\oldnl}}
  \Input{$I$, $O$, $queue$}
  \Output{composition weighted graph $WG$}
- Create $start$ vertex with outputs $I$ and $end$ vertex with inputs $O$\;
- Create graph $WG$ containing the $start$ vertex\;
- Create available outputs set containing $start$ outputs\;
+ \textbf{1.} Create $start$ vertex with outputs $O$ and $end$ vertex with inputs $I$.\\
+ \textbf{2.} Create graph $WG$ containing the $start$ vertex.\\
+ \textbf{3.} Create available outputs set containing $start$ outputs.\\
  \While{available outputs do not satisfy $end$ inputs}{
- Get next candidate from queue\;
+ \textbf{4.} Get next candidate from queue.\\
  \If{candidate inputs are satisfied by available outputs}{
- \textcolor{blue}{Create edge assigned with weight\;}
- \textcolor{blue}{Connect vertex to graph with the edge\;}
- Remove it from queue and go back to the queue's beginning\;
+ \textcolor{blue}{\textbf{5.} Create edge assigned with weight.\\}
+ \textcolor{blue}{\textbf{6.} Connect vertex to graph with the edge.\\}
+ \textbf{7.} Remove it from queue and go back to the queue's beginning.\\
  }}
- Connect end vetex\;
- Remove dangling vertices from graph $WG$\;
- Remove dangling edges from graph $WG$
- \KwRet $WG$\;
+ \textbf{8.} Connect end vertex.\\
+ \textbf{9.} Remove dangling vertices from graph $WG$.\\
+ \textcolor{blue}{\textbf{10.} Remove dangling edges from graph $WG$.\\}
+ \KwRet $WG$.\\
  \caption{Create a composition weighted graph from a queue}	

### 2016-11-03 paper.tex
update
,….

@@
 
-\section{QoS-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
+\section{Comprehensive quality-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
 \begin{figure}[h]
@@
 
-\subsection{Semantic matchmaking} \label{semantic_matchmaking}
+\subsection{Semantic Matchmaking} \label{semantic_matchmaking}
 To perform semantic matchmaking, we transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match in \ref{semantic Web service Discovery}.
@@
 
-\subsection{Comprehensive quality model and aggregation matrix}\label{qualityModel}
+\subsection{Comprehensive Quality Model and Aggregation Matrix}\label{qualityModel}
 In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition.
@@
 \end{table}
+
+\subsection{Composition Weighted Graph}
+We defined our semantic web service composition solution as $WG = (V, E)Graph$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of edges $E = {e_{1}, e_{2},...
+e_{n}}$.
+Each $e$ is associated with $q(e_{sm})$ as weight value that mapped to a pair of quality values $q(e_{mt})$ and $q(e_{s})$ on the edge level.
+where $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$.
+Here we provide an example of the web service composition, which can be described in the Figure \ref{wscs}.
+The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections.
+Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},...
+e_{n}}$, and further aggregated in $Q_{mt}$ and $Q_{s}$ respectively on the construct level.
+In addition, $Q_{QoS}$ is calculated by all the non-functional attributes of $V$ using aggregation rules defined previously.
+
+\begin{figure}[h]
+\centerline{
+\fbox{
+\includegraphics[width=8cm]{weigtedGraphExample.pdf}}}
+ \caption{Composition weighted graph solution}
+ \label{wscs}
+\end{figure}
 
@@
 \subsection{Comparision Test}\label{comparisionTest}
-\begin{figure}[h]
-\centerline{
-\fbox{
-\includegraphics[width=8cm]{wscs.pdf}}}
- \caption{Example composition solutions for problem1 WSC'09.}
- \label{wscs}
-\end{figure}
-We defined our optimised web service composition as $WSC = (V, E)Graph$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of service connections as edges associated with two values of matchType quality and semantic similarity quality: $E = {e_{1}, e_{2},...
-e_{n}}$ where $e1$ is define as $(S_{1},S_{2})={q_{mt}, q_{s}}$.
-Here we provide an example of the web service composition solution to task 1, which can be described in the Figure \ref{wscs}.
-The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections.
-Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},...
-e_{n}}$, and further aggregated in $Q_{mt}$ and $Q_{s}$ respectively.
-In addition, $Q_{QoS}$ is calculated by all the non-functional attributes of $V$ using aggregation rules defined before.
-The demonstration of the solution is to make better comparison of results using the same solution model from different approaches .
+
+In this section, we analyse the composition solution generated by using our approach.
+In particularly, we show that our proposed approach can produce solutions that results better matchmaking , which meets user's goal better.
 

### 2016-11-03 paper.tex
UP

@@
 \section{Results and Analysis}\label{results_analysis}
-\subsection{Comparision Test}\label{comparisionTest}
+\subsection{Comparison Test}\label{comparisonTest}
 
@@
 In particularly, we show that our proposed approach can produce solutions that results better matchmaking , which meets user's goal better.
-
 Now we look at $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ defined in the solution model using black-box testing for the comparison, where the comprehensive quality awareness approach and QoS awareness approach \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} are compared to reveal how good our evaluation mode is in a decision table shown in Table \ref{decisionTable}.
@@
 
+To visually compare the results generated from two evaluation approaches, we demonstrate the differences of composition weighted graphs under two different methods.
+The Figure \ref{comparison} shows two composition weighted graphs, which are the solutions to Task 3 for comprehensive quality-aware and QoS-aware web service composition respectively.
+The two weighted graphs have exactly the same workflow structure, in which the different service vertex and edges are denoted in red for making a comparison.
+
+\begin{figure}[h]
+\centerline{
+\fbox{
+\includegraphics[width=8cm]{comparision.pdf}}}
+ \caption{Example Comparison of solutions to Task 3 under different approaches.}
+ \label{comparison}
+\end{figure}
+
 \subsection{Convergence Test}\label{convergenceTest}

### 2016-11-03 paper.tex
update

@@
 
-In this section, we analyse the composition solution generated by using our approach.
+In this section, we analyse the composition solution generated by using our approach comparing with QoS-aware approach.
 In particularly, we show that our proposed approach can produce solutions that results better matchmaking , which meets user's goal better.
-Now we look at $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ defined in the solution model using black-box testing for the comparison, where the comprehensive quality awareness approach and QoS awareness approach \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} are compared to reveal how good our evaluation mode is in a decision table shown in Table \ref{decisionTable}.
-Solutions to five tasks are compared using two evaluation models in WSC09.
+In particularly, we look at mean value of $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ in the comprehensive quality awareness approach and QoS awareness approach are compared to reveal how good our evaluation mode in Table \ref{decisionTable}.
 In each task, we compare $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$, and $Q_{QoS}$ is normalised to make it comparable to another method in our comprehensive awareness approach
@@
 \centering
-\caption{Quality of two evaluation model in a decision table}
+\caption{Mean Quality for comprehensive quality-aware methods and QoS-aware appraoch}
 \label{decisionTable}
@@
 \hline
-\multicolumn{2}{|c|}{\multirow{2}{*}{}}                              &Approach 1           &Approach 2                           \\ \cline{3-4} 
 \multicolumn{2}{|c|}{}                                               & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
-\multirow{3}{*}{Condition}            & dataset1             & $\surd$              & $\surd$                            \\ \cline{2-4} 
-                                      & dataset2             & $\surd$              & $\surd$                            \\ \cline{2-4} 
-                                      & dataset3             & $\surd$              & $\surd$                            \\ \hline
-\multirow{3}{*}{\shortstack{Task1\\Optimised solution}}  &$Q_{mt}$   & .232635              & .232635                          \\ \cline{2-4} 
+\multirow{3}{*}{Task1}  &$Q_{mt}$   & .232635              & .232635                          \\ \cline{2-4} 
                                       &$Q_{s}$                       & .903572              & .903572                          \\ \cline{2-4}
                                       &$Q_{QoS}$                     & .578577              & .578577                          \\ \hline
-\multirow{3}{*}{\shortstack{Task2\\Optimised solution}}  &$Q_{mt}$   & .001828              & .000851$\downarrow$               \\ \cline{2-4} 
+\multirow{3}{*}{Task2}  &$Q_{mt}$   & .001828              & .000851$\downarrow$               \\ \cline{2-4} 
                                       &$Q_{s}$                       & .917172              & .938840$\uparrow$                 \\ \cline{2-4}
                                       &$Q_{QoS}$                     & .480251              & .473002$\downarrow$               \\ \hline
-\multirow{3}{*}{\shortstack{Task3\\Optimised solution}}  &$Q_{mt}$   & .191188              & .247836$\uparrow$                  \\ \cline{2-4} 
+\multirow{3}{*}{Task3}  &$Q_{mt}$   & .191188              & .247836$\uparrow$                  \\ \cline{2-4} 
                                       &$Q_{s}$                       & .951509              & .973723$\uparrow$                  \\ \cline{2-4}
                                       &$Q_{QoS}$                     & .493927              & .491538$\downarrow$                 \\ \hline
-\multirow{3}{*}{\shortstack{Task4\\Optimised solution}}  &$Q_{mt}$   & .919678              & .943406$\uparrow$                  \\ \cline{2-4} 
+\multirow{3}{*}{Task4}  &$Q_{mt}$   & .919678              & .943406$\uparrow$                  \\ \cline{2-4} 
                                       &$Q_{s}$                       & .000000              & .000009$\uparrow$                  \\ \cline{2-4}
                                       &$Q_{QoS}$                     & .480818              & .472485$\downarrow$                 \\ \hline
-\multirow{3}{*}{\shortstack{Task5\\Optimised solution}}  &$Q_{mt}$   & .000094              & .000109$\uparrow$                  \\ \cline{2-4} 
+\multirow{3}{*}{Task5}  &$Q_{mt}$   & .000094              & .000109$\uparrow$                  \\ \cline{2-4} 
                                       &$Q_{s}$                       & .927476              & .930975$\uparrow$                  \\ \cline{2-4}
@@
 
+% Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table}[]
+\centering
+\caption{My caption}
+\label{my-label}
+\begin{tabular}{|l|l|l|l|l|}
+\hline
+\multicolumn{2}{|l|}{} & Comprehensive-aware & QoS-aware &  $\Delta Q$\\ \hline
+\multirow{2}{*}{e1} &$q(e_{mt})$        &        1   &  1 &0\\ \cline{2-5} 
+                    & $q(e_{s})$                    &     1      & 1& 0\\ \hline
+\multirow{2}{*}{e2} & $q(e_{mt})$                     &    0.9167       & 0.75 & \\ \cline{2-5} 
+                    &   $q(e_{s})$                    &   0.9630        & 0.9232 &\\ \hline
+\multirow{2}{*}{e3} &  $q(e_{mt})$                   &    0.8333       & 0.75 &\\ \cline{2-5} 
+                    &   $q(e_{s})$                    &    0.9608       &  0.8230 &\\ \hline
+\multirow{2}{*}{e4} & $q(e_{mt})$                      &    0.875       & 0.75 &\\ \cline{2-5} 
+                    &  $q(e_{s})$                     &    0.9167       & 0.9090 &\\ \hline
+\multicolumn{2}{|l|}{SM} &                     &           &  \\ \hline
+\multicolumn{2}{|l|}{QoS} &        0.4915             &  0.4949         &  \\ \hline
+\end{tabular}
+\end{table}
+
 \subsection{Convergence Test}\label{convergenceTest}
@@
 The value plotted in the first column group ranges from 0 to 1 in figure \ref{exp_fitnessvalue}, and it is considered to be more optimised if its value is closer to value 1.
-We can see that there is a significant increase in the fitness value (avg) with optimum between generation 0 and generation 15-25, the remained generation continues to produce a steady but moderate improvement in the fitness value and eventually reach a plateau with no further changes.
+We can see that there is a significant increase in the fitness values with optimum between generation 0 and generation 15-25, the remained generation continues to produce a steady but moderate improvement in the fitness value and eventually reach a plateau with no further changes.
 The same behaviour is observed over the rest tasks.
@@
 The dominant tendency of the marked value representing a similar characteristic compared to the average fitness value group trend in five tasks.
-However, there are some slight fluctuations over the generations, it due to the single objective fitness function that prevents selecting the worst component quality without granting for the best.
+However, there are some slight fluctuations over the generations, due to the single objective fitness function that prevents selecting the worst component quality without granting for the best.
 
-Lastly, It is interesting to look at the average QoS per generation for the 30 independent runs when the behaviour of functional quality moves upward.
+Lastly, it is interesting to look at the average QoS per generation for the 30 independent runs when the behaviour of functional quality moves upward.
 Here average QoS with optimum is also the value corresponding to the fitness value with optimum in each generation, and we display the results in the fourth column group in Figure \ref{exp_fitnessvalue}.
@@
 \section{Conclusion}\label{conclusion}
-This work introduced a more applicable and simpler evaluation model for comprehensive quality awareness semantic automated web service composition that relies on semantic matchmaking quality extension to QoS-aware consideration.
-The key idea of these evaluation model is to consider the quality of semantic matchmaking corresponding to different matchmaking types.
-Also, the effectiveness of our model is also proved to obtain better functional quality with a reasonable trade-off in QoS.
-Future works in this area should investigate more reasonable matching types, explore the comprehensive quality in multi-objective approach, and improve efficiency in the functional quality calculation.
+This work introduced a evaluation model for QoS-aware automated semantic automated web service composition that is based on a semantic matchmaking quality extends existing QoS.
+The results shows that our comprehensive quality model is proved to obtain better functional quality with a reasonable trade-off in QoS.
+Future works in this area could explore the comprehensive quality with multi-objectives to maximising quality of matchmaking and to optimise QoS, and improve efficiency in calculating semantic quality.
 \bibliographystyle{splncs03}

### 2016-11-04 paper.tex
update

@@
 The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory.
-This construct is shown in Figure \ref{sequence}.
+This construct is shown in Fig.
+\ref{sequence}.
 \subsubsection{Parallel construct}
@@
 The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is delimited by the maximum time consumed path in the composite flow of the solution.
-This construct is presented in Figure \ref{parallel}.
+This construct is presented in Fig.
+\ref{parallel}.
 
@@
 where $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$.
-Here we provide an example of the web service composition, which can be described in the Figure \ref{wscs}.
+Here we provide an example of the web service composition, which can be described in the Fig.
+\ref{wscs}.
 The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections.
@@
 
-To visually compare the results generated from two evaluation approaches, we demonstrate the differences of composition weighted graphs under two different methods.
-The Figure \ref{comparison} shows two composition weighted graphs, which are the solutions to Task 3 for comprehensive quality-aware and QoS-aware web service composition respectively.
-The two weighted graphs have exactly the same workflow structure, in which the different service vertex and edges are denoted in red for making a comparison.
+To visually compare the results generated from two evaluation approaches, we demonstrate the differences in the solutions of two composition weighted graphs under two different methods.
+The Fig.
+\ref{comparison} shows two composition weighted graphs, which are the solutions to Task 3 for(1) QoS-aware approach and $(2)$ Comprehensive quality-aware method and respectively.
+It can be observed that two composition weighted graphs have exactly the same workflow structure, in which the same service vertex and edges are different denoted in red.
+Meanwhile, we make a comparison of those different edges weights representing the quality of semantic matchmaking in Table \ref{comparisontable},as well as QoS.
+We can see edges obtain better semantic matchmaking quality with a reasonable trade-off in QoS
 
@@
 \centering
-\caption{My caption}
-\label{my-label}
+\caption{Comparison of Composition Weighted Graphs}
+\label{comparisontable}
 \begin{tabular}{|l|l|l|l|l|}
 \hline
-\multicolumn{2}{|l|}{} & Comprehensive-aware & QoS-aware &  $\Delta Q$\\ \hline
-\multirow{2}{*}{e1} &$q(e_{mt})$        &        1   &  1 &0\\ \cline{2-5} 
-                    & $q(e_{s})$                    &     1      & 1& 0\\ \hline
-\multirow{2}{*}{e2} & $q(e_{mt})$                     &    0.9167       & 0.75 & \\ \cline{2-5} 
-                    &   $q(e_{s})$                    &   0.9630        & 0.9232 &\\ \hline
-\multirow{2}{*}{e3} &  $q(e_{mt})$                   &    0.8333       & 0.75 &\\ \cline{2-5} 
-                    &   $q(e_{s})$                    &    0.9608       &  0.8230 &\\ \hline
-\multirow{2}{*}{e4} & $q(e_{mt})$                      &    0.875       & 0.75 &\\ \cline{2-5} 
-                    &  $q(e_{s})$                     &    0.9167       & 0.9090 &\\ \hline
-\multicolumn{2}{|l|}{SM} &                     &           &  \\ \hline
-\multicolumn{2}{|l|}{QoS} &        0.4915             &  0.4949         &  \\ \hline
+\multicolumn{2}{|l|}{Quality criteria} & Weighted Graph $(1)$ & Weighted Graph $(2)$ &  $\Delta Q$\\ \hline
+\multirow{2}{*}{e1} &$q(e_{mt})$   &1        &1                       &0     \\ \cline{2-5} 
+                    & $q(e_{s})$   &1        &1                       &0\\ \hline
+\multirow{2}{*}{e2} & $q(e_{mt})$  &0.75     &0.9167                  &+0.1667 \\ \cline{2-5} 
+                    & $q(e_{s})$   &0.9232   &0.9630                &+0.0398\\ \hline
+\multirow{2}{*}{e3} &  $q(e_{mt})$ &0.75     &0.8333                 &+0.08333\\ \cline{2-5} 
+                    &   $q(e_{s})$ &0.8230   &0.9608                 &+0.1378\\ \hline
+\multirow{2}{*}{e4} & $q(e_{mt})$  &0.75     &0.875                  &+0.125\\ \cline{2-5} 
+                    &  $q(e_{s})$  &0.9090   &0.9167                 &+0.0077\\ \hline
+\multicolumn{2}{|l|}{QoS} &0.4949            &0.4915                 &-0.0034  \\ \hline
 \end{tabular}
@@
 
-To analysis the effectiveness of our approach, we explore the convergency rate of the proposed method in this section to investigate the convergency of five tasks in WSC09.
-To further study an overall effectiveness of evaluation model and impacts of all involved components in the fitness function.
-We analysis all the performances of these components in the whole evolutionary process in Figure \ref{exp_fitnessvalue}, in which the five tasks' experiment results are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average QoS for generation 0-99 with optimum.
+To analyse the effectiveness of our approach, we will study the convergence rate of the proposed method in this section to understand the convergence rate of five tasks in WSC09.
+To further study the overall effectiveness of evaluation model and explore impacts of all involved components in the fitness function.
+We analysis all the performances of these components in the whole evolutionary process in Fig.
+\ref{exp_fitnessvalue}, in which the five tasks' experiment results are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average QoS for generation 0-99 with optimum.
 
 Firstly, the average fitness value with optimum is calculated by the average value of best fitness found in each generation over 30 independent runs.
-The value plotted in the first column group ranges from 0 to 1 in figure \ref{exp_fitnessvalue}, and it is considered to be more optimised if its value is closer to value 1.
-We can see that there is a significant increase in the fitness values with optimum between generation 0 and generation 15-25, the remained generation continues to produce a steady but moderate improvement in the fitness value and eventually reach a plateau with no further changes.
+The value plotted in the first column group ranges from 0 to 1 in Fig.
+\ref{exp_fitnessvalue}, and it is considered to be more optimised if its value is closer to value 1.
+We can see that there is a significant increase in the fitness values with optimum between generation 0 and generation 15-25, the remaining generation continues to produce a steady but moderate improvement in the fitness value and eventually reach a plateau with no further changes.
 The same behaviour is observed over the rest tasks.
-Also, there is a fast convergence of the fitness value that be observed.
-That is simply because of many repetitive solutions in the indirect web service composition representations in the search space.
+We also witnessed a fast convergence rate of the fitness value.
 
-We also investigate the variation of two factors consisted in the functional quality part --- average matchType quality with optimum and average similarity quality with optimum from generation 0 to 99 in second and third column groups of Figure \ref{exp_fitnessvalue}.
+We also investigate the variation of quality of semantic matchmaking where average matchType quality with optimum and average similarity quality with optimum are studied from generation 0 to 99 in second and third column groups of Fig.
+\ref{exp_fitnessvalue}.
 In these groups,  both the average matchType quality with optimum and average similarity quality with optimum are the mean value corresponding to the best fitness value found in each generation over 30 independent runs.
 The dominant tendency of the marked value representing a similar characteristic compared to the average fitness value group trend in five tasks.
-However, there are some slight fluctuations over the generations, due to the single objective fitness function that prevents selecting the worst component quality without granting for the best.
+However, there are some slight fluctuations over the generations.
 
-Lastly, it is interesting to look at the average QoS per generation for the 30 independent runs when the behaviour of functional quality moves upward.
-Here average QoS with optimum is also the value corresponding to the fitness value with optimum in each generation, and we display the results in the fourth column group in Figure \ref{exp_fitnessvalue}.
+Lastly, it is interesting to look at the average QoS per generation for the 30 independent runs when the functional quality heads up.
+Here average QoS with optimum is also the value corresponding to the fitness value with optimum in each generation, and we display the results in the fourth column group in Fig.
+\ref{exp_fitnessvalue}.
 It is obvious that the overall trend of QoS moves upward to a high constant level in five independent tasks.

### 2016-11-06 paper.tex
update

@@
 In this section, we analyse the composition solution generated by using our approach comparing with QoS-aware approach.
-In particularly, we show that our proposed approach can produce solutions that results better matchmaking , which meets user's goal better.
-In particularly, we look at mean value of $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ in the comprehensive quality awareness approach and QoS awareness approach are compared to reveal how good our evaluation mode in Table \ref{decisionTable}.
-In each task, we compare $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$, and $Q_{QoS}$ is normalised to make it comparable to another method in our comprehensive awareness approach
+In particularly, we show that our proposed approach can produce solutions that results better matchmaking, which meets user's goal better.
+
+First, we look at mean value of $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ at optimum at the 100th generation for two approaches, shown in Table \ref{decisionTable}, where QoS-aware approach record $Q_{mt}$, $Q_{s}$ while utilise fitness function $Fitness = w_1A + w_2R + w_3(1 - T) + w_4(1 - C)$ when $\sum_{i=1}^{4} w_i = 1$ without considering $MT$ and $S$, and its $Q_(QoS)$ is normalised from 0 to 0.5 to make it comparable to $Q_{QoS}$ in our approach.
+We observe an interesting pattern from the Table \ref{decisionTable} using statistic analysis: mean value of $Q_{mt}$ and $Q_{s}$ at optimum by our approach is consistently higher than those of QoS-aware approach in Task 1, 3, 4, and 5 with an exception in Task 2 while the combination of mean $Q_{mt}$ and $Q_{s}$ at optimum in Task 2 is still considered to be higher in our approach with 0.1 and 0.4 weights respectively.
+However, the mean value $Q_{QoS}$ at optimum at 100th generation of QoS-aware approach can obtain a slightly higher value than that of our approach.
+In conclusion, we can perceive that our evaluation could find out better functional quality with a reasonable trade off in QoS.
 
@@
 \centering
-\caption{Mean Quality for comprehensive quality-aware methods and QoS-aware appraoch}
+\caption{Mean Quality for comprehensive quality-aware methods and QoS-aware approach}
 \label{decisionTable}
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{|l|l|l|l|}
 \hline
-\multicolumn{2}{|c|}{}                                               & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
-\multirow{3}{*}{Task1}  &$Q_{mt}$   & .232635              & .232635                          \\ \cline{2-4} 
-                                      &$Q_{s}$                       & .903572              & .903572                          \\ \cline{2-4}
-                                      &$Q_{QoS}$                     & .578577              & .578577                          \\ \hline
-\multirow{3}{*}{Task2}  &$Q_{mt}$   & .001828              & .000851$\downarrow$               \\ \cline{2-4} 
-                                      &$Q_{s}$                       & .917172              & .938840$\uparrow$                 \\ \cline{2-4}
-                                      &$Q_{QoS}$                     & .480251              & .473002$\downarrow$               \\ \hline
-\multirow{3}{*}{Task3}  &$Q_{mt}$   & .191188              & .247836$\uparrow$                  \\ \cline{2-4} 
-                                      &$Q_{s}$                       & .951509              & .973723$\uparrow$                  \\ \cline{2-4}
-                                      &$Q_{QoS}$                     & .493927              & .491538$\downarrow$                 \\ \hline
-\multirow{3}{*}{Task4}  &$Q_{mt}$   & .919678              & .943406$\uparrow$                  \\ \cline{2-4} 
-                                      &$Q_{s}$                       & .000000              & .000009$\uparrow$                  \\ \cline{2-4}
-                                      &$Q_{QoS}$                     & .480818              & .472485$\downarrow$                 \\ \hline
-\multirow{3}{*}{Task5}  &$Q_{mt}$   & .000094              & .000109$\uparrow$                  \\ \cline{2-4} 
-                                      &$Q_{s}$                       & .927476              & .930975$\uparrow$                  \\ \cline{2-4}
-                                      &$Q_{QoS}$                     & .476236              & .475128$\downarrow$                 \\ \hline                                                   
+\multicolumn{2}{|c|}{WSC09}              & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
+\multirow{3}{*}{Task1}  &$Q_{mt}$   &0.189787 $\pm$ 0.039278686  &0.220594 $\pm$ 0.009318 $\uparrow$ \\ \cline{2-4} 
+                        &$Q_{s}$    &0.884962 $\pm$ 0.014140   &0.893713 $\pm$ 0.007769  $\uparrow$ \\ \cline{2-4}
+                        &$Q_{QoS}$  &0.278730 $\pm$ 0.007786     &0.279548 $\pm$ 0.007627                          \\ \hline
+\multirow{3}{*}{Task2}  &$Q_{mt}$   &0.001795 $\pm$ 0.000719 $\uparrow$    &0.001135 $\pm$ 0.000633  \\ \cline{2-4} 
+                        &$Q_{s}$    &0.906971 $\pm$ 0.005855     &0.927965 $\pm$ 0.007306 $\uparrow$   \\ \cline{2-4}
+                        &$Q_{QoS}$  &0.239979 $\pm$ 0.000578 $\uparrow$     &0.237845 $\pm$ 0.001439 \\ \hline
+\multirow{3}{*}{Task3}  &$Q_{mt}$   &0.158526 $\pm$ 0.014028               &  0.245830 $\pm$ 0.007761 $\uparrow$   \\ \cline{2-4} 
+                        &$Q_{s}$    & 0.949109 $\pm$ 0.002331           &   0.972765 $\pm$ 0.002980 $\uparrow$           \\ \cline{2-4}
+                        &$Q_{QoS}$  &  0.247002 $\pm$ 0.000661 $\uparrow$             &  0.245631 $\pm$ 0.000431            \\ \hline
+\multirow{3}{*}{Task4}  &$Q_{mt}$   &              &                 \\ \cline{2-4} 
+                        &$Q_{s}$    &               &                   \\ \cline{2-4}
+                        &$Q_{QoS}$  &               &                     \\ \hline
+\multirow{3}{*}{Task5}  &$Q_{mt}$   &  0.000042 $\pm$ 0.000030     &  0.000078 $\pm$ 0.000031 $\uparrow$           \\ \cline{2-4} 
+                        &$Q_{s}$    &  0.915933 $\pm$ 0.012888      &  0.928189 $\pm$ 0.002486 $\uparrow$                 \\ \cline{2-4}
+                        &$Q_{QoS}$  & 0.238189 $\pm$ 0.000240$\uparrow$      &  0.237232 $\pm$  0.000391  \\ \hline                                                   
 \end{tabular}
 \end{table}
-In Table \ref{decisionTable}, Task 1 represents the same solution using different methods where the values of $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$ are all the same.
-It is due to the size of dataset 01 is very small in both available services and ontologies.
-However, As the size of dataset increase, we can recognise a trade-offs in task 2 using our evaluation approach, where a 0.021668 increase in similarity quality and a 0.00098 decrease in matchType quality with weights 0.4 and 0.1 respectively so that solution to task 2 is still considered to be an improvement in the functional quality part while a decrease value of 0.007249 in QoS.
-In task 3, the benefit of functional part quality is clearer with an increase value of 0.056648 and 0.078862 in  similarity quality and matchType quality respectively while a slight decrease in QoS.
-later on, the rest tasks perform the same behaviour in $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$ as task 3.
-In conclusion, we can perceive that our evaluation could find out better functional quality with a reasonable trade off in QoS.
 
-To visually compare the results generated from two evaluation approaches, we demonstrate the differences in the solutions of two composition weighted graphs under two different methods.
+Second, to compare the results generated from two evaluation approaches, we demonstrate an example solution that shows the differences in two composition weighted graphs representations under two different methods.
 The Fig.
-\ref{comparison} shows two composition weighted graphs, which are the solutions to Task 3 for(1) QoS-aware approach and $(2)$ Comprehensive quality-aware method and respectively.
-It can be observed that two composition weighted graphs have exactly the same workflow structure, in which the same service vertex and edges are different denoted in red.
-Meanwhile, we make a comparison of those different edges weights representing the quality of semantic matchmaking in Table \ref{comparisontable},as well as QoS.
-We can see edges obtain better semantic matchmaking quality with a reasonable trade-off in QoS
+\ref{comparison} shows two composition weighted graphs as the solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method.
+Two approaches generate exactly the same service workflow structure while some service vertex and edges denoted in red are different part.
+Therefore, we make a comparison of the quality among these different edges ($e_1$ to $e4$) associated service vertex in terms of quality of semantic matchmaking and QoS attributes.
+We also look at $\Delta Q$ which reveals the amount of variation between two methods, where the positive values means the benefits gained under our approach while the negative values means the trade-off.
+There is an consistency in our methods that edges are with higher values and service vertex with slightly lower QoS.
+To demonstrate the benefits of the positive value, we shows our methods have better quality in semantic making in Fig.
+\ref{}.
 
@@
 \fbox{
-\includegraphics[width=8cm]{comparision.pdf}}}
+\includegraphics[width=6cm]{comparision.pdf}}}
+ \caption{Example Comparison of solutions to Task 3 under different approaches.}
+ \label{comparison}
+\end{figure}
+\vspace{0.3cm}
+\begin{figure}
+\centerline{
+\fbox{
+\includegraphics[width=4cm]{comparisontaxonomy.pdf}}}
  \caption{Example Comparison of solutions to Task 3 under different approaches.}
@@
 \hline
-\multicolumn{2}{|l|}{Quality criteria} & Weighted Graph $(1)$ & Weighted Graph $(2)$ &  $\Delta Q$\\ \hline
+\multicolumn{2}{|l|}{\shortstack{Quality \\ Criteria}} & WG $(1)$ & WG $(2)$ &  $\Delta Q$\\ \hline
 \multirow{2}{*}{e1} &$q(e_{mt})$   &1        &1                       &0     \\ \cline{2-5} 

### 2016-11-06 paper.tex
update

@@
 There is an consistency in our methods that edges are with higher values and service vertex with slightly lower QoS.
-To demonstrate the benefits of the positive value, we shows our methods have better quality in semantic making in Fig.
-\ref{}.
+To demonstrate the benefits of the positive value, we analyse the smallest value $e_4$ and demonstrate how the output and required input are different in in Fig.
+\ref{comparisontaxonomy}.
+$Ser1640238160$ and $Ser1947554374$ are selected service vertex with output concept-related parameters $Inst795998200$ and $Inst582785907$ respectively under two methods while $Inst658772240$ are the required input related to $Con2113572083$.
+It is obviously that our approach select the service providing parameters that are closer the users' requirement, which means our methods results in better semantic matchmaking quality.
 
@@
 \includegraphics[width=4cm]{comparisontaxonomy.pdf}}}
- \caption{Example Comparison of solutions to Task 3 under different approaches.}
+ \caption{Example Comparison of Edge 4 in Task 3 solution under two methods.}
  \label{comparison}
@@
 \caption{Comparison of Composition Weighted Graphs}
-\label{comparisontable}
+\label{comparisontaxonomy}
 \begin{tabular}{|l|l|l|l|l|}

### 2016-11-06 paper.tex
update

@@
  \item To propose a PSO-based service composition model that utilise the proposed quality model.
-In PSO, weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively represent the solutions of semantic web service composition as particles in the searching space, which are decoded from an optimised service queue with the consideration of comprehensive quality.
+In PSO, weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively represent the solutions of semantic web service composition in the searching space, which are decoded from an optimised service queue with the consideration of comprehensive quality.
 
@@
 Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, which is a taxonomy-based measurement for ontology matching.
-This formula \ref{equation1} is used to estimate the similarity between parameter-related output concept and parameter-related input concept for selecting web services.
-Therefore, given the quality match type and the similarity of two parameters-related concepts, the semantic matchmaking quality of matched parameters is defined by Formula \ref{equation2}, where the value of $q(p_ {matchType})$ is set up as the same as the quality of the semantic link in \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).
+This formula (\ref{equation1}) is used to estimate the similarity between parameter-related output concept and parameter-related input concept for selecting web services.
+Therefore, given the quality match type and the similarity of two parameters-related concepts, the semantic matchmaking quality of matched parameters is defined by Formula (\ref{equation2}), where the value of $q(p_ {matchType})$ is set up as the same as the quality of the semantic link in \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).
 
@@
 The comprehensive quality of our service composition representation refers to QoS of service vertices and Semantic matching quality of Edges in weighted graphs.
-Consequently, the comprehensive quality model is defined in Formula \ref{equation4}, which could be further broken down into Formula \ref{equation5}.
+Consequently, the comprehensive quality model is defined in Formula (\ref{equation4}), which could be further broken down into Formula (\ref{equation5}).
 \begin{equation}
@@
 \label{table1}
-\begin{tabular}{|c|c|c|c|l|}
+\begin{tabular}{c|c|c|c|c}
 \hline
-\multicolumn{3}{|c|}{Composition Construct}                                      & Sequence                             & Parallel \\ \hline
+\multicolumn{3}{c|}{Composition Construct}                                      & Sequence                             & Parallel \\ \hline
 \multirow{5}{*}{QualityFactors} & \multirow{2}{*}{Functional}    & $Q(e_ {mt})$  &$\prod_{n=1}^{m} q(e_ {mt})$          &  $\prod_{n=1}^{m} q(e_ {mt})$ \\ \cline{3-5}
@@
 \subsection{Fitness Calculation}
-The fitness value of a service composition solution is a weighted sum of all the quality components discussed previously shown in Formula \ref{equation6}, in which fitness value of 1 means the best comprehensive quality and 0 means the worst.
+The fitness value of a service composition solution is a weighted sum of all the quality components discussed previously shown in Formula (\ref{equation6}), in which fitness value of 1 means the best comprehensive quality and 0 means the worst.
 As the sum of all the components' weights ($w_1$ to $w_6$) equals to 1, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the fitness value falls within the range from 0 to 1.
-Also, the lowest T and C value represent the best component quality so that the objective function can be offset using $(1 - T)$ and $(1 - C)$ using normalisation formula \ref{equation8}, and normalisation formula \ref{equation7} is for the rest components.
-Therefore, the whole problem is treated as a maximisation problem.
+Also, the lowest T and C value represent the best component quality so that the objective function can be offset using $(1 - T)$ and $(1 - C)$ using normalisation formula (\ref{equation8}), and normalisation formula (\ref{equation7}) is for the rest components.
+Therefore, the whole problem is treated as a maximisation problem.\^{Q}
 
@@
 \label{equation6}
-Fitness = w_1MT + w_2S + w_3A + w_4R + w_5(1 - T) + w_6(1 - C)
+Fitness = w_1 \hat{MT} + w_2 \hat{S} + w_3 \hat{A} + w_4 \hat{R} + w_5(1 - \hat{T}) + w_6(1 - \hat{C})
 \end{equation}
@@
 \label{equation7}
-normalise(value) = 
+\hat{Q_i} = 
 \begin{cases}
-	\frac{value - min}{max - min} & \text{ if }max - min \neq 0.\\
+	\frac{Q_i - Q_{i, min}}{Q_{i, max} - Q_{i, min}} & \text{ if }Q_{i, max} - Q_{i, min} \neq 0.\\
 	1 & \mathrm{ otherwise}.
@@
 \end{equation}
+\noindent where $i$ $=$ $1$, $2$, $3$, and $4$ with $Q_1$ as $MT$, $Q_2$ as $S$, $Q_3$ as $A$, and $Q_4$ as $R$.
 \begin{equation}
 \label{equation8}
-normalise(value) = 
+\hat{Q_i} = 
 \begin{cases}
-	\frac{max - value}{max - min} & \text{ if }max - min \neq 0.\\
+	\frac{Q_{i,max} - \hat{Q_i}}{Q_{i, max} - Q_{i, min}} & \text{ if }Q_{i, max} - Q_{i, min} \neq 0.\\
 	1 & \mathrm{ otherwise}.
@@
 \end{equation}
+\noindent where $i$ $=$ $1$, and $2$ with $Q_1$ as $T$ and $Q_2$ as $C$.
 
@@
 \label{wsc09datasetTable}
-\begin{tabular}{|l|l|l|l|}
+\begin{tabular}{l|l|l|l}
 \hline
-\multicolumn{1}{|c|}{Dataset} & No.Concept & No.Individual & No.Service \\ \hline
+\multicolumn{1}{c|}{Dataset} & No.Concept & No.Individual & No.Service \\ \hline
 WSC09 01                     & 1578       &3102           &572      \\ \hline
@@
 We run 30 times independently for each dataset.
-In addition, weight settings are flexibly defined by users' preferences.
-As part of their requirement, we configure weight of fitness function to properly balance functional side and nonfunctional side.
+We configure weight of fitness function to properly balance functional side and nonfunctional side.
 Therefore, $w_{1}$ and $w_{2}$ are equals to 0.1 and 0.4,  and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly.
+However, the settings of the values does not impact the method.
+In general, weight settings are adjusted according to users' preferences.
 
@@
 
-First, we look at mean value of $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ at optimum at the 100th generation for two approaches, shown in Table \ref{decisionTable}, where QoS-aware approach record $Q_{mt}$, $Q_{s}$ while utilise fitness function $Fitness = w_1A + w_2R + w_3(1 - T) + w_4(1 - C)$ when $\sum_{i=1}^{4} w_i = 1$ without considering $MT$ and $S$, and its $Q_(QoS)$ is normalised from 0 to 0.5 to make it comparable to $Q_{QoS}$ in our approach.
+First, we look at mean value of $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ at optimum at the 100th generation for two approaches, shown in Table \ref{decisionTable}, where QoS-aware approach record $Q_{mt}$, $Q_{s}$ while utilise fitness function $Fitness = w_1 \hat{A} + w_2R + w_3(1 - T) + w_4(1 - C)$ when $\sum_{i=1}^{4} w_i = 1$ without considering $MT$ and $S$, and its $Q_(QoS)$ is normalised from 0 to 0.5 to make it comparable to $Q_{QoS}$ in our approach.
 We observe an interesting pattern from the Table \ref{decisionTable} using statistic analysis: mean value of $Q_{mt}$ and $Q_{s}$ at optimum by our approach is consistently higher than those of QoS-aware approach in Task 1, 3, 4, and 5 with an exception in Task 2 while the combination of mean $Q_{mt}$ and $Q_{s}$ at optimum in Task 2 is still considered to be higher in our approach with 0.1 and 0.4 weights respectively.
@@
 \label{decisionTable}
-\begin{tabular}{|l|l|l|l|}
+\begin{tabular}{l|l|l|l}
 \hline
-\multicolumn{2}{|c|}{WSC09}              & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
+\multicolumn{2}{c|}{WSC09}              & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
 \multirow{3}{*}{Task1}  &$Q_{mt}$   &0.189787 $\pm$ 0.039278686  &0.220594 $\pm$ 0.009318 $\uparrow$ \\ \cline{2-4} 
@@
 \ref{comparisontaxonomy}.
-$Ser1640238160$ and $Ser1947554374$ are selected service vertex with output concept-related parameters $Inst795998200$ and $Inst582785907$ respectively under two methods while $Inst658772240$ are the required input related to $Con2113572083$.
+$Ser1640238160$ and $Ser1947554374$ are selected service vertex with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to $Con103314376$ and $Con2037585750$ respectively under two methods while $Inst658772240$ are the required input related to $Con2113572083$, in which there exist $Con103314376$ $\sqsubseteq_{2}$ $Con2113572083$ and $Con2037585750$ $\sqsubseteq_{3}$ $Con2113572083$.
 It is obviously that our approach select the service providing parameters that are closer the users' requirement, which means our methods results in better semantic matchmaking quality.
@@
 \label{comparisontaxonomy}
-\begin{tabular}{|l|l|l|l|l|}
+\begin{tabular}{l|l|l|l|l}
 \hline
-\multicolumn{2}{|l|}{\shortstack{Quality \\ Criteria}} & WG $(1)$ & WG $(2)$ &  $\Delta Q$\\ \hline
+\multicolumn{2}{l|}{\shortstack{Quality \\ Criteria}} & WG $(1)$ & WG $(2)$ &  $\Delta Q$\\ \hline
 \multirow{2}{*}{e1} &$q(e_{mt})$   &1        &1                       &0     \\ \cline{2-5} 
@@
                     &  $q(e_{s})$  &0.9090   &0.9167                 &+0.0077\\ \hline
-\multicolumn{2}{|l|}{QoS} &0.4949            &0.4915                 &-0.0034  \\ \hline
+\multicolumn{2}{l|}{QoS} &0.4949            &0.4915                 &-0.0034  \\ \hline
 \end{tabular}

### 2016-11-07 paper.tex
update

@@
 Therefore, the consideration in these two quality dimensions is a must, so that service composition needs to deal with optimisation problems in both quality of semantic matchmaking and QoS.
-This paper develops a more applicable way for measuring a proposed comprehensive quality model in both semantic matchmaking and QoS for automated semantic web service composition.
+This paper develops a more applicable way of measuring a proposed comprehensive quality model in both semantic matchmaking and QoS for automated semantic web service composition.
 \end{abstract}
@@
 Particularly, this paper considers the quality of semantic matchmaking quality and QoS and two structural constructs (sequence and parallel) for building optimised composition solution using Particle Swarm Optimisation (PSO).
-We aim to provide a more applicable and adaptive way to measure semantic matchmaking in automated semantic web service composition.
+We aim to provide a more applicable way to measure semantic matchmaking in automated semantic web service composition.
 We will achieve three objectives in this work as follows:
@@
 The remains of this paper are organised as the following: Sect.
-\ref{background} provides the background on the semantic web service composition, and related works; Sect.
-\ref{qswsc_approach} presents an overview of comprehensive quality-aware semantic automated web service composition consisting of comprehensive quality evaluation model and PSO-based service composition algorithm; Sect.
+\ref{relatedWork} provides related works in the semantic web service composition; Sect.
+\ref{qswsc_approach} presents an overview of comprehensive quality-aware semantic automated web service composition consisting of comprehensive quality evaluation model, proposed weighted graphs as solution presention and PSO-based service composition algorithm; Sect.
 \ref{experiment_design} describes the experiments conducted to test the effectiveness of proposed model; Sect.
@@
 Additionally, a semi-automated service composition approach is considered in their paper, rather than a fully automated method.
-In QoS, only cost and time are considered in the optimised problems.
+Only cost and time are considered in the optimised problems.
 Therefore, we introduce a more applicable comprehensive quality model in a fully automated approach.
@@
 In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS.
-Therefore, we fill the gap by considering different matching types and the similarity when evaluate an overall quality of web service composition and utilising weighed graphs as different particle representations from \cite{da2016particle}.
+Therefore, we fill the gap by considering different matching types and the similarity when evaluate an overall quality of web service composition and utilising weighed graphs as a different semantic web service composition representations from \cite{da2016particle}.
 
@@
 Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from a Service Repository: $S =  \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$.
-If no atomic web service could satisfy the composite goal, a combination of web services will be found concretely to meet $Comp.G$.
+If no atomic web service could satisfy the composite goal, a combination of web services will be found to meet $Comp.G$.
 To ensure the composite solution returns the desired $Comp.G$, we consider a comprehensive quality model for service discovery and selection, where challenges $(1)$ and $(2)$ mentioned in Sect.
@@
 To measure the quality of semantic matchmaking, different matching levels are typically considered in the literature \cite{paolucci2002semantic}.
-To understand these levels, let us define two web services associated with parameters in a particular domain.
+To understand these levels, let us define two web services associated with concept-related parameters in a particular domain.
 $S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S_{2}$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$.
@@
 \ref{pso_algorithm} to find best particle location.
-Overall, this approach is different from \cite{da2016particle}, as we use weighted graphs as particle presentation while considering a comprehensive quality.
+This PSO-based approach is different from \cite{da2016particle}, as we use weighted graphs as solution presentation while considering a comprehensive quality for optimisation problem.
 
 \subsection{Semantic Matchmaking} \label{semantic_matchmaking}
-To perform semantic matchmaking, we transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match in \ref{semantic Web service Discovery}.
+To perform semantic matchmaking, we transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match demonstrated in Sect.
+\ref{semantic Web service Discovery}.
 The matching process attempts to determine semantic matching between the source concepts of $C_{1}$ and the target concepts of $C_{2}$.
@@
 Due to the discretisational characteristics of different match types driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}, match types are considered to be one factor for the semantic matchmaking quality.
-Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, which is a taxonomy-based measurement for ontology matching.
+Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, a taxonomy-based measurement for ontology matching.
 This formula (\ref{equation1}) is used to estimate the similarity between parameter-related output concept and parameter-related input concept for selecting web services.
-Therefore, given the quality match type and the similarity of two parameters-related concepts, the semantic matchmaking quality of matched parameters is defined by Formula (\ref{equation2}), where the value of $q(p_ {matchType})$ is set up as the same as the quality of the semantic link in \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).
+Therefore, given the quality match type and the similarity of two parameters-related concepts, the semantic matchmaking quality of matched parameters is defined by Formula (\ref{equation2}), where the value of $q(p_ {matchType})$ is set up as the same as that in \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).
 
@@
 Further more, edges represent services connections in our weighted graph presentations, where assigned weight value $q(e_{sm})$ is considered to be semantic matching quality on edge level according to parameter aggregations.
-The weight value $q(e_{sm})$ is defined in \ref{equation3}, where $q(e_ {matchType})$ and $q(e_ {similarity})$ are the mean value of concept-related parameters quality in $q(p_{mt})$ and $q(p_{s})$ respectively.
+The weight value $q(e_{sm})$ is defined in \ref{equation3}, where $q(e_ {matchType})$ and $q(e_ {similarity})$ are the average value of concept-related parameters quality in $q(p_{mt})$ and $q(p_{s})$ respectively.
 
@@
 e_{n}}$.
-Each $e$ is associated with $q(e_{sm})$ as weight value that mapped to a pair of quality values $q(e_{mt})$ and $q(e_{s})$ on the edge level.
-where $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$.
-Here we provide an example of the web service composition, which can be described in the Fig.
+Each $e$ is associated with $q(e_{sm})$ as weight value that mapped to a pair of quality values $q(e_{mt})$ and $q(e_{s})$ on the edge level, and $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$.
+Here we provide an example of the web service composition, which is described in the Fig.
 \ref{wscs}.
@@
 Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},...
-e_{n}}$, and further aggregated in $Q_{mt}$ and $Q_{s}$ respectively on the construct level.
-In addition, $Q_{QoS}$ is calculated by all the non-functional attributes of $V$ using aggregation rules defined previously.
+e_{n}}$ assigned as weights.
 
@@
 \begin{cases}
-	\frac{Q_{i,max} - \hat{Q_i}}{Q_{i, max} - Q_{i, min}} & \text{ if }Q_{i, max} - Q_{i, min} \neq 0.\\
+	\frac{Q_{i,max} - Q_i}{Q_{i, max} - Q_{i, min}} & \text{ if }Q_{i, max} - Q_{i, min} \neq 0.\\
 	1 & \mathrm{ otherwise}.
@@
 WSC09 provides problems where five tasks consisted in with variable size in both services, and ontologies.
-Therefore, it is a proper dataset for the scalability measures in our defined quality evaluation model.
+Therefore, it is a proper dataset for the scalability measures for our quality evaluation model.
 Table \ref{wsc09datasetTable} presents the features of the WSC’09 dataset.
@@
 
-First, we look at mean value of $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ at optimum at the 100th generation for two approaches, shown in Table \ref{decisionTable}, where QoS-aware approach record $Q_{mt}$, $Q_{s}$ while utilise fitness function $Fitness = w_1 \hat{A} + w_2R + w_3(1 - T) + w_4(1 - C)$ when $\sum_{i=1}^{4} w_i = 1$ without considering $MT$ and $S$, and its $Q_(QoS)$ is normalised from 0 to 0.5 to make it comparable to $Q_{QoS}$ in our approach.
-We observe an interesting pattern from the Table \ref{decisionTable} using statistic analysis: mean value of $Q_{mt}$ and $Q_{s}$ at optimum by our approach is consistently higher than those of QoS-aware approach in Task 1, 3, 4, and 5 with an exception in Task 2 while the combination of mean $Q_{mt}$ and $Q_{s}$ at optimum in Task 2 is still considered to be higher in our approach with 0.1 and 0.4 weights respectively.
-However, the mean value $Q_{QoS}$ at optimum at 100th generation of QoS-aware approach can obtain a slightly higher value than that of our approach.
+First, we look at mean value of $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ at optimum at the 100th generation for two approaches, shown in Table \ref{decisionTable}, where QoS-aware approach record $Q_{mt}$, $Q_{s}$ while utilise fitness function $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$ without considering $MT$ and $S$, and $Q_(QoS)$ is normalised from 0 to 0.5 to make it comparable to $Q_{QoS}$ in our approach.
+We observe an interesting pattern from the Table \ref{decisionTable} using statistic analysis: mean value of $Q_{mt}$ and $Q_{s}$ at optimum by our approach is consistently higher than those by QoS-aware approach in Task 1, 3, 4, and 5 with an exception in Task 2 while the combination of mean $Q_{mt}$ and $Q_{s}$ at optimum in Task 2 is still considered to be higher in our approach with 0.1 and 0.4 weights respectively.
+Meanwhile, $Q_{QoS}$ generated by QoS-aware approach can obtain a slightly higher value than that of our approach.
 In conclusion, we can perceive that our evaluation could find out better functional quality with a reasonable trade off in QoS.
@@
 The Fig.
-\ref{comparison} shows two composition weighted graphs as the solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method.
-Two approaches generate exactly the same service workflow structure while some service vertex and edges denoted in red are different part.
+\ref{comparison} shows two composition weighted graphs as the solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method respectively.
+Two approaches generate exactly the same service workflow structure while some service vertex and edges denoted in red are different.
 Therefore, we make a comparison of the quality among these different edges ($e_1$ to $e4$) associated service vertex in terms of quality of semantic matchmaking and QoS attributes.
-We also look at $\Delta Q$ which reveals the amount of variation between two methods, where the positive values means the benefits gained under our approach while the negative values means the trade-off.
-There is an consistency in our methods that edges are with higher values and service vertex with slightly lower QoS.
-To demonstrate the benefits of the positive value, we analyse the smallest value $e_4$ and demonstrate how the output and required input are different in in Fig.
+We also look at $\Delta Q$ which reveals the amount of variation on quality between two methods, where the positive values means the benefits gained under our approach while the negative values means the trade-off.
+To demonstrate the benefits of the positive value, we analyse the smallest positive $\Delta Q$ corresponding to $e_4$ and demonstrate how the output and required input are different under two approaches in in Fig.
 \ref{comparisontaxonomy}.
-$Ser1640238160$ and $Ser1947554374$ are selected service vertex with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to $Con103314376$ and $Con2037585750$ respectively under two methods while $Inst658772240$ are the required input related to $Con2113572083$, in which there exist $Con103314376$ $\sqsubseteq_{2}$ $Con2113572083$ and $Con2037585750$ $\sqsubseteq_{3}$ $Con2113572083$.
-It is obviously that our approach select the service providing parameters that are closer the users' requirement, which means our methods results in better semantic matchmaking quality.
+$Ser1640238160$ and $Ser1947554374$ are selected service vertex with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to $Con103314376$ and $Con2037585750$ respectively while $Inst658772240$ are the required input related to $Con2113572083$, in which there exist $Con103314376$ $\sqsubseteq_{2}$ $Con2113572083$ and $Con2037585750$ $\sqsubseteq_{3}$ $Con2113572083$.
+It is obviously that our approach select the service providing $Inst795998200$ that are closer the users' requirement, which means our methods results in better semantic matchmaking quality.
 
@@
  \caption{Example Comparison of Edge 4 in Task 3 solution under two methods.}
- \label{comparison}
+ \label{comparisontaxonomy}
 \end{figure}
@@
                     &  $q(e_{s})$  &0.9090   &0.9167                 &+0.0077\\ \hline
-\multicolumn{2}{l|}{QoS} &0.4949            &0.4915                 &-0.0034  \\ \hline
+\multicolumn{2}{l|}{WG QoS} &0.4949            &0.4915                 &-0.0034  \\ \hline
 \end{tabular}

### 2016-11-12 paper.tex
update

@@
 Service-oriented computing (SOC) is a novel computing paradigm that employs services as fundamental elements to achieve agile development of cost-efficient and integratable enterprise applications in heterogeneous environments \cite{papazoglou2003service}.
-Service Oriented Architecture (SOA) could abstractly realise service-oriented paradigm of computing.
-This accomplishment has been contributing to the reuse of software components, from functions to units, and from units to services during the development in SOA \cite{booth2004web}.
+Service Oriented Architecture (SOA) is capable of abstractly realising service-oriented paradigm of computing.
+Since its inception, SOA has been contributing to the reuse of software components, from functions to units, and from units to services during the development in SOA \cite{booth2004web}.
 One of the most typical realisations of SOA is \textit{web service}, which is designated as ``modular, self-describing, self-contained applications that are available on the Internet'' \cite{curbera2001web}.
@@
 This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems.
-Due to the increase in the number of large-scale enterprise applications, the number of Web services has increased dramatically and unprecedentedly, which cause an immense redundancy in functionality in a huge searching space.
-Therefore, manual and semi-automated web service composition are considered to be less efficient while automated web service composition is deemed to be less human intervention, less time consumption, and high productivity.
+Due to the increase in the number of large-scale enterprise applications, the number of Web services has increased substantially and unprecedentedly.
+Therefore, manual and semi-automated web service composition are considered to be less efficient while automated web service composition enjoys less human intervention, less time consumption, and high productivity.
 
 Two most notable challenges for web service composition are $(1)$ ensuring interoperability of services and $(2)$ achieving QoS optimisation \cite{fensel2011semantic}.
-\textit{Interoperability} of web services presents challenge $(1)$ in the dimensions of syntactic and semantics \cite{fensel2011semantic}.
-The syntactic dimension is covered the XML-based technologies (such as $WSDL$, $SOAP$).
+\textit{Interoperability} of web services presents challenge $(1)$ in syntactic and semantics dimensions \cite{fensel2011semantic}.
+The syntactic dimension is covered by the XML-based technologies (such as $WSDL$, $SOAP$).
 The semantics aspect, on the other hand, demands further research.
-Through semantics given by ontologies \cite{o2005review}, web services understand and better collaborate with each other.
+Through ontology-based semantics \cite{o2005review}, web services can understand and better collaborate with each other.
 Historically, there are many ontologies languages and formats for semantic service descriptions, such as OWL-S \cite{martin2004owl}, WSML \cite{fensel2006enabling}, and SAWSDL \cite{lausen2007semantic}.
@@
 The second challenge $(2)$ is related to finding \textit{optimised solutions} to Quality of Service ($QoS$) over composite web services.
-This problems give birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements \cite {sahai2002automated} manifesting a collection of SLA rules and policies for supporting QoS-based composition.
+This problem gives birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements \cite {sahai2002automated} involving a collection of SLA rules and policies for supporting QoS-based composition.
 
-Existing works on service composition focus mainly addressing two challenges above.
-One group optimises the quality of compositions under a pre-defined abstract workflow, which is considered to be a \textit{semi-automated Web service composition} approach.
-Another group attempts to generate a composite plan automatically in discovering and selecting suitable web services, which are deemed to NP-hard \cite{moghaddam2014service}.
-\textit{Semantic web services composition} is distinguished from the syntactic service composition.
-Its benefits are presented in eliminating conflicts by the semantic level of web services.
+Existing works on service composition focus mainly on addressing the two challenges above.
+A lot of works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as \textit{semi-automated Web service composition} approach.
+Meanwhile, many research works consider the possibility of generating a composite plan automatically in discovering and selecting suitable web services, which are deemed to NP-hard \cite{moghaddam2014service}.
+\textit{Semantic web services composition} is distinguished from the syntactic service composition, with the hope of eliminating conflicts by the semantic level of web services.
 In the past few years, substantial works have been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}.
 However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously.
-However, customers often prefer a service composition that matches their requirement most with highest QoS.
+However, customers often prefer a service composition that best matches their requirement with highest QoS.
 
@@
 \begin{enumerate}
- \item To propose a comprehensive quality model that address QoS and semantic matchmaking quality in considering different matching types associated with corresponding semantic similarity.
+ \item To propose a comprehensive quality model that address QoS and semantic matchmaking quality in considering different matching types with corresponding semantic similarity.
 This approach is consider to be a more applicable and effective way of finding an optimised solution in semantic web service composition.
 
- \item To propose a PSO-based service composition model that utilise the proposed quality model.
-In PSO, weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively represent the solutions of semantic web service composition in the searching space, which are decoded from an optimised service queue with the consideration of comprehensive quality.
+ \item To propose a PSO-based service composition algorithm that utilises the proposed quality model.
+In PSO, weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively represent the solutions of semantic web service composition in the searching space, and the weighted graph solutions are decoded from an optimised service queue with the consideration of the proposed comprehensive quality.
 
@@
 \textbf{Semantic web service matchmaking}.
-Substantial work \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} on web service composition focused mainly on non-functional requirements consistently neglecting functional requirements.
-However few researchers addressed both addressed both of them at the same time in web service composition.
-To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing} are the papers could be found so far.
+Substantial work \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} on web service composition focused primarily on non-functional requirements consistently neglecting functional requirements.
+However few researchers addressed both functional and nonfunctional requirements at the same time in web service composition.
+To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing} reported some recent attempts over published.
 Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output parameter concepts of web services to ensure a semantic matchmaking.
-It is considered be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and mapping between two knowledge representations encoded utilising the ontology \cite{lecue2006formal}.
+It is considered to be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and mapping between two knowledge representations encoded utilising the ontology.
 
-In \cite{shet2012new}, three approaches are surveyed three approaches regarding the similarity measures using taxonomies: $(1)$ The first one is based on nodes, in which similarity is determined by the information content of the nodes; $(2)$ the second is entirely based on edge, where concept distance in a hierarchy structure is evaluated, and $(3)$ the hybrid approach features a combination of $(1)$ and $(2)$.
+In \cite{shet2012new}, three approaches have been studied regarding the similarity measures using taxonomies: $(1)$ The first one is based on nodes, in which similarity is determined by the information content of the nodes; $(2)$ the second is entirely based on edge, where concept distance in a hierarchy structure is evaluated, and $(3)$ the hybrid approach features a combination of $(1)$ and $(2)$.
 A new similarity measure based on edge counting in taxonomy is introduced in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}.
@@
 
-In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, one possible measure is applied for the degree of similarity using Common Description rate of a semantic link, where Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are required to be pre-calculated.
+In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, one possible measure is applied to the degree of similarity using Common Description rate of a semantic link, where Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are required to be pre-calculated.
 They also chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint.
 Therefore, the quality of the semantic link is estimated as quality criteria $q_{m}$ associated with their corresponding quality of vector $q_{cd}$.
+However, the weakness of semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined ontology in class, class axioms and properties in OWL2.
+This makes it difficult to measure semantic matchmaking quality in most available semantic web services, as it takes huge cost and time for the domain experts to establish required ontology.
+In comparison, we introduce a more applicable comprehensive quality model in a fully automated approach.
 
-However, the weakness of semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined ontology in class, class axioms and properties in OWL2.
-This makes it difficult to measure semantic matchmaking quality in most semantic web services applications, as it takes unpredictable cost and time for the domain experts to establish required ontology.
-Additionally, a semi-automated service composition approach is considered in their paper, rather than a fully automated method.
-Only cost and time are considered in the optimised problems.
-Therefore, we introduce a more applicable comprehensive quality model in a fully automated approach.
-
-In \cite{fanjiang2014semantic}, it covers the concerns in both functional and non-functional requirements in design time of semantic-based automatic service composition, where a GA-based approach with four unusual independent fitness functions are designed to solve the problems with these concerns.
+The paper \cite{fanjiang2014semantic} covers the concerns in both functional and non-functional requirements in design time of semantic-based automatic service composition, where a GA-based approach with four unusual independent fitness functions are designed to solve the problems with these concerns.
 In details, a sequence of fitness functions are used in the binary selection of chromosomes, rather than a single objective consisting of both functional and non-functional quality.
@@
 \textbf{QoS-aware EC approaches}.
-Evolution Computing techniques are widely used to solve optimisation problem.
-Genetic Programming (GP) \cite{da2016particle,da2015graphevol} is a typical EC technique to solve automated web service composition.
-This GP-based approach utilises tree representations, on which service and constructs as represented as terminal nodes and functional nodes respectively.
+Evolution Computing techniques are widely used to solve optimisation problems.
+Genetic Programming (GP) \cite{da2016particle,da2015graphevol} is a typical EC technique for automated web service composition.
+This GP-based approach utilises tree representations, on which service and constructs are represented as terminal nodes and functional nodes respectively.
 The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure.
@@
 To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}.
-A general graph is used as representation as particles in their PSO algorithm considering QoS optimisation.
-However, this solution does not distinguish different matching types and parameter similarity, which could lead to the outputs returned by the selected service that we think may be too general.
-In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the outputs requested by users.
-In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS.
-Therefore, we fill the gap by considering different matching types and the similarity when evaluate an overall quality of web service composition and utilising weighed graphs as a different semantic web service composition representations from \cite{da2016particle}.
+A general graph is used as representation as composite solution in their PSO algorithm considering QoS optimisation.
+However, this solution does not consider distinguished matchmaking quality, which could lead to over-general outputs to be produced by selected services.
+In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users.
+In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS.
+Therefore, we fill the gap by considering different matching types and parameter similarity to determine the overall quality of web service composition.
+Weighed graphs are also utilised in PSP to facilitate a new representation of web service composition adopted from \cite{da2016particle}.
 
@@
 This overall composite goal is demonstrated in two parts.
-The first functional part is a given task input or input set to get the desired Task output or output set.
+The first functional part focus on transfering a given task input or input set to the desired Task output or output set.
 It typically refers to users' functional requirement.
@@
 \subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
-The semantic service matchmaking aims to discover appropriate services from service repository relevant to a customer's functional requests.
-A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$ with both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Taxonomy\}$.
+The semantic service matchmaking aims to discover appropriate services from service repository in view of customers' functional requests.
+A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$, where both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Taxonomy\}$.
 A web service matching process is to match the output and input concepts of two services according to the Taxonomy within an Ontology (O).
@@
 
-Note that, to find relevant services for service compositions according to a given goal, we consider Exact, Plugin, Subsume and Fail match types in our paper.
-Therefore, these matches will be used to discover web service candidates for service composition in our proposed the comprehensive quality-aware model in Sect.\ref{semantic_matchmaking}
-
 \subsection{Quality of Service and Composition Constructs}\label{Quality of Service and Composition Constructs}
@@
 This problem has been explored in both single objective and multi-objectives optimisation problems.
-Customers prefer lowest execution cost with highest response time and reliability so that it could be involved as a single objective optimisation problem while cost and reliability of web service are two conflicting objectives that could be optimised simultaneously in multi-objective problem.
+Customers prefer lowest execution cost with highest response time and reliability that could be optimised simultaneously.
 According to \cite{zeng2003quality}, four most often considered QoS parameters are as follows:
@@
 \end{itemize}
-The aggregation value of QoS attributes for web services composition varies with respect to different constructs, which explains how services associated with each other in a service composition \cite{zeng2003quality}.
-Here we consider two composite constructs: sequence and parallel constructs, in building the composite flow.
+The aggregation value of QoS attributes for web services composition varies with respect to different constructs, which reflects how services associated with each other in a service composition \cite{zeng2003quality}.
+Here we consider two composite constructs: sequence and parallel constructs, in building the composite web service.
 The QoS calculation models are described as follows:
@@
 \subsubsection{Parallel construct}
-Web services in a parallel construct are executed in the meantime.
-The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is delimited by the maximum time consumed path in the composite flow of the solution.
+Web services in a parallel construct are executed concurrently.
+The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is determined by the most time-consuming path in the composite flow of the solution.
 This construct is presented in Fig.
@@
 PSO has shown its efficiency in solving combinatorial optimisation problems.
-Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing comparing to GP \cite{da2014graph}.
+Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing that often required by GP \cite{da2014graph}.
 Fig.
@@
 Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional.
-A functional requirement is defined as $F(T_{Input}, T_{Output})$ , and a nonfunctional one is users' accepted level of QoS.
-Step 2: Those requirements are used to discover all relevant web services, which leads to a shrunken service repository that further used by PSO as a searching space.
-Step 3: A weighted graph representation is randomly built up interleaving with semantic matchmaking process, where web services are discovered as graph vertices while edges are assigned with semantic matchmaking quality as weights.
-Step 4,5: The selection of web services performs PSO algorithm in Sect.
-\ref{pso_algorithm} to find best particle location.
-This PSO-based approach is different from \cite{da2016particle}, as we use weighted graphs as solution presentation while considering a comprehensive quality for optimisation problem.
+Step 2: This composition goal are used to discover all relevant web services, which lead to a shrunken service repository that is subsequently used by PSO as a searching space.
+Step 3: A weighted graph representation is randomly built up from the an initial service queue that mapped to the particle's location, interleaving with semantic matchmaking process.
+In the weighted graph, graph edges are assigned with semantic matchmaking quality as weights.
+Step 4: The fitness value of the weighted graph is evaluated to update the position of particle under PSO algorithm in Sect.
+\ref{pso_algorithm}, where the position is mapped to the index of service queue.
+later on, the updated service queue is used to decode a new weighted graph as the composition solution.
+Step 4.
+Lastly, the best position found in the searching space is selected and decode into the final optimised solution.
+This PSO-based approach is different from \cite{da2016particle}, as we use weighted graphs as solution presentation.
 
@@
 The matching process attempts to determine semantic matching between the source concepts of $C_{1}$ and the target concepts of $C_{2}$.
-Meanwhile, the quality of matched concepts are calculated in the mode model in subSection \ref{qualityModel}.
-The purpose of semantic matchmaking is to find more component services that could also potentially satisfies the quality of QoS with considering its functional quality.
+Meanwhile, the quality of matched concepts are calculated in the quality model in subSection \ref{qualityModel}.
+The purpose of semantic matchmaking is to find more component services that could also potentially satisfy the quality of QoS with good functional quality.
 
 The semantic matchmaking is achieved by utilising OWL2 and OWL-S or other semantic markup languages for web services.
-In this paper, we use MECE (Mediation Contract Extension) \cite{bleul2008self} and OWL-DL, MECE is considered to be an alternative semantic annotation for WSDL.
+In this paper, we use MECE (Mediation Contract Extension) \cite{bleul2008self} and OWL-DL.
+MECE is considered to be an alternative semantic annotation for WSDL.
 MECE defines the service-related inputs and outputs with parameter-related concepts.
-OWL-DL is a sublanguage of OWL from extension of RDF.
-which specifies semantic information of concepts involved in MECE.
+OWL-DL is a sublanguage of OWL extended from RDF.
+It specifies semantic information of concepts involved in MECE.
 
@@
 In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition.
-This model overcome the disadvantages of current prevailing QoS-aware optimisation, in which quality of semantic matchmaking are not considered \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive}.
+This model overcome the disadvantages of current prevailing QoS-aware optimisation \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} that ignores quality of semantic matchmaking.
 
 \textbf{Semantic matchmaking model}.
-Due to the discretisational characteristics of different match types driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}, match types are considered to be one factor for the semantic matchmaking quality.
-Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, a taxonomy-based measurement for ontology matching.
+Due to the discretisational characteristics of different match types and values assigned to matching types that driven by the cost of data integration and manipulation \cite{lecue2009optimizing}, partial ordering match types are considered to be one factor for the semantic matchmaking quality.
+For example, Exact matching type demands less time for computation compared to that of Plugin match.
+Another factor in our proposed model is concept similarity, which could be evaluated based on the edge counting method defined in \cite{shet2012new}.
 This formula (\ref{equation1}) is used to estimate the similarity between parameter-related output concept and parameter-related input concept for selecting web services.
-Therefore, given the quality match type and the similarity of two parameters-related concepts, the semantic matchmaking quality of matched parameters is defined by Formula (\ref{equation2}), where the value of $q(p_ {matchType})$ is set up as the same as that in \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).
+Therefore, given the quality match type and the similarity of two parameters-related concepts, the semantic matchmaking quality of matched parameters is defined by Formula (\ref{equation2}), where the value of $q(p_ {mt})$ follows the same settings in \cite{lecue2009optimizing}.
+Particularly, 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).
 
@@
 
-Further more, edges represent services connections in our weighted graph presentations, where assigned weight value $q(e_{sm})$ is considered to be semantic matching quality on edge level according to parameter aggregations.
-The weight value $q(e_{sm})$ is defined in \ref{equation3}, where $q(e_ {matchType})$ and $q(e_ {similarity})$ are the average value of concept-related parameters quality in $q(p_{mt})$ and $q(p_{s})$ respectively.
+Further more, edges represent services connections in our weighted graph representations, where assigned weight value $q(e_{sm})$ is considered to be semantic matching quality on edge level according to parameter aggregations.
+The weight value $q(e_{sm})$ is defined in \ref{equation3}, where $q(e_ {mt})$ and $q(e_ {s})$ are the average value of concept-related parameters quality in $q(p_{mt})$ and $q(p_{s})$ respectively.
 
@@
 \textbf{Comprehensive quality model}.
-Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional requirements of a goal.
+Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional requirements.
 The comprehensive quality of our service composition representation refers to QoS of service vertices and Semantic matching quality of Edges in weighted graphs.
@@
 \textbf{Quality aggregate matrix}.
-The quality aggregation is defined based on the constructs of composite web services on the criteria of functional and non-functional properties.
-The quality on construct level is further calculated and by following the rules summarised in Table \ref{table1}.
+The quality aggregation is defined based on the constructs of composite web services, in consideration of functional and non-functional properties.
+The quality on construct level is further calculated by following the rules summarised in Table \ref{table1}.
 
@@
 \subsection{Composition Weighted Graph}
-We defined our semantic web service composition solution as $WG = (V, E)Graph$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of edges $E = {e_{1}, e_{2},...
+We defined our semantic web service composition solution as a weighted graph $WG = (V, E)$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of edges $E = {e_{1}, e_{2},...
 e_{n}}$.
 Each $e$ is associated with $q(e_{sm})$ as weight value that mapped to a pair of quality values $q(e_{mt})$ and $q(e_{s})$ on the edge level, and $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$.
-Here we provide an example of the web service composition, which is described in the Fig.
+Here we provide an example of the web service composition, which is described in Fig.
 \ref{wscs}.
@@
 \subsection{Fitness Calculation}
-The fitness value of a service composition solution is a weighted sum of all the quality components discussed previously shown in Formula (\ref{equation6}), in which fitness value of 1 means the best comprehensive quality and 0 means the worst.
-As the sum of all the components' weights ($w_1$ to $w_6$) equals to 1, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the fitness value falls within the range from 0 to 1.
-Also, the lowest T and C value represent the best component quality so that the objective function can be offset using $(1 - T)$ and $(1 - C)$ using normalisation formula (\ref{equation8}), and normalisation formula (\ref{equation7}) is for the rest components.
-Therefore, the whole problem is treated as a maximisation problem.\^{Q}
+The fitness value of a service composition solution is a weighted sum of all the quality related components in Formula (\ref{equation6}), in which fitness value of 1 means the best comprehensive quality and 0 means the worst.
+For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the fitness value falls within the range from 0 to 1.
+Therefore, the service composition problem in this paper is treated as a fitness maximisation problem.
 
@@
 \label{equation7}
-\hat{Q_i} = 
+\hat{Q_k} = 
 \begin{cases}
-	\frac{Q_i - Q_{i, min}}{Q_{i, max} - Q_{i, min}} & \text{ if }Q_{i, max} - Q_{i, min} \neq 0.\\
+	\frac{Q_k - Q_{k, min}}{Q_{k, max} - Q_{k, min}} & \text{ if }Q_{k, max} - Q_{k, min} \neq 0.\\
 	1 & \mathrm{ otherwise}.
@@
 \end{equation}
-\noindent where $i$ $=$ $1$, $2$, $3$, and $4$ with $Q_1$ as $MT$, $Q_2$ as $S$, $Q_3$ as $A$, and $Q_4$ as $R$.
+\noindent where $k$ $=$ $1$, $2$, $3$, and $4$, where $Q_1$ as $MT$, $Q_2$ as $S$, $Q_3$ as $A$, and $Q_4$ as $R$.
 \begin{equation}
 \label{equation8}
-\hat{Q_i} = 
+\hat{Q_j} = 
 \begin{cases}
-	\frac{Q_{i,max} - Q_i}{Q_{i, max} - Q_{i, min}} & \text{ if }Q_{i, max} - Q_{i, min} \neq 0.\\
+	\frac{Q_{j,max} - Q_j}{Q_{j, max} - Q_{j, min}} & \text{ if }Q_{j, max} - Q_{j, min} \neq 0.\\
 	1 & \mathrm{ otherwise}.
@@
 \end{equation}
-\noindent where $i$ $=$ $1$, and $2$ with $Q_1$ as $T$ and $Q_2$ as $C$.
+\noindent where $j$ $=$ $1$, and $2$, where $Q_1$ as $T$ and $Q_2$ as $C$.
 
@@
 
-The overall algorithm investigated here is a PSO-based web service composition algorithm \ref{novelSteps} from   \cite{da2016particle} with a different decoded algorithm \ref{graph_building} to generate a composition weighted graph from a queue.
-In the first algorithm, the idea is to translate the particle location into a service queue as an indirect representation of composition weighted graph, so finding the best fitness of the composite weighted graph is to discover the optimised location of the particle in the search space.
-In PSO, the dimension of the particle is set up as the same number as relevant web services, and the index of services is mapped to the location vectors in a particle, and we put services in a queue in ascending order, from which we decode a weighted graph using Algorithm \ref{graph_building}.
+The overall algorithm investigated here is made up of a PSO-based web service composition algorithm \ref{novelSteps} and a decoding algorithm \ref{graph_building}, to generate a composition weighted graph.
+In algorithm \ref{novelSteps}, the idea is to translate the particle location produced by PSO into a service queue as an indirect representation of weighted graph, such that finding the best fitness of the weighted graph is to discover the optimised location of the particle in the search space.
+In PSO, the dimension of each particle is equals to the number of relevant web services.
+The index of each services is mapped to a separate location component in a particle.
+Services in a queue follow the ascending order, from which we decode a weighted graph using Algorithm \ref{graph_building}.
 We select and connect  service vertex to the start vertex from the service queue if the web service can satisfy the output of start vertex.
-Meanwhile, an Output Set is initialised and kept being updated using outputs from the new-added service vertex in the weighted graph, later on, more services vertex are connected with edges if services' inputs could be satisfied by any output in the Output Set.
-At last, The end vertex is connected if the updated Output Set contains all end inputs.
-In addition, dangling service vertex and edges should be removed.
+Meanwhile, an Output Set is initialised and kept being updated using outputs from the newly added service vertex in the weighted graph, later on, more services vertices are connected with edges if services' inputs could be satisfied by any output in the Output Set.
+Finally, the end vertex is connected to the graph if the updated Output Set contains all end inputs.
+In addition, dangling service vertex and edges will be removed.
 
@@
 In this section, a quantitative evaluation approach is adopted in our experiment design.
-The objectives of the evaluation are $(1)$ to measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach, $(2)$ to explore the impacts of the semantic matchmaking that contributes to overall composition quality, and $(3)$ to compare solutions generated by QoS-ware approach with our method.
+The objectives of the evaluation are to $(1)$ measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach; $(2)$ explore the impacts of the semantic matchmaking that contributes to overall composition quality; and $(3)$ compare solutions generated by QoS-ware approach with our method.
 
-We utilise benchmark dataset web service challenge 2009 (WSC09) \cite{kona2009wsc} to perform a evaluation.
-WSC09 provides problems where five tasks consisted in with variable size in both services, and ontologies.
-Therefore, it is a proper dataset for the scalability measures for our quality evaluation model.
+We utilise benchmark dataset web service challenge 2009 (WSC09) \cite{kona2009wsc} to perform the evaluation.
+WSC09 provides problems with five tasks corresponding to variable number of services, and ontologies.
+Therefore, it is a challenge dataset for measuring the scalability of our quality evaluation model.
 Table \ref{wsc09datasetTable} presents the features of the WSC’09 dataset.
@@
 
-We run the experiment under computing grid comprising of almost 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine.
+We run the experiment on computing grid comprising of almost 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine.
 Experimentation is done using the approach explained in Section \ref{qswsc_approach}, and evaluated in the comprehensive quality model introduced in Subsection \ref{qualityModel}.
@@
 \multirow{3}{*}{Task3}  &$Q_{mt}$   &0.158526 $\pm$ 0.014028               &  0.245830 $\pm$ 0.007761 $\uparrow$   \\ \cline{2-4} 
-                        &$Q_{s}$    & 0.949109 $\pm$ 0.002331           &   0.972765 $\pm$ 0.002980 $\uparrow$           \\ \cline{2-4}
-                        &$Q_{QoS}$  &  0.247002 $\pm$ 0.000661 $\uparrow$             &  0.245631 $\pm$ 0.000431            \\ \hline
-\multirow{3}{*}{Task4}  &$Q_{mt}$   &              &                 \\ \cline{2-4} 
-                        &$Q_{s}$    &               &                   \\ \cline{2-4}
-                        &$Q_{QoS}$  &               &                     \\ \hline
+                        &$Q_{s}$    &0.949109 $\pm$ 0.002331           &   0.972765 $\pm$ 0.002980 $\uparrow$           \\ \cline{2-4}
+                        &$Q_{QoS}$  &0.247002 $\pm$ 0.000661 $\uparrow$             &  0.245631 $\pm$ 0.000431            \\ \hline
+\multirow{3}{*}{Task4}  &$Q_{mt}$   &0.000000 $\pm$ 0.000000  &0.000001 $\pm$ 0.000002 $\uparrow$ \\ \cline{2-4} 
+                        &$Q_{s}$    &0.880058 $\pm$ 0.006603    &0.930632 $\pm$ 0.009043 $\uparrow$ \\ \cline{2-4}
+                        &$Q_{QoS}$  &0.242338 $\pm$ 0.000516 $\uparrow$    &0.236677 $\pm$ 0.002211  \\ \hline
 \multirow{3}{*}{Task5}  &$Q_{mt}$   &  0.000042 $\pm$ 0.000030     &  0.000078 $\pm$ 0.000031 $\uparrow$           \\ \cline{2-4} 
@@
 \fbox{
-\includegraphics[width=6cm]{comparision.pdf}}}
+\includegraphics[width=8cm]{comparision.pdf}}}
  \caption{Example Comparison of solutions to Task 3 under different approaches.}
@@
 \end{figure}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{multirow}
-\begin{table}[]
-\centering
-\caption{Comparison of Composition Weighted Graphs}
-\label{comparisontaxonomy}
-\begin{tabular}{l|l|l|l|l}
-\hline
-\multicolumn{2}{l|}{\shortstack{Quality \\ Criteria}} & WG $(1)$ & WG $(2)$ &  $\Delta Q$\\ \hline
-\multirow{2}{*}{e1} &$q(e_{mt})$   &1        &1                       &0     \\ \cline{2-5} 
-                    & $q(e_{s})$   &1        &1                       &0\\ \hline
-\multirow{2}{*}{e2} & $q(e_{mt})$  &0.75     &0.9167                  &+0.1667 \\ \cline{2-5} 
-                    & $q(e_{s})$   &0.9232   &0.9630                &+0.0398\\ \hline
-\multirow{2}{*}{e3} &  $q(e_{mt})$ &0.75     &0.8333                 &+0.08333\\ \cline{2-5} 
-                    &   $q(e_{s})$ &0.8230   &0.9608                 &+0.1378\\ \hline
-\multirow{2}{*}{e4} & $q(e_{mt})$  &0.75     &0.875                  &+0.125\\ \cline{2-5} 
-                    &  $q(e_{s})$  &0.9090   &0.9167                 &+0.0077\\ \hline
-\multicolumn{2}{l|}{WG QoS} &0.4949            &0.4915                 &-0.0034  \\ \hline
-\end{tabular}
-\end{table}
 

### 2016-11-12 paper.tex
update

@@
 PSO has shown its efficiency in solving combinatorial optimisation problems.
-Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing that often required by GP \cite{da2014graph}.
+Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing that often required by GP \cite{da2016particle}.
 Fig.
@@
 
-The overall algorithm investigated here is made up of a PSO-based web service composition algorithm \ref{novelSteps} and a decoding algorithm \ref{graph_building}, to generate a composition weighted graph.
+The overall algorithm investigated here is made up of a PSO-based web service composition algorithm \ref{novelSteps} and a decoding algorithm \ref{graph_building}, to generate a composition weighted graph, where code lines in blue are different from the algorithm in \cite{da2016particle}.
 In algorithm \ref{novelSteps}, the idea is to translate the particle location produced by PSO into a service queue as an indirect representation of weighted graph, such that finding the best fitness of the weighted graph is to discover the optimised location of the particle in the search space.
@@
 
-We run the experiment on computing grid comprising of almost 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine.
-Experimentation is done using the approach explained in Section \ref{qswsc_approach}, and evaluated in the comprehensive quality model introduced in Subsection \ref{qualityModel}.
-The parameters were chosen based on general settings from \cite{shi2001particle} for our PSO-based approach, 30 particles evolved in 100 generations in the searching space, in which problem dimension's size equals to the number of relevant services in service repository.
+We run the experiment on computing grid comprising of 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine.
+The parameters were chosen based on general settings from \cite{shi2001particle} for our PSO-based approach, In particular, PSO population size is 30 with 100 generations.
 We run 30 times independently for each dataset.
 We configure weight of fitness function to properly balance functional side and nonfunctional side.
-Therefore, $w_{1}$ and $w_{2}$ are equals to 0.1 and 0.4,  and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly.
-However, the settings of the values does not impact the method.
+Therefore, $w_{1}$ and $w_{2}$ equal to 0.1 and 0.4,  and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly.
+However, the settings of these weight values does not impact the method.
 In general, weight settings are adjusted according to users' preferences.
@@
 In this section, we analyse the composition solution generated by using our approach comparing with QoS-aware approach.
-In particularly, we show that our proposed approach can produce solutions that results better matchmaking, which meets user's goal better.
+In particularly, we show that our proposed approach can produce solutions that results in better matchmaking, which meets user's goal better.
 
-First, we look at mean value of $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ at optimum at the 100th generation for two approaches, shown in Table \ref{decisionTable}, where QoS-aware approach record $Q_{mt}$, $Q_{s}$ while utilise fitness function $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$ without considering $MT$ and $S$, and $Q_(QoS)$ is normalised from 0 to 0.5 to make it comparable to $Q_{QoS}$ in our approach.
-We observe an interesting pattern from the Table \ref{decisionTable} using statistic analysis: mean value of $Q_{mt}$ and $Q_{s}$ at optimum by our approach is consistently higher than those by QoS-aware approach in Task 1, 3, 4, and 5 with an exception in Task 2 while the combination of mean $Q_{mt}$ and $Q_{s}$ at optimum in Task 2 is still considered to be higher in our approach with 0.1 and 0.4 weights respectively.
+First, we look at mean value of $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ at optimum at the 100th generation for two approaches, shown in Table \ref{decisionTable}.
+The QoS-aware approach record $Q_{mt}$, $Q_{s}$ and utilise fitness function $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$ without considering $MT$ and $S$, in which $Q_(QoS)$ is normalised from 0 to 0.5 to make it comparable to $Q_{QoS}$ in our approach.
+We observe an interesting pattern from the Table \ref{decisionTable} using statistic analysis: mean value of $Q_{mt}$ and $Q_{s}$ at optimum by our approach is consistently higher than those by QoS-aware approach with one exception in Task 2 while the combination of mean $Q_{mt}$ and $Q_{s}$ at optimum in Task 2 is still significantly higher in our approach under statistical anlysis.
 Meanwhile, $Q_{QoS}$ generated by QoS-aware approach can obtain a slightly higher value than that of our approach.
@@
 
-% Please add the following required packages to your document preamble:
-% \usepackage{multirow}
 \begin{table}[]
@@
 
-Second, to compare the results generated from two evaluation approaches, we demonstrate an example solution that shows the differences in two composition weighted graphs representations under two different methods.
-The Fig.
+Second, to compare the results generated from two evaluation approaches, we demonstrate an example solution that shows the differences in composite web services obtained through two different methods.
+Fig.
 \ref{comparison} shows two composition weighted graphs as the solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method respectively.
-Two approaches generate exactly the same service workflow structure while some service vertex and edges denoted in red are different.
-Therefore, we make a comparison of the quality among these different edges ($e_1$ to $e4$) associated service vertex in terms of quality of semantic matchmaking and QoS attributes.
+Two approaches generate exactly the same service workflow structure where those service vertices and edges denoted in red are different.
+We make a comparison of the quality among these different edges ($e_1$ to $e4$) associated service vertices in terms of quality of semantic matchmaking and QoS attributes.
 We also look at $\Delta Q$ which reveals the amount of variation on quality between two methods, where the positive values means the benefits gained under our approach while the negative values means the trade-off.
-To demonstrate the benefits of the positive value, we analyse the smallest positive $\Delta Q$ corresponding to $e_4$ and demonstrate how the output and required input are different under two approaches in in Fig.
+To demonstrate the benefits of the positive value, we analyse the smallest positive $\Delta Q$ corresponding to $e_4$ and demonstrate how the output and required input are different under two approaches in Fig.
 \ref{comparisontaxonomy}.
-$Ser1640238160$ and $Ser1947554374$ are selected service vertex with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to $Con103314376$ and $Con2037585750$ respectively while $Inst658772240$ are the required input related to $Con2113572083$, in which there exist $Con103314376$ $\sqsubseteq_{2}$ $Con2113572083$ and $Con2037585750$ $\sqsubseteq_{3}$ $Con2113572083$.
-It is obviously that our approach select the service providing $Inst795998200$ that are closer the users' requirement, which means our methods results in better semantic matchmaking quality.
+$Ser1640238160$ and $Ser1947554374$ are selected service vertices with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to two concepts $Con103314376$ and $Con2037585750$ respectively, and $Inst658772240$ are the required parameter related to concept $Con2113572083$.
+There exist $Inst795998200$ $\in$ $Con103314376$ $\sqsubseteq_{2}$ $Inst658772240$ $\in$ $Con2113572083$ and $Inst582785907$ $\in$ $Con2037585750$ $\sqsubseteq_{3}$ $Inst658772240$ $\in$ $Con2113572083$.
+It is obvious that our approach selects the service providing $Inst795998200$ that are closer to the users' requirements suggesting that our method can produce better semantic matchmaking quality.
 
@@
 
-To analyse the effectiveness of our approach, we will study the convergence rate of the proposed method in this section to understand the convergence rate of five tasks in WSC09.
-To further study the overall effectiveness of evaluation model and explore impacts of all involved components in the fitness function.
-We analysis all the performances of these components in the whole evolutionary process in Fig.
-\ref{exp_fitnessvalue}, in which the five tasks' experiment results are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average QoS for generation 0-99 with optimum.
+To analyse the effectiveness of our approach, we study the convergence rate of the proposed method in this section to understand the convergence rate of five tasks in WSC09.
+We analysis the performances during the whole evolutionary process in Fig.
+\ref{exp_fitnessvalue}, in which experiment results on five tasks are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average QoS for generation 0-99 with optimum.
 
-Firstly, the average fitness value with optimum is calculated by the average value of best fitness found in each generation over 30 independent runs.
-The value plotted in the first column group ranges from 0 to 1 in Fig.
-\ref{exp_fitnessvalue}, and it is considered to be more optimised if its value is closer to value 1.
-We can see that there is a significant increase in the fitness values with optimum between generation 0 and generation 15-25, the remaining generation continues to produce a steady but moderate improvement in the fitness value and eventually reach a plateau with no further changes.
+Firstly, the average fitness value with optimum is calculated by averaging the best fitness found in each generation over 30 independent runs.
+We can see that there is a significant increase in the fitness values towards optimum between generation 0 and generation 15-25, the remaining generation continues to produce a steady but moderate improvement in the fitness value and eventually reach a plateau with no further improvements can be observed.
 The same behaviour is observed over the rest tasks.
-We also witnessed a fast convergence rate of the fitness value.
 
@@
 \ref{exp_fitnessvalue}.
-In these groups,  both the average matchType quality with optimum and average similarity quality with optimum are the mean value corresponding to the best fitness value found in each generation over 30 independent runs.
-The dominant tendency of the marked value representing a similar characteristic compared to the average fitness value group trend in five tasks.
-However, there are some slight fluctuations over the generations.
-
-Lastly, it is interesting to look at the average QoS per generation for the 30 independent runs when the functional quality heads up.
-Here average QoS with optimum is also the value corresponding to the fitness value with optimum in each generation, and we display the results in the fourth column group in Fig.
-\ref{exp_fitnessvalue}.
-It is obvious that the overall trend of QoS moves upward to a high constant level in five independent tasks.
-Additionally, we don't see too much trade-off from the QoS.
+In these subfigures, both the average matchType quality with optimum and average similarity quality with optimum refers to the mean values of the quality values associated to the best fitness value found in each generation over 30 independent runs.
+Similar to the fitness values, clear evidence of fast convergence can be observed with respect to theses quality values.
+This observation is also consistent for the improvement of mean QoS quality with optimum shown in the last column in Fig \ref{exp_fitnessvalue}.
+Additionally, we don't see too much trade-off from the QoS as the a consistently increase in semantic matchmaking quality is observed.
 

### 2016-11-13 paper.tex
update first page

@@
 Semantic web service composition has been a prevailing research area in recent years.
-There are two major governance challenges faced by researchers.
-One is semantic matchmaking for discovering interoperable web services, which demands a rich “machine understanding” language such as OWL-S (Web Ontology language for Web Services), WSML (Web Service Modeling language, SAWSDL (Semantic Annotations for WSDL and XML Schema).
-This interaction of web services enables us to pair service functionalities through understanding and reasoning those semantic descriptions.
-Optimisation problems are another challenge.
+There are two major governance challenges faced by researchers (semantic matching and QoS optimisation).
+Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning.
+QoS optimisation aims to meet non-functional requirement of service users.
+e.g minimum cost, maximal reliability.
 Many scholars have looked into nonfunctional optimisation problems in QoS-aware web service composition applying AI planning and Evolution Computing techniques.
-However, it is not sufficient without considering good balance between functional and nonfunctional quality in most scenarios.
-Therefore, the consideration in these two quality dimensions is a must, so that service composition needs to deal with optimisation problems in both quality of semantic matchmaking and QoS.
-This paper develops a more applicable way of measuring a proposed comprehensive quality model in both semantic matchmaking and QoS for automated semantic web service composition.
+To meet users' requirement, one often needs to consider both semantic matching and QoS optimisation simultaneously.
+Existing works on web service composition often concerns either semantic service composition or QoS-aware service composition.
+However, there are very few works concerns both quality of semantic matching and quality of services at the same time.
+Therefore, In this paper we consider two quality dimensions in a proposed more applicable comprehensive quality model for semantic web service composition, and present a automated semantic web service composition approach that can generate service composition solutions that meet both functional and non-functional requirement.
+We will evaluate our approach utilising a semantic benchmark dataset.
+
 \end{abstract}
@@
 Service-oriented computing (SOC) is a novel computing paradigm that employs services as fundamental elements to achieve agile development of cost-efficient and integratable enterprise applications in heterogeneous environments \cite{papazoglou2003service}.
-Service Oriented Architecture (SOA) is capable of abstractly realising service-oriented paradigm of computing.
+Service Oriented Architecture (SOA) is capable of abstractly realising service-oriented computing.
 Since its inception, SOA has been contributing to the reuse of software components, from functions to units, and from units to services during the development in SOA \cite{booth2004web}.

### 2016-11-14 paper.tex
up

@@
 Existing works on web service composition often concerns either semantic service composition or QoS-aware service composition.
-However, there are very few works concerns both quality of semantic matching and quality of services at the same time.
+However, there are very few works concerns both quality of semantic matchmaking and quality of services at the same time.
 Therefore, In this paper we consider two quality dimensions in a proposed more applicable comprehensive quality model for semantic web service composition, and present a automated semantic web service composition approach that can generate service composition solutions that meet both functional and non-functional requirement.
@@
 This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems.
-Due to the increase in the number of large-scale enterprise applications, the number of Web services has increased substantially and unprecedentedly.
+Due to the increase of the number of large-scale enterprise applications, the number of Web services has increased substantially and unprecedentedly.
 Therefore, manual and semi-automated web service composition are considered to be less efficient while automated web service composition enjoys less human intervention, less time consumption, and high productivity.
@@
 Through ontology-based semantics \cite{o2005review}, web services can understand and better collaborate with each other.
-Historically, there are many ontologies languages and formats for semantic service descriptions, such as OWL-S \cite{martin2004owl}, WSML \cite{fensel2006enabling}, and SAWSDL \cite{lausen2007semantic}.
-The logical characteristics in reasoning makes ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments.
-The second challenge $(2)$ is related to finding \textit{optimised solutions} to Quality of Service ($QoS$) over composite web services.
-This problem gives birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements \cite {sahai2002automated} involving a collection of SLA rules and policies for supporting QoS-based composition.
+There are many ontologies languages and formats for semantic service descriptions, such as OWL-S \cite{martin2004owl}, WSML \cite{fensel2006enabling}, and SAWSDL \cite{lausen2007semantic}, which make ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments.
+The second challenge $(2)$ is related to finding \textit{optimised solutions} to Quality of Service ($QoS$).
+This problem gives birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements (SLA) \cite {sahai2002automated} involving a collection of SLA rules and policies for supporting QoS-based composition.
 
-Existing works on service composition focus mainly on addressing the two challenges above.
+Existing works on service composition focus mainly on addressing the one of challenges above.
 A lot of works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as \textit{semi-automated Web service composition} approach.
@@
 However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously.
-However, customers often prefer a service composition that best matches their requirement with highest QoS.
+To a given service request, the quality of service composition solution depends on both QoS and quality of semantic matchmaking.
+Therefore, a comprehensive quality model is needed to measure the quality of service composition solution.
 
 The overall goal of this paper is to \textit{develop an comprehensive quality-aware automated semantic web service composition that satisfactorily optimises both functional and non-functional requirements}.
-Particularly, this paper considers the quality of semantic matchmaking quality and QoS and two structural constructs (sequence and parallel) for building optimised composition solution using Particle Swarm Optimisation (PSO).
-We aim to provide a more applicable way to measure semantic matchmaking in automated semantic web service composition.
+Particularly, this paper extends existing works on semantic service composition and QoS-aware service composition by considering both QoS optimisation and semantic matching optimisation in our comprehensive quality model.
+Particle Swarm Optimisation (PSO) has show its promise in searching near-optimised service composition solution \cite{da2016particle}, we will propose a PSO-based service composition approach using our comprehensive quality model, which is considered to be more applicable way to measure semantic matchmaking in automated semantic web service composition.
 We will achieve three objectives in this work as follows:
@@
 \begin{tabular}{p{0.6\linewidth}}
-\space\hfill\includegraphics[width=2in]{sequence.pdf}\hfill\space\\[0.2cm]
+\space\hfill\includegraphics[width=2in]{sequence.eps}\hfill\space\\[0.2cm]
 $T=\sum\limits^m_{n=1}t_n$ \hfill $C=\sum\limits^m_{n=1}c_n$ \hfill
@@
 \begin{tabular}{p{0.6\linewidth}}
-\space\hfill\includegraphics[width=1.4in]{parallel.pdf}\hfill\space\\[0.2cm]
+\space\hfill\includegraphics[width=1.4in]{parallel.eps}\hfill\space\\[0.2cm]
 \space\hfill$T=MAX\{t_n|n\in\{1,\ldots,m\}\}$\hfill\space\\[0.2cm]
@@
 \fbox{
-\includegraphics[width=12cm]{overview.pdf}}}
+\includegraphics[width=12cm]{overview.eps}}}
  \caption{Overview of the proposed approach.}
@@
 \fbox{
-\includegraphics[width=8cm]{weigtedGraphExample.pdf}}}
+\includegraphics[width=8cm]{weigtedGraphExample.eps}}}
  \caption{Composition weighted graph solution}
@@
 Fig.
-\ref{comparison} shows two composition weighted graphs as the solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method respectively.
+\ref{comparisontest} $(1)$ and $(2)$shows two composition weighted graphs as the solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method respectively.
 Two approaches generate exactly the same service workflow structure where those service vertices and edges denoted in red are different.
-We make a comparison of the quality among these different edges ($e_1$ to $e4$) associated service vertices in terms of quality of semantic matchmaking and QoS attributes.
+We make a comparison of the quality among these different edges ($e_1$ to $e4$) associated service vertices in terms of quality of semantic matchmaking and QoS attributes in Fig.
+\ref{comparisontest} $(3)$.
 We also look at $\Delta Q$ which reveals the amount of variation on quality between two methods, where the positive values means the benefits gained under our approach while the negative values means the trade-off.
 To demonstrate the benefits of the positive value, we analyse the smallest positive $\Delta Q$ corresponding to $e_4$ and demonstrate how the output and required input are different under two approaches in Fig.
-\ref{comparisontaxonomy}.
+\ref{comparisontest} $(4)$.
 $Ser1640238160$ and $Ser1947554374$ are selected service vertices with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to two concepts $Con103314376$ and $Con2037585750$ respectively, and $Inst658772240$ are the required parameter related to concept $Con2113572083$.
@@
 \fbox{
-\includegraphics[width=8cm]{comparision.pdf}}}
+\includegraphics[width=9cm]{comparisontest.eps}}}
  \caption{Example Comparison of solutions to Task 3 under different approaches.}
- \label{comparison}
-\end{figure}
-\vspace{0.3cm}
-\begin{figure}
-\centerline{
-\fbox{
-\includegraphics[width=4cm]{comparisontaxonomy.pdf}}}
- \caption{Example Comparison of Edge 4 in Task 3 solution under two methods.}
- \label{comparisontaxonomy}
+ \label{comparisontest}
 \end{figure}
@@
 \fbox{
-\includegraphics[width=12cm]{convergency.pdf}}}
+\includegraphics[width=12cm]{convergency.eps}}}
  \caption{Average Fitness, Average MatchType Quality, Average Similarity quality and Average QoS per generation with comprehensive quality optimum}

### 2016-11-15 paper.tex
after cut

@@
 \title{Comprehensive quality - aware Automated Semantic Web Service Composition}
-
-\author{Chen Wang, Hui Ma, and Aaron Chen}
-\institute{School of Engineering and Computer Science,
-\\Victoria University of Wellington, New Zealand \\
-\email{\{Chen.Wang, Hui.Ma, and Aaron.Chen\}@ecs.vuw.ac.nz }}
-
 \makeatletter
@@
 \section{Introduction}\label{introduction}
-Service-oriented computing (SOC) is a novel computing paradigm that employs services as fundamental elements to achieve agile development of cost-efficient and integratable enterprise applications in heterogeneous environments \cite{papazoglou2003service}.
-Service Oriented Architecture (SOA) is capable of abstractly realising service-oriented computing.
-Since its inception, SOA has been contributing to the reuse of software components, from functions to units, and from units to services during the development in SOA \cite{booth2004web}.
-One of the most typical realisations of SOA is \textit{web service}, which is designated as ``modular, self-describing, self-contained applications that are available on the Internet'' \cite{curbera2001web}.
-Several standards play a significant role in registering, enquiring and grounding web services including particularly UDDI, WSDL and SOAP \cite{fensel2011semantic}.
 
@@
  \item To propose a PSO-based service composition algorithm that utilises the proposed quality model.
-In PSO, weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively represent the solutions of semantic web service composition in the searching space, and the weighted graph solutions are decoded from an optimised service queue with the consideration of the proposed comprehensive quality.
+To do that we will first propose a representation of semantic service composition, which can model the quality of semantic matchmaking and QoS with the representation.
+A particle is then used to represent a queue of services that can be used to generate a near-optimised semantic service composition solution.
 
@@
 However few researchers addressed both functional and nonfunctional requirements at the same time in web service composition.
-To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing} reported some recent attempts over published.
-Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output parameter concepts of web services to ensure a semantic matchmaking.
-It is considered to be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and mapping between two knowledge representations encoded utilising the ontology.
+To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing} reported some recent attempts on service composition that considers both nonfunctional (QoS) and functional (semantic) aspects.
+Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} to search for services that ensure semantic matching utilising an ontology of the corresponding domain.
 
-In \cite{shet2012new}, three approaches have been studied regarding the similarity measures using taxonomies: $(1)$ The first one is based on nodes, in which similarity is determined by the information content of the nodes; $(2)$ the second is entirely based on edge, where concept distance in a hierarchy structure is evaluated, and $(3)$ the hybrid approach features a combination of $(1)$ and $(2)$.
-A new similarity measure based on edge counting in taxonomy is introduced in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}.
+In \cite{shet2012new}, three approaches have been studied regarding the similarity measures using taxonomies: The first one is based on nodes, in which similarity is determined by the information content of the nodes; the second is entirely based on edge, where concept distance in a hierarchy structure is evaluated, and third one is the hybrid approach features a combination of these two.
+A similarity measure based on edge counting in taxonomy is introduced in \cite{shet2012new}, which extends similarity measure defined in \cite{wu1994verbs}.
 Neighbourhood concepts are considered in their model when $\lambda$ = 1 (default value as 0).
@@
 
-The paper \cite{fanjiang2014semantic} covers the concerns in both functional and non-functional requirements in design time of semantic-based automatic service composition, where a GA-based approach with four unusual independent fitness functions are designed to solve the problems with these concerns.
-In details, a sequence of fitness functions are used in the binary selection of chromosomes, rather than a single objective consisting of both functional and non-functional quality.
+The work \cite{fanjiang2014semantic} concerns both functional and non-functional requirements in design time of semantic-based automatic service composition, where a GA-based approach with four unusual independent fitness functions are designed to solve the problems with these concerns.
+A sequence of fitness functions are used in the binary selection of chromosomes, rather than a single objective consisting of both functional and non-functional quality.
 Apart from that, match types are ignored in their quality evaluation of semantic matching.
@@
 \textbf{QoS-aware EC approaches}.
-Evolution Computing techniques are widely used to solve optimisation problems.
-Genetic Programming (GP) \cite{da2016particle,da2015graphevol} is a typical EC technique for automated web service composition.
-This GP-based approach utilises tree representations, on which service and constructs are represented as terminal nodes and functional nodes respectively.
+Evolution Computing techniques are widely used to solve optimisation problems, where the search space is big, so that near-optimised solutions can be found in reasonable time.
+Genetic Programming (GP) \cite{da2016particle,da2015graphevol} is a typical EC technique applied to automated web service composition.
+GP-based approaches utilise tree representations, on which service and constructs are represented as terminal nodes and functional nodes respectively.
 The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure.
@@
 \end{figure}
-In this paper, we propose a comprehensive quality model for automated semantic service composition, and optimise both the quality of semantic matchmaking and QoS.
-PSO has shown its efficiency in solving combinatorial optimisation problems.
+In this section, we propose a comprehensive quality model for automated semantic service composition, and optimise both the quality of semantic matchmaking and QoS.
+PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}.
 Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing that often required by GP \cite{da2016particle}.
@@
 		}
-		\textbf{7.} Assign best particle's pBest value to gBest, if better than gBest.\\
+		\textbf{7.} Assign best particle's \emph{pBest} value to \emph{gBest}, if better than gBest.\\
 		\textbf{8.} Calculate the velocity of each particle according to the equation:\\
@@
 In algorithm \ref{novelSteps}, the idea is to translate the particle location produced by PSO into a service queue as an indirect representation of weighted graph, such that finding the best fitness of the weighted graph is to discover the optimised location of the particle in the search space.
-In PSO, the dimension of each particle is equals to the number of relevant web services.
+In PSO, the dimension of each particle equals to the number of relevant web services.
 The index of each services is mapped to a separate location component in a particle.
@@
 The QoS-aware approach record $Q_{mt}$, $Q_{s}$ and utilise fitness function $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$ without considering $MT$ and $S$, in which $Q_(QoS)$ is normalised from 0 to 0.5 to make it comparable to $Q_{QoS}$ in our approach.
-We observe an interesting pattern from the Table \ref{decisionTable} using statistic analysis: mean value of $Q_{mt}$ and $Q_{s}$ at optimum by our approach is consistently higher than those by QoS-aware approach with one exception in Task 2 while the combination of mean $Q_{mt}$ and $Q_{s}$ at optimum in Task 2 is still significantly higher in our approach under statistical anlysis.
+We observe an interesting pattern from Table \ref{decisionTable} using statistic analysis: mean value of $Q_{mt}$ and $Q_{s}$ at optimum by our approach is consistently higher than those by QoS-aware approach with one exception in Task 2 while the combination of mean $Q_{mt}$ and $Q_{s}$ at optimum in Task 2 is still significantly higher in our approach under statistical anlysis.
 Meanwhile, $Q_{QoS}$ generated by QoS-aware approach can obtain a slightly higher value than that of our approach.
@@
 Fig.
-\ref{comparisontest} $(1)$ and $(2)$shows two composition weighted graphs as the solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method respectively.
+\ref{comparisontest} $(1)$ and $(2)$ show two composition weighted graphs as the solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method respectively.
 Two approaches generate exactly the same service workflow structure where those service vertices and edges denoted in red are different.
@@
 \section{Conclusion}\label{conclusion}
-This work introduced a evaluation model for QoS-aware automated semantic automated web service composition that is based on a semantic matchmaking quality extends existing QoS.
+This work introduced an evaluation model for QoS-aware automated semantic automated web service composition that combines quality of semantic matchmaking with QoS.
 The results shows that our comprehensive quality model is proved to obtain better functional quality with a reasonable trade-off in QoS.
-Future works in this area could explore the comprehensive quality with multi-objectives to maximising quality of matchmaking and to optimise QoS, and improve efficiency in calculating semantic quality.
+Future works could explore the comprehensive quality with multi-objectives to maximising the quality of matchmaking and to optimise QoS, and to improve efficiency in calculating semantic matchmaking quality.
 \bibliographystyle{splncs03}

### 2016-11-15 paper.tex
cut update

@@
 \end{abstract}
-
+\vspace{-0.8cm}
 \section{Introduction}\label{introduction}
@@
 \end{enumerate}
-
-The remains of this paper are organised as the following: Sect.
-\ref{relatedWork} provides related works in the semantic web service composition; Sect.
-\ref{qswsc_approach} presents an overview of comprehensive quality-aware semantic automated web service composition consisting of comprehensive quality evaluation model, proposed weighted graphs as solution presention and PSO-based service composition algorithm; Sect.
-\ref{experiment_design} describes the experiments conducted to test the effectiveness of proposed model; Sect.
-\ref{results_analysis} presents and analyses the experiment; Sect.
-\ref{conclusion} concludes our work.
-
+\vspace{-0.8cm}
 \section{Related Work} \label{relatedWork}
@@
 In \cite{shet2012new}, three approaches have been studied regarding the similarity measures using taxonomies: The first one is based on nodes, in which similarity is determined by the information content of the nodes; the second is entirely based on edge, where concept distance in a hierarchy structure is evaluated, and third one is the hybrid approach features a combination of these two.
-A similarity measure based on edge counting in taxonomy is introduced in \cite{shet2012new}, which extends similarity measure defined in \cite{wu1994verbs}.
+A similarity measure based on edge counting in taxonomy is introduced in \cite{shet2012new}.
 Neighbourhood concepts are considered in their model when $\lambda$ = 1 (default value as 0).
 
-In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, one possible measure is applied to the degree of similarity using Common Description rate of a semantic link, where Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are required to be pre-calculated.
-They also chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint.
-Therefore, the quality of the semantic link is estimated as quality criteria $q_{m}$ associated with their corresponding quality of vector $q_{cd}$.
-However, the weakness of semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined ontology in class, class axioms and properties in OWL2.
-This makes it difficult to measure semantic matchmaking quality in most available semantic web services, as it takes huge cost and time for the domain experts to establish required ontology.
+In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links, one possible measure is applied to the degree of similarity using Common Description rate of a semantic link, where Extra Description and Least common subsume are required to be pre-calculated.
+Therefore, the quality of the semantic link is estimated as quality of matching types associated with their corresponding quality of Common Description rate.
+However, the weakness of semantic link quality is that calculation requires well and completely defined ontology in class, class axioms and properties.
+This makes it difficult to measure semantic matchmaking quality as it takes huge cost and time for the domain experts to establish required ontology.
 In comparison, we introduce a more applicable comprehensive quality model in a fully automated approach.
@@
 Weighed graphs are also utilised in PSP to facilitate a new representation of web service composition adopted from \cite{da2016particle}.
-
+\vspace{-0.5cm}
 \section{Problem Description}\label{problemDes}
@@
 \ref{parallel}.
+\vspace{-0.1cm}
 

### 2016-11-15 paper.tex
cut to 16 pages

@@
 \maketitle
+\vspace{-0.8cm}
 
@@
 \end{itemize}
-
+\vspace{-0.5cm}
 \subsection{Quality of Service and Composition Constructs}\label{Quality of Service and Composition Constructs}
@@
 \end{figure}
-
+\vspace{-0.5cm}
 \subsubsection{Sequence construct}
@@
 \ref{sequence}.
+\vspace{-0.5cm}
 \subsubsection{Parallel construct}
@@
 \ref{parallel}.
-\vspace{-0.1cm}
 
+\vspace{-0.5cm}
 \section{Comprehensive quality-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
+
 \begin{figure}[h]
@@
 \end{figure}
+
 In this section, we propose a comprehensive quality model for automated semantic service composition, and optimise both the quality of semantic matchmaking and QoS.
@@
 This PSO-based approach is different from \cite{da2016particle}, as we use weighted graphs as solution presentation.
-
+\vspace{-0.5cm}
 \subsection{Semantic Matchmaking} \label{semantic_matchmaking}
@@
 The purpose of semantic matchmaking is to find more component services that could also potentially satisfy the quality of QoS with good functional quality.
-
-The semantic matchmaking is achieved by utilising OWL2 and OWL-S or other semantic markup languages for web services.
-In this paper, we use MECE (Mediation Contract Extension) \cite{bleul2008self} and OWL-DL.
-MECE is considered to be an alternative semantic annotation for WSDL.
-MECE defines the service-related inputs and outputs with parameter-related concepts.
-OWL-DL is a sublanguage of OWL extended from RDF.
-It specifies semantic information of concepts involved in MECE.
+\vspace{-0.5cm}
 
@@
 \fbox{
-\includegraphics[width=8cm]{weigtedGraphExample.eps}}}
+\includegraphics[width=7cm]{weigtedGraphExample.eps}}}
  \caption{Composition weighted graph solution}
@@
 
+\vspace{-1cm}
 \subsection{Fitness Calculation}
@@
 Therefore, the service composition problem in this paper is treated as a fitness maximisation problem.
-
+\vspace{-0.2cm}
 \begin{equation}
@@
 \noindent where $\sum_{i=1}^{6} w_i = 1$
-\\\\
+\\
+\vspace{-0.2cm}
 \begin{equation}
@@
 \subsection{QoS-aware Semantic Web Service Composition Algorithm} \label{pso_algorithm}
-
+\vspace{-0.5cm}
 \begin{algorithm}[!htb]
@@
 \end{algorithm}
-
+\vspace{-1.5cm}
 \begin{algorithm}[!htb]
@@
 \end{algorithm}
-
+\vspace{-0.8cm}
 The overall algorithm investigated here is made up of a PSO-based web service composition algorithm \ref{novelSteps} and a decoding algorithm \ref{graph_building}, to generate a composition weighted graph, where code lines in blue are different from the algorithm in \cite{da2016particle}.
@@
 In addition, dangling service vertex and edges will be removed.
-
+\vspace{-1cm}
 \section{Experiment Design}\label{experiment_design}
@@
 Also, we extend all the datasets with QoS attributes from service providers to enable our evaluation.
+\vspace{-0.5cm}
 \begin{table}[]
@@
 
+\vspace{-0.5cm}
 We run the experiment on computing grid comprising of 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine.
@@
 In general, weight settings are adjusted according to users' preferences.
-
 \section{Results and Analysis}\label{results_analysis}
@@
 In conclusion, we can perceive that our evaluation could find out better functional quality with a reasonable trade off in QoS.
-
+\vspace{-0.5cm}
 \begin{table}[]
@@
 \end{table}
-
+\vspace{-0.5cm}
 Second, to compare the results generated from two evaluation approaches, we demonstrate an example solution that shows the differences in composite web services obtained through two different methods.
@@
 \fbox{
-\includegraphics[width=9cm]{comparisontest.eps}}}
+\includegraphics[width=12cm]{comparisontest.eps}}}
  \caption{Example Comparison of solutions to Task 3 under different approaches.}
@@
 \end{figure}
-
+\vspace{-1cm}
 \subsection{Convergence Test}\label{convergenceTest}
-
 \begin{figure}[h]

### 2016-11-15 paper.tex
submit version
15 Nov 2016

--- 2016-11-15 paper.tex
@@
 
-\title{Comprehensive quality - aware Automated Semantic Web Service Composition}
+\title{Comprehensive Quality-Aware Automated Semantic Web Service Composition}
 \makeatletter
@@
 Through ontology-based semantics \cite{o2005review}, web services can understand and better collaborate with each other.
-There are many ontologies languages and formats for semantic service descriptions, such as OWL-S \cite{martin2004owl}, WSML \cite{fensel2006enabling}, and SAWSDL \cite{lausen2007semantic}, which make ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments.
+There are many ontologies languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}, which make ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments.
 The second challenge $(2)$ is related to finding \textit{optimised solutions} to Quality of Service ($QoS$).
@@
 \begin{tabular}{p{0.6\linewidth}}
-\space\hfill\includegraphics[width=2in]{sequence.eps}\hfill\space\\[0.2cm]
+\space\hfill\includegraphics[width=2in]{sequence.pdf}\hfill\space\\[0.2cm]
 $T=\sum\limits^m_{n=1}t_n$ \hfill $C=\sum\limits^m_{n=1}c_n$ \hfill
@@
 \begin{tabular}{p{0.6\linewidth}}
-\space\hfill\includegraphics[width=1.4in]{parallel.eps}\hfill\space\\[0.2cm]
+\space\hfill\includegraphics[width=1.4in]{parallel.pdf}\hfill\space\\[0.2cm]
 \space\hfill$T=MAX\{t_n|n\in\{1,\ldots,m\}\}$\hfill\space\\[0.2cm]
@@
 \ref{parallel}.
-\vspace{-0.1cm}
 
+\vspace{-0.5cm}
 \section{Comprehensive quality-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
+
 \begin{figure}[h]
-\centerline{
-\fbox{
-\includegraphics[width=12cm]{overview.eps}}}
+\centering
+\fbox{\includegraphics[scale=.35]{overview.pdf}}
  \caption{Overview of the proposed approach.}
@@
 It specifies semantic information of concepts involved in MECE.
-
+\vspace{-0.5cm}
 \subsection{Comprehensive Quality Model and Aggregation Matrix}\label{qualityModel}
@@
 \begin{figure}[h]
-\centerline{
-\fbox{
-\includegraphics[width=8cm]{weigtedGraphExample.eps}}}
+\centering
+\fbox{\includegraphics[scale=.29]{weigtedGraphExample.pdf}}
  \caption{Composition weighted graph solution}
@@
 In addition, dangling service vertex and edges will be removed.
-
+\vspace{-0.5cm}
 \section{Experiment Design}\label{experiment_design}
@@
 In general, weight settings are adjusted according to users' preferences.
-
 \section{Results and Analysis}\label{results_analysis}
+\vspace{-0.2cm}
 \subsection{Comparison Test}\label{comparisonTest}
-
 In this section, we analyse the composition solution generated by using our approach comparing with QoS-aware approach.
@@
 \end{table}
+\vspace{-0.5cm}
 
@@
 It is obvious that our approach selects the service providing $Inst795998200$ that are closer to the users' requirements suggesting that our method can produce better semantic matchmaking quality.
-
+\vspace{-0.5cm}
 \begin{figure}[h]
-\centerline{
+\centering{
 \fbox{
-\includegraphics[width=9cm]{comparisontest.eps}}}
+\includegraphics[scale=.31]{comparisontest.pdf}}}
  \caption{Example Comparison of solutions to Task 3 under different approaches.}
@@
 \end{figure}
-
+\vspace{-0.5cm}
 \subsection{Convergence Test}\label{convergenceTest}
+To analyse the effectiveness of our approach, we study the convergence rate of the proposed method in this section to understand the convergence rate of five tasks in WSC09.
+We analysis the performances during the whole evolutionary process in Fig.
+\ref{exp_fitnessvalue}, in which experiment results on five tasks are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average QoS for generation 0-99 with optimum.
 
 \begin{figure}[h]
-\centerline{
+\centering{
 \fbox{
-\includegraphics[width=12cm]{convergency.eps}}}
+\includegraphics[scale=.136]{convergency.pdf}}}
  \caption{Average Fitness, Average MatchType Quality, Average Similarity quality and Average QoS per generation with comprehensive quality optimum}
@@
 \end{figure}
-
-To analyse the effectiveness of our approach, we study the convergence rate of the proposed method in this section to understand the convergence rate of five tasks in WSC09.
-We analysis the performances during the whole evolutionary process in Fig.
-\ref{exp_fitnessvalue}, in which experiment results on five tasks are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average QoS for generation 0-99 with optimum.
+\vspace{-0.5cm}
 
@@
 
+\vspace{-0.5cm}
 \section{Conclusion}\label{conclusion}
@@
 Future works could explore the comprehensive quality with multi-objectives to maximising the quality of matchmaking and to optimise QoS, and to improve efficiency in calculating semantic matchmaking quality.
+\vspace{-0.5cm}
 \bibliographystyle{splncs03}

### 2017-01-24 paper.tex
up
formatings

@@
-\documentclass{llncs}
+\documentclass{IEEEtran}
 \usepackage[ruled,vlined]{algorithm2e}
@@
 \centering
-\fbox{\includegraphics[scale=.35]{overview.pdf}}
+\fbox{\includegraphics[scale=.27]{overview.pdf}}
  \caption{Overview of the proposed approach.}
@@
 \multicolumn{3}{c|}{Composition Construct}                                      & Sequence                             & Parallel \\ \hline
-\multirow{5}{*}{QualityFactors} & \multirow{2}{*}{Functional}    & $Q(e_ {mt})$  &$\prod_{n=1}^{m} q(e_ {mt})$          &  $\prod_{n=1}^{m} q(e_ {mt})$ \\ \cline{3-5}
+\multirow{5}{*}{Quality} & \multirow{2}{*}{F}    & $Q(e_ {mt})$  &$\prod_{n=1}^{m} q(e_ {mt})$          &  $\prod_{n=1}^{m} q(e_ {mt})$ \\ \cline{3-5}
                                 &                                & $Q(e_ {s})$  & $(\sum_{n=1}^m q(e_ {s}))/m$        &  $(\sum_{n=1}^m q(e_ {s}))/m$  \\ \cline{2-5}   
-                                & \multirow{4}{*}{NonFunctional} & $Q(v_{a})$    & $\prod_{n=1}^{m} q(v_a)$             &  $\prod_{n=1}^{m} q(v_a)$ \\ \cline{3-5} 
+                                & \multirow{4}{*}{NF} & $Q(v_{a})$    & $\prod_{n=1}^{m} q(v_a)$             &  $\prod_{n=1}^{m} q(v_a)$ \\ \cline{3-5} 
                                 &                                & $Q(v_{r})$    & $\prod_{n=1}^{m} q(v_r)$             &  $\prod_{n=1}^{m} q(v_r)$ \\ \cline{3-5} 
@@
 
-\vspace{-1cm}
 \subsection{Fitness Calculation}
@@
 \subsection{QoS-aware Semantic Web Service Composition Algorithm} \label{pso_algorithm}
-\vspace{-0.5cm}
 \begin{algorithm}[!htb]
@@
 \label{novelSteps}
+
 \end{algorithm}
-\vspace{-1.5cm}
 \begin{algorithm}[!htb]
@@
 \end{algorithm}
-\vspace{-0.8cm}
+
 The overall algorithm investigated here is made up of a PSO-based web service composition algorithm \ref{novelSteps} and a decoding algorithm \ref{graph_building}, to generate a composition weighted graph, where code lines in blue are different from the algorithm in \cite{da2016particle}.
@@
 Also, we extend all the datasets with QoS attributes from service providers to enable our evaluation.
-\vspace{-0.5cm}
+
 \begin{table}[]
@@
 
-\vspace{-0.5cm}
 We run the experiment on computing grid comprising of 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine.
@@
 \section{Results and Analysis}\label{results_analysis}
-\vspace{-0.2cm}
 \subsection{Comparison Test}\label{comparisonTest}
@@
 In conclusion, we can perceive that our evaluation could find out better functional quality with a reasonable trade off in QoS.
-\vspace{-0.5cm}
 \begin{table}[]
@@
 \end{table}
-\vspace{-0.5cm}
 
@@
 It is obvious that our approach selects the service providing $Inst795998200$ that are closer to the users' requirements suggesting that our method can produce better semantic matchmaking quality.
-\vspace{-0.5cm}
+
 \begin{figure}[h]
@@
 \fbox{
-\includegraphics[scale=.31]{comparisontest.pdf}}}
+\includegraphics[scale=.22]{comparisontest.pdf}}}
  \caption{Example Comparison of solutions to Task 3 under different approaches.}
@@
 \end{figure}
-\vspace{-0.5cm}
 \subsection{Convergence Test}\label{convergenceTest}
@@
 \fbox{
-\includegraphics[scale=.136]{convergency.pdf}}}
+\includegraphics[scale=.095]{convergency.pdf}}}
  \caption{Average Fitness, Average MatchType Quality, Average Similarity quality and Average QoS per generation with comprehensive quality optimum}
@@
 \end{figure}
-\vspace{-0.5cm}
-
 Firstly, the average fitness value with optimum is calculated by averaging the best fitness found in each generation over 30 independent runs.
@@
 
-\vspace{-0.5cm}
 \section{Conclusion}\label{conclusion}
@@
 Future works could explore the comprehensive quality with multi-objectives to maximising the quality of matchmaking and to optimise QoS, and to improve efficiency in calculating semantic matchmaking quality.
-\vspace{-0.5cm}
-\bibliographystyle{splncs03}
-\bibliography{bibliography}
+\bibliographystyle{IEEEtran}
+\bibliography{IEEEexample}
 

### 2017-01-24 paper.tex
update

@@
 \title{Comprehensive Quality-Aware Automated Semantic Web Service Composition}
+\author{\IEEEauthorblockN{Michael Shell}
+\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
+Georgia Institute of Technology\\
+Atlanta, Georgia 30332--0250\\
+Email: http://www.michaelshell.org/contact.html}
+\and
+\IEEEauthorblockN{Homer Simpson}
+\IEEEauthorblockA{Twentieth Century Fox\\
+Springfield, USA\\
+Email: homer@thesimpsons.com}
+\and
+\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
+\IEEEauthorblockA{Starfleet Academy\\
+San Francisco, California 96678--2391\\
+Telephone: (800) 555--1212\\
+Fax: (888) 555--1212}}
 \makeatletter
-\usepackage[pdfauthor={\@author}, pdftitle={\@title}]{hyperref}
-\makeatother
+%\usepackage[pdfauthor={\@author}, pdftitle={\@title}]{hyperref}
+%\makeatother
 
-\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}}
+%\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}}
 
@@
 \end{enumerate}
-\vspace{-0.8cm}
+
 \section{Related Work} \label{relatedWork}
@@
 Weighed graphs are also utilised in PSP to facilitate a new representation of web service composition adopted from \cite{da2016particle}.
-\vspace{-0.5cm}
 \section{Problem Description}\label{problemDes}
@@
 \end{figure}
-\vspace{-0.5cm}
 \subsubsection{Sequence construct}
@@
 \ref{sequence}.
-\vspace{-0.5cm}
 \subsubsection{Parallel construct}
@@
 
-\vspace{-0.5cm}
 \section{Comprehensive quality-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
 
-\begin{figure}[h]
+\begin{figure*}[h]
 \centering
-\fbox{\includegraphics[scale=.27]{overview.pdf}}
+\fbox{\includegraphics[scale=.4]{overview.pdf}}
  \caption{Overview of the proposed approach.}
  \label{overview}
-\end{figure}
+\end{figure*}
 
@@
 This PSO-based approach is different from \cite{da2016particle}, as we use weighted graphs as solution presentation.
-\vspace{-0.5cm}
 \subsection{Semantic Matchmaking} \label{semantic_matchmaking}
@@
 In addition, dangling service vertex and edges will be removed.
-\vspace{-0.5cm}
 \section{Experiment Design}\label{experiment_design}
@@
 In general, weight settings are adjusted according to users' preferences.
+
 \section{Results and Analysis}\label{results_analysis}
-\subsection{Comparison Test}\label{comparisonTest}
+\subsection{Comparison Test with QoS Evaluation Model}\label{comparisonTest}
 In this section, we analyse the composition solution generated by using our approach comparing with QoS-aware approach.
@@
 \end{figure}
+
+\subsection{Comparison Test with GP-based approach}\label{comparisonTestWithGP}
+We compare a GP-based approach  \cite{ma2015hybrid} with our PSO method, where the individual is a tree structure transferred from a DAG employing unfolding techniques.
+We further mark all the tree nodes in the representation with its outgoing edges for semantic matchmaking quality, and those edges information are maintained correctly throughout the evolutionary process.
+At last, we evaluate both semantic matchmaking quality and QoS simultaneously using the discussed the comprehensive quality model to investigate the performances of both GP-based approaches and PSO-based approach.
+To make a fair comparison with our PSO approach that the same number of evaluations (3000 times) should be considered, we adjust the parameters settings for GP approach \cite{ma2015hybrid} to 30 individual for 100 generations.
+\begin{table}[]
+\centering
+\caption{Mean fitness results for comparing GP-based approach}
+\label{meanFitness}
+\begin{tabular}{l|l|l}
+\hline
+\multicolumn{1}{c|}{Dataset} & PSO-based approach & GP-based approach  \\ \hline
+WSC09 01                     &0.559207 $\pm$ 0.012780 $\uparrow$      &0.518411 $\pm$ 0.018470               \\ \hline
+WSC09 02                     &0.470083 $\pm$  0.001106   &0.471594 $\pm$  0.002436 $\uparrow$           \\ \hline
+WSC09 03                     & 0.559207 $\pm$ 0.012780 $\pm$ $\uparrow$  &0.552947 $\pm$ 0.007094            \\ \hline
+WSC09 04                     & 0.468942 $\pm$ 0.001670 $\pm$ $\uparrow$  &0.442934 $\pm$ 0.010154            \\ \hline
+WSC09 05                     & 0.469424 $\pm$ 0.000800 $\pm$ $\uparrow$  &0.256425 $\pm$ 0.038916            \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[]
+\centering
+\caption{Mean time results for comparing GP-based approach}
+\label{meanTime}
+\begin{tabular}{l|l|l}
+\hline
+\multicolumn{1}{c|}{Dataset} & PSO-based approach & GP-based approach  \\ \hline
+WSC09 01                     &12907.533333 $\pm$ 8105.111787      &5168.166667 $\pm$ 520.475319 $\downarrow$                \\ \hline
+WSC09 02                     &292346.400000 $\pm$  96726.846023 $\uparrow$   &27483.100000 $\pm$  3083.391833           \\ \hline
+WSC09 03                     & 12907.533333 $\pm$ 8105.111787 $\pm$ $\uparrow$  &28053.166667 $\pm$ 3202.059629            \\ \hline
+WSC09 04                     & 6553640.033333 $\pm$ 1468203.652702 $\pm$ $\uparrow$  &540418.366667 $\pm$ 186540.432797            \\ \hline
+WSC09 05                     & 1208192.500000 $\pm$ 266911.585694 $\pm$ $\uparrow$  &180408.366667 $\pm$ 435246.958095            \\ \hline
+\end{tabular}
+\end{table}
+
 \subsection{Convergence Test}\label{convergenceTest}

### 2017-01-25 paper.tex
up

@@
 \title{Comprehensive Quality-Aware Automated Semantic Web Service Composition}
-\author{\IEEEauthorblockN{Michael Shell}
-\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
-Georgia Institute of Technology\\
-Atlanta, Georgia 30332--0250\\
-Email: http://www.michaelshell.org/contact.html}
-\and
-\IEEEauthorblockN{Homer Simpson}
-\IEEEauthorblockA{Twentieth Century Fox\\
-Springfield, USA\\
-Email: homer@thesimpsons.com}
-\and
-\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
-\IEEEauthorblockA{Starfleet Academy\\
-San Francisco, California 96678--2391\\
-Telephone: (800) 555--1212\\
-Fax: (888) 555--1212}}
-\makeatletter
-%\usepackage[pdfauthor={\@author}, pdftitle={\@title}]{hyperref}
-%\makeatother
+ \author{Chen Wang, Hui Ma, Aaron Chen\\ School of
+ Engineering and Computer Science, Victoria University of Wellington, New Zealand\\
+Email: chen.wang@ecs.vuw.ac.nz, hui.ma@ecs.vuw.ac.nz, aaron.chen@ecs.vuw.ac.nz}
+
+\usepackage[pdfauthor={\@author}, pdftitle={\@title}]{hyperref}
+\makeatother
 
 %\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}}
+\vspace{-1.5cm}
 
 \begin{document}
-
 \maketitle
-\vspace{-0.8cm}
-
 \begin{abstract}
@@
 \multicolumn{1}{c|}{Dataset} & PSO-based approach & GP-based approach  \\ \hline
-WSC09 01                     &12907.533333 $\pm$ 8105.111787      &5168.166667 $\pm$ 520.475319 $\downarrow$                \\ \hline
-WSC09 02                     &292346.400000 $\pm$  96726.846023 $\uparrow$   &27483.100000 $\pm$  3083.391833           \\ \hline
-WSC09 03                     & 12907.533333 $\pm$ 8105.111787 $\pm$ $\uparrow$  &28053.166667 $\pm$ 3202.059629            \\ \hline
-WSC09 04                     & 6553640.033333 $\pm$ 1468203.652702 $\pm$ $\uparrow$  &540418.366667 $\pm$ 186540.432797            \\ \hline
-WSC09 05                     & 1208192.500000 $\pm$ 266911.585694 $\pm$ $\uparrow$  &180408.366667 $\pm$ 435246.958095            \\ \hline
+WSC09 01                     &12907 $\pm$ 8105      &5168 $\pm$ 520 $\downarrow$                \\ \hline
+WSC09 02                     &292346 $\pm$  96727    &27483 $\pm$  3083 $\downarrow$          \\ \hline
+WSC09 03                     & 12908 $\pm$ 8105   &28053 $\pm$ 3202 $\downarrow$           \\ \hline
+WSC09 04                     & 6553640 $\pm$ 1468204   &540418 $\pm$ 186540 $\downarrow$            \\ \hline
+WSC09 05                     & 1208193 $\pm$ 266916   &180408 $\pm$ 435247 $\downarrow$           \\ \hline
 \end{tabular}

### 2017-01-25 paper.tex
up

@@
 
+\subsection{Convergence Test}\label{convergenceTest}
+To analyse the effectiveness of our approach, we study the convergence rate of the proposed method in this section to understand the convergence rate of five tasks in WSC09.
+We analysis the performances during the whole evolutionary process in Fig.
+\ref{exp_fitnessvalue}, in which experiment results on five tasks are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average QoS for generation 0-99 with optimum.
+
+\begin{figure}[h]
+\centering{
+\fbox{
+\includegraphics[scale=.095]{convergency.pdf}}}
+ \caption{Average Fitness, Average MatchType Quality, Average Similarity quality and Average QoS per generation with comprehensive quality optimum}
+ \label{exp_fitnessvalue}
+\end{figure}
+Firstly, the average fitness value with optimum is calculated by averaging the best fitness found in each generation over 30 independent runs.
+We can see that there is a significant increase in the fitness values towards optimum between generation 0 and generation 15-25, the remaining generation continues to produce a steady but moderate improvement in the fitness value and eventually reach a plateau with no further improvements can be observed.
+The same behaviour is observed over the rest tasks.
+
+We also investigate the variation of quality of semantic matchmaking where average matchType quality with optimum and average similarity quality with optimum are studied from generation 0 to 99 in second and third column groups of Fig.
+\ref{exp_fitnessvalue}.
+In these subfigures, both the average matchType quality with optimum and average similarity quality with optimum refers to the mean values of the quality values associated to the best fitness value found in each generation over 30 independent runs.
+Similar to the fitness values, clear evidence of fast convergence can be observed with respect to theses quality values.
+This observation is also consistent for the improvement of mean QoS quality with optimum shown in the last column in Fig \ref{exp_fitnessvalue}.
+Additionally, we don't see too much trade-off from the QoS as the a consistently increase in semantic matchmaking quality is observed.
+
 \subsection{Comparison Test with GP-based approach}\label{comparisonTestWithGP}
@@
 To make a fair comparison with our PSO approach that the same number of evaluations (3000 times) should be considered, we adjust the parameters settings for GP approach \cite{ma2015hybrid} to 30 individual for 100 generations.
+
+The Table \ref{meanFitness} shows the mean fitness values accomplished by two approaches and Table \ref{meanTime} shows the mean execution time required by them.
+We employ statistical analysis to test the significant differences in mean fitness value and execution time.
+The results show that the PSO-based approach performs better in four of five tasks.
+
 \begin{table}[]
@@
 WSC09 02                     &292346 $\pm$  96727    &27483 $\pm$  3083 $\downarrow$          \\ \hline
-WSC09 03                     & 12908 $\pm$ 8105   &28053 $\pm$ 3202 $\downarrow$           \\ \hline
+WSC09 03                     & 12908 $\pm$ 8105 $\downarrow$  &28053 $\pm$ 3202            \\ \hline
 WSC09 04                     & 6553640 $\pm$ 1468204   &540418 $\pm$ 186540 $\downarrow$            \\ \hline
@@
 
-\subsection{Convergence Test}\label{convergenceTest}
-To analyse the effectiveness of our approach, we study the convergence rate of the proposed method in this section to understand the convergence rate of five tasks in WSC09.
-We analysis the performances during the whole evolutionary process in Fig.
-\ref{exp_fitnessvalue}, in which experiment results on five tasks are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average QoS for generation 0-99 with optimum.
+We study the mean fitness value with the optimum for both PSO-based and GP-based approach over 30 independent runs.
+Fig.
+\ref{psovsgp} is an example of convergence rate performance in WSC09 03, which shows the behaviour of PSO-based approach manifests the characteristics of fast convergence and reaches a better-optimised solution, while the performance of GP is barely satisfactory.
 
 \begin{figure}[h]
-\centering{
-\fbox{
-\includegraphics[scale=.095]{convergency.pdf}}}
- \caption{Average Fitness, Average MatchType Quality, Average Similarity quality and Average QoS per generation with comprehensive quality optimum}
- \label{exp_fitnessvalue}
+\centering
+\fbox{\includegraphics[scale=.29]{psovsgp.pdf}}
+ \caption{An example of comparing convergency rate from PSO and GP approaches for task 3}
+ \label{psovsgp}
 \end{figure}
-Firstly, the average fitness value with optimum is calculated by averaging the best fitness found in each generation over 30 independent runs.
-We can see that there is a significant increase in the fitness values towards optimum between generation 0 and generation 15-25, the remaining generation continues to produce a steady but moderate improvement in the fitness value and eventually reach a plateau with no further improvements can be observed.
-The same behaviour is observed over the rest tasks.
-
-We also investigate the variation of quality of semantic matchmaking where average matchType quality with optimum and average similarity quality with optimum are studied from generation 0 to 99 in second and third column groups of Fig.
-\ref{exp_fitnessvalue}.
-In these subfigures, both the average matchType quality with optimum and average similarity quality with optimum refers to the mean values of the quality values associated to the best fitness value found in each generation over 30 independent runs.
-Similar to the fitness values, clear evidence of fast convergence can be observed with respect to theses quality values.
-This observation is also consistent for the improvement of mean QoS quality with optimum shown in the last column in Fig \ref{exp_fitnessvalue}.
-Additionally, we don't see too much trade-off from the QoS as the a consistently increase in semantic matchmaking quality is observed.
 

### 2017-01-25 paper.tex
up

@@
 However few researchers addressed both functional and nonfunctional requirements at the same time in web service composition.
-To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing} reported some recent attempts on service composition that considers both nonfunctional (QoS) and functional (semantic) aspects.
+To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some recent attempts on service composition that considers both nonfunctional (QoS) and functional (semantic) aspects.
 Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} to search for services that ensure semantic matching utilising an ontology of the corresponding domain.
@@
 In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions.
+Also, this paper increase the mutation rate while encountering low diversity in the population and adopt a higher crossover probability while trapped in local optimisation.
+
+A hyper approach employs both a greedy search algorithm and genetic programming is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness.
+In particularly, the greedy search is used to the directed acrylic graph as composite solutions, which is further transferred to tree structure using unfolding techniques as the first generation in GP.
+In each individual,  terminal nodes are considered as task inputs,  root node as outputs, and inner nodes as atomic web services.
+During the reproduction process,  a randomly selected node in one individual is replaced with a new subtree generated by a greedy search to perform mutation while same atomic inner nodes in two random chosen individuals are swapped to perform crossover.
 
@@
 It specifies semantic information of concepts involved in MECE.
-\vspace{-0.5cm}
+
+\subsection{Ontology-based Index Cached Optimisation}
+In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively.
+To effectively construct weighted graphs, we pre-calculate semantic matchmaking quality and mark the input-parameter concepts with a set of services.
+The key idea of the index is to create a mapping from the output-related concepts to matched input-related services while considering different levels of match types.
+Furthermore, this index size could also be reduced by only considering parameter-related concepts in the shrunken service repository, which contains  those task-relevant web services.
+This optimised cache also contributes to less and constant time for weighted graph building for the whole evolutionary process.
+
 \subsection{Comprehensive Quality Model and Aggregation Matrix}\label{qualityModel}
@@
 
-The Table \ref{meanFitness} shows the mean fitness values accomplished by two approaches and Table \ref{meanTime} shows the mean execution time required by them.
+The Table \ref{meanFitness} shows the mean fitness values accomplished by two methods and Table \ref{meanTime} shows the average execution time required by them.
 We employ statistical analysis to test the significant differences in mean fitness value and execution time.
 The results show that the PSO-based approach performs better in four of five tasks.
+However, there is also a trade-off between optimised solution and execution time.
+We can see the PSO-based approach takes longer execution time, it due to that the every individual in each generation must be decoded from generated optimised queue, and this process is very time-consuming.
+However,  the initialisation first population in GP-based approach is costly in time as transformation process from a DAG, but following new individuals are generated through mutation and crossover, which are considered be much less time consumed comparing decoding process.
 
@@
 
-We study the mean fitness value with the optimum for both PSO-based and GP-based approach over 30 independent runs.
-Fig.
-\ref{psovsgp} is an example of convergence rate performance in WSC09 03, which shows the behaviour of PSO-based approach manifests the characteristics of fast convergence and reaches a better-optimised solution, while the performance of GP is barely satisfactory.
-
 \begin{figure}[h]
 \centering
-\fbox{\includegraphics[scale=.29]{psovsgp.pdf}}
+\fbox{\includegraphics[scale=.25]{psovsgp.pdf}}
  \caption{An example of comparing convergency rate from PSO and GP approaches for task 3}
@@
 \end{figure}
+
+We also study the average fitness value with the optimum through the evolutionary process for both PSO-based and GP-based approach over 30 independent runs.
+Fig.
+\ref{psovsgp} is an example of convergence rate from Task 3, where the behaviour of PSO-based approach presents a very clear evidence of fast convergence and reaches a better-optimised solution, while the performance of GP is barely satisfactory, as this method improves its fitness value gradually.
 

### 2017-01-25 paper.tex
up

@@
 e.g minimum cost, maximal reliability.
-Many scholars have looked into nonfunctional optimisation problems in QoS-aware web service composition applying AI planning and Evolution Computing techniques.
+Many scholars have looked into nonfunctional optimisation problems in QoS-aware web service composition applying AI planning and Evolutionary Computation techniques.
 To meet users' requirement, one often needs to consider both semantic matching and QoS optimisation simultaneously.
@@
 A lot of works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as \textit{semi-automated Web service composition} approach.
-Meanwhile, many research works consider the possibility of generating a composite plan automatically in discovering and selecting suitable web services, which are deemed to NP-hard \cite{moghaddam2014service}.
+Meanwhile, many research works consider the possibility of generating a composite plan automatically in discovering and selecting suitable web services, which are considered to be NP-hard \cite{moghaddam2014service}.
 \textit{Semantic web services composition} is distinguished from the syntactic service composition, with the hope of eliminating conflicts by the semantic level of web services.
@@
  \item To evaluate the performance of comprehensive quality awareness semantic web service composition by utilising benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
+Also, we make a comparison between PSO-based and an existing GP-based approach employing our proposed comprehensive quality model.
+
 \end{enumerate}
@@
 \textbf{QoS-aware EC approaches}.
-Evolution Computing techniques are widely used to solve optimisation problems, where the search space is big, so that near-optimised solutions can be found in reasonable time.
+Evolutionary Computation techniques are widely used to solve optimisation problems, where the search space is big, so that near-optimised solutions can be found in reasonable time.
 Genetic Programming (GP) \cite{da2016particle,da2015graphevol} is a typical EC technique applied to automated web service composition.

### 2017-01-25 paper.tex
update two references

@@
 Evolutionary Computation techniques are widely used to solve optimisation problems, where the search space is big, so that near-optimised solutions can be found in reasonable time.
-Genetic Programming (GP) \cite{da2016particle,da2015graphevol} is a typical EC technique applied to automated web service composition.
+Genetic Programming (GP) \cite{da2015graphevol} is a typical EC technique applied to automated web service composition.
 GP-based approaches utilise tree representations, on which service and constructs are represented as terminal nodes and functional nodes respectively.
 The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure.
+
+Gupta et al.
+\cite{gupta2015optimization} proposed an improved Genetic Algorithm for QoS-ware web service composition, where some population associated with lower fitness are discarded with bringing in new offerings in each generation.
+
 In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions.
 Also, this paper increase the mutation rate while encountering low diversity in the population and adopt a higher crossover probability while trapped in local optimisation.
+
+A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of Directed Acyclic Graph(DAG) employing Graph-based evolutionary operators like crossover and mutation.
 
@@
 A general graph is used as representation as composite solution in their PSO algorithm considering QoS optimisation.
-However, this solution does not consider distinguished matchmaking quality, which could lead to over-general outputs to be produced by selected services.
+
+Other non-EC techniques are also introduced in QoS-ware web service composition.
+A heuristic service composition method is proposed by Tang et al.
+\cite{qi2010combining} proposed,  named local optimisation and enumeration, which is to filter a small number of promising candidates related to each task by local selection, and all the composite solutions are enumerated to reach the near-to-optimal.
+
+However, composite solutions from \cite{qi2010combining,da2016particle,ma2015hybrid,da2015graphevol,yu2013adaptive} does not consider distinguished matchmaking quality in their fitness function, which might lead to over-general outputs to be produced by selected services, The finding is evidently supported by comparing two different evaluation model in Sect.
+\ref{comparisonTest}.
 In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users.

### 2017-01-26 paper.tex
update all reviewers comments

@@
 Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning.
-QoS optimisation aims to meet non-functional requirement of service users.
-e.g minimum cost, maximal reliability.
+QoS optimisation aims to meet the non-functional requirement of service users.
+E.g., minimum cost, maximal reliability.
 Many scholars have looked into nonfunctional optimisation problems in QoS-aware web service composition applying AI planning and Evolutionary Computation techniques.
@@
 Existing works on web service composition often concerns either semantic service composition or QoS-aware service composition.
-However, there are very few works concerns both quality of semantic matchmaking and quality of services at the same time.
-Therefore, In this paper we consider two quality dimensions in a proposed more applicable comprehensive quality model for semantic web service composition, and present a automated semantic web service composition approach that can generate service composition solutions that meet both functional and non-functional requirement.
-We will evaluate our approach utilising a semantic benchmark dataset.
+However, there are few works concerns both quality of semantic matchmaking and quality of services at the same time and points out the benefits clearly.
+Therefore, In this paper, we consider two quality dimensions in a proposed more applicable comprehensive quality model for semantic web service composition and present an automated semantic web service composition approach that can generate service composition solutions that meet both functional and non-functional requirement.
+The results show our method can find better semantic matchmaking quality with a very slight trade off in QoS.
+Also, we comparing our PSO-based approach with one GP-based approach, our method performs better in finding optimised solution with a trade off in execution time.
 
 \end{abstract}
-\vspace{-0.8cm}
 \section{Introduction}\label{introduction}
@@
 Step 2: This composition goal are used to discover all relevant web services, which lead to a shrunken service repository that is subsequently used by PSO as a searching space.
-Step 3: A weighted graph representation is randomly built up from the an initial service queue that mapped to the particle's location, interleaving with semantic matchmaking process.
+Step 3: A weighted graph representation is randomly built up from the an initial service queue that mapped to the particle's location, interleaving with semantic matchmaking process utilising ontology-based index cache.
 In the weighted graph, graph edges are assigned with semantic matchmaking quality as weights.
@@
 
-\subsection{Ontology-based Index Cached Optimisation}
+\subsection{Ontology-based Index Cached Optimisation}\label{indexCache}
 In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively.
@@
 \subsection{Fitness Calculation}
-The fitness value of a service composition solution is a weighted sum of all the quality related components in Formula (\ref{equation6}), in which fitness value of 1 means the best comprehensive quality and 0 means the worst.
+In real life, given a unique and optimised solution is always easier for customers choose from when many quality criteria involved in the composite solution, rather than provided a set of solutions.
+Therefore, it is very practical to define a single fitness as a weighted sum of all the quality related components in Formula (\ref{equation6}), where weights setting is very flexible, it could be adjusted according to users' preferences.
+The fitness value of 1 means the best comprehensive quality and 0 means the worst.
 For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the fitness value falls within the range from 0 to 1.
@@
 \subsection{QoS-aware Semantic Web Service Composition Algorithm} \label{pso_algorithm}
+
 \begin{algorithm}[!htb]
@@
 		    \textbf{3.} Create queue of services using the particle's position vector.\\
-			\textcolor{blue}{\textbf{4.} Build a weighted graph using the queue.}\\
-			\textcolor{blue}{\textbf{5.} Calculate the fitness of the weighted graph.}\\
+			{\textbf{4.} $WG \leftarrow$ generatedWeigthedGraph().}\\
+			{\textbf{5.} Calculate the $WG$ fitness value.}\\
 			\eIf{fitness value better than pBest}{
@@
 \label{novelSteps}
+\end{algorithm}
 
-\end{algorithm}
-\begin{algorithm}[!htb]
+\begin{algorithm}
  \setlength\hsize{0.9\linewidth}
  \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
- \let\oldnl\nl% Store \nl in \oldnl
-\newcommand{\nonl}{\renewcommand{\nl}{\let\nl\oldnl}}
- \Input{$I$, $O$, $queue$}
- \Output{composition weighted graph $WG$}
- \textbf{1.} Create $start$ vertex with outputs $O$ and $end$ vertex with inputs $I$.\\
- \textbf{2.} Create graph $WG$ containing the $start$ vertex.\\
- \textbf{3.} Create available outputs set containing $start$ outputs.\\
- \While{available outputs do not satisfy $end$ inputs}{
- \textbf{4.} Get next candidate from queue.\\
- \If{candidate inputs are satisfied by available outputs}{
- \textcolor{blue}{\textbf{5.} Create edge assigned with weight.\\}
- \textcolor{blue}{\textbf{6.} Connect vertex to graph with the edge.\\}
- \textbf{7.} Remove it from queue and go back to the queue's beginning.\\
- }}
- \textbf{8.} Connect end vertex.\\
- \textbf{9.} Remove dangling vertices from graph $WG$.\\
- \textcolor{blue}{\textbf{10.} Remove dangling edges from graph $WG$.\\}
- \KwRet $WG$.\\
- \caption{Create a composition weighted graph from a queue}	
+ \SetKwFunction{generateWeightedGraph}{generateWeightedGraph}
+ \SetKwProg{Procedure}{Procedure}{}{}
+ \LinesNumbered
+ \SetNlSty{}{}{:}
+  \Procedure{\generateWeightedGraph{}}{
+ \Input{Task inputs $I$, task outputs $O$, relevant Web services $queue$, IndexCache $IndexCache$}
+ \Output{Weighted Graph $WG$}
+ $WG \leftarrow  null$\;
+ $WG \leftarrow$ new $endNode$(), new $startNode$()\;
+ $OutputSet \leftarrow$ \{$I$\}\;
+  \While {all $O$ $\notin$ $OutputSet$  and $queue !=null$}{
+     \ForEach{$ws$ in $queue$}{
+      \uIf{$ws.inputs$ $\in$ $OutputSet$ }{    
+    		 \ForEach{$I$ in $ws.inputs$}{
+    		$parameter.matchType \leftarrow$ query $IndexCache$\;
+     		$parameter.conceptSiminarity \leftarrow$ query $IndexCache$\;
+              }
+        $WG.edge \leftarrow$ new $Edge$()\;
+        $edge.weights \leftarrow$ aggregation($parameters$)\;
+        $WG \leftarrow$ new $wsNode$()\;
+         $OutputSet$ add \{$ws.outputs$\}\;    
+       $queue$.remove $ws$\;
+       }	
+     }
+  }
+ remove $dangling nodes$\; 
+ remove $dangling edges$\;
+ \KwRet $WG$\;
+ }
+ \vspace{2mm}
+ \caption{Create a composition weighted graph from a queue.}
 \label{graph_building}
@@
 
-The overall algorithm investigated here is made up of a PSO-based web service composition algorithm \ref{novelSteps} and a decoding algorithm \ref{graph_building}, to generate a composition weighted graph, where code lines in blue are different from the algorithm in \cite{da2016particle}.
+The overall algorithm investigated here is made up of a PSO-based web service composition algorithm \ref{novelSteps} and a decoding algorithm \ref{graph_building}, to generate a composition weighted graph.
 In algorithm \ref{novelSteps}, the idea is to translate the particle location produced by PSO into a service queue as an indirect representation of weighted graph, such that finding the best fitness of the weighted graph is to discover the optimised location of the particle in the search space.
@@
 Services in a queue follow the ascending order, from which we decode a weighted graph using Algorithm \ref{graph_building}.
-We select and connect  service vertex to the start vertex from the service queue if the web service can satisfy the output of start vertex.
-Meanwhile, an Output Set is initialised and kept being updated using outputs from the newly added service vertex in the weighted graph, later on, more services vertices are connected with edges if services' inputs could be satisfied by any output in the Output Set.
+We select and connect  service node to the start node from the service queue if the inputs of web service can satisfy the output of start node.
+The edge associated with two connected nodes is also created, the weight of which is also calculated as a quality aggregated value from concept-related parameters.
+Meanwhile, an Output Set is initialised and kept being updated using outputs from the newly added service node in the weighted graph, later on, more services vertices are connected with edges if services' inputs could be satisfied by any output in the Output Set.
 Finally, the end vertex is connected to the graph if the updated Output Set contains all end inputs.
@@
 We configure weight of fitness function to properly balance functional side and nonfunctional side.
-Therefore, $w_{1}$ and $w_{2}$ equal to 0.1 and 0.4,  and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly.
+Therefore, $w_{1}$ and $w_{2}$ are set equally to 0.25, and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly.
 However, the settings of these weight values does not impact the method.
@@
 \fbox{\includegraphics[scale=.25]{psovsgp.pdf}}
- \caption{An example of comparing convergency rate from PSO and GP approaches for task 3}
+ \caption{An example of comparing convergency rate of PSO and GP approaches for task 3}
  \label{psovsgp}
@@
 \section{Conclusion}\label{conclusion}
-This work introduced an evaluation model for QoS-aware automated semantic automated web service composition that combines quality of semantic matchmaking with QoS.
-The results shows that our comprehensive quality model is proved to obtain better functional quality with a reasonable trade-off in QoS.
-Future works could explore the comprehensive quality with multi-objectives to maximising the quality of matchmaking and to optimise QoS, and to improve efficiency in calculating semantic matchmaking quality.
+This work introduced a comprehensive evaluation model for QoS-aware automated semantic automated web service composition that combines the quality of semantic matchmaking with QoS.
+The results show that our comprehensive quality model is proved to obtain better functional quality with a reasonable trade-off in QoS.
+Also, we comparing one GP-approach with our PSO-based method to show our better performance in find more optimised solution.
+Future works could investigate other direct or indirect representations of semantic web service composition on semantic web service composition, and look into more EC techniques to evaluate their performance.
+Also, we could reshape the problem as providing customers with a set of solutions to choose from, rather than a single solution, so the research problem is transferred into multi-objectives or many objective problems.
 \bibliographystyle{IEEEtran}

### 2017-01-26 paper.tex
update

@@
 \section{Related Work} \label{relatedWork}
-\textbf{Semantic web service matchmaking}.
+\textbf{Semantic web service composition}.
 Substantial work \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} on web service composition focused primarily on non-functional requirements consistently neglecting functional requirements.
 However few researchers addressed both functional and nonfunctional requirements at the same time in web service composition.
-To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some recent attempts on service composition that considers both nonfunctional (QoS) and functional (semantic) aspects.
+To the best of our knowledge, \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} reported some recent attempts on service composition that considers both nonfunctional (QoS) and functional (semantic) aspects.
 Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} to search for services that ensure semantic matching utilising an ontology of the corresponding domain.
+
+The combination of enhancing planning graph (EPG) and clonal selection algorithm is introduced in the work \cite{pop2009immune}  to solve web service optimisation problem as an immune-inspired web service composition approach.
+During the clonal selection process, the antigen is represented as a fitness function, and the antibody is represented as a binary alphabet to encode EPG.
+In this work,  semantic matchmaking is considered by measuring the quality of the similarity measure using information retrieval technique.
 
@@
 This PSO-based approach is different from \cite{da2016particle}, as we use weighted graphs as solution presentation.
+
 \subsection{Semantic Matchmaking} \label{semantic_matchmaking}
@@
 In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition.
-This model overcome the disadvantages of current prevailing QoS-aware optimisation \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} that ignores quality of semantic matchmaking.
+This model overcome the disadvantages of current prevailing QoS-aware optimisation that ignores quality of semantic matchmaking.
 
@@
 The QoS-aware approach record $Q_{mt}$, $Q_{s}$ and utilise fitness function $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$ without considering $MT$ and $S$, in which $Q_(QoS)$ is normalised from 0 to 0.5 to make it comparable to $Q_{QoS}$ in our approach.
-We observe an interesting pattern from Table \ref{decisionTable} using statistic analysis: mean value of $Q_{mt}$ and $Q_{s}$ at optimum by our approach is consistently higher than those by QoS-aware approach with one exception in Task 2 while the combination of mean $Q_{mt}$ and $Q_{s}$ at optimum in Task 2 is still significantly higher in our approach under statistical anlysis.
+We observe an interesting pattern from Table \ref{decisionTable} using statistic analysis: mean value of $Q_{mt}$ and $Q_{s}$ at optimum by our approach is consistently higher than those by QoS-aware approach.
 Meanwhile, $Q_{QoS}$ generated by QoS-aware approach can obtain a slightly higher value than that of our approach.
@@
 \multicolumn{2}{c|}{WSC09}              & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
-\multirow{3}{*}{Task1}  &$Q_{mt}$   &0.189787 $\pm$ 0.039278686  &0.220594 $\pm$ 0.009318 $\uparrow$ \\ \cline{2-4} 
-                        &$Q_{s}$    &0.884962 $\pm$ 0.014140   &0.893713 $\pm$ 0.007769  $\uparrow$ \\ \cline{2-4}
-                        &$Q_{QoS}$  &0.278730 $\pm$ 0.007786     &0.279548 $\pm$ 0.007627                          \\ \hline
-\multirow{3}{*}{Task2}  &$Q_{mt}$   &0.001795 $\pm$ 0.000719 $\uparrow$    &0.001135 $\pm$ 0.000633  \\ \cline{2-4} 
-                        &$Q_{s}$    &0.906971 $\pm$ 0.005855     &0.927965 $\pm$ 0.007306 $\uparrow$   \\ \cline{2-4}
-                        &$Q_{QoS}$  &0.239979 $\pm$ 0.000578 $\uparrow$     &0.237845 $\pm$ 0.001439 \\ \hline
-\multirow{3}{*}{Task3}  &$Q_{mt}$   &0.158526 $\pm$ 0.014028               &  0.245830 $\pm$ 0.007761 $\uparrow$   \\ \cline{2-4} 
-                        &$Q_{s}$    &0.949109 $\pm$ 0.002331           &   0.972765 $\pm$ 0.002980 $\uparrow$           \\ \cline{2-4}
-                        &$Q_{QoS}$  &0.247002 $\pm$ 0.000661 $\uparrow$             &  0.245631 $\pm$ 0.000431            \\ \hline
-\multirow{3}{*}{Task4}  &$Q_{mt}$   &0.000000 $\pm$ 0.000000  &0.000001 $\pm$ 0.000002 $\uparrow$ \\ \cline{2-4} 
-                        &$Q_{s}$    &0.880058 $\pm$ 0.006603    &0.930632 $\pm$ 0.009043 $\uparrow$ \\ \cline{2-4}
-                        &$Q_{QoS}$  &0.242338 $\pm$ 0.000516 $\uparrow$    &0.236677 $\pm$ 0.002211  \\ \hline
-\multirow{3}{*}{Task5}  &$Q_{mt}$   &  0.000042 $\pm$ 0.000030     &  0.000078 $\pm$ 0.000031 $\uparrow$           \\ \cline{2-4} 
-                        &$Q_{s}$    &  0.915933 $\pm$ 0.012888      &  0.928189 $\pm$ 0.002486 $\uparrow$                 \\ \cline{2-4}
-                        &$Q_{QoS}$  & 0.238189 $\pm$ 0.000240$\uparrow$      &  0.237232 $\pm$  0.000391  \\ \hline                                                   
+\multirow{3}{*}{Task1}  &$Q_{mt}$   &0.189787 $\pm$ 0.039278686            &0.221862 $\pm$ 0.009582 $\uparrow$ \\ \cline{2-4} 
+                        &$Q_{s}$    &0.884962 $\pm$ 0.014140               &0.894082 $\pm$ 0.009206 $\uparrow$ \\ \cline{2-4}
+                        &$Q_{QoS}$  &0.278730 $\pm$ 0.007786               &0.280222 $\pm$ 0.008212                          \\ \hline
+\multirow{3}{*}{Task2}  &$Q_{mt}$   &0.001795 $\pm$ 0.000719               &0.001977 $\pm$ 0.001566 $\uparrow$ \\ \cline{2-4} 
+                        &$Q_{s}$    &0.906971 $\pm$ 0.005855               &0.923970 $\pm$ 0.006898 $\uparrow$   \\ \cline{2-4}
+                        &$Q_{QoS}$  &0.239979 $\pm$ 0.000578 $\uparrow$    &0.238596 $\pm$ 0.001264 \\ \hline
+\multirow{3}{*}{Task3}  &$Q_{mt}$   &0.158526 $\pm$ 0.014028               &0.245830 $\pm$ 0.007761 $\uparrow$   \\ \cline{2-4} 
+                        &$Q_{s}$    &0.949109 $\pm$ 0.002331               &0.972765 $\pm$ 0.002980 $\uparrow$           \\ \cline{2-4}
+                        &$Q_{QoS}$  &0.247002 $\pm$ 0.000661 $\uparrow$    &0.245631 $\pm$ 0.000431            \\ \hline
+\multirow{3}{*}{Task4}  &$Q_{mt}$   &0.000000 $\pm$ 0.000000               &0.000004 $\pm$ 0.000002 $\uparrow$ \\ \cline{2-4} 
+                        &$Q_{s}$    &0.879514 $\pm$ 0.007456               &0.920733 $\pm$ 0.000001 $\uparrow$ \\ \cline{2-4}
+                        &$Q_{QoS}$  &0.242297 $\pm$ 0.000507 $\uparrow$    &0.236677 $\pm$ 0.002211  \\ \hline
+\multirow{3}{*}{Task5}  &$Q_{mt}$   &  0.000042 $\pm$ 0.000030             &0.000078 $\pm$ 0.000020 $\uparrow$           \\ \cline{2-4} 
+                        &$Q_{s}$    &  0.915933 $\pm$ 0.012888             &0.927678 $\pm$ 0.002578 $\uparrow$                 \\ \cline{2-4}
+                        &$Q_{QoS}$  & 0.238189 $\pm$ 0.000240 $\uparrow$      &  0.237485 $\pm$  0.000328  \\ \hline                                                   
 \end{tabular}

### 2017-01-26 paper.tex
update

@@
 Semantic web service composition has been a prevailing research area in recent years.
-There are two major governance challenges faced by researchers (semantic matching and QoS optimisation).
+There are two major governance challenges faced by researchers (semantic matchmaking and QoS optimisation).
 Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning.
-QoS optimisation aims to meet the non-functional requirement of service users.
+QoS optimisation aims to optimise the non-functional requirement of service users.
 E.g., minimum cost, maximal reliability.
 Many scholars have looked into nonfunctional optimisation problems in QoS-aware web service composition applying AI planning and Evolutionary Computation techniques.
-To meet users' requirement, one often needs to consider both semantic matching and QoS optimisation simultaneously.
+To meet users' requirement, one often needs to consider both semantic matchmaking quality and QoS simultaneously.
 Existing works on web service composition often concerns either semantic service composition or QoS-aware service composition.
@@
 The results show our method can find better semantic matchmaking quality with a very slight trade off in QoS.
-Also, we comparing our PSO-based approach with one GP-based approach, our method performs better in finding optimised solution with a trade off in execution time.
+Also, our method performs better in finding optimised solution with a trade off in execution time comparing an existing GP-based method.
 
@@
 Two most notable challenges for web service composition are $(1)$ ensuring interoperability of services and $(2)$ achieving QoS optimisation \cite{fensel2011semantic}.
-\textit{Interoperability} of web services presents challenge $(1)$ in syntactic and semantics dimensions \cite{fensel2011semantic}.
+\textit{Interoperability} of web services presents challenge $(1)$ in syntactic and semantics dimensions.
 The syntactic dimension is covered by the XML-based technologies (such as $WSDL$, $SOAP$).
@@
 \textit{Semantic web services composition} is distinguished from the syntactic service composition, with the hope of eliminating conflicts by the semantic level of web services.
-In the past few years, substantial works have been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}.
+In the past few years, substantial works have been done on semantic web service composition \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune}.
 However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously.
 To a given service request, the quality of service composition solution depends on both QoS and quality of semantic matchmaking.
-Therefore, a comprehensive quality model is needed to measure the quality of service composition solution.
+Therefore, a comprehensive quality model is needed to be addressed, and more methods are needed to be applied specifically on the problem that optimises semantic matchmaking quality and QoS simultaneously.
 
 The overall goal of this paper is to \textit{develop an comprehensive quality-aware automated semantic web service composition that satisfactorily optimises both functional and non-functional requirements}.
-Particularly, this paper extends existing works on semantic service composition and QoS-aware service composition by considering both QoS optimisation and semantic matching optimisation in our comprehensive quality model.
-Particle Swarm Optimisation (PSO) has show its promise in searching near-optimised service composition solution \cite{da2016particle}, we will propose a PSO-based service composition approach using our comprehensive quality model, which is considered to be more applicable way to measure semantic matchmaking in automated semantic web service composition.
+Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matching optimisation in our proposed comprehensive quality model.
+Particle Swarm Optimisation (PSO) has show its promise in searching near-optimised service composition solution \cite{da2016particle}, we will propose a PSO-based service composition approach using our comprehensive quality model, which is also considered to be more applicable way to measure semantic matchmaking in automated semantic web service composition.
 We will achieve three objectives in this work as follows:
@@
 \begin{enumerate}
- \item To propose a comprehensive quality model that address QoS and semantic matchmaking quality in considering different matching types with corresponding semantic similarity.
-This approach is consider to be a more applicable and effective way of finding an optimised solution in semantic web service composition.
+ \item To propose a comprehensive quality model that address QoS and semantic matchmaking quality in considering different matching types with corresponding concept similarity.
+This method is consider to be a more applicable and effective way of finding an optimised solution in semantic web service composition.
 
  \item To propose a PSO-based service composition algorithm that utilises the proposed quality model.
-To do that we will first propose a representation of semantic service composition, which can model the quality of semantic matchmaking and QoS with the representation.
-A particle is then used to represent a queue of services that can be used to generate a near-optimised semantic service composition solution.
+To do that we will first propose a representation of semantic service composition, which can model the quality of semantic matchmaking and QoS together.
+A particle is then used to represent a queue of services that can be used to decoded into a near-optimised semantic service composition solution.
 
@@
 \textbf{Semantic web service composition}.
-Substantial work \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} on web service composition focused primarily on non-functional requirements consistently neglecting functional requirements.
+Substantial work \cite{da2016particle,bansal2016generalized,mier2015integrated,da2015graphevol,yu2013adaptive} on web service composition focused primarily on non-functional requirements consistently neglecting functional requirements.
 However few researchers addressed both functional and nonfunctional requirements at the same time in web service composition.
@@
 
-The combination of enhancing planning graph (EPG) and clonal selection algorithm is introduced in the work \cite{pop2009immune}  to solve web service optimisation problem as an immune-inspired web service composition approach.
+The combination of enhancing planning graph (EPG) and clonal selection algorithm is introduced in the work \cite{pop2009immune} as an immune-inspired web service composition approach.
 During the clonal selection process, the antigen is represented as a fitness function, and the antibody is represented as a binary alphabet to encode EPG.
 In this work,  semantic matchmaking is considered by measuring the quality of the similarity measure using information retrieval technique.
-
-In \cite{shet2012new}, three approaches have been studied regarding the similarity measures using taxonomies: The first one is based on nodes, in which similarity is determined by the information content of the nodes; the second is entirely based on edge, where concept distance in a hierarchy structure is evaluated, and third one is the hybrid approach features a combination of these two.
-A similarity measure based on edge counting in taxonomy is introduced in \cite{shet2012new}.
-Neighbourhood concepts are considered in their model when $\lambda$ = 1 (default value as 0).
 
@@
 A sequence of fitness functions are used in the binary selection of chromosomes, rather than a single objective consisting of both functional and non-functional quality.
-Apart from that, match types are ignored in their quality evaluation of semantic matching.
+Apart from that, semantic matching types are ignored in their quality evaluation of semantic matching.
 
-\textbf{QoS-aware EC approaches}.
+\textbf{QoS-aware web service composition}.
 Evolutionary Computation techniques are widely used to solve optimisation problems, where the search space is big, so that near-optimised solutions can be found in reasonable time.
-Genetic Programming (GP) \cite{da2015graphevol} is a typical EC technique applied to automated web service composition.
-GP-based approaches utilise tree representations, on which service and constructs are represented as terminal nodes and functional nodes respectively.
-The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure.
 
@@
 \cite{gupta2015optimization} proposed an improved Genetic Algorithm for QoS-ware web service composition, where some population associated with lower fitness are discarded with bringing in new offerings in each generation.
-
 In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions.
 Also, this paper increase the mutation rate while encountering low diversity in the population and adopt a higher crossover probability while trapped in local optimisation.
-
+A hyper approach employs both a greedy search algorithm and genetic programming is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness.
+In particularly, the greedy search is used to generate directed acrylic graph as composite solutions, which is further transferred to tree structure using unfolding techniques for initialisation and mutation during the evolutionary process.
 A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of Directed Acyclic Graph(DAG) employing Graph-based evolutionary operators like crossover and mutation.
-
-A hyper approach employs both a greedy search algorithm and genetic programming is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness.
-In particularly, the greedy search is used to the directed acrylic graph as composite solutions, which is further transferred to tree structure using unfolding techniques as the first generation in GP.
-In each individual,  terminal nodes are considered as task inputs,  root node as outputs, and inner nodes as atomic web services.
-During the reproduction process,  a randomly selected node in one individual is replaced with a new subtree generated by a greedy search to perform mutation while same atomic inner nodes in two random chosen individuals are swapped to perform crossover.
-
 To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}.
@@
 
-However, composite solutions from \cite{qi2010combining,da2016particle,ma2015hybrid,da2015graphevol,yu2013adaptive} does not consider distinguished matchmaking quality in their fitness function, which might lead to over-general outputs to be produced by selected services, The finding is evidently supported by comparing two different evaluation model in Sect.
+However, composite solutions from \cite{qi2010combining,da2016particle,ma2015hybrid,da2015graphevol,yu2013adaptive} does not consider distinguished matchmaking quality in their fitness function, which might lead to over-general outputs to be produced by selected services, The finding is evidently supported by comparing two solutions employing different evaluation model in Sect.
 \ref{comparisonTest}.
@@
 In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS.
-Therefore, we fill the gap by considering different matching types and parameter similarity to determine the overall quality of web service composition.
-Weighed graphs are also utilised in PSP to facilitate a new representation of web service composition adopted from \cite{da2016particle}.
+Therefore, we fill the gap by considering different matching types and parameter-related concept similarity to determine the overall quality of web service composition.
+Also, Weighed graphs are utilised as representationd of semantic web service composition decoded from optimised service queue using PSO adopted from \cite{da2016particle}.
 \section{Problem Description}\label{problemDes}
@@
 \fbox{\includegraphics[scale=.4]{overview.pdf}}
- \caption{Overview of the proposed approach.}
+ \caption{Overview of POS-based automated semantic web service composition approach.}
  \label{overview}
@@
 
-In this section, we propose a comprehensive quality model for automated semantic service composition, and optimise both the quality of semantic matchmaking and QoS.
+In this section, we propose a comprehensive quality model for automated semantic service composition, and optimise both semantic matchmaking quality and QoS.
 PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}.
@@
 Lastly, the best position found in the searching space is selected and decode into the final optimised solution.
-This PSO-based approach is different from \cite{da2016particle}, as we use weighted graphs as solution presentation.
+This PSO-based approach is similar to \cite{da2016particle}, but we employ weighted graphs as a different solution presentation.
 
@@
 In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively.
-To effectively construct weighted graphs, we pre-calculate semantic matchmaking quality and mark the input-parameter concepts with a set of services.
-The key idea of the index is to create a mapping from the output-related concepts to matched input-related services while considering different levels of match types.
-Furthermore, this index size could also be reduced by only considering parameter-related concepts in the shrunken service repository, which contains  those task-relevant web services.
-This optimised cache also contributes to less and constant time for weighted graph building for the whole evolutionary process.
+To effectively construct weighted graphs, we pre-calculate semantic matchmaking quality.
+The key idea of the index is to create a mapping from the output-related concepts to potentially matched input-related concepts while considering different levels of match types.
+Meanwhile, this index size could also be reduced by only considering the concepts related in the shrunken service repository, which means the index cache is filtered by those task-relevant web services.
+This optimised cache also contributes to less and constant time for weighted graphs building through the whole evolutionary process.
 
@@
 Another factor in our proposed model is concept similarity, which could be evaluated based on the edge counting method defined in \cite{shet2012new}.
-This formula (\ref{equation1}) is used to estimate the similarity between parameter-related output concept and parameter-related input concept for selecting web services.
-Therefore, given the quality match type and the similarity of two parameters-related concepts, the semantic matchmaking quality of matched parameters is defined by Formula (\ref{equation2}), where the value of $q(p_ {mt})$ follows the same settings in \cite{lecue2009optimizing}.
+This formula (\ref{equation1}) is used to estimate the similarity between concept-related parameters for selecting web services.
+Therefore, given the quality match type and the concept similarity of two parameters-related concepts, the semantic matchmaking quality of matched parameters is defined by Formula (\ref{equation2}), where the value of $q(p_ {mt})$ follows the same settings in \cite{lecue2009optimizing}.
 Particularly, 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).
@@
 \subsection{Fitness Calculation}
-In real life, given a unique and optimised solution is always easier for customers choose from when many quality criteria involved in the composite solution, rather than provided a set of solutions.
+In real life, given a unique and optimised solution is always easier for customers to pick up directly when many quality criteria involved into decision making, rather than provided a set of solutions.
 Therefore, it is very practical to define a single fitness as a weighted sum of all the quality related components in Formula (\ref{equation6}), where weights setting is very flexible, it could be adjusted according to users' preferences.
@@
 
-\begin{algorithm}[!htb]
+\begin{algorithm}
  \setlength\hsize{0.9\linewidth}
  \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
- \let\oldnl\nl% Store \nl in \oldnl
-\newcommand{\nonl}{\renewcommand{\nl}{\let\nl\oldnl}}
+ \SetKwFunction{generateWeightedGraph}{generateWeightedGraph}
+ \SetKwProg{Procedure}{Procedure}{}{}
  \LinesNumbered
- 	\textbf{1.} Map each relevant service to an index in the particle's position vector.\\
-	\textbf{2.} Randomly initialise each particle in the swarm.\\
-	\nonl \While {max. iterations not met}{
-		\ForAll{particles in the swarm}{
-		    \textbf{3.} Create queue of services using the particle's position vector.\\
-			{\textbf{4.} $WG \leftarrow$ generatedWeigthedGraph().}\\
-			{\textbf{5.} Calculate the $WG$ fitness value.}\\
-			\eIf{fitness value better than pBest}{
-				\textbf{6a.} Assign current fitness as new pBest.\\
+ \SetNlSty{}{}{:}
+ \Input{relevant Web services $rws$}
+ \Output{Optimised service queue $queue$,Optimised Weighted Graph $OPTWG$}
+ Map each relevant service to an index in the particle's position vector\;
+ Randomly initialise each particle in the swarm\;
+  \While {max. iterations not met}{
+     \ForEach{particles in the swarm}{
+     $queue \leftarrow$ particle's position vector\;
+     $WG \leftarrow$ $generateWeightedGraph$()\;
+	 Calculate the $WG$ fitness value\;
+
+      \eIf{fitness value better than pBest }{    
+        Assign current fitness as new pBest\;
        }{
-				\textbf{6b.} Keep previous pBest.\\
+        Keep previous pBest\;
        }	
      }
-		\textbf{7.} Assign best particle's \emph{pBest} value to \emph{gBest}, if better than gBest.\\
-		\textbf{8.} Calculate the velocity of each particle according to the equation:\\
-		\Indp $v_{id} = v_{id} + c_1 * rand() * (p_{id} - x_{id}) + c_2 * rand() * (p_{gd} - x_{id})$\\
-		\Indm \textbf{9.} Update the position of each particle according to the equation:\\
-		\Indp $x_{id} = x_{id} + v_{id}$\\
+    Assign best particle's \emph{pBest} value to \emph{gBest}, if better than gBest\;
+ 	Calculate the velocity of each particle\;
+  	Update the position of each particle\;
   }
-
+ \KwRet $OPTWG$\;
  \caption{Steps of the PSO-based Web service composition technique.}
@@
   \Procedure{\generateWeightedGraph{}}{
- \Input{Task inputs $I$, task outputs $O$, relevant Web services $queue$, IndexCache $IndexCache$}
+ \Input{Task inputs $I$, task outputs $O$, Optimised service queue $queue$, IndexCache $IndexCache$}
  \Output{Weighted Graph $WG$}
@@
     		 \ForEach{$I$ in $ws.inputs$}{
-    		$parameter.matchType \leftarrow$ query $IndexCache$\;
-     		$parameter.conceptSiminarity \leftarrow$ query $IndexCache$\;
+    		$p_{mt} \leftarrow$ query $IndexCache$\;
+     		$p_{s} \leftarrow$ query $IndexCache$\;
               }
-        $WG.edge \leftarrow$ new $Edge$()\;
-        $edge.weights \leftarrow$ aggregation($parameters$)\;
+        $e_{sm} \leftarrow$ aggregation($p_{mt}$,$p_{s}$)\;
+        $WG.edge \leftarrow$  $e_{sm} $\;
         $WG \leftarrow$ new $wsNode$()\;
@@
  }
- \vspace{2mm}
  \caption{Create a composition weighted graph from a queue.}
@@
 
-The overall algorithm investigated here is made up of a PSO-based web service composition algorithm \ref{novelSteps} and a decoding algorithm \ref{graph_building}, to generate a composition weighted graph.
-In algorithm \ref{novelSteps}, the idea is to translate the particle location produced by PSO into a service queue as an indirect representation of weighted graph, such that finding the best fitness of the weighted graph is to discover the optimised location of the particle in the search space.
+The overall algorithm investigated here is made up of the PSO-based web service composition algorithm \ref{novelSteps} and the decoding algorithm \ref{graph_building}.
+In algorithm \ref{novelSteps}, the idea is to translate the particle location produced by PSO into a service queue as an indirect representation, such that finding the best fitness of the weighted graph is to discover the optimised location of the particle in the search space.
 In PSO, the dimension of each particle equals to the number of relevant web services.
@@
 Services in a queue follow the ascending order, from which we decode a weighted graph using Algorithm \ref{graph_building}.
-We select and connect  service node to the start node from the service queue if the inputs of web service can satisfy the output of start node.
-The edge associated with two connected nodes is also created, the weight of which is also calculated as a quality aggregated value from concept-related parameters.
-Meanwhile, an Output Set is initialised and kept being updated using outputs from the newly added service node in the weighted graph, later on, more services vertices are connected with edges if services' inputs could be satisfied by any output in the Output Set.
-Finally, the end vertex is connected to the graph if the updated Output Set contains all end inputs.
-In addition, dangling service vertex and edges will be removed.
+It is a simple forward graph building algorithm, and this method can lead to more services and edges connected to the graph as redundancies that must be removed.
+Also, semantic quality value are assigned to all the edges, which is calculated from a quality aggregation function from all involved concept-related parameters.
+
 \section{Experiment Design}\label{experiment_design}
 In this section, a quantitative evaluation approach is adopted in our experiment design.
-The objectives of the evaluation are to $(1)$ measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach; $(2)$ explore the impacts of the semantic matchmaking that contributes to overall composition quality; and $(3)$ compare solutions generated by QoS-ware approach with our method.
+The objectives of the evaluation are to $(1)$ measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach; $(2)$ explore the impacts of the semantic matchmaking that contributes to overall composition quality; and $(3)$ compare solutions generated by QoS-ware approach with our method; and $(4)$ compare our method with one existing GP-based approach.
 
@@
 In this section, we analyse the composition solution generated by using our approach comparing with QoS-aware approach.
-In particularly, we show that our proposed approach can produce solutions that results in better matchmaking, which meets user's goal better.
-
 First, we look at mean value of $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ at optimum at the 100th generation for two approaches, shown in Table \ref{decisionTable}.
-The QoS-aware approach record $Q_{mt}$, $Q_{s}$ and utilise fitness function $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$ without considering $MT$ and $S$, in which $Q_(QoS)$ is normalised from 0 to 0.5 to make it comparable to $Q_{QoS}$ in our approach.
+The QoS-aware approach record $Q_{mt}$, $Q_{s}$ and utilise fitness function $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$, but $MT$ and $S$ are recorded, and $Q_(QoS)$ is normalised from 0 to 0.5 to make it comparable to $Q_{QoS}$ in our approach.
 We observe an interesting pattern from Table \ref{decisionTable} using statistic analysis: mean value of $Q_{mt}$ and $Q_{s}$ at optimum by our approach is consistently higher than those by QoS-aware approach.
@@
 Fig.
-\ref{comparisontest} $(1)$ and $(2)$ show two composition weighted graphs as the solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method respectively.
+\ref{comparisontest} $(1)$ and $(2)$ show two composition weighted graphs as the two optmised solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method respectively.
 Two approaches generate exactly the same service workflow structure where those service vertices and edges denoted in red are different.
@@
 
-We also investigate the variation of quality of semantic matchmaking where average matchType quality with optimum and average similarity quality with optimum are studied from generation 0 to 99 in second and third column groups of Fig.
+We also investigate the variation of quality of semantic matchmaking where average matchType quality with optimum and average similarity quality with optimum are studied in second and third column groups of Fig.
 \ref{exp_fitnessvalue}.
-In these subfigures, both the average matchType quality with optimum and average similarity quality with optimum refers to the mean values of the quality values associated to the best fitness value found in each generation over 30 independent runs.
 Similar to the fitness values, clear evidence of fast convergence can be observed with respect to theses quality values.
@@
 \subsection{Comparison Test with GP-based approach}\label{comparisonTestWithGP}
-We compare a GP-based approach  \cite{ma2015hybrid} with our PSO method, where the individual is a tree structure transferred from a DAG employing unfolding techniques.
-We further mark all the tree nodes in the representation with its outgoing edges for semantic matchmaking quality, and those edges information are maintained correctly throughout the evolutionary process.
-At last, we evaluate both semantic matchmaking quality and QoS simultaneously using the discussed the comprehensive quality model to investigate the performances of both GP-based approaches and PSO-based approach.
-To make a fair comparison with our PSO approach that the same number of evaluations (3000 times) should be considered, we adjust the parameters settings for GP approach \cite{ma2015hybrid} to 30 individual for 100 generations.
+We compare one GP-based approach  \cite{ma2015hybrid} with our PSO method, where the individuals are tree structure with strict constrains transferred from a DAG employing unfolding techniques.
+We further mark all the service nodes in the tree representation with all their outgoing edges for considering semantic matchmaking quality, and those edges information are maintained correctly in the crossover and mutation.
+At last, we evaluate both semantic matchmaking quality and QoS simultaneously using the discussed the comprehensive quality model to investigate the performances of two approaches.
+To make a fair comparison with our PSO approach considering the same number of evaluations (3000 times), we adjust the parameters settings for GP approach \cite{ma2015hybrid} to 30 individual for 100 generations.
 
@@
 However, there is also a trade-off between optimised solution and execution time.
-We can see the PSO-based approach takes longer execution time, it due to that the every individual in each generation must be decoded from generated optimised queue, and this process is very time-consuming.
-However,  the initialisation first population in GP-based approach is costly in time as transformation process from a DAG, but following new individuals are generated through mutation and crossover, which are considered be much less time consumed comparing decoding process.
+We can see the PSO-based approach takes longer execution time, it due to that every individual in each generation must be decoded into a solution from optimised queue, and this process is very time-consuming.
+However, In GP, the initialisation first population is costly in time as transformation process from a DAG, but following new individuals are generated through mutation and crossover, which demands much less time comparing decoding process.
 
@@
 \end{tabular}
-\end{table}
-
-\begin{table}[]
+\vspace{2mm}
 \centering
@@
 
-We also study the average fitness value with the optimum through the evolutionary process for both PSO-based and GP-based approach over 30 independent runs.
+At last, We also compare the average fitness value with optimum through the evolutionary process for both two approaches over 30 independent runs.
 Fig.
-\ref{psovsgp} is an example of convergence rate from Task 3, where the behaviour of PSO-based approach presents a very clear evidence of fast convergence and reaches a better-optimised solution, while the performance of GP is barely satisfactory, as this method improves its fitness value gradually.
+\ref{psovsgp} is an example of convergence rate from Task 3, where the behaviour of PSO-based approach presents a very clear evidence of fast convergence and reaches a better-optimised solution, while the performance of GP is barely satisfactory, as GP-based method improves its fitness value gradually.
 
 \section{Conclusion}\label{conclusion}
-This work introduced a comprehensive evaluation model for QoS-aware automated semantic automated web service composition that combines the quality of semantic matchmaking with QoS.
-The results show that our comprehensive quality model is proved to obtain better functional quality with a reasonable trade-off in QoS.
-Also, we comparing one GP-approach with our PSO-based method to show our better performance in find more optimised solution.
-Future works could investigate other direct or indirect representations of semantic web service composition on semantic web service composition, and look into more EC techniques to evaluate their performance.
-Also, we could reshape the problem as providing customers with a set of solutions to choose from, rather than a single solution, so the research problem is transferred into multi-objectives or many objective problems.
+This work introduces a comprehensive evaluation model employed our PSO-based method for QoS-aware automated semantic automated web service composition that combines the quality of semantic matchmaking with QoS.
+The results show that our approach obtain better functional quality with a reasonable trade-off in QoS.
+Also, we compare one GP-approach with our PSO-based method to show our performance results in finding better-optimised solution.
+Future works could investigate other direct or indirect representations of semantic web service composition on semantic web service composition, and look into other EC techniques to evaluate their performance.
+Also, we could reshape the problem on providing customers with a set of solutions to choose from, rather than a single solution, so research question is redefined as multi-objectives or many objective problems.
+
 \bibliographystyle{IEEEtran}

### 2017-01-27 paper.tex
update

@@
 \title{Comprehensive Quality-Aware Automated Semantic Web Service Composition}
- \author{Chen Wang, Hui Ma, Aaron Chen\\ School of
+\author{Chen Wang, Hui Ma, Aaron Chen\\ \small School of
 Engineering and Computer Science, Victoria University of Wellington, New Zealand\\
-Email: chen.wang@ecs.vuw.ac.nz, hui.ma@ecs.vuw.ac.nz, aaron.chen@ecs.vuw.ac.nz}
+Email: \{chen.wang, hui.ma, aaron.chen\}@ecs.vuw.ac.nz}
 
@@
 Semantic web service composition has been a prevailing research area in recent years.
-There are two major governance challenges faced by researchers (semantic matchmaking and QoS optimisation).
+There are two major challenges faced by researchers, semantic matchmaking and QoS optimisation.
 Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning.
-QoS optimisation aims to optimise the non-functional requirement of service users.
-E.g., minimum cost, maximal reliability.
-Many scholars have looked into nonfunctional optimisation problems in QoS-aware web service composition applying AI planning and Evolutionary Computation techniques.
+QoS optimisation aims to optimise the non-functional requirement of service users, e.g., minimum cost, maximal reliability.
+Many scholars have looked into QoS optimisation problems in QoS-aware web service composition applying AI planning and Evolutionary Computation techniques.
 To meet users' requirement, one often needs to consider both semantic matchmaking quality and QoS simultaneously.
 Existing works on web service composition often concerns either semantic service composition or QoS-aware service composition.
-However, there are few works concerns both quality of semantic matchmaking and quality of services at the same time and points out the benefits clearly.
-Therefore, In this paper, we consider two quality dimensions in a proposed more applicable comprehensive quality model for semantic web service composition and present an automated semantic web service composition approach that can generate service composition solutions that meet both functional and non-functional requirement.
-The results show our method can find better semantic matchmaking quality with a very slight trade off in QoS.
-Also, our method performs better in finding optimised solution with a trade off in execution time comparing an existing GP-based method.
+However, there are few works concerns both quality of semantic matchmaking and QoS at the same time and points out the benefits clearly.
+Therefore, In this paper, proposed a more comprehensive quality model which is suitable to be tackled through EC algorithms and developed a general EC-based service composition system with explicit support for the comprehensive model, which can generate service composition solutions that meet both functional and non-functional requirement.
+We have evaluate our proposed model by comparing QoS evaluation model using benchmark dataset.
+The results show our approach can produce more opimised semantic matchmaking quality with a very slight trade off in QoS.
+We also conduct a experiment shows our EC mehtod performs better in finding more optimised solution by comparing one existing GP-based method using our proposed model.
 
@@
 
-\textit{Web service composition} pertains to a combination of multiple web services to provide a value-added composite service that accommodates customers' arbitrarily complex requirements.
+\textit{Web service composition} pertains to a combination of multiple web services to provide a value-added composition service that accommodates customers' arbitrarily complex requirements.
 This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems.
@@
 Through ontology-based semantics \cite{o2005review}, web services can understand and better collaborate with each other.
-There are many ontologies languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}, which make ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments.
+There are many ontology languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}, which make ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments.
 The second challenge $(2)$ is related to finding \textit{optimised solutions} to Quality of Service ($QoS$).
@@
 Existing works on service composition focus mainly on addressing the one of challenges above.
-A lot of works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as \textit{semi-automated Web service composition} approach.
-Meanwhile, many research works consider the possibility of generating a composite plan automatically in discovering and selecting suitable web services, which are considered to be NP-hard \cite{moghaddam2014service}.
+A lot of works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as \textit{semi-automated Web service composition} approach \cite{parejo2008qos,bahadori2009optimal}.
+Meanwhile, many research works consider the possibility of generating a composition plan automatically in discovering and selecting suitable web services, which are considered to be NP-hard \cite{moghaddam2014service}.
 \textit{Semantic web services composition} is distinguished from the syntactic service composition, with the hope of eliminating conflicts by the semantic level of web services.
@@
 To a given service request, the quality of service composition solution depends on both QoS and quality of semantic matchmaking.
-Therefore, a comprehensive quality model is needed to be addressed, and more methods are needed to be applied specifically on the problem that optimises semantic matchmaking quality and QoS simultaneously.
 
-The overall goal of this paper is to \textit{develop an comprehensive quality-aware automated semantic web service composition that satisfactorily optimises both functional and non-functional requirements}.
-Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matching optimisation in our proposed comprehensive quality model.
-Particle Swarm Optimisation (PSO) has show its promise in searching near-optimised service composition solution \cite{da2016particle}, we will propose a PSO-based service composition approach using our comprehensive quality model, which is also considered to be more applicable way to measure semantic matchmaking in automated semantic web service composition.
+The overall goal of this paper is to \textit{develop an comprehensive appraoch to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}.
+Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matchmaking quality optimisation in our proposed comprehensive quality model.
+Particle Swarm Optimisation (PSO) has show its promise in searching near-optimised service composition solutions \cite{da2016particle}.
+We will propose a PSO-based service composition approach using our comprehensive quality model to measure semantic matchmaking in automated semantic web service composition.
 We will achieve three objectives in this work as follows:
@@
  \item To propose a comprehensive quality model that address QoS and semantic matchmaking quality in considering different matching types with corresponding concept similarity.
-This method is consider to be a more applicable and effective way of finding an optimised solution in semantic web service composition.
 
@@
 
- \item To evaluate the performance of comprehensive quality awareness semantic web service composition by utilising benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
-Also, we make a comparison between PSO-based and an existing GP-based approach employing our proposed comprehensive quality model.
+ \item To evaluate our proposed approach, we conduct experiment to compare our comphensive quality model with QoS evaluation model, we also compare an one existing GP approach with our appraoch using our comprehensive model.
+Both comparison utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}
 
@@
 A hyper approach employs both a greedy search algorithm and genetic programming is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness.
-In particularly, the greedy search is used to generate directed acrylic graph as composite solutions, which is further transferred to tree structure using unfolding techniques for initialisation and mutation during the evolutionary process.
+In particularly, the greedy search is used to generate directed acrylic graph as composition solutions, which is further transferred to tree structure using unfolding techniques for initialisation and mutation during the evolutionary process.
 A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of Directed Acyclic Graph(DAG) employing Graph-based evolutionary operators like crossover and mutation.
 To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}.
-A general graph is used as representation as composite solution in their PSO algorithm considering QoS optimisation.
+A general graph is used as representation as composition solution in their PSO algorithm considering QoS optimisation.
 
@@
 A heuristic service composition method is proposed by Tang et al.
-\cite{qi2010combining} proposed,  named local optimisation and enumeration, which is to filter a small number of promising candidates related to each task by local selection, and all the composite solutions are enumerated to reach the near-to-optimal.
+\cite{qi2010combining} proposed,  named local optimisation and enumeration, which is to filter a small number of promising candidates related to each task by local selection, and all the composition solutions are enumerated to reach the near-to-optimal.
 
-However, composite solutions from \cite{qi2010combining,da2016particle,ma2015hybrid,da2015graphevol,yu2013adaptive} does not consider distinguished matchmaking quality in their fitness function, which might lead to over-general outputs to be produced by selected services, The finding is evidently supported by comparing two solutions employing different evaluation model in Sect.
+However, composition solutions from \cite{qi2010combining,da2016particle,ma2015hybrid,da2015graphevol,yu2013adaptive} does not consider distinguished matchmaking quality in their fitness function, which might lead to over-general outputs to be produced by selected services, The finding is evidently supported by comparing two solutions employing different evaluation model in Sect.
 \ref{comparisonTest}.
@@
 
-The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as a composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$.
-This overall composite goal is demonstrated in two parts.
+The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as a composition goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$.
+This overall composition goal is demonstrated in two parts.
 The first functional part focus on transfering a given task input or input set to the desired Task output or output set.
 It typically refers to users' functional requirement.
-Another nonfunctional part specifies the acceptable level of composite quality of service.
-To accomplish the composite goal, two stages are involved: services discovery and service selection.
+Another nonfunctional part specifies the acceptable level of composition quality of service.
+To accomplish the composition goal, two stages are involved: services discovery and service selection.
 Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from a Service Repository: $S =  \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$.
-If no atomic web service could satisfy the composite goal, a combination of web services will be found to meet $Comp.G$.
-To ensure the composite solution returns the desired $Comp.G$, we consider a comprehensive quality model for service discovery and selection, where challenges $(1)$ and $(2)$ mentioned in Sect.
+If no atomic web service could satisfy the composition goal, a combination of web services will be found to meet $Comp.G$.
+To ensure the composition solution returns the desired $Comp.G$, we consider a comprehensive quality model for service discovery and selection, where challenges $(1)$ and $(2)$ mentioned in Sect.
 \ref{introduction} are also addressed in Sect.
@@
 The aggregation value of QoS attributes for web services composition varies with respect to different constructs, which reflects how services associated with each other in a service composition \cite{zeng2003quality}.
-Here we consider two composite constructs: sequence and parallel constructs, in building the composite web service.
+Here we consider two composition constructs: sequence and parallel constructs, in building the composition web service.
 The QoS calculation models are described as follows:
@@
 \subsubsection{Sequence construct}
-The composite web service executes each atomic service associated with a sequence construct in a definite sequence order.
+The composition web service executes each atomic service associated with a sequence construct in a definite sequence order.
 The aggregation value for total time ($T$) and total cost ($C$) is as the sum of time and cost of web services involved respectively.
@@
 Web services in a parallel construct are executed concurrently.
-The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is determined by the most time-consuming path in the composite flow of the solution.
+The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is determined by the most time-consuming path in the composition flow of the solution.
 This construct is presented in Fig.
@@
 \ref{overview} shows the overview of our approach with five steps.
-Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional.
+Step 1: The composition process is triggered by a composition goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional.
 Step 2: This composition goal are used to discover all relevant web services, which lead to a shrunken service repository that is subsequently used by PSO as a searching space.
@@
 \textbf{Quality aggregate matrix}.
-The quality aggregation is defined based on the constructs of composite web services, in consideration of functional and non-functional properties.
+The quality aggregation is defined based on the constructs of composition web services, in consideration of functional and non-functional properties.
 The quality on construct level is further calculated by following the rules summarised in Table \ref{table1}.
@@
 \ref{wscs}.
-The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections.
+The data of composition web service flows from the start to the end, where five web services involved and linked with each other using edge connections.
 Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},...
@@
 
-Second, to compare the results generated from two evaluation approaches, we demonstrate an example solution that shows the differences in composite web services obtained through two different methods.
+Second, to compare the results generated from two evaluation approaches, we demonstrate an example solution that shows the differences in web services composition obtained through two different methods.
 Fig.

### 2017-01-29 paper.tex
update

@@
 Existing works on web service composition often concerns either semantic service composition or QoS-aware service composition.
-However, there are few works concerns both quality of semantic matchmaking and QoS at the same time and points out the benefits clearly.
-Therefore, In this paper, proposed a more comprehensive quality model which is suitable to be tackled through EC algorithms and developed a general EC-based service composition system with explicit support for the comprehensive model, which can generate service composition solutions that meet both functional and non-functional requirement.
-We have evaluate our proposed model by comparing QoS evaluation model using benchmark dataset.
-The results show our approach can produce more opimised semantic matchmaking quality with a very slight trade off in QoS.
-We also conduct a experiment shows our EC mehtod performs better in finding more optimised solution by comparing one existing GP-based method using our proposed model.
+However, there are few works concerns both semantic matchmaking quality and QoS at the same time and achieve a more
+desirable tradeoff in consideration of both sides.
+Therefore, In this paper, proposed a genral comprehensive quality model that can achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS.
+This model is also suitable to be tackled through EC algorithms, and we develope a PSO-based service composition approach with explicit support for the comprehensive model, which can generate more desiable balanced web service composition that meet both senmantic matchmaking quality and QoS requirement by comparing existing QoS evaluation model using benchmark dataset.
+We also conduct an experiment shows our PSO-based mehtod performs better in finding more optimised solution by comparing one existing GP-based method.
 
@@
 \begin{enumerate}
- \item To propose a comprehensive quality model that address QoS and semantic matchmaking quality in considering different matching types with corresponding concept similarity.
+ \item To propose a general comprehensive quality model that address QoS and semantic matchmaking quality in considering different matching types with corresponding concept similarity.
 
@@
 \section{Related Work} \label{relatedWork}
-\textbf{Semantic web service composition}.
-Substantial work \cite{da2016particle,bansal2016generalized,mier2015integrated,da2015graphevol,yu2013adaptive} on web service composition focused primarily on non-functional requirements consistently neglecting functional requirements.
-However few researchers addressed both functional and nonfunctional requirements at the same time in web service composition.
-To the best of our knowledge, \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} reported some recent attempts on service composition that considers both nonfunctional (QoS) and functional (semantic) aspects.
-Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} to search for services that ensure semantic matching utilising an ontology of the corresponding domain.
+Substantial work on web service composition either focused on semantic web service composiiton \cite{boustil2014semantic,mier2015integrated, bansal2016generalized} or QoS-aware web service composiiton \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining}, However few researchers addressed both semantic mathmaking quality and QoS requirements at the same time for web service composition problems.
+To the best of our knowledge, \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} reported some recent attempts on service composition that considers both aspects.
 
-The combination of enhancing planning graph (EPG) and clonal selection algorithm is introduced in the work \cite{pop2009immune} as an immune-inspired web service composition approach.
-During the clonal selection process, the antigen is represented as a fitness function, and the antibody is represented as a binary alphabet to encode EPG.
-In this work,  semantic matchmaking is considered by measuring the quality of the similarity measure using information retrieval technique.
+\cite{boustil2014semantic,mier2015integrated, bansal2016generalized} captures the semantics of the parameters of web services using some kind of logic (e.g., description logic) for enabling semantic web service composition, where the number of web servces or length of the graph is minimised to reach the optimised graph-based compositin solutions.
+However, these approaches always need to improve their scalability for a large number of web services, and the evalution method does not fit for today's customers' requirements properly.
 
-In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links, one possible measure is applied to the degree of similarity using Common Description rate of a semantic link, where Extra Description and Least common subsume are required to be pre-calculated.
-Therefore, the quality of the semantic link is estimated as quality of matching types associated with their corresponding quality of Common Description rate.
-However, the weakness of semantic link quality is that calculation requires well and completely defined ontology in class, class axioms and properties.
-This makes it difficult to measure semantic matchmaking quality as it takes huge cost and time for the domain experts to establish required ontology.
-In comparison, we introduce a more applicable comprehensive quality model in a fully automated approach.
+A heuristic service composition method is proposed by Qi et al.
+\cite{qi2010combining}for QoS-aware web service composiiton, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal for QoS consideration.
+but obviously there exists scalability problem for enumeration techniques.
 
-The work \cite{fanjiang2014semantic} concerns both functional and non-functional requirements in design time of semantic-based automatic service composition, where a GA-based approach with four unusual independent fitness functions are designed to solve the problems with these concerns.
-A sequence of fitness functions are used in the binary selection of chromosomes, rather than a single objective consisting of both functional and non-functional quality.
-Apart from that, semantic matching types are ignored in their quality evaluation of semantic matching.
-
-\textbf{QoS-aware web service composition}.
-Evolutionary Computation techniques are widely used to solve optimisation problems, where the search space is big, so that near-optimised solutions can be found in reasonable time.
-
+Evolutionary Computation (EC) techniques are used to improve the scalability for solving NP-hard problems.
 Gupta et al.
-\cite{gupta2015optimization} proposed an improved Genetic Algorithm for QoS-ware web service composition, where some population associated with lower fitness are discarded with bringing in new offerings in each generation.
-In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions.
-Also, this paper increase the mutation rate while encountering low diversity in the population and adopt a higher crossover probability while trapped in local optimisation.
-A hyper approach employs both a greedy search algorithm and genetic programming is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness.
+\cite{gupta2015optimization} employ an Genetic Algorithm to the problem of QoS-ware web service composition, and a set of binary strings are used as individuals, which demands to be decoded into composition solutions.
+Genetic Programming are employed by  \cite{yu2013adaptive} with direct reprentation of compsotion solutions, the overall quality of solutions are measured by a fitness function that is liable for penalising infeasible solutions.
+A hyper approach employs both a greedy search algorithm and Genetic Programming (GP) is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness.
 In particularly, the greedy search is used to generate directed acrylic graph as composition solutions, which is further transferred to tree structure using unfolding techniques for initialisation and mutation during the evolutionary process.
-A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of Directed Acyclic Graph(DAG) employing Graph-based evolutionary operators like crossover and mutation.
-To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}.
-A general graph is used as representation as composition solution in their PSO algorithm considering QoS optimisation.
-
-Other non-EC techniques are also introduced in QoS-ware web service composition.
-A heuristic service composition method is proposed by Tang et al.
-\cite{qi2010combining} proposed,  named local optimisation and enumeration, which is to filter a small number of promising candidates related to each task by local selection, and all the composition solutions are enumerated to reach the near-to-optimal.
-
-However, composition solutions from \cite{qi2010combining,da2016particle,ma2015hybrid,da2015graphevol,yu2013adaptive} does not consider distinguished matchmaking quality in their fitness function, which might lead to over-general outputs to be produced by selected services, The finding is evidently supported by comparing two solutions employing different evaluation model in Sect.
-\ref{comparisonTest}.
+To eliminating the transformation process from DAG, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of Directed Acyclic Graph(DAG) employing Graph-based evolutionary operators like crossover and mutation.
+PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}, an indirect PSO-based approach was introduced in \cite{da2016particle}.
+An opimised queue is used as indirect representation as composition solution that decoding into Direct Acyclic Graph (DAG).
+These QoS-aware appraoches does not consider semantic matchmaking quality, which could lead to over-general outputs to be produced by selected services, The finding is evidently supported by our first comparision experiment.
 In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users.
 In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS.
-Therefore, we fill the gap by considering different matching types and parameter-related concept similarity to determine the overall quality of web service composition.
-Also, Weighed graphs are utilised as representationd of semantic web service composition decoded from optimised service queue using PSO adopted from \cite{da2016particle}.
+
+Few works \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} employ EC technique for considering both semantic matchmaking quality and QoS simultaneously.
+Lecue et al.
+\cite{lecue2009optimizing} employ Genetic Algorithm for semi-automated web service composition considering semantic matchmaking quality and QoS, where the semantic matchmaking quality is measured the quality of semantic links that requires formal definition of ontology in Description logic.
+This evaluation takes huge cost and time for the domain experts to establish required ontology.
+Another GA-based appraoch work \cite{fanjiang2014semantic} employs a sequence of fitness functions are used in the binary selection of chromosomes, where semantic matchmaking quality is evaluate in two fitness functions considering concept similarity and parameter similarity respectively, However, different semantic matchmaking types are ignored in evaluation model.
+The work \cite{pop2009immune} as an immune-inspired web service composition approach employ indirect reprentation that a binary alphabet to encode a planning graph, where the semantic matchmaking quality is measured  by the similarity using information retrieval technique.
+
+In summary, composition solutions from semantic web service composition does not consier QoS \cite{boustil2014semantic,mier2015integrated, bansal2016generalized}, and QoS-aware web service composiiton \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining} does not consider distinguished matchmaking quality in their fitness function.
+Few works do consider both quality aspects, but some limitatins lie in semi-automated approach \cite{lecue2009optimizing}, less general semantic quality measurement \cite{lecue2009optimizing, pop2009immune}, or semantic matchmaking types ignorance \cite{pop2009immune}.
+In addition, experiments design for  \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} are not conducted using benchamark dataset for the scalability, only small datasets are utilised that might suffer scalability.
+Results analysis for \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} also do not evidently point out what desired balance could be rearched by considering semantic matchmaking quality and QoS.
+Therefore, we proposed a general comprehensive quality model which achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS to fill the gaps dissussed above, and then we proposed a POS-based method with explicit support for the comprehensive model, and evaluate its performace by comparing with one existing GP-based approach.
+
 \section{Problem Description}\label{problemDes}
 
-The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as a composition goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$.
-This overall composition goal is demonstrated in two parts.
-The first functional part focus on transfering a given task input or input set to the desired Task output or output set.
-It typically refers to users' functional requirement.
-Another nonfunctional part specifies the acceptable level of composition quality of service.
-To accomplish the composition goal, two stages are involved: services discovery and service selection.
-Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from a Service Repository: $S =  \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$.
-If no atomic web service could satisfy the composition goal, a combination of web services will be found to meet $Comp.G$.
-To ensure the composition solution returns the desired $Comp.G$, we consider a comprehensive quality model for service discovery and selection, where challenges $(1)$ and $(2)$ mentioned in Sect.
-\ref{introduction} are also addressed in Sect.
-\ref{qswsc_approach}.
+The aim of web service composition is to fulfil customers' requirements, which could be denoted as a composition goal: $Comp.G(F(I_{T}, O_{T}), NF(QoS_{T}))$.
+This overall composition goal is demonstrated in two parts: functional part and non-functional part.
+The functional part is defined by a given task input and a desired task output.
+The nonfunctional part specifies QoS.
+To accomplish the composition goal, two stages are involved, services discovery and service selection.
+Service discovery is to find matching web services: $S_{n}(F(I_{S}, O_{S}), NF(QoS_{S}))$ from a Service Repository: $\mathcal{S}$ $=  \{S_{1}, S_{2},..., S_{n} \}$ for the given $I_{T}$.
+If no atomic web service could satisfy the composition goal, a composition of web services will be found to meet $Comp.G$.
+To ensure the composition solution returns the desired $Comp.G$, we use a quality model that take care of QoS and semantic matchmaking quality.
 
-\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
-The semantic service matchmaking aims to discover appropriate services from service repository in view of customers' functional requests.
-A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$, where both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Taxonomy\}$.
-A web service matching process is to match the output and input concepts of two services according to the Taxonomy within an Ontology (O).
-To measure the quality of semantic matchmaking, different matching levels are typically considered in the literature \cite{paolucci2002semantic}.
-To understand these levels, let us define two web services associated with concept-related parameters in a particular domain.
-$S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S_{2}$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$.
-The matching levels to be considered are:
-
-\begin{itemize}
-\item \textit{Exact} ($\equiv$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Exact match ($ S_{output} \in S_{1} \equiv S_{input}S_{2}$), if  Concept $C_{2}$ and Concept $C_{3}$ are equivalent.
-\item \textit{Plugin} ($\sqsubseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Plugin match ($S_{output} \in S_{1} \sqsubseteq_{n} S_{input} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of children concepts ($n=1$ stands for direct children).
-\item \textit{Subsume} ($\sqsupseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Subsume matched($S_{output} \in S_{1} \sqsupseteq_{n} S_{input} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of  Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of parent concepts ($n=1$ stands for direct parent).
-\item \textit{Fail} ($\perp$).
-Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are not matched (Fail) ($S_{output} \in S_{1} \perp S_{input} \in S_{2}$), if none of the previous matches discovered.
-\end{itemize}
-\vspace{-0.5cm}
 \subsection{Quality of Service and Composition Constructs}\label{Quality of Service and Composition Constructs}
-Currently, most of the optimisation problems \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} in web service composition are focusing on QoS, which covers aspects in non-functional requirements.
-This problem has been explored in both single objective and multi-objectives optimisation problems.
-Customers prefer lowest execution cost with highest response time and reliability that could be optimised simultaneously.
-According to \cite{zeng2003quality}, four most often considered QoS parameters are as follows:
+According to \cite{zeng2003quality}, four most often considered QoS parameters are response time, cost, reliability and availability decribed as follows:
 \begin{itemize}
@@
 \end{itemize}
-The aggregation value of QoS attributes for web services composition varies with respect to different constructs, which reflects how services associated with each other in a service composition \cite{zeng2003quality}.
+The aggregation value of QoS attributes for a composite service varies with respect to different constructs, which reflects how services associated with each other in a service composition \cite{zeng2003quality}.
 Here we consider two composition constructs: sequence and parallel constructs, in building the composition web service.
 The QoS calculation models are described as follows:
+\subsubsection{Sequence construct}
+The composition web service executes each atomic service associated with a sequence construct in a definite sequence order.
+The aggregation value for total time ($T$) and total cost ($C$) is as the sum of time and cost of web services involved respectively.
+The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory.
+This construct is shown in Fig.
+\ref{sequence}.
+\subsubsection{Parallel construct}
+Web services in a parallel construct are executed concurrently.
+The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is determined by the most time-consuming path in the composition flow of the solution.
+This construct is presented in Fig.
+\ref{parallel}.
 
@@
 %\end{figure}
-\vspace{0.3cm}
+\vspace{0.2cm}
 %\begin{figure}
@@
 \end{figure}
-\subsubsection{Sequence construct}
-The composition web service executes each atomic service associated with a sequence construct in a definite sequence order.
-The aggregation value for total time ($T$) and total cost ($C$) is as the sum of time and cost of web services involved respectively.
-The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory.
-This construct is shown in Fig.
-\ref{sequence}.
-\subsubsection{Parallel construct}
-Web services in a parallel construct are executed concurrently.
-The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is determined by the most time-consuming path in the composition flow of the solution.
-This construct is presented in Fig.
-\ref{parallel}.
 
-\section{Comprehensive quality-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
+\section{Comprehensive Quality-Aware Service model}\label{qswsc_approach}
+In this section, we propose a comprehensive quality-aware service model to achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS for semantic web service composition.
 
-\begin{figure*}[h]
-\centering
-\fbox{\includegraphics[scale=.4]{overview.pdf}}
- \caption{Overview of POS-based automated semantic web service composition approach.}
- \label{overview}
-\end{figure*}
+\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
+The semantic service matchmaking aims to discover appropriate services from service repository.
+A semantic web service is defined by $S(F(I_{S}\in C_{1}, O_{S}\in C_{2}), NF(QoS_{S}))$, where both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology $O$ respectively, satisfying $O=\{C, Taxonomy\}$.
+A web service matching process is to match the output and input concepts of two services according to the Taxonomy within an ontology.
+To measure the quality of semantic matchmaking, different matching levels are typically considered in the literature \cite{paolucci2002semantic}.
+To understand these levels, let us define two web services associated with concept-related parameters in a particular domain.
+$S_{1}$ $(F(I_{S}\in C_{1}, O_{S}\in C_{2}), NF(QoS_{S}))$ and  $S_{2}$ $(F(I_{S}\in C_{3}, O_{S}\in C_{4}), NF(QoS_{S}))$ and an ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$.
+The matching levels to be considered are:
 
-In this section, we propose a comprehensive quality model for automated semantic service composition, and optimise both semantic matchmaking quality and QoS.
-PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}.
-Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing that often required by GP \cite{da2016particle}.
-Fig.
-\ref{overview} shows the overview of our approach with five steps.
-Step 1: The composition process is triggered by a composition goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional.
-Step 2: This composition goal are used to discover all relevant web services, which lead to a shrunken service repository that is subsequently used by PSO as a searching space.
-Step 3: A weighted graph representation is randomly built up from the an initial service queue that mapped to the particle's location, interleaving with semantic matchmaking process utilising ontology-based index cache.
-In the weighted graph, graph edges are assigned with semantic matchmaking quality as weights.
-Step 4: The fitness value of the weighted graph is evaluated to update the position of particle under PSO algorithm in Sect.
-\ref{pso_algorithm}, where the position is mapped to the index of service queue.
-later on, the updated service queue is used to decode a new weighted graph as the composition solution.
-Step 4.
-Lastly, the best position found in the searching space is selected and decode into the final optimised solution.
-This PSO-based approach is similar to \cite{da2016particle}, but we employ weighted graphs as a different solution presentation.
-
-\subsection{Semantic Matchmaking} \label{semantic_matchmaking}
-To perform semantic matchmaking, we transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match demonstrated in Sect.
-\ref{semantic Web service Discovery}.
-The matching process attempts to determine semantic matching between the source concepts of $C_{1}$ and the target concepts of $C_{2}$.
-Meanwhile, the quality of matched concepts are calculated in the quality model in subSection \ref{qualityModel}.
-The purpose of semantic matchmaking is to find more component services that could also potentially satisfy the quality of QoS with good functional quality.
+\begin{itemize}
+\item \textit{Exact} ($\equiv$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Exact match ($ O_{S} \in S_{1} \equiv I_{S} \in S_{2}$), if  Concept $C_{2}$ and Concept $C_{3}$ are equivalent.
+\item \textit{Plugin} ($\sqsubseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Plugin match ($O_{S} \in S_{1} \sqsubseteq_{n} I_{S} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of children concepts ($n=1$ stands for direct children).
+\item \textit{Subsume} ($\sqsupseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Subsume matched($O_{S} \in S_{1} \sqsupseteq_{n} I_{S} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of  Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of parent concepts ($n=1$ stands for direct parent).
+\item \textit{Fail} ($\perp$).
+Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are not matched (Fail) ($O_{S} \in S_{1} \perp I_{S} \in S_{2}$), if none of the previous matches discovered.
+\end{itemize}
 
@@
 
-\subsection{Ontology-based Index Cached Optimisation}\label{indexCache}
-In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively.
-To effectively construct weighted graphs, we pre-calculate semantic matchmaking quality.
-The key idea of the index is to create a mapping from the output-related concepts to potentially matched input-related concepts while considering different levels of match types.
-Meanwhile, this index size could also be reduced by only considering the concepts related in the shrunken service repository, which means the index cache is filtered by those task-relevant web services.
-This optimised cache also contributes to less and constant time for weighted graphs building through the whole evolutionary process.
-
-\subsection{Comprehensive Quality Model and Aggregation Matrix}\label{qualityModel}
+\subsection{Comprehensive Quality-Aware Model}\label{qualityModel}
 In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition.
@@
 
+\textbf{Semantic Web Service link}
 \textbf{Semantic matchmaking model}.
@@
 
-\subsection{Composition Weighted Graph}
-We defined our semantic web service composition solution as a weighted graph $WG = (V, E)$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of edges $E = {e_{1}, e_{2},...
-e_{n}}$.
-Each $e$ is associated with $q(e_{sm})$ as weight value that mapped to a pair of quality values $q(e_{mt})$ and $q(e_{s})$ on the edge level, and $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$.
-Here we provide an example of the web service composition, which is described in Fig.
-\ref{wscs}.
-The data of composition web service flows from the start to the end, where five web services involved and linked with each other using edge connections.
-Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},...
-e_{n}}$ assigned as weights.
-
-\begin{figure}[h]
-\centering
-\fbox{\includegraphics[scale=.29]{weigtedGraphExample.pdf}}
- \caption{Composition weighted graph solution}
- \label{wscs}
-\end{figure}
-
-\subsection{Fitness Calculation}
+\subsection{Objective Function}
 In real life, given a unique and optimised solution is always easier for customers to pick up directly when many quality criteria involved into decision making, rather than provided a set of solutions.
@@
 \noindent where $j$ $=$ $1$, and $2$, where $Q_1$ as $T$ and $Q_2$ as $C$.
+
+\section{PSO-based Appraoch to QoS-Aware Semantic Web Service Composition}\label{qswsc_approach}
+
+\begin{figure*}[h]
+\centering
+\fbox{\includegraphics[scale=.4]{overview.pdf}}
+ \caption{Overview of POS-based automated semantic web service composition approach.}
+ \label{overview}
+\end{figure*}
+
+PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}.
+Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing that often required by GP \cite{da2016particle}.
+Fig.
+\ref{overview} shows the overview of our approach with five steps.
+Step 1: The composition process is triggered by a composition goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional.
+Step 2: This composition goal are used to discover all relevant web services, which lead to a shrunken service repository that is subsequently used by PSO as a searching space.
+Step 3: A weighted graph representation is randomly built up from the an initial service queue that mapped to the particle's location, interleaving with semantic matchmaking process utilising ontology-based index cache.
+In the weighted graph, graph edges are assigned with semantic matchmaking quality as weights.
+Step 4: The fitness value of the weighted graph is evaluated to update the position of particle under PSO algorithm in Sect.
+\ref{pso_algorithm}, where the position is mapped to the index of service queue.
+later on, the updated service queue is used to decode a new weighted graph as the composition solution.
+Step 4.
+Lastly, the best position found in the searching space is selected and decode into the final optimised solution.
+This PSO-based approach is similar to \cite{da2016particle}, but we employ weighted graphs as a different solution presentation.
+
+\subsection{Ontology-based Index Cached Optimisation}\label{indexCache}
+In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively.
+To effectively construct weighted graphs, we pre-calculate semantic matchmaking quality.
+The key idea of the index is to create a mapping from the output-related concepts to potentially matched input-related concepts while considering different levels of match types.
+Meanwhile, this index size could also be reduced by only considering the concepts related in the shrunken service repository, which means the index cache is filtered by those task-relevant web services.
+This optimised cache also contributes to less and constant time for weighted graphs building through the whole evolutionary process.
+
+\subsection{Composition Weighted Graph}
+We defined our semantic web service composition solution as a weighted graph $WG = (V, E)$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of edges $E = {e_{1}, e_{2},...
+e_{n}}$.
+Each $e$ is associated with $q(e_{sm})$ as weight value that mapped to a pair of quality values $q(e_{mt})$ and $q(e_{s})$ on the edge level, and $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$.
+Here we provide an example of the web service composition, which is described in Fig.
+\ref{wscs}.
+The data of composition web service flows from the start to the end, where five web services involved and linked with each other using edge connections.
+Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},...
+e_{n}}$ assigned as weights.
+
+\begin{figure}[h]
+\centering
+\fbox{\includegraphics[scale=.29]{weigtedGraphExample.pdf}}
+ \caption{Composition weighted graph solution}
+ \label{wscs}
+\end{figure}
 
@@
 
-\subsection{Convergence Test}\label{convergenceTest}
-To analyse the effectiveness of our approach, we study the convergence rate of the proposed method in this section to understand the convergence rate of five tasks in WSC09.
-We analysis the performances during the whole evolutionary process in Fig.
-\ref{exp_fitnessvalue}, in which experiment results on five tasks are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average QoS for generation 0-99 with optimum.
-
-\begin{figure}[h]
-\centering{
-\fbox{
-\includegraphics[scale=.095]{convergency.pdf}}}
- \caption{Average Fitness, Average MatchType Quality, Average Similarity quality and Average QoS per generation with comprehensive quality optimum}
- \label{exp_fitnessvalue}
-\end{figure}
-Firstly, the average fitness value with optimum is calculated by averaging the best fitness found in each generation over 30 independent runs.
-We can see that there is a significant increase in the fitness values towards optimum between generation 0 and generation 15-25, the remaining generation continues to produce a steady but moderate improvement in the fitness value and eventually reach a plateau with no further improvements can be observed.
-The same behaviour is observed over the rest tasks.
-
-We also investigate the variation of quality of semantic matchmaking where average matchType quality with optimum and average similarity quality with optimum are studied in second and third column groups of Fig.
-\ref{exp_fitnessvalue}.
-Similar to the fitness values, clear evidence of fast convergence can be observed with respect to theses quality values.
-This observation is also consistent for the improvement of mean QoS quality with optimum shown in the last column in Fig \ref{exp_fitnessvalue}.
-Additionally, we don't see too much trade-off from the QoS as the a consistently increase in semantic matchmaking quality is observed.
-
 \subsection{Comparison Test with GP-based approach}\label{comparisonTestWithGP}
@@
 \end{tabular}
-\vspace{2mm}
-\centering
-\caption{Mean time results for comparing GP-based approach}
-\label{meanTime}
-\begin{tabular}{l|l|l}
-\hline
-\multicolumn{1}{c|}{Dataset} & PSO-based approach & GP-based approach  \\ \hline
-WSC09 01                     &12907 $\pm$ 8105      &5168 $\pm$ 520 $\downarrow$                \\ \hline
-WSC09 02                     &292346 $\pm$  96727    &27483 $\pm$  3083 $\downarrow$          \\ \hline
-WSC09 03                     & 12908 $\pm$ 8105 $\downarrow$  &28053 $\pm$ 3202            \\ \hline
-WSC09 04                     & 6553640 $\pm$ 1468204   &540418 $\pm$ 186540 $\downarrow$            \\ \hline
-WSC09 05                     & 1208193 $\pm$ 266916   &180408 $\pm$ 435247 $\downarrow$           \\ \hline
-\end{tabular}
 \end{table}

### 2017-01-29 paper.tex
update

@@
 
-\section{Comprehensive Quality-Aware Service model}\label{qswsc_approach}
+\section{Comprehensive Quality Model}\label{qswsc_approach}
 In this section, we propose a comprehensive quality-aware service model to achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS for semantic web service composition.
@@
 
-\subsection{Comprehensive Quality-Aware Model}\label{qualityModel}
+\subsection{Comprehensive Quality Model}\label{qualityModel}
 In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition.
@@
 
-\textbf{Semantic Web Service link}
-\textbf{Semantic matchmaking model}.
-Due to the discretisational characteristics of different match types and values assigned to matching types that driven by the cost of data integration and manipulation \cite{lecue2009optimizing}, partial ordering match types are considered to be one factor for the semantic matchmaking quality.
-For example, Exact matching type demands less time for computation compared to that of Plugin match.
+\textbf{Semantic web Service link}.
+In Fig.
+\ref{semanticLink}, $S_{1}$ and $S_{2}$ are linked to together if exists any parameter matchmaking between  Output of $S_1$ and Input of $S_2$.
+Therefore, measuring semantic matchmaking quality ($SM$) is to measure the quality of semantic web service link ($sm_{L}$), which is aggregated from the quality of parameter matchmaking ($sm_{P}$).
+This semantic web service link is adopt from \cite{lecue2009optimizing}.
+
+\begin{figure}[h]
+\centering
+\fbox{\includegraphics[scale=.38]{semanticLink.pdf}}
+ \caption{ An example of semantic web service link}
+ \label{semanticLink}
+\end{figure}
+
+\textbf{Semantic web service link quality model}.
+Due to the discretisational characteristics of different match types and values assigned to matching types that driven by the cost of data integration and manipulation \cite{lecue2009optimizing}, partial ordering match types are considered to be one factor for quality of parameter matchmaking, denoted as $mt_{p}$,  For example, Exact matching type demands less time for computation compared to that of Plugin match.
 Another factor in our proposed model is concept similarity, which could be evaluated based on the edge counting method defined in \cite{shet2012new}.
-This formula (\ref{equation1}) is used to estimate the similarity between concept-related parameters for selecting web services.
-Therefore, given the quality match type and the concept similarity of two parameters-related concepts, the semantic matchmaking quality of matched parameters is defined by Formula (\ref{equation2}), where the value of $q(p_ {mt})$ follows the same settings in \cite{lecue2009optimizing}.
+This formula (\ref{equation1}) is used to estimate the concept similarity between matching parameters, which is denoted as $s_{p}$.
+Therefore, given the quality of parameter matchmaking type and quality of parameter concept similarity, the quality of parameter matchmaking is defined by Formula (\ref{equation2}), where the value of $mt_{p}$ follows the same settings in \cite{lecue2009optimizing}.
 Particularly, 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).
@@
 \label{equation2}
-q(p_{sm}) \stackrel{.}{=} (q(p_ {mt}), \  q(p_ {s}))
+sm_{p} \stackrel{.}{=} (mt_ {p}, \  s_ {p})
 \end{equation}
 
-Further more, edges represent services connections in our weighted graph representations, where assigned weight value $q(e_{sm})$ is considered to be semantic matching quality on edge level according to parameter aggregations.
-The weight value $q(e_{sm})$ is defined in \ref{equation3}, where $q(e_ {mt})$ and $q(e_ {s})$ are the average value of concept-related parameters quality in $q(p_{mt})$ and $q(p_{s})$ respectively.
+Further more, semantic web service link represent services connections, where quality of semantic web service link $sm_{L})$ is considered to be semantic matching quality on service connection level by parameter aggregations.
+Therefore, $sm_{L}$ is defined in formula (\ref{equation3}), where $sm_{L}$ and $s_{L}$ are the average value of concept-related parameters quality in $mt_{P}$ and $s_{P}$ respectively.
 
@@
 \label{equation3}
-q(e_{sm}) \stackrel{.}{=} (q(e_ {mt}), \  q(e_ {s}))
+sm_{L} \stackrel{.}{=} (mt_ {L}, \  s_ {L})
 \end{equation}
@@
 \textbf{Comprehensive quality model}.
-Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional requirements.
-The comprehensive quality of our service composition representation refers to QoS of service vertices and Semantic matching quality of Edges in weighted graphs.
+The comprehensive quality model consider both semantic matchmaking quality and QoS.
+The semantic matchmaking quality refers to the quality of semantic web service link.
 Consequently, the comprehensive quality model is defined in Formula (\ref{equation4}), which could be further broken down into Formula (\ref{equation5}).
@@
 \label{equation4}
-q_{cq} \stackrel{.}{=} (q(e_ {sm}), \  q(v_ {QoS}))
+q_{cq} \stackrel{.}{=} (sm_ {L}, \  QoS_ {s})
 \end{equation}
@@
 \label{equation5}
-q_{cq} \stackrel{.}{=} (q(e_ {mt}), \  q(e_ {s}), \  q(v_{a}),\  q(v_{r}),\  q(v_{c}),\  q(v_{t}))
+q_{cq} \stackrel{.}{=} (mt_ {L}, \  s_ {L}, \  a_{s},\  r_{s},\  c_{s},\  t_{s})
 \end{equation}
 
-\textbf{Quality aggregate matrix}.
-The quality aggregation is defined based on the constructs of composition web services, in consideration of functional and non-functional properties.
-The quality on construct level is further calculated by following the rules summarised in Table \ref{table1}.
+\textbf{Semantic matchmaking quality aggregation}.
+The quality aggregation is defined based on the constructs of composition web services, in consideration of quality semantic web service link and QoS.
+The quality on composition solution is further calculated by following the formula (\ref{equation6})(\ref{equation7}), and QoS aggregation are discussed in Sect.
+\ref{Quality of Service and Composition Constructs}
 
-% Please add the following required packages to your document preamble:
-% \usepackage{multirow}
-\begin{table}[]
-\centering
-\caption{Quality aggregate matrix for semantic web service composition}
-\label{table1}
-\begin{tabular}{c|c|c|c|c}
-\hline
-\multicolumn{3}{c|}{Composition Construct}                                      & Sequence                             & Parallel \\ \hline
-\multirow{5}{*}{Quality} & \multirow{2}{*}{F}    & $Q(e_ {mt})$  &$\prod_{n=1}^{m} q(e_ {mt})$          &  $\prod_{n=1}^{m} q(e_ {mt})$ \\ \cline{3-5}
-                                &                                & $Q(e_ {s})$  & $(\sum_{n=1}^m q(e_ {s}))/m$        &  $(\sum_{n=1}^m q(e_ {s}))/m$  \\ \cline{2-5}   
-                                & \multirow{4}{*}{NF} & $Q(v_{a})$    & $\prod_{n=1}^{m} q(v_a)$             &  $\prod_{n=1}^{m} q(v_a)$ \\ \cline{3-5} 
-                                &                                & $Q(v_{r})$    & $\prod_{n=1}^{m} q(v_r)$             &  $\prod_{n=1}^{m} q(v_r)$ \\ \cline{3-5} 
-                                &                                & $Q(v_{c})$    & $\sum_{n=1}^m q(v_ {c})$             &  $\sum_{n=1}^m q(v_ {c})$ \\ \cline{3-5} 
-                                &                                & $Q(v_{t})$    & $\sum_{n=1}^m q(v_ {t})$             &  $max(q(v_ {t}))$ \\ \hline
-\end{tabular}
-\end{table}
+\begin{equation}
+\label{equation6}
+MT {=} \prod_{n=1}^{m} mt_ {L_{n}}
+\end{equation}
+\begin{equation}
+\label{equation7}
+S {=} (\sum_{n=1}^m s_ {L_{n}})/m
+\end{equation}
 
@@
 In real life, given a unique and optimised solution is always easier for customers to pick up directly when many quality criteria involved into decision making, rather than provided a set of solutions.
-Therefore, it is very practical to define a single fitness as a weighted sum of all the quality related components in Formula (\ref{equation6}), where weights setting is very flexible, it could be adjusted according to users' preferences.
-The fitness value of 1 means the best comprehensive quality and 0 means the worst.
-For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the fitness value falls within the range from 0 to 1.
-Therefore, the service composition problem in this paper is treated as a fitness maximisation problem.
+It is very practical to define a single fitness as a weighted sum of all the quality related components in Formula (\ref{equation8}).
+Note that weights can be adjusted according to users' preferences.
+The function value of 1 means the best comprehensive quality and 0 means the worst.
+For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the function value falls within the range from 0 to 1.
+Therefore, the service composition is try to maximise the value of objective function.
 \vspace{-0.2cm}
 \begin{equation}
-\label{equation6}
+\label{equation8}
 Fitness = w_1 \hat{MT} + w_2 \hat{S} + w_3 \hat{A} + w_4 \hat{R} + w_5(1 - \hat{T}) + w_6(1 - \hat{C})
@@
 \begin{equation}
-\label{equation7}
+\label{equation9}
 \hat{Q_k} = 
@@
 \begin{equation}
-\label{equation8}
+\label{equation10}
 \hat{Q_j} = 
@@
 
-\section{PSO-based Appraoch to QoS-Aware Semantic Web Service Composition}\label{qswsc_approach}
+\section{PSO-based Approach to QoS-Aware Semantic Web Service Composition}\label{qswsc_approach}
 
@@
 \fbox{\includegraphics[scale=.4]{overview.pdf}}
- \caption{Overview of POS-based automated semantic web service composition approach.}
+ \caption{Overview of POS-based approach to QoS-aware automated semantic web service composition.}
  \label{overview}
 \end{figure*}
+
+\subsection{Weighted Graph Composition}
+
+We defined our semantic web service composition solution as a weighted graph $WG = (V, E)$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of edges $E = {e_{1}, e_{2},...
+e_{n}}$.
+Each $e$ is associated with $q(e_{sm})$ as weight value that mapped to a pair of quality values $q(e_{mt})$ and $q(e_{s})$ on the edge level, and $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$.
+Here we provide an example of the web service composition, which is described in Fig.
+\ref{wscs}.
+The data of composition web service flows from the start to the end, where five web services involved and linked with each other using edge connections.
+Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},...
+e_{n}}$ assigned as weights.
+
+\begin{figure}[h]
+\centering
+\fbox{\includegraphics[scale=.29]{weigtedGraphExample.pdf}}
+ \caption{Composition weighted graph solution}
+ \label{wscs}
+\end{figure}
+
+\subsection{PSO-based Approach to QoS-Aware Semantic Web Service Composition}
 
@@
 This optimised cache also contributes to less and constant time for weighted graphs building through the whole evolutionary process.
-
-\subsection{Composition Weighted Graph}
-We defined our semantic web service composition solution as a weighted graph $WG = (V, E)$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of edges $E = {e_{1}, e_{2},...
-e_{n}}$.
-Each $e$ is associated with $q(e_{sm})$ as weight value that mapped to a pair of quality values $q(e_{mt})$ and $q(e_{s})$ on the edge level, and $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$.
-Here we provide an example of the web service composition, which is described in Fig.
-\ref{wscs}.
-The data of composition web service flows from the start to the end, where five web services involved and linked with each other using edge connections.
-Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},...
-e_{n}}$ assigned as weights.
-
-\begin{figure}[h]
-\centering
-\fbox{\includegraphics[scale=.29]{weigtedGraphExample.pdf}}
- \caption{Composition weighted graph solution}
- \label{wscs}
-\end{figure}
 

### 2017-01-29 paper.tex
update

@@
 
-We defined our semantic web service composition solution as a weighted graph $WG = (V, E)$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of edges $E = {e_{1}, e_{2},...
-e_{n}}$.
-Each $e$ is associated with $q(e_{sm})$ as weight value that mapped to a pair of quality values $q(e_{mt})$ and $q(e_{s})$ on the edge level, and $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$.
-Here we provide an example of the web service composition, which is described in Fig.
+We defined our semantic web service composition solution as a weighted graph $WG = (V, E)$, where $V$ is a set of services as vertex: $V=\{S1, S2...Sn \}$ and $E$ is a set of edges $E = \{e_{1}, e_{2},...
+e_{n} \}$.
+Each edge is mapped to a semantic web service link, so each edge $e$ is associated with $sm_{L}$ as weight value as a pair value of quality values $mt_{L}$ and $s_{L}$ on the edge level, Here we provide an example of semantic web service composition, which is described in Fig.
 \ref{wscs}.
 The data of composition web service flows from the start to the end, where five web services involved and linked with each other using edge connections.
-Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},...
-e_{n}}$ assigned as weights.
+Besides that, pair values that $mt_{L}$ and $s_{L}$ are calculated for all edges $e_{1}, e_{2},...
+e_{n}$ assigned as weights.
 
@@
 \centering
-\fbox{\includegraphics[scale=.29]{weigtedGraphExample.pdf}}
+\fbox{\includegraphics[scale=.28]{weigtedGraphExample.pdf}}
  \caption{Composition weighted graph solution}
@@
 \ref{overview} shows the overview of our approach with five steps.
-Step 1: The composition process is triggered by a composition goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional.
+Step 1: The composition process is triggered by a composition goal defined in Subsection \ref{problemDes}, which describes customers requirements both semantic matchmaking quality and QoS.
 Step 2: This composition goal are used to discover all relevant web services, which lead to a shrunken service repository that is subsequently used by PSO as a searching space.
@@
 Lastly, the best position found in the searching space is selected and decode into the final optimised solution.
-This PSO-based approach is similar to \cite{da2016particle}, but we employ weighted graphs as a different solution presentation.
+This PSO-based approach is similar to \cite{da2016particle}, but we employ weighted graphs as a different solution presentation with edges transferred from semantic web service links.
 
 \subsection{Ontology-based Index Cached Optimisation}\label{indexCache}
-In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively.
+In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic web service matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively.
 To effectively construct weighted graphs, we pre-calculate semantic matchmaking quality.
@@
      \ForEach{particles in the swarm}{
-     $queue \leftarrow$ particle's position vector\;
+     $queue \leftarrow$ map particle's position vector to service\;
      $WG \leftarrow$ $generateWeightedGraph$()\;
@@
 
-      \eIf{fitness value better than pBest }{    
-        Assign current fitness as new pBest\;
+      \eIf{fitness value better than \emph{pBest}}{    
+        Assign current fitness as new \emph{pBest}\;
        }{
-        Keep previous pBest\;
+        Keep previous \emph{pBest}\;
        }	
      }
-    Assign best particle's \emph{pBest} value to \emph{gBest}, if better than gBest\;
+    Assign best particle's \emph{pBest} value to \emph{gBest}, if better than \emph{gBest}\;
  	Calculate the velocity of each particle\;
@@
     		 \ForEach{$I$ in $ws.inputs$}{
-    		$p_{mt} \leftarrow$ query $IndexCache$\;
-     		$p_{s} \leftarrow$ query $IndexCache$\;
+    		$mt_{P}, s_{P} \leftarrow$ query $IndexCache$\;
+     		$mt_{L} \leftarrow$ aggregation($mt_{P}$)\;
+ 			$s_{L} \leftarrow$ aggregation($s_{P}$)\;
               }
-        $e_{sm} \leftarrow$ aggregation($p_{mt}$,$p_{s}$)\;
-        $WG.edge \leftarrow$  $e_{sm} $\;
+        $sm_{L} \leftarrow$ aggregation($mt_{L}$,$s_{L}$)\;
+        $WG.edge \leftarrow$  $sm_{L} $\;
         $WG \leftarrow$ new $wsNode$()\;
@@
 \multicolumn{2}{c|}{WSC09}              & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
-\multirow{3}{*}{Task1}  &$Q_{mt}$   &0.189787 $\pm$ 0.039278686            &0.221862 $\pm$ 0.009582 $\uparrow$ \\ \cline{2-4} 
-                        &$Q_{s}$    &0.884962 $\pm$ 0.014140               &0.894082 $\pm$ 0.009206 $\uparrow$ \\ \cline{2-4}
-                        &$Q_{QoS}$  &0.278730 $\pm$ 0.007786               &0.280222 $\pm$ 0.008212                          \\ \hline
-\multirow{3}{*}{Task2}  &$Q_{mt}$   &0.001795 $\pm$ 0.000719               &0.001977 $\pm$ 0.001566 $\uparrow$ \\ \cline{2-4} 
-                        &$Q_{s}$    &0.906971 $\pm$ 0.005855               &0.923970 $\pm$ 0.006898 $\uparrow$   \\ \cline{2-4}
-                        &$Q_{QoS}$  &0.239979 $\pm$ 0.000578 $\uparrow$    &0.238596 $\pm$ 0.001264 \\ \hline
-\multirow{3}{*}{Task3}  &$Q_{mt}$   &0.158526 $\pm$ 0.014028               &0.245830 $\pm$ 0.007761 $\uparrow$   \\ \cline{2-4} 
-                        &$Q_{s}$    &0.949109 $\pm$ 0.002331               &0.972765 $\pm$ 0.002980 $\uparrow$           \\ \cline{2-4}
-                        &$Q_{QoS}$  &0.247002 $\pm$ 0.000661 $\uparrow$    &0.245631 $\pm$ 0.000431            \\ \hline
-\multirow{3}{*}{Task4}  &$Q_{mt}$   &0.000000 $\pm$ 0.000000               &0.000004 $\pm$ 0.000002 $\uparrow$ \\ \cline{2-4} 
-                        &$Q_{s}$    &0.879514 $\pm$ 0.007456               &0.920733 $\pm$ 0.000001 $\uparrow$ \\ \cline{2-4}
-                        &$Q_{QoS}$  &0.242297 $\pm$ 0.000507 $\uparrow$    &0.236677 $\pm$ 0.002211  \\ \hline
-\multirow{3}{*}{Task5}  &$Q_{mt}$   &  0.000042 $\pm$ 0.000030             &0.000078 $\pm$ 0.000020 $\uparrow$           \\ \cline{2-4} 
-                        &$Q_{s}$    &  0.915933 $\pm$ 0.012888             &0.927678 $\pm$ 0.002578 $\uparrow$                 \\ \cline{2-4}
-                        &$Q_{QoS}$  & 0.238189 $\pm$ 0.000240 $\uparrow$      &  0.237485 $\pm$  0.000328  \\ \hline                                                   
+\multirow{3}{*}{Task1}  &$MT$   &0.189787 $\pm$ 0.039278686            &0.221862 $\pm$ 0.009582 $\uparrow$ \\ \cline{2-4} 
+                        &$S$    &0.884962 $\pm$ 0.014140               &0.894082 $\pm$ 0.009206 $\uparrow$ \\ \cline{2-4}
+                        &$QoS$  &0.278730 $\pm$ 0.007786               &0.280222 $\pm$ 0.008212                          \\ \hline
+\multirow{3}{*}{Task2}  &$MT$   &0.001795 $\pm$ 0.000719               &0.001977 $\pm$ 0.001566 $\uparrow$ \\ \cline{2-4} 
+                        &$S$    &0.906971 $\pm$ 0.005855               &0.923970 $\pm$ 0.006898 $\uparrow$   \\ \cline{2-4}
+                        &$QoS$  &0.239979 $\pm$ 0.000578 $\uparrow$    &0.238596 $\pm$ 0.001264 \\ \hline
+\multirow{3}{*}{Task3}  &$MT$   &0.158526 $\pm$ 0.014028               &0.245830 $\pm$ 0.007761 $\uparrow$   \\ \cline{2-4} 
+                        &$S$    &0.949109 $\pm$ 0.002331               &0.972765 $\pm$ 0.002980 $\uparrow$           \\ \cline{2-4}
+                        &$QoS$  &0.247002 $\pm$ 0.000661 $\uparrow$    &0.245631 $\pm$ 0.000431            \\ \hline
+\multirow{3}{*}{Task4}  &$MT$   &0.000000 $\pm$ 0.000000               &0.000004 $\pm$ 0.000002 $\uparrow$ \\ \cline{2-4} 
+                        &$S$    &0.879514 $\pm$ 0.007456               &0.920733 $\pm$ 0.000001 $\uparrow$ \\ \cline{2-4}
+                        &$QoS$  &0.242297 $\pm$ 0.000507 $\uparrow$    &0.236677 $\pm$ 0.002211  \\ \hline
+\multirow{3}{*}{Task5}  &$MT$   &  0.000042 $\pm$ 0.000030             &0.000078 $\pm$ 0.000020 $\uparrow$           \\ \cline{2-4} 
+                        &$S$    &  0.915933 $\pm$ 0.012888             &0.927678 $\pm$ 0.002578 $\uparrow$                 \\ \cline{2-4}
+                        &$QoS$  & 0.238189 $\pm$ 0.000240 $\uparrow$      &  0.237485 $\pm$  0.000328  \\ \hline                                                   
 \end{tabular}

### 2017-01-29 paper.tex
update

@@
 Existing works on web service composition often concerns either semantic service composition or QoS-aware service composition.
-However, there are few works concerns both semantic matchmaking quality and QoS at the same time and achieve a more
-desirable tradeoff in consideration of both sides.
-Therefore, In this paper, proposed a genral comprehensive quality model that can achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS.
-This model is also suitable to be tackled through EC algorithms, and we develope a PSO-based service composition approach with explicit support for the comprehensive model, which can generate more desiable balanced web service composition that meet both senmantic matchmaking quality and QoS requirement by comparing existing QoS evaluation model using benchmark dataset.
-We also conduct an experiment shows our PSO-based mehtod performs better in finding more optimised solution by comparing one existing GP-based method.
+However, there are few works concerns both semantic matchmaking quality and QoS at the same time and achieve a more desirable tradeoff in consideration of both sides.
+Therefore, In this paper, proposed a general comprehensive quality model for semantic matchmaking quality and QoS.
+This model is also suitable to be tackled through EC algorithms, and we develop a PSO-based service composition approach with explicit support for the comprehensive model, which can generate a more desirable balanced web service composition that meet both semantic matchmaking quality and QoS requirement by comparing existing QoS evaluation model using benchmark dataset.
+We also conduct an experiment shows our PSO-based method performs better in finding more optimised solution by comparing one existing GP-based method.
 
@@
 
-The overall goal of this paper is to \textit{develop an comprehensive appraoch to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}.
+The overall goal of this paper is to \textit{develop an comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}.
 Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matchmaking quality optimisation in our proposed comprehensive quality model.
@@
 
- \item To evaluate our proposed approach, we conduct experiment to compare our comphensive quality model with QoS evaluation model, we also compare an one existing GP approach with our appraoch using our comprehensive model.
+ \item To evaluate our proposed approach, we conduct experiment to compare our comprehensive quality model with QoS evaluation model, we also compare an one existing GP approach with our approach using our comprehensive model.
 Both comparison utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}
@@
 \section{Related Work} \label{relatedWork}
-Substantial work on web service composition either focused on semantic web service composiiton \cite{boustil2014semantic,mier2015integrated, bansal2016generalized} or QoS-aware web service composiiton \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining}, However few researchers addressed both semantic mathmaking quality and QoS requirements at the same time for web service composition problems.
+Substantial work on web service composition focused on either semantic web service composiiton \cite{boustil2014semantic,mier2015integrated, bansal2016generalized} or QoS-aware web service composiiton \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining,ma2015hybrid}, However few researchers addressed both semantic mathmaking quality and QoS requirements at the same time for web service composition problems.
 To the best of our knowledge, \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} reported some recent attempts on service composition that considers both aspects.
 
-\cite{boustil2014semantic,mier2015integrated, bansal2016generalized} captures the semantics of the parameters of web services using some kind of logic (e.g., description logic) for enabling semantic web service composition, where the number of web servces or length of the graph is minimised to reach the optimised graph-based compositin solutions.
-However, these approaches always need to improve their scalability for a large number of web services, and the evalution method does not fit for today's customers' requirements properly.
+\cite{boustil2014semantic,mier2015integrated, bansal2016generalized} captures the semantics of the parameters of web services using some kind of logic (e.g., description logic) for enabling semantic web service composition, where the number of web services or length of the graph is minimised to reach the optimised graph-based composition solutions.
+However, these approaches always need to improve their scalability for a large number of web services, and the evaluation method does not fit for today's customers' requirements properly.
 
@@
 \cite{gupta2015optimization} employ an Genetic Algorithm to the problem of QoS-ware web service composition, and a set of binary strings are used as individuals, which demands to be decoded into composition solutions.
-Genetic Programming are employed by  \cite{yu2013adaptive} with direct reprentation of compsotion solutions, the overall quality of solutions are measured by a fitness function that is liable for penalising infeasible solutions.
+Genetic Programming are employed by  \cite{yu2013adaptive} with direct representation of composition solutions, the overall quality of solutions are measured by a fitness function that is liable for penalising infeasible solutions.
 A hyper approach employs both a greedy search algorithm and Genetic Programming (GP) is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness.
@@
 PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}, an indirect PSO-based approach was introduced in \cite{da2016particle}.
-An opimised queue is used as indirect representation as composition solution that decoding into Direct Acyclic Graph (DAG).
-These QoS-aware appraoches does not consider semantic matchmaking quality, which could lead to over-general outputs to be produced by selected services, The finding is evidently supported by our first comparision experiment.
+An optimised queue is used as indirect representation as composition solution that decoding into Direct Acyclic Graph (DAG).
+These QoS-aware approaches does not consider semantic matchmaking quality, which could lead to over-general outputs to be produced by selected services, The finding is evidently supported by our first comparison experiment.
 In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users.
@@
 This evaluation takes huge cost and time for the domain experts to establish required ontology.
-Another GA-based appraoch work \cite{fanjiang2014semantic} employs a sequence of fitness functions are used in the binary selection of chromosomes, where semantic matchmaking quality is evaluate in two fitness functions considering concept similarity and parameter similarity respectively, However, different semantic matchmaking types are ignored in evaluation model.
-The work \cite{pop2009immune} as an immune-inspired web service composition approach employ indirect reprentation that a binary alphabet to encode a planning graph, where the semantic matchmaking quality is measured  by the similarity using information retrieval technique.
+Another GA-based approach work \cite{fanjiang2014semantic} employs a sequence of fitness functions are used in the binary selection of chromosomes, where semantic matchmaking quality is evaluate in two fitness functions considering concept similarity and parameter similarity respectively, However, different semantic matchmaking types are ignored in evaluation model.
+The work \cite{pop2009immune} as an immune-inspired web service composition approach employ indirect representation that a binary alphabet to encode a planning graph, where the semantic matchmaking quality is measured  by the similarity using information retrieval technique.
 
-In summary, composition solutions from semantic web service composition does not consier QoS \cite{boustil2014semantic,mier2015integrated, bansal2016generalized}, and QoS-aware web service composiiton \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining} does not consider distinguished matchmaking quality in their fitness function.
-Few works do consider both quality aspects, but some limitatins lie in semi-automated approach \cite{lecue2009optimizing}, less general semantic quality measurement \cite{lecue2009optimizing, pop2009immune}, or semantic matchmaking types ignorance \cite{pop2009immune}.
-In addition, experiments design for  \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} are not conducted using benchamark dataset for the scalability, only small datasets are utilised that might suffer scalability.
-Results analysis for \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} also do not evidently point out what desired balance could be rearched by considering semantic matchmaking quality and QoS.
-Therefore, we proposed a general comprehensive quality model which achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS to fill the gaps dissussed above, and then we proposed a POS-based method with explicit support for the comprehensive model, and evaluate its performace by comparing with one existing GP-based approach.
+In summary, composition solutions from semantic web service composition does not consider QoS \cite{boustil2014semantic,mier2015integrated, bansal2016generalized}, and QoS-aware web service composiiton \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining,ma2015hybrid} does not consider distinguished matchmaking quality in their fitness function.
+Few works do consider both quality aspects, but some limitations lie in semi-automated approach \cite{lecue2009optimizing}, less general semantic quality measurement \cite{lecue2009optimizing, pop2009immune}, or semantic matchmaking types ignorance \cite{pop2009immune}.
+In addition, experiments design for  \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} are not conducted using benchmark dataset for the scalability, only small datasets are utilised that might suffer scalability.
+Results analysis for \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} also do not evidently point out what desired balance could be reached by considering semantic matchmaking quality and QoS.
+Therefore, we proposed a general comprehensive quality model which achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS to fill the gaps discussed above, and then we proposed a POS-based method with explicit support for the comprehensive model, and evaluate its performance by comparing with one existing GP-based approach.
 
@@
 \subsection{Quality of Service and Composition Constructs}\label{Quality of Service and Composition Constructs}
-According to \cite{zeng2003quality}, four most often considered QoS parameters are response time, cost, reliability and availability decribed as follows:
+According to \cite{zeng2003quality}, four most often considered QoS parameters are response time, cost, reliability and availability described as follows:
 \begin{itemize}
@@
 
-\textbf{Semantic web service link quality model}.
+\textbf{Semantic web matchmaking quality model}.
 Due to the discretisational characteristics of different match types and values assigned to matching types that driven by the cost of data integration and manipulation \cite{lecue2009optimizing}, partial ordering match types are considered to be one factor for quality of parameter matchmaking, denoted as $mt_{p}$,  For example, Exact matching type demands less time for computation compared to that of Plugin match.
@@
 \begin{equation}
-q(p_ {s}){=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
+s_{P}{=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
 \label{equation1}
@@
 \subsection{Comparison Test with QoS Evaluation Model}\label{comparisonTest}
-In this section, we analyse the composition solution generated by using our approach comparing with QoS-aware approach.
-First, we look at mean value of $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ at optimum at the 100th generation for two approaches, shown in Table \ref{decisionTable}.
-The QoS-aware approach record $Q_{mt}$, $Q_{s}$ and utilise fitness function $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$, but $MT$ and $S$ are recorded, and $Q_(QoS)$ is normalised from 0 to 0.5 to make it comparable to $Q_{QoS}$ in our approach.
-We observe an interesting pattern from Table \ref{decisionTable} using statistic analysis: mean value of $Q_{mt}$ and $Q_{s}$ at optimum by our approach is consistently higher than those by QoS-aware approach.
-Meanwhile, $Q_{QoS}$ generated by QoS-aware approach can obtain a slightly higher value than that of our approach.
-In conclusion, we can perceive that our evaluation could find out better functional quality with a reasonable trade off in QoS.
+QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid} do consider two semantic matchmaking types (Exact and Plugin) for discovering desired web service, but there is no measurement of matchmaking types and concept similarity, so the weights for $MT$ and $S$ are considered to be 0.
+Consequently, our evaluation mode become a widely used fitness function $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$ \cite{ma2015hybrid} for QoS-aware web service composition.
+To compare the composition solution generated by using our approach comparing with QoS-aware approach.
+We look at mean value of $MT$, $S$ and $QoS$ at optimum at the 100th generation for two approaches.
+In QoS-aware approach, $MT$ and $S$ are recorded, and $QoS$ is normalised from 0 to 0.5 to make it comparable, besides that, all weights in QoS-aware fitness function are set equally to 0.25.
+
+We observe an interesting pattern from Table \ref{decisionTable} using statistic analysis: mean value of $MT$ and $S$ at optimum by our approach is consistently higher than those by QoS-aware approach.
+Meanwhile, $QoS$ generated by QoS-aware approach can achieve a more desirable tradeoff in both semantic matchmaking quality and  QoS.
+
 \begin{table}[]
@@
 
-Second, to compare the results generated from two evaluation approaches, we demonstrate an example solution that shows the differences in web services composition obtained through two different methods.
+To compare the results generated from two evaluation approaches, we demonstrate an example solution that shows the differences in web services composition obtained through two different methods.
 Fig.
-\ref{comparisontest} $(1)$ and $(2)$ show two composition weighted graphs as the two optmised solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method respectively.
+\ref{comparisontest} $(1)$ and $(2)$ show two composition weighted graphs as the two optimised solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method respectively.
 Two approaches generate exactly the same service workflow structure where those service vertices and edges denoted in red are different.
@@
 \ref{comparisontest} $(3)$.
-We also look at $\Delta Q$ which reveals the amount of variation on quality between two methods, where the positive values means the benefits gained under our approach while the negative values means the trade-off.
+We also look at $\Delta Q$ which reveals the amount of variation on quality between two methods, where the positive values means the benefits gained under our approach while the negative values means the tradeoff.
 To demonstrate the benefits of the positive value, we analyse the smallest positive $\Delta Q$ corresponding to $e_4$ and demonstrate how the output and required input are different under two approaches in Fig.
@@
 There exist $Inst795998200$ $\in$ $Con103314376$ $\sqsubseteq_{2}$ $Inst658772240$ $\in$ $Con2113572083$ and $Inst582785907$ $\in$ $Con2037585750$ $\sqsubseteq_{3}$ $Inst658772240$ $\in$ $Con2113572083$.
-It is obvious that our approach selects the service providing $Inst795998200$ that are closer to the users' requirements suggesting that our method can produce better semantic matchmaking quality.
+It is obvious that our approach selects the service providing $Inst795998200$ that are closer to the users' requirements suggesting that our method can produce better semantic matchmaking quality in terms of less general outputs.
 
@@
 \subsection{Comparison Test with GP-based approach}\label{comparisonTestWithGP}
-We compare one GP-based approach  \cite{ma2015hybrid} with our PSO method, where the individuals are tree structure with strict constrains transferred from a DAG employing unfolding techniques.
-We further mark all the service nodes in the tree representation with all their outgoing edges for considering semantic matchmaking quality, and those edges information are maintained correctly in the crossover and mutation.
-At last, we evaluate both semantic matchmaking quality and QoS simultaneously using the discussed the comprehensive quality model to investigate the performances of two approaches.
-To make a fair comparison with our PSO approach considering the same number of evaluations (3000 times), we adjust the parameters settings for GP approach \cite{ma2015hybrid} to 30 individual for 100 generations.
+To evaluate the performance of our proposed PSO-based approach, we compare one GP-based approach  \cite{ma2015hybrid} with our PSO method.
+We consider the links between child nodes and parent nodes as semantic web service links for semantic matchmaking quality, and those links information are maintained correctly for the crossover and mutation.
+Therefore, we evaluate both semantic matchmaking quality and QoS simultaneously using the proposed comprehensive quality model.
+To make a fair comparison with our PSO-based, we consider the same number of evaluations (3000 times), we set the parameters settings for GP-based approach \cite{ma2015hybrid}, 30 individuals and 100 generations.
 
-The Table \ref{meanFitness} shows the mean fitness values accomplished by two methods and Table \ref{meanTime} shows the average execution time required by them.
-We employ statistical analysis to test the significant differences in mean fitness value and execution time.
+The Table \ref{meanFitness} shows the mean fitness values accomplished by two methods.
+We employ statistical analysis to test the significant differences in mean fitness value.
 The results show that the PSO-based approach performs better in four of five tasks.
-However, there is also a trade-off between optimised solution and execution time.
-We can see the PSO-based approach takes longer execution time, it due to that every individual in each generation must be decoded into a solution from optimised queue, and this process is very time-consuming.
-However, In GP, the initialisation first population is costly in time as transformation process from a DAG, but following new individuals are generated through mutation and crossover, which demands much less time comparing decoding process.
 
@@
 
+At last, We also compare the average fitness value with optimum through the evolutionary process for both two approaches over 30 independent runs.
+Fig.
+\ref{psovsgp} is an example of convergence rate from Task 3, where the behaviour of PSO-based approach presents a very clear evidence of fast convergence and reaches a better-optimised solution, while the performance of GP is barely satisfactory, as GP-based method improves its fitness value gradually.
+
 \begin{figure}[h]
@@
 
-At last, We also compare the average fitness value with optimum through the evolutionary process for both two approaches over 30 independent runs.
-Fig.
-\ref{psovsgp} is an example of convergence rate from Task 3, where the behaviour of PSO-based approach presents a very clear evidence of fast convergence and reaches a better-optimised solution, while the performance of GP is barely satisfactory, as GP-based method improves its fitness value gradually.
-
 \section{Conclusion}\label{conclusion}
-This work introduces a comprehensive evaluation model employed our PSO-based method for QoS-aware automated semantic automated web service composition that combines the quality of semantic matchmaking with QoS.
-The results show that our approach obtain better functional quality with a reasonable trade-off in QoS.
+This work introduces a general comprehensive evaluation model that for considering semantic matchmaking quality and QoS.
+We proposed a PSO-based service composition approach utilising our proposed quality mode that can achieve a desired balance off of both quality aspects.
 Also, we compare one GP-approach with our PSO-based method to show our performance results in finding better-optimised solution.
-Future works could investigate other direct or indirect representations of semantic web service composition on semantic web service composition, and look into other EC techniques to evaluate their performance.
-Also, we could reshape the problem on providing customers with a set of solutions to choose from, rather than a single solution, so research question is redefined as multi-objectives or many objective problems.
+Future works can investigate multi-objective EC techniques to produce a set of composition solutions for the situations that quality preference is not known.
 

### 2017-01-29 paper.tex
up

@@
 \usepackage{color,graphicx,epstopdf,changepage,amsmath,multirow}
-
+\usepackage[justification=centering]{caption}
 \SetAlgoCaptionSeparator{.\space}
@@
 \ref{semanticLink}, $S_{1}$ and $S_{2}$ are linked to together if exists any parameter matchmaking between  Output of $S_1$ and Input of $S_2$.
-Therefore, measuring semantic matchmaking quality ($SM$) is to measure the quality of semantic web service link ($sm_{L}$), which is aggregated from the quality of parameter matchmaking ($sm_{P}$).
+Therefore, measuring semantic matchmaking quality ($SM$) is to measure the overall quality of semantic web service link ($sm_{L}$), which is aggregated from the quality of parameter matchmaking ($sm_{P}$).
 This semantic web service link is adopt from \cite{lecue2009optimizing}.

### 2017-01-30 paper.tex
update

@@
 To meet users' requirement, one often needs to consider both semantic matchmaking quality and QoS simultaneously.
-Existing works on web service composition often concerns either semantic service composition or QoS-aware service composition.
+Existing works on web service composition often concerns either semantic web  service composition or QoS-aware web service composition.
 However, there are few works concerns both semantic matchmaking quality and QoS at the same time and achieve a more desirable tradeoff in consideration of both sides.
 Therefore, In this paper, proposed a general comprehensive quality model for semantic matchmaking quality and QoS.
-This model is also suitable to be tackled through EC algorithms, and we develop a PSO-based service composition approach with explicit support for the comprehensive model, which can generate a more desirable balanced web service composition that meet both semantic matchmaking quality and QoS requirement by comparing existing QoS evaluation model using benchmark dataset.
-We also conduct an experiment shows our PSO-based method performs better in finding more optimised solution by comparing one existing GP-based method.
+This model is also suitable to be tackled through EC algorithms, and we develop a PSO-based service composition approach with explicit support for the comprehensive model, which can generate a more desirable balance in considering semantic matchmaking quality and QoS requirement by comparing existing QoS evaluation model.
+We also conduct an experiment shows that our PSO-based method performs better in finding more optimised solution by comparing one existing GP-based method.
 
@@
 This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems.
-Due to the increase of the number of large-scale enterprise applications, the number of Web services has increased substantially and unprecedentedly.
+Due to the increasing number of large-scale enterprise applications, the number of Web services has increased substantially and unprecedentedly.
 Therefore, manual and semi-automated web service composition are considered to be less efficient while automated web service composition enjoys less human intervention, less time consumption, and high productivity.
@@
 \textit{Semantic web services composition} is distinguished from the syntactic service composition, with the hope of eliminating conflicts by the semantic level of web services.
-In the past few years, substantial works have been done on semantic web service composition \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune}.
-However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously.
-To a given service request, the quality of service composition solution depends on both QoS and quality of semantic matchmaking.
+In the past few years, substantial works have been done on semantic web service composition \cite{boustil2014semantic, mier2015integrated, bansal2016generalized}.
+However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously and achieved a desired balance.
 
@@
 Particle Swarm Optimisation (PSO) has show its promise in searching near-optimised service composition solutions \cite{da2016particle}.
-We will propose a PSO-based service composition approach using our comprehensive quality model to measure semantic matchmaking in automated semantic web service composition.
+We will propose a PSO-based service composition approach with explicit support for our proposed quality mode.
 We will achieve three objectives in this work as follows:
@@
 To do that we will first propose a representation of semantic service composition, which can model the quality of semantic matchmaking and QoS together.
-A particle is then used to represent a queue of services that can be used to decoded into a near-optimised semantic service composition solution.
 
- \item To evaluate our proposed approach, we conduct experiment to compare our comprehensive quality model with QoS evaluation model, we also compare an one existing GP approach with our approach using our comprehensive model.
+ \item To evaluate our proposed approach, we conduct experiment to compare our comprehensive quality model with one widely used QoS evaluation model, we also compare an one existing GP approach with our PSO-based approach using our comprehensive model.
 Both comparison utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}
@@
 
-\cite{boustil2014semantic,mier2015integrated, bansal2016generalized} captures the semantics of the parameters of web services using some kind of logic (e.g., description logic) for enabling semantic web service composition, where the number of web services or length of the graph is minimised to reach the optimised graph-based composition solutions.
-However, these approaches always need to improve their scalability for a large number of web services, and the evaluation method does not fit for today's customers' requirements properly.
+\cite{boustil2014semantic,mier2015integrated, bansal2016generalized} captures the semantics of web services' parameters using some kind of logic (e.g., description logic) for enabling semantic web service composition, where the number of web services or length of the graph is minimised to reach the optimised graph-based composition solutions.
+However, these approaches need to be improved for the scalability that considering a large number of web services, and the evaluation method does not fit properly for customers' complex requirements.
 
 A heuristic service composition method is proposed by Qi et al.
-\cite{qi2010combining}for QoS-aware web service composiiton, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal for QoS consideration.
-but obviously there exists scalability problem for enumeration techniques.
+\cite{qi2010combining} for QoS-aware web service composiiton, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal for QoS.
+Obviously, there exists scalability problem for enumeration techniques.
 
@@
 A hyper approach employs both a greedy search algorithm and Genetic Programming (GP) is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness.
-In particularly, the greedy search is used to generate directed acrylic graph as composition solutions, which is further transferred to tree structure using unfolding techniques for initialisation and mutation during the evolutionary process.
+In particularly, the greedy search is used to generate directed acrylic graph as composition solutions, which is further transferred to the tree structure for initialisation and mutation using unfolding techniques.
 To eliminating the transformation process from DAG, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of Directed Acyclic Graph(DAG) employing Graph-based evolutionary operators like crossover and mutation.
@@
 Lecue et al.
-\cite{lecue2009optimizing} employ Genetic Algorithm for semi-automated web service composition considering semantic matchmaking quality and QoS, where the semantic matchmaking quality is measured the quality of semantic links that requires formal definition of ontology in Description logic.
+\cite{lecue2009optimizing} employ Genetic Algorithm for semi-automated web service composition considering semantic matchmaking quality and QoS, where the semantic matchmaking quality is measured by the quality of semantic links that requires formal definition of ontology in Description Logic.
 This evaluation takes huge cost and time for the domain experts to establish required ontology.
-Another GA-based approach work \cite{fanjiang2014semantic} employs a sequence of fitness functions are used in the binary selection of chromosomes, where semantic matchmaking quality is evaluate in two fitness functions considering concept similarity and parameter similarity respectively, However, different semantic matchmaking types are ignored in evaluation model.
+Another GA-based approach work \cite{fanjiang2014semantic} employs a sequence of fitness functions are used in the binary selection of chromosomes, where semantic matchmaking quality is evaluate in two fitness functions considering concept similarity and parameter similarity respectively, but different semantic matchmaking types are ignored in the evaluation model.
 The work \cite{pop2009immune} as an immune-inspired web service composition approach employ indirect representation that a binary alphabet to encode a planning graph, where the semantic matchmaking quality is measured  by the similarity using information retrieval technique.
 
-In summary, composition solutions from semantic web service composition does not consider QoS \cite{boustil2014semantic,mier2015integrated, bansal2016generalized}, and QoS-aware web service composiiton \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining,ma2015hybrid} does not consider distinguished matchmaking quality in their fitness function.
+In summary, composition solutions from semantic web service composition \cite{boustil2014semantic,mier2015integrated, bansal2016generalized} does not consider QoS, and QoS-aware web service composiiton \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining,ma2015hybrid} does not consider distinguished matchmaking quality in their fitness function.
 Few works do consider both quality aspects, but some limitations lie in semi-automated approach \cite{lecue2009optimizing}, less general semantic quality measurement \cite{lecue2009optimizing, pop2009immune}, or semantic matchmaking types ignorance \cite{pop2009immune}.
@@
 This overall composition goal is demonstrated in two parts: functional part and non-functional part.
-The functional part is defined by a given task input and a desired task output.
-The nonfunctional part specifies QoS.
+The functional part is defined by given task input and desired task output.
+The nonfunctional part specifies overall QoS requirements.
 To accomplish the composition goal, two stages are involved, services discovery and service selection.
@@
 \section{Comprehensive Quality Model}\label{qswsc_approach}
-In this section, we propose a comprehensive quality-aware service model to achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS for semantic web service composition.
+In this section, we propose a general comprehensive quality-aware service model in consideration of both semantic matchmaking quality and QoS for semantic web service composition.
 
@@
 To understand these levels, let us define two web services associated with concept-related parameters in a particular domain.
-$S_{1}$ $(F(I_{S}\in C_{1}, O_{S}\in C_{2}), NF(QoS_{S}))$ and  $S_{2}$ $(F(I_{S}\in C_{3}, O_{S}\in C_{4}), NF(QoS_{S}))$ and an ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$.
+$S_{1}$ $(F(I_{S_1}\in C_{1}, O_{S_1}\in C_{2}), NF(QoS_{S_1}))$ and  $S_{2}$ $(F(I_{S_2}\in C_{3}, O_{S_2}\in C_{4}), NF(QoS_{S_2}))$ and an ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$.
 The matching levels to be considered are:
@@
 \begin{itemize}
-\item \textit{Exact} ($\equiv$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Exact match ($ O_{S} \in S_{1} \equiv I_{S} \in S_{2}$), if  Concept $C_{2}$ and Concept $C_{3}$ are equivalent.
-\item \textit{Plugin} ($\sqsubseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Plugin match ($O_{S} \in S_{1} \sqsubseteq_{n} I_{S} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of children concepts ($n=1$ stands for direct children).
-\item \textit{Subsume} ($\sqsupseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Subsume matched($O_{S} \in S_{1} \sqsupseteq_{n} I_{S} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of  Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of parent concepts ($n=1$ stands for direct parent).
+\item \textit{Exact} ($\equiv$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Exact match ($ O_{S_1} \in S_{1} \equiv I_{S_2} \in S_{2}$), if  Concept $C_{2}$ and Concept $C_{3}$ are equivalent.
+\item \textit{Plugin} ($\sqsubseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Plugin match ($O_{S_1} \in S_{1} \sqsubseteq_{n} I_{S_2} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of children concepts ($n=1$ stands for direct children).
+\item \textit{Subsume} ($\sqsupseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Subsume matched($O_{S_1} \in S_{1} \sqsupseteq_{n} I_{S_2} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of  Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of parent concepts ($n=1$ stands for direct parent).
 \item \textit{Fail} ($\perp$).
-Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are not matched (Fail) ($O_{S} \in S_{1} \perp I_{S} \in S_{2}$), if none of the previous matches discovered.
+Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are not matched (Fail) ($O_{S_1} \in S_{1} \perp I_{S_2} \in S_{2}$), if none of the previous matches discovered.
 \end{itemize}
@@
 \subsection{Comprehensive Quality Model}\label{qualityModel}
-In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition.
+We propose a comprehensive quality model to evaluate the overall quality of semantic web service composition.
 This model overcome the disadvantages of current prevailing QoS-aware optimisation that ignores quality of semantic matchmaking.
@@
 \textbf{Semantic web matchmaking quality model}.
-Due to the discretisational characteristics of different match types and values assigned to matching types that driven by the cost of data integration and manipulation \cite{lecue2009optimizing}, partial ordering match types are considered to be one factor for quality of parameter matchmaking, denoted as $mt_{p}$,  For example, Exact matching type demands less time for computation compared to that of Plugin match.
+Due to that the discretisational characteristics of different match types and values assigned to matching types are driven by the cost of data integration and manipulation \cite{lecue2009optimizing}, partial ordering match types are considered to be one factor for quality of parameter matchmaking, denoted as $mt_{p}$,  For example, Exact matching type demands less time for computation compared to that of Plugin match.
 Another factor in our proposed model is concept similarity, which could be evaluated based on the edge counting method defined in \cite{shet2012new}.
@@
 \begin{equation}
-s_{P}{=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
+s_{p}{=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
 \label{equation1}
@@
 
-Further more, semantic web service link represent services connections, where quality of semantic web service link $sm_{L})$ is considered to be semantic matching quality on service connection level by parameter aggregations.
-Therefore, $sm_{L}$ is defined in formula (\ref{equation3}), where $sm_{L}$ and $s_{L}$ are the average value of concept-related parameters quality in $mt_{P}$ and $s_{P}$ respectively.
+Further more, since semantic web service link represent services connections, where quality of semantic web service link $(sm_{L})$ is considered to be semantic matching quality on service level by the aggregation of parameter matchmaking quality.
+Therefore, $sm_{L}$ is defined in formula (\ref{equation3}), where $sm_{L}$ and $s_{L}$ are the average value of all involved $mt_{p}$ and $s_{p}$ respectively.
 
@@
 The comprehensive quality model consider both semantic matchmaking quality and QoS.
-The semantic matchmaking quality refers to the quality of semantic web service link.
+The semantic matchmaking quality refers to $sm_{L}$.
 Consequently, the comprehensive quality model is defined in Formula (\ref{equation4}), which could be further broken down into Formula (\ref{equation5}).
@@
 \label{equation4}
-q_{cq} \stackrel{.}{=} (sm_ {L}, \  QoS_ {s})
+cq \stackrel{.}{=} (sm_ {L}, \  QoS_ {s})
 \end{equation}
@@
 \label{equation5}
-q_{cq} \stackrel{.}{=} (mt_ {L}, \  s_ {L}, \  a_{s},\  r_{s},\  c_{s},\  t_{s})
+cq \stackrel{.}{=} (mt_ {L}, \  s_ {L}, \  a_{s},\  r_{s},\  c_{s},\  t_{s})
 \end{equation}
@@
 \textbf{Semantic matchmaking quality aggregation}.
-The quality aggregation is defined based on the constructs of composition web services, in consideration of quality semantic web service link and QoS.
+The quality aggregation is defined based on the constructs of composition web services in consideration of semantic matchmaking quality and QoS.
 The quality on composition solution is further calculated by following the formula (\ref{equation6})(\ref{equation7}), and QoS aggregation are discussed in Sect.
@@
 
-We defined our semantic web service composition solution as a weighted graph $WG = (V, E)$, where $V$ is a set of services as vertex: $V=\{S1, S2...Sn \}$ and $E$ is a set of edges $E = \{e_{1}, e_{2},...
+We defined our semantic web service composition representation as a weighted graph $WG = (V, E)$, where $V$ is a set of services as vertex: $V=\{S1, S2...Sn \}$ and $E$ is a set of edges $E = \{e_{1}, e_{2},...
 e_{n} \}$.
-Each edge is mapped to a semantic web service link, so each edge $e$ is associated with $sm_{L}$ as weight value as a pair value of quality values $mt_{L}$ and $s_{L}$ on the edge level, Here we provide an example of semantic web service composition, which is described in Fig.
+Each edge is considered to be a semantic web service link $sm_{L}$ , so each edge $e$ is consisting of a pair of quality values, $mt_{L}$ and $s_{L}$ as weigths.
+Here we provide an example of semantic web service composition, which is described in Fig.
 \ref{wscs}.
 The data of composition web service flows from the start to the end, where five web services involved and linked with each other using edge connections.
-Besides that, pair values that $mt_{L}$ and $s_{L}$ are calculated for all edges $e_{1}, e_{2},...
-e_{n}$ assigned as weights.
+Besides that, weights are calculated for all edges $e_{1}, e_{2},...
+e_{n}$.
 
@@
 Lastly, the best position found in the searching space is selected and decode into the final optimised solution.
-This PSO-based approach is similar to \cite{da2016particle}, but we employ weighted graphs as a different solution presentation with edges transferred from semantic web service links.
+This PSO-based approach is similar to \cite{da2016particle}, but we employ weighted graphs as a different solution presentation with explicit support for the proposed quality model.
 
@@
 To effectively construct weighted graphs, we pre-calculate semantic matchmaking quality.
-The key idea of the index is to create a mapping from the output-related concepts to potentially matched input-related concepts while considering different levels of match types.
+The key idea of the index is to create a map using a pair of keys, output-related concepts and potentially matched input-related concepts with considering different levels of match types, and the map values stored $mt_{p}$ and $mt_{s}$.
 Meanwhile, this index size could also be reduced by only considering the concepts related in the shrunken service repository, which means the index cache is filtered by those task-relevant web services.
@@
      \ForEach{particles in the swarm}{
-     $queue \leftarrow$ map particle's position vector to service\;
+     $queue \leftarrow$ map service in a descending order by particle's position vector\;
      $WG \leftarrow$ $generateWeightedGraph$()\;
@@
     		$mt_{P}, s_{P} \leftarrow$ query $IndexCache$\;
-     		$mt_{L} \leftarrow$ aggregation($mt_{P}$)\;
- 			$s_{L} \leftarrow$ aggregation($s_{P}$)\;
+     		$mt_{L} \leftarrow$ aggregation($mt_{p}$)\;
+ 			$s_{L} \leftarrow$ aggregation($s_{p}$)\;
               }
-        $sm_{L} \leftarrow$ aggregation($mt_{L}$,$s_{L}$)\;
+        $sm_{L} \leftarrow$ \{ $mt_{L}$,$s_{L}$ \}\;
         $WG.edge \leftarrow$  $sm_{L} $\;
@@
 The index of each services is mapped to a separate location component in a particle.
-Services in a queue follow the ascending order, from which we decode a weighted graph using Algorithm \ref{graph_building}.
-It is a simple forward graph building algorithm, and this method can lead to more services and edges connected to the graph as redundancies that must be removed.
-Also, semantic quality value are assigned to all the edges, which is calculated from a quality aggregation function from all involved concept-related parameters.
+Then services queue is sorted by the particles' position vector in the ascending order, from which we decode a weighted graph using Algorithm \ref{graph_building}.
+It is a simple forward graph building algorithm, and this method can lead to more services and edges connected to the graph that must be removed.
+Also, semantic quality value are assigned to all the edges, which is calculated from quality aggregation function with given parameter matchmaking quality.
 
@@
 In this section, a quantitative evaluation approach is adopted in our experiment design.
-The objectives of the evaluation are to $(1)$ measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach; $(2)$ explore the impacts of the semantic matchmaking that contributes to overall composition quality; and $(3)$ compare solutions generated by QoS-ware approach with our method; and $(4)$ compare our method with one existing GP-based approach.
+The objectives of the evaluation are to $(1)$ measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach; and $(2)$ compare solutions generated by QoS-ware approach with our method; and $(3)$ compare our method with one existing GP-based approach.
 
@@
 QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid} do consider two semantic matchmaking types (Exact and Plugin) for discovering desired web service, but there is no measurement of matchmaking types and concept similarity, so the weights for $MT$ and $S$ are considered to be 0.
-Consequently, our evaluation mode become a widely used fitness function $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$ \cite{ma2015hybrid} for QoS-aware web service composition.
-To compare the composition solution generated by using our approach comparing with QoS-aware approach.
+Consequently, our evaluation mode become a widely used fitness function \cite{ma2015hybrid, da2016particle}, $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$  for QoS-aware web service composition.
+To compare the composition solution generated by our approach with QoS-aware approach.
 We look at mean value of $MT$, $S$ and $QoS$ at optimum at the 100th generation for two approaches.
@@
 To evaluate the performance of our proposed PSO-based approach, we compare one GP-based approach  \cite{ma2015hybrid} with our PSO method.
-We consider the links between child nodes and parent nodes as semantic web service links for semantic matchmaking quality, and those links information are maintained correctly for the crossover and mutation.
+We consider the links between child nodes and parent nodes as semantic web service links for measuring  semantic matchmaking quality, and those links information are maintained correctly for the crossover and mutation.
 Therefore, we evaluate both semantic matchmaking quality and QoS simultaneously using the proposed comprehensive quality model.
-To make a fair comparison with our PSO-based, we consider the same number of evaluations (3000 times), we set the parameters settings for GP-based approach \cite{ma2015hybrid}, 30 individuals and 100 generations.
+To make a fair comparison with our PSO-based, we consider the same number of evaluations (3000 times), we set the parameters settings for GP-based approach \cite{ma2015hybrid} using 30 individuals and 100 generations.
 
@@
 Fig.
-\ref{psovsgp} is an example of convergence rate from Task 3, where the behaviour of PSO-based approach presents a very clear evidence of fast convergence and reaches a better-optimised solution, while the performance of GP is barely satisfactory, as GP-based method improves its fitness value gradually.
+\ref{psovsgp} is an example of convergence rate for Task 3, where the behaviour of PSO-based approach presents a very clear evidence of fast convergence and reaches a better-optimised solution, while the performance of GP is barely satisfactory, as GP-based method improves its fitness value gradually.
 
@@
 \section{Conclusion}\label{conclusion}
-This work introduces a general comprehensive evaluation model that for considering semantic matchmaking quality and QoS.
-We proposed a PSO-based service composition approach utilising our proposed quality mode that can achieve a desired balance off of both quality aspects.
-Also, we compare one GP-approach with our PSO-based method to show our performance results in finding better-optimised solution.
+This work introduces a general comprehensive evaluation model for considering semantic matchmaking quality and QoS.
+We proposed a PSO-based service composition approach utilising our proposed quality mode that can achieve a desired balance of both quality aspects.
+Also, we compare one GP-approach with our PSO-based method to show our performance results in finding more optimised solution.
 Future works can investigate multi-objective EC techniques to produce a set of composition solutions for the situations that quality preference is not known.

### 2017-01-30 paper.tex
update

@@
 However, there are few works concerns both semantic matchmaking quality and QoS at the same time and achieve a more desirable tradeoff in consideration of both sides.
-Therefore, In this paper, proposed a general comprehensive quality model for semantic matchmaking quality and QoS.
-This model is also suitable to be tackled through EC algorithms, and we develop a PSO-based service composition approach with explicit support for the comprehensive model, which can generate a more desirable balance in considering semantic matchmaking quality and QoS requirement by comparing existing QoS evaluation model.
-We also conduct an experiment shows that our PSO-based method performs better in finding more optimised solution by comparing one existing GP-based method.
+Therefore, In this paper, proposed a general comprehensive quality model considering semantic matchmaking quality and QoS.
+This model is also suitable to be tackled through EC algorithms.
+And we develop a PSO-based service composition approach with explicit support for the comprehensive model, this method can generate a more desirable balance in considering semantic matchmaking quality and QoS requirement that is evidently supported by our experiment for comparing QoS-aware approach.
+We also conduct another experiment shows that our PSO-based method performs better in finding more optimised solution by comparing one existing GP-based method.
 
@@
 
-The overall goal of this paper is to \textit{develop an comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}.
+The overall goal of this paper is to \textit{develop an general comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}.
 Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matchmaking quality optimisation in our proposed comprehensive quality model.
@@
 
- \item To evaluate our proposed approach, we conduct experiment to compare our comprehensive quality model with one widely used QoS evaluation model, we also compare an one existing GP approach with our PSO-based approach using our comprehensive model.
+ \item To evaluate our proposed approach, we conduct experiment to compare our comprehensive quality model with one widely used QoS evaluation model, we also compare an one existing GP approach with our PSO-based approach using our proposed model.
 Both comparison utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}

### 2017-03-16 paper.tex
update

@@
 Semantic web service composition has been a prevailing research area in recent years.
-There are two major challenges faced by researchers, semantic matchmaking and QoS optimisation.
+There are two major challenges faced by researchers, semantic matchmaking and Quality of Service (QoS) optimisation.
 Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning.
-QoS optimisation aims to optimise the non-functional requirement of service users, e.g., minimum cost, maximal reliability.
-Many scholars have looked into QoS optimisation problems in QoS-aware web service composition applying AI planning and Evolutionary Computation techniques.
-To meet users' requirement, one often needs to consider both semantic matchmaking quality and QoS simultaneously.
-Existing works on web service composition often concerns either semantic web  service composition or QoS-aware web service composition.
-However, there are few works concerns both semantic matchmaking quality and QoS at the same time and achieve a more desirable tradeoff in consideration of both sides.
-Therefore, In this paper, proposed a general comprehensive quality model considering semantic matchmaking quality and QoS.
+QoS optimisation aims to optimise the non-functional requirements of service users, e.g., minimum cost, maximal reliability.
+Many scholars have looked into QoS optimisation problems in QoS-aware web service composition, applying AI planning and Evolutionary Computation techniques.
+To meet users' requirements, one often needs to consider both semantic matchmaking quality and QoS simultaneously.
+Existing works on web service composition often concern either semantic web  service composition or QoS-aware web service composition.
+However, there are few works concerning both semantic matchmaking quality and QoS at the same time and achieving a more desirable tradeoff in consideration of both sides.
+Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS in this paper.
 This model is also suitable to be tackled through EC algorithms.
-And we develop a PSO-based service composition approach with explicit support for the comprehensive model, this method can generate a more desirable balance in considering semantic matchmaking quality and QoS requirement that is evidently supported by our experiment for comparing QoS-aware approach.
-We also conduct another experiment shows that our PSO-based method performs better in finding more optimised solution by comparing one existing GP-based method.
+Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model.
+This method can generate a more desirable balance in considering semantic matchmaking quality and QoS requirements that is supported by our experiment when compared to QoS-aware approach.
+We also conduct another experiment that shows our PSO-based method performs better in finding a more optimised solution by comparing with one existing GP-based method.
 
@@
 Due to the increasing number of large-scale enterprise applications, the number of Web services has increased substantially and unprecedentedly.
-Therefore, manual and semi-automated web service composition are considered to be less efficient while automated web service composition enjoys less human intervention, less time consumption, and high productivity.
+Therefore, manual and semi-automated web service compositions are considered to be less efficient while automated web service composition has less human intervention, less time consumption, and high productivity.
 
-Two most notable challenges for web service composition are $(1)$ ensuring interoperability of services and $(2)$ achieving QoS optimisation \cite{fensel2011semantic}.
-\textit{Interoperability} of web services presents challenge $(1)$ in syntactic and semantics dimensions.
+Two most notable challenges for web service composition are ensuring interoperability of services and achieving Quality of Service (QoS) optimisation \cite{fensel2011semantic}.
+\textit{Interoperability} of web services presents challenge in syntactic and semantic dimensions.
 The syntactic dimension is covered by the XML-based technologies (such as $WSDL$, $SOAP$).
-The semantics aspect, on the other hand, demands further research.
+The semantic aspect, on the other hand, demands further research.
 Through ontology-based semantics \cite{o2005review}, web services can understand and better collaborate with each other.
-There are many ontology languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}, which make ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments.
-The second challenge $(2)$ is related to finding \textit{optimised solutions} to Quality of Service ($QoS$).
+There are many ontology languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}, which make ``machine understanding'' possible through identifying and matching semantic similarities in input/output parameters of web services in heterogeneous environments.
+The second challenge $(2)$ is related to finding \textit{optimised solutions} to QoS.
 This problem gives birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements (SLA) \cite {sahai2002automated} involving a collection of SLA rules and policies for supporting QoS-based composition.
 
-Existing works on service composition focus mainly on addressing the one of challenges above.
-A lot of works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as \textit{semi-automated Web service composition} approach \cite{parejo2008qos,bahadori2009optimal}.
+Existing works on service composition focus mainly on addressing one of challenges above.
+Many works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as a \textit{semi-automated Web service composition} approach \cite{parejo2008qos,bahadori2009optimal}.
 Meanwhile, many research works consider the possibility of generating a composition plan automatically in discovering and selecting suitable web services, which are considered to be NP-hard \cite{moghaddam2014service}.
@@
 Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matchmaking quality optimisation in our proposed comprehensive quality model.
-Particle Swarm Optimisation (PSO) has show its promise in searching near-optimised service composition solutions \cite{da2016particle}.
+Particle Swarm Optimisation (PSO) has shown its promise in searching for near-optimised service composition solutions \cite{da2016particle}.
 We will propose a PSO-based service composition approach with explicit support for our proposed quality mode.
@@
 \begin{enumerate}
- \item To propose a general comprehensive quality model that address QoS and semantic matchmaking quality in considering different matching types with corresponding concept similarity.
+ \item To propose a general comprehensive quality model that addresses QoS and semantic matchmaking quality in considering different matching types with corresponding concept similarities.
 
@@
 
- \item To evaluate our proposed approach, we conduct experiment to compare our comprehensive quality model with one widely used QoS evaluation model, we also compare an one existing GP approach with our PSO-based approach using our proposed model.
-Both comparison utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}
+ \item To evaluate our proposed approach, we conduct experiments to compare our comprehensive quality model with one widely used QoS evaluation model.
+We also compare one recent GP approach \cite{ma2015hybrid} with our PSO-based approach using our proposed model.
+Both comparisons utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}
 
@@
 This overall composition goal is demonstrated in two parts: functional part and non-functional part.
-The functional part is defined by given task input and desired task output.
+The functional part is defined by given task inputs and desired task outputs.
 The nonfunctional part specifies overall QoS requirements.
@@
 If no atomic web service could satisfy the composition goal, a composition of web services will be found to meet $Comp.G$.
-To ensure the composition solution returns the desired $Comp.G$, we use a quality model that take care of QoS and semantic matchmaking quality.
+To ensure the composition solution returns the desired $Comp.G$ that considers a higher degree of matching $O_{T}$ and a near-optimised $QoS_{T}$, We first demonstrate the concepts in both semantic matchmaking types and $QoS$ as follows, and then propose a quality model that take care of semantic matchmaking quality and QoS simultaneously in Sect.
+\ref{Comprehensive_Quality_Model}.
 
-\subsection{Quality of Service and Composition Constructs}\label{Quality of Service and Composition Constructs}
+\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
+The semantic service matchmaking aims to discover appropriate services from service repository.
+A semantic web service is defined by $S(F(I_{S}\in C_{1}, O_{S}\in C_{2}), NF(QoS_{S}))$, where both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology $O$ respectively, satisfying $O=\{C, Taxonomy\}$.
+A web service matching process is to match the output and input concepts of two services according to the Taxonomy within an ontology.
+To measure the quality of semantic matchmaking, different matching levels are typically considered in the literature \cite{paolucci2002semantic}.
+To understand these levels, let us define two web services associated with concept-related parameters in a particular domain.
+$S_{1}$ $(F(I_{S_1}\in C_{1}, O_{S_1}\in C_{2}), NF(QoS_{S_1}))$ and  $S_{2}$ $(F(I_{S_2}\in C_{3}, O_{S_2}\in C_{4}), NF(QoS_{S_2}))$ and an ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$.
+The matching levels to be considered are:
+
+\begin{itemize}
+\item \textit{Exact} ($\equiv$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Exact match ($ O_{S_1} \in S_{1} \equiv I_{S_2} \in S_{2}$), if  Concept $C_{2}$ and Concept $C_{3}$ are equivalent.
+\item \textit{Plugin} ($\sqsubseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Plugin match ($O_{S_1} \in S_{1} \sqsubseteq_{n} I_{S_2} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of children concepts ($n=1$ stands for direct children).
+\item \textit{Subsume} ($\sqsupseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Subsume matched($O_{S_1} \in S_{1} \sqsupseteq_{n} I_{S_2} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of  Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of parent concepts ($n=1$ stands for direct parent).
+\item \textit{Fail} ($\perp$).
+Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are not matched (Fail) ($O_{S_1} \in S_{1} \perp I_{S_2} \in S_{2}$), if none of the previous matches discovered.
+\end{itemize}
+
+The semantic matchmaking is achieved by utilising OWL2 and OWL-S or other semantic markup languages for web services.
+In this paper, we use MECE (Mediation Contract Extension) \cite{bleul2008self} and OWL-DL.
+MECE is considered to be an alternative semantic annotation for WSDL.
+MECE defines the service-related inputs and outputs with parameter-related concepts.
+OWL-DL is a sublanguage of OWL extended from RDF.
+It specifies semantic information of concepts involved in MECE.
+
+\subsection{Quality of Service}\label{Quality of Service and Composition Constructs}
 According to \cite{zeng2003quality}, four most often considered QoS parameters are response time, cost, reliability and availability described as follows:
@@
 \subsubsection{Sequence construct}
-The composition web service executes each atomic service associated with a sequence construct in a definite sequence order.
+all involved atomic services associated with a sequence construct are executed in a definite sequence order.
 The aggregation value for total time ($T$) and total cost ($C$) is as the sum of time and cost of web services involved respectively.
@@
 
-\section{Comprehensive Quality Model}\label{qswsc_approach}
+\section{Comprehensive Quality Model}\label{Comprehensive_Quality_Model}
 In this section, we propose a general comprehensive quality-aware service model in consideration of both semantic matchmaking quality and QoS for semantic web service composition.
-
-\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
-The semantic service matchmaking aims to discover appropriate services from service repository.
-A semantic web service is defined by $S(F(I_{S}\in C_{1}, O_{S}\in C_{2}), NF(QoS_{S}))$, where both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology $O$ respectively, satisfying $O=\{C, Taxonomy\}$.
-A web service matching process is to match the output and input concepts of two services according to the Taxonomy within an ontology.
-To measure the quality of semantic matchmaking, different matching levels are typically considered in the literature \cite{paolucci2002semantic}.
-To understand these levels, let us define two web services associated with concept-related parameters in a particular domain.
-$S_{1}$ $(F(I_{S_1}\in C_{1}, O_{S_1}\in C_{2}), NF(QoS_{S_1}))$ and  $S_{2}$ $(F(I_{S_2}\in C_{3}, O_{S_2}\in C_{4}), NF(QoS_{S_2}))$ and an ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$.
-The matching levels to be considered are:
-
-\begin{itemize}
-\item \textit{Exact} ($\equiv$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Exact match ($ O_{S_1} \in S_{1} \equiv I_{S_2} \in S_{2}$), if  Concept $C_{2}$ and Concept $C_{3}$ are equivalent.
-\item \textit{Plugin} ($\sqsubseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Plugin match ($O_{S_1} \in S_{1} \sqsubseteq_{n} I_{S_2} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of children concepts ($n=1$ stands for direct children).
-\item \textit{Subsume} ($\sqsupseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Subsume matched($O_{S_1} \in S_{1} \sqsupseteq_{n} I_{S_2} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of  Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of parent concepts ($n=1$ stands for direct parent).
-\item \textit{Fail} ($\perp$).
-Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are not matched (Fail) ($O_{S_1} \in S_{1} \perp I_{S_2} \in S_{2}$), if none of the previous matches discovered.
-\end{itemize}
-
-The semantic matchmaking is achieved by utilising OWL2 and OWL-S or other semantic markup languages for web services.
-In this paper, we use MECE (Mediation Contract Extension) \cite{bleul2008self} and OWL-DL.
-MECE is considered to be an alternative semantic annotation for WSDL.
-MECE defines the service-related inputs and outputs with parameter-related concepts.
-OWL-DL is a sublanguage of OWL extended from RDF.
-It specifies semantic information of concepts involved in MECE.
 
@@
 \multicolumn{1}{c|}{Dataset} & PSO-based approach & GP-based approach  \\ \hline
-WSC09 01                     &0.559207 $\pm$ 0.012780 $\uparrow$      &0.518411 $\pm$ 0.018470               \\ \hline
-WSC09 02                     &0.470083 $\pm$  0.001106   &0.471594 $\pm$  0.002436 $\uparrow$           \\ \hline
-WSC09 03                     & 0.559207 $\pm$ 0.012780 $\pm$ $\uparrow$  &0.552947 $\pm$ 0.007094            \\ \hline
-WSC09 04                     & 0.468942 $\pm$ 0.001670 $\pm$ $\uparrow$  &0.442934 $\pm$ 0.010154            \\ \hline
-WSC09 05                     & 0.469424 $\pm$ 0.000800 $\pm$ $\uparrow$  &0.256425 $\pm$ 0.038916            \\ \hline
+WSC09 01                     &0.559207 $\pm$ 0.012780  $\uparrow$ (P:0.000)  &0.520659 $\pm$ 0.020758           \\ \hline
+WSC09 02                     &0.470083 $\pm$  0.001106 $\uparrow$ (P:0.008)   &0.459681 $\pm$  0.002874          \\ \hline
+WSC09 03                     & 0.550396 $\pm$ 0.012780                        &0.567915 $\pm$ 0.023447 $\uparrow$  (P:0.000) \\ \hline
+WSC09 04                     & 0.468942 $\pm$ 0.001670  $\uparrow$ (P:0.003)  &0.431704 $\pm$ 0.009774            \\ \hline
+WSC09 05                     & 0.469424 $\pm$ 0.000800  $\uparrow$ (P:0.000)  &0.245222 $\pm$ 0.036885            \\ \hline
 \end{tabular}

### 2017-03-16 paper.tex
up

@@
 Particle Swarm Optimisation (PSO) has shown its promise in searching for near-optimised service composition solutions \cite{da2016particle}.
-We will propose a PSO-based service composition approach with explicit support for our proposed quality mode.
+We will propose a PSO-based service composition approach with explicit support for our proposed quality model.
 We will achieve three objectives in this work as follows:
@@
 In this section, we propose a general comprehensive quality-aware service model in consideration of both semantic matchmaking quality and QoS for semantic web service composition.
+This model overcome the disadvantages of current prevailing QoS-aware quality model that ignores quality of semantic matchmaking.
 
 \subsection{Comprehensive Quality Model}\label{qualityModel}
-We propose a comprehensive quality model to evaluate the overall quality of semantic web service composition.
-This model overcome the disadvantages of current prevailing QoS-aware optimisation that ignores quality of semantic matchmaking.
 
@@
 This formula (\ref{equation1}) is used to estimate the concept similarity between matching parameters, which is denoted as $s_{p}$.
-Therefore, given the quality of parameter matchmaking type and quality of parameter concept similarity, the quality of parameter matchmaking is defined by Formula (\ref{equation2}), where the value of $mt_{p}$ follows the same settings in \cite{lecue2009optimizing}.
-Particularly, 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).
+N1 and N2 measure the distances from an output-related concept and an input-related concept to the top node of a taxonomy respectively, and N measure the distances from the closest common ancestor of these two matched input-related and output-related concepts.
+$\lambda$ is set to 0 if we do not measure the similarities of neighbourhood concepts that is not the matching levels considered in this paper.
+Consequently, given the quality of parameter matchmaking type and quality of parameter concept similarity, the quality of parameter matchmaking is defined by Formula (\ref{equation2}).
 
@@
 \end{equation}
-\noindent where $k$ $=$ $1$, $2$, $3$, and $4$, where $Q_1$ as $MT$, $Q_2$ as $S$, $Q_3$ as $A$, and $Q_4$ as $R$.
+\noindent where $k$ $=$ $1$, $2$, $3$, and $4$, where $Q_1$ is $MT$, $Q_2$ is $S$, $Q_3$ is $A$, and $Q_4$ is $R$.
 \begin{equation}
@@
 \end{equation}
-\noindent where $j$ $=$ $1$, and $2$, where $Q_1$ as $T$ and $Q_2$ as $C$.
+\noindent where $j$ $=$ $1$, and $2$, where $Q_1$ is $T$ and $Q_2$ is $C$.
 
@@
 Therefore, $w_{1}$ and $w_{2}$ are set equally to 0.25, and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly.
-However, the settings of these weight values does not impact the method.
-In general, weight settings are adjusted according to users' preferences.
+The $mt_{p}$ is set to 1 (Exact match) and 0.75 (Plugin).
+In general, weight settings and parameter match type quality are decided by users' preferences.
 
@@
 Also, we compare one GP-approach with our PSO-based method to show our performance results in finding more optimised solution.
-Future works can investigate multi-objective EC techniques to produce a set of composition solutions for the situations that quality preference is not known.
+Future works can investigate multi-objective EC techniques to produce a set of composition solutions for the situations when the quality preference is not known.
 

### 2017-03-16 paper.tex
update

@@
 
-To compare the results generated from two evaluation approaches, we demonstrate an example solution that shows the differences in web services composition obtained through two different methods.
+To better understand that our evaluation approach could generate solutions having better semantic matchmaking quality with a slight trade off in $QoS$, we demonstrate an example solution to Task 3.
 Fig.
-\ref{comparisontest} $(1)$ and $(2)$ show two composition weighted graphs as the two optimised solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method respectively.
-Two approaches generate exactly the same service workflow structure where those service vertices and edges denoted in red are different.
-We make a comparison of the quality among these different edges ($e_1$ to $e4$) associated service vertices in terms of quality of semantic matchmaking and QoS attributes in Fig.
+\ref{comparisontest} $(1)$ and $(2)$ show two weighted DAGs as two solutions employing QoS-aware approach and Comprehensive quality-aware method respectively.
+Two approaches generate exactly the same service workflow structure while some service vertices and edges denoted in red are different.
+We list the semantic matchmaking quality represented by all edges ($e_1$ to $e4$) and overall QoS in Fig.
 \ref{comparisontest} $(3)$.
-We also look at $\Delta Q$ which reveals the amount of variation on quality between two methods, where the positive values means the benefits gained under our approach while the negative values means the tradeoff.
-To demonstrate the benefits of the positive value, we analyse the smallest positive $\Delta Q$ corresponding to $e_4$ and demonstrate how the output and required input are different under two approaches in Fig.
-\ref{comparisontest} $(4)$.
-$Ser1640238160$ and $Ser1947554374$ are selected service vertices with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to two concepts $Con103314376$ and $Con2037585750$ respectively, and $Inst658772240$ are the required parameter related to concept $Con2113572083$.
+To demonstrate how different the semantic matchmaking quality is, we analyse $e_4$ that has the smallest $\Delta Q$, which reveals the smallest semantic matchmaking quality gained using our approach.
+$e_4$ has two different source service vertices ($Ser1640238160$ and $Ser1947554374$) and two same $end$ vertices .
+Further more, in Fig.
+\ref{comparisontest} $(4)$, $Ser1640238160$ and $Ser1947554374$ are service with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to two concepts $Con103314376$ and $Con2037585750$ respectively, and $Inst658772240$ are the required parameter for the $end$ vertice, which is related to concept $Con2113572083$.
 There exist $Inst795998200$ $\in$ $Con103314376$ $\sqsubseteq_{2}$ $Inst658772240$ $\in$ $Con2113572083$ and $Inst582785907$ $\in$ $Con2037585750$ $\sqsubseteq_{3}$ $Inst658772240$ $\in$ $Con2113572083$.
-It is obvious that our approach selects the service providing $Inst795998200$ that are closer to the users' requirements suggesting that our method can produce better semantic matchmaking quality in terms of less general outputs.
-
+It is obvious that our approach selects the service providing $Inst795998200$ that are closer to the users' required outputs.
 \begin{figure}[h]
@@
 \includegraphics[scale=.22]{comparisontest.pdf}}}
- \caption{Example Comparison of solutions to Task 3 under different approaches.}
+ \caption{Example Comparison of solutions to Task 3 using two different evaluation model.}
  \label{comparisontest}
@@
 We employ statistical analysis to test the significant differences in mean fitness value.
-The results show that the PSO-based approach performs better in four of five tasks.
+The results show that the PSO-based approach performs better in four of five tasks (all the p-values are consistently smaller than 0.01).
 
@@
 \multicolumn{1}{c|}{Dataset} & PSO-based approach & GP-based approach  \\ \hline
-WSC09 01                     &0.559207 $\pm$ 0.012780  $\uparrow$ (P:0.000)  &0.520659 $\pm$ 0.020758           \\ \hline
-WSC09 02                     &0.470083 $\pm$  0.001106 $\uparrow$ (P:0.008)   &0.459681 $\pm$  0.002874          \\ \hline
-WSC09 03                     & 0.550396 $\pm$ 0.012780                        &0.567915 $\pm$ 0.023447 $\uparrow$  (P:0.000) \\ \hline
-WSC09 04                     & 0.468942 $\pm$ 0.001670  $\uparrow$ (P:0.003)  &0.431704 $\pm$ 0.009774            \\ \hline
-WSC09 05                     & 0.469424 $\pm$ 0.000800  $\uparrow$ (P:0.000)  &0.245222 $\pm$ 0.036885            \\ \hline
+WSC09 01                     &0.559207 $\pm$ 0.012780  $\uparrow$   &0.520659 $\pm$ 0.020758           \\ \hline
+WSC09 02                     &0.470083 $\pm$  0.001106 $\uparrow$   &0.459681 $\pm$  0.002874          \\ \hline
+WSC09 03                     & 0.550396 $\pm$ 0.012780                        &0.567915 $\pm$ 0.023447 $\uparrow$   \\ \hline
+WSC09 04                     & 0.468942 $\pm$ 0.001670  $\uparrow$   &0.431704 $\pm$ 0.009774            \\ \hline
+WSC09 05                     & 0.469424 $\pm$ 0.000800  $\uparrow$   &0.245222 $\pm$ 0.036885            \\ \hline
 \end{tabular}

### 2017-03-16 paper.tex
update

@@
 
-To better understand that our evaluation approach could generate solutions having better semantic matchmaking quality with a slight trade off in $QoS$, we demonstrate an example solution to Task 3.
+To better understand that our evaluation approach could generate solutions having better semantic matchmaking quality with a slight trade-off in $QoS$, we demonstrate an example solution to Task 3.
 Fig.
-\ref{comparisontest} $(1)$ and $(2)$ show two weighted DAGs as two solutions employing QoS-aware approach and Comprehensive quality-aware method respectively.
+\ref{comparisontest} $(1)$ and $(2)$ are two weighted DAGs as best solutions found employing QoS-aware approach and Comprehensive quality-aware method respectively.
 Two approaches generate exactly the same service workflow structure while some service vertices and edges denoted in red are different.
-We list the semantic matchmaking quality represented by all edges ($e_1$ to $e4$) and overall QoS in Fig.
+We list the semantic matchmaking quality represented by all edges ($e_1$ to $e4$), overall semantic matchmaking quality and QoS in Fig.
 \ref{comparisontest} $(3)$.
-To demonstrate how different the semantic matchmaking quality is, we analyse $e_4$ that has the smallest $\Delta Q$, which reveals the smallest semantic matchmaking quality gained using our approach.
-$e_4$ has two different source service vertices ($Ser1640238160$ and $Ser1947554374$) and two same $end$ vertices .
-Further more, in Fig.
+To demonstrate how different the semantic matchmaking quality is, we analyse $e_4$ that has the smallest $\Delta Q$, which reveals the gain (positive $\Delta Q$) or loss (negative $\Delta Q$) for the listed qualities using our approach.
+The $e_4$ has two different source service vertices ($Ser1640238160$ and $Ser1947554374$) and the same $end$ vertices in two solutions.
+The outputs of two different source service are marked on the related taxonomy in Fig.
 \ref{comparisontest} $(4)$, $Ser1640238160$ and $Ser1947554374$ are service with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to two concepts $Con103314376$ and $Con2037585750$ respectively, and $Inst658772240$ are the required parameter for the $end$ vertice, which is related to concept $Con2113572083$.

### 2017-03-17 paper.tex
update

@@
 Meanwhile, many research works consider the possibility of generating a composition plan automatically in discovering and selecting suitable web services, which are considered to be NP-hard \cite{moghaddam2014service}.
-\textit{Semantic web services composition} is distinguished from the syntactic service composition, with the hope of eliminating conflicts by the semantic level of web services.
+\textit{Semantic web services composition} is distinguished from the syntactic service composition, which supplements well defined semantic descriptions from the concept of ontologies, instead of parameters value.
 In the past few years, substantial works have been done on semantic web service composition \cite{boustil2014semantic, mier2015integrated, bansal2016generalized}.
@@
 
-The overall goal of this paper is to \textit{develop an general comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}.
+The overall goal of this paper is to \textit{develop a general comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}.
 Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matchmaking quality optimisation in our proposed comprehensive quality model.
@@
 \section{Related Work} \label{relatedWork}
-Substantial work on web service composition focused on either semantic web service composiiton \cite{boustil2014semantic,mier2015integrated, bansal2016generalized} or QoS-aware web service composiiton \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining,ma2015hybrid}, However few researchers addressed both semantic mathmaking quality and QoS requirements at the same time for web service composition problems.
+Substantial work on web service composition focused on either semantic web service composition \cite{boustil2014semantic,mier2015integrated, bansal2016generalized} or QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining,ma2015hybrid}, However few researchers addressed both semantic matchmaking quality and QoS requirements at the same time for web service composition problems.
 To the best of our knowledge, \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} reported some recent attempts on service composition that considers both aspects.
@@
 A heuristic service composition method is proposed by Qi et al.
-\cite{qi2010combining} for QoS-aware web service composiiton, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal for QoS.
+\cite{qi2010combining} for QoS-aware web service composition, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal for QoS.
 Obviously, there exists scalability problem for enumeration techniques.
@@
 A hyper approach employs both a greedy search algorithm and Genetic Programming (GP) is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness.
-In particularly, the greedy search is used to generate directed acrylic graph as composition solutions, which is further transferred to the tree structure for initialisation and mutation using unfolding techniques.
-To eliminating the transformation process from DAG, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of Directed Acyclic Graph(DAG) employing Graph-based evolutionary operators like crossover and mutation.
+In particularly, the greedy search is used to generate  directed acyclic graphs (DAGs) as composition solutions, which is further transferred to the tree structure for initialisation and mutation using unfolding techniques.
+To eliminating the transformation process from DAGs, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation.
 PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}, an indirect PSO-based approach was introduced in \cite{da2016particle}.
-An optimised queue is used as indirect representation as composition solution that decoding into Direct Acyclic Graph (DAG).
+An optimised queue is used as an indirect representation that is decoded into a DAG as a composition solution.
 These QoS-aware approaches does not consider semantic matchmaking quality, which could lead to over-general outputs to be produced by selected services, The finding is evidently supported by our first comparison experiment.
@@
 
-In summary, composition solutions from semantic web service composition \cite{boustil2014semantic,mier2015integrated, bansal2016generalized} does not consider QoS, and QoS-aware web service composiiton \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining,ma2015hybrid} does not consider distinguished matchmaking quality in their fitness function.
+In summary, composition solutions from semantic web service composition \cite{boustil2014semantic,mier2015integrated, bansal2016generalized} does not consider QoS, and QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining,ma2015hybrid} does not consider distinguished matchmaking quality in their fitness function.
 Few works do consider both quality aspects, but some limitations lie in semi-automated approach \cite{lecue2009optimizing}, less general semantic quality measurement \cite{lecue2009optimizing, pop2009immune}, or semantic matchmaking types ignorance \cite{pop2009immune}.
@@
 \item \textit{Plugin} ($\sqsubseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Plugin match ($O_{S_1} \in S_{1} \sqsubseteq_{n} I_{S_2} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of children concepts ($n=1$ stands for direct children).
-\item \textit{Subsume} ($\sqsupseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Subsume matched($O_{S_1} \in S_{1} \sqsupseteq_{n} I_{S_2} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of  Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of parent concepts ($n=1$ stands for direct parent).
+\item \textit{Subsume} ($\sqsupseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Subsume matched($O_{S_1} \in S_{1} \sqsupseteq_{n} I_{S_2} \in S_{2}$), if  Concept $C_{2}$ is a super-concept of  Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of parent concepts ($n=1$ stands for direct parent).
 \item \textit{Fail} ($\perp$).
@@
 The function value of 1 means the best comprehensive quality and 0 means the worst.
-For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the function value falls within the range from 0 to 1.
-Therefore, the service composition is try to maximise the value of objective function.
+For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the function value falls within the range from 0 to 1 using Formula (\ref{equation9}) and (\ref{equation10}), where the maximum and minimum value of $A$, $R$, $T$, and $C$ are calculated by all web services related to the composition task.
+$MT$ and $S$ are using a bound from 0 to 1.
+Therefore, the composition task is try to find maximised value of objective function associated to the solutions.
+
 \vspace{-0.2cm}
@@
 
-\section{PSO-based Approach to QoS-Aware Semantic Web Service Composition}\label{qswsc_approach}
+\section{PSO-based Approach to Comprehensive Quality-Aware Automated Semantic Web Service Composition}\label{qswsc_approach}
 
@@
 PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}.
-Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing that often required by GP \cite{da2016particle}.
+Therefore, we will employ a PSO-based approach, which is considered to be easier to maintain the correctness of solutions compared to GP-based approaches that often require repairing or penalising the solutions \cite{da2016particle}.
 Fig.
@@
 Step 2: This composition goal are used to discover all relevant web services, which lead to a shrunken service repository that is subsequently used by PSO as a searching space.
-Step 3: A weighted graph representation is randomly built up from the an initial service queue that mapped to the particle's location, interleaving with semantic matchmaking process utilising ontology-based index cache.
+Step 3: A weighted graph representation is randomly built up from an initial service queue that mapped to the particle's location, interleaving with semantic matchmaking process utilising ontology-based index cache.
 In the weighted graph, graph edges are assigned with semantic matchmaking quality as weights.
@@
 later on, the updated service queue is used to decode a new weighted graph as the composition solution.
-Step 4.
+Step 5.
 Lastly, the best position found in the searching space is selected and decode into the final optimised solution.
@@
 \subsection{Ontology-based Index Cached Optimisation}\label{indexCache}
-In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic web service matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively.
-To effectively construct weighted graphs, we pre-calculate semantic matchmaking quality.
+our PSO-based approach demands decoding processes from optimised queues to weighted DAGs, the bottlenecks of efficiently generating weighted DAGs lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively.
+To effectively construct weighted DAGs, we pre-calculate semantic matchmaking quality.
 The key idea of the index is to create a map using a pair of keys, output-related concepts and potentially matched input-related concepts with considering different levels of match types, and the map values stored $mt_{p}$ and $mt_{s}$.
@@
 In this section, a quantitative evaluation approach is adopted in our experiment design.
-The objectives of the evaluation are to $(1)$ measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach; and $(2)$ compare solutions generated by QoS-ware approach with our method; and $(3)$ compare our method with one existing GP-based approach.
+The objectives of the evaluation are to $(1)$ measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach; and $(2)$ compare solutions generated by a recent QoS-ware evaluation approach \cite{ma2015hybrid,da2016genetic} with our evaluation method proposed in the paper; and $(3)$ compare our PSP-based method with one existing GP-based approach \cite{ma2015hybrid}.
 
@@
 
-We run the experiment on computing grid comprising of 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine.
 The parameters were chosen based on general settings from \cite{shi2001particle} for our PSO-based approach, In particular, PSO population size is 30 with 100 generations.
@@
 Therefore, we evaluate both semantic matchmaking quality and QoS simultaneously using the proposed comprehensive quality model.
-To make a fair comparison with our PSO-based, we consider the same number of evaluations (3000 times), we set the parameters settings for GP-based approach \cite{ma2015hybrid} using 30 individuals and 100 generations.
+To make a fair comparison with our PSO-based, we consider the same number of evaluations (3000 times) as that in our PSO-based approach, we set the parameters settings for GP-based approach \cite{ma2015hybrid} using 30 individuals and 100 generations.
 

### 2017-03-17 paper.tex
update

@@
-\documentclass{IEEEtran}
+\documentclass{llncs}
 \usepackage[ruled,vlined]{algorithm2e}
@@
 
-\title{Comprehensive Quality-Aware Automated Semantic Web Service Composition}
-\author{Chen Wang, Hui Ma, Aaron Chen\\ \small School of
-Engineering and Computer Science, Victoria University of Wellington, New Zealand\\
+\title{Comprehensive Quality Awareness Automated Semantic Web Service Composition}
+\author{Chen Wang, Hui Ma, and Aaron Chen}
+\institute{School of Engineering and Computer Science,
+\\Victoria University of Wellington, New Zealand \\
 Email: \{chen.wang, hui.ma, aaron.chen\}@ecs.vuw.ac.nz}
@@
 Existing works on service composition focus mainly on addressing one of challenges above.
-Many works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as a \textit{semi-automated Web service composition} approach \cite{parejo2008qos,bahadori2009optimal}.
+Many works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as a \textit{semi-automated Web service composition} approach \cite{bahadori2009optimal,parejo2008qos}.
 Meanwhile, many research works consider the possibility of generating a composition plan automatically in discovering and selecting suitable web services, which are considered to be NP-hard \cite{moghaddam2014service}.
 \textit{Semantic web services composition} is distinguished from the syntactic service composition, which supplements well defined semantic descriptions from the concept of ontologies, instead of parameters value.
-In the past few years, substantial works have been done on semantic web service composition \cite{boustil2014semantic, mier2015integrated, bansal2016generalized}.
+In the past few years, substantial works have been done on semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated}.
 However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously and achieved a desired balance.
@@
 \section{Related Work} \label{relatedWork}
-Substantial work on web service composition focused on either semantic web service composition \cite{boustil2014semantic,mier2015integrated, bansal2016generalized} or QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining,ma2015hybrid}, However few researchers addressed both semantic matchmaking quality and QoS requirements at the same time for web service composition problems.
+Substantial work on web service composition focused on either semantic web service composition \cite{boustil2014semantic,mier2015integrated,bansal2016generalized} or QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,gupta2015optimization,qi2010combining,ma2015hybrid}, However few researchers addressed both semantic matchmaking quality and QoS requirements at the same time for web service composition problems.
 To the best of our knowledge, \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} reported some recent attempts on service composition that considers both aspects.
 
-\cite{boustil2014semantic,mier2015integrated, bansal2016generalized} captures the semantics of web services' parameters using some kind of logic (e.g., description logic) for enabling semantic web service composition, where the number of web services or length of the graph is minimised to reach the optimised graph-based composition solutions.
+\cite{boustil2014semantic,mier2015integrated,bansal2016generalized} captures the semantics of web services' parameters using some kind of logic (e.g., description logic) for enabling semantic web service composition, where the number of web services or length of the graph is minimised to reach the optimised graph-based composition solutions.
 However, these approaches need to be improved for the scalability that considering a large number of web services, and the evaluation method does not fit properly for customers' complex requirements.
@@
 
-In summary, composition solutions from semantic web service composition \cite{boustil2014semantic,mier2015integrated, bansal2016generalized} does not consider QoS, and QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining,ma2015hybrid} does not consider distinguished matchmaking quality in their fitness function.
-Few works do consider both quality aspects, but some limitations lie in semi-automated approach \cite{lecue2009optimizing}, less general semantic quality measurement \cite{lecue2009optimizing, pop2009immune}, or semantic matchmaking types ignorance \cite{pop2009immune}.
-In addition, experiments design for  \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} are not conducted using benchmark dataset for the scalability, only small datasets are utilised that might suffer scalability.
+In summary, composition solutions from semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} does not consider QoS, and QoS-aware web service composition
+\cite{gupta2015optimization,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} does not consider distinguished matchmaking quality in their fitness function.
+Few works do consider both quality aspects, but some limitations lie in semi-automated approach \cite{lecue2009optimizing}, less general semantic quality measurement \cite{lecue2009optimizing,pop2009immune}, or semantic matchmaking types ignorance \cite{pop2009immune}.
+In addition, experiments design for  \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} are not conducted using benchmark dataset for the scalability, only small datasets are utilised that might suffer scalability.
 Results analysis for \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} also do not evidently point out what desired balance could be reached by considering semantic matchmaking quality and QoS.
@@
 QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid} do consider two semantic matchmaking types (Exact and Plugin) for discovering desired web service, but there is no measurement of matchmaking types and concept similarity, so the weights for $MT$ and $S$ are considered to be 0.
-Consequently, our evaluation mode become a widely used fitness function \cite{ma2015hybrid, da2016particle}, $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$  for QoS-aware web service composition.
+Consequently, our evaluation mode become a widely used fitness function \cite{ma2015hybrid,da2016particle}, $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$  for QoS-aware web service composition.
 To compare the composition solution generated by our approach with QoS-aware approach.
@@
 
-\bibliographystyle{IEEEtran}
+\bibliographystyle{splncs03}
 \bibliography{IEEEexample}

### 2017-03-17 paper.tex
update

@@
 Existing works on web service composition often concern either semantic web  service composition or QoS-aware web service composition.
-However, there are few works concerning both semantic matchmaking quality and QoS at the same time and achieving a more desirable tradeoff in consideration of both sides.
-Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS in this paper.
-This model is also suitable to be tackled through EC algorithms.
-Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model.
-This method can generate a more desirable balance in considering semantic matchmaking quality and QoS requirements that is supported by our experiment when compared to QoS-aware approach.
-We also conduct another experiment that shows our PSO-based method performs better in finding a more optimised solution by comparing with one existing GP-based method.
+Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS simultaneously that can achieve a more desirable trade-off in consideration of both sides by conducting an experiment comparing with promising QoS-aware model.
+Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model, and compare the PSO-based method with one recent GP-based method to show its performance in finding a more optimised solution.
 
@@
 \section{Related Work} \label{relatedWork}
-Substantial work on web service composition focused on either semantic web service composition \cite{boustil2014semantic,mier2015integrated,bansal2016generalized} or QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,gupta2015optimization,qi2010combining,ma2015hybrid}, However few researchers addressed both semantic matchmaking quality and QoS requirements at the same time for web service composition problems.
-To the best of our knowledge, \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} reported some recent attempts on service composition that considers both aspects.
+Substantial work on web service composition focused on either semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive}, However few researchers addressed both semantic matchmaking quality and QoS requirements at the same time for web service composition problems.
+To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some recent attempts on service composition that considers both aspects.
 
-\cite{boustil2014semantic,mier2015integrated,bansal2016generalized} captures the semantics of web services' parameters using some kind of logic (e.g., description logic) for enabling semantic web service composition, where the number of web services or length of the graph is minimised to reach the optimised graph-based composition solutions.
+\cite{boustil2014semantic,bansal2016generalized,mier2015integrated} captures the semantics of web services' parameters using some kind of logic (e.g., description logic) for enabling semantic web service composition, where the number of web services or length of the graph is minimised to reach the optimised graph-based composition solutions.
 However, these approaches need to be improved for the scalability that considering a large number of web services, and the evaluation method does not fit properly for customers' complex requirements.

### 2017-03-17 paper.tex
update

@@
 \section{Related Work} \label{relatedWork}
-Substantial work on web service composition focused on either semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive}, However few researchers addressed both semantic matchmaking quality and QoS requirements at the same time for web service composition problems.
-To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some recent attempts on service composition that considers both aspects.
+Substantial works on web service composition focus on either semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive}, However, few researchers address both semantic matchmaking quality and QoS requirements at the same time for web service composition problems.
+To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some attempts on service composition that considers both aspects.
 
-\cite{boustil2014semantic,bansal2016generalized,mier2015integrated} captures the semantics of web services' parameters using some kind of logic (e.g., description logic) for enabling semantic web service composition, where the number of web services or length of the graph is minimised to reach the optimised graph-based composition solutions.
-However, these approaches need to be improved for the scalability that considering a large number of web services, and the evaluation method does not fit properly for customers' complex requirements.
+Semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} captures the semantic description of web services' parameters using some kind of logic (e.g., description logic) for enabling the interoperability of web services, where the number of web services or length of the graph is minimised to reach the optimised graph-based composition solutions.
+However, this evaluation approach does not guarantee optimised qualities of composition solutions for QoS.
 
-A heuristic service composition method is proposed by Qi et al.
-\cite{qi2010combining} for QoS-aware web service composition, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal for QoS.
-Obviously, there exists scalability problem for enumeration techniques.
-
-Evolutionary Computation (EC) techniques are used to improve the scalability for solving NP-hard problems.
+QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques.
+Qi et al.
+\cite{qi2010combining} propose a heuristic service composition method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal for QoS.
+but there exists scalability problems for the enumeration technique.
+EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problems.
 Gupta et al.
-\cite{gupta2015optimization} employ an Genetic Algorithm to the problem of QoS-ware web service composition, and a set of binary strings are used as individuals, which demands to be decoded into composition solutions.
-Genetic Programming are employed by  \cite{yu2013adaptive} with direct representation of composition solutions, the overall quality of solutions are measured by a fitness function that is liable for penalising infeasible solutions.
-A hyper approach employs both a greedy search algorithm and Genetic Programming (GP) is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness.
+\cite{gupta2015optimization} employ an Genetic Algorithm using a set of binary strings as individuals, which demands to be decoded into composition solutions.
+Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function.
+A hybird approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions with functional correctness.
 In particularly, the greedy search is used to generate  directed acyclic graphs (DAGs) as composition solutions, which is further transferred to the tree structure for initialisation and mutation using unfolding techniques.
 To eliminating the transformation process from DAGs, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation.
-PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}, an indirect PSO-based approach was introduced in \cite{da2016particle}.
+An indirect PSO-based approach was introduced in \cite{da2016particle}.
 An optimised queue is used as an indirect representation that is decoded into a DAG as a composition solution.
@@
 
-Few works \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} employ EC technique for considering both semantic matchmaking quality and QoS simultaneously.
+Few works \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} employ EC technique for considering both semantic matchmaking quality and QoS simultaneously.
 Lecue et al.
@@
 
-In summary, composition solutions from semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} does not consider QoS, and QoS-aware web service composition
-\cite{gupta2015optimization,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} does not consider distinguished matchmaking quality in their fitness function.
-Few works do consider both quality aspects, but some limitations lie in semi-automated approach \cite{lecue2009optimizing}, less general semantic quality measurement \cite{lecue2009optimizing,pop2009immune}, or semantic matchmaking types ignorance \cite{pop2009immune}.
-In addition, experiments design for  \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} are not conducted using benchmark dataset for the scalability, only small datasets are utilised that might suffer scalability.
-Results analysis for \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} also do not evidently point out what desired balance could be reached by considering semantic matchmaking quality and QoS.
-Therefore, we proposed a general comprehensive quality model which achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS to fill the gaps discussed above, and then we proposed a POS-based method with explicit support for the comprehensive model, and evaluate its performance by comparing with one existing GP-based approach.
+In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches.
+There is a lack of a general approaches that achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS.
+Therefore, we proposed a general comprehensive quality model to fill the gaps, and then we proposed a POS-based method with explicit support for the comprehensive model to find optimal compositions.
 

### 2017-03-18 paper.tex
update

@@
 
-The aim of web service composition is to fulfil customers' requirements, which could be denoted as a composition goal: $Comp.G(F(I_{T}, O_{T}), NF(QoS_{T}))$.
+The aim of web service composition considered in this paper is to automatically select the optimal solutions in both QoS and semantic matchmaking quality by a user's request.
+The request is to provide inputs and obtain outputs that should meet the optimal requirements above.
+A motivating example of this problem is shown in Fig \ref{motivation}
+
+\begin{figure}[h]
+\centering
+\fbox{\includegraphics[scale=.28]{motivation.pdf}}
+ \caption{ An example of web service composition}
+ \label{motivation}
+\end{figure}
+
+which could be denoted as a composition goal: $Comp.G(F(I_{T}, O_{T}), NF(QoS_{T}))$.
 This overall composition goal is demonstrated in two parts: functional part and non-functional part.

### 2017-03-18 paper.tex
update

--- 2017-03-17 paper.tex
@@
 
-\section{Problem Description}\label{problemDes}
+\section{Motivation and Problem Description}\label{problemDes}
 
-The aim of web service composition is to fulfil customers' requirements, which could be denoted as a composition goal: $Comp.G(F(I_{T}, O_{T}), NF(QoS_{T}))$.
+The aim of web service composition considered in this paper is to automatically select the optimal solutions in considering both QoS and semantic matchmaking quality by a user's request.
+The request is to provide inputs and obtain outputs, the composition results that should meet the optimal requirements above.
+A motivating example of this problem is shown in Fig \ref{motivation}.
+The figure is a DAG represent a solution with four web services involved for a request $R$ as a composition task, where inputs of the task are \{TravelDepartureDate, HomeCity, ConferenceCity, TravelReturnDate \} and outputs are \{BusTicket, FlightTicket, TouristMap, HotelReservation \}.
+This is a classic example of travel planning from a scholar who seeks for booking services of airplanes, buses and hotels reservation, and also the  tourist map for the conference city.
+The graph also contains edges that marked with connecting outputs and inputs, which represent valid semantic matches where the outputs of a web service can be passed as the inputs of its successors.
+
+\begin{figure}[h]
+\centering
+\fbox{\includegraphics[scale=.25]{motivation.pdf}}
+ \caption{ An example of a web service composition}
+ \label{motivation}
+\end{figure}
+
+Although obtaining a correct combination of web service is essential, there are many ways to chain web services to reach users' needs with different web services in a service repository.
+These web services have different QoS (such as availability, price, reliability and response time ).
+Moreover, the valid semantic matches between two web services could be associated with different semantic matchmaking quality.
+For example, Generate Map service produce StreetMap which is considered to be a valid semantic match to TouristMap required by users.
+Fig .\ref{taxonomy} represents a taxonomy of all the inputs and  the outputs described in Fig.
+\ref{motivation} for a travel planning domain, where the concept Map and its sub-concept urbanMap are assigned with a touristMap instance and streetMap instance respectively.
+The valid semantic match is considered that an instance of urban Map must be an instance of Map, not vice versa.
+If a web service $GenerateTouristMap$ found in the service repository that produces TouristMap as an output.
+I consider its semantic matchmaking quality is higher than that of $GenerateMap$.
+However, $GenerateTouristMap$ might have a very bad QoS.
+
+\begin{figure}[h]
+\centering
+\fbox{\includegraphics[scale=.28]{taxonomy.pdf}}
+ \caption{ A taxonomy of a travel planning domain}
+ \label{taxonomy}
+\end{figure}
+
+We herein formalise the assumptions and concepts utilised in our approach
+which could be denoted as a composition goal: $Comp.G(F(I_{T}, O_{T}), NF(QoS_{T}))$.
 This overall composition goal is demonstrated in two parts: functional part and non-functional part.
@@
 \ref{Comprehensive_Quality_Model}.
+
+We defined our semantic web service composition representation as a weighted graph $WG = (V, E)$, where $V$ is a set of services as vertex: $V=\{S1, S2...Sn \}$ and $E$ is a set of edges $E = \{e_{1}, e_{2},...
+e_{n} \}$.
+Each edge is considered to be a semantic web service link $sm_{L}$ , so each edge $e$ is consisting of a pair of quality values, $mt_{L}$ and $s_{L}$ as weigths.
+Here we provide an example of semantic web service composition, which is described in Fig.
+\ref{wscs}.
+The data of composition web service flows from the start to the end, where five web services involved and linked with each other using edge connections.
+Besides that, weights are calculated for all edges $e_{1}, e_{2},...
+e_{n}$.
 
@@
 \end{figure*}
-
-\subsection{Weighted Graph Composition}
-
-We defined our semantic web service composition representation as a weighted graph $WG = (V, E)$, where $V$ is a set of services as vertex: $V=\{S1, S2...Sn \}$ and $E$ is a set of edges $E = \{e_{1}, e_{2},...
-e_{n} \}$.
-Each edge is considered to be a semantic web service link $sm_{L}$ , so each edge $e$ is consisting of a pair of quality values, $mt_{L}$ and $s_{L}$ as weigths.
-Here we provide an example of semantic web service composition, which is described in Fig.
-\ref{wscs}.
-The data of composition web service flows from the start to the end, where five web services involved and linked with each other using edge connections.
-Besides that, weights are calculated for all edges $e_{1}, e_{2},...
-e_{n}$.
-
-\begin{figure}[h]
-\centering
-\fbox{\includegraphics[scale=.28]{weigtedGraphExample.pdf}}
- \caption{Composition weighted graph solution}
- \label{wscs}
-\end{figure}
 

### 2017-03-19 paper.tex
update

@@
 \cite{qi2010combining} propose a heuristic service composition method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal for QoS.
-but there exists scalability problems for the enumeration technique.
+but there exists a scalability problem for the enumeration technique.
 EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problems.
@@
 \section{Motivation and Problem Description}\label{problemDes}
+\subsection{Motivation}\label{Motivation}
 
@@
 The figure is a DAG represent a solution with four web services involved for a request $R$ as a composition task, where inputs of the task are \{TravelDepartureDate, HomeCity, ConferenceCity, TravelReturnDate \} and outputs are \{BusTicket, FlightTicket, TouristMap, HotelReservation \}.
-This is a classic example of travel planning from a scholar who seeks for booking services of airplanes, buses and hotels reservation, and also the  tourist map for the conference city.
+This is a classic example of travel planning problem from scholars who seeks for booking services of airplanes, buses and hotels reservation, and also the  tourist map for the conference city.
 The graph also contains edges that marked with connecting outputs and inputs, which represent valid semantic matches where the outputs of a web service can be passed as the inputs of its successors.
@@
 
-We herein formalise the assumptions and concepts utilised in our approach
-which could be denoted as a composition goal: $Comp.G(F(I_{T}, O_{T}), NF(QoS_{T}))$.
-This overall composition goal is demonstrated in two parts: functional part and non-functional part.
-The functional part is defined by given task inputs and desired task outputs.
-The nonfunctional part specifies overall QoS requirements.
+\subsection{Problem Formulation}\label{Motivation}
+
+We herein give formal definitions of the concepts regarding the semantic web service composition problem utilised in our approach that consists of three main concepts: a semantic web service model, a weighted DAG composition model, and QoS calculation model.
+
+\textbf{Semantic Web Service Model}.
+The semantic web service model represent web services with functional descriptions, and how interoperability of web services enable matchmaking to automatically generate composition solutions.
+
+\textbf{Definition 1.} A request from users is defined as a composition task in a tuple: $Comp.T = \{I_{T}, O_{T}\}$ by giving task inputs $I_{T}$ and expecting desired task outputs $O_{T}$, where $I_{T}$ and $O_{T}$ are linked to the concepts $C$ in an ontology $O = \{C, Taxonomy\}$.
+
+\textbf{Definition 2.} A semantic web service is defined as a tuple $S = \{ I_{S}, O_{S}, QoS_S \}$
+
+The nonfunctional part specifies overall QoS
+
+ requirements.
 To accomplish the composition goal, two stages are involved, services discovery and service selection.

### 2017-03-19 paper.tex
update

@@
 
-We herein give formal definitions of the concepts regarding the semantic web service composition problem utilised in our approach that consists of three main concepts: a semantic web service model, a weighted DAG composition model, and QoS calculation model.
+We herein give formal definitions of the assumptions the concepts regarding the semantic web service composition problem utilised in our approach that consists of three main concepts: a semantic web service model, a semantic matchmaking model, a weighted DAG composition model, and QoS calculation model.
 
@@
 
-\textbf{Definition 1.} A request from users is defined as a composition task in a tuple: $Comp.T = \{I_{T}, O_{T}\}$ by giving task inputs $I_{T}$ and expecting desired task outputs $O_{T}$, where $I_{T}$ and $O_{T}$ are linked to the concepts $C$ in an ontology $O = \{C, Taxonomy\}$.
+\textbf{Definition 1.} A request from users is defined as a composition task in a tuple: $Comp.T = \{I_{T}, O_{T}\}$ by giving a set of task inputs $I_{T}$ and expecting  a set of desired task outputs $O_{T}$, where $I_{T}$ and $O_{T}$ are associated with related concepts $I^{C}_{T}$ and $O^{C}_{T}$ respectively in an ontology $O = \{C, Taxonomy \mid I^{C}_{T}, O^{C}_{T}  \subseteq C \}$.
 
-\textbf{Definition 2.} A semantic web service is defined as a tuple $S = \{ I_{S}, O_{S}, QoS_S \}$
+\textbf{Definition 2.} A semantic web service is defined as a tuple $S = \{ I_{S}, O_{S}, QoS_S \}$ $\in$ $\mathcal{SR}$, where $I_{S}$ is a set of service inputs that must be satisfied to invoke $S$, and $O_{S}$ is a set of service outputs returned by the execution of $S$.
+$I_{S}$ and $O_{S}$ are concept-related instances that are linked to the concepts $I^{C}_{S}$ and $O^{C}_{S}$, where $ I^{C}_{S}, O^{C}_{S}  \subseteq C$.
+$QoS_S = \{ t_s, c_s, r_s, a_s, ...
+\} $ is a set of non-functional attributes of $S$, it typically refers to response time $t_s$, cost $c_s$, reliability $r_s$, and availability $a_s$ \cite{zeng2003quality}.
+$\mathcal{SR}$ is a set of $S$, where all the $S$ are registered.
 
-The nonfunctional part specifies overall QoS
+\textbf{Semantic Matchmaking Model}.
+The mechanism to compose web services relays on the semantic inputs and outputs, which enable inputs to be matched by outputs.
+To measure the quality of these matches, we utilise different matchmaking types (\textit{exact, plugin subsumes and fail} \cite{paolucci2002semantic} ) into consideration for exploiting the semantics of inputs and outputs.
 
- requirements.
-To accomplish the composition goal, two stages are involved, services discovery and service selection.
-Service discovery is to find matching web services: $S_{n}(F(I_{S}, O_{S}), NF(QoS_{S}))$ from a Service Repository: $\mathcal{S}$ $=  \{S_{1}, S_{2},..., S_{n} \}$ for the given $I_{T}$.
-If no atomic web service could satisfy the composition goal, a composition of web services will be found to meet $Comp.G$.
-To ensure the composition solution returns the desired $Comp.G$ that considers a higher degree of matching $O_{T}$ and a near-optimised $QoS_{T}$, We first demonstrate the concepts in both semantic matchmaking types and $QoS$ as follows, and then propose a quality model that take care of semantic matchmaking quality and QoS simultaneously in Sect.
-\ref{Comprehensive_Quality_Model}.
+\textbf{Definition 3.} Given $a, b \in C$, $type(a, b)$ returns the matchmaking types of between two concepts related to outputs and inputs of two difference web services, and this matchmaking type is determined by the logic described in the $O$.
 
-We defined our semantic web service composition representation as a weighted graph $WG = (V, E)$, where $V$ is a set of services as vertex: $V=\{S1, S2...Sn \}$ and $E$ is a set of edges $E = \{e_{1}, e_{2},...
-e_{n} \}$.
-Each edge is considered to be a semantic web service link $sm_{L}$ , so each edge $e$ is consisting of a pair of quality values, $mt_{L}$ and $s_{L}$ as weigths.
-Here we provide an example of semantic web service composition, which is described in Fig.
-\ref{wscs}.
-The data of composition web service flows from the start to the end, where five web services involved and linked with each other using edge connections.
-Besides that, weights are calculated for all edges $e_{1}, e_{2},...
-e_{n}$.
+If both $a$ and $b$ are equivalent, $exact$ type ($a \equiv b$) is returned.
+If the concept of $a$ is a sub-concept of the concept of $b$ type ($a \sqsubseteq b$) is returned. 
+If the concept of $a$ is a super-concept of the concept of $b$, $subsumes$ type ($a \sqsupseteq b$) is returned. 
+If none of previous matchmaking types are returned, $fail$ type ($a \perp b$) is returned.
+
+\textbf{Definition 4.} Given $(a \in O^{C}_{S_m}) \vee (b \in I^{C}_{S_n}) \wedge (m \neq n) $, a $full match(a \rightarrow b)$ holds if $type(a, b) \neq subsumes \mid fail$.
+The operator ``$ \rightarrow$'' means $a$ is passed to $b$.
+The full match is a guarantee of completely valid  ``$ \rightarrow$'' operation as $b$ is fully satisfied by $a$.
+
+\textbf{Weighted DAG Composition Model}.
+web service composition is considered to be a data workflow, where services are chained together by their inputs and outputs using the two models defined before.
+Naturally, all these concepts can be captured in a weighted DAG as $WG = (V, E)$ , where:
+
+$V=\{Start, S1, S2...Sn, End\}$ is a set of services, where $Start$ and $End$ are two special services defined as $Start = \{ \phi, I_T, \phi \}$ and $End  = \{ O_T, \phi, \phi \}$.
+
+$E = \{e_{1}, e_{2},... e_{n} \}$ is a set of edges. where $e = O_{S_{m}} \cup I_{S_{n}} \cup $ $fullmatch(O_{m} \rightarrow I_{n})$ is source service $S_m$ and target service $s_n$
 
 \subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
-The semantic service matchmaking aims to discover appropriate services from service repository.
-A semantic web service is defined by $S(F(I_{S}\in C_{1}, O_{S}\in C_{2}), NF(QoS_{S}))$, where both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology $O$ respectively, satisfying $O=\{C, Taxonomy\}$.
-A web service matching process is to match the output and input concepts of two services according to the Taxonomy within an ontology.
-To measure the quality of semantic matchmaking, different matching levels are typically considered in the literature \cite{paolucci2002semantic}.
-To understand these levels, let us define two web services associated with concept-related parameters in a particular domain.
-$S_{1}$ $(F(I_{S_1}\in C_{1}, O_{S_1}\in C_{2}), NF(QoS_{S_1}))$ and  $S_{2}$ $(F(I_{S_2}\in C_{3}, O_{S_2}\in C_{4}), NF(QoS_{S_2}))$ and an ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$.
-The matching levels to be considered are:
-
-\begin{itemize}
-\item \textit{Exact} ($\equiv$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Exact match ($ O_{S_1} \in S_{1} \equiv I_{S_2} \in S_{2}$), if  Concept $C_{2}$ and Concept $C_{3}$ are equivalent.
-\item \textit{Plugin} ($\sqsubseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Plugin match ($O_{S_1} \in S_{1} \sqsubseteq_{n} I_{S_2} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of children concepts ($n=1$ stands for direct children).
-\item \textit{Subsume} ($\sqsupseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Subsume matched($O_{S_1} \in S_{1} \sqsupseteq_{n} I_{S_2} \in S_{2}$), if  Concept $C_{2}$ is a super-concept of  Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of parent concepts ($n=1$ stands for direct parent).
-\item \textit{Fail} ($\perp$).
-Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are not matched (Fail) ($O_{S_1} \in S_{1} \perp I_{S_2} \in S_{2}$), if none of the previous matches discovered.
-\end{itemize}
-
-The semantic matchmaking is achieved by utilising OWL2 and OWL-S or other semantic markup languages for web services.
-In this paper, we use MECE (Mediation Contract Extension) \cite{bleul2008self} and OWL-DL.
-MECE is considered to be an alternative semantic annotation for WSDL.
-MECE defines the service-related inputs and outputs with parameter-related concepts.
-OWL-DL is a sublanguage of OWL extended from RDF.
-It specifies semantic information of concepts involved in MECE.
 

### 2017-03-19 paper.tex
update

@@
 
-\textbf{Definition 3.} Given $a, b \in C$, $type(a, b)$ returns the matchmaking types of between two concepts related to outputs and inputs of two difference web services, and this matchmaking type is determined by the logic described in the $O$.
-
+\textbf{Definition 3.} Given $a, b \in C$, $type(a, b)$ returns the matchmaking types of two concepts, and this matchmaking type is determined by the logic described in the $O$.
 If both $a$ and $b$ are equivalent, $exact$ type ($a \equiv b$) is returned.
@@
 
-\textbf{Definition 4.} Given $(a \in O^{C}_{S_m}) \vee (b \in I^{C}_{S_n}) \wedge (m \neq n) $, a $full match(a \rightarrow b)$ holds if $type(a, b) \neq subsumes \mid fail$.
-The operator ``$ \rightarrow$'' means $a$ is passed to $b$.
-The full match is a guarantee of completely valid  ``$ \rightarrow$'' operation as $b$ is fully satisfied by $a$.
+We use the $type(a, b)$ to define full matchmaking between two concept-related input and output of two services.
+
+\textbf{Definition 4.} Given $(a \in O^{C}_{S_m}) \vee (b \in I^{C}_{S_n}) \wedge (m \neq n) $, a $full match(a \rightarrow b)$ holds if $type(a, b)$ returns $exact$ or $plugin$.
+The operator ``$ \rightarrow$'' means $a$ is passed to $b$, and $b$ is fully satisfied by $a$.
+The full match is a guarantee of completely valid  ``$ \rightarrow$'' operation, whereas, partial matches are not considered in this paper.
 
@@
 
-$E = \{e_{1}, e_{2},... e_{n} \}$ is a set of edges. where $e = O_{S_{m}} \cup I_{S_{n}} \cup $ $fullmatch(O_{m} \rightarrow I_{n})$ is source service $S_m$ and target service $s_n$
+$E = \{e_{1}, e_{2},...
+e_{n} \}$ is a set of edges, where each edge has a set of incoming outputs $O_{S_{src}}$ from source service $S_{src}$ and a set of outgoing inputs $I_{S_{src}}$ from target service $S_{tar}$.
 
-\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
+$e = \{ (O_{S_{src}} \cup I_{S_{src}}) \mid \forall o \in O_{S_{src}}, \exists i \in O_{S_{src}} \wedge fullmatch (o \rightarrow i) \}$
+
+\textbf{QoS Model in Weighted DAG}
 

### 2017-03-20 paper.tex
update

@@
 We herein give formal definitions of the assumptions the concepts regarding the semantic web service composition problem utilised in our approach that consists of three main concepts: a semantic web service model, a semantic matchmaking model, a weighted DAG composition model, and QoS calculation model.
+\vspace{0.3cm}
 
@@
 $\mathcal{SR}$ is a set of $S$, where all the $S$ are registered.
+\vspace{0.3cm}
 
@@
 The full match is a guarantee of completely valid  ``$ \rightarrow$'' operation, whereas, partial matches are not considered in this paper.
+\vspace{0.3cm}
 
@@
 $E = \{e_{1}, e_{2},...
-e_{n} \}$ is a set of edges, where each edge has a set of incoming outputs $O_{S_{src}}$ from source service $S_{src}$ and a set of outgoing inputs $I_{S_{src}}$ from target service $S_{tar}$.
+e_{m} \}$ is a set of edges, where each edge has a set of incoming outputs $O_{S_{src}}$ from source service $S_{src}$ and a set of outgoing inputs $I_{S_{src}}$ from target service $S_{tar}$.
 
 $e = \{ (O_{S_{src}} \cup I_{S_{src}}) \mid \forall o \in O_{S_{src}}, \exists i \in O_{S_{src}} \wedge fullmatch (o \rightarrow i) \}$
+\vspace{0.5cm}
 
-\textbf{QoS Model in Weighted DAG}
+\textbf{QoS Model in a Weighted DAG}
+Four most often considered QoS parameters \cite{zeng2003quality} are response time, cost, reliability and availability described as follows:\textit{Response time} ($T$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.\textit{Cost} ($C$) is the amount of money that a service requester has to pay for executing the web service.
+\textit{Reliability} ($R$) is the probability that a request is correctly responded within the maximum expected time frame.
+\textit{Availability} ($A$) is the probability that a web service is accessible.
 
-\subsection{Quality of Service}\label{Quality of Service and Composition Constructs}
-According to \cite{zeng2003quality}, four most often considered QoS parameters are response time, cost, reliability and availability described as follows:
-\begin{itemize}
-\item \textit{Response time} ($T$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.
-\item \textit{Cost} ($C$) is the amount of money that a service requester has to pay for executing the web service
-\item \textit{Reliability} ($R$) is the probability that a request is correctly responded within the maximum expected time frame.
-\item \textit{Availability} ($A$) is the probability that a web service is accessible.
-\end{itemize}
-The aggregation value of QoS attributes for a composite service varies with respect to different constructs, which reflects how services associated with each other in a service composition \cite{zeng2003quality}.
+	The aggregation value of QoS in a DAG with respect to different constructs, which reflects how services associated with each other in a service composition.
 Here we consider two composition constructs: sequence and parallel constructs, in building the composition web service.
 The QoS calculation models are described as follows:
-\subsubsection{Sequence construct}
-all involved atomic services associated with a sequence construct are executed in a definite sequence order.
-The aggregation value for total time ($T$) and total cost ($C$) is as the sum of time and cost of web services involved respectively.
-The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory.
-This construct is shown in Fig.
-\ref{sequence}.
-\subsubsection{Parallel construct}
-Web services in a parallel construct are executed concurrently.
-The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is determined by the most time-consuming path in the composition flow of the solution.
-This construct is presented in Fig.
-\ref{parallel}.
 
-\begin{figure}[h]
-\centerline{
-\fbox{
-\begin{tabular}{p{0.6\linewidth}}
-\space\hfill\includegraphics[width=2in]{sequence.pdf}\hfill\space\\[0.2cm]
-$T=\sum\limits^m_{n=1}t_n$ \hfill $C=\sum\limits^m_{n=1}c_n$ \hfill
-$A=\prod\limits^m_{n=1}a_n$ \hfill $R=\prod\limits^m_{n=1}r_n$
-\end{tabular}}}
-\caption{Sequence construct and calculation of its QoS properties
-\cite{yu2013adaptive}.}
-\label{sequence}
-%\end{figure}
-\vspace{0.2cm}
-%\begin{figure}
-\centerline{
-\fbox{
-\begin{tabular}{p{0.6\linewidth}}
-\space\hfill\includegraphics[width=1.4in]{parallel.pdf}\hfill\space\\[0.2cm]
-\space\hfill$T=MAX\{t_n|n\in\{1,\ldots,m\}\}$\hfill\space\\[0.2cm]
-$C=\sum\limits^m_{n=1}c_n$ \hfill $A=\prod\limits^m_{n=1}a_n$ \hfill
-$R=\prod\limits^m_{n=1}r_n$
-\end{tabular}}}
-\caption{Parallel construct and calculation of its QoS properties
-\cite{yu2013adaptive}.}
-\label{parallel}
-\end{figure}
+\textbf{Definition 5.} $V_{A}(WG)$ is a function that given a $WG$, a aggregated $availability$ value is returned, which is defined as :
+$V_{A}(WG)=\prod\limits^n_{k=1}a_k$, for all ${S_1, S_2, ... S_n} \subset V$.
+
+\textbf{Definition 6.} $V_{R}(WG)$ is a function that given a $WG$, a aggregated $reliability$ value is returned, which is defined as :
+$V_{R}(WG)=\prod\limits^n_{k=1}r_k$, for all ${S_1, S_2, ... S_n} \subset V$.
+
+\textbf{Definition 7.} $V_{C}(WG)$ is a function that given a $WG$, a aggregated cost value is returned, which is defined as :
+$V_{C}(WG)=\sum\limits^n_{k=1}c_k$, for all ${S_1, S_2, ... S_n} \subset V$.
+
+\textbf{Definition 8.} $V_{T}(WG)$ is a function that given a $WG$, a aggregated time value is returned, where  $T$ is determined by the most time-consuming path in the composition flow of the solution, which is defined as :
+$V_{T}(WG)$ $=MAX\{timePath(WG)_n$ $|n\in\{1,\ldots,m\}\}$, where m is the number of $timePath$.
+
+\vspace{0.5cm}
+
+\textbf{Composition Problem}
+A set of semantic web services $S$ are chained as a weighted DAG composition mode $WG$ when a composition task $Comp.T$ is requested by users.
+The composition problem considered in this paper satisfying the follows:
 

### 2017-03-20 paper.tex
update

@@
 
-\textbf{Definition 1.} A request from users is defined as a composition task in a tuple: $Comp.T = \{I_{T}, O_{T}\}$ by giving a set of task inputs $I_{T}$ and expecting  a set of desired task outputs $O_{T}$, where $I_{T}$ and $O_{T}$ are associated with related concepts $I^{C}_{T}$ and $O^{C}_{T}$ respectively in an ontology $O = \{C, Taxonomy \mid I^{C}_{T}, O^{C}_{T}  \subseteq C \}$.
+\textbf{Definition 1.} A request from users is defined as a composition task in a tuple: $Comp.T = \{I_{T}, O_{T}\}$ by giving a set of task inputs $I_{T}$ and expecting  a set of desired task outputs $O_{T}$, where $I_{T}$ and $O_{T}$ are associated with related concepts $I^{C}_{T}$ and $O^{C}_{T}$ respectively in an ontology $O = \{(C, Taxonomy) \mid I^{C}_{T}, O^{C}_{T}  \subseteq C \}$.
 
@@
 
-\textbf{Definition 4.} Given $(a \in O^{C}_{S_m}) \vee (b \in I^{C}_{S_n}) \wedge (m \neq n) $, a $full match(a \rightarrow b)$ holds if $type(a, b)$ returns $exact$ or $plugin$.
-The operator ``$ \rightarrow$'' means $a$ is passed to $b$, and $b$ is fully satisfied by $a$.
-The full match is a guarantee of completely valid  ``$ \rightarrow$'' operation, whereas, partial matches are not considered in this paper.
+\textbf{Definition 4.} Given $(a \in O^{C}_{S_m}) \vee (b \in I^{C}_{S_n}) \wedge (m \neq n) $, a $full match(a \Rightarrow b)$ holds if $type(a, b)$ returns $exact$ or $plugin$.
+The operator ``$ \Rightarrow$'' means $a$ is passed to $b$, and $b$ is fully satisfied by $a$.
+The full match is a guarantee of completely valid  ``$ \Rightarrow$'' operation, whereas, partial matches are not considered in this paper.
+
+\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $q(a \Rightarrow b)$ is a function that given a output-related concept of a service and a input-related concept of another service, it returns the concept similarities between them.
 \vspace{0.3cm}
@@
 
-$e = \{ (O_{S_{src}} \cup I_{S_{src}}) \mid \forall o \in O_{S_{src}}, \exists i \in O_{S_{src}} \wedge fullmatch (o \rightarrow i) \}$
+$e = \{ (O_{S_{src}} \cup I_{S_{src}}) \mid \forall o \in O_{S_{src}}, \exists i \in O_{S_{src}} \wedge fullmatch (o \Rightarrow i) \}$
 \vspace{0.5cm}
@@
 
-\textbf{Definition 5.} $V_{A}(WG)$ is a function that given a $WG$, a aggregated $availability$ value is returned, which is defined as :
+\textbf{Definition 6.} $V_{A}(WG)$ is a function that given a $WG$, a aggregated $availability$ value is returned, which is defined as :
 $V_{A}(WG)=\prod\limits^n_{k=1}a_k$, for all ${S_1, S_2, ... S_n} \subset V$.
 
-\textbf{Definition 6.} $V_{R}(WG)$ is a function that given a $WG$, a aggregated $reliability$ value is returned, which is defined as :
+\textbf{Definition 7.} $V_{R}(WG)$ is a function that given a $WG$, a aggregated $reliability$ value is returned, which is defined as :
 $V_{R}(WG)=\prod\limits^n_{k=1}r_k$, for all ${S_1, S_2, ... S_n} \subset V$.
 
-\textbf{Definition 7.} $V_{C}(WG)$ is a function that given a $WG$, a aggregated cost value is returned, which is defined as :
+\textbf{Definition 8.} $V_{C}(WG)$ is a function that given a $WG$, a aggregated cost value is returned, which is defined as :
 $V_{C}(WG)=\sum\limits^n_{k=1}c_k$, for all ${S_1, S_2, ... S_n} \subset V$.
 
-\textbf{Definition 8.} $V_{T}(WG)$ is a function that given a $WG$, a aggregated time value is returned, where  $T$ is determined by the most time-consuming path in the composition flow of the solution, which is defined as :
+\textbf{Definition 9.} $V_{T}(WG)$ is a function that given a $WG$, a aggregated time value is returned, where  $T$ is determined by the most time-consuming path in the composition flow of the solution, which is defined as :
 $V_{T}(WG)$ $=MAX\{timePath(WG)_n$ $|n\in\{1,\ldots,m\}\}$, where m is the number of $timePath$.
@@
 A set of semantic web services $S$ are chained as a weighted DAG composition mode $WG$ when a composition task $Comp.T$ is requested by users.
-The composition problem considered in this paper satisfying the follows:
+The composition problem considered in this paper to automatically generate $WG$, satisfying the follows:
+
+$\forall WG^{'}$ , $q(a \Rightarrow b) \cup V_{A}(WG^{'}) \cup V_{R}(WG^{'}) \cup V_{C}(WG^{'}) \cup V_{T}(WG^{'})  \leq q(a \Rightarrow b) \cup V_{A}(WG) \cup V_{R}(WG) \cup V_{C}(WG) \cup V_{T}(WG) $
 

### 2017-03-20 paper.tex
update

@@
 Existing works on web service composition often concern either semantic web  service composition or QoS-aware web service composition.
-Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS simultaneously that can achieve a more desirable trade-off in consideration of both sides by conducting an experiment comparing with promising QoS-aware model.
-Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model, and compare the PSO-based method with one recent GP-based method to show its performance in finding a more optimised solution.
+Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS simultaneously that can achieve a more desirable trade-off in consideration of both sides.
+Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model.
+We compare this model with a promising QoS-aware model, and also compare our PSO-based method with one recent GP-based method to show its performance in finding a more optimised solution.
 
@@
 \section{Related Work} \label{relatedWork}
-Substantial works on web service composition focus on either semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive}, However, few researchers address both semantic matchmaking quality and QoS requirements at the same time for web service composition problems.
+Substantial works on web service composition focus on either semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive}, However, few researchers address both semantic matchmaking quality and QoS requirements for web service composition problems.
 To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some attempts on service composition that considers both aspects.
 
-Semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} captures the semantic description of web services' parameters using some kind of logic (e.g., description logic) for enabling the interoperability of web services, where the number of web services or length of the graph is minimised to reach the optimised graph-based composition solutions.
+Semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} captures the semantic description of web services' parameters using some kind of logic (e.g., description logic) for enabling the interoperability of web services, where the number of web services or length of a graph is minimised to reach the optimised graph-based composition solutions.
 However, this evaluation approach does not guarantee optimised qualities of composition solutions for QoS.
@@
 Qi et al.
-\cite{qi2010combining} propose a heuristic service composition method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal for QoS.
+\cite{qi2010combining} propose a heuristic service composition method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal QoS.
 but there exists a scalability problem for the enumeration technique.
-EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problems.
+EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problem.
 Gupta et al.
@@
 A hybird approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions with functional correctness.
-In particularly, the greedy search is used to generate  directed acyclic graphs (DAGs) as composition solutions, which is further transferred to the tree structure for initialisation and mutation using unfolding techniques.
+In particularly, a greedy search is used to generate  directed acyclic graphs (DAGs) as composition solutions that is further transferred to tree structures for initialisation and mutation.
 To eliminating the transformation process from DAGs, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation.
 An indirect PSO-based approach was introduced in \cite{da2016particle}.
-An optimised queue is used as an indirect representation that is decoded into a DAG as a composition solution.
-These QoS-aware approaches does not consider semantic matchmaking quality, which could lead to over-general outputs to be produced by selected services, The finding is evidently supported by our first comparison experiment.
-In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users.
-In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS.
+An optimised queue is used as an indirect representation that is decoded into a DAG-based solution.
+These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality, which could lead to too specific outputs produced by the selected services, The finding is supported by our first comparison experiment.
 
@@
 Lecue et al.
-\cite{lecue2009optimizing} employ Genetic Algorithm for semi-automated web service composition considering semantic matchmaking quality and QoS, where the semantic matchmaking quality is measured by the quality of semantic links that requires formal definition of ontology in Description Logic.
-This evaluation takes huge cost and time for the domain experts to establish required ontology.
+\cite{lecue2009optimizing} employ Genetic Algorithm for semi-automated web service composition considering semantic matchmaking quality and QoS, where the semantic matchmaking quality is measured through evaluating semantic links, which requires a formal definition of ontology in Description Logic.
+This evaluation method takes huge cost and time for the domain experts to establish required ontology.
 Another GA-based approach work \cite{fanjiang2014semantic} employs a sequence of fitness functions are used in the binary selection of chromosomes, where semantic matchmaking quality is evaluate in two fitness functions considering concept similarity and parameter similarity respectively, but different semantic matchmaking types are ignored in the evaluation model.
@@
 There is a lack of a general approaches that achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS.
-Therefore, we proposed a general comprehensive quality model to fill the gaps, and then we proposed a POS-based method with explicit support for the comprehensive model to find optimal compositions.
+Therefore, we proposed a general comprehensive quality model to fill the gaps, and then we proposed a PSO-based method with explicit support for the comprehensive model to find optimal compositions.
 
@@
 The figure is a DAG represent a solution with four web services involved for a request $R$ as a composition task, where inputs of the task are \{TravelDepartureDate, HomeCity, ConferenceCity, TravelReturnDate \} and outputs are \{BusTicket, FlightTicket, TouristMap, HotelReservation \}.
-This is a classic example of travel planning problem from scholars who seeks for booking services of airplanes, buses and hotels reservation, and also the  tourist map for the conference city.
+This is a classic example of travel planning problem for scholars who seek for booking services of airplanes, buses and hotels reservation, and also generating tourist maps for the conference city.
 The graph also contains edges that marked with connecting outputs and inputs, which represent valid semantic matches where the outputs of a web service can be passed as the inputs of its successors.
@@
 
-Although obtaining a correct combination of web service is essential, there are many ways to chain web services to reach users' needs with different web services in a service repository.
-These web services have different QoS (such as availability, price, reliability and response time ).
-Moreover, the valid semantic matches between two web services could be associated with different semantic matchmaking quality.
-For example, Generate Map service produce StreetMap which is considered to be a valid semantic match to TouristMap required by users.
-Fig .\ref{taxonomy} represents a taxonomy of all the inputs and  the outputs described in Fig.
-\ref{motivation} for a travel planning domain, where the concept Map and its sub-concept urbanMap are assigned with a touristMap instance and streetMap instance respectively.
-The valid semantic match is considered that an instance of urban Map must be an instance of Map, not vice versa.
-If a web service $GenerateTouristMap$ found in the service repository that produces TouristMap as an output.
-I consider its semantic matchmaking quality is higher than that of $GenerateMap$.
-However, $GenerateTouristMap$ might have a very bad QoS.
+Although obtaining a correct combination of web service is essential, there are many ways to chain web services to reach users' needs with different web services from a service repository.
+These web services have different QoS in terms of different availability, price, reliability and response time.
+Moreover, valid semantic matches between two web services could also have different matchmaking quality.
+For example, Generate Map service produce StreetMap which is considered to be a valid semantic match to TouristMap from users' perspectives.
+These perspectives are captured in a taxonomy Fig .\ref{taxonomy}, where all the inputs and the outputs related to the web services are described for a travel planning domain.
+For example, the concept Map and its sub-concept urbanMap are assigned with a touristMap instance and streetMap instance respectively in Fig .\ref{taxonomy}.
+The valid semantic match is considered that an instance of urban Map can be an instance of Map, but not vice versa.
+However, if a web service $GenerateTouristMap$ is found in the service repository that produces TouristMap as an output, but price is "16.87".
+I consider its semantic matchmaking quality is higher than the service $GenerateMap$, but price negatively contributes to the overall QoS.
+Therefore, automatically generating solutions in considering both QoS and matchmaking quality is a very challenging problem.
 
@@
 
-We herein give formal definitions of the assumptions the concepts regarding the semantic web service composition problem utilised in our approach that consists of three main concepts: a semantic web service model, a semantic matchmaking model, a weighted DAG composition model, and QoS calculation model.
+We herein give formal definitions of the assumptions the concepts regarding the semantic web service composition problem utilised in our approach that consists of four main concepts: a semantic web service model, a semantic matchmaking model, a weighted DAG composition model, and QoS calculation model, and composition problem model.
 \vspace{0.3cm}
@@
 \textbf{Semantic Web Service Model}.
-The semantic web service model represent web services with functional descriptions, and how interoperability of web services enable matchmaking to automatically generate composition solutions.
+The semantic web service model represents web services with functional descriptions, and how interoperability of web services enables matchmaking for automatically generating composition solutions.
 
@@
 \} $ is a set of non-functional attributes of $S$, it typically refers to response time $t_s$, cost $c_s$, reliability $r_s$, and availability $a_s$ \cite{zeng2003quality}.
-$\mathcal{SR}$ is a set of $S$, where all the $S$ are registered.
+$\mathcal{SR}$ is a service repository consisting of a set of $S$, where all the $S$ are registered.
 \vspace{0.3cm}
@@
 \textbf{Semantic Matchmaking Model}.
-The mechanism to compose web services relays on the semantic inputs and outputs, which enable inputs to be matched by outputs.
+The mechanism to compose web services relays on the semantic descriptions of inputs and outputs, which enable inputs of a service to be matched by outputs of another.
 To measure the quality of these matches, we utilise different matchmaking types (\textit{exact, plugin subsumes and fail} \cite{paolucci2002semantic} ) into consideration for exploiting the semantics of inputs and outputs.
@@
 \textit{Availability} ($A$) is the probability that a web service is accessible.
-
-	The aggregation value of QoS in a DAG with respect to different constructs, which reflects how services associated with each other in a service composition.
-Here we consider two composition constructs: sequence and parallel constructs, in building the composition web service.
+The aggregation value of QoS in a DAG respect to the structures of DAG, which reflects how services associated with each other in a service composition.
 The QoS calculation models are described as follows:
 
-\textbf{Definition 6.} $V_{A}(WG)$ is a function that given a $WG$, a aggregated $availability$ value is returned, which is defined as :
-$V_{A}(WG)=\prod\limits^n_{k=1}a_k$, for all ${S_1, S_2, ... S_n} \subset V$.
+\textbf{Definition 6.} $V_{A}(WG)$ is a function that given a $WG$, a aggregated $availability$ value is returned defined as :
+$V_{A}(WG)=\prod\limits^n_{k=1}a_k$, for all $\{S_1, S_2, ... S_n\} \subset V$.
 
-\textbf{Definition 7.} $V_{R}(WG)$ is a function that given a $WG$, a aggregated $reliability$ value is returned, which is defined as :
-$V_{R}(WG)=\prod\limits^n_{k=1}r_k$, for all ${S_1, S_2, ... S_n} \subset V$.
+\textbf{Definition 7.} $V_{R}(WG)$ is a function that given a $WG$, a aggregated $reliability$ value is returned defined as :
+$V_{R}(WG)=\prod\limits^n_{k=1}r_k$, for all $\{S_1, S_2, ... S_n\} \subset V$.
 
-\textbf{Definition 8.} $V_{C}(WG)$ is a function that given a $WG$, a aggregated cost value is returned, which is defined as :
-$V_{C}(WG)=\sum\limits^n_{k=1}c_k$, for all ${S_1, S_2, ... S_n} \subset V$.
+\textbf{Definition 8.} $V_{C}(WG)$ is a function that given a $WG$, a aggregated cost value is returned defined as :
+$V_{C}(WG)=\sum\limits^n_{k=1}c_k$, for all $\{S_1, S_2, ... S_n\} \subset V$.
 
@@
 
-$\forall WG^{'}$ , $q(a \Rightarrow b) \cup V_{A}(WG^{'}) \cup V_{R}(WG^{'}) \cup V_{C}(WG^{'}) \cup V_{T}(WG^{'})  \leq q(a \Rightarrow b) \cup V_{A}(WG) \cup V_{R}(WG) \cup V_{C}(WG) \cup V_{T}(WG) $
+$\forall WG^{'}$ , $\{q(a \Rightarrow b) \} \cup V_{A}(WG^{'}) \cup V_{R}(WG^{'}) \cup V_{C}(WG^{'}) \cup V_{T}(WG^{'})  \leq \{ q(a \Rightarrow b) \} \cup V_{A}(WG) \cup V_{R}(WG) \cup V_{C}(WG) \cup V_{T}(WG) $
 

### 2017-03-22 paper.tex
commit

@@
  \Output{Optimised service queue $queue$,Optimised Weighted Graph $OPTWG$}
- Map each relevant service to an index in the particle's position vector\;
+ Map each relevant service to an index in the particle's position vector\;https://www.facebook.com/
  Randomly initialise each particle in the swarm\;
@@
 \section{Results and Analysis}\label{results_analysis}
-\subsection{Comparison Test with QoS Evaluation Model}\label{comparisonTest}
+\subsection{Comparison Test for Comprehensive Quality Evaluation Mode and QoS Evaluation Model}\label{comparisonTest}
+To analyse the differences between optimal solutions evaluated by comprehensive evaluation model and QoS evluation mode, We first look at the $MT$, $S$ and $QoS$
+
 QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid} do consider two semantic matchmaking types (Exact and Plugin) for discovering desired web service, but there is no measurement of matchmaking types and concept similarity, so the weights for $MT$ and $S$ are considered to be 0.

### 2017-03-23 paper.tex
update

@@
 but there exists a scalability problem for the enumeration technique.
-EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problem.
+EC tecQoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid}hniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problem.
 Gupta et al.
@@
  \label{motivation}
-\end{figure}
+\end{figure}QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid}
 
@@
 \textbf{Semantic Web Service Model}.
-The semantic web service model represents web services with functional descriptions, and how interoperability of web services enables matchmaking for automatically generating composition solutions.
+The semantic web service model represents web services with functional descriptions, and how interoperability of web services enables matchmaking for automatically generating composition solutions.QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid}
 
@@
 \textbf{Composition Problem}
-A set of semantic web services $S$ are chained as a weighted DAG composition mode $WG$ when a composition task $Comp.T$ is requested by users.
+A set of semantic web services $S$ are chained as a weighted DAG composition model $WG$ when a composition task $Comp.T$ is requested by users.
 The composition problem considered in this paper to automatically generate $WG$, satisfying the follows:
@@
 
+Our comprehensive quality evaluation model is considered to be more general.
+Semantic matchmaking types (Exact and Plugin) are considered for discovering desired web service in QoS-aware web service composition  \cite{ma2015hybrid,da2016particle,da2015graphevol}, but there are no measurements of matchmaking types and concept similarities.
+Consequently, weights for $MT$ and $S$ are considered to be 0 in our propopsed comprehensive evaluation model, it turns to a widely used QoS evaluation model in \cite{ma2015hybrid,da2016particle,da2015graphevol}.
 \section{PSO-based Approach to Comprehensive Quality-Aware Automated Semantic Web Service Composition}\label{qswsc_approach}
@@
 \section{Results and Analysis}\label{results_analysis}
-\subsection{Comparison Test for Comprehensive Quality Evaluation Mode and QoS Evaluation Model}\label{comparisonTest}
-To analyse the differences between optimal solutions evaluated by comprehensive evaluation model and QoS evluation mode, We first look at the $MT$, $S$ and $QoS$
+\subsection{Comparison Test for Comprehensive Quality Evaluation Model and QoS Evaluation Model}\label{comparisonTest}
 
-QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid} do consider two semantic matchmaking types (Exact and Plugin) for discovering desired web service, but there is no measurement of matchmaking types and concept similarity, so the weights for $MT$ and $S$ are considered to be 0.
-Consequently, our evaluation mode become a widely used fitness function \cite{ma2015hybrid,da2016particle}, $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$  for QoS-aware web service composition.
-To compare the composition solution generated by our approach with QoS-aware approach.
-We look at mean value of $MT$, $S$ and $QoS$ at optimum at the 100th generation for two approaches.
-In QoS-aware approach, $MT$ and $S$ are recorded, and $QoS$ is normalised from 0 to 0.5 to make it comparable, besides that, all weights in QoS-aware fitness function are set equally to 0.25.
+A recent widely used QoS Evaluation Model, $QoS = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$, where $\sum_{i=1}^{4} w_i = 1$, is used for QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol}.
+We employ this QoS evluation model and our proposed comprehensive quality evluation model using our proposed PSO-based approach for searching for optimal solutions.
+To analyse the differences in optimal solutions found by these two evaluation model, we recorded and compared the different mean values of $MT$, $S$, $QoS$ at the 100th generation over 30 runs.
+To make a sense of the comparison, all these recorded values are normalised from 0 to 1, and compared using statistical analysis in in Table \ref{decisionTable}.
 
-We observe an interesting pattern from Table \ref{decisionTable} using statistic analysis: mean value of $MT$ and $S$ at optimum by our approach is consistently higher than those by QoS-aware approach.
-Meanwhile, $QoS$ generated by QoS-aware approach can achieve a more desirable tradeoff in both semantic matchmaking quality and QoS.
+We observe an interesting pattern from Table \ref{decisionTable}.
+The mean values of $QoS$ using QoS evaluation model are significantly higher than those using comprehensive quality evaluation model for Task 2, 3, 4 and 5,  but the mean value of $MT$ and $S$ using comprehensive quality evaluation model are consistently significantly higher than those using QoS evluation model for all tasks with a slight trade-off in $QoS$.
 
@@
 \centering
-\caption{Mean Quality for comprehensive quality-aware methods and QoS-aware approach}
+\caption{Mean values of $MT$, $S$, and $QoS$ for QoS Evaluation Model and Comprehensive Quality Evaluation Model using PSO-based approach}
 \label{decisionTable}
@@
 \hline
-\multicolumn{2}{c|}{WSC09}              & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
+\multicolumn{2}{c|}{WSC09}              & QoS Evaluation Model         &\shortstack{Comprehensive \\ Quality Evaluation Model} \\ \hline
 \multirow{3}{*}{Task1}  &$MT$   &0.189787 $\pm$ 0.039278686            &0.221862 $\pm$ 0.009582 $\uparrow$ \\ \cline{2-4} 
@@
 
-To better understand that our evaluation approach could generate solutions having better semantic matchmaking quality with a slight trade-off in $QoS$, we demonstrate an example solution to Task 3.
+To better understand a better semantic matchmaking quality with a slight trade-off in the opitmal solutions using comprehensive quality evaluation model, we demonstrate the optimal solutions using task 3 as an example.
 Fig.
-\ref{comparisontest} $(1)$ and $(2)$ are two weighted DAGs as best solutions found employing QoS-aware approach and Comprehensive quality-aware method respectively.
-Two approaches generate exactly the same service workflow structure while some service vertices and edges denoted in red are different.
-We list the semantic matchmaking quality represented by all edges ($e_1$ to $e4$), overall semantic matchmaking quality and QoS in Fig.
-\ref{comparisontest} $(3)$.
-To demonstrate how different the semantic matchmaking quality is, we analyse $e_4$ that has the smallest $\Delta Q$, which reveals the gain (positive $\Delta Q$) or loss (negative $\Delta Q$) for the listed qualities using our approach.
-The $e_4$ has two different source service vertices ($Ser1640238160$ and $Ser1947554374$) and the same $end$ vertices in two solutions.
-The outputs of two different source service are marked on the related taxonomy in Fig.
-\ref{comparisontest} $(4)$, $Ser1640238160$ and $Ser1947554374$ are service with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to two concepts $Con103314376$ and $Con2037585750$ respectively, and $Inst658772240$ are the required parameter for the $end$ vertice, which is related to concept $Con2113572083$.
-There exist $Inst795998200$ $\in$ $Con103314376$ $\sqsubseteq_{2}$ $Inst658772240$ $\in$ $Con2113572083$ and $Inst582785907$ $\in$ $Con2037585750$ $\sqsubseteq_{3}$ $Inst658772240$ $\in$ $Con2113572083$.
-It is obvious that our approach selects the service providing $Inst795998200$ that are closer to the users' required outputs.
+\ref{comparisontest} $(1)$ and $(2)$ show two weighted DAGs as best solutions found by employing QoS-aware approach and Comprehensive quality-aware method respectively.
+Two approaches generate exactly the same service workflow structure, but some service vertices and edges denoted in red are different.
+To better understand these differences, we list the overall semantic matchmaking quality $SM$,  overall $QoS$ and semantic matchmaking quality associated to each edge ($sm_{e_1}$ to $sm_{e_4}$) for the two weighted DAGs in Fig.
+\ref{comparisontest} $(3)$, where $\Delta Q$ reveals the gain (positive $\Delta Q$) or loss (negative $\Delta Q$) for the listed qualities using our comprehensive quality evalutaion model.
+Therefore, an overall gain 0.1433 is calculated from a sum of $SM$ gain (0.1467) and $QoS$ loss (-0.0034).
+Consequently, our comprehensive evaluation model acheive a desirable trade-off in considering both semantic matchmaking and QoS.
+To demonstrate the value of semantic matchmking gain, we pick up $e_4$ associated with a smallest $\Delta Q$, where edeges $e_4$ to $WG(1)$ using QoS evaluation model and $WG(2)$ using comprehensive quality model have two different source service vertices $Ser1640238160$ and $Ser1947554374$ respectively,  and the same $end$ vertices.
+$Ser1640238160$ and $Ser1947554374$ are services with concept-related output parameters $Inst795998200$ and $Inst582785907$ corresponds to two concepts $Con103314376$ and $Con2037585750$ respectively marked on the related taxonomy in Fig.
+\ref{comparisontest} $(4)$.
+These two services $Ser1640238160$ and $Ser1947554374$ are associated with concept-related output parameters $Inst795998200$ and $Inst582785907$, and these parameters  are corresponds to two concepts $Con103314376$ and $Con2037585750$ respectively marked on the related taxonomy in Fig.
+\ref{comparisontest} $(4)$.
+In addtion, $Inst658772240$ are the required parameter for the $end$ vertice, which is related to concept $Con2113572083$.
+There exist $Inst582785907$ $\in$ $Con2037585750$ $\sqsubseteq_{3}$ $Inst658772240$ $\in$ $Con2113572083$ for $e_4$ in $WG(1)$ and $Inst795998200$ $\in$ $Con103314376$ $\sqsubseteq_{2}$ $Inst658772240$ $\in$ $Con2113572083$ for $e_4$ in $WG(2)$.
+Therefore, 2-levels Subsumes is closer 3-level Subsumes, $Inst795998200$ is closer to user's required outputs $Inst658772240$ compared with $Inst582785907$.
+
 \begin{figure}[h]
@@
 To evaluate the performance of our proposed PSO-based approach, we compare one GP-based approach  \cite{ma2015hybrid} with our PSO method.
-We consider the links between child nodes and parent nodes as semantic web service links for measuring  semantic matchmaking quality, and those links information are maintained correctly for the crossover and mutation.
+we consider the links between child nodes and parent nodes as semantic web service links for measuring  semantic matchmaking quality, and those links information are maintained correctly for the crossover and mutation.
 Therefore, we evaluate both semantic matchmaking quality and QoS simultaneously using the proposed comprehensive quality model.

### 2017-03-23 paper.tex
update

@@
 We observe an interesting pattern from Table \ref{decisionTable}.
-The mean values of $QoS$ using QoS evaluation model are significantly higher than those using comprehensive quality evaluation model for Task 2, 3, 4 and 5,  but the mean value of $MT$ and $S$ using comprehensive quality evaluation model are consistently significantly higher than those using QoS evluation model for all tasks with a slight trade-off in $QoS$.
+The mean values of $QoS$ using QoS evaluation model are significantly higher than those using comprehensive quality evaluation model for Task 2, 3, 4 and 5,  but the mean value of $MT$ and $S$ using comprehensive quality evaluation model are consistently significantly higher than those using QoS evaluation model for all tasks with a slight trade-off in $QoS$.
 
@@
 \centering
-\caption{Mean values of $MT$, $S$, and $QoS$ for QoS Evaluation Model and Comprehensive Quality Evaluation Model using PSO-based approach}
+\caption{Mean values of $SM$ and $QoS$ for QoS Evaluation Model and Comprehensive Quality Evaluation Model using PSO-based approach}
 \label{decisionTable}
@@
 \multicolumn{2}{c|}{WSC09}              & QoS Evaluation Model         &\shortstack{Comprehensive \\ Quality Evaluation Model} \\ \hline
-\multirow{3}{*}{Task1}  &$MT$   &0.189787 $\pm$ 0.039278686            &0.221862 $\pm$ 0.009582 $\uparrow$ \\ \cline{2-4} 
-                        &$S$    &0.884962 $\pm$ 0.014140               &0.894082 $\pm$ 0.009206 $\uparrow$ \\ \cline{2-4}
-                        &$QoS$  &0.278730 $\pm$ 0.007786               &0.280222 $\pm$ 0.008212                          \\ \hline
-\multirow{3}{*}{Task2}  &$MT$   &0.001795 $\pm$ 0.000719               &0.001977 $\pm$ 0.001566 $\uparrow$ \\ \cline{2-4} 
-                        &$S$    &0.906971 $\pm$ 0.005855               &0.923970 $\pm$ 0.006898 $\uparrow$   \\ \cline{2-4}
-                        &$QoS$  &0.239979 $\pm$ 0.000578 $\uparrow$    &0.238596 $\pm$ 0.001264 \\ \hline
-\multirow{3}{*}{Task3}  &$MT$   &0.158526 $\pm$ 0.014028               &0.245830 $\pm$ 0.007761 $\uparrow$   \\ \cline{2-4} 
-                        &$S$    &0.949109 $\pm$ 0.002331               &0.972765 $\pm$ 0.002980 $\uparrow$           \\ \cline{2-4}
-                        &$QoS$  &0.247002 $\pm$ 0.000661 $\uparrow$    &0.245631 $\pm$ 0.000431            \\ \hline
-\multirow{3}{*}{Task4}  &$MT$   &0.000000 $\pm$ 0.000000               &0.000004 $\pm$ 0.000002 $\uparrow$ \\ \cline{2-4} 
-                        &$S$    &0.879514 $\pm$ 0.007456               &0.920733 $\pm$ 0.000001 $\uparrow$ \\ \cline{2-4}
-                        &$QoS$  &0.242297 $\pm$ 0.000507 $\uparrow$    &0.236677 $\pm$ 0.002211  \\ \hline
-\multirow{3}{*}{Task5}  &$MT$   &  0.000042 $\pm$ 0.000030             &0.000078 $\pm$ 0.000020 $\uparrow$           \\ \cline{2-4} 
-                        &$S$    &  0.915933 $\pm$ 0.012888             &0.927678 $\pm$ 0.002578 $\uparrow$                 \\ \cline{2-4}
-                        &$QoS$  & 0.238189 $\pm$ 0.000240 $\uparrow$      &  0.237485 $\pm$  0.000328  \\ \hline                                                   
+\multirow{2}{*}{Task1}  &$SM$   &0.537375 $\pm$ 0.026709               &0.557972 $\pm$ 0.009394 $\uparrow$ \\ \cline{2-4}
+                        &$QoS$  &0.557460 $\pm$ 0.015572               &0.560444 $\pm$ 0.016424                          \\ \hline
+\multirow{2}{*}{Task2}  &$SM$   &0.454383 $\pm$ 0.003287               &0.462974 $\pm$ 0.004232 $\uparrow$ \\ \cline{2-4} 
+                        &$QoS$  &0.479958 $\pm$ 0.001156 $\uparrow$    &0.477192 $\pm$ 0.002528 \\ \hline
+\multirow{2}{*}{Task3}  &$SM$   &0.553818 $\pm$ 0.008180               &0.609298 $\pm$ 0.005371 $\uparrow$   \\ \cline{2-4} 
+                        &$QoS$  &0.494004 $\pm$ 0.001322 $\uparrow$    &0.491262 $\pm$ 0.000862            \\ \hline
+\multirow{3}{*}{Task4}  &$SM$   &0.439757 $\pm$ 0.003728               &0.460369 $\pm$ 0.000002 $\uparrow$ \\ \cline{2-4} 
+                        &$QoS$  &0.484594 $\pm$ 0.001014 $\uparrow$    &0.473354 $\pm$ 0.004422  \\ \hline
+\multirow{3}{*}{Task5}  &$SM$   &0.457988 $\pm$ 0.006459               &0.463878 $\pm$ 0.001299 $\uparrow$           \\ \cline{2-4} 
+                        &$QoS$  &0.476378 $\pm$ 0.000480 $\uparrow$    &0.474970 $\pm$ 0.000656  \\ \hline                                                   
 \end{tabular}
@@
 \fbox{
-\includegraphics[scale=.22]{comparisontest.pdf}}}
+\includegraphics[scale=.29]{comparisontest.pdf}}}
  \caption{Example Comparison of solutions to Task 3 using two different evaluation model.}

### 2017-03-23 paper.tex
update

@@
 
-A recent widely used QoS Evaluation Model, $QoS = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$, where $\sum_{i=1}^{4} w_i = 1$, is used for QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol}.
+A recent widely used QoS Evaluation Model, $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$, where $\sum_{i=1}^{4} w_i = 1$, is used for QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol}.
 We employ this QoS evluation model and our proposed comprehensive quality evluation model using our proposed PSO-based approach for searching for optimal solutions.
-To analyse the differences in optimal solutions found by these two evaluation model, we recorded and compared the different mean values of $MT$, $S$, $QoS$ at the 100th generation over 30 runs.
+To analyse the differences in optimal solutions found by these two evaluation model, we recorded and compared the different mean values of $SM$ (consisiting of $MT$ and $S$), $QoS$(consisting of $A$, $R$, $T$ and $C$) at the 100th generation of 30 runs.
 To make a sense of the comparison, all these recorded values are normalised from 0 to 1, and compared using statistical analysis in in Table \ref{decisionTable}.
@@
 We observe an interesting pattern from Table \ref{decisionTable}.
-The mean values of $QoS$ using QoS evaluation model are significantly higher than those using comprehensive quality evaluation model for Task 2, 3, 4 and 5,  but the mean value of $MT$ and $S$ using comprehensive quality evaluation model are consistently significantly higher than those using QoS evaluation model for all tasks with a slight trade-off in $QoS$.
+The mean values of $QoS$ using QoS evaluation model are significantly higher than those using comprehensive quality evaluation model for Task 2, 3, 4 and 5,  but the mean value of $SM$ using comprehensive quality evaluation model are consistently significantly higher than those using QoS evaluation model for all tasks with a slight trade-off in $QoS$.
 
@@
 \centering
-\caption{Mean values of $SM$ and $QoS$ for QoS Evaluation Model and Comprehensive Quality Evaluation Model using PSO-based approach}
+\caption{Mean values of $SM$ and $QoS$ for QoS evaluation model and comprehensive quality evaluation model using PSO-based approach}
 \label{decisionTable}
@@
 Fig.
-\ref{comparisontest} $(1)$ and $(2)$ show two weighted DAGs as best solutions found by employing QoS-aware approach and Comprehensive quality-aware method respectively.
+\ref{comparisontest} $(1)$ and $(2)$ show two weighted DAGs as best solutions found by employing QoS evaluation model and comprehensive quality evaluation model respectively.
 Two approaches generate exactly the same service workflow structure, but some service vertices and edges denoted in red are different.
 To better understand these differences, we list the overall semantic matchmaking quality $SM$,  overall $QoS$ and semantic matchmaking quality associated to each edge ($sm_{e_1}$ to $sm_{e_4}$) for the two weighted DAGs in Fig.
-\ref{comparisontest} $(3)$, where $\Delta Q$ reveals the gain (positive $\Delta Q$) or loss (negative $\Delta Q$) for the listed qualities using our comprehensive quality evalutaion model.
-Therefore, an overall gain 0.1433 is calculated from a sum of $SM$ gain (0.1467) and $QoS$ loss (-0.0034).
-Consequently, our comprehensive evaluation model acheive a desirable trade-off in considering both semantic matchmaking and QoS.
-To demonstrate the value of semantic matchmking gain, we pick up $e_4$ associated with a smallest $\Delta Q$, where edeges $e_4$ to $WG(1)$ using QoS evaluation model and $WG(2)$ using comprehensive quality model have two different source service vertices $Ser1640238160$ and $Ser1947554374$ respectively,  and the same $end$ vertices.
-$Ser1640238160$ and $Ser1947554374$ are services with concept-related output parameters $Inst795998200$ and $Inst582785907$ corresponds to two concepts $Con103314376$ and $Con2037585750$ respectively marked on the related taxonomy in Fig.
+\ref{comparisontest} $(3)$, where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) for the listed qualities using our comprehensive quality evalutaion model.
+Therefore, an overall gain 0.1433 is calculated from a sum of a $SM$ gain (0.1467) and $QoS$ loss (-0.0034).
+Consequently, our comprehensive evaluation model acheive a desirable trade-off in considering both $SM$ and $QoS$.
+To explain the value of $SM$ gain, we pick up $e_4$ that is associated with a smallest $\Delta Q$.
+The $e_4$ of $WG(1)$ using QoS evaluation model and $WG(2)$ using comprehensive quality model has two different source service vertices $Ser1640238160$ and $Ser947554374$ respectively,  and the same $end$ vertices.
+$Ser1640238160$ and $Ser947554374$ are services with concept-related output parameters $Inst795998200$ and $Inst582785907$ corresponds to two concepts $Con103314376$ and $Con2037585750$ respectively, which are marked on the related taxonomy in Fig.
 \ref{comparisontest} $(4)$.
-These two services $Ser1640238160$ and $Ser1947554374$ are associated with concept-related output parameters $Inst795998200$ and $Inst582785907$, and these parameters  are corresponds to two concepts $Con103314376$ and $Con2037585750$ respectively marked on the related taxonomy in Fig.
-\ref{comparisontest} $(4)$.
-In addtion, $Inst658772240$ are the required parameter for the $end$ vertice, which is related to concept $Con2113572083$.
+In addtion, $Inst658772240$ is a required parameter of the $end$ vertice as one of composition task outputs, which is related to concept $Con2113572083$.
 There exist $Inst582785907$ $\in$ $Con2037585750$ $\sqsubseteq_{3}$ $Inst658772240$ $\in$ $Con2113572083$ for $e_4$ in $WG(1)$ and $Inst795998200$ $\in$ $Con103314376$ $\sqsubseteq_{2}$ $Inst658772240$ $\in$ $Con2113572083$ for $e_4$ in $WG(2)$.
-Therefore, 2-levels Subsumes is closer 3-level Subsumes, $Inst795998200$ is closer to user's required outputs $Inst658772240$ compared with $Inst582785907$.
+Therefore, 2-level Subsumes is closer than 3-level Subsumes, $Inst795998200$ is closer to user's required output $Inst658772240$ compared with $Inst582785907$.
 
@@
 \includegraphics[scale=.29]{comparisontest.pdf}}}
- \caption{Example Comparison of solutions to Task 3 using two different evaluation model.}
+ \caption{An example of comparision to optimal solutions using Task 3 for QoS evaluation model and comprehensive evluation model.}
  \label{comparisontest}
@@
 \subsection{Comparison Test with GP-based approach}\label{comparisonTestWithGP}
-To evaluate the performance of our proposed PSO-based approach, we compare one GP-based approach  \cite{ma2015hybrid} with our PSO method.
-we consider the links between child nodes and parent nodes as semantic web service links for measuring  semantic matchmaking quality, and those links information are maintained correctly for the crossover and mutation.
-Therefore, we evaluate both semantic matchmaking quality and QoS simultaneously using the proposed comprehensive quality model.
-To make a fair comparison with our PSO-based, we consider the same number of evaluations (3000 times) as that in our PSO-based approach, we set the parameters settings for GP-based approach \cite{ma2015hybrid} using 30 individuals and 100 generations.
+To evaluate the performance of our proposed PSO-based approach, we compare one GP-based approach  \cite{ma2015hybrid} with our PSO-based method.
+we consider the links between child nodes and parent nodes as semantic web service links for measuring  semantic matchmaking quality.
+Therefore, we evaluate both semantic matchmaking quality and QoS simultaneously using our proposed comprehensive quality model.
+To make a fair comparison with our PSO-based, we consider the same number of evaluations (3000 times) used in our PSO-based approach, we set the parameters settings for the GP-based approach using 30 individuals and 100 generations.
 
-The Table \ref{meanFitness} shows the mean fitness values accomplished by two methods.
+The Table \ref{meanFitness} shows the mean fitness values of 30 independent runs accomplished by two methods.
 We employ statistical analysis to test the significant differences in mean fitness value.
@@
 
-At last, We also compare the average fitness value with optimum through the evolutionary process for both two approaches over 30 independent runs.
-Fig.
-\ref{psovsgp} is an example of convergence rate for Task 3, where the behaviour of PSO-based approach presents a very clear evidence of fast convergence and reaches a better-optimised solution, while the performance of GP is barely satisfactory, as GP-based method improves its fitness value gradually.
-
-\begin{figure}[h]
-\centering
-\fbox{\includegraphics[scale=.25]{psovsgp.pdf}}
- \caption{An example of comparing convergency rate of PSO and GP approaches for task 3}
- \label{psovsgp}
-\end{figure}
-
 \section{Conclusion}\label{conclusion}
-This work introduces a general comprehensive evaluation model for considering semantic matchmaking quality and QoS.
-We proposed a PSO-based service composition approach utilising our proposed quality mode that can achieve a desired balance of both quality aspects.
-Also, we compare one GP-approach with our PSO-based method to show our performance results in finding more optimised solution.
+This work introduces a general comprehensive evaluation model for considering semantic matchmaking quality and QoS simultaneously.
+We proposed a PSO-based service composition approach utilising our proposed quality mode that can achieve a desired trade-off of both quality aspects.
+In addtion, we compare one recent GP-approach with our PSO-based method to show our performance that results in finding more optimised solutions.
 Future works can investigate multi-objective EC techniques to produce a set of composition solutions for the situations when the quality preference is not known.

### 2017-03-23 paper.tex
update

@@
 
-\subsection{Comparison Test with GP-based approach}\label{comparisonTestWithGP}
+\subsection{Comparison Test for GP-based approach and PSO-based approach}\label{comparisonTestWithGP}
 To evaluate the performance of our proposed PSO-based approach, we compare one GP-based approach  \cite{ma2015hybrid} with our PSO-based method.

### 2017-03-24 paper.tex
update

@@
 There are two major challenges faced by researchers, semantic matchmaking and Quality of Service (QoS) optimisation.
-Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning.
+Semantic matchmaking aims to discover interoperable web services that can interact with each other by their resources described semantically.
 QoS optimisation aims to optimise the non-functional requirements of service users, e.g., minimum cost, maximal reliability.
@@
 To meet users' requirements, one often needs to consider both semantic matchmaking quality and QoS simultaneously.
-Existing works on web service composition often concern either semantic web  service composition or QoS-aware web service composition.
-Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS simultaneously that can achieve a more desirable trade-off in consideration of both sides.
-Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model.
-We compare this model with a promising QoS-aware model, and also compare our PSO-based method with one recent GP-based method to show its performance in finding a more optimised solution.
+Existing works on web service composition focus mainly on one single type of requirements.
+Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS simultaneously with an aim of achieving a more desirable trade-off in consideration of both sides.
+Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model, where PSO optimse a queue of task related services that is decoded into composition solutions.
+We compare proposed comprehensive quality model with one promising QoS model, and also compare the effectiveness of PSO-based method with one recent GP-based method using comprehensive quality model.
 
@@
 
-\textit{Web service composition} pertains to a combination of multiple web services to provide a value-added composition service that accommodates customers' arbitrarily complex requirements.
+\textit{Web service composition} pertains to a chain of multiple web services to provide a value-added composition service that accommodates customers' arbitrarily complex requirements.
 This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems.
 Due to the increasing number of large-scale enterprise applications, the number of Web services has increased substantially and unprecedentedly.
-Therefore, manual and semi-automated web service compositions are considered to be less efficient while automated web service composition has less human intervention, less time consumption, and high productivity.
+Therefore, \textit{manual and semi-automated web service compositions} are considered to be less efficient while \textit{automated web service composition} demands less human intervention, less time consumption, and high productivity.
 
@@
 The syntactic dimension is covered by the XML-based technologies (such as $WSDL$, $SOAP$).
-The semantic aspect, on the other hand, demands further research.
-Through ontology-based semantics \cite{o2005review}, web services can understand and better collaborate with each other.
-There are many ontology languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}, which make ``machine understanding'' possible through identifying and matching semantic similarities in input/output parameters of web services in heterogeneous environments.
-The second challenge $(2)$ is related to finding \textit{optimised solutions} to QoS.
-This problem gives birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements (SLA) \cite {sahai2002automated} involving a collection of SLA rules and policies for supporting QoS-based composition.
+The semantic dimension enables a better underrstanding and collaboration through ontology-based semantics \cite{o2005review}.
+There are many ontology languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}, which make ``machine understanding'' possible through identifying and matching semantic similarities in input/output parameters of web services.
+The second challenge is related to finding optimised solutions in QoS.
+This problem gives birth to \textit{QoS-aware service composition} that aims to find composition solutions associated with a single optimised QoS value.
 
-Existing works on service composition focus mainly on addressing one of challenges above.
-Many works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as a \textit{semi-automated Web service composition} approach \cite{bahadori2009optimal,parejo2008qos}.
-Meanwhile, many research works consider the possibility of generating a composition plan automatically in discovering and selecting suitable web services, which are considered to be NP-hard \cite{moghaddam2014service}.
-\textit{Semantic web services composition} is distinguished from the syntactic service composition, which supplements well defined semantic descriptions from the concept of ontologies, instead of parameters value.
+Existing works on service composition focus mainly on addressing only one challenge above.
+Among these works, huge efforts have been devoted to optimise the quality of compositions under a pre-defined abstract workflow.
+This is generally considered as a \textit{semi-automated Web service composition} approach \cite{bahadori2009optimal,parejo2008qos}.
+Meanwhile, many research works consider the NP-hard problem of generating a composition plan automatically in discovering and selecting suitable web services \cite{moghaddam2014service}.
+\textit{Semantic web services composition} is distinguished from the syntactic service composition, the resources of semantic web services are described semantically to enable a better interoperability for chaining web services.
 In the past few years, substantial works have been done on semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated}.
-However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously and achieved a desired balance.
+However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously to achieve a desired balance.
 
 The overall goal of this paper is to \textit{develop a general comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}.
-Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matchmaking quality optimisation in our proposed comprehensive quality model.
+Particularly, this paper extends existing works of QoS-aware service composition by considering jointly optimise QoS and semantic matchmaking quality based on our proposed comprehensive quality model.
 Particle Swarm Optimisation (PSO) has shown its promise in searching for near-optimised service composition solutions \cite{da2016particle}.
@@
 \begin{enumerate}
- \item To propose a general comprehensive quality model that addresses QoS and semantic matchmaking quality in considering different matching types with corresponding concept similarities.
+ \item To propose a general comprehensive quality model that addresses QoS and semantic matchmaking quality simultaneously to achieve a desirable balance on both sides.
 
- \item To propose a PSO-based service composition algorithm that utilises the proposed quality model.
-To do that we will first propose a representation of semantic service composition, which can model the quality of semantic matchmaking and QoS together.
+ \item To propose a PSO-based service composition approach that utilises the proposed comprehensive quality model.
+To do that we optimise a queue of web services by evaluating its decoded representations.
+These representations are the solutions for semantic web service composition.
 
- \item To evaluate our proposed approach, we conduct experiments to compare our comprehensive quality model with one widely used QoS evaluation model.
-We also compare one recent GP approach \cite{ma2015hybrid} with our PSO-based approach using our proposed model.
+ \item To address a desirable balance that can be achieved using our comprehensive quality model, we conduct experiments to compare our propopsed model with one widely used QoS model using PSO-based approach.
+In addtion, to evaluate the effectiveness of our PSO-based approach,  we also compare one recent GP approach \cite{ma2015hybrid} with our PSO-based approach using our proposed model.
 Both comparisons utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}
@@
 \section{Related Work} \label{relatedWork}
-Substantial works on web service composition focus on either semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive}, However, few researchers address both semantic matchmaking quality and QoS requirements for web service composition problems.
+Substantial works on web service composition focus on either semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive}, However, only a few researchers address both semantic matchmaking quality and QoS requirements for web service composition problems.
 To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some attempts on service composition that considers both aspects.
 
-Semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} captures the semantic description of web services' parameters using some kind of logic (e.g., description logic) for enabling the interoperability of web services, where the number of web services or length of a graph is minimised to reach the optimised graph-based composition solutions.
-However, this evaluation approach does not guarantee optimised qualities of composition solutions for QoS.
+Semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} captures the semantic description of web services' parameters using some kind of logic (e.g., description logic) that ensuring the interoperability of web services, where the number of web services or length of a graph representation for web service composition is minimised to reach the optimised composition solutions.
+However, this evaluation approach does not guarantee optimised QoS of composition solutions.
 
-QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques.
+QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques for finding near-optimised solutions.
 Qi et al.
 \cite{qi2010combining} propose a heuristic service composition method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal QoS.
-but there exists a scalability problem for the enumeration technique.
-EC tecQoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid}hniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problem.
+However, there exists a scalability problem for the enumeration technique.
+EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problem.
 Gupta et al.

### 2017-03-24 paper.tex
update

@@
 Qi et al.
-\cite{qi2010combining} propose a heuristic service composition method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal QoS.
+\cite{qi2010combining} propose a heuristic service composition method, named LOEM (Local Optimization and Enumeration Method), where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal QoS.
 However, there exists a scalability problem for the enumeration technique.
@@
 Gupta et al.
-\cite{gupta2015optimization} employ an Genetic Algorithm using a set of binary strings as individuals, which demands to be decoded into composition solutions.
+\cite{gupta2015optimization} employ a modified Genetic Algorithm (GA) using a binary string as an individual, which demands to be decoded into composition solutions.
 Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function.
-A hybird approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions with functional correctness.
-In particularly, a greedy search is used to generate  directed acyclic graphs (DAGs) as composition solutions that is further transferred to tree structures for initialisation and mutation.
-To eliminating the transformation process from DAGs, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation.
+A hybird approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions that are functionally correct.
+In particularly, greedy search techniques have been used to generate directed acyclic graphs (DAGs) as composition solutions that is further transferred to tree structures for initialisation and mutation.
+To eliminating the transformation process from DAGs, a promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation.
 An indirect PSO-based approach was introduced in \cite{da2016particle}.
 An optimised queue is used as an indirect representation that is decoded into a DAG-based solution.
-These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality, which could lead to too specific outputs produced by the selected services, The finding is supported by our first comparison experiment.
+These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality, which could lead to too specific outputs produced by the selected services, and this finding is supported by our first comparison experiment.
 
-Few works \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} employ EC technique for considering both semantic matchmaking quality and QoS simultaneously.
+Only a few works \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} consider both semantic matchmaking quality and QoS simultaneously.
 Lecue et al.
-\cite{lecue2009optimizing} employ Genetic Algorithm for semi-automated web service composition considering semantic matchmaking quality and QoS, where the semantic matchmaking quality is measured through evaluating semantic links, which requires a formal definition of ontology in Description Logic.
-This evaluation method takes huge cost and time for the domain experts to establish required ontology.
-Another GA-based approach work \cite{fanjiang2014semantic} employs a sequence of fitness functions are used in the binary selection of chromosomes, where semantic matchmaking quality is evaluate in two fitness functions considering concept similarity and parameter similarity respectively, but different semantic matchmaking types are ignored in the evaluation model.
+\cite{lecue2009optimizing} employ GA for semi-automated web service composition considering semantic matchmaking quality and QoS, where the semantic matchmaking quality is measured through evaluating semantic links, which requires a formal definition of ontology in Description Logic.
+This evaluation model takes huge cost and time for the domain experts to establish required ontology.
+Another GA-based approach work \cite{fanjiang2014semantic} employs a sequence of fitness functions are used in the binary selection of chromosomes, where semantic matchmaking quality is evaluate in two fitness functions considering concept similarity and parameter similarity respectively, but .
 The work \cite{pop2009immune} as an immune-inspired web service composition approach employ indirect representation that a binary alphabet to encode a planning graph, where the semantic matchmaking quality is measured by the similarity using information retrieval technique.

### 2017-03-25 paper.tex
up

@@
 Lecue et al.
-\cite{lecue2009optimizing} employ GA for semi-automated web service composition considering semantic matchmaking quality and QoS, where the semantic matchmaking quality is measured through evaluating semantic links, which requires a formal definition of ontology in Description Logic.
+\cite{lecue2009optimizing} propose a semi-automated web service composition using GA to encode a given abstract service workflow, where the semantic matchmaking quality is measured through evaluating the quality of semantic links that require a formal definition of ontology in Description Logic.
 This evaluation model takes huge cost and time for the domain experts to establish required ontology.
-Another GA-based approach work \cite{fanjiang2014semantic} employs a sequence of fitness functions are used in the binary selection of chromosomes, where semantic matchmaking quality is evaluate in two fitness functions considering concept similarity and parameter similarity respectively, but .
-The work \cite{pop2009immune} as an immune-inspired web service composition approach employ indirect representation that a binary alphabet to encode a planning graph, where the semantic matchmaking quality is measured by the similarity using information retrieval technique.
+Another GA-based approach \cite{fanjiang2014semantic} utilise process description language to encode pre-stored cases-based workflows, where workable services are composed to complete this workflow.
+The work \cite{pop2009immune} is an automated immune-inspired web service composition approach, where an indirect representation that a binary alphabet is used to encode a planning graph.
+However, this composition method is only evaluated on a set of scenarios.
 
-In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches.
-There is a lack of a general approaches that achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS.
-Therefore, we proposed a general comprehensive quality model to fill the gaps, and then we proposed a PSO-based method with explicit support for the comprehensive model to find optimal compositions.
+In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches, there is a lack of a fully automated semantic web service composition approach to optimse semantic matchmaking quality and QoS simultaneously.
+Therefore, we first propose a general comprehensive quality model that aims to achieve a better semantic matchmaking quality with a slight trade-off in QoS, and then we propose an automated PSO-based approach with explicit support for the comprehensive model to find optimal service compositions.
 
@@
 
-The aim of web service composition considered in this paper is to automatically select the optimal solutions in considering both QoS and semantic matchmaking quality by a user's request.
-The request is to provide inputs and obtain outputs, the composition results that should meet the optimal requirements above.
+The aim of web service composition considered in this paper is to automatically compose optimal solutions in considering both QoS and semantic matchmaking quality based on a user's request.
+The request is to provide inputs and obtain outputs.
+The resulting composition of this request is a composition solution with an optimal comprehensive quality in terms of semantic matchmaking quality and QoS.
 A motivating example of this problem is shown in Fig \ref{motivation}.
-The figure is a DAG represent a solution with four web services involved for a request $R$ as a composition task, where inputs of the task are \{TravelDepartureDate, HomeCity, ConferenceCity, TravelReturnDate \} and outputs are \{BusTicket, FlightTicket, TouristMap, HotelReservation \}.
-This is a classic example of travel planning problem for scholars who seek for booking services of airplanes, buses and hotels reservation, and also generating tourist maps for the conference city.
-The graph also contains edges that marked with connecting outputs and inputs, which represent valid semantic matches where the outputs of a web service can be passed as the inputs of its successors.
+The figure shows a DAG that represents a solution with four web services involved for a request $R$ as a composition task, where inputs of the task are \{TravelDepartureDate, HomeCity, ConferenceCity, TravelReturnDate \} and outputs are \{BusTicket, FlightTicket, TouristMap, HotelReservation \}.
+This is a classic example of travel planning problem for people who seek for booking services of airplanes, buses and hotels reservation, and also generating tourist maps for the conference city.
+The graph also contains edges that marked with connected outputs and inputs of two connected atomic services, which represent valid semantic matches that the outputs of a web service can be passed as the inputs of its successors.
 
@@
  \label{motivation}
-\end{figure}QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid}
+\end{figure}
 
-Although obtaining a correct combination of web service is essential, there are many ways to chain web services to reach users' needs with different web services from a service repository.
-These web services have different QoS in terms of different availability, price, reliability and response time.
-Moreover, valid semantic matches between two web services could also have different matchmaking quality.
-For example, Generate Map service produce StreetMap which is considered to be a valid semantic match to TouristMap from users' perspectives.
-These perspectives are captured in a taxonomy Fig .\ref{taxonomy}, where all the inputs and the outputs related to the web services are described for a travel planning domain.
-For example, the concept Map and its sub-concept urbanMap are assigned with a touristMap instance and streetMap instance respectively in Fig .\ref{taxonomy}.
-The valid semantic match is considered that an instance of urban Map can be an instance of Map, but not vice versa.
-However, if a web service $GenerateTouristMap$ is found in the service repository that produces TouristMap as an output, but price is "16.87".
-I consider its semantic matchmaking quality is higher than the service $GenerateMap$, but price negatively contributes to the overall QoS.
-Therefore, automatically generating solutions in considering both QoS and matchmaking quality is a very challenging problem.
+Although obtaining a correct combination of web service is essential, there are many ways to connect multiple web services chosen from a service repository.
+These web services provide different QoS in terms of availability, price, reliability and response time.
+Moreover, valid semantic matches between two connected web services could also have different matchmaking quality.
+For example, $Generate Map$ service produce $StreetMap$ which is considered to be a valid semantic match to $TouristMap$, while $Bus Service$ produce $BusTicket$ which is considered to be a better valid semantic match to $BusTicket$.
+The descriptions of these matched resources are captured in a taxonomy depicted in Fig .\ref{taxonomy}, where all the inputs and the outputs related to the web services are described for a travel planning problem.
+For example, the concept $Map$ and its sub-concept $urbanMap$ are assigned with a $touristMap$ instance and $streetMap$ instance respectively in Fig .\ref{taxonomy}.
+The valid semantic match is considered that an instance of $urban Map$ can be an instance of $Map$, but not vice versa.
+To demonstrate the motivation of proposing a comprehensive quality, we give a simple example.
+The service $GenerateMap$ with a output ($StreetMap$) and a price (``6.72") in the web service composition can be replace by a service $GenerateTouristMap$ with a different output ($TouristMap$) and a different price (``16.87") availabile in the service repository.
+This composition solution results in a better semantic matchmaking quality, but price negatively contributes to the QoS.
+Therefore, we need to measure these changes to the solutions considering matchmaking quality and QoS simultaneously for automatically generated solutions.
 
@@
 
-We herein give formal definitions of the assumptions the concepts regarding the semantic web service composition problem utilised in our approach that consists of four main concepts: a semantic web service model, a semantic matchmaking model, a weighted DAG composition model, and QoS calculation model, and composition problem model.
-\vspace{0.3cm}
+We herein give formal definitions of the concepts regarding the semantic web service composition problem utilised in our approach, and these concepts are captured in serveral models: a semantic web service model, a semantic matchmaking model, a weighted DAG composition model, and QoS calculation model, and composition problem model.
 
@@
 
-\textbf{Definition 1.} A request from users is defined as a composition task in a tuple: $Comp.T = \{I_{T}, O_{T}\}$ by giving a set of task inputs $I_{T}$ and expecting  a set of desired task outputs $O_{T}$, where $I_{T}$ and $O_{T}$ are associated with related concepts $I^{C}_{T}$ and $O^{C}_{T}$ respectively in an ontology $O = \{(C, Taxonomy) \mid I^{C}_{T}, O^{C}_{T}  \subseteq C \}$.
+\textbf{Definition 1.} A request from users is defined as a composition task in a tuple: $Comp.T = \{I_{T}, O_{T}\}$ by giving a set of task inputs $I_{T}$ and expecting  a set of desired task outputs $O_{T}$, where $I_{T}$ and $O_{T}$ are associated with related concepts $I^{C}_{T}$ and $O^{C}_{T}$ respectively in an ontology $O = \{ C \mid I^{C}_{T}, O^{C}_{T}  \subseteq C \}$.
 
@@
 $QoS_S = \{ t_s, c_s, r_s, a_s, ...
-\} $ is a set of non-functional attributes of $S$, it typically refers to response time $t_s$, cost $c_s$, reliability $r_s$, and availability $a_s$ \cite{zeng2003quality}.
-$\mathcal{SR}$ is a service repository consisting of a set of $S$, where all the $S$ are registered.
+\} $ is a set of non-functional attributes of $S$, it refers to response time $t_s$, cost $c_s$, reliability $r_s$, and availability $a_s$ \cite{zeng2003quality}.
+$\mathcal{SR}$ is a service repository consisting of a set of $S$.
 \vspace{0.3cm}
@@
 \textbf{Semantic Matchmaking Model}.
-The mechanism to compose web services relays on the semantic descriptions of inputs and outputs, which enable inputs of a service to be matched by outputs of another.
-To measure the quality of these matches, we utilise different matchmaking types (\textit{exact, plugin subsumes and fail} \cite{paolucci2002semantic} ) into consideration for exploiting the semantics of inputs and outputs.
+The mechanism to compose web services relies on the semantic descriptions of inputs and outputs, which enable inputs of a service to be matched by outputs of another.
+To measure the quality of these matches, we utilise different matchmaking types (\textit{exact, plugin subsumes and fail} \cite{paolucci2002semantic} ).
 
-\textbf{Definition 3.} Given $a, b \in C$, $type(a, b)$ returns the matchmaking types of two concepts, and this matchmaking type is determined by the logic described in the $O$.
+\textbf{Definition 3.} Given $a, b \in C$, $type(a, b)$ returns the matchmaking types of two concepts, and this matchmaking type is determined by the logic relationship described in the $O$.
 If both $a$ and $b$ are equivalent, $exact$ type ($a \equiv b$) is returned.
@@
 
-We use the $type(a, b)$ to define full matchmaking between two concept-related input and output of two services.
+We use the returns of $type(a, b)$ to define a full matchmaking considerd in the scenario of connecting two services through concept-related output and concept-related input.
 

### 2017-03-26 paper.tex
update

@@
 Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS simultaneously with an aim of achieving a more desirable trade-off in consideration of both sides.
-Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model, where PSO optimse a queue of task related services that is decoded into composition solutions.
+Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model, where PSO optimise a queue of task related services that is decoded into composition solutions.
 We compare proposed comprehensive quality model with one promising QoS model, and also compare the effectiveness of PSO-based method with one recent GP-based method using comprehensive quality model.
@@
 The syntactic dimension is covered by the XML-based technologies (such as $WSDL$, $SOAP$).
-The semantic dimension enables a better underrstanding and collaboration through ontology-based semantics \cite{o2005review}.
+The semantic dimension enables a better understanding and collaboration through ontology-based semantics \cite{o2005review}.
 There are many ontology languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}, which make ``machine understanding'' possible through identifying and matching semantic similarities in input/output parameters of web services.
@@
 
- \item To address a desirable balance that can be achieved using our comprehensive quality model, we conduct experiments to compare our propopsed model with one widely used QoS model using PSO-based approach.
-In addtion, to evaluate the effectiveness of our PSO-based approach,  we also compare one recent GP approach \cite{ma2015hybrid} with our PSO-based approach using our proposed model.
+ \item To address a desirable balance that can be achieved using our comprehensive quality model, we conduct experiments to compare our proposed model with one widely used QoS model using PSO-based approach.
+In addition, to evaluate the effectiveness of our PSO-based approach,  we also compare one recent GP approach \cite{ma2015hybrid} with our PSO-based approach using our proposed model.
 Both comparisons utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}
@@
 Qi et al.
-\cite{qi2010combining} propose a heuristic service composition method, named LOEM (Local Optimization and Enumeration Method), where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal QoS.
+\cite{qi2010combining} propose a heuristic service composition method, named LOEM (Local Optimisation and Enumeration Method), where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal QoS.
 However, there exists a scalability problem for the enumeration technique.
@@
 Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function.
-A hybird approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions that are functionally correct.
+A hybrid approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions that are functionally correct.
 In particularly, greedy search techniques have been used to generate directed acyclic graphs (DAGs) as composition solutions that is further transferred to tree structures for initialisation and mutation.
@@
 
-In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches, there is a lack of a fully automated semantic web service composition approach to optimse semantic matchmaking quality and QoS simultaneously.
+In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches, there is a lack of a fully automated semantic web service composition approach to optimise semantic matchmaking quality and QoS simultaneously.
 Therefore, we first propose a general comprehensive quality model that aims to achieve a better semantic matchmaking quality with a slight trade-off in QoS, and then we propose an automated PSO-based approach with explicit support for the comprehensive model to find optimal service compositions.
@@
 To demonstrate the motivation of proposing a comprehensive quality, we give a simple example.
-The service $GenerateMap$ with a output ($StreetMap$) and a price (``6.72") in the web service composition can be replace by a service $GenerateTouristMap$ with a different output ($TouristMap$) and a different price (``16.87") availabile in the service repository.
+The service $GenerateMap$ with a output ($StreetMap$) and a price (``6.72") in the web service composition can be replace by a service $GenerateTouristMap$ with a different output ($TouristMap$) and a different price (``16.87") available in the service repository.
 This composition solution results in a better semantic matchmaking quality, but price negatively contributes to the QoS.
@@
 
-We herein give formal definitions of the concepts regarding the semantic web service composition problem utilised in our approach, and these concepts are captured in serveral models: a semantic web service model, a semantic matchmaking model, a weighted DAG composition model, and QoS calculation model, and composition problem model.
+We herein give formal definitions of the concepts regarding the semantic web service composition problem utilised in our approach, and these concepts are captured in several models: a semantic web service model, a semantic matchmaking model, a weighted DAG composition model, and QoS calculation model, and composition problem model.
 
@@
 
-\textbf{Definition 2.} A semantic web service is defined as a tuple $S = \{ I_{S}, O_{S}, QoS_S \}$ $\in$ $\mathcal{SR}$, where $I_{S}$ is a set of service inputs that must be satisfied to invoke $S$, and $O_{S}$ is a set of service outputs returned by the execution of $S$.
+\textbf{Definition 2.} A semantic web service (hereafter "service") is defined as a tuple $S = \{ I_{S}, O_{S}, QoS_S \}$ $\in$ $\mathcal{SR}$, where $I_{S}$ is a set of service inputs that must be satisfied to invoke $S$, and $O_{S}$ is a set of service outputs returned by the execution of $S$.
 $I_{S}$ and $O_{S}$ are concept-related instances that are linked to the concepts $I^{C}_{S}$ and $O^{C}_{S}$, where $ I^{C}_{S}, O^{C}_{S}  \subseteq C$.
@@
 
-We use the returns of $type(a, b)$ to define a full matchmaking considerd in the scenario of connecting two services through concept-related output and concept-related input.
+We use the returns of $type(a, b)$ to define a full matchmaking considered in the scenario of connecting two services through concept-related output and concept-related input.
 
@@
 
-\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $q(a \Rightarrow b)$ is a function that given a output-related concept of a service and a input-related concept of another service, it returns the concept similarities between them.
+\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $q_{sim}(a, b)$ is a function that given a output-related concept of a service and a input-related concept of another service, it returns the concept similarities between them.
 \vspace{0.3cm}

### 2017-03-26 paper.tex
update

@@
 This composition solution results in a better semantic matchmaking quality, but price negatively contributes to the QoS.
-Therefore, we need to measure these changes to the solutions considering matchmaking quality and QoS simultaneously for automatically generated solutions.
+Therefore, to reach the optimal solutions, we need to measure these changes to the solutions considering matchmaking quality and QoS simultaneously for automatically generated solutions.
 
@@
 The full match is a guarantee of completely valid  ``$ \Rightarrow$'' operation, whereas, partial matches are not considered in this paper.
+\vspace{0.3cm}
 
-\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $q_{sim}(a, b)$ is a function that given a output-related concept of a service and a input-related concept of another service, it returns the concept similarities between them.
-\vspace{0.3cm}
+\textbf{QoS calculation Model in a DAG}
+Four most often considered QoS parameters \cite{zeng2003quality} are response time, cost, reliability and availability described as follows:\textit{Response time} ($t_s$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.\textit{Cost} ($c_s$) is the amount of money that a service requester has to pay for executing the web service.
+\textit{Reliability} ($r_s$) is the probability that a request is correctly responded within the maximum expected time frame, which is expressed as a number between 1 and 0.
+\textit{Availability} ($a_s$) is the probability that a web service is accessible, which is expressed in the same way as $r_s$.
+The aggregation value of QoS in a DAG respect to the DAG's structures that determine how services associated with each other in a service composition.
+The QoS calculation models are described based on QoS aggregation method \cite{da2015graphevol} as follows:
+
+$A$, $R$, $C$, $T$ is aggregated $a_s$, $r_s$, $c_s$ and $t_n$ respectively a given $WG$, where  $\{S_1, S_2, ... S_n\} \subset V$, such that: $A=\prod\limits^n_{k=1}a_k
+$; $R=\prod\limits^n_{k=1}r_k$; $C=\sum\limits^n_{k=1}c_k$; $T$ is the time of most time-consumption path of $WG$, so $T = MAX \{timePath_n |n\in\{1,\ldots,m\}\}$.
+
+\section{Comprehensive Quality Model}\label{Comprehensive_Quality_Model}
+
+In this section, we propose a general comprehensive quality model in considering semantic matchmaking quality and QoS simultaneously.
+This comprehensive model is fully supported by the representations of service composition discussed in this paper, as a weighted DAG model formulated in this section.
+
+\subsection{Comprehensive Quality Model}\label{qualityModel}
+
+\textbf{Semantic matchmaking quality model}.
+Due to that the discretisational characteristics of different match types and values assigned to matching types driven by the cost of data manipulation \cite{lecue2009optimizing}, match types are considered to be one factor for the quality of matchmaking.
+For example, Exact matching type demands less time for computation compared to that of Plugin match.
+Another factor in concept similarity of two matched concepts.
+For example, two plugin types with different concept similarities: $publication \sqsubseteq printedmaterial$ and $romanticnovel \sqsubseteq printedmaterial$.
+
+\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $q_{sim}(a, b)$ is a function that given a output-related concept of a service and a input-related concept of another service, it returns a concept similarity value between them.
+
+The $q_{sim}(a, b)$ is calculated based on the edge counting method defined in the formula (\ref{equation1}) from \cite{shet2012new}, where $N_1$, $N_2$ and $N$ measure the distances from an output-related concept $a$, an input-related concept $b$, a closest common ancestor of these two matched $a$ and $b$ to the top concept of an ontology $O$ respectively.
+$\lambda$ is set to 0 if we do not measure the similarities of neighbourhood concepts, which is not the matching type considered in this paper.
+
+\begin{equation}
+s_{p}{=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
+\label{equation1}
+\end{equation}
+
+\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $sm(a,b)$ is a function that returns a pair of values consisitng of $type(a, b)$ and $q_{sim}(a, b)$ defined in Formula (\ref{equation2}).
+
+\begin{equation}
+\label{equation2}
+sm(a, b) \stackrel{.}{=} ( type(a, b), \  q_{sim}(a, b) )
+\end{equation}
 
@@
 $e = \{ (O_{S_{src}} \cup I_{S_{src}}) \mid \forall o \in O_{S_{src}}, \exists i \in O_{S_{src}} \wedge fullmatch (o \Rightarrow i) \}$
-\vspace{0.5cm}
+\vspace{0.3cm}
 
-\textbf{QoS Model in a Weighted DAG}
-Four most often considered QoS parameters \cite{zeng2003quality} are response time, cost, reliability and availability described as follows:\textit{Response time} ($T$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.\textit{Cost} ($C$) is the amount of money that a service requester has to pay for executing the web service.
-\textit{Reliability} ($R$) is the probability that a request is correctly responded within the maximum expected time frame.
-\textit{Availability} ($A$) is the probability that a web service is accessible.
-The aggregation value of QoS in a DAG respect to the structures of DAG, which reflects how services associated with each other in a service composition.
-The QoS calculation models are described as follows:
+\textbf{Comprehensive quality model in a weighted DAG}.
 
-\textbf{Definition 6.} $V_{A}(WG)$ is a function that given a $WG$, a aggregated $availability$ value is returned defined as :
-$V_{A}(WG)=\prod\limits^n_{k=1}a_k$, for all $\{S_1, S_2, ... S_n\} \subset V$.
-
-\textbf{Definition 7.} $V_{R}(WG)$ is a function that given a $WG$, a aggregated $reliability$ value is returned defined as :
-$V_{R}(WG)=\prod\limits^n_{k=1}r_k$, for all $\{S_1, S_2, ... S_n\} \subset V$.
-
-\textbf{Definition 8.} $V_{C}(WG)$ is a function that given a $WG$, a aggregated cost value is returned defined as :
-$V_{C}(WG)=\sum\limits^n_{k=1}c_k$, for all $\{S_1, S_2, ... S_n\} \subset V$.
-
-\textbf{Definition 9.} $V_{T}(WG)$ is a function that given a $WG$, a aggregated time value is returned, where  $T$ is determined by the most time-consuming path in the composition flow of the solution, which is defined as :
-$V_{T}(WG)$ $=MAX\{timePath(WG)_n$ $|n\in\{1,\ldots,m\}\}$, where m is the number of $timePath$.
-
-\vspace{0.5cm}
-
-\textbf{Composition Problem}
-A set of semantic web services $S$ are chained as a weighted DAG composition model $WG$ when a composition task $Comp.T$ is requested by users.
-The composition problem considered in this paper to automatically generate $WG$, satisfying the follows:
-
-$\forall WG^{'}$ , $\{q(a \Rightarrow b) \} \cup V_{A}(WG^{'}) \cup V_{R}(WG^{'}) \cup V_{C}(WG^{'}) \cup V_{T}(WG^{'})  \leq \{ q(a \Rightarrow b) \} \cup V_{A}(WG) \cup V_{R}(WG) \cup V_{C}(WG) \cup V_{T}(WG) $
-
-\section{Comprehensive Quality Model}\label{Comprehensive_Quality_Model}
-In this section, we propose a general comprehensive quality-aware service model in consideration of both semantic matchmaking quality and QoS for semantic web service composition.
-This model overcome the disadvantages of current prevailing QoS-aware quality model that ignores quality of semantic matchmaking.
-
-\subsection{Comprehensive Quality Model}\label{qualityModel}
-
-\textbf{Semantic web Service link}.
-In Fig.
-\ref{semanticLink}, $S_{1}$ and $S_{2}$ are linked to together if exists any parameter matchmaking between  Output of $S_1$ and Input of $S_2$.
-Therefore, measuring semantic matchmaking quality ($SM$) is to measure the overall quality of semantic web service link ($sm_{L}$), which is aggregated from the quality of parameter matchmaking ($sm_{P}$).
-This semantic web service link is adopt from \cite{lecue2009optimizing}.
-
-\begin{figure}[h]
-\centering
-\fbox{\includegraphics[scale=.38]{semanticLink.pdf}}
- \caption{ An example of semantic web service link}
- \label{semanticLink}
-\end{figure}
-
-\textbf{Semantic web matchmaking quality model}.
-Due to that the discretisational characteristics of different match types and values assigned to matching types are driven by the cost of data integration and manipulation \cite{lecue2009optimizing}, partial ordering match types are considered to be one factor for quality of parameter matchmaking, denoted as $mt_{p}$,  For example, Exact matching type demands less time for computation compared to that of Plugin match.
-Another factor in our proposed model is concept similarity, which could be evaluated based on the edge counting method defined in \cite{shet2012new}.
-This formula (\ref{equation1}) is used to estimate the concept similarity between matching parameters, which is denoted as $s_{p}$.
-N1 and N2 measure the distances from an output-related concept and an input-related concept to the top node of a taxonomy respectively, and N measure the distances from the closest common ancestor of these two matched input-related and output-related concepts.
-$\lambda$ is set to 0 if we do not measure the similarities of neighbourhood concepts that is not the matching levels considered in this paper.
-Consequently, given the quality of parameter matchmaking type and quality of parameter concept similarity, the quality of parameter matchmaking is defined by Formula (\ref{equation2}).
-
-\begin{equation}
-s_{p}{=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
-\label{equation1}
-\end{equation}
-
-\begin{equation}
-\label{equation2}
-sm_{p} \stackrel{.}{=} (mt_ {p}, \  s_ {p})
-\end{equation}
-
-Further more, since semantic web service link represent services connections, where quality of semantic web service link $(sm_{L})$ is considered to be semantic matching quality on service level by the aggregation of parameter matchmaking quality.
-Therefore, $sm_{L}$ is defined in formula (\ref{equation3}), where $sm_{L}$ and $s_{L}$ are the average value of all involved $mt_{p}$ and $s_{p}$ respectively.
+Since each $e$ defined in $E$ could have more than one $fullmatch(a \Rightarrow b)$ form a edge $e$.
+Therefore, semantic matchmaking quality of one $e$, denoted as $sm_e$ is defined in formula (\ref{equation3}), where $type_{e}$ and $sim_{e}$ are the average values of all involved $type(a, b)$ and $q_{sim}(a, b)$ respectively.
 
@@
 \label{equation3}
-sm_{L} \stackrel{.}{=} (mt_ {L}, \  s_ {L})
+sm_{e} \stackrel{.}{=} (type_ {e}, \  sim_ {e})
 \end{equation}
 
-\textbf{Comprehensive quality model}.
-The comprehensive quality model consider both semantic matchmaking quality and QoS.
-The semantic matchmaking quality refers to $sm_{L}$.
-Consequently, the comprehensive quality model is defined in Formula (\ref{equation4}), which could be further broken down into Formula (\ref{equation5}).
+The semantic matchmaking quality $SM$ is futher aggregated with considering all $\{e_{1}, e_{2},...
+e_{m} \}$ in $E$, calculated by following the formula (\ref{eqSM})(\ref{equation6})(\ref{equation7}).
+Consequently, in Formula \ref{eqCQ}, the comprehensive quality $CQ$ consists of the aggregated semantic matchmaking quality $SM$ and the QoS calculation in DAG discussed before.
+
 \begin{equation}
-\label{equation4}
-cq \stackrel{.}{=} (sm_ {L}, \  QoS_ {s})
+\label{eqSM}
+SM \stackrel{.}{=} (MT, SIM)
 \end{equation}
 \begin{equation}
-\label{equation5}
-cq \stackrel{.}{=} (mt_ {L}, \  s_ {L}, \  a_{s},\  r_{s},\  c_{s},\  t_{s})
-\end{equation}
-
-\textbf{Semantic matchmaking quality aggregation}.
-The quality aggregation is defined based on the constructs of composition web services in consideration of semantic matchmaking quality and QoS.
-The quality on composition solution is further calculated by following the formula (\ref{equation6})(\ref{equation7}), and QoS aggregation are discussed in Sect.
-\ref{Quality of Service and Composition Constructs}
-
-\begin{equation}
 \label{equation6}
-MT {=} \prod_{n=1}^{m} mt_ {L_{n}}
+MT {=} \prod_{n=1}^{m} type_ {e_{n}}
 \end{equation}
@@
 \label{equation7}
-S {=} (\sum_{n=1}^m s_ {L_{n}})/m
+SIM {=} (\sum_{n=1}^m sim_ {e_{n}})/m
+\end{equation}
+\begin{equation}
+\label{eqCQ}
+CQ \stackrel{.}{=} (MT, \  SIM, \  A,\  R,\  C,\  T)
 \end{equation}

### 2017-03-26 paper.tex
update

@@
  \item To propose a PSO-based service composition approach that utilises the proposed comprehensive quality model.
-To do that we optimise a queue of web services by evaluating its decoded representations.
-These representations are the solutions for semantic web service composition.
+To do that we optimise a queue of web services by evaluating the comprehensive quality of its decoded representations.
 
@@
 
-Semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} captures the semantic description of web services' parameters using some kind of logic (e.g., description logic) that ensuring the interoperability of web services, where the number of web services or length of a graph representation for web service composition is minimised to reach the optimised composition solutions.
-However, this evaluation approach does not guarantee optimised QoS of composition solutions.
+Semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} captures the semantic description of web services' parameters using some kind of logic (e.g., description logic) that ensuring the interoperability of web services, where the number of web services or length of a graph representation for web service composition is minimised to reach the optimised composition solutions.
+However, this evaluation approach does not guarantee an optimised QoS of composition solutions.
 
@@
 Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function.
-A hybrid approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions that are functionally correct.
+A hybrid approach employs both greedy search algorithm and GP introduced in \cite{ma2015hybrid} to generate solutions that are functionally correct.
 In particularly, greedy search techniques have been used to generate directed acyclic graphs (DAGs) as composition solutions that is further transferred to tree structures for initialisation and mutation.
@@
 Lecue et al.
-\cite{lecue2009optimizing} propose a semi-automated web service composition using GA to encode a given abstract service workflow, where the semantic matchmaking quality is measured through evaluating the quality of semantic links that require a formal definition of ontology in Description Logic.
+\cite{lecue2009optimizing} propose a semi-automated web service composition using GA to encode a given abstract service workflow, where the semantic matchmaking quality is measured through evaluating the quality of semantic links that require a complete and formal definition of ontology in Description Logic.
 This evaluation model takes huge cost and time for the domain experts to establish required ontology.
@@
 
-In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches, there is a lack of a fully automated semantic web service composition approach to optimise semantic matchmaking quality and QoS simultaneously.
+In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches, there is a lack of a fully automated semantic web service composition approach to optimise semantic matchmaking quality and QoS simultaneously, and this approach must be tested utilising benchmark dataset.
 Therefore, we first propose a general comprehensive quality model that aims to achieve a better semantic matchmaking quality with a slight trade-off in QoS, and then we propose an automated PSO-based approach with explicit support for the comprehensive model to find optimal service compositions.
@@
 A motivating example of this problem is shown in Fig \ref{motivation}.
-The figure shows a DAG that represents a solution with four web services involved for a request $R$ as a composition task, where inputs of the task are \{TravelDepartureDate, HomeCity, ConferenceCity, TravelReturnDate \} and outputs are \{BusTicket, FlightTicket, TouristMap, HotelReservation \}.
+The figure shows a DAG that represents a solution with four web services involved for a request $R$ as a composition task, where inputs of the task are \{$TravelDepartureDate$, $HomeCity$, $ConferenceCity$, $TravelReturnDate$ \} and outputs are \{$BusTicket$, $FlightTicket$, $TouristMap$, $HotelReservation$ \}.
 This is a classic example of travel planning problem for people who seek for booking services of airplanes, buses and hotels reservation, and also generating tourist maps for the conference city.
@@
 Moreover, valid semantic matches between two connected web services could also have different matchmaking quality.
-For example, $Generate Map$ service produce $StreetMap$ which is considered to be a valid semantic match to $TouristMap$, while $Bus Service$ produce $BusTicket$ which is considered to be a better valid semantic match to $BusTicket$.
-The descriptions of these matched resources are captured in a taxonomy depicted in Fig .\ref{taxonomy}, where all the inputs and the outputs related to the web services are described for a travel planning problem.
+For example, $Generate Map$ service produce $StreetMap$ which is considered to be a valid semantic match to $TouristMap$, but $Bus Service$ produce $BusTicket$ which is considered to be a better valid semantic match to $BusTicket$.
+The descriptions of these matched resources are captured in a ontology depicted in Fig .\ref{taxonomy}, where all the inputs and the outputs related to the web services are described for the travel planning problem discuss here.
 For example, the concept $Map$ and its sub-concept $urbanMap$ are assigned with a $touristMap$ instance and $streetMap$ instance respectively in Fig .\ref{taxonomy}.
 The valid semantic match is considered that an instance of $urban Map$ can be an instance of $Map$, but not vice versa.
-To demonstrate the motivation of proposing a comprehensive quality, we give a simple example.
+To demonstrate the motivation of proposing a comprehensive quality, we give a simple example here.
 The service $GenerateMap$ with a output ($StreetMap$) and a price (``6.72") in the web service composition can be replace by a service $GenerateTouristMap$ with a different output ($TouristMap$) and a different price (``16.87") available in the service repository.
 This composition solution results in a better semantic matchmaking quality, but price negatively contributes to the QoS.
-Therefore, to reach the optimal solutions, we need to measure these changes to the solutions considering matchmaking quality and QoS simultaneously for automatically generated solutions.
+Therefore, to reach the optimal solutions automatically, we need to measure these changes to the solutions considering matchmaking quality and QoS simultaneously.
 
@@
 \fbox{\includegraphics[scale=.28]{taxonomy.pdf}}
- \caption{ A taxonomy of a travel planning domain}
+ \caption{ An ontology of a travel planning domain}
  \label{taxonomy}
@@
 
-We herein give formal definitions of the concepts regarding the semantic web service composition problem utilised in our approach, and these concepts are captured in several models: a semantic web service model, a semantic matchmaking model, a weighted DAG composition model, and QoS calculation model, and composition problem model.
+We herein give formal definitions of the concepts regarding the semantic web service composition problem utilised in our approach, and these concepts are captured in several models as follows.
 
 \textbf{Semantic Web Service Model}.
-The semantic web service model represents web services with functional descriptions, and how interoperability of web services enables matchmaking for automatically generating composition solutions.QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid}
+The semantic web service model represents web services with functional descriptions, and how interoperability of web services enables matchmaking for automatically generating composition solutions.
 
@@
 \textbf{Definition 2.} A semantic web service (hereafter "service") is defined as a tuple $S = \{ I_{S}, O_{S}, QoS_S \}$ $\in$ $\mathcal{SR}$, where $I_{S}$ is a set of service inputs that must be satisfied to invoke $S$, and $O_{S}$ is a set of service outputs returned by the execution of $S$.
-$I_{S}$ and $O_{S}$ are concept-related instances that are linked to the concepts $I^{C}_{S}$ and $O^{C}_{S}$, where $ I^{C}_{S}, O^{C}_{S}  \subseteq C$.
+$I_{S}$ and $O_{S}$ are concept-related instances that are linked to their corresponding concepts $I^{C}_{S}$ and $O^{C}_{S}$, where $ I^{C}_{S}, O^{C}_{S}  \subseteq C$.
 $QoS_S = \{ t_s, c_s, r_s, a_s, ...
@@
 
-We use the returns of $type(a, b)$ to define a full matchmaking considered in the scenario of connecting two services through concept-related output and concept-related input.
+We use $type(a, b)$ to define a full matchmaking considered in the scenario of connecting two services through concept-related output and concept-related input.
 
@@
 \textbf{QoS calculation Model in a DAG}
-Four most often considered QoS parameters \cite{zeng2003quality} are response time, cost, reliability and availability described as follows:\textit{Response time} ($t_s$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.\textit{Cost} ($c_s$) is the amount of money that a service requester has to pay for executing the web service.
+Four most often considered QoS parameters \cite{zeng2003quality} are response time, cost, reliability and availability described as follows: \textit{Response time} ($t_s$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.\textit{Cost} ($c_s$) is the amount of money that a service requester has to pay for executing the web service.
 \textit{Reliability} ($r_s$) is the probability that a request is correctly responded within the maximum expected time frame, which is expressed as a number between 1 and 0.
@@
 
-$A$, $R$, $C$, $T$ is aggregated $a_s$, $r_s$, $c_s$ and $t_n$ respectively a given $WG$, where  $\{S_1, S_2, ... S_n\} \subset V$, such that: $A=\prod\limits^n_{k=1}a_k
-$; $R=\prod\limits^n_{k=1}r_k$; $C=\sum\limits^n_{k=1}c_k$; $T$ is the time of most time-consumption path of $WG$, so $T = MAX \{timePath_n |n\in\{1,\ldots,m\}\}$.
+$A$, $R$, $C$, $T$ is aggregated $a_s$, $r_s$, $c_s$ and $t_n$ respectively with a given $WG$, where  $\{S_1, S_2, ... S_n\} \subset V$, such that: $A=\prod\limits^n_{k=1}a_k
+$; $R=\prod\limits^n_{k=1}r_k$; $C=\sum\limits^n_{k=1}c_k$; $T$ is the time of most time-consumption path of $WG$, so $T = MAX \{timePath()_n |n\in\{1,\ldots,m\}\}$ where $m$ is the number of $WG$ path, and $timePath() = \sum\limits^j_{k=1}t_k$, where $j$ is the number of services involved this path.
 
@@
 For example, Exact matching type demands less time for computation compared to that of Plugin match.
-Another factor in concept similarity of two matched concepts.
-For example, two plugin types with different concept similarities: $publication \sqsubseteq printedmaterial$ and $romanticnovel \sqsubseteq printedmaterial$.
+Another factor is concept similarity of two matched concepts.
+For example, two plugin types, $publication \sqsubseteq printedmaterial$ and $romanticnovel \sqsubseteq printedmaterial$, are associated with different similarities.
 
-\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $q_{sim}(a, b)$ is a function that given a output-related concept of a service and a input-related concept of another service, it returns a concept similarity value between them.
+\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $q_{sim}(a, b)$ is a function that given a output-related concept $a$ of a service and a input-related concept $b$ of another service, it returns a concept similarity value between $a$ and $b$.
 
 The $q_{sim}(a, b)$ is calculated based on the edge counting method defined in the formula (\ref{equation1}) from \cite{shet2012new}, where $N_1$, $N_2$ and $N$ measure the distances from an output-related concept $a$, an input-related concept $b$, a closest common ancestor of these two matched $a$ and $b$ to the top concept of an ontology $O$ respectively.
-$\lambda$ is set to 0 if we do not measure the similarities of neighbourhood concepts, which is not the matching type considered in this paper.
+$\lambda$ is set to 0 as we do not measure the similarities of neighbourhood concepts, which is not the matching type considered in this paper.
 
@@
 
-\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $sm(a,b)$ is a function that returns a pair of values consisitng of $type(a, b)$ and $q_{sim}(a, b)$ defined in Formula (\ref{equation2}).
+\textbf{Definition 6.} Given $full match(a \Rightarrow b)$, $sm(a,b)$ is a function for measuring semantic matchmaking quality between two concepts, which returns a pair of values consisting of $type(a, b)$ and $q_{sim}(a, b)$ defined in Formula (\ref{equation2}).
 
@@
 web service composition is considered to be a data workflow, where services are chained together by their inputs and outputs using the two models defined before.
-Naturally, all these concepts can be captured in a weighted DAG as $WG = (V, E)$ , where:
+All these concepts are captured and tackled in a weighted DAG as $WG = (V, E)$ , where:
 
@@
 $E = \{e_{1}, e_{2},...
-e_{m} \}$ is a set of edges, where each edge has a set of incoming outputs $O_{S_{src}}$ from source service $S_{src}$ and a set of outgoing inputs $I_{S_{src}}$ from target service $S_{tar}$.
+e_{m} \}$ is a set of edges, where each edge has a set of incoming outputs $O_{S_{src}}$ from source service $S_{src}$ and a set of outgoing inputs $I_{S_{tar}}$ from target service $S_{tar}$.
 
@@
 
-Since each $e$ defined in $E$ could have more than one $fullmatch(a \Rightarrow b)$ form a edge $e$.
-Therefore, semantic matchmaking quality of one $e$, denoted as $sm_e$ is defined in formula (\ref{equation3}), where $type_{e}$ and $sim_{e}$ are the average values of all involved $type(a, b)$ and $q_{sim}(a, b)$ respectively.
+Since each $e$ defined in $E$ could have more than one $fullmatch(a \Rightarrow b)$ form a edge.
+Therefore, semantic matchmaking quality of one edge, denoted as $sm_e$ is defined in formula (\ref{equation3}), where $type_{e}$ and $sim_{e}$ are the average values of all involved $type(a, b)$ and $q_{sim}(a, b)$ respectively.
 
@@
 
-The semantic matchmaking quality $SM$ is futher aggregated with considering all $\{e_{1}, e_{2},...
+The semantic matchmaking quality $SM$ is further aggregated with considering all $\{e_{1}, e_{2},...
 e_{m} \}$ in $E$, calculated by following the formula (\ref{eqSM})(\ref{equation6})(\ref{equation7}).
@@
 The function value of 1 means the best comprehensive quality and 0 means the worst.
-For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the function value falls within the range from 0 to 1 using Formula (\ref{equation9}) and (\ref{equation10}), where the maximum and minimum value of $A$, $R$, $T$, and $C$ are calculated by all web services related to the composition task.
+For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the function value falls within the range from 0 to 1 using Formula (\ref{equation9}) and (\ref{equation10}), where the maximum and minimum value of $A$, $R$, $T$, and $C$ are calculated by all web services candidates to the composition task, which are generated by a greedy search discussed in Sect.\ref{PSO_based_approach}.
 $MT$ and $S$ are using a bound from 0 to 1.
@@
 Our comprehensive quality evaluation model is considered to be more general.
-Semantic matchmaking types (Exact and Plugin) are considered for discovering desired web service in QoS-aware web service composition  \cite{ma2015hybrid,da2016particle,da2015graphevol}, but there are no measurements of matchmaking types and concept similarities.
-Consequently, weights for $MT$ and $S$ are considered to be 0 in our propopsed comprehensive evaluation model, it turns to a widely used QoS evaluation model in \cite{ma2015hybrid,da2016particle,da2015graphevol}.
+Two semantic matchmaking types (Exact and Plugin) are considered for discovering desired web service in recent QoS-aware web service composition  \cite{ma2015hybrid,da2016particle,da2015graphevol}, but there are no measurements of matchmaking types and concept similarities in their approaches.
+Consequently, weights for $MT$ and $S$ are considered to be 0 in our proposed comprehensive evaluation model, it turns to be a widely used QoS evaluation model in \cite{ma2015hybrid,da2016particle,da2015graphevol}.
 \section{PSO-based Approach to Comprehensive Quality-Aware Automated Semantic Web Service Composition}\label{qswsc_approach}
@@
 
-\subsection{PSO-based Approach to QoS-Aware Semantic Web Service Composition}
+\subsection{PSO-based Approach to QoS-Aware Semantic Web Service Composition}\label{PSO_based_approach}
 

### 2017-03-27 paper.tex
update

@@
 
-\section{Motivation and Problem Description}\label{problemDes}
+\section{Motivation and Problem Description}\label{Motivation and Problem Description}
 \subsection{Motivation}\label{Motivation}
@@
 
-\subsection{Problem Formulation}\label{Motivation}
+\subsection{Problem Formulation}\label{problemDes}
 
@@
 
-\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $q_{sim}(a, b)$ is a function that given a output-related concept $a$ of a service and a input-related concept $b$ of another service, it returns a concept similarity value between $a$ and $b$.
+\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $sim(a, b)$ is a function that given a output-related concept $a$ of a service and a input-related concept $b$ of another service, it returns a concept similarity value between $a$ and $b$.
 
-The $q_{sim}(a, b)$ is calculated based on the edge counting method defined in the formula (\ref{equation1}) from \cite{shet2012new}, where $N_1$, $N_2$ and $N$ measure the distances from an output-related concept $a$, an input-related concept $b$, a closest common ancestor of these two matched $a$ and $b$ to the top concept of an ontology $O$ respectively.
+The $sim(a, b)$ is calculated based on the edge counting method defined in the formula (\ref{equation1}) from \cite{shet2012new}, where $N_1$, $N_2$ and $N$ measure the distances from an output-related concept $a$, an input-related concept $b$, a closest common ancestor of these two matched $a$ and $b$ to the top concept of an ontology $O$ respectively.
 $\lambda$ is set to 0 as we do not measure the similarities of neighbourhood concepts, which is not the matching type considered in this paper.
@@
 \begin{equation}
-s_{p}{=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
+sim(a, b){=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
 \label{equation1}
@@
 \label{equation2}
-sm(a, b) \stackrel{.}{=} ( type(a, b), \  q_{sim}(a, b) )
+sm(a, b) \stackrel{.}{=} ( type(a, b), \  sim(a, b) )
 \end{equation}
 
-\textbf{Weighted DAG Composition Model}.
+\textbf{Weighted DAG composition model}.
 web service composition is considered to be a data workflow, where services are chained together by their inputs and outputs using the two models defined before.
@@
 Consequently, weights for $MT$ and $S$ are considered to be 0 in our proposed comprehensive evaluation model, it turns to be a widely used QoS evaluation model in \cite{ma2015hybrid,da2016particle,da2015graphevol}.
+
 \section{PSO-based Approach to Comprehensive Quality-Aware Automated Semantic Web Service Composition}\label{qswsc_approach}
 
-\begin{figure*}[h]
+\begin{figure}[h]
 \centering
 \fbox{\includegraphics[scale=.4]{overview.pdf}}
- \caption{Overview of POS-based approach to QoS-aware automated semantic web service composition.}
+ \caption{An overview of POS-based approach to comprehensive quality-aware automated semantic web service composition.}
  \label{overview}
-\end{figure*}
+\end{figure}
 
-\subsection{PSO-based Approach to QoS-Aware Semantic Web Service Composition}\label{PSO_based_approach}
+\subsection{An Overview to PSO-based Method}\label{PSO_based_approach}
 
-PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}.
-Therefore, we will employ a PSO-based approach, which is considered to be easier to maintain the correctness of solutions compared to GP-based approaches that often require repairing or penalising the solutions \cite{da2016particle}.
+PSO has shown its promising in solving combinatorial optimisation problems, which is considered to a easier way to maintain the correctness of solutions comparing to GP-based approaches that often require repairing or penalising the solutions \cite{da2016particle}.
+Therefore, we will employ a PSO-based approach to comprehensive quality-aware automated semantic web service composition.
 Fig.
-\ref{overview} shows the overview of our approach with five steps.
-Step 1: The composition process is triggered by a composition goal defined in Subsection \ref{problemDes}, which describes customers requirements both semantic matchmaking quality and QoS.
-Step 2: This composition goal are used to discover all relevant web services, which lead to a shrunken service repository that is subsequently used by PSO as a searching space.
-Step 3: A weighted graph representation is randomly built up from an initial service queue that mapped to the particle's location, interleaving with semantic matchmaking process utilising ontology-based index cache.
-In the weighted graph, graph edges are assigned with semantic matchmaking quality as weights.
+\ref{overview} shows an overview of our approach with five steps.
+Step 1: The composition process is triggered by a composition task defined in Subsection \ref{problemDes}.
+Step 2: This composition task is used to discover all task-related service candidates using a greedy search adopt from \cite{ma2015hybrid}.
+This algorithm keeps storing and adding outputs of the evocable services as available outputs, and these available outputs are used to discovery new services in service repository and updated themselves.
+This loop process does not stop until no service is satisfied by the available outputs.
+During the greedy search, an ontology-based cache is initialised, which stores the concept similarities of inputs and outputs of task-related candidate that demonstrated in SubSect.
+\ref{indexCache}.
+Step 3: Particle initialisation and mapping.
+In the initialisation, each particle's position size is determined by the size of task-related service candidates.
+Meanwhile, each service candidate are mapped to an index of a particle’s position vector (each vector have a weight value that falls between 0.0 and 1.0).
+After that, all the services are put in a queue and sorted according to their corresponding weight values in a descending order.
+This sorted queue is used to construct a weighted DAG.
+Step 4.
+Follows the standard PSO steps after step 3.
 Step 4: The fitness value of the weighted graph is evaluated to update the position of particle under PSO algorithm in Sect.

### 2017-03-27 paper.tex
update

@@
 
-PSO has shown its promising in solving combinatorial optimisation problems, which is considered to a easier way to maintain the correctness of solutions comparing to GP-based approaches that often require repairing or penalising the solutions \cite{da2016particle}.
-Therefore, we will employ a PSO-based approach to comprehensive quality-aware automated semantic web service composition.
+PSO has shown its promising in solving combinatorial optimisation problems, which is considered to an easier way to maintain the correctness of solutions comparing to GP-based approaches that often require repairing or penalising the solutions \cite{da2016particle}.
+Therefore, we will employ a PSO-based approach to comprehensive quality-aware automated semantic web service composition consisting a forward decoding process.
 Fig.
-\ref{overview} shows an overview of our approach with five steps.
-Step 1: The composition process is triggered by a composition task defined in Subsection \ref{problemDes}.
-Step 2: This composition task is used to discover all task-related service candidates using a greedy search adopt from \cite{ma2015hybrid}.
-This algorithm keeps storing and adding outputs of the evocable services as available outputs, and these available outputs are used to discovery new services in service repository and updated themselves.
+\ref{overview} shows an overview of our approach consisting of four steps:
+
+Step 1: The composition process is triggered by a composition task, which is clearly defined in Subsection \ref{problemDes}.
+
+Step 2: This composition task is used to discover all task-related service candidates using a greedy search adopted from \cite{ma2015hybrid}.
+This algorithm keeps adding outputs of the evocable services as available outputs, and these available outputs are used to discovery new services from service repository and be updated with the outputs of these discovered services.
 This loop process does not stop until no service is satisfied by the available outputs.
-During the greedy search, an ontology-based cache is initialised, which stores the concept similarities of inputs and outputs of task-related candidate that demonstrated in SubSect.
+During this greedy search, an ontology-based cache is initialised, which stores the concept similarities of inputs and outputs of task-related candidate that are further demonstrated in SubSect.
 \ref{indexCache}.
-Step 3: Particle initialisation and mapping.
+
+Step 3: Particle initialisation and serivce-to-index mapping.
 In the initialisation, each particle's position size is determined by the size of task-related service candidates.
-Meanwhile, each service candidate are mapped to an index of a particle’s position vector (each vector have a weight value that falls between 0.0 and 1.0).
-After that, all the services are put in a queue and sorted according to their corresponding weight values in a descending order.
-This sorted queue is used to construct a weighted DAG.
-Step 4.
-Follows the standard PSO steps after step 3.
-Step 4: The fitness value of the weighted graph is evaluated to update the position of particle under PSO algorithm in Sect.
-\ref{pso_algorithm}, where the position is mapped to the index of service queue.
-later on, the updated service queue is used to decode a new weighted graph as the composition solution.
-Step 5.
-Lastly, the best position found in the searching space is selected and decode into the final optimised solution.
-This PSO-based approach is similar to \cite{da2016particle}, but we employ weighted graphs as a different solution presentation with explicit support for the proposed quality model.
+Meanwhile, each service candidate is mapped to an index of a particle’s position vector (each vector have a weight value that falls between 0.0 and 1.0).
+After that, all the service candidates are put in a queue and sorted according to their corresponding weight values in a descending order.
+This procedure are a part of  Algorithm \ref{novelSteps} below.
+This sorted queue is used as one of the input of a forward decoding algorithm \ref{graph_building} to create a weighted graph using ontology-based cache in Step 2.
+In addition, this forward graph building Algorithm can lead to more services and edges connected to the graph, which should be removed at last.
+
+Step 4. Follows left steps of algorithm \ref{novelSteps} as the same as the standard PSO steps, Besides that, particles' fitness is calculated on the decoded weight DAGs.
 
 \subsection{Ontology-based Index Cached Optimisation}\label{indexCache}
-our PSO-based approach demands decoding processes from optimised queues to weighted DAGs, the bottlenecks of efficiently generating weighted DAGs lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively.
-To effectively construct weighted DAGs, we pre-calculate semantic matchmaking quality.
-The key idea of the index is to create a map using a pair of keys, output-related concepts and potentially matched input-related concepts with considering different levels of match types, and the map values stored $mt_{p}$ and $mt_{s}$.
-Meanwhile, this index size could also be reduced by only considering the concepts related in the shrunken service repository, which means the index cache is filtered by those task-relevant web services.
-This optimised cache also contributes to less and constant time for weighted graphs building through the whole evolutionary process.
-
-\subsection{QoS-aware Semantic Web Service Composition Algorithm} \label{pso_algorithm}
+our PSO-based approach demands decoding processes from optimised queues to weighted DAGs, a bottleneck of efficiently constructing weighted DAGs lie in building required information of edges, which is related to the cost of $fullmatch$
+$(a \Rightarrow b)$ identifications and $sim(a, b)$ calculations between input-related and output-related concepts of service candidates.
+To efficiently construct weighted DAGs, we calculate $sim(a, b)$ of all $fullmatch(a \Rightarrow b)$ interleaving with the greedy search discussed in Sect \ref{PSO_based_approach}.
+This information is stored in a table structure with special $X$ value if no $fullmatch(a \Rightarrow b)$ is satisfied.
+Therefore, this optimised cache contributes to less and constant time for weighted DAG building through the evolutionary process.
 
 \begin{algorithm}
- \setlength\hsize{0.9\linewidth}
  \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
@@
  \SetNlSty{}{}{:}
- \Input{relevant Web services $rws$}
- \Output{Optimised service queue $queue$,Optimised Weighted Graph $OPTWG$}
- Map each relevant service to an index in the particle's position vector\;https://www.facebook.com/
  Randomly initialise each particle in the swarm\;
@@
      \ForEach{particles in the swarm}{
-     $queue \leftarrow$ map service in a descending order by particle's position vector\;
-     $WG \leftarrow$ $generateWeightedGraph$()\;
-	 Calculate the $WG$ fitness value\;
+     Map service candidates to particle's position vector\;
+     Create a service queue and sort it by position vectors' weights\;
+     Decode the service into a weighted DAG \;
+	 Calculate the $Weighted DAG$ fitness value\;
 
@@
   }
- \KwRet $OPTWG$\;
- \caption{Steps of the PSO-based Web service composition technique.}
+\caption{Steps of PSO-based service composition technique \cite{da2016particle}.}
 \label{novelSteps}
 \end{algorithm} 
-
 \begin{algorithm}
- \setlength\hsize{0.9\linewidth}
  \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
- \SetKwFunction{generateWeightedGraph}{generateWeightedGraph}
+ \SetKwFunction{createWeightedDAG}{createWeightedDAG}
  \SetKwProg{Procedure}{Procedure}{}{}
@@
  \SetNlSty{}{}{:}
-  \Procedure{\generateWeightedGraph{}}{
- \Input{Task inputs $I$, task outputs $O$, Optimised service queue $queue$, IndexCache $IndexCache$}
- \Output{Weighted Graph $WG$}
- $WG \leftarrow  null$\;
- $WG \leftarrow$ new $endNode$(), new $startNode$()\;
- $OutputSet \leftarrow$ \{$I$\}\;
-  \While {all $O$ $\notin$ $OutputSet$  and $queue !=null$}{
-     \ForEach{$ws$ in $queue$}{
-      \uIf{$ws.inputs$ $\in$ $OutputSet$ }{    
-    		 \ForEach{$I$ in $ws.inputs$}{
-    		$mt_{P}, s_{P} \leftarrow$ query $IndexCache$\;
-     		$mt_{L} \leftarrow$ aggregation($mt_{p}$)\;
- 			$s_{L} \leftarrow$ aggregation($s_{p}$)\;
+  \Procedure{\createWeightedDAG{}}{
+ \Input{ $I_T$, $O_T$, $queue$, $Cache$}
+ \Output{WG}
+ $WG = (V, E)$\;
+ $V \leftarrow$ \{$Start$, $End$ \} \;
+ $OutputSet \leftarrow$ \{$I_{T}$\}\;
+  \While { $O_{T}$ $\notin$ $OutputSet$  and $queue !=null$}{
+     \ForEach{$S$ in $queue$}{
+      \uIf{$fullmatch(a \Rightarrow b)$$\wedge$ $(a \in OutputSet)$ $\wedge$ $(b \in I_{S})$ $\wedge$ $\mid fullmatch(a \Rightarrow b) \mid = \mid I_{S} \mid$}{    
+    		 \ForEach{$fullmatch(a \Rightarrow b)$}{
+    		$sim(a,b) \leftarrow$ query $IndexCache$\;
+ 			$sm(a,b) \leftarrow$ $( type(a,b), sim(a,b))$\;
               }
-        $sm_{L} \leftarrow$ \{ $mt_{L}$,$s_{L}$ \}\;
-        $WG.edge \leftarrow$  $sm_{L} $\;
-        $WG \leftarrow$ new $wsNode$()\;
-         $OutputSet$ add \{$ws.outputs$\}\;    
-       $queue$.remove $ws$\;
+        $sm_{e} \leftarrow$ aggregate \{ $sm(a,b)$ \}\;
+        $E \leftarrow$ add $e$\;
+        $V \leftarrow$ add $S$\;
+        $OutputSet$ add \{$O_{S}$\}\;    
+        $queue$.remove $S$\;
        }	
@@
  }
- \caption{Create a composition weighted graph from a queue.}
+ \caption{Create a weighted DAG from a  sorted queue.}
 \label{graph_building}
 \end{algorithm}
-
-The overall algorithm investigated here is made up of the PSO-based web service composition algorithm \ref{novelSteps} and the decoding algorithm \ref{graph_building}.
-In algorithm \ref{novelSteps}, the idea is to translate the particle location produced by PSO into a service queue as an indirect representation, such that finding the best fitness of the weighted graph is to discover the optimised location of the particle in the search space.
-In PSO, the dimension of each particle equals to the number of relevant web services.
-The index of each services is mapped to a separate location component in a particle.
-Then services queue is sorted by the particles' position vector in the ascending order, from which we decode a weighted graph using Algorithm \ref{graph_building}.
-It is a simple forward graph building algorithm, and this method can lead to more services and edges connected to the graph that must be removed.
-Also, semantic quality value are assigned to all the edges, which is calculated from quality aggregation function with given parameter matchmaking quality.
 

### 2017-03-28 paper.tex
update

@@
 \documentclass{llncs}
-\usepackage[ruled,vlined]{algorithm2e}
+\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
 \usepackage{color,graphicx,epstopdf,changepage,amsmath,multirow}
@@
 Step 2: This composition task is used to discover all task-related service candidates using a greedy search adopted from \cite{ma2015hybrid}.
-This algorithm keeps adding outputs of the evocable services as available outputs, and these available outputs are used to discovery new services from service repository and be updated with the outputs of these discovered services.
+During this greedy search, an ontology-based cache ($Cache$) is initialised, which stores the concept similarities of inputs and outputs of task-related candidates.
+
+Step 3 and Step 4: These two steps follow the stardard PSO steps \cite{shi2001particle} except some differences that lie in  particles initialisation and decoding process.
+These two differences are related to sort a service queue using a serivce-to-index mapping for a particle' position vectors and evaluate the fitness of a particle after decoding this serivce queue into a weighted DAG respectively, which are further addressed in Algorithm \ref{novelSteps} and \ref{graph_building} in SubSect \ref{POS-based_algomargin}.
+
+.
+
+\subsection{PSO-based approach algorithm}\label{POS-based_algomargin}
+The overall algorithm investigated here is made up of the PSO-based web service composition algorithm \ref{novelSteps} and the decoding algorithm \ref{graph_building}.
+In algorithm \ref{novelSteps}, the  steps $4$, $5$, $6$ and $7$ are different steps from those of stardard PSO.
+First, each particle's position size is determined by the size of task-related service candidates generated by a greedy search.
+This greedy search algorithm keeps adding outputs of the evocable services as available outputs, and these available outputs are used to discovery task-related services from service repository and be updated with the outputs of these discovered services.
 This loop process does not stop until no service is satisfied by the available outputs.
-During this greedy search, an ontology-based cache is initialised, which stores the concept similarities of inputs and outputs of task-related candidate that are further demonstrated in SubSect.
-\ref{indexCache}.
-
-Step 3: Particle initialisation and serivce-to-index mapping.
-In the initialisation, each particle's position size is determined by the size of task-related service candidates.
-Meanwhile, each service candidate is mapped to an index of a particle’s position vector (each vector have a weight value that falls between 0.0 and 1.0).
-After that, all the service candidates are put in a queue and sorted according to their corresponding weight values in a descending order.
-This procedure are a part of  Algorithm \ref{novelSteps} below.
-This sorted queue is used as one of the input of a forward decoding algorithm \ref{graph_building} to create a weighted graph using ontology-based cache in Step 2.
-In addition, this forward graph building Algorithm can lead to more services and edges connected to the graph, which should be removed at last.
-
-Step 4. Follows left steps of algorithm \ref{novelSteps} as the same as the standard PSO steps, Besides that, particles' fitness is calculated on the decoded weight DAGs.
-
-\subsection{Ontology-based Index Cached Optimisation}\label{indexCache}
-our PSO-based approach demands decoding processes from optimised queues to weighted DAGs, a bottleneck of efficiently constructing weighted DAGs lie in building required information of edges, which is related to the cost of $fullmatch$
-$(a \Rightarrow b)$ identifications and $sim(a, b)$ calculations between input-related and output-related concepts of service candidates.
-To efficiently construct weighted DAGs, we calculate $sim(a, b)$ of all $fullmatch(a \Rightarrow b)$ interleaving with the greedy search discussed in Sect \ref{PSO_based_approach}.
-This information is stored in a table structure with special $X$ value if no $fullmatch(a \Rightarrow b)$ is satisfied.
-Therefore, this optimised cache contributes to less and constant time for weighted DAG building through the evolutionary process.
-
+Second, each service candidate is mapped to an index of a particle’s position vector, where each vector have a weight value that falls between 0.0 and 1.0.
+This a service-to-index mapping for position vectors discussed in Step 3 in SubSect \ref{PSO_based_approach}.
+Third, all the service candidates are put in a queue and sorted according to their corresponding weight values in a descending order.
+Fourth, this sorted queue is used as one of the input of a forward decoding algorithm \ref{graph_building} to create a weighted DAG, this fitness value of this weighted DAG is the fitness value of the particle.
 \begin{algorithm}
+ %\LinesNumbered
  \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
@@
  \SetKwProg{Procedure}{Procedure}{}{}
- \LinesNumbered
  \SetNlSty{}{}{:}
@@
      Create a service queue and sort it by position vectors' weights\;
-     Decode the service into a weighted DAG \;
+     Create the service into a weighted DAG \;
 	 Calculate the $Weighted DAG$ fitness value\;
@@
 \end{algorithm}
+
+This Algorithm  \ref{graph_building}is a forward graph graph buidling algorithm based on \cite{blum1997fast}.
+This algorthm take an input of the sorted service queues discussed above, and service queues with diferent order is possible to create different weighted DAGs as composition solutions.
+In additon.
+$I_{T}$, $O_{T}$ and $Cache$ are also taken as inputs.
+Firstly, $Start$ and $End$ are added to V of WG initialization, $OutputSet$ is created with $I_{T}$.
+If all the inputs of first $S$ popped from $queue$ can be satisfied by provided outputs of $OutputSet$, this $S$ is added to $V$ and its outputs are added to $OutputSet$.
+Meanwhile, $sm_{e}$ is calcated based on the aggregation value of $sm(a, b)$
+
+Otherwise,  next $S$ popped from the $queue$ is to be considered. These steps are not stopped until all  $O_{T}$ can satisfied from $Outputset$ or queue is null.
+
+can lead to more services and edges connected to the graph, which should be removed at last.
+
 \begin{algorithm}
@@
  \SetKwProg{Procedure}{Procedure}{}{}
- \LinesNumbered
+ %\LinesNumbered
  \SetNlSty{}{}{:}
@@
  $OutputSet \leftarrow$ \{$I_{T}$\}\;
-  \While { $O_{T}$ $\notin$ $OutputSet$  and $queue !=null$}{
+  \While { all $O_{T}$ do not satisfied by $OutputSet$}{
      \ForEach{$S$ in $queue$}{
-      \uIf{$fullmatch(a \Rightarrow b)$$\wedge$ $(a \in OutputSet)$ $\wedge$ $(b \in I_{S})$ $\wedge$ $\mid fullmatch(a \Rightarrow b) \mid = \mid I_{S} \mid$}{    
-    		 \ForEach{$fullmatch(a \Rightarrow b)$}{
-    		$sim(a,b) \leftarrow$ query $IndexCache$\;
- 			$sm(a,b) \leftarrow$ $( type(a,b), sim(a,b))$\;
+      \uIf{all $I_{S}$ satisfied by $OutputSet$}{    
+    		 \ForEach{$I_{S}$}{
+		$sm(a \in Outputset, b \in I_{S}) \leftarrow$ query $Cache$\;
               }
-        $sm_{e} \leftarrow$ aggregate \{ $sm(a,b)$ \}\;
+        Calculate $sm_{}$\;
         $E \leftarrow$ add $e$\;
@@
 
-\section{Experiment Design}\label{experiment_design}
+\section{Experiment Study}\label{experiment_design}
 In this section, a quantitative evaluation approach is adopted in our experiment design.
@@
 
-\section{Results and Analysis}\label{results_analysis}
 \subsection{Comparison Test for Comprehensive Quality Evaluation Model and QoS Evaluation Model}\label{comparisonTest}
@@
 \end{table}
+
+\subsection{Further Discussion}\label{discuss1}
 

### 2017-03-28 paper.tex
update

@@
 
-The aim of web service composition considered in this paper is to automatically compose optimal solutions in considering both QoS and semantic matchmaking quality based on a user's request.
-The request is to provide inputs and obtain outputs.
-The resulting composition of this request is a composition solution with an optimal comprehensive quality in terms of semantic matchmaking quality and QoS.
-A motivating example of this problem is shown in Fig \ref{motivation}.
-The figure shows a DAG that represents a solution with four web services involved for a request $R$ as a composition task, where inputs of the task are \{$TravelDepartureDate$, $HomeCity$, $ConferenceCity$, $TravelReturnDate$ \} and outputs are \{$BusTicket$, $FlightTicket$, $TouristMap$, $HotelReservation$ \}.
-This is a classic example of travel planning problem for people who seek for booking services of airplanes, buses and hotels reservation, and also generating tourist maps for the conference city.
-The graph also contains edges that marked with connected outputs and inputs of two connected atomic services, which represent valid semantic matches that the outputs of a web service can be passed as the inputs of its successors.
+Our goal in this paper is to develop a PSO-based approach that can automatically produce composition services in the form of graph-based representation (e.g.
+DAG).
+The nodes in the DAG represent component services.
+On the other hand, the edge that connects any two component services in the DAG, e.g.
+$S_1->S_2$, indicates that the output information from service S1 will subsequently serve as the input information for service S2.
+Apparently, such output and input information must semantically match to ensure the correct execution of the DAG.
+Moreover, the overall service inputs and outputs associated with the DAG must satisfy the composition requirements provided by users.
 
-\begin{figure}[h]
-\centering
-\fbox{\includegraphics[scale=.25]{motivation.pdf}}
- \caption{ An example of a web service composition}
- \label{motivation}
-\end{figure}
-
-Although obtaining a correct combination of web service is essential, there are many ways to connect multiple web services chosen from a service repository.
-These web services provide different QoS in terms of availability, price, reliability and response time.
-Moreover, valid semantic matches between two connected web services could also have different matchmaking quality.
-For example, $Generate Map$ service produce $StreetMap$ which is considered to be a valid semantic match to $TouristMap$, but $Bus Service$ produce $BusTicket$ which is considered to be a better valid semantic match to $BusTicket$.
-The descriptions of these matched resources are captured in a ontology depicted in Fig .\ref{taxonomy}, where all the inputs and the outputs related to the web services are described for the travel planning problem discuss here.
-For example, the concept $Map$ and its sub-concept $urbanMap$ are assigned with a $touristMap$ instance and $streetMap$ instance respectively in Fig .\ref{taxonomy}.
-The valid semantic match is considered that an instance of $urban Map$ can be an instance of $Map$, but not vice versa.
-To demonstrate the motivation of proposing a comprehensive quality, we give a simple example here.
-The service $GenerateMap$ with a output ($StreetMap$) and a price (``6.72") in the web service composition can be replace by a service $GenerateTouristMap$ with a different output ($TouristMap$) and a different price (``16.87") available in the service repository.
-This composition solution results in a better semantic matchmaking quality, but price negatively contributes to the QoS.
-Therefore, to reach the optimal solutions automatically, we need to measure these changes to the solutions considering matchmaking quality and QoS simultaneously.
-
-\begin{figure}[h]
-\centering
-\fbox{\includegraphics[scale=.28]{taxonomy.pdf}}
- \caption{ An ontology of a travel planning domain}
- \label{taxonomy}
-\end{figure}
+In practice, many different DAGs can meet the given requirements but differ significantly in terms of QoS and semantic matchmaking quality.
+For example, in the classical travel planning context, during the process of building a DAG, a component service needs to be employed to obtain a travel map.
+Suppose that two optional services can be considered for this purpose.
+One service S1 can provide a street map at a price of 6.72.
+The other service S2 can provide a tourist map at a price of 16.87.
+Because in our DAG a tourist map is more desirable than a street map, service S2 clearly enjoys better semantic matchmaking quality but will have negative impact on the QoS of the DAG (i.e.
+the price is much higher).
+It can be easily imagined that similar problems can frequently occur while building the DAG for the travel planning problem or other web service composition problems.
+Due to this reason, aimed at achieving a good balance in between QoS and semantic matchmaking quality, our PSO-based service composition system will be further guided by a comprehensive quality model to be proposed in Section 4.
 
@@
 
-.
-
 \subsection{PSO-based approach algorithm}\label{POS-based_algomargin}
@@
 Third, all the service candidates are put in a queue and sorted according to their corresponding weight values in a descending order.
-Fourth, this sorted queue is used as one of the input of a forward decoding algorithm \ref{graph_building} to create a weighted DAG, this fitness value of this weighted DAG is the fitness value of the particle.
+Fourth, this sorted queue is used as one of the input of a forward decoding algorithm \ref{graph_building} to create a weighted DAG, this fitness value of this weighted DAG is the fitness value of the particle calculated by the comprehensive model discussed in Sect \ref{Comprehensive_Quality_Model}.
 \begin{algorithm}
@@
 
-This Algorithm  \ref{graph_building}is a forward graph graph buidling algorithm based on \cite{blum1997fast}.
-This algorthm take an input of the sorted service queues discussed above, and service queues with diferent order is possible to create different weighted DAGs as composition solutions.
-In additon.
+This Algorithm  \ref{graph_building} is a forward graph graph buidling algorithm based on \cite{blum1997fast}.
+This algorithm take one input as the sorted service queues from step 5 of Algorithm \ref{novelSteps}.
+If service queues are sorted with different service order, it is possible to create different corresponding weighted DAGs as composition solutions.
+In addition.
 $I_{T}$, $O_{T}$ and $Cache$ are also taken as inputs.
-Firstly, $Start$ and $End$ are added to V of WG initialization, $OutputSet$ is created with $I_{T}$.
-If all the inputs of first $S$ popped from $queue$ can be satisfied by provided outputs of $OutputSet$, this $S$ is added to $V$ and its outputs are added to $OutputSet$.
-Meanwhile, $sm_{e}$ is calcated based on the aggregation value of $sm(a, b)$
-
-Otherwise,  next $S$ popped from the $queue$ is to be considered. These steps are not stopped until all  $O_{T}$ can satisfied from $Outputset$ or queue is null.
-
-can lead to more services and edges connected to the graph, which should be removed at last.
+Firstly, $Start$ and $End$ are added to V of WG as an initialisation, and a $OutputSet$ is also created with $I_{T}$.
+If all the inputs $I_{S}$ of first popped  $S$ from $queue$ can be satisfied by provided outputs of $OutputSet$, this $S$ is added to $V$ and its outputs are added to $OutputSet$.
+Meanwhile, $e$ is created with its $sm_{e}$ calculated based on the aggregation value of all semantic matchmaking quality from each satisfied input of $S$.
+These steps are not stopped until all  $O_{T}$ can satisfied from $Outputset$ or queue is null.
+Consequently, this forward graph building technique could lead to more services and edges connected to the $WG$, which should be removed before $WG$ is returned.
 
@@
               }
-        Calculate $sm_{}$\;
-        $E \leftarrow$ add $e$\;
-        $V \leftarrow$ add $S$\;
+        $e \leftarrow$ calculate aggregated $sm_{e}$\;
+        $E$ add $e$\;
+        $V$ add $S$\;
         $OutputSet$ add \{$O_{S}$\}\;    
@@
 \hline
-\multicolumn{2}{c|}{WSC09}              & QoS Evaluation Model         &\shortstack{Comprehensive \\ Quality Evaluation Model} \\ \hline
-\multirow{2}{*}{Task1}  &$SM$   &0.537375 $\pm$ 0.026709               &0.557972 $\pm$ 0.009394 $\uparrow$ \\ \cline{2-4}
-                        &$QoS$  &0.557460 $\pm$ 0.015572               &0.560444 $\pm$ 0.016424                          \\ \hline
-\multirow{2}{*}{Task2}  &$SM$   &0.454383 $\pm$ 0.003287               &0.462974 $\pm$ 0.004232 $\uparrow$ \\ \cline{2-4} 
-                        &$QoS$  &0.479958 $\pm$ 0.001156 $\uparrow$    &0.477192 $\pm$ 0.002528 \\ \hline
-\multirow{2}{*}{Task3}  &$SM$   &0.553818 $\pm$ 0.008180               &0.609298 $\pm$ 0.005371 $\uparrow$   \\ \cline{2-4} 
-                        &$QoS$  &0.494004 $\pm$ 0.001322 $\uparrow$    &0.491262 $\pm$ 0.000862            \\ \hline
-\multirow{3}{*}{Task4}  &$SM$   &0.439757 $\pm$ 0.003728               &0.460369 $\pm$ 0.000002 $\uparrow$ \\ \cline{2-4} 
-                        &$QoS$  &0.484594 $\pm$ 0.001014 $\uparrow$    &0.473354 $\pm$ 0.004422  \\ \hline
-\multirow{3}{*}{Task5}  &$SM$   &0.457988 $\pm$ 0.006459               &0.463878 $\pm$ 0.001299 $\uparrow$           \\ \cline{2-4} 
-                        &$QoS$  &0.476378 $\pm$ 0.000480 $\uparrow$    &0.474970 $\pm$ 0.000656  \\ \hline                                                   
+\multicolumn{2}{c|}{WSC09}              & QoS Evaluation Model         &\shortstack{Comprehensive Quality \\ Model} \\ \hline
+\multirow{2}{*}{Task1}  &$SM$   &0.5373 $\pm$ 0.0267               &0.5580 $\pm$ 0.0094 $\uparrow$ \\ \cline{2-4}
+                        &$QoS$  &0.5574 $\pm$ 0.0156               &0.5604 $\pm$ 0.0164                          \\ \hline
+\multirow{2}{*}{Task2}  &$SM$   &0.4549 $\pm$ 0.0033               &0.4630 $\pm$ 0.0042 $\uparrow$ \\ \cline{2-4} 
+                        &$QoS$  &0.4800 $\pm$ 0.0012 $\uparrow$    &0.4772 $\pm$ 0.0025 \\ \hline
+\multirow{2}{*}{Task3}  &$SM$   &0.5538 $\pm$ 0.0082               &0.6093 $\pm$ 0.0054 $\uparrow$   \\ \cline{2-4} 
+                        &$QoS$  &0.4940 $\pm$ 0.0013 $\uparrow$    &0.4913 $\pm$ 0.0009            \\ \hline
+\multirow{3}{*}{Task4}  &$SM$   &0.4398 $\pm$ 0.0037               &0.4604 $\pm$ 0.0000 $\uparrow$ \\ \cline{2-4} 
+                        &$QoS$  &0.4845 $\pm$ 0.0010 $\uparrow$    &0.4734 $\pm$ 0.0044  \\ \hline
+\multirow{3}{*}{Task5}  &$SM$   &0.4580 $\pm$ 0.0065               &0.4639 $\pm$ 0.0013 $\uparrow$           \\ \cline{2-4} 
+                        &$QoS$  &0.4764 $\pm$ 0.0005 $\uparrow$    &0.4750 $\pm$ 0.0007  \\ \hline                                                   
 \end{tabular}
@@
 \hline
-\multicolumn{1}{c|}{Dataset} & PSO-based approach & GP-based approach  \\ \hline
-WSC09 01                     &0.559207 $\pm$ 0.012780  $\uparrow$   &0.520659 $\pm$ 0.020758           \\ \hline
-WSC09 02                     &0.470083 $\pm$  0.001106 $\uparrow$   &0.459681 $\pm$  0.002874          \\ \hline
-WSC09 03                     & 0.550396 $\pm$ 0.012780              &0.567915 $\pm$ 0.023447 $\uparrow$   \\ \hline
-WSC09 04                     & 0.468942 $\pm$ 0.001670  $\uparrow$  &0.431704 $\pm$ 0.009774            \\ \hline
-WSC09 05                     & 0.469424 $\pm$ 0.000800  $\uparrow$  &0.245222 $\pm$ 0.036885            \\ \hline
+\multicolumn{1}{c|}{WSC09} & PSO-based approach & GP-based approach  \\ \hline
+Task 1                     &0.559207 $\pm$ 0.012780  $\uparrow$   &0.520659 $\pm$ 0.020758           \\ \hline
+Task 2                     &0.470083 $\pm$  0.001106 $\uparrow$   &0.459681 $\pm$  0.002874          \\ \hline
+Task 3                     & 0.550396 $\pm$ 0.012780              &0.567915 $\pm$ 0.023447 $\uparrow$   \\ \hline
+Task 4                     & 0.468942 $\pm$ 0.001670  $\uparrow$  &0.431704 $\pm$ 0.009774            \\ \hline
+Task 5                     & 0.469424 $\pm$ 0.000800  $\uparrow$  &0.245222 $\pm$ 0.036885            \\ \hline
 \end{tabular}

### 2017-03-28 paper.tex
up

@@
 \title{Comprehensive Quality Awareness Automated Semantic Web Service Composition}
-\author{Chen Wang, Hui Ma, and Aaron Chen}
+\author{Chen Wang, Hui Ma, Aaron Chen and Sven Hartmann}
 \institute{School of Engineering and Computer Science,
@@
 
-We utilise benchmark dataset web service challenge 2009 (WSC09) \cite{kona2009wsc} to perform the evaluation.
-WSC09 provides problems with five tasks corresponding to variable number of services, and ontologies.
-Therefore, it is a challenge dataset for measuring the scalability of our quality evaluation model.
-Table \ref{wsc09datasetTable} presents the features of the WSC’09 dataset.
-The number of concepts, individuals in the ontology and services in each data set is shown in the second, third, fourth column respectively.
-Also, we extend all the datasets with QoS attributes from service providers to enable our evaluation.
-
-\begin{table}[]
-\centering
-\caption{Features of the WSC09 datasets}
-\label{wsc09datasetTable}
-\begin{tabular}{l|l|l|l}
-\hline
-\multicolumn{1}{c|}{Dataset} & No.Concept & No.Individual & No.Service \\ \hline
-WSC09 01                     & 1578       &3102           &572      \\ \hline
-WSC09 02                     & 12388      &24815          &4129      \\ \hline
-WSC09 03                     & 18573      &37316          &8138      \\ \hline
-WSC09 04                     & 18673      &37324          &8301      \\ \hline
-WSC09 05                     & 31044      &62132          &15211    \\ \hline
-\end{tabular}
-\end{table}
+Web service challenge 2009 (WSC09) \cite{kona2009wsc} is a benchmark dataset consisting of five composition tasks that associated with an increasing number of services, and concepts in ontologies.
+An augmented version of WSC09 is utilised including QoS attributes for services, this version of WSC09 dataset is used in \cite{ma2015hybrid,da2016genetic}
 
@@
 Therefore, $w_{1}$ and $w_{2}$ are set equally to 0.25, and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly.
-The $mt_{p}$ is set to 1 (Exact match) and 0.75 (Plugin).
+The $type(a,b)$ is set to 1 ($Exact$) and 0.75 ($Plugin$) according to \cite{lecue2009optimizing}.
 In general, weight settings and parameter match type quality are decided by users' preferences.
+
+\subsection{Comparison Test for GP-based approach and PSO-based approach}\label{comparisonTestWithGP}
+To evaluate the performance of our proposed PSO-based approach, we compare one GP-based approach  \cite{ma2015hybrid} with our PSO-based method.
+we consider the links between child nodes and parent nodes as semantic web service links for measuring  semantic matchmaking quality.
+Therefore, we evaluate both semantic matchmaking quality and QoS simultaneously using our proposed comprehensive quality model.
+To make a fair comparison with our PSO-based, we consider the same number of evaluations (3000 times) used in our PSO-based approach, we set the parameters settings for the GP-based approach using 30 individuals and 100 generations.
+
+The first column of the table \ref{meanFitness} shows five tasks from WSC09 Dataset.
+The second and third column of the table \ref{meanFitness} show the orginal service repository size and shrunk service repository size after the greedy search respectively regarding the five tasks for the initialisation discussed in step 2 SubSect.\ref{PSO_based_approach}.
+These significant decreased number of services demonstrate that the researching space is effectively reduced.
+The fourth and fifth column of the table \ref{meanFitness} show the mean fitness values of 30 independent runs accomplished by two methods.
+We employ statistical analysis to test the significant differences in mean fitness value.
+The results show that the PSO-based approach performs better in four of five tasks (all the p-values are consistently smaller than 0.01).
+
+\begin{table}[]
+\centering
+\caption{Mean fitness results for comparing GP-based approach}
+\label{meanFitness}
+\begin{tabular}{l|l|l|l|l}
+\hline
+\multicolumn{1}{c|}{WSC09} &Original $SR$  &Shrunk $SR$   &PSO-based approach & GP-based approach  \\ \hline
+Task 1                     &572            &80    &0.5592 $\pm$ 0.0128  $\uparrow$  &0.5207 $\pm$ 0.0208           \\ \hline
+Task 2                     &4129           &140   &0.4701 $\pm$ 0.0011  $\uparrow$  &0.4597 $\pm$ 0.0029          \\ \hline
+Task 3                     &8138           &153   &0.5504 $\pm$ 0.0128              &0.5679 $\pm$ 0.0234 $\uparrow$   \\ \hline
+Task 4                     &8301           &330   &0.4690 $\pm$ 0.0017  $\uparrow$  &0.4317 $\pm$ 0.0097            \\ \hline
+Task 5                     &15211          &237   &0.4694 $\pm$ 0.0008  $\uparrow$  &0.2452 $\pm$ 0.0369            \\ \hline
+\end{tabular}
+\end{table}
 
@@
 
-\subsection{Comparison Test for GP-based approach and PSO-based approach}\label{comparisonTestWithGP}
-To evaluate the performance of our proposed PSO-based approach, we compare one GP-based approach  \cite{ma2015hybrid} with our PSO-based method.
-we consider the links between child nodes and parent nodes as semantic web service links for measuring  semantic matchmaking quality.
-Therefore, we evaluate both semantic matchmaking quality and QoS simultaneously using our proposed comprehensive quality model.
-To make a fair comparison with our PSO-based, we consider the same number of evaluations (3000 times) used in our PSO-based approach, we set the parameters settings for the GP-based approach using 30 individuals and 100 generations.
-
-The Table \ref{meanFitness} shows the mean fitness values of 30 independent runs accomplished by two methods.
-We employ statistical analysis to test the significant differences in mean fitness value.
-The results show that the PSO-based approach performs better in four of five tasks (all the p-values are consistently smaller than 0.01).
-
-\begin{table}[]
-\centering
-\caption{Mean fitness results for comparing GP-based approach}
-\label{meanFitness}
-\begin{tabular}{l|l|l}
-\hline
-\multicolumn{1}{c|}{WSC09} & PSO-based approach & GP-based approach  \\ \hline
-Task 1                     &0.559207 $\pm$ 0.012780  $\uparrow$   &0.520659 $\pm$ 0.020758           \\ \hline
-Task 2                     &0.470083 $\pm$  0.001106 $\uparrow$   &0.459681 $\pm$  0.002874          \\ \hline
-Task 3                     & 0.550396 $\pm$ 0.012780              &0.567915 $\pm$ 0.023447 $\uparrow$   \\ \hline
-Task 4                     & 0.468942 $\pm$ 0.001670  $\uparrow$  &0.431704 $\pm$ 0.009774            \\ \hline
-Task 5                     & 0.469424 $\pm$ 0.000800  $\uparrow$  &0.245222 $\pm$ 0.036885            \\ \hline
-\end{tabular}
-\end{table}
-
 \section{Conclusion}\label{conclusion}

### 2017-03-29 paper.tex
up

@@
 It can be easily imagined that similar problems can frequently occur while building the DAG for the travel planning problem or other web service composition problems.
-Due to this reason, aimed at achieving a good balance in between QoS and semantic matchmaking quality, our PSO-based service composition system will be further guided by a comprehensive quality model to be proposed in Section 4.
+Due to this reason, aimed at achieving a good balance in between QoS and semantic matchmaking quality, our PSO-based service composition system will be further guided by a comprehensive quality model to be proposed in 4.
 
@@
 The function value of 1 means the best comprehensive quality and 0 means the worst.
-For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the function value falls within the range from 0 to 1 using Formula (\ref{equation9}) and (\ref{equation10}), where the maximum and minimum value of $A$, $R$, $T$, and $C$ are calculated by all web services candidates to the composition task, which are generated by a greedy search discussed in Sect.\ref{PSO_based_approach}.
+For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the function value falls within the range from 0 to 1 using Formula (\ref{equation9}) and (\ref{equation10}), where the maximum and minimum value of $A$, $R$, $T$, and $C$ are calculated by all web services candidates to the composition task, which are generated by a greedy search discussed in \ref{PSO_based_approach}.
 $MT$ and $S$ are using a bound from 0 to 1.
@@
 
-PSO has shown its promising in solving combinatorial optimisation problems, which is considered to an easier way to maintain the correctness of solutions comparing to GP-based approaches that often require repairing or penalising the solutions \cite{da2016particle}.
-Therefore, we will employ a PSO-based approach to comprehensive quality-aware automated semantic web service composition consisting a forward decoding process.
+PSO has shown promise in solving combinatorial optimisation problems, and considered an easier way to maintain the correctness of solutions compared to GP-based approaches that often require repairing the solutions \cite{da2016particle}.
+Therefore, we employ a PSO-based approach to comprehensive quality-aware automated semantic web service composition.
 Fig.
@@
 
-Step 1: The composition process is triggered by a composition task, which is clearly defined in Subsection \ref{problemDes}.
+Step 1: The composition process is triggered by a composition task, which is clearly defined in \ref{problemDes}.
 
 Step 2: This composition task is used to discover all task-related service candidates using a greedy search adopted from \cite{ma2015hybrid}.
-During this greedy search, an ontology-based cache ($Cache$) is initialised, which stores the concept similarities of inputs and outputs of task-related candidates.
+This greedy search algorithm keeps adding outputs of the invoked services as available outputs (initialised with $I_{T}$) , and these available outputs are used to discover task-related services from a service repository and updated with the outputs of these discovered services.
+This operation is repeated until no service is satisfied by the available outputs.
+This greedy search contributes to a shrunken service repository.
+During the greedy search, an ontology-based cache ($cache$) is initialised that stores the concept similarities of potentially matched inputs and outputs of task-related candidates.
+This $cache$ is also used to check whether services can be invoked by satisfying their input-related concepts with provided output-related concepts.
 
-Step 3 and Step 4: These two steps follow the stardard PSO steps \cite{shi2001particle} except some differences that lie in  particles initialisation and decoding process.
-These two differences are related to sort a service queue using a serivce-to-index mapping for a particle' position vectors and evaluate the fitness of a particle after decoding this serivce queue into a weighted DAG respectively, which are further addressed in Algorithm \ref{novelSteps} and \ref{graph_building} in SubSect \ref{POS-based_algomargin}.
+Step 3 and Step 4: These two steps follow the standard PSO steps \cite{shi2001particle} except for some differences in particles mapping and decoding processes.
+In particular, these two differences are related to sorting a created service queue using serivce-to-index mapping for a particle' position vectors and evaluating the fitness of a particle after decoding this serivce queue into a weighted DAG respectively.
+Those differences are further addressed in Algorithms \ref{novelSteps} and \ref{graph_building} in \ref{POS-based_algomargin}.
 
 \subsection{PSO-based approach algorithm}\label{POS-based_algomargin}
-The overall algorithm investigated here is made up of the PSO-based web service composition algorithm \ref{novelSteps} and the decoding algorithm \ref{graph_building}.
-In algorithm \ref{novelSteps}, the  steps $4$, $5$, $6$ and $7$ are different steps from those of stardard PSO.
-First, each particle's position size is determined by the size of task-related service candidates generated by a greedy search.
-This greedy search algorithm keeps adding outputs of the evocable services as available outputs, and these available outputs are used to discovery task-related services from service repository and be updated with the outputs of these discovered services.
-This loop process does not stop until no service is satisfied by the available outputs.
-Second, each service candidate is mapped to an index of a particle’s position vector, where each vector have a weight value that falls between 0.0 and 1.0.
-This a service-to-index mapping for position vectors discussed in Step 3 in SubSect \ref{PSO_based_approach}.
-Third, all the service candidates are put in a queue and sorted according to their corresponding weight values in a descending order.
-Fourth, this sorted queue is used as one of the input of a forward decoding algorithm \ref{graph_building} to create a weighted DAG, this fitness value of this weighted DAG is the fitness value of the particle calculated by the comprehensive model discussed in Sect \ref{Comprehensive_Quality_Model}.
+The overall algorithm investigated here is made up of a PSO-based web service composition algorithm \ref{novelSteps} and a decoding algorithm \ref{graph_building}.
+In Algorithm \ref{novelSteps}, the  steps $4$, $5$, $6$ and $7$ are different from those of stardard PSO: In step 4, the size of task-related service candidates generated by a greedy search determines the size of each particle's position, and each candidate in a created service candidates queue is mapped to an index of a particle’s position vectors, where each vector has a weight value between 0.0 and 1.0.
+In step 5, all the task-related service candidates in the queue are sorted according to their corresponding weight values in descending order.
+In step 6, this sorted queue is used as one of the inputs of the forward decoding algorithm \ref{graph_building} to create a weighted DAG.
+In step 7, this fitness value of this weighted DAG is the fitness value of the particle calculated by the comprehensive model discussed in \ref{Comprehensive_Quality_Model}.
 \begin{algorithm}
@@
      \ForEach{particles in the swarm}{
-     Map service candidates to particle's position vector\;
-     Create a service queue and sort it by position vectors' weights\;
-     Create the service into a weighted DAG \;
-	 Calculate the $Weighted DAG$ fitness value\;
+     Create a service candidates queue and map service candidates to a particle's position vectors\;
+     Sort the service queue by position vectors' weights\;
+     Create a weighted DAG from the service queue ( Algorithm\ref{graph_building}) \;
+     Calculate the Weighted DAG fitness value\;
 
@@
 
-This Algorithm  \ref{graph_building} is a forward graph graph buidling algorithm based on \cite{blum1997fast}.
-This algorithm take one input as the sorted service queues from step 5 of Algorithm \ref{novelSteps}.
-If service queues are sorted with different service order, it is possible to create different corresponding weighted DAGs as composition solutions.
+Algorithm  \ref{graph_building} is a forward graph buidling algorithm based on \cite{blum1997fast}.
+This algorithm take one input, a sorted service queue from step 5 of Algorithm \ref{novelSteps}.
+If service queues are sorted resulting in different service order, it is possible to create different corresponding weighted DAGs as composition solutions.
 In addition.
-$I_{T}$, $O_{T}$ and $Cache$ are also taken as inputs.
-Firstly, $Start$ and $End$ are added to V of WG as an initialisation, and a $OutputSet$ is also created with $I_{T}$.
-If all the inputs $I_{S}$ of first popped  $S$ from $queue$ can be satisfied by provided outputs of $OutputSet$, this $S$ is added to $V$ and its outputs are added to $OutputSet$.
-Meanwhile, $e$ is created with its $sm_{e}$ calculated based on the aggregation value of all semantic matchmaking quality from each satisfied input of $S$.
-These steps are not stopped until all  $O_{T}$ can satisfied from $Outputset$ or queue is null.
+$I_{T}$, $O_{T}$ and $cache$ are also taken as the inputs.
+Firstly, $Start$ and $End$ are added to $V$ of $WG$ as an initialisation, and $OutputSet$ is also created with $I_{T}$.
+If all the inputs $I_{S}$ of the first popped  $S$ from $queue$ can be satisfied by provided outputs from $OutputSet$.
+This $S$ is added to $V$ and its outputs are added to $OutputSet$, and $S$ is removed from $queue$.
+Meanwhile, $e$ is created with its $sm_{e}$ calculated based on the aggregation value of all semantic matchmaking qualities from each satisfied input of $S$.
+These steps are repeated until all  $O_{T}$ can be satisfied by $Outputset$ or the service queue is $null$.
 Consequently, this forward graph building technique could lead to more services and edges connected to the $WG$, which should be removed before $WG$ is returned.
@@
 In this section, a quantitative evaluation approach is adopted in our experiment design.
-The objectives of the evaluation are to $(1)$ measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach; and $(2)$ compare solutions generated by a recent QoS-ware evaluation approach \cite{ma2015hybrid,da2016genetic} with our evaluation method proposed in the paper; and $(3)$ compare our PSP-based method with one existing GP-based approach \cite{ma2015hybrid}.
+Two objectives of this evaluation are to: $(1)$ measure the effectiveness of our PSO-based approach.
+To do this, we compare our PSO-based method with one existing GP-based approach \cite{ma2015hybrid}.
+$(2)$ measure the effectiveness of our proposed comprehensive quality model.
+To do this, we compare a widely used QoS model in QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol} with our comprehensive quality model using our proposed PSO-based approach.
 
-Web service challenge 2009 (WSC09) \cite{kona2009wsc} is a benchmark dataset consisting of five composition tasks that associated with an increasing number of services, and concepts in ontologies.
-An augmented version of WSC09 is utilised including QoS attributes for services, this version of WSC09 dataset is used in \cite{ma2015hybrid,da2016genetic}
+An augmented version of Web service challenge 2009 (WSC09) used in \cite{ma2015hybrid,da2016genetic} including QoS attributes is used for our experiment.
+WSC09 is a benchmark dataset consisting of five composition tasks that associated with an increasing number of services, and concepts in ontologies.
 
-The parameters were chosen based on general settings from \cite{shi2001particle} for our PSO-based approach, In particular, PSO population size is 30 with 100 generations.
+The parameters are chosen based on the settings from \cite{shi2001particle} for our PSO-based approach, In particular, PSO population size is 30 with 100 generations.
 We run 30 times independently for each dataset.
 We configure weight of fitness function to properly balance functional side and nonfunctional side.
-Therefore, $w_{1}$ and $w_{2}$ are set equally to 0.25, and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly.
-The $type(a,b)$ is set to 1 ($Exact$) and 0.75 ($Plugin$) according to \cite{lecue2009optimizing}.
+Therefore, $w_{1}$ and $w_{2}$ are set equally to 0.25, and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125.
+The returned value of $type(a,b)$ is set to 1 ($Exact$) and 0.75 ($Plugin$) according to \cite{lecue2009optimizing}.
 In general, weight settings and parameter match type quality are decided by users' preferences.
@@
 \subsection{Comparison Test for GP-based approach and PSO-based approach}\label{comparisonTestWithGP}
-To evaluate the performance of our proposed PSO-based approach, we compare one GP-based approach  \cite{ma2015hybrid} with our PSO-based method.
-we consider the links between child nodes and parent nodes as semantic web service links for measuring  semantic matchmaking quality.
-Therefore, we evaluate both semantic matchmaking quality and QoS simultaneously using our proposed comprehensive quality model.
-To make a fair comparison with our PSO-based, we consider the same number of evaluations (3000 times) used in our PSO-based approach, we set the parameters settings for the GP-based approach using 30 individuals and 100 generations.
+To evaluate the effectiveness of our proposed PSO-based approach, we compare one recent GP-based approach \cite{ma2015hybrid} with our PSO-based method.
+The semantic matchmaking quality of this GP-based approach is easy to evaluated considering measuring links between parent nodes and children nodes.
+Therefore, we evaluate both semantic matchmaking quality and QoS simultaneously for that GP-based approach using the proposed comprehensive quality model.
+To make a fair comparison, we consider the same number of evaluations (3000 times) used in our PSO-based approach.
+We set the parameters' settings of that GP-based approach as 30 individuals and 100 generations, it is considered to be proper settings refering to \cite{da2015gp}.
 
-The first column of the table \ref{meanFitness} shows five tasks from WSC09 Dataset.
-The second and third column of the table \ref{meanFitness} show the orginal service repository size and shrunk service repository size after the greedy search respectively regarding the five tasks for the initialisation discussed in step 2 SubSect.\ref{PSO_based_approach}.
-These significant decreased number of services demonstrate that the researching space is effectively reduced.
-The fourth and fifth column of the table \ref{meanFitness} show the mean fitness values of 30 independent runs accomplished by two methods.
-We employ statistical analysis to test the significant differences in mean fitness value.
-The results show that the PSO-based approach performs better in four of five tasks (all the p-values are consistently smaller than 0.01).
+The first column of Table \ref{meanFitness} shows five tasks from WSC09 Dataset.
+The second and third column of Table \ref{meanFitness} show the orginal service repository size before the greedy search and shrunk service repository size after the greedy search respectively regarding the five tasks.
+This greedy search helps reducing the repository size by considering only task-related service candidates, which also contributes to a significant reduced researching space.
+The fourth and fifth column of Table \ref{meanFitness} show the mean fitness values of 30 independent runs accomplished by two methods.
+We employ independent-samples T tests to test the significant differences in mean fitness value.
+The results show that the PSO-based approach outperformes the existing GP-based approach in most cases except task 3 (all the p-values are consistently smaller than 0.01).
+In task 5, PSO-based approach performs significantly better than GP-based approach in finding optimal solutions.
+It may refer to that GP-based approach is stuck in the local optimal due to a very large searching space of our composition problem, but PSO-based approach requres a decoding process, and small changes in a sorted queue might lead to a varying decoded solutions.
+Therefore, PSO-based approach is considered to be hard to be stuck in the local optimal for our composition problem.
 
@@
 \hline
-\multicolumn{1}{c|}{WSC09} &Original $SR$  &Shrunk $SR$   &PSO-based approach & GP-based approach  \\ \hline
+\multicolumn{1}{c|}{WSC09} &Original $SR$  &Shrunken $SR$   &PSO-based approach & GP-based approach  \\ \hline
 Task 1                     &572            &80    &0.5592 $\pm$ 0.0128  $\uparrow$  &0.5207 $\pm$ 0.0208           \\ \hline
@@
 In addtion, $Inst658772240$ is a required parameter of the $end$ vertice as one of composition task outputs, which is related to concept $Con2113572083$.
-There exist $Inst582785907$ $\in$ $Con2037585750$ $\sqsubseteq_{3}$ $Inst658772240$ $\in$ $Con2113572083$ for $e_4$ in $WG(1)$ and $Inst795998200$ $\in$ $Con103314376$ $\sqsubseteq_{2}$ $Inst658772240$ $\in$ $Con2113572083$ for $e_4$ in $WG(2)$.
-Therefore, 2-level Subsumes is closer than 3-level Subsumes, $Inst795998200$ is closer to user's required output $Inst658772240$ compared with $Inst582785907$.
+Obviouly,  $Inst795998200$ is closer to user's required output $Inst658772240$ compared to $Inst582785907$.
 

### 2017-03-29 paper.tex
update

@@
 
-A recent widely used QoS Evaluation Model, $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$, where $\sum_{i=1}^{4} w_i = 1$, is used for QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol}.
-We employ this QoS evluation model and our proposed comprehensive quality evluation model using our proposed PSO-based approach for searching for optimal solutions.
-To analyse the differences in optimal solutions found by these two evaluation model, we recorded and compared the different mean values of $SM$ (consisiting of $MT$ and $S$), $QoS$(consisting of $A$, $R$, $T$ and $C$) at the 100th generation of 30 runs.
-To make a sense of the comparison, all these recorded values are normalised from 0 to 1, and compared using statistical analysis in in Table \ref{decisionTable}.
+Recently, a QoS Evaluation Model, $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$, where $\sum_{i=1}^{4} w_i = 1$, is widely used for QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol}.
+This QoS evluation model is compared to our proposed comprehensive quality evluation model using our proposed PSO-based approach for measuring the effectiveness of our proposed comprehensive quality model.
+To analyse the differences in optimal solutions found by these two evaluation models, we recorded and compared the different mean values of $SM$ (consisiting of $MT$ and $S$), $QoS$(consisting of $A$, $R$, $T$ and $C$) after 100 generations.
+To make a sense of the comparison, all these recorded values are normalised from 0 to 1, and compared using independent-samples T tests in Table \ref{decisionTable}.
 
 We observe an interesting pattern from Table \ref{decisionTable}.
-The mean values of $QoS$ using QoS evaluation model are significantly higher than those using comprehensive quality evaluation model for Task 2, 3, 4 and 5,  but the mean value of $SM$ using comprehensive quality evaluation model are consistently significantly higher than those using QoS evaluation model for all tasks with a slight trade-off in $QoS$.
+The mean values of $QoS$ using QoS evaluation model are significantly higher than those using comprehensive quality evaluation model for Tasks 2, 3, 4 and 5.
+However, the mean value of $SM$ using the comprehensive quality evaluation model are significantly higher than those using the QoS evaluation model, while a slight trade-off in $QoS$ are observed in all tasks.
 
@@
 
-To better understand a better semantic matchmaking quality with a slight trade-off in the opitmal solutions using comprehensive quality evaluation model, we demonstrate the optimal solutions using task 3 as an example.
+To determine the importance of achieving a good comprehensive quality at the expense of slightly reduced QoS, we demonstrate the best solutions identified by our approach using task 3 as an example.
 Fig.
-\ref{comparisontest} $(1)$ and $(2)$ show two weighted DAGs as best solutions found by employing QoS evaluation model and comprehensive quality evaluation model respectively.
-Two approaches generate exactly the same service workflow structure, but some service vertices and edges denoted in red are different.
-To better understand these differences, we list the overall semantic matchmaking quality $SM$,  overall $QoS$ and semantic matchmaking quality associated to each edge ($sm_{e_1}$ to $sm_{e_4}$) for the two weighted DAGs in Fig.
-\ref{comparisontest} $(3)$, where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) for the listed qualities using our comprehensive quality evalutaion model.
+\ref{comparisontest} $(1)$ and $(2)$ show two weighted DAGs obtained by employing the QoS evaluation model and the comprehensive quality evaluation model respectively.
+Both weighted DAGs have exactly the same service workflow structure, but some service vertices and edges denoted in red are different.
+To better understand these differences, we list the overall semantic matchmaking quality $SM$,  overall $QoS$ and semantic matchmaking quality associated to each edge ($sm_{e_1}$ to $sm_{e_4}$) in Fig.
+\ref{comparisontest} $(3)$, where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) of the listed qualities for our comprehensive quality evalutaion model.
 Therefore, an overall gain 0.1433 is calculated from a sum of a $SM$ gain (0.1467) and $QoS$ loss (-0.0034).
 Consequently, our comprehensive evaluation model acheive a desirable trade-off in considering both $SM$ and $QoS$.
-To explain the value of $SM$ gain, we pick up $e_4$ that is associated with a smallest $\Delta Q$.
+To explain the value of $SM$ gain, we pick up $e_4$ that is associated with the smallest $\Delta Q$.
 The $e_4$ of $WG(1)$ using QoS evaluation model and $WG(2)$ using comprehensive quality model has two different source service vertices $Ser1640238160$ and $Ser947554374$ respectively,  and the same $end$ vertices.
@@
 \includegraphics[scale=.29]{comparisontest.pdf}}}
- \caption{An example of comparision to optimal solutions using Task 3 for QoS evaluation model and comprehensive evluation model.}
+ \caption{An example of comparision to optimal solutions using Task 3 for QoS evaluation model and comprehensive quality evluation model.}
  \label{comparisontest}

### 2017-03-29 paper.tex
up

@@
 QoS optimisation aims to optimise the non-functional requirements of service users, e.g., minimum cost, maximal reliability.
-Many scholars have looked into QoS optimisation problems in QoS-aware web service composition, applying AI planning and Evolutionary Computation techniques.
 To meet users' requirements, one often needs to consider both semantic matchmaking quality and QoS simultaneously.
@@
 Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS simultaneously with an aim of achieving a more desirable trade-off in consideration of both sides.
-Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model, where PSO optimise a queue of task related services that is decoded into composition solutions.
-We compare proposed comprehensive quality model with one promising QoS model, and also compare the effectiveness of PSO-based method with one recent GP-based method using comprehensive quality model.
+Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model, where PSO optimise a queue of task-related services that is decoded into composition solutions.
+We compare the effectiveness of PSO-based method with one recent GP-based method using the proposed comprehensive quality model, and also compare the effectiveness of our proposed comprehensive quality model with one promising QoS model.
 
@@
 We will propose a PSO-based service composition approach with explicit support for our proposed quality model.
-We will achieve three objectives in this work as follows:
+We will achieve three objectives in this work:
 
@@
 To do this, we compare our PSO-based method with one existing GP-based approach \cite{ma2015hybrid}.
-$(2)$ measure the effectiveness of our proposed comprehensive quality model.
-To do this, we compare a widely used QoS model in QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol} with our comprehensive quality model using our proposed PSO-based approach.
+$(2)$ measure the effectiveness of our proposed comprehensive quality model for achieving desired balance of semantic matchmaking quality and QoS.
+To do this, we compare a widely used QoS model in QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol} with our comprehensive quality model using our PSO-based approach.
 
 An augmented version of Web service challenge 2009 (WSC09) used in \cite{ma2015hybrid,da2016genetic} including QoS attributes is used for our experiment.
-WSC09 is a benchmark dataset consisting of five composition tasks that associated with an increasing number of services, and concepts in ontologies.
+WSC09 is a benchmark dataset consisting of five composition tasks.
+These tasks are associated with an increasing number of services, and concepts in ontologies.
 
@@
 We run 30 times independently for each dataset.
-We configure weight of fitness function to properly balance functional side and nonfunctional side.
+We configure the weights of fitness function to properly balance functional side and nonfunctional side.
 Therefore, $w_{1}$ and $w_{2}$ are set equally to 0.25, and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125.
@@
 In task 5, PSO-based approach performs significantly better than GP-based approach in finding optimal solutions.
-It may refer to that GP-based approach is stuck in the local optimal due to a very large searching space of our composition problem, but PSO-based approach requres a decoding process, and small changes in a sorted queue might lead to a varying decoded solutions.
-Therefore, PSO-based approach is considered to be hard to be stuck in the local optimal for our composition problem.
+It may refer to that GP-based approach is stuck in the local optimal due to a very large searching space in Task 5, but PSO-based approach requres decoding processes of sorted queues, where small changes of the queues might lead to different decoded solutions.
 
@@
 \label{meanFitness}
-\begin{tabular}{l|l|l|l|l}
+\begin{tabular}{c|c|c|l|l}
 \hline
@@
 \label{decisionTable}
-\begin{tabular}{l|l|l|l}
+\begin{tabular}{c|l|l|l}
 \hline
-\multicolumn{2}{c|}{WSC09}              & QoS Evaluation Model         &\shortstack{Comprehensive Quality \\ Model} \\ \hline
+\multicolumn{2}{c|}{WSC09}              & \shortstack{QoS \\ Evaluation Model}         &\shortstack{Comprehensive Quality \\ Evaluation Model} \\ \hline
 \multirow{2}{*}{Task1}  &$SM$   &0.5373 $\pm$ 0.0267               &0.5580 $\pm$ 0.0094 $\uparrow$ \\ \cline{2-4}

### 2017-03-29 paper.tex
update

@@
 
-\textit{Web service composition} pertains to a chain of multiple web services to provide a value-added composition service that accommodates customers' arbitrarily complex requirements.
+\textit{Web service composition} pertains to a chain of multiple web services to provide a value-added composition service that accommodates customers' complex requirements.
 This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems.
-Due to the increasing number of large-scale enterprise applications, the number of Web services has increased substantially and unprecedentedly.
-Therefore, \textit{manual and semi-automated web service compositions} are considered to be less efficient while \textit{automated web service composition} demands less human intervention, less time consumption, and high productivity.
 
@@
 The syntactic dimension is covered by the XML-based technologies (such as $WSDL$, $SOAP$).
-The semantic dimension enables a better understanding and collaboration through ontology-based semantics \cite{o2005review}.
-There are many ontology languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}, which make ``machine understanding'' possible through identifying and matching semantic similarities in input/output parameters of web services.
+The semantic dimension enables a better collaboration through ontology-based semantics.
+There are many ontology languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}.
 The second challenge is related to finding optimised solutions in QoS.
-This problem gives birth to \textit{QoS-aware service composition} that aims to find composition solutions associated with a single optimised QoS value.
+This problem gives birth to \textit{QoS-aware service composition} that aims to find composition solutions with optimised QoS.
 
 Existing works on service composition focus mainly on addressing only one challenge above.
-Among these works, huge efforts have been devoted to optimise the quality of compositions under a pre-defined abstract workflow.
-This is generally considered as a \textit{semi-automated Web service composition} approach \cite{bahadori2009optimal,parejo2008qos}.
-Meanwhile, many research works consider the NP-hard problem of generating a composition plan automatically in discovering and selecting suitable web services \cite{moghaddam2014service}.
+In these works, huge efforts have been devoted to optimise the quality of compositions under a pre-defined abstract workflow.
+This is generally considered as a \textit{semi-automated Web service composition} approach \cite{parejo2008qos}.
+Meanwhile, many research works consider a NP-hard problem of generating a composition plan automatically in discovering and selecting suitable web services \cite{moghaddam2014service}.
 \textit{Semantic web services composition} is distinguished from the syntactic service composition, the resources of semantic web services are described semantically to enable a better interoperability for chaining web services.
 In the past few years, substantial works have been done on semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated}.
-However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously to achieve a desired balance.
+However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously to achieve a desirable balance.
 
 The overall goal of this paper is to \textit{develop a general comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}.
-Particularly, this paper extends existing works of QoS-aware service composition by considering jointly optimise QoS and semantic matchmaking quality based on our proposed comprehensive quality model.
-Particle Swarm Optimisation (PSO) has shown its promise in searching for near-optimised service composition solutions \cite{da2016particle}.
+Particularly, this paper extends existing works of QoS-aware service composition by considering jointly optimise QoS and semantic matchmaking quality using our proposed comprehensive quality model.
+Particle Swarm Optimisation (PSO) has shown promise in searching for near-optimised service composition solutions \cite{da2016particle}.
 We will propose a PSO-based service composition approach with explicit support for our proposed quality model.
@@
 \begin{enumerate}
- \item To propose a general comprehensive quality model that addresses QoS and semantic matchmaking quality simultaneously to achieve a desirable balance on both sides.
+ \item To propose a general comprehensive quality model that addresses QoS and semantic matchmaking quality simultaneously with a desirable balance on both sides.
 
- \item To propose a PSO-based service composition approach that utilises the proposed comprehensive quality model.
-To do that we optimise a queue of web services by evaluating the comprehensive quality of its decoded representations.
+ \item To propose a PSO-based service composition approach using the proposed comprehensive quality model.
+To do that we optimise a service candidates queue by evaluating the comprehensive quality of its decoded representation.
 
- \item To address a desirable balance that can be achieved using our comprehensive quality model, we conduct experiments to compare our proposed model with one widely used QoS model using PSO-based approach.
-In addition, to evaluate the effectiveness of our PSO-based approach,  we also compare one recent GP approach \cite{ma2015hybrid} with our PSO-based approach using our proposed model.
-Both comparisons utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}
-
+ \item To address the effectiveness of our PSO-based approach and a desirable balance achieved using our comprehensive quality model, we first compare our PSO-based approach with one recent GP-based approach \cite{ma2015hybrid} using our proposed quality model, and then compare our proposed quality model with one widely used QoS model using our proposed PSO-based approach.
 \end{enumerate}
@@
 
-\textbf{Definition 1.} A request from users is defined as a composition task in a tuple: $Comp.T = \{I_{T}, O_{T}\}$ by giving a set of task inputs $I_{T}$ and expecting  a set of desired task outputs $O_{T}$, where $I_{T}$ and $O_{T}$ are associated with related concepts $I^{C}_{T}$ and $O^{C}_{T}$ respectively in an ontology $O = \{ C \mid I^{C}_{T}, O^{C}_{T}  \subseteq C \}$.
+\textbf{Definition 1.} A request from users is defined as a composition task in a tuple: $Comp.T = \{I_{T}, O_{T}\}$ by giving a set of task inputs $I_{T}$ and expecting  a set of task outputs $O_{T}$, where $I_{T}$ and $O_{T}$ are associated with related concepts $I^{C}_{T}$ and $O^{C}_{T}$ respectively in an ontology $O = \{ C \mid I^{C}_{T}, O^{C}_{T}  \subseteq C \}$.
 
@@
 To do this, we compare our PSO-based method with one existing GP-based approach \cite{ma2015hybrid}.
-$(2)$ measure the effectiveness of our proposed comprehensive quality model for achieving desired balance of semantic matchmaking quality and QoS.
+$(2)$ measure the effectiveness of our proposed comprehensive quality model for achieving desirable balance of semantic matchmaking quality and QoS.
 To do this, we compare a widely used QoS model in QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol} with our comprehensive quality model using our PSO-based approach.
@@
 This work introduces a general comprehensive evaluation model for considering semantic matchmaking quality and QoS simultaneously.
-We proposed a PSO-based service composition approach utilising our proposed quality mode that can achieve a desired trade-off of both quality aspects.
+We proposed a PSO-based service composition approach utilising our proposed quality mode that can achieve a desirable trade-off of both quality aspects.
 In addtion, we compare one recent GP-approach with our PSO-based method to show our performance that results in finding more optimised solutions.

### 2017-03-29 paper.tex
update

@@
 \section{Related Work} \label{relatedWork}
-Substantial works on web service composition focus on either semantic web service composition \cite{boustil2014semantic,bansal2016generalized,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive}, However, only a few researchers address both semantic matchmaking quality and QoS requirements for web service composition problems.
+Substantial works on web service composition focus on either semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive}, However, only a few researchers address both semantic matchmaking quality and QoS requirements for web service composition problems.
 To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some attempts on service composition that considers both aspects.
@@
 Qi et al.
-\cite{qi2010combining} propose a heuristic service composition method, named LOEM (Local Optimisation and Enumeration Method), where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal QoS.
-However, there exists a scalability problem for the enumeration technique.
-EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problem.
+\cite{qi2010combining} propose a heuristic service composition method, named LOEM (Local Optimisation and Enumeration Method), where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near optimal QoS.
+EC techniques are used to automatically generate solutions with optimal QoS.
 Gupta et al.
 \cite{gupta2015optimization} employ a modified Genetic Algorithm (GA) using a binary string as an individual, which demands to be decoded into composition solutions.
-Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function.
-A hybrid approach employs both greedy search algorithm and GP introduced in \cite{ma2015hybrid} to generate solutions that are functionally correct.
-In particularly, greedy search techniques have been used to generate directed acyclic graphs (DAGs) as composition solutions that is further transferred to tree structures for initialisation and mutation.
-To eliminating the transformation process from DAGs, a promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation.
+Genetic Programming (GP) are used by Yu et al.
+\cite{yu2013adaptive}, the optimal solutions are reached by penalising infeasible solutions using a fitness function.
+A hybrid approach employing a greedy search and GP is introduced in \cite{ma2015hybrid} to generate functionally correct tree-based individuals, which are transformed from DAGs.
+To eliminating the transformation process, a promising GraphEvol is proposed in \cite{da2015graphevol}, where DAG-based service composition representations employ Graph-based evolutionary operators.
 An indirect PSO-based approach was introduced in \cite{da2016particle}.
-An optimised queue is used as an indirect representation that is decoded into a DAG-based solution.
-These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality, which could lead to too specific outputs produced by the selected services, and this finding is supported by our first comparison experiment.
+An optimised queue is used as an indirect representation that is decoded into a DAG.
+These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality, which could lead to too specific outputs produced by the selected services.
 
@@
 Lecue et al.
-\cite{lecue2009optimizing} propose a semi-automated web service composition using GA to encode a given abstract service workflow, where the semantic matchmaking quality is measured through evaluating the quality of semantic links that require a complete and formal definition of ontology in Description Logic.
-This evaluation model takes huge cost and time for the domain experts to establish required ontology.
+\cite{lecue2009optimizing} propose a semi-automated web service composition using GA to encode a given abstract service workflow, where the evaluation of semantic matchmaking quality requires a complete and formal definition of ontology using description logic that associated to the resources of web services.
 Another GA-based approach \cite{fanjiang2014semantic} utilise process description language to encode pre-stored cases-based workflows, where workable services are composed to complete this workflow.
-The work \cite{pop2009immune} is an automated immune-inspired web service composition approach, where an indirect representation that a binary alphabet is used to encode a planning graph.
-However, this composition method is only evaluated on a set of scenarios.
+An automated immune-inspired web service composition approach \cite{pop2009immune} employs a clonal section algorithm with an decoded planning graph, but this approach is only studied in some cases.
 
-In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches, there is a lack of a fully automated semantic web service composition approach to optimise semantic matchmaking quality and QoS simultaneously, and this approach must be tested utilising benchmark dataset.
-Therefore, we first propose a general comprehensive quality model that aims to achieve a better semantic matchmaking quality with a slight trade-off in QoS, and then we propose an automated PSO-based approach with explicit support for the comprehensive model to find optimal service compositions.
+In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches, there is a lack of a fully automated semantic web service composition approach to optimise semantic matchmaking quality and QoS simultaneously.
+Therefore, we first propose an automated comprehensive quality-aware semantic web service composition approach.
+To do that, we will design a comprehensive quality model that considers both QoS and quality of semantic matchmaking between services.
+We will then propose a PSO-based approach to this semantic service composition using our proposed comprehensive quality model to evaluate candidate solutions.
 
@@
 Our comprehensive quality evaluation model is considered to be more general.
-Two semantic matchmaking types (Exact and Plugin) are considered for discovering desired web service in recent QoS-aware web service composition  \cite{ma2015hybrid,da2016particle,da2015graphevol}, but there are no measurements of matchmaking types and concept similarities in their approaches.
+Two semantic matchmaking types (Exact and Plugin) are considered for discovering web services in recent QoS-aware web service composition  \cite{ma2015hybrid,da2016particle,da2015graphevol}, but there are no measurements of semantic matchmaking quality in their approaches.
 Consequently, weights for $MT$ and $S$ are considered to be 0 in our proposed comprehensive evaluation model, it turns to be a widely used QoS evaluation model in \cite{ma2015hybrid,da2016particle,da2015graphevol}.

### 2017-03-29 paper.tex
update

@@
 Step 3 and Step 4: These two steps follow the standard PSO steps \cite{shi2001particle} except for some differences in particles mapping and decoding processes.
-In particular, these two differences are related to sorting a created service queue using serivce-to-index mapping for a particle' position vectors and evaluating the fitness of a particle after decoding this serivce queue into a weighted DAG respectively.
+In particular, these two differences are related to sorting a created service queue using serivce-to-index mapping for a particle' position vectors and evaluating the fitness of a particle after decoding this service queue into a weighted DAG respectively.
 Those differences are further addressed in Algorithms \ref{novelSteps} and \ref{graph_building} in \ref{POS-based_algomargin}.
@@
 The overall algorithm investigated here is made up of a PSO-based web service composition algorithm \ref{novelSteps} and a decoding algorithm \ref{graph_building}.
-In Algorithm \ref{novelSteps}, the  steps $4$, $5$, $6$ and $7$ are different from those of stardard PSO: In step 4, the size of task-related service candidates generated by a greedy search determines the size of each particle's position, and each candidate in a created service candidates queue is mapped to an index of a particle’s position vectors, where each vector has a weight value between 0.0 and 1.0.
+In Algorithm \ref{novelSteps}, the  steps $4$, $5$, $6$ and $7$ are different from those of standard PSO: In step 4, the size of task-related service candidates generated by a greedy search determines the size of each particle's position, and each candidate in a created service candidates queue is mapped to an index of a particle’s position vectors, where each vector has a weight value between 0.0 and 1.0.
 In step 5, all the task-related service candidates in the queue are sorted according to their corresponding weight values in descending order.
@@
 
-Algorithm  \ref{graph_building} is a forward graph buidling algorithm based on \cite{blum1997fast}.
+Algorithm  \ref{graph_building} is a forward graph building algorithm based on \cite{blum1997fast}.
 This algorithm take one input, a sorted service queue from step 5 of Algorithm \ref{novelSteps}.

### 2017-03-30 paper.tex
update

@@
 An optimised queue is used as an indirect representation that is decoded into a DAG.
-These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality, which could lead to too specific outputs produced by the selected services.
+These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality.
 
@@
 The results show that the PSO-based approach outperformes the existing GP-based approach in most cases except task 3 (all the p-values are consistently smaller than 0.01).
-In task 5, PSO-based approach performs significantly better than GP-based approach in finding optimal solutions.
-It may refer to that GP-based approach is stuck in the local optimal due to a very large searching space in Task 5, but PSO-based approach requres decoding processes of sorted queues, where small changes of the queues might lead to different decoded solutions.
-
+In task 5, the PSO-based approach performs significantly better than the GP-based approach in finding optimal solutions.
+It may be that the GP-based approach is stuck in local optima due to the very large search space in Task 5.
+On the other hand, the decoding process used by the PSO-based approach allows for small changes that more effectively prevent this from happening.
 \begin{table}[]

### 2017-04-01 paper.tex
update

@@
 
-In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches, there is a lack of a fully automated semantic web service composition approach to optimise semantic matchmaking quality and QoS simultaneously.
-Therefore, we first propose an automated comprehensive quality-aware semantic web service composition approach.
+In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches, there is a lack of a fully automated semantic service composition approach to optimise semantic matchmaking quality and QoS simultaneously.
+%Therefore, we first propose an automated comprehensive quality-aware semantic web service composition approach.
 To do that, we will design a comprehensive quality model that considers both QoS and quality of semantic matchmaking between services.
@@
 
-\section{Motivation and Problem Description}\label{Motivation and Problem Description}
-\subsection{Motivation}\label{Motivation}
+\section{Motivation and Problem Description}\label{Motivation and Problem Description}\label{Motivation}\label{problemDes}\label{qualityModel}\label{Comprehensive_Quality_Model}\label{qualityModel}
 
-Our goal in this paper is to develop a PSO-based approach that can automatically produce composition services in the form of graph-based representation (e.g.
-DAG).
-The nodes in the DAG represent component services.
-On the other hand, the edge that connects any two component services in the DAG, e.g.
-$S_1->S_2$, indicates that the output information from service S1 will subsequently serve as the input information for service S2.
-Apparently, such output and input information must semantically match to ensure the correct execution of the DAG.
-Moreover, the overall service inputs and outputs associated with the DAG must satisfy the composition requirements provided by users.
+Our goal is to develop a PSO-based approach for automatically generating good service compositions.
+Often, many different service compositions can meet a user request but differ significantly in terms of QoS and semantic matchmaking quality.
+For example, in the classical travel planning context, some component service must be employed to obtain a travel map.
+Suppose that two services can be considered for this purpose.
+One service $S$ can provide a street map at a price of 6.72.
+The other service $S'$ can provide a tourist map at a price of 16.87.
+Because in our context a tourist map is more desirable than a street map, $S'$ clearly enjoys better semantic matchmaking quality than $S$ but will have negative impact on the QoS of the service composition (i.e., the price is much higher).
+One can easily imagine that similar challenges frequently occur when looking for service compositions.
+Hence, a good balance between QoS and semantic matchmaking quality is called for.
+We therefore propose a general comprehensive quality model in considering semantic matchmaking quality and QoS simultaneously.
 
-In practice, many different DAGs can meet the given requirements but differ significantly in terms of QoS and semantic matchmaking quality.
-For example, in the classical travel planning context, during the process of building a DAG, a component service needs to be employed to obtain a travel map.
-Suppose that two optional services can be considered for this purpose.
-One service S1 can provide a street map at a price of 6.72.
-The other service S2 can provide a tourist map at a price of 16.87.
-Because in our DAG a tourist map is more desirable than a street map, service S2 clearly enjoys better semantic matchmaking quality but will have negative impact on the QoS of the DAG (i.e.
-the price is much higher).
-It can be easily imagined that similar problems can frequently occur while building the DAG for the travel planning problem or other web service composition problems.
-Due to this reason, aimed at achieving a good balance in between QoS and semantic matchmaking quality, our PSO-based service composition system will be further guided by a comprehensive quality model to be proposed in 4.
+We consider a \emph{semantic web service} (\emph{service}, for short) as a tuple $S = (I_{S}, O_{S}, QoS_S)$ where $I_{S}$ is the set of service inputs that are consumed by $S$, $O_{S}$ the set of service outputs that are produced by $S$, and $QoS_{S}=\{t_S, c_S, r_S, a_S\}$ the set of non-functional attributes of $S$.
+The inputs in $I_{S}$ and the outputs in $O_{S}$ are concepts in an ontology $\mathcal{O}$.
+The attributes $t_S, c_S, r_S, a_S$ refer to the response time, cost, reliability, and availability of service $S$, respectively.
+These four QoS attributes are most commonly used \cite{zeng2003quality}.
+\textit{Response time} ($t_S$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.
+\textit{Cost} ($c_S$) is the amount of money that a service requester has to pay for executing the service.
+\textit{Reliability} ($r_S$) is the probability that a request is correctly responded within the maximum expected time frame, which is expressed as a number between 1 and 0.
+Similarly, \textit{availability} ($a_S$) is the probability that a service is accessible.
 
-\subsection{Problem Formulation}\label{problemDes}
+A \emph{service repository} $\mathcal{SR}$ is a finite collection of services with a common ontology $\mathcal{O}$.
+A \emph{service request} (also called \emph{composition task}) over $\mathcal{SR}$ is a tuple $T=(I_{T}, O_{T})$ where $I_{T}$ is the set of task inputs, and $O_{T}$ the set of task outputs.
+The inputs in $I_{T}$ and the outputs in $O_{T}$ are concepts in the ontology $\mathcal{O}$.
 
-We herein give formal definitions of the concepts regarding the semantic web service composition problem utilised in our approach, and these concepts are captured in several models as follows.
+A service composition is commonly represented as a \emph{directed acyclic graph} (DAG).
+It nodes correspond to the services in the composition.
+Two services $S$ and $S'$ are connected by an edge $e$ if some output of $S$ serves as input for $S'$.
+Apparently, such outputs and inputs must semantically match to ensure the correct execution of the service composition.
+%Moreover, the overall service inputs and outputs associated with the DAG must satisfy the composition requirements provided by users.
+%To answer a request from a user a suitable service composition is sought. 
+The mechanism to compose services relies on the semantic descriptions of inputs and outputs, which enables inputs of services to be matched by outputs of other services.
+The following \emph{matchmaking types} are often used to describe the level of a match \cite{paolucci2002semantic}: For concepts $a, b$ in $\mathcal{O}$ the \emph{matchmaking} returns $exact$ if $a$ and $b$ are equivalent ($a \equiv b$), $plugin$ if $a$ ia a sub-concept of $b$ ($a \sqsubseteq b$), $subsume$ if $a$ is a super-concept of $b$ ($a \sqsupseteq b$), and $fail$ if none of previous matchmaking types is returned.
+%($a \perp b$)
+In this paper we are only interested in robust compositions where only $exact$ and $plugin$ matches are considered, see \cite{lecue2009optimizing}. 
+%
+As argued in \cite{lecue2009optimizing} $plugin$ matches are less preferable than $exact$ matches due to the overheads associated with data processing.
+We suggest to consider the semantic similarity of concepts when comparing different plugin types.
+For concepts $a, b$ in $\mathcal{O}$ the \emph{semantic similarity} $sim(a, b)$ is calculated based on the edge counting method defined in the formula (\ref{equation1}) from \cite{shet2012new}, where $N_a$, $N_b$ and $N_c$ measure the distances from concept $a$, concept $b$, and a closest common ancestor $c$ of $a$ and $b$ to the top concept of the ontology $\mathcal{O}$, respectively.
 
-\textbf{Semantic Web Service Model}.
-The semantic web service model represents web services with functional descriptions, and how interoperability of web services enables matchmaking for automatically generating composition solutions.
+\begin{equation}
+sim(a, b){=} \frac{2N_c \cdot e^{-\lambda L/D} }{N_{a}+N_{b}}
+\label{equation1}
+\end{equation}
 
-\textbf{Definition 1.} A request from users is defined as a composition task in a tuple: $Comp.T = \{I_{T}, O_{T}\}$ by giving a set of task inputs $I_{T}$ and expecting  a set of task outputs $O_{T}$, where $I_{T}$ and $O_{T}$ are associated with related concepts $I^{C}_{T}$ and $O^{C}_{T}$ respectively in an ontology $O = \{ C \mid I^{C}_{T}, O^{C}_{T}  \subseteq C \}$.
+\noindent For our purposes, $\lambda$ can be set to 0 as we do not measure the similarities of neighbourhood concepts, which is not the matching type considered in this paper. 
+%Thus, we obtain a combined function for measuring semantic matchmaking quality between two concepts:
 
-\textbf{Definition 2.} A semantic web service (hereafter "service") is defined as a tuple $S = \{ I_{S}, O_{S}, QoS_S \}$ $\in$ $\mathcal{SR}$, where $I_{S}$ is a set of service inputs that must be satisfied to invoke $S$, and $O_{S}$ is a set of service outputs returned by the execution of $S$.
-$I_{S}$ and $O_{S}$ are concept-related instances that are linked to their corresponding concepts $I^{C}_{S}$ and $O^{C}_{S}$, where $ I^{C}_{S}, O^{C}_{S}  \subseteq C$.
-$QoS_S = \{ t_s, c_s, r_s, a_s, ...
-\} $ is a set of non-functional attributes of $S$, it refers to response time $t_s$, cost $c_s$, reliability $r_s$, and availability $a_s$ \cite{zeng2003quality}.
-$\mathcal{SR}$ is a service repository consisting of a set of $S$.
-\vspace{0.3cm}
+%\begin{equation}\label{equation2}sm(a, b) \stackrel{.}{=} ( type(a, b), \  sim(a, b) )\end{equation}
 
-\textbf{Semantic Matchmaking Model}.
-The mechanism to compose web services relies on the semantic descriptions of inputs and outputs, which enable inputs of a service to be matched by outputs of another.
-To measure the quality of these matches, we utilise different matchmaking types (\textit{exact, plugin subsumes and fail} \cite{paolucci2002semantic} ).
+Given a service request $T=(I_T,O_T)$, we represent a service composition solution for $T$ with services $S_1,\ldots,S_n$  by a DAG $WG=(V,E)$ with node set $V=\{Start, S_1, S_2, \ldots, S_n, End\}$ and edge set $E = \{e_{1}, e_{2},...
+e_{m} \}$.
+$Start$ and $End$ are two special services defined as $Start = (\emptyset, I_T, \emptyset )$ and $End  = (O_T, \emptyset, \emptyset)$ that account for the input and output requirements given by the request.
+%Each edge $e$ between two services $S$ and $S'$ is associated with a set of incoming outputs produced by $S$ and a set of outgoing inputs consumed by $S'$.
+Each edge $e$ from a service $S$ to a service $S'$ means that service $S$ produces an output $a\in O_S$ that is matched (exact or plugin) to an input $b\in I_{S'}$ to be consumed by service $S'$ in the composition.
+Based on the matchmaking type the \emph{semantic matchmaking quality} of edge $e$ can be defined as follows:
 
-\textbf{Definition 3.} Given $a, b \in C$, $type(a, b)$ returns the matchmaking types of two concepts, and this matchmaking type is determined by the logic relationship described in the $O$.
-If both $a$ and $b$ are equivalent, $exact$ type ($a \equiv b$) is returned.
-If the concept of $a$ is a sub-concept of the concept of $b$ type ($a \sqsubseteq b$) is returned.
-If the concept of $a$ is a super-concept of the concept of $b$, $subsumes$ type ($a \sqsupseteq b$) is returned.
-If none of previous matchmaking types are returned, $fail$ type ($a \perp b$) is returned.
+\begin{equation}
+\label{equation10}
+type_e = 
+\begin{cases}
+	1 & \text{ if $a\equiv b$ ($exact$ match)},\\
+	p & \text{ if $a \sqsubseteq b$ ($plugin$ match)}
+\end{cases}
+\end{equation}
+\begin{equation}
+\label{equation11}
+sim_e = sim(a,b) = \frac{2N_c}{N_{a}+N_{b}}
+\end{equation}
 
-We use $type(a, b)$ to define a full matchmaking considered in the scenario of connecting two services through concept-related output and concept-related input.
+\noindent with a suitable parameter $p, 0<p< 1$ to chosen, for discussion see Section \ref{PSO_based_approach}.
 
-\textbf{Definition 4.} Given $(a \in O^{C}_{S_m}) \vee (b \in I^{C}_{S_n}) \wedge (m \neq n) $, a $full match(a \Rightarrow b)$ holds if $type(a, b)$ returns $exact$ or $plugin$.
+%$e = \{ (O_{S_{src}} \cup I_{S_{src}}) \mid \forall o \in O_{S_{src}}, \exists i \in O_{S_{src}} \wedge fullmatch (o \Rightarrow i) \}$
+
+%\textbf{Definition 4.} Given $(a \in O^{C}_{S_m}) \vee (b \in I^{C}_{S_n}) \wedge (m \neq n) $, a $full match(a \Rightarrow b)$ holds if $type(a, b)$ returns $exact$ or $plugin$.
 The operator ``$ \Rightarrow$'' means $a$ is passed to $b$, and $b$ is fully satisfied by $a$.
 The full match is a guarantee of completely valid  ``$ \Rightarrow$'' operation, whereas, partial matches are not considered in this paper.
-\vspace{0.3cm}
 
-\textbf{QoS calculation Model in a DAG}
-Four most often considered QoS parameters \cite{zeng2003quality} are response time, cost, reliability and availability described as follows: \textit{Response time} ($t_s$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.\textit{Cost} ($c_s$) is the amount of money that a service requester has to pay for executing the web service.
-\textit{Reliability} ($r_s$) is the probability that a request is correctly responded within the maximum expected time frame, which is expressed as a number between 1 and 0.
-\textit{Availability} ($a_s$) is the probability that a web service is accessible, which is expressed in the same way as $r_s$.
-The aggregation value of QoS in a DAG respect to the DAG's structures that determine how services associated with each other in a service composition.
-The QoS calculation models are described based on QoS aggregation method \cite{da2015graphevol} as follows:
-
-$A$, $R$, $C$, $T$ is aggregated $a_s$, $r_s$, $c_s$ and $t_n$ respectively with a given $WG$, where  $\{S_1, S_2, ... S_n\} \subset V$, such that: $A=\prod\limits^n_{k=1}a_k
-$; $R=\prod\limits^n_{k=1}r_k$; $C=\sum\limits^n_{k=1}c_k$; $T$ is the time of most time-consumption path of $WG$, so $T = MAX \{timePath()_n |n\in\{1,\ldots,m\}\}$ where $m$ is the number of $WG$ path, and $timePath() = \sum\limits^j_{k=1}t_k$, where $j$ is the number of services involved this path.
-
-\section{Comprehensive Quality Model}\label{Comprehensive_Quality_Model}
-
-In this section, we propose a general comprehensive quality model in considering semantic matchmaking quality and QoS simultaneously.
-This comprehensive model is fully supported by the representations of service composition discussed in this paper, as a weighted DAG model formulated in this section.
-
-\subsection{Comprehensive Quality Model}\label{qualityModel}
-
-\textbf{Semantic matchmaking quality model}.
+%\textbf{Semantic matchmaking quality model}.
 Due to that the discretisational characteristics of different match types and values assigned to matching types driven by the cost of data manipulation \cite{lecue2009optimizing}, match types are considered to be one factor for the quality of matchmaking.
@@
 
-\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $sim(a, b)$ is a function that given a output-related concept $a$ of a service and a input-related concept $b$ of another service, it returns a concept similarity value between $a$ and $b$.
+%\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $sim(a, b)$ is a function that given a output-related concept $a$ of a service and a input-related concept $b$ of another service, it returns a concept similarity value between $a$ and $b$.
 
-The $sim(a, b)$ is calculated based on the edge counting method defined in the formula (\ref{equation1}) from \cite{shet2012new}, where $N_1$, $N_2$ and $N$ measure the distances from an output-related concept $a$, an input-related concept $b$, a closest common ancestor of these two matched $a$ and $b$ to the top concept of an ontology $O$ respectively.
-$\lambda$ is set to 0 as we do not measure the similarities of neighbourhood concepts, which is not the matching type considered in this paper.
+%\textbf{Definition 6.} Given $full match(a \Rightarrow b)$, $sm(a,b)$ is a function for measuring semantic matchmaking quality between two concepts, which returns a pair of values consisting of $type(a, b)$ and $q_{sim}(a, b)$ defined in Formula (\ref{equation2}).
 
-\begin{equation}
-sim(a, b){=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
-\label{equation1}
-\end{equation}
-
-\textbf{Definition 6.} Given $full match(a \Rightarrow b)$, $sm(a,b)$ is a function for measuring semantic matchmaking quality between two concepts, which returns a pair of values consisting of $type(a, b)$ and $q_{sim}(a, b)$ defined in Formula (\ref{equation2}).
-
-\begin{equation}
-\label{equation2}
-sm(a, b) \stackrel{.}{=} ( type(a, b), \  sim(a, b) )
-\end{equation}
-
-\textbf{Weighted DAG composition model}.
+%\textbf{Weighted DAG composition model}.
 web service composition is considered to be a data workflow, where services are chained together by their inputs and outputs using the two models defined before.
@@
 
-$V=\{Start, S1, S2...Sn, End\}$ is a set of services, where $Start$ and $End$ are two special services defined as $Start = \{ \phi, I_T, \phi \}$ and $End  = \{ O_T, \phi, \phi \}$.
+%\textbf{Comprehensive quality model in a weighted DAG}.
 
-$E = \{e_{1}, e_{2},...
-e_{m} \}$ is a set of edges, where each edge has a set of incoming outputs $O_{S_{src}}$ from source service $S_{src}$ and a set of outgoing inputs $I_{S_{tar}}$ from target service $S_{tar}$.
-
-$e = \{ (O_{S_{src}} \cup I_{S_{src}}) \mid \forall o \in O_{S_{src}}, \exists i \in O_{S_{src}} \wedge fullmatch (o \Rightarrow i) \}$
-\vspace{0.3cm}
-
-\textbf{Comprehensive quality model in a weighted DAG}.
-
-Since each $e$ defined in $E$ could have more than one $fullmatch(a \Rightarrow b)$ form a edge.
+%Since each $e$ defined in $E$ could have more than one $fullmatch(a \Rightarrow b)$ form a edge.
 Therefore, semantic matchmaking quality of one edge, denoted as $sm_e$ is defined in formula (\ref{equation3}), where $type_{e}$ and $sim_{e}$ are the average values of all involved $type(a, b)$ and $q_{sim}(a, b)$ respectively.
 
-\begin{equation}
-\label{equation3}
-sm_{e} \stackrel{.}{=} (type_ {e}, \  sim_ {e})
-\end{equation}
+%\begin{equation}\label{equation3}sm_{e} \stackrel{.}{=} (type_ {e}, \  sim_ {e})\end{equation}
 
-The semantic matchmaking quality $SM$ is further aggregated with considering all $\{e_{1}, e_{2},...
-e_{m} \}$ in $E$, calculated by following the formula (\ref{eqSM})(\ref{equation6})(\ref{equation7}).
-Consequently, in Formula \ref{eqCQ}, the comprehensive quality $CQ$ consists of the aggregated semantic matchmaking quality $SM$ and the QoS calculation in DAG discussed before.
+The \emph{semantic matchmaking quality} of the service composition can be obtained by aggregating over all edges in $E$ as follows:
 
-\begin{equation}
-\label{eqSM}
-SM \stackrel{.}{=} (MT, SIM)
-\end{equation}
+%\begin{equation}
+%\label{eqSM}
+%SM \stackrel{.}{=} (MT, SIM)
+%\end{equation}
 \begin{equation}
 \label{equation6}
-MT {=} \prod_{n=1}^{m} type_ {e_{n}}
+MT {=} \prod_{j=1}^{m} type_ {e_{j}}
 \end{equation}
@@
 \label{equation7}
-SIM {=} (\sum_{n=1}^m sim_ {e_{n}})/m
+SIM {=} \frac{1}{m}\sum_{j=1}^m sim_ {e_{j}}
 \end{equation}
-\begin{equation}
-\label{eqCQ}
-CQ \stackrel{.}{=} (MT, \  SIM, \  A,\  R,\  C,\  T)
-\end{equation}
+%\begin{equation}
+%\label{eqCQ}
+%CQ \stackrel{.}{=} (MT, \  SIM, \  A,\  R,\  C,\  T)
+%\end{equation}
 
-\subsection{Objective Function}
-In real life, given a unique and optimised solution is always easier for customers to pick up directly when many quality criteria involved into decision making, rather than provided a set of solutions.
-It is very practical to define a single fitness as a weighted sum of all the quality related components in Formula (\ref{equation8}).
-Note that weights can be adjusted according to users' preferences.
-The function value of 1 means the best comprehensive quality and 0 means the worst.
-For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the function value falls within the range from 0 to 1 using Formula (\ref{equation9}) and (\ref{equation10}), where the maximum and minimum value of $A$, $R$, $T$, and $C$ are calculated by all web services candidates to the composition task, which are generated by a greedy search discussed in \ref{PSO_based_approach}.
-$MT$ and $S$ are using a bound from 0 to 1.
-Therefore, the composition task is try to find maximised value of objective function associated to the solutions.
+The \emph{QoS} of the service composition can be obtained by aggregating the QoS values of the participating services.
+For a service composition with services $ S_1, S_2, ...
+S_n$ we obtain the reliabilitiy $R=\prod\limits^n_{k=1}r_{S_k}$, the availability $A=\prod\limits^n_{k=1}a_{S_k}$, the cost $C=\sum\limits^n_{k=1}c_{S_k}$, and the response time $T$ is the time of most time-consumption path in the composition, i.e., $$T = MAX \{\sum\limits^{\ell_j}_{k=1}t_{S_k} | \text{ $j\in\{1,\ldots,m\}$ and $P_j$ is a path of length $\ell_j$}\} \cite{da2015graphevol}.$$
 
-\vspace{-0.2cm}
+%Consequently, in Formula \ref{eqCQ}, the comprehensive quality $CQ$ consists of the aggregated semantic matchmaking quality $SM$ and the QoS calculation in DAG discussed before.
+
+\noindent When multiple quality criteria are involved into decision making, then the overall fitness of a solution can be defined as a weighted sum of the individual criteria:
+
 \begin{equation}
 \label{equation8}
-Fitness = w_1 \hat{MT} + w_2 \hat{S} + w_3 \hat{A} + w_4 \hat{R} + w_5(1 - \hat{T}) + w_6(1 - \hat{C})
+Fitness = w_1 \hat{MT} + w_2 \hat{SIM} + w_3 \hat{A} + w_4 \hat{R} + w_5(1 - \hat{T}) + w_6(1 - \hat{C})
 \end{equation}
-\noindent where $\sum_{i=1}^{6} w_i = 1$
-\\
-\vspace{-0.2cm}
+\noindent with $\sum_{k=1}^{6} w_k= 1$.
+The weights can be adjusted according to users' preferences.
+Herein, the individual criteria are normalized so that the QoS value falls within the range from 0 to 1 where 1 means the best value and 0 means the worst.
+For this purpose, we normalize $MT$, $SIM$, $A$, $R$, $T$, and $C$ so that the function value falls within the range from 0 to 1 using formula (\ref{equation9}).
+To simplify the presentation we also use the notation $(Q_1,Q_2,Q_3,Q_4,Q_5,Q_6) = (MT,SIM,A,R,T,C)$.
+$MT$ and $S$ have minimum value 0 and maximum value 1.
+The minimum and maximum value of $A$, $R$, $T$, and $C$ are calculated across all service candidates in the service repository $\mathcal{SR}$ using greedy search, for discussion see Section \ref{PSO_based_approach}.
+
 \begin{equation}
@@
 \begin{cases}
-	\frac{Q_k - Q_{k, min}}{Q_{k, max} - Q_{k, min}} & \text{ if }Q_{k, max} - Q_{k, min} \neq 0.\\
-	1 & \mathrm{ otherwise}.
+	\frac{Q_k - Q_{k, min}}{Q_{k, max} - Q_{k, min}} & \text{ if $k=1,\ldots,4$ and }Q_{k, max} - Q_{k, min} \neq 0,\\
+	\frac{Q_{k,max} - Q_k}{Q_{k, max} - Q_{k, min}} & \text{ if $k=5,6$ and }Q_{k, max} - Q_{k, min} \neq 0,\\
+	1 & \text{ otherwise}.
 \end{cases}
 \end{equation}
-\noindent where $k$ $=$ $1$, $2$, $3$, and $4$, where $Q_1$ is $MT$, $Q_2$ is $S$, $Q_3$ is $A$, and $Q_4$ is $R$.
-\begin{equation}
-\label{equation10}
-\hat{Q_j} = 
-\begin{cases}
-	\frac{Q_{j,max} - Q_j}{Q_{j, max} - Q_{j, min}} & \text{ if }Q_{j, max} - Q_{j, min} \neq 0.\\
-	1 & \mathrm{ otherwise}.
-\end{cases}
-\end{equation}
-\noindent where $j$ $=$ $1$, and $2$, where $Q_1$ is $T$ and $Q_2$ is $C$.
 
-Our comprehensive quality evaluation model is considered to be more general.
-Two semantic matchmaking types (Exact and Plugin) are considered for discovering web services in recent QoS-aware web service composition  \cite{ma2015hybrid,da2016particle,da2015graphevol}, but there are no measurements of semantic matchmaking quality in their approaches.
-Consequently, weights for $MT$ and $S$ are considered to be 0 in our proposed comprehensive evaluation model, it turns to be a widely used QoS evaluation model in \cite{ma2015hybrid,da2016particle,da2015graphevol}.
+\noindent The composition task is to find the maximum value of objective function in (\ref{equation8}).
 
-\section{PSO-based Approach to Comprehensive Quality-Aware Automated Semantic Web Service Composition}\label{qswsc_approach}
-
-\begin{figure}[h]
-\centering
-\fbox{\includegraphics[scale=.4]{overview.pdf}}
- \caption{An overview of POS-based approach to comprehensive quality-aware automated semantic web service composition.}
- \label{overview}
-\end{figure}
+%If the weights for $MT$ and $S$ are put to 0 we obtain the QoS-aware service composition approach \cite{ma2015hybrid,da2016particle,da2015graphevol} as a special case.
+To adequatley reflect the relevance of semantic quality it is recommended to choose he weights for $MT$ and $S$ strictly larger than 0.
 

### 2017-04-01 paper.tex
update

@@
 \textit{Web service composition} pertains to a chain of multiple web services to provide a value-added composition service that accommodates customers' complex requirements. 
-This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems.
+%This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems.
 
@@
 \textit{Interoperability} of web services presents challenge in syntactic and semantic dimensions.
-The syntactic dimension is covered by the XML-based technologies (such as $WSDL$, $SOAP$).
-The semantic dimension enables a better collaboration through ontology-based semantics.
-There are many ontology languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}.
-The second challenge is related to finding optimised solutions in QoS.
+The syntactic dimension is covered by the XML-based technologies, such as $WSDL$, $SOAP$.
+The semantic dimension enables a better collaboration through ontology-based semantics, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}.
+\textit{Semantic web services composition} is distinguished from the syntactic service composition, the resources of semantic web services are described semantically to enable a better interoperability for chaining web services.
+The second challenge is related to finding solutions with optimised QoS.
 This problem gives birth to \textit{QoS-aware service composition} that aims to find composition solutions with optimised QoS.
@@
 Existing works on service composition focus mainly on addressing only one challenge above.
-In these works, huge efforts have been devoted to optimise the quality of compositions under a pre-defined abstract workflow.
-This is generally considered as a \textit{semi-automated Web service composition} approach \cite{parejo2008qos}.
-Meanwhile, many research works consider a NP-hard problem of generating a composition plan automatically in discovering and selecting suitable web services \cite{moghaddam2014service}.
-\textit{Semantic web services composition} is distinguished from the syntactic service composition, the resources of semantic web services are described semantically to enable a better interoperability for chaining web services.
-In the past few years, substantial works have been done on semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated}.
-However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously to achieve a desirable balance.
+In these works, huge efforts have been devoted to QoS-aware web service compositions given a pre-defined abstract workflow.
+This is generally considered as a \textit{semi-automated web service composition} approach \cite{parejo2008qos}.
+Generating composition plans automatically in discovering and selecting suitable web services is a NP-hard problem \cite{moghaddam2014service}.
+In the past few years, despite many QoS-aware web service composition works \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive} employ Evolutionary Computation (EC) techniques to automatically generate composition solutions, but few works have enabled an \textit{automatic semantic web service composition}, where both QoS and quality of semantic matchmaking are optimised simultaneously to achieve a desirable balance.
 
-The overall goal of this paper is to \textit{develop a general comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}.
-Particularly, this paper extends existing works of QoS-aware service composition by considering jointly optimise QoS and semantic matchmaking quality using our proposed comprehensive quality model.
+The overall goal of this paper is to \textit{develop a PSO-based approach to automated comprehensive quality-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}.
+Particularly, this paper extends existing works of QoS-aware service composition by considering jointly optimising QoS and semantic matchmaking quality using our proposed comprehensive quality model.
 Particle Swarm Optimisation (PSO) has shown promise in searching for near-optimised service composition solutions \cite{da2016particle}.
@@
 \begin{enumerate}
- \item To propose a general comprehensive quality model that addresses QoS and semantic matchmaking quality simultaneously with a desirable balance on both sides.
+ \item To propose a comprehensive quality model that addresses QoS and semantic matchmaking quality simultaneously with a desirable balance on both sides.
 
  \item To propose a PSO-based service composition approach using the proposed comprehensive quality model.
-To do that we optimise a service candidates queue by evaluating the comprehensive quality of its decoded representation.
-
+To do that, we aim to find a service candidate queue that can be decoded into a service composition with the near-optimal comprehensive quality.
  \item To address the effectiveness of our PSO-based approach and a desirable balance achieved using our comprehensive quality model, we first compare our PSO-based approach with one recent GP-based approach \cite{ma2015hybrid} using our proposed quality model, and then compare our proposed quality model with one widely used QoS model using our proposed PSO-based approach.
@@
 
+\section{PSO-based Approach to Comprehensive Quality-Aware Automated Semantic Web Service Composition}\label{qswsc_approach}
+
+\begin{figure}[h]
+\centering
+\fbox{\includegraphics[scale=.4]{overview.pdf}}
+ \caption{An overview of POS-based approach to comprehensive quality-aware automated semantic web service composition.}
+ \label{overview}
+\end{figure}
+
 \subsection{An Overview to PSO-based Method}\label{PSO_based_approach}
@@
      Create a weighted DAG from the service queue ( Algorithm\ref{graph_building}) \;
-     Calculate the Weighted DAG fitness value\;
+     Calculate the weighted DAG fitness value\;
 
-      \eIf{fitness value better than \emph{pBest}}{    
+      \eIf{fitness value better than pBest}{    
         Assign current fitness as new \emph{pBest}\;
@@
  \SetNlSty{}{}{:}
-  \Procedure{\createWeightedDAG{}}{
- \Input{ $I_T$, $O_T$, $queue$, $Cache$}
+ % \Procedure{}{
+ \Input{ $I_T$, $O_T$, $queue$, $cache$}
  \Output{WG}
@@
     		 \ForEach{$I_{S}$}{
-		$sm(a \in Outputset, b \in I_{S}) \leftarrow$ query $Cache$\;
+		$sm(a \in Outputset, b \in I_{S}) \leftarrow$ query $cache$\;
               }
@@
  \KwRet $WG$\;
- }
+ %}
  \caption{Create a weighted DAG from a  sorted queue.}

### 2017-04-01 paper.tex
update

@@
 Existing works on web service composition focus mainly on one single type of requirements.
-Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS simultaneously with an aim of achieving a more desirable trade-off in consideration of both sides.
-Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model, where PSO optimise a queue of task-related services that is decoded into composition solutions.
+Therefore, we propose a comprehensive quality model considering semantic matchmaking quality and QoS simultaneously with an aim of achieving a more desirable balance on both sides.
+Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model.
+We also conduct experiments to address the effectiveness of our PSO-based approach and a desirable balance achieved using our comprehensive quality model.
+
+%where PSO optimise a queue of task-related services that is decoded into composition solutions.
 We compare the effectiveness of PSO-based method with one recent GP-based method using the proposed comprehensive quality model, and also compare the effectiveness of our proposed comprehensive quality model with one promising QoS model.
@@
 
-\textit{Web service composition} pertains to a chain of multiple web services to provide a value-added composition service that accommodates customers' complex requirements. 
+\textit{Web service composition} pertains to a chain of multiple web services to provide a value-added composite service that accommodates customers' complex requirements. 
 %This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems.
@@
 \textit{Semantic web services composition} is distinguished from the syntactic service composition, the resources of semantic web services are described semantically to enable a better interoperability for chaining web services.
-The second challenge is related to finding solutions with optimised QoS.
+The second challenge is related to QoS optimisation.
 This problem gives birth to \textit{QoS-aware service composition} that aims to find composition solutions with optimised QoS.
@@
 Existing works on service composition focus mainly on addressing only one challenge above.
-In these works, huge efforts have been devoted to QoS-aware web service compositions given a pre-defined abstract workflow.
+In these works, huge efforts have been devoted to QoS-aware web service compositions assuming a pre-defined abstract workflow is given.
 This is generally considered as a \textit{semi-automated web service composition} approach \cite{parejo2008qos}.
 Generating composition plans automatically in discovering and selecting suitable web services is a NP-hard problem \cite{moghaddam2014service}.
-In the past few years, despite many QoS-aware web service composition works \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive} employ Evolutionary Computation (EC) techniques to automatically generate composition solutions, but few works have enabled an \textit{automatic semantic web service composition}, where both QoS and quality of semantic matchmaking are optimised simultaneously to achieve a desirable balance.
+In the past few years, many approaches \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive} to QoS-aware web service composition employ Evolutionary Computation (EC) techniques to automatically generate composition solutions, but few works have enabled an \textit{automatic semantic web service composition}, where both QoS and quality of semantic matchmaking are optimised simultaneously to achieve a desirable balance on both sides.
 
@@
 \end{enumerate}
-
 \section{Related Work} \label{relatedWork}
-Substantial works on web service composition focus on either semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive}, However, only a few researchers address both semantic matchmaking quality and QoS requirements for web service composition problems.
+Substantial works on web service composition focus on either semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive}, However, only a few researchers address both semantic matchmaking quality and QoS for web service composition problems.
 To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some attempts on service composition that considers both aspects.
 
-Semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} captures the semantic description of web services' parameters using some kind of logic (e.g., description logic) that ensuring the interoperability of web services, where the number of web services or length of a graph representation for web service composition is minimised to reach the optimised composition solutions.
+Semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} captures the semantic descriptions of web services' parameters using some kind of logic (e.g., description logic) that ensuring the interoperability of web services.
+In these approach, the number of web services or length of a graph representation for web service composition is minimised to reach the optimised composition solutions.
 However, this evaluation approach does not guarantee an optimised QoS of composition solutions.
@@
 Qi et al.
-\cite{qi2010combining} propose a heuristic service composition method, named LOEM (Local Optimisation and Enumeration Method), where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near optimal QoS.
-EC techniques are used to automatically generate solutions with optimal QoS.
+\cite{qi2010combining} propose a local optimisation and enumeration method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near optimal QoS.
+EC techniques are widely used to automatically generate solutions with optimal QoS.
 Gupta et al.
 \cite{gupta2015optimization} employ a modified Genetic Algorithm (GA) using a binary string as an individual, which demands to be decoded into composition solutions.
-Genetic Programming (GP) are used by Yu et al.
-\cite{yu2013adaptive}, the optimal solutions are reached by penalising infeasible solutions using a fitness function.
-A hybrid approach employing a greedy search and GP is introduced in \cite{ma2015hybrid} to generate functionally correct tree-based individuals, which are transformed from DAGs.
-To eliminating the transformation process, a promising GraphEvol is proposed in \cite{da2015graphevol}, where DAG-based service composition representations employ Graph-based evolutionary operators.
+Yu et al.
+\cite{yu2013adaptive} use Genetic Programming (GP) for finding optimal solutions that are reached by penalising infeasible solutions using a fitness function.
+A hybrid approach employing a greedy search and GP is introduced in \cite{ma2015hybrid} to generate functionally correct tree-based individuals, which are transformed from \emph{directed acyclic graph}s (DAGs).
+To eliminating the transformation process, a promising GraphEvol is proposed in \cite{da2015graphevol}, where graph-based evolutionary operators are employed.
 An indirect PSO-based approach was introduced in \cite{da2016particle}.
-An optimised queue is used as an indirect representation that is decoded into a DAG.
+An service queue is used as an indirect representation that is decoded into a DAG.
 These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality.
@@
 Another GA-based approach \cite{fanjiang2014semantic} utilise process description language to encode pre-stored cases-based workflows, where workable services are composed to complete this workflow.
-An automated immune-inspired web service composition approach \cite{pop2009immune} employs a clonal section algorithm with an decoded planning graph, but this approach is only studied in some cases.
+An automated immune-inspired web service composition approach \cite{pop2009immune} employs a clonal selection algorithm to proliferate decoded planning graphs, but this approach is only studied in some cases.
 
@@
 Hence, a good balance between QoS and semantic matchmaking quality is called for.
-We therefore propose a general comprehensive quality model in considering semantic matchmaking quality and QoS simultaneously.
+We therefore propose a comprehensive quality model in considering semantic matchmaking quality and QoS simultaneously.
 
 We consider a \emph{semantic web service} (\emph{service}, for short) as a tuple $S = (I_{S}, O_{S}, QoS_S)$ where $I_{S}$ is the set of service inputs that are consumed by $S$, $O_{S}$ the set of service outputs that are produced by $S$, and $QoS_{S}=\{t_S, c_S, r_S, a_S\}$ the set of non-functional attributes of $S$.
-The inputs in $I_{S}$ and the outputs in $O_{S}$ are concepts in an ontology $\mathcal{O}$.
+The inputs in $I_{S}$ and the outputs in $O_{S}$ are concept-related parameters with the concepts in an ontology $\mathcal{O}$.
 The attributes $t_S, c_S, r_S, a_S$ refer to the response time, cost, reliability, and availability of service $S$, respectively.
 These four QoS attributes are most commonly used \cite{zeng2003quality}.
-\textit{Response time} ($t_S$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.
+% \textit{Response time} ($t_S$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.
 \textit{Cost} ($c_S$) is the amount of money that a service requester has to pay for executing the service.
@@
 A \emph{service request} (also called \emph{composition task}) over $\mathcal{SR}$ is a tuple $T=(I_{T}, O_{T})$ where $I_{T}$ is the set of task inputs, and $O_{T}$ the set of task outputs.
-The inputs in $I_{T}$ and the outputs in $O_{T}$ are concepts in the ontology $\mathcal{O}$.
+The inputs in $I_{T}$ and the outputs in $O_{T}$ are concept-related parameters with the concepts in the ontology $\mathcal{O}$.
 
-A service composition is commonly represented as a \emph{directed acyclic graph} (DAG).
+A service composition is commonly represented as a DAG.
 It nodes correspond to the services in the composition.
@@
 The mechanism to compose services relies on the semantic descriptions of inputs and outputs, which enables inputs of services to be matched by outputs of other services.
-The following \emph{matchmaking types} are often used to describe the level of a match \cite{paolucci2002semantic}: For concepts $a, b$ in $\mathcal{O}$ the \emph{matchmaking} returns $exact$ if $a$ and $b$ are equivalent ($a \equiv b$), $plugin$ if $a$ ia a sub-concept of $b$ ($a \sqsubseteq b$), $subsume$ if $a$ is a super-concept of $b$ ($a \sqsupseteq b$), and $fail$ if none of previous matchmaking types is returned.
+The following \emph{matchmaking types} are often used to describe the level of a match \cite{paolucci2002semantic}: For concepts $a, b$ in $\mathcal{O}$ the \emph{matchmaking} returns $exact$ if $a$ and $b$ are equivalent ($a \equiv b$), $plugin$ if $a$ is a sub-concept of $b$ ($a \sqsubseteq b$), $subsume$ if $a$ is a super-concept of $b$ ($a \sqsupseteq b$), and $fail$ if none of previous matchmaking types is returned.
 %($a \perp b$)
@@
 
-Given a service request $T=(I_T,O_T)$, we represent a service composition solution for $T$ with services $S_1,\ldots,S_n$  by a DAG $WG=(V,E)$ with node set $V=\{Start, S_1, S_2, \ldots, S_n, End\}$ and edge set $E = \{e_{1}, e_{2},...
+Given a service request $T=(I_T,O_T)$, we represent a service composition solution for $T$ with services $S_1,\ldots,S_n$  by a weighted DAG, $WG=(V,E)$ with node set $V=\{Start, S_1, S_2, \ldots, S_n, End\}$ and edge set $E = \{e_{1}, e_{2},...
 e_{m} \}$.
@@
 %Each edge $e$ between two services $S$ and $S'$ is associated with a set of incoming outputs produced by $S$ and a set of outgoing inputs consumed by $S'$.
-Each edge $e$ from a service $S$ to a service $S'$ means that service $S$ produces an output $a\in O_S$ that is matched (exact or plugin) to an input $b\in I_{S'}$ to be consumed by service $S'$ in the composition.
+Each edge $e$ from a service $S$ to a service $S'$ means that service $S$ produces an output $a\in O_S$ that is matched ($exact$ or $plugin$) to an input $b\in I_{S'}$ to be consumed by service $S'$ in the composition.
 Based on the matchmaking type the \emph{semantic matchmaking quality} of edge $e$ can be defined as follows:
@@
 For a service composition with services $ S_1, S_2, ...
-S_n$ we obtain the reliabilitiy $R=\prod\limits^n_{k=1}r_{S_k}$, the availability $A=\prod\limits^n_{k=1}a_{S_k}$, the cost $C=\sum\limits^n_{k=1}c_{S_k}$, and the response time $T$ is the time of most time-consumption path in the composition, i.e., $$T = MAX \{\sum\limits^{\ell_j}_{k=1}t_{S_k} | \text{ $j\in\{1,\ldots,m\}$ and $P_j$ is a path of length $\ell_j$}\} \cite{da2015graphevol}.$$
+S_n$ we obtain the reliabilitiy $R=\prod\limits^n_{k=1}r_{S_k}$, the availability $A=\prod\limits^n_{k=1}a_{S_k}$, the cost $C=\sum\limits^n_{k=1}c_{S_k}$, and the response time $T$ is the time of most time-consumption path in the composition, i.e., $$T = MAX \{\sum\limits^{\ell_j}_{k=1}t_{S_k} | \text{ $j\in\{1,\ldots,m\}$ and $P_j$ is a path of length $\ell_j$}\}.$$
 
@@
 
-\noindent When multiple quality criteria are involved into decision making, then the overall fitness of a solution can be defined as a weighted sum of the individual criteria:
+\noindent When multiple quality criteria are involved into decision making, then the overall fitness of a solution is evaluated by a proposed comprehensive quality model, which can be defined as a weighted sum of the individual criteria:
 
@@
 The weights can be adjusted according to users' preferences.
-Herein, the individual criteria are normalized so that the QoS value falls within the range from 0 to 1 where 1 means the best value and 0 means the worst.
-For this purpose, we normalize $MT$, $SIM$, $A$, $R$, $T$, and $C$ so that the function value falls within the range from 0 to 1 using formula (\ref{equation9}).
+Herein, the individual criteria are normalised to a range between 0 to 1, where 1 means the best value and 0 means the worst.
+For this purpose, we normalise $MT$, $SIM$, $A$, $R$, $T$, and $C$ so that the function value falls within the range from 0 to 1 using formula (\ref{equation9}).
 To simplify the presentation we also use the notation $(Q_1,Q_2,Q_3,Q_4,Q_5,Q_6) = (MT,SIM,A,R,T,C)$.
 $MT$ and $S$ have minimum value 0 and maximum value 1.
-The minimum and maximum value of $A$, $R$, $T$, and $C$ are calculated across all service candidates in the service repository $\mathcal{SR}$ using greedy search, for discussion see Section \ref{PSO_based_approach}.
+The minimum and maximum value of $A$, $R$, $T$, and $C$ are calculated across all task-related candidates in the service repository $\mathcal{SR}$ using greedy search, for discussion see Section \ref{PSO_based_approach}.
 
@@
 \section{Experiment Study}\label{experiment_design}
-In this section, a quantitative evaluation approach is adopted in our experiment design.
+In this section, a quantitative evaluation approach is adopted in our experiment design using an augmented version of Web service challenge 2009 including QoS attributes, which is used in \cite{ma2015hybrid,da2016genetic}.
 Two objectives of this evaluation are to: $(1)$ measure the effectiveness of our PSO-based approach.
-To do this, we compare our PSO-based method with one existing GP-based approach \cite{ma2015hybrid}.
+%To do this, we compare our PSO-based method with one existing GP-based approach \cite{ma2015hybrid}. 
 $(2)$ measure the effectiveness of our proposed comprehensive quality model for achieving desirable balance of semantic matchmaking quality and QoS. 
-To do this, we compare a widely used QoS model in QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol} with our comprehensive quality model using our PSO-based approach.
+%To do this, we compare a widely used QoS model in QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol} with our comprehensive quality model using our PSO-based approach.
 
-An augmented version of Web service challenge 2009 (WSC09) used in \cite{ma2015hybrid,da2016genetic} including QoS attributes is used for our experiment.
-WSC09 is a benchmark dataset consisting of five composition tasks.
-These tasks are associated with an increasing number of services, and concepts in ontologies.
+%WSC09 is a benchmark dataset consisting of five composition tasks. These tasks are associated with an increasing number of services, and concepts in ontologies.
 
@@
 \section{Conclusion}\label{conclusion}
-This work introduces a general comprehensive evaluation model for considering semantic matchmaking quality and QoS simultaneously.
+This work introduces a comprehensive evaluation model for considering semantic matchmaking quality and QoS simultaneously.
 We proposed a PSO-based service composition approach utilising our proposed quality mode that can achieve a desirable trade-off of both quality aspects.

### 2017-04-01 paper.tex
update

@@
 \noindent with a suitable parameter $p, 0<p< 1$ to chosen, for discussion see Section \ref{PSO_based_approach}.
+However, if more than one pair of matched output and input from services $S$ and $S'$ respectively, $type_e$ and $sim_e$ will take on their average values.
 
@@
 \section{PSO-based Approach to Comprehensive Quality-Aware Automated Semantic Web Service Composition}\label{qswsc_approach}
-
+\vspace{-0.8cm}
 \begin{figure}[h]
@@
 \end{figure}
-
+\vspace{-1.0cm}
 \subsection{An Overview to PSO-based Method}\label{PSO_based_approach}
 
-PSO has shown promise in solving combinatorial optimisation problems, and considered an easier way to maintain the correctness of solutions compared to GP-based approaches that often require repairing the solutions \cite{da2016particle}.
+PSO has shown promise in solving combinatorial optimisation problems, and is also considered to be an easy way to maintain the correctness of solutions.
+For example, GP-based approaches often require repairing the solutions \cite{da2016particle}.
 Therefore, we employ a PSO-based approach to comprehensive quality-aware automated semantic web service composition.
@@
 
-Step 2: This composition task is used to discover all task-related service candidates using a greedy search adopted from \cite{ma2015hybrid}.
+Step 2: This composition task is used to discover all task-related service candidates using a greedy search algorithm adopted from \cite{ma2015hybrid}, which contributes to a shrunken service repository.
 This greedy search algorithm keeps adding outputs of the invoked services as available outputs (initialised with $I_{T}$) , and these available outputs are used to discover task-related services from a service repository and updated with the outputs of these discovered services.
 This operation is repeated until no service is satisfied by the available outputs.
-This greedy search contributes to a shrunken service repository.
-During the greedy search, an ontology-based cache ($cache$) is initialised that stores the concept similarities of potentially matched inputs and outputs of task-related candidates.
-This $cache$ is also used to check whether services can be invoked by satisfying their input-related concepts with provided output-related concepts.
+During the greedy search, an ontology-based cache ($cache$) is initialised that stores the concept similarities of matched inputs and outputs of task-related candidates.
+This $cache$ is also used to discover services by checking whether $null$ is returned by given two output-related and input-related concepts.
 
 Step 3 and Step 4: These two steps follow the standard PSO steps \cite{shi2001particle} except for some differences in particles mapping and decoding processes.
-In particular, these two differences are related to sorting a created service queue using serivce-to-index mapping for a particle' position vectors and evaluating the fitness of a particle after decoding this service queue into a weighted DAG respectively.
+In particular, these two differences are related to sorting a created service queue using serivce-to-index mapping for a particle' position vectors and evaluating the fitness of a particle after decoding this service queue into a $WG$ respectively.
 Those differences are further addressed in Algorithms \ref{novelSteps} and \ref{graph_building} in \ref{POS-based_algomargin}.
@@
 In Algorithm \ref{novelSteps}, the  steps $4$, $5$, $6$ and $7$ are different from those of standard PSO: In step 4, the size of task-related service candidates generated by a greedy search determines the size of each particle's position, and each candidate in a created service candidates queue is mapped to an index of a particle’s position vectors, where each vector has a weight value between 0.0 and 1.0.
-In step 5, all the task-related service candidates in the queue are sorted according to their corresponding weight values in descending order.
-In step 6, this sorted queue is used as one of the inputs of the forward decoding algorithm \ref{graph_building} to create a weighted DAG.
-In step 7, this fitness value of this weighted DAG is the fitness value of the particle calculated by the comprehensive model discussed in \ref{Comprehensive_Quality_Model}.
+In step 5, service candidates in the queue are sorted according to their corresponding weight values in descending order.
+In step 6, this sorted queue is used as one of the inputs of the forward decoding algorithm \ref{graph_building} to create a $WG$.
+In step 7, the fitness value of this $WG$ is the fitness value of the particle calculated by the comprehensive model discussed in \ref{Comprehensive_Quality_Model}.
 \begin{algorithm}
@@
 This algorithm take one input, a sorted service queue from step 5 of Algorithm \ref{novelSteps}.
-If service queues are sorted resulting in different service order, it is possible to create different corresponding weighted DAGs as composition solutions.
+If service queues are sorted resulting in different service order, it is possible to create different corresponding $WGs$ as composition solutions.
 In addition.
@@
 This $S$ is added to $V$ and its outputs are added to $OutputSet$, and $S$ is removed from $queue$.
-Meanwhile, $e$ is created with its $sm_{e}$ calculated based on the aggregation value of all semantic matchmaking qualities from each satisfied input of $S$.
-These steps are repeated until all  $O_{T}$ can be satisfied by $Outputset$ or the service queue is $null$.
+Meanwhile, $e$ is created with $type_e$ and $sim_e$ calculated.
+These steps are repeated until $O_{T}$ can be satisfied by $Outputset$ or the service queue is $null$.
 Consequently, this forward graph building technique could lead to more services and edges connected to the $WG$, which should be removed before $WG$ is returned.
@@
  $OutputSet \leftarrow$ \{$I_{T}$\}\;
-  \While { all $O_{T}$ do not satisfied by $OutputSet$}{
+  \While { $O_{T}$ do not satisfied by $OutputSet$}{
      \ForEach{$S$ in $queue$}{
       \uIf{all $I_{S}$ satisfied by $OutputSet$}{    
-    		 \ForEach{$I_{S}$}{
-		$sm(a \in Outputset, b \in I_{S}) \leftarrow$ query $cache$\;
-              }
-        $e \leftarrow$ calculate aggregated $sm_{e}$\;
+        $e \leftarrow$ calcuate $type_e$, $sim_e$\;
         $E$ add $e$\;
@@
 
+\vspace{-1.0cm}
+
 \section{Experiment Study}\label{experiment_design}
-In this section, a quantitative evaluation approach is adopted in our experiment design using an augmented version of Web service challenge 2009 including QoS attributes, which is used in \cite{ma2015hybrid,da2016genetic}.
+In this section, a quantitative evaluation approach is adopted in our experiment using a benchmark dataset, an augmented version of Web service challenge 2009 including QoS attributes, which is used in \cite{ma2015hybrid,da2016genetic}.
 Two objectives of this evaluation are to: $(1)$ measure the effectiveness of our PSO-based approach.

### 2017-04-01 paper.tex
update

@@
 \maketitle
+\vspace{-0.8cm}
 \begin{abstract}
@@
 Therefore, we propose a comprehensive quality model considering semantic matchmaking quality and QoS simultaneously with an aim of achieving a more desirable balance on both sides.
-Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model.
+Further, we develop a PSO-based service composition approach with explicit support for the comprehensive model.
 We also conduct experiments to address the effectiveness of our PSO-based approach and a desirable balance achieved using our comprehensive quality model.
@@
 \end{abstract}
+\vspace{-0.8cm}
 \section{Introduction}\label{introduction}
@@
 \textit{Semantic web services composition} is distinguished from the syntactic service composition, the resources of semantic web services are described semantically to enable a better interoperability for chaining web services.
-The second challenge is related to QoS optimisation.
+Another challenge is related to QoS optimisation.
 This problem gives birth to \textit{QoS-aware service composition} that aims to find composition solutions with optimised QoS.
@@
 \end{enumerate}
+\vspace{-0.5cm}
 \section{Related Work} \label{relatedWork}
@@
 We will then propose a PSO-based approach to this semantic service composition using our proposed comprehensive quality model to evaluate candidate solutions.
+\vspace{-0.3cm}
 
@@
 
-\noindent with a suitable parameter $p, 0<p< 1$ to chosen, for discussion see Section \ref{PSO_based_approach}.
-However, if more than one pair of matched output and input from services $S$ and $S'$ respectively, $type_e$ and $sim_e$ will take on their average values.
+\noindent with a suitable parameter $p, 0<p< 1$ to chosen, for discussion see \ref{PSO_based_approach}.
+However, if more than one pair of matched output and input exist from services $S$ and $S'$ respectively, $type_e$ and $sim_e$ will take on their average values.
 
@@
 $MT$ and $S$ have minimum value 0 and maximum value 1.
-The minimum and maximum value of $A$, $R$, $T$, and $C$ are calculated across all task-related candidates in the service repository $\mathcal{SR}$ using greedy search, for discussion see Section \ref{PSO_based_approach}.
+The minimum and maximum value of $A$, $R$, $T$, and $C$ are calculated across all task-related candidates in the service repository $\mathcal{SR}$ using greedy search, for discussion see \ref{PSO_based_approach}.
 
@@
 For example, GP-based approaches often require repairing the solutions \cite{da2016particle}.
-Therefore, we employ a PSO-based approach to comprehensive quality-aware automated semantic web service composition.
+Therefore, we propose a PSO-based approach to comprehensive quality-aware automated semantic web service composition.
 Fig.
@@
 
-\subsection{PSO-based approach algorithm}\label{POS-based_algomargin}
+\subsection{PSO-based Approach Algorithm}\label{POS-based_algomargin}
 The overall algorithm investigated here is made up of a PSO-based web service composition algorithm \ref{novelSteps} and a decoding algorithm \ref{graph_building}.
@@
      Sort the service queue by position vectors' weights\;
-     Create a weighted DAG from the service queue ( Algorithm\ref{graph_building}) \;
+     Create a weighted DAG from the service queue (Algorithm\ref{graph_building}) \;
      Calculate the weighted DAG fitness value\;
@@
 
-Algorithm  \ref{graph_building} is a forward graph building algorithm based on \cite{blum1997fast}.
+Algorithm  \ref{graph_building} is a forward graph building algorithm extended from \cite{blum1997fast}.
 This algorithm take one input, a sorted service queue from step 5 of Algorithm \ref{novelSteps}.
-If service queues are sorted resulting in different service order, it is possible to create different corresponding $WGs$ as composition solutions.
+Note that different service queues may lead to different $WGs$.
 In addition.
@@
 \section{Experiment Study}\label{experiment_design}
-In this section, a quantitative evaluation approach is adopted in our experiment using a benchmark dataset, an augmented version of Web service challenge 2009 including QoS attributes, which is used in \cite{ma2015hybrid,da2016genetic}.
-Two objectives of this evaluation are to: $(1)$ measure the effectiveness of our PSO-based approach.
+In this section, we employ a quantitative evaluation approach with a benchmark dataset used in \cite{ma2015hybrid,da2016genetic}, an augmented version of Web Service Challenge 2009(wsc09) including QoS attributes.
+Two objectives of this evaluation are to: $(1)$ measure the effectiveness of our PSO-based approach, see comparision test in \ref{comparisonTestWithGP}.
 %To do this, we compare our PSO-based method with one existing GP-based approach \cite{ma2015hybrid}. 
-$(2)$ measure the effectiveness of our proposed comprehensive quality model for achieving desirable balance of semantic matchmaking quality and QoS. 
+$(2)$ measure the effectiveness of our proposed comprehensive quality to achieve a desirable balance on semantic matchmaking quality and QoS, see comparision test in \ref{comparisonTest}.
 %To do this, we compare a widely used QoS model in QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol} with our comprehensive quality model using our PSO-based approach.
@@
 
-The parameters are chosen based on the settings from \cite{shi2001particle} for our PSO-based approach, In particular, PSO population size is 30 with 100 generations.
+The parameters for the PSO are chosen from the settings from \cite{shi2001particle}, In particular, PSO population size is 30 with 100 generations.
 We run 30 times independently for each dataset.
-We configure the weights of fitness function to properly balance functional side and nonfunctional side.
+We configure the weights of fitness function to properly balance semantic matchmaking quality and QoS.
 Therefore, $w_{1}$ and $w_{2}$ are set equally to 0.25, and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125.
-The returned value of $type(a,b)$ is set to 1 ($Exact$) and 0.75 ($Plugin$) according to \cite{lecue2009optimizing}.
-In general, weight settings and parameter match type quality are decided by users' preferences.
-
+The $p$ of $type_e$ is set to 0.75 ($plugin match$) according to \cite{lecue2009optimizing}.
+In general, weight settings and parameter $p$ are decided by users' preferences.
+\vspace{-0.5cm}
 \subsection{Comparison Test for GP-based approach and PSO-based approach}\label{comparisonTestWithGP}
-To evaluate the effectiveness of our proposed PSO-based approach, we compare one recent GP-based approach \cite{ma2015hybrid} with our PSO-based method.
-The semantic matchmaking quality of this GP-based approach is easy to evaluated considering measuring links between parent nodes and children nodes.
-Therefore, we evaluate both semantic matchmaking quality and QoS simultaneously for that GP-based approach using the proposed comprehensive quality model.
-To make a fair comparison, we consider the same number of evaluations (3000 times) used in our PSO-based approach.
+To evaluate the effectiveness of our proposed PSO-based approach, we compare one recent GP-based approach \cite{ma2015hybrid} with our PSO-based method using our proposed comprehensive quality model.
+We extend the GP-based approach by measuring the semantic matchmaking quality between parent nodes and children nodes.
+To make a fair comparison, we use the same number of evaluations (3000 times) for these two approach.
 We set the parameters' settings of that GP-based approach as 30 individuals and 100 generations, it is considered to be proper settings refering to \cite{da2015gp}.
 
-The first column of Table \ref{meanFitness} shows five tasks from WSC09 Dataset.
-The second and third column of Table \ref{meanFitness} show the orginal service repository size before the greedy search and shrunk service repository size after the greedy search respectively regarding the five tasks.
-This greedy search helps reducing the repository size by considering only task-related service candidates, which also contributes to a significant reduced researching space.
+The first column of Table \ref{meanFitness} shows five tasks from WSC09.
+The second and third column of Table \ref{meanFitness} show the orginal service repository size before the greedy search and the shrunk service repository size after the greedy search respectively regarding the five tasks.
+This greedy search helps reducing the original repository size significantly, which contributes to a reduced searching space.
 The fourth and fifth column of Table \ref{meanFitness} show the mean fitness values of 30 independent runs accomplished by two methods.
@@
 On the other hand, the decoding process used by the PSO-based approach allows for small changes that more effectively prevent this from happening.
+\vspace{-0.8cm}
 \begin{table}[]
 \centering
-\caption{Mean fitness results for comparing GP-based approach}
+\caption{Mean fitness values for comparing GP-based approach}
 \label{meanFitness}
@@
 \hline
-\multicolumn{1}{c|}{WSC09} &Original $SR$  &Shrunken $SR$   &PSO-based approach & GP-based approach  \\ \hline
+\multicolumn{1}{c|}{WSC09} &Original $\mathcal{SR}$  &Shrunken $\mathcal{SR}$   &PSO-based approach & GP-based approach  \\ \hline
 Task 1                     &572            &80    &0.5592 $\pm$ 0.0128  $\uparrow$  &0.5207 $\pm$ 0.0208           \\ \hline
@@
 \end{table}
+\vspace{-0.8cm}
 
@@
 Recently, a QoS Evaluation Model, $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$, where $\sum_{i=1}^{4} w_i = 1$, is widely used for QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol}.
-This QoS evluation model is compared to our proposed comprehensive quality evluation model using our proposed PSO-based approach for measuring the effectiveness of our proposed comprehensive quality model.
-To analyse the differences in optimal solutions found by these two evaluation models, we recorded and compared the different mean values of $SM$ (consisiting of $MT$ and $S$), $QoS$(consisting of $A$, $R$, $T$ and $C$) after 100 generations.
+This QoS evaluation model is compared to our proposed comprehensive quality model using our PSO-based approach.
+To address a desirable balance achieved by our comprehensive quality model, we compare optimal solutions found by these two evaluation models, we record and compare the different mean values of $SM$ ($SM = w_1 \hat{MT} + w_2 \hat{SIM}$, where $\sum_{i=1}^{2} w_i = 1$), $QoS$($QoS = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$, where $\sum_{i=1}^{4} w_i = 1$) after 100 generations.
 To make a sense of the comparison, all these recorded values are normalised from 0 to 1, and compared using independent-samples T tests in Table \ref{decisionTable}.
@@
 However, the mean value of $SM$ using the comprehensive quality evaluation model are significantly higher than those using the QoS evaluation model, while a slight trade-off in $QoS$ are observed in all tasks.
-
+\vspace{-0.8cm}
 \begin{table}[]
@@
 \end{table}
-
+\vspace{-0.8cm}
 \subsection{Further Discussion}\label{discuss1}
-
-To determine the importance of achieving a good comprehensive quality at the expense of slightly reduced QoS, we demonstrate the best solutions identified by our approach using task 3 as an example.
+To analyze the effectiveness of achieving a good comprehensive quality at the expense of slightly reduced QoS, we demonstrate two best solutions produced using task 3 as an example.
 Fig.
-\ref{comparisontest} $(1)$ and $(2)$ show two weighted DAGs obtained by employing the QoS evaluation model and the comprehensive quality evaluation model respectively.
+\ref{comparisontest} $(1)$ and $(2)$ show two $WGs$ obtained by employing the QoS evaluation model and the comprehensive quality evaluation model respectively.
 Both weighted DAGs have exactly the same service workflow structure, but some service vertices and edges denoted in red are different.
@@
 \ref{comparisontest} $(3)$, where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) of the listed qualities for our comprehensive quality evalutaion model.
-Therefore, an overall gain 0.1433 is calculated from a sum of a $SM$ gain (0.1467) and $QoS$ loss (-0.0034).
-Consequently, our comprehensive evaluation model acheive a desirable trade-off in considering both $SM$ and $QoS$.
-To explain the value of $SM$ gain, we pick up $e_4$ that is associated with the smallest $\Delta Q$.
-The $e_4$ of $WG(1)$ using QoS evaluation model and $WG(2)$ using comprehensive quality model has two different source service vertices $Ser1640238160$ and $Ser947554374$ respectively,  and the same $end$ vertices.
-$Ser1640238160$ and $Ser947554374$ are services with concept-related output parameters $Inst795998200$ and $Inst582785907$ corresponds to two concepts $Con103314376$ and $Con2037585750$ respectively, which are marked on the related taxonomy in Fig.
+Therefore, an overall gain 0.1433 is calculated from a sum of a $SM$ gain (0.1467) and $QoS$ loss (-0.0034) using comprehensive quality evaluation model.
+To understand the improvement of semantic matchmaking quality from these numbers, we pick up $e_4$ that is associated with the smallest $\Delta Q$.
+The $e_4$ of Fig.
+\ref{comparisontest} $(1)$ and Fig.
+\ref{comparisontest} $(2)$ has two different source service vertices, $Ser1640238160$ and $Ser947554374$, and the same $end$ vertices.
+$Ser1640238160$ and $Ser947554374$ are services with concept-related output parameters $Inst795998200$ and $Inst582785907$ corresponds to two concepts $Con103314376$ and $Con2037585750$ respectively in the ontology shown in Fig.
 \ref{comparisontest} $(4)$.
-In addtion, $Inst658772240$ is a required parameter of the $end$ vertice as one of composition task outputs, which is related to concept $Con2113572083$.
+In addtion, $Inst658772240$ is a required parameter of the $end$ vertice, which is related to concept $Con2113572083$.
 Obviouly,  $Inst795998200$ is closer to user's required output $Inst658772240$ compared to $Inst582785907$.
+\vspace{-0.6cm}
 
@@
 \end{figure}
+\vspace{-1.0cm}
 
 \section{Conclusion}\label{conclusion}
-This work introduces a comprehensive evaluation model for considering semantic matchmaking quality and QoS simultaneously.
-We proposed a PSO-based service composition approach utilising our proposed quality mode that can achieve a desirable trade-off of both quality aspects.
-In addtion, we compare one recent GP-approach with our PSO-based method to show our performance that results in finding more optimised solutions.
+
+In this work, we propose a PSO-based approach to comprehensive quality-aware semantic web service composition, which produces serivce composition solutions with a desirable balance on both semantic matchmaking quality and QoS.
 Future works can investigate multi-objective EC techniques to produce a set of composition solutions for the situations when the quality preference is not known.
 
+\vspace{-0.3cm}
 \bibliographystyle{splncs03}

### 2017-04-01 paper.tex
update

@@
 For a service composition with services $ S_1, S_2, ...
-S_n$ we obtain the reliabilitiy $R=\prod\limits^n_{k=1}r_{S_k}$, the availability $A=\prod\limits^n_{k=1}a_{S_k}$, the cost $C=\sum\limits^n_{k=1}c_{S_k}$, and the response time $T$ is the time of most time-consumption path in the composition, i.e., $$T = MAX \{\sum\limits^{\ell_j}_{k=1}t_{S_k} | \text{ $j\in\{1,\ldots,m\}$ and $P_j$ is a path of length $\ell_j$}\}.$$
+S_n$ we obtain the reliability $R=\prod\limits^n_{k=1}r_{S_k}$, the availability $A=\prod\limits^n_{k=1}a_{S_k}$, the cost $C=\sum\limits^n_{k=1}c_{S_k}$, and the response time $T$ is the time of most time-consumption path in the composition, i.e., $$T = MAX \{\sum\limits^{\ell_j}_{k=1}t_{S_k} | \text{ $j\in\{1,\ldots,m\}$ and $P_j$ is a path of length $\ell_j$}\}.$$
 
@@
       \uIf{all $I_{S}$ satisfied by $OutputSet$}{    
-        $e \leftarrow$ calcuate $type_e$, $sim_e$\;
+        $e \leftarrow$ calculate $type_e$, $sim_e$\;
         $E$ add $e$\;
@@
 In this section, we employ a quantitative evaluation approach with a benchmark dataset used in \cite{ma2015hybrid,da2016genetic}, an augmented version of Web Service Challenge 2009(wsc09) including QoS attributes.
-Two objectives of this evaluation are to: $(1)$ measure the effectiveness of our PSO-based approach, see comparision test in \ref{comparisonTestWithGP}.
+Two objectives of this evaluation are to: $(1)$ measure the effectiveness of our PSO-based approach, see comparison test in \ref{comparisonTestWithGP}.
 %To do this, we compare our PSO-based method with one existing GP-based approach \cite{ma2015hybrid}. 
-$(2)$ measure the effectiveness of our proposed comprehensive quality to achieve a desirable balance on semantic matchmaking quality and QoS, see comparision test in \ref{comparisonTest}.
+$(2)$ measure the effectiveness of our proposed comprehensive quality to achieve a desirable balance on semantic matchmaking quality and QoS, see comparison test in \ref{comparisonTest}.
 %To do this, we compare a widely used QoS model in QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol} with our comprehensive quality model using our PSO-based approach.
@@
 To make a fair comparison, we use the same number of evaluations (3000 times) for these two approach.
-We set the parameters' settings of that GP-based approach as 30 individuals and 100 generations, it is considered to be proper settings refering to \cite{da2015gp}.
+We set the parameters' settings of that GP-based approach as 30 individuals and 100 generations, it is considered to be proper settings referring to \cite{da2015gp}.
 
 The first column of Table \ref{meanFitness} shows five tasks from WSC09.
-The second and third column of Table \ref{meanFitness} show the orginal service repository size before the greedy search and the shrunk service repository size after the greedy search respectively regarding the five tasks.
+The second and third column of Table \ref{meanFitness} show the original service repository size before the greedy search and the shrunk service repository size after the greedy search respectively regarding the five tasks.
 This greedy search helps reducing the original repository size significantly, which contributes to a reduced searching space.
@@
 We employ independent-samples T tests to test the significant differences in mean fitness value.
-The results show that the PSO-based approach outperformes the existing GP-based approach in most cases except task 3 (all the p-values are consistently smaller than 0.01).
+The results show that the PSO-based approach outperforms the existing GP-based approach in most cases except task 3 (all the p-values are consistently smaller than 0.01).
 In task 5, the PSO-based approach performs significantly better than the GP-based approach in finding optimal solutions.
@@
 \subsection{Further Discussion}\label{discuss1}
-To analyze the effectiveness of achieving a good comprehensive quality at the expense of slightly reduced QoS, we demonstrate two best solutions produced using task 3 as an example.
+To analyse the effectiveness of achieving a good comprehensive quality at the expense of slightly reduced QoS, we demonstrate two best solutions produced using task 3 as an example.
 Fig.
@@
 To better understand these differences, we list the overall semantic matchmaking quality $SM$,  overall $QoS$ and semantic matchmaking quality associated to each edge ($sm_{e_1}$ to $sm_{e_4}$) in Fig.
-\ref{comparisontest} $(3)$, where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) of the listed qualities for our comprehensive quality evalutaion model.
+\ref{comparisontest} $(3)$, where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) of the listed qualities for our comprehensive quality evaluation model.
 Therefore, an overall gain 0.1433 is calculated from a sum of a $SM$ gain (0.1467) and $QoS$ loss (-0.0034) using comprehensive quality evaluation model.
@@
 \ref{comparisontest} $(4)$.
-In addtion, $Inst658772240$ is a required parameter of the $end$ vertice, which is related to concept $Con2113572083$.
-Obviouly,  $Inst795998200$ is closer to user's required output $Inst658772240$ compared to $Inst582785907$.
+In addition, $Inst658772240$ is a required parameter of the $end$ service, and related to concept $Con2113572083$.
+Obviously,  $Inst795998200$ is closer to user's required output $Inst658772240$ compared to $Inst582785907$.
 \vspace{-0.6cm}
@@
 \includegraphics[scale=.29]{comparisontest.pdf}}}
- \caption{An example of comparision to optimal solutions using Task 3 for QoS evaluation model and comprehensive quality evluation model.}
+ \caption{An example of comparison to optimal solutions using Task 3 for QoS evaluation model and comprehensive quality evluation model.}
  \label{comparisontest}
@@
 
-In this work, we propose a PSO-based approach to comprehensive quality-aware semantic web service composition, which produces serivce composition solutions with a desirable balance on both semantic matchmaking quality and QoS.
+In this work, we propose a PSO-based approach to comprehensive quality-aware semantic web service composition, which produces service composition solutions with a desirable balance on both semantic matchmaking quality and QoS.
 Future works can investigate multi-objective EC techniques to produce a set of composition solutions for the situations when the quality preference is not known.

### 2017-04-02 paper.tex
update

@@
 \title{Comprehensive Quality Awareness Automated Semantic Web Service Composition}
-\author{Chen Wang, Hui Ma, Aaron Chen and Sven Hartmann}
-\institute{School of Engineering and Computer Science,
-\\Victoria University of Wellington, New Zealand \\
-Email: \{chen.wang, hui.ma, aaron.chen\}@ecs.vuw.ac.nz}
+\author{Chen Wang$^1$ \quad Hui Ma$^1$ \quad Aaron Chen$^1$ \quad Sven Hartmann$^2$}
+
+\institute{$^1$ School of Engineering and Computer Science, \\Victoria University of Wellington, New Zealand\\
+  \{chen.wang, hui.ma, aaron.chen\}@ecs.vuw.ac.nz \\[1ex]
+  $^2$ Department of Informatics, \\Clausthal University of Technology, Germany\\
+   sven.hartmann@tu-clausthal.de}
+
+%\author{Chen Wang, Hui Ma, Aaron Chen and Sven Hartmann}
+%\institute{School of Engineering and Computer Science,
+%\\Victoria University of Wellington, New Zealand \\
+%Email: \{chen.wang, hui.ma, aaron.chen\}@ecs.vuw.ac.nz}
 
@@
 Generating composition plans automatically in discovering and selecting suitable web services is a NP-hard problem \cite{moghaddam2014service}.
-In the past few years, many approaches \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive} to QoS-aware web service composition employ Evolutionary Computation (EC) techniques to automatically generate composition solutions, but few works have enabled an \textit{automatic semantic web service composition}, where both QoS and quality of semantic matchmaking are optimised simultaneously to achieve a desirable balance on both sides.
+In the past few years, many approaches \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive} to QoS-aware web service composition employ Evolutionary Computation (EC) techniques to automatically generate composition solutions.
+Genetic Programming (GP) based approaches produce promising results, but these approaches often require repairing or penalising the solutions \cite{ma2015hybrid,yu2013adaptive}.
+However, Particle Swarm Optimisation (PSO) is considered to be an easy way to maintain the correctness of solutions in solving combinatorial optimisation problems \cite{da2016particle}.
+All these works have enabled an \textit{automatic semantic web service composition}, but do not optimise QoS and quality of semantic matchmaking simultaneously to achieve a desirable balance on both sides.
 
 The overall goal of this paper is to \textit{develop a PSO-based approach to automated comprehensive quality-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}.
-Particularly, this paper extends existing works of QoS-aware service composition by considering jointly optimising QoS and semantic matchmaking quality using our proposed comprehensive quality model.
-Particle Swarm Optimisation (PSO) has shown promise in searching for near-optimised service composition solutions \cite{da2016particle}.
-We will propose a PSO-based service composition approach with explicit support for our proposed quality model.
+Particularly, this paper extends existing works of QoS-aware service composition by considering jointly optimising QoS and semantic matchmaking quality, which is proposed as a comprehensive quality model.
 We will achieve three objectives in this work:
@@
 
-QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques for finding near-optimised solutions.
+QoS-aware web service composition is studied using traditional approaches or EC techniques for finding near-optimised solutions.
 Qi et al.
@@
 Yu et al.
-\cite{yu2013adaptive} use Genetic Programming (GP) for finding optimal solutions that are reached by penalising infeasible solutions using a fitness function.
+\cite{yu2013adaptive} use GP for finding optimal solutions that are reached by penalising infeasible solutions using a fitness function.
 A hybrid approach employing a greedy search and GP is introduced in \cite{ma2015hybrid} to generate functionally correct tree-based individuals, which are transformed from \emph{directed acyclic graph}s (DAGs).
@@
 Another GA-based approach \cite{fanjiang2014semantic} utilise process description language to encode pre-stored cases-based workflows, where workable services are composed to complete this workflow.
-An automated immune-inspired web service composition approach \cite{pop2009immune} employs a clonal selection algorithm to proliferate decoded planning graphs, but this approach is only studied in some cases.
+An automated immune-inspired web service composition approach \cite{pop2009immune} employs a clonal selection algorithm to proliferate decoded planning graphs, but this approach is only evaluated with some simple cases.
 
@@
 Hence, a good balance between QoS and semantic matchmaking quality is called for.
-We therefore propose a comprehensive quality model in considering semantic matchmaking quality and QoS simultaneously.
+We therefore propose a \emph{comprehensive quality model} in considering semantic matchmaking quality and QoS simultaneously.
 
@@
 
-\noindent When multiple quality criteria are involved into decision making, then the overall fitness of a solution is evaluated by a proposed comprehensive quality model, which can be defined as a weighted sum of the individual criteria:
+\noindent When multiple quality criteria are involved into decision making, then the overall fitness of a solution is proposed as a \emph{comprehensive quality model}, which can be defined as a weighted sum of the individual criteria:
 
@@
 
-PSO has shown promise in solving combinatorial optimisation problems, and is also considered to be an easy way to maintain the correctness of solutions.
-For example, GP-based approaches often require repairing the solutions \cite{da2016particle}.
-Therefore, we propose a PSO-based approach to comprehensive quality-aware automated semantic web service composition.
+As PSO has shown promise in solving combinatorial optimisation problems, we propose a PSO-based approach to comprehensive quality-aware automated semantic web service composition.
 Fig.
@@
 \subsection{PSO-based Approach Algorithm}\label{POS-based_algomargin}
-The overall algorithm investigated here is made up of a PSO-based web service composition algorithm \ref{novelSteps} and a decoding algorithm \ref{graph_building}.
+The overall algorithm investigated here is made up of a PSO-based web service composition algorithm \ref{novelSteps} and a decoding Algorithm \ref{graph_building}.
 In Algorithm \ref{novelSteps}, the  steps $4$, $5$, $6$ and $7$ are different from those of standard PSO: In step 4, the size of task-related service candidates generated by a greedy search determines the size of each particle's position, and each candidate in a created service candidates queue is mapped to an index of a particle’s position vectors, where each vector has a weight value between 0.0 and 1.0.
 In step 5, service candidates in the queue are sorted according to their corresponding weight values in descending order.
-In step 6, this sorted queue is used as one of the inputs of the forward decoding algorithm \ref{graph_building} to create a $WG$.
-In step 7, the fitness value of this $WG$ is the fitness value of the particle calculated by the comprehensive model discussed in \ref{Comprehensive_Quality_Model}.
+In step 6, this sorted queue is used as one of the inputs of the forward decoding Algorithm \ref{graph_building} to create a $WG$.
+In step 7, the fitness value of the created $WG$ is the fitness value of the particle calculated by the comprehensive model discussed in \ref{Comprehensive_Quality_Model}.
 \begin{algorithm}
@@
      Sort the service queue by position vectors' weights\;
-     Create a weighted DAG from the service queue (Algorithm\ref{graph_building}) \;
-     Calculate the weighted DAG fitness value\;
+     Create a $WG$ from the service queue (Algorithm\ref{graph_building}) \;
+     Calculate the $WG$ fitness value\;
 
@@
 This $S$ is added to $V$ and its outputs are added to $OutputSet$, and $S$ is removed from $queue$.
-Meanwhile, $e$ is created with $type_e$ and $sim_e$ calculated.
+Meanwhile, $e$ is created with $type_e$ and $sim_e$ calculated using infomation provided from $cache$.
 These steps are repeated until $O_{T}$ can be satisfied by $Outputset$ or the service queue is $null$.
@@
       \uIf{all $I_{S}$ satisfied by $OutputSet$}{    
-        $e \leftarrow$ calculate $type_e$, $sim_e$\;
+        $e \leftarrow$ calculate $type_e$, $sim_e$ using $cache$\;
         $E$ add $e$\;
@@
  %}
- \caption{Create a weighted DAG from a  sorted queue.}
+ \caption{Create a $WG$ from a sorted service queue.}
 \label{graph_building}
@@
 %To do this, we compare our PSO-based method with one existing GP-based approach \cite{ma2015hybrid}. 
-$(2)$ measure the effectiveness of our proposed comprehensive quality to achieve a desirable balance on semantic matchmaking quality and QoS, see comparison test in \ref{comparisonTest}.
+$(2)$ measure the effectiveness of our proposed comprehensive quality model to achieve a desirable balance on semantic matchmaking quality and QoS, see comparison test in \ref{comparisonTest}.
 %To do this, we compare a widely used QoS model in QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol} with our comprehensive quality model using our PSO-based approach.
@@
 This QoS evaluation model is compared to our proposed comprehensive quality model using our PSO-based approach.
-To address a desirable balance achieved by our comprehensive quality model, we compare optimal solutions found by these two evaluation models, we record and compare the different mean values of $SM$ ($SM = w_1 \hat{MT} + w_2 \hat{SIM}$, where $\sum_{i=1}^{2} w_i = 1$), $QoS$($QoS = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$, where $\sum_{i=1}^{4} w_i = 1$) after 100 generations.
+To address a desirable balance achieved by our comprehensive quality model, we compare optimal solutions found by these two evaluation models, we record and compare the different mean values of $SM$ ($SM = 0.5 \hat{MT} + 0.5 \hat{SIM}$), $QoS$($QoS = 0.25 \hat{A} + 0.25 \hat{R} + 0.25(1 - \hat{T}) + 0.25(1 - \hat{C})$) after 100 generations.
 To make a sense of the comparison, all these recorded values are normalised from 0 to 1, and compared using independent-samples T tests in Table \ref{decisionTable}.
@@
 \centering
-\caption{Mean values of $SM$ and $QoS$ for QoS evaluation model and comprehensive quality evaluation model using PSO-based approach}
+\caption{Mean values of $SM$, $QoS$ and sum of $SM$ and $QoS$ for QoS evaluation model and comprehensive quality evaluation model using PSO-based approach}
 \label{decisionTable}
-\begin{tabular}{c|l|l|l}
+\begin{tabular}{c|c|l|l}
 \hline
 \multicolumn{2}{c|}{WSC09}              & \shortstack{QoS \\ Evaluation Model}         &\shortstack{Comprehensive Quality \\ Evaluation Model} \\ \hline
-\multirow{2}{*}{Task1}  &$SM$   &0.5373 $\pm$ 0.0267               &0.5580 $\pm$ 0.0094 $\uparrow$ \\ \cline{2-4}
-                        &$QoS$  &0.5574 $\pm$ 0.0156               &0.5604 $\pm$ 0.0164                          \\ \hline
-\multirow{2}{*}{Task2}  &$SM$   &0.4549 $\pm$ 0.0033               &0.4630 $\pm$ 0.0042 $\uparrow$ \\ \cline{2-4} 
-                        &$QoS$  &0.4800 $\pm$ 0.0012 $\uparrow$    &0.4772 $\pm$ 0.0025 \\ \hline
-\multirow{2}{*}{Task3}  &$SM$   &0.5538 $\pm$ 0.0082               &0.6093 $\pm$ 0.0054 $\uparrow$   \\ \cline{2-4} 
-                        &$QoS$  &0.4940 $\pm$ 0.0013 $\uparrow$    &0.4913 $\pm$ 0.0009            \\ \hline
+\multirow{3}{*}{Task1}  &$SM$      &0.5373 $\pm$ 0.0267               &0.5580 $\pm$ 0.0094 $\uparrow$ \\ \cline{2-4}
+                        &$QoS$     &0.5574 $\pm$ 0.0156               &0.5604 $\pm$ 0.0164            \\ \cline{2-4}
+                        &$SM+QoS$  &0.5574 $\pm$ 0.0156               &0.5604 $\pm$ 0.0164            \\ \hline
+\multirow{3}{*}{Task2}  &$SM$      &0.4549 $\pm$ 0.0033               &0.4630 $\pm$ 0.0042 $\uparrow$ \\ \cline{2-4} 
+                        &$QoS$     &0.4800 $\pm$ 0.0012 $\uparrow$    &0.4772 $\pm$ 0.0025            \\ \cline{2-4}
+                        &$SM+QoS$  &0.5574 $\pm$ 0.0156               &0.5604 $\pm$ 0.0164            \\ \hline
+\multirow{3}{*}{Task3}  &$SM$      &0.5538 $\pm$ 0.0082               &0.6093 $\pm$ 0.0054 $\uparrow$ \\ \cline{2-4} 
+                        &$QoS$     &0.4940 $\pm$ 0.0013 $\uparrow$    &0.4913 $\pm$ 0.0009            \\ \cline{2-4}
+                        &$SM+QoS$  &0.5574 $\pm$ 0.0156               &0.5604 $\pm$ 0.0164            \\ \hline
 \multirow{3}{*}{Task4}  &$SM$      &0.4398 $\pm$ 0.0037               &0.4604 $\pm$ 0.0000 $\uparrow$ \\ \cline{2-4} 
-                        &$QoS$  &0.4845 $\pm$ 0.0010 $\uparrow$    &0.4734 $\pm$ 0.0044  \\ \hline
+                        &$QoS$     &0.4845 $\pm$ 0.0010 $\uparrow$    &0.4734 $\pm$ 0.0044            \\ \cline{2-4}
+                        &$SM+QoS$  &0.5574 $\pm$ 0.0156               &0.5604 $\pm$ 0.0164            \\ \hline
 \multirow{3}{*}{Task5}  &$SM$      &0.4580 $\pm$ 0.0065               &0.4639 $\pm$ 0.0013 $\uparrow$ \\ \cline{2-4} 
-                        &$QoS$  &0.4764 $\pm$ 0.0005 $\uparrow$    &0.4750 $\pm$ 0.0007  \\ \hline                                                   
+                        &$QoS$     &0.4764 $\pm$ 0.0005 $\uparrow$    &0.4750 $\pm$ 0.0007            \\ \cline{2-4}
+                        &$SM+QoS$  &0.5574 $\pm$ 0.0156               &0.5604 $\pm$ 0.0164            \\ \hline
 \end{tabular}
@@
 Both weighted DAGs have exactly the same service workflow structure, but some service vertices and edges denoted in red are different.
-To better understand these differences, we list the overall semantic matchmaking quality $SM$,  overall $QoS$ and semantic matchmaking quality associated to each edge ($sm_{e_1}$ to $sm_{e_4}$) in Fig.
-\ref{comparisontest} $(3)$, where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) of the listed qualities for our comprehensive quality evaluation model.
+To better understand these differences, we list the overall semantic matchmaking quality $SM$,  overall $QoS$ and semantic matchmaking quality associated to each edge in Fig.
+\ref{comparisontest} $(3)$ (Note: $sm_{e_n} = 0.5type_{e_n} + 0.5 sim_{e_n}$), where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) of the listed qualities for our comprehensive quality evaluation model.
 Therefore, an overall gain 0.1433 is calculated from a sum of a $SM$ gain (0.1467) and $QoS$ loss (-0.0034) using comprehensive quality evaluation model.

### 2017-04-02 paper.tex
update

@@
 To meet users' requirements, one often needs to consider both semantic matchmaking quality and QoS simultaneously.
-Existing works on web service composition focus mainly on one single type of requirements.
+Existing works on web service composition focus mainly on one single type of quality requirements.
 Therefore, we propose a comprehensive quality model considering semantic matchmaking quality and QoS simultaneously with an aim of achieving a more desirable balance on both sides.
@@
 %This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems. 
-
 Two most notable challenges for web service composition are ensuring interoperability of services and achieving Quality of Service (QoS) optimisation \cite{fensel2011semantic}.
@@
 For concepts $a, b$ in $\mathcal{O}$ the \emph{semantic similarity} $sim(a, b)$ is calculated based on the edge counting method defined in the formula (\ref{equation1}) from \cite{shet2012new}, where $N_a$, $N_b$ and $N_c$ measure the distances from concept $a$, concept $b$, and a closest common ancestor $c$ of $a$ and $b$ to the top concept of the ontology $\mathcal{O}$, respectively.
+\vspace{-0.2cm}
 
@@
 \end{equation}
-
 \noindent For our purposes, $\lambda$ can be set to 0 as we do not measure the similarities of neighbourhood concepts, which is not the matching type considered in this paper. 
@@
 Based on the matchmaking type the \emph{semantic matchmaking quality} of edge $e$ can be defined as follows:
-
+\vspace{-0.2cm}
 \begin{equation}
@@
 The \emph{semantic matchmaking quality} of the service composition can be obtained by aggregating over all edges in $E$ as follows:
-
 %\begin{equation}
@@
 %\end{equation}
+\vspace{-0.2cm}
 \begin{equation}
@@
 In step 7, the fitness value of the created $WG$ is the fitness value of the particle calculated by the comprehensive model discussed in \ref{Comprehensive_Quality_Model}.
+\vspace{-0.5cm}
 \begin{algorithm}
@@
 
+\vspace{-0.5cm}
 Algorithm  \ref{graph_building} is a forward graph building algorithm extended from \cite{blum1997fast}.
@@
 Consequently, this forward graph building technique could lead to more services and edges connected to the $WG$, which should be removed before $WG$ is returned.
+\vspace{-0.5cm}
 
@@
 
-\vspace{-1.0cm}
+\vspace{-1.2cm}
 
 \section{Experiment Study}\label{experiment_design}
-In this section, we employ a quantitative evaluation approach with a benchmark dataset used in \cite{ma2015hybrid,da2016genetic}, an augmented version of Web Service Challenge 2009(wsc09) including QoS attributes.
-Two objectives of this evaluation are to: $(1)$ measure the effectiveness of our PSO-based approach, see comparison test in \ref{comparisonTestWithGP}.
+In this section, we employ a quantitative evaluation approach with a benchmark dataset used in \cite{ma2015hybrid,da2016genetic}, an augmented version of Web Service Challenge 2009 (WSC09) including QoS attributes.
+Two objectives of this evaluation are to: $(1)$ evaluate the effectiveness of our PSO-based approach, see comparison test in \ref{comparisonTestWithGP}.
 %To do this, we compare our PSO-based method with one existing GP-based approach \cite{ma2015hybrid}. 
-$(2)$ measure the effectiveness of our proposed comprehensive quality model to achieve a desirable balance on semantic matchmaking quality and QoS, see comparison test in \ref{comparisonTest}.
+$(2)$ evaluate the effectiveness of our proposed comprehensive quality model to achieve a desirable balance on semantic matchmaking quality and QoS, see comparison test in \ref{comparisonTest}.
 %To do this, we compare a widely used QoS model in QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol} with our comprehensive quality model using our PSO-based approach.
@@
 Therefore, $w_{1}$ and $w_{2}$ are set equally to 0.25, and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125.
-The $p$ of $type_e$ is set to 0.75 ($plugin match$) according to \cite{lecue2009optimizing}.
+The $p$ of $type_e$ is set to 0.75 ($plugin$ match) according to \cite{lecue2009optimizing}.
 In general, weight settings and parameter $p$ are decided by users' preferences.
@@
 \subsection{Comparison Test for GP-based approach and PSO-based approach}\label{comparisonTestWithGP}
-To evaluate the effectiveness of our proposed PSO-based approach, we compare one recent GP-based approach \cite{ma2015hybrid} with our PSO-based method using our proposed comprehensive quality model.
+To evaluate the effectiveness of our proposed PSO-based approach, we compare our PSO-based method with one recent GP-based approach \cite{ma2015hybrid} using our proposed comprehensive quality model.
 We extend the GP-based approach by measuring the semantic matchmaking quality between parent nodes and children nodes.
 To make a fair comparison, we use the same number of evaluations (3000 times) for these two approach.
-We set the parameters' settings of that GP-based approach as 30 individuals and 100 generations, it is considered to be proper settings referring to \cite{da2015gp}.
+We set the parameters of that GP-based approach as 30 individuals and 100 generations, which is considered to be proper settings referring to \cite{da2015gp}.
 
 The first column of Table \ref{meanFitness} shows five tasks from WSC09.
-The second and third column of Table \ref{meanFitness} show the original service repository size before the greedy search and the shrunk service repository size after the greedy search respectively regarding the five tasks.
+The second and third column of Table \ref{meanFitness} show the original service repository size and the shrunk service repository size after the greedy search respectively regarding the five tasks.
 This greedy search helps reducing the original repository size significantly, which contributes to a reduced searching space.
@@
 We employ independent-samples T tests to test the significant differences in mean fitness value.
-The results show that the PSO-based approach outperforms the existing GP-based approach in most cases except task 3 (all the p-values are consistently smaller than 0.01).
+The results show that the PSO-based approach outperforms the existing GP-based approach in most cases except task 3.
+Note that all the p-values are consistently smaller than 0.01.
 In task 5, the PSO-based approach performs significantly better than the GP-based approach in finding optimal solutions.
-It may be that the GP-based approach is stuck in local optima due to the very large search space in Task 5.
+It may be that the GP-based approach is stuck in local optima in a very large search space due to its evolutionary operators.
 On the other hand, the decoding process used by the PSO-based approach allows for small changes that more effectively prevent this from happening.
@@
 
-\subsection{Comparison Test for Comprehensive Quality Evaluation Model and QoS Evaluation Model}\label{comparisonTest}
+\subsection{Comparison Test for Comprehensive Quality Model and QoS Model}\label{comparisonTest}
 
-Recently, a QoS Evaluation Model, $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$, where $\sum_{i=1}^{4} w_i = 1$, is widely used for QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol}.
-This QoS evaluation model is compared to our proposed comprehensive quality model using our PSO-based approach.
-To address a desirable balance achieved by our comprehensive quality model, we compare optimal solutions found by these two evaluation models, we record and compare the different mean values of $SM$ ($SM = 0.5 \hat{MT} + 0.5 \hat{SIM}$), $QoS$($QoS = 0.25 \hat{A} + 0.25 \hat{R} + 0.25(1 - \hat{T}) + 0.25(1 - \hat{C})$) after 100 generations.
+Recently, a QoS Model, $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$, where $\sum_{i=1}^{4} w_i = 1$, is widely used for QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol}.
+To show the effectiveness of our proposed comprehensive quality model, we compare the best solutions found using our PSO-based approach evaluated by this QoS model and our comprehensive model.
+We record and compare the mean values of $SM$ ($SM = 0.5 \hat{MT} + 0.5 \hat{SIM}$), $QoS$($QoS = 0.25 \hat{A} + 0.25 \hat{R} + 0.25(1 - \hat{T}) + 0.25(1 - \hat{C})$) at 100 generations over 30 independent runs.
 To make a sense of the comparison, all these recorded values are normalised from 0 to 1, and compared using independent-samples T tests in Table \ref{decisionTable}.
@@
 We observe an interesting pattern from Table \ref{decisionTable}.
-The mean values of $QoS$ using QoS evaluation model are significantly higher than those using comprehensive quality evaluation model for Tasks 2, 3, 4 and 5.
-However, the mean value of $SM$ using the comprehensive quality evaluation model are significantly higher than those using the QoS evaluation model, while a slight trade-off in $QoS$ are observed in all tasks.
+The mean values of $QoS$ using QoS model are significantly higher than those using comprehensive quality model for Tasks 2, 3, 4 and 5.
+However, the mean value of $SM$ using the comprehensive quality model are significantly higher than those using the QoS model, while a slight trade-off in $QoS$ are observed in all tasks.
+In addition, our comprehensive model achieves a consistently higher comprehensive quality in terms of a combination of $SM$ and $QoS$, which is significantly better in task 1, 2, 3 and 4.
 \vspace{-0.8cm}
@@
 \centering
-\caption{Mean values of $SM$, $QoS$ and sum of $SM$ and $QoS$ for QoS evaluation model and comprehensive quality evaluation model using PSO-based approach}
+\caption{Mean values of $SM$, $QoS$ and sum of $SM$ and $QoS$ for QoS model and comprehensive quality model using PSO-based approach}
 \label{decisionTable}
@@
 \hline
-\multicolumn{2}{c|}{WSC09}              & \shortstack{QoS \\ Evaluation Model}         &\shortstack{Comprehensive Quality \\ Evaluation Model} \\ \hline
+\multicolumn{2}{c|}{WSC09}              & \shortstack{QoS \\ Model}         &\shortstack{Comprehensive Quality \\ Model} \\ \hline
 \multirow{3}{*}{Task1}  &$SM$      &0.5373 $\pm$ 0.0267               &0.5580 $\pm$ 0.0094 $\uparrow$ \\ \cline{2-4}
                         &$QoS$     &0.5574 $\pm$ 0.0156               &0.5604 $\pm$ 0.0164            \\ \cline{2-4}
-                        &$SM+QoS$  &0.5574 $\pm$ 0.0156               &0.5604 $\pm$ 0.0164            \\ \hline
+                        &$SM+QoS$  &1.0947 $\pm$ 0.0423               &1.1184 $\pm$ 0.0258 $\uparrow$ \\ \hline
 \multirow{3}{*}{Task2}  &$SM$      &0.4549 $\pm$ 0.0033               &0.4630 $\pm$ 0.0042 $\uparrow$ \\ \cline{2-4} 
                         &$QoS$     &0.4800 $\pm$ 0.0012 $\uparrow$    &0.4772 $\pm$ 0.0025            \\ \cline{2-4}
-                        &$SM+QoS$  &0.5574 $\pm$ 0.0156               &0.5604 $\pm$ 0.0164            \\ \hline
+                        &$SM+QoS$  &0.9349 $\pm$ 0.0045               &0.9402 $\pm$ 0.0067 $\uparrow$           \\ \hline
 \multirow{3}{*}{Task3}  &$SM$      &0.5538 $\pm$ 0.0082               &0.6093 $\pm$ 0.0054 $\uparrow$ \\ \cline{2-4} 
                         &$QoS$     &0.4940 $\pm$ 0.0013 $\uparrow$    &0.4913 $\pm$ 0.0009            \\ \cline{2-4}
-                        &$SM+QoS$  &0.5574 $\pm$ 0.0156               &0.5604 $\pm$ 0.0164            \\ \hline
+                        &$SM+QoS$  &1.0478 $\pm$ 0.0095               &1.1006 $\pm$ 0.0063 $\uparrow$           \\ \hline
 \multirow{3}{*}{Task4}  &$SM$      &0.4398 $\pm$ 0.0037               &0.4604 $\pm$ 0.0000 $\uparrow$ \\ \cline{2-4} 
                         &$QoS$     &0.4845 $\pm$ 0.0010 $\uparrow$    &0.4734 $\pm$ 0.0044            \\ \cline{2-4}
-                        &$SM+QoS$  &0.5574 $\pm$ 0.0156               &0.5604 $\pm$ 0.0164            \\ \hline
+                        &$SM+QoS$  &0.9243 $\pm$ 0.0047               &0.9338 $\pm$ 0.0044 $\uparrow$           \\ \hline
 \multirow{3}{*}{Task5}  &$SM$      &0.4580 $\pm$ 0.0065               &0.4639 $\pm$ 0.0013 $\uparrow$ \\ \cline{2-4} 
                         &$QoS$     &0.4764 $\pm$ 0.0005 $\uparrow$    &0.4750 $\pm$ 0.0007            \\ \cline{2-4}
-                        &$SM+QoS$  &0.5574 $\pm$ 0.0156               &0.5604 $\pm$ 0.0164            \\ \hline
+                        &$SM+QoS$  &0.9344 $\pm$ 0.0070               &0.9389 $\pm$ 0.0020           \\ \hline
 \end{tabular}
@@
 Fig.
-\ref{comparisontest} $(1)$ and $(2)$ show two $WGs$ obtained by employing the QoS evaluation model and the comprehensive quality evaluation model respectively.
-Both weighted DAGs have exactly the same service workflow structure, but some service vertices and edges denoted in red are different.
+\ref{comparisontest} $(1)$ and $(2)$ show two $WGs$ obtained by employing the QoS model and the comprehensive quality model respectively.
+Both $WGs$ have exactly the same service workflow structure, but some service vertices and edges denoted in red are different.
 To better understand these differences, we list the overall semantic matchmaking quality $SM$,  overall $QoS$ and semantic matchmaking quality associated to each edge in Fig.
-\ref{comparisontest} $(3)$ (Note: $sm_{e_n} = 0.5type_{e_n} + 0.5 sim_{e_n}$), where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) of the listed qualities for our comprehensive quality evaluation model.
-Therefore, an overall gain 0.1433 is calculated from a sum of a $SM$ gain (0.1467) and $QoS$ loss (-0.0034) using comprehensive quality evaluation model.
+\ref{comparisontest} $(3)$ (Note: $sm_{e_n} = 0.5type_{e_n} + 0.5 sim_{e_n}$), where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) of the listed qualities for our comprehensive quality model.
+Therefore, we achieve an overall gain 0.1433, which is calculated from a sum of a $SM$ gain (0.1467) and $QoS$ loss (-0.0034) using comprehensive quality model.
 To understand the improvement of semantic matchmaking quality from these numbers, we pick up $e_4$ that is associated with the smallest $\Delta Q$.
@@
 \ref{comparisontest} $(1)$ and Fig.
-\ref{comparisontest} $(2)$ has two different source service vertices, $Ser1640238160$ and $Ser947554374$, and the same $end$ vertices.
-$Ser1640238160$ and $Ser947554374$ are services with concept-related output parameters $Inst795998200$ and $Inst582785907$ corresponds to two concepts $Con103314376$ and $Con2037585750$ respectively in the ontology shown in Fig.
+\ref{comparisontest} $(2)$ has two different source service vertices, $Ser1640238160$ and $Ser947554374$, and two same $end$ vertices.
+$Ser1640238160$ and $Ser947554374$ are services with output parameters $Inst582785907$ and  $Inst795998200$ corresponds to two related concepts $Con2037585750$ and $Con103314376$ respectively in an ontology shown in Fig.
 \ref{comparisontest} $(4)$.
-In addition, $Inst658772240$ is a required parameter of the $end$ service, and related to concept $Con2113572083$.
+In addition, $Inst658772240$ is a required parameter of the $end$, and related to concept $Con2113572083$.
 Obviously, $Inst795998200$ is closer to user's required output $Inst658772240$ compared to $Inst582785907$.
+Consequently,  $Ser947554374$ is selected with a better semantic matchmaking quality compared to $Ser1640238160$.
 \vspace{-0.6cm}
@@
 \includegraphics[scale=.29]{comparisontest.pdf}}}
- \caption{An example of comparison to optimal solutions using Task 3 for QoS evaluation model and comprehensive quality evluation model.}
+ \caption{An example of comparison to best solutions for QoS model and comprehensive quality evluation model using Task 3.}
  \label{comparisontest}
@@
 
-In this work, we propose a PSO-based approach to comprehensive quality-aware semantic web service composition, which produces service composition solutions with a desirable balance on both semantic matchmaking quality and QoS.
+In this work, we propose an effective PSO-based approach to comprehensive quality-aware semantic web service composition, which has shown promise in achieving a better comprehensive quality in terms of a combination of semantic matchmaking quality and QoS compared to exisitng works.
 Future works can investigate multi-objective EC techniques to produce a set of composition solutions for the situations when the quality preference is not known.

### 2017-04-02 paper.tex
update

@@
 
-\title{Comprehensive Quality Awareness Automated Semantic Web Service Composition}
+\title{Comprehensive Quality-Aware Automated Semantic Web Service Composition}
 \author{Chen Wang$^1$ \quad Hui Ma$^1$ \quad Aaron Chen$^1$ \quad Sven Hartmann$^2$}
@@
 In these works, huge efforts have been devoted to QoS-aware web service compositions assuming a pre-defined abstract workflow is given.
-This is generally considered as a \textit{semi-automated web service composition} approach \cite{parejo2008qos}.
+This is generally considered as a \textit{semi-automated web service composition} approach.
 Generating composition plans automatically in discovering and selecting suitable web services is a NP-hard problem \cite{moghaddam2014service}.
@@
 However, Particle Swarm Optimisation (PSO) is considered to be an easy way to maintain the correctness of solutions in solving combinatorial optimisation problems \cite{da2016particle}.
-All these works have enabled an \textit{automatic semantic web service composition}, but do not optimise QoS and quality of semantic matchmaking simultaneously to achieve a desirable balance on both sides.
+All these works have enabled an \textit{automatic web service composition}, but do not optimise QoS and quality of semantic matchmaking simultaneously to achieve a desirable balance on both sides.
 
-The overall goal of this paper is to \textit{develop a PSO-based approach to automated comprehensive quality-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}.
+The overall goal of this paper is to \textit{develop a PSO-based approach to comprehensive quality-aware automated semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}.
 Particularly, this paper extends existing works of QoS-aware service composition by considering jointly optimising QoS and semantic matchmaking quality, which is proposed as a comprehensive quality model.
@@
  \item To propose a PSO-based service composition approach using the proposed comprehensive quality model.
-To do that, we aim to find a service candidate queue that can be decoded into a service composition with the near-optimal comprehensive quality.
+To do that, we aim to find a service candidate queue that can be decoded into a service composition with near-optimal comprehensive quality.
  \item To address the effectiveness of our PSO-based approach and a desirable balance achieved using our comprehensive quality model, we first compare our PSO-based approach with one recent GP-based approach \cite{ma2015hybrid} using our proposed quality model, and then compare our proposed quality model with one widely used QoS model using our proposed PSO-based approach.
@@
 
-Semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} captures the semantic descriptions of web services' parameters using some kind of logic (e.g., description logic) that ensuring the interoperability of web services.
+Semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} captures the semantic descriptions of web services' parameters using some kind of logic (e.g., description logic) that ensures the interoperability of web services.
 In these approach, the number of web services or length of a graph representation for web service composition is minimised to reach the optimised composition solutions.
@@
 Yu et al.
-\cite{yu2013adaptive} use GP for finding optimal solutions that are reached by penalising infeasible solutions using a fitness function.
-A hybrid approach employing a greedy search and GP is introduced in \cite{ma2015hybrid} to generate functionally correct tree-based individuals, which are transformed from \emph{directed acyclic graph}s (DAGs).
+\cite{yu2013adaptive} use GP for finding near-optimal solutions that are reached by penalising infeasible solutions using a fitness function.
+A hybrid approach employing a greedy search and GP is introduced in \cite{ma2015hybrid} to generate functionally correct tree-based representations, which are transformed from graph-based representations.
 To eliminating the transformation process, a promising GraphEvol is proposed in \cite{da2015graphevol}, where graph-based evolutionary operators are employed.
 An indirect PSO-based approach was introduced in \cite{da2016particle}.
-An service queue is used as an indirect representation that is decoded into a DAG.
+An service queue is used as an indirect representation that is decoded into a \emph{directed acyclic graph} (DAG).
 These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality.
@@
 Lecue et al.
-\cite{lecue2009optimizing} propose a semi-automated web service composition using GA to encode a given abstract service workflow, where the evaluation of semantic matchmaking quality requires a complete and formal definition of ontology using description logic that associated to the resources of web services.
+\cite{lecue2009optimizing} propose a semi-automated web service composition using GA to encode a given abstract service workflow, where the evaluation of semantic matchmaking quality requires a complete and formal definition of ontology using description logic, which is associated to the resources of web services.
 Another GA-based approach \cite{fanjiang2014semantic} utilise process description language to encode pre-stored cases-based workflows, where workable services are composed to complete this workflow.
@@
 %\end{equation}
-
 The \emph{QoS} of the service composition can be obtained by aggregating the QoS values of the participating services.
@@
 %Consequently, in Formula \ref{eqCQ}, the comprehensive quality $CQ$ consists of the aggregated semantic matchmaking quality $SM$ and the QoS calculation in DAG discussed before.
-
+\vspace{-0.1cm}
 \noindent When multiple quality criteria are involved into decision making, then the overall fitness of a solution is proposed as a \emph{comprehensive quality model}, which can be defined as a weighted sum of the individual criteria:
-
+\vspace{-0.2cm}
 \begin{equation}
@@
 This operation is repeated until no service is satisfied by the available outputs.
-During the greedy search, an ontology-based cache ($cache$) is initialised that stores the concept similarities of matched inputs and outputs of task-related candidates.
+During the greedy search, an ontology-based cache ($cache$) is initialised, which stores the concept similarities of matched inputs and outputs of task-related candidates.
 This $cache$ is also used to discover services by checking whether $null$ is returned by given two output-related and input-related concepts.
@@
 \subsection{PSO-based Approach Algorithm}\label{POS-based_algomargin}
-The overall algorithm investigated here is made up of a PSO-based web service composition algorithm \ref{novelSteps} and a decoding Algorithm \ref{graph_building}.
-In Algorithm \ref{novelSteps}, the  steps $4$, $5$, $6$ and $7$ are different from those of standard PSO: In step 4, the size of task-related service candidates generated by a greedy search determines the size of each particle's position, and each candidate in a created service candidates queue is mapped to an index of a particle’s position vectors, where each vector has a weight value between 0.0 and 1.0.
+The overall algorithm investigated here is made up of a PSO-based web service composition Algorithm \ref{novelSteps} and a decoding Algorithm \ref{graph_building}.
+In Algorithm \ref{novelSteps}, the  steps $4$, $5$, $6$ and $7$ are different from those of standard PSO: In step 4, the size of task-related service candidates generated by a greedy search determines the size of each particle's position.
+Each service candidate in a created service candidates queue is mapped to an index of a particle’s position vectors, where each vector has a weight value between 0.0 and 1.0.
 In step 5, service candidates in the queue are sorted according to their corresponding weight values in descending order.
@@
 Firstly, $Start$ and $End$ are added to $V$ of $WG$ as an initialisation, and $OutputSet$ is also created with $I_{T}$.
-If all the inputs $I_{S}$ of the first popped  $S$ from $queue$ can be satisfied by provided outputs from $OutputSet$.
-This $S$ is added to $V$ and its outputs are added to $OutputSet$, and $S$ is removed from $queue$.
-Meanwhile, $e$ is created with $type_e$ and $sim_e$ calculated using infomation provided from $cache$.
-These steps are repeated until $O_{T}$ can be satisfied by $Outputset$ or the service queue is $null$.
-Consequently, this forward graph building technique could lead to more services and edges connected to the $WG$, which should be removed before $WG$ is returned.
+The following steps are repeated until $O_{T}$ can be satisfied by $Outputset$ or the service queue is $null$.
+If all the inputs $I_{S}$ of the first popped  $S$ from $queue$ can be satisfied by provided outputs from $OutputSet$, this $S$ is added to $V$ and its outputs are added to $OutputSet$, and $S$ is removed from $queue$.
+Otherwise, the second popped  $S$ from $queue$ is considered for these operations.
+Meanwhile, $e$ is created with $type_e$ and $sim_e$ if $S$ is added, and calculated using information provided from $cache$.
+This forward graph building technique could lead to more services and edges connected to the $WG$, these redundancies should be removed before $WG$ is returned.
 \vspace{-0.5cm}
@@
       \uIf{all $I_{S}$ satisfied by $OutputSet$}{  
-        $e \leftarrow$ calculate $type_e$, $sim_e$ using $cache$\;
-        $E$ add $e$\;
         $V$ add $S$\;  
@@
         $queue$.remove $S$\;   
+        $e \leftarrow$ calculate $type_e$, $sim_e$ using $cache$\;
+        $E$ add $e$\;
        }	
@@
   }
- remove $dangling nodes$\; 
- remove $dangling edges$\;
+ remove $dangling$ $nodes$\; 
+ remove $dangling$ $edges$\;
  \KwRet $WG$\;
@@
 \section{Experiment Study}\label{experiment_design}
-In this section, we employ a quantitative evaluation approach with a benchmark dataset used in \cite{ma2015hybrid,da2016genetic}, an augmented version of Web Service Challenge 2009 (WSC09) including QoS attributes.
+In this section, we employ a quantitative evaluation approach with a benchmark dataset used in \cite{ma2015hybrid,da2016genetic}, which is an augmented version of Web Service Challenge 2009 (WSC09) including QoS attributes.
 Two objectives of this evaluation are to: $(1)$ evaluate the effectiveness of our PSO-based approach, see comparison test in \ref{comparisonTestWithGP}.
@@
 To evaluate the effectiveness of our proposed PSO-based approach, we compare our PSO-based method with one recent GP-based approach \cite{ma2015hybrid} using our proposed comprehensive quality model.
-We extend the GP-based approach by measuring the semantic matchmaking quality between parent nodes and children nodes.
+We extend this GP-based approach by measuring the semantic matchmaking quality between parent nodes and children nodes.
 To make a fair comparison, we use the same number of evaluations (3000 times) for these two approach.
@@
 Recently, a QoS Model, $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$, where $\sum_{i=1}^{4} w_i = 1$, is widely used for QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol}.
-To show the effectiveness of our proposed comprehensive quality model, we compare the best solutions found using our PSO-based approach evaluated by this QoS model and our comprehensive model.
-We record and compare the mean values of $SM$ ($SM = 0.5 \hat{MT} + 0.5 \hat{SIM}$), $QoS$($QoS = 0.25 \hat{A} + 0.25 \hat{R} + 0.25(1 - \hat{T}) + 0.25(1 - \hat{C})$) at 100 generations over 30 independent runs.
+To show the effectiveness of our proposed comprehensive quality model, we compare the best solutions found by this QoS model and our comprehensive model using our PSO-based approach.
+We record and compare the mean values of both $SM$ ($SM = 0.5 \hat{MT} + 0.5 \hat{SIM}$) and $QoS$($QoS = 0.25 \hat{A} + 0.25 \hat{R} + 0.25(1 - \hat{T}) + 0.25(1 - \hat{C})$) of best solutions over 30 independent runs.
 To make a sense of the comparison, all these recorded values are normalised from 0 to 1, and compared using independent-samples T tests in Table \ref{decisionTable}.
@@
 Fig.
-\ref{comparisontest} $(1)$ and $(2)$ show two $WGs$ obtained by employing the QoS model and the comprehensive quality model respectively.
+\ref{comparisontest} $(1)$ and $(2)$ show two $WGs$ as the best solutions obtained by employing the QoS model and the comprehensive quality model respectively.
 Both $WGs$ have exactly the same service workflow structure, but some service vertices and edges denoted in red are different.
@@
 \ref{comparisontest} $(3)$ (Note: $sm_{e_n} = 0.5type_{e_n} + 0.5 sim_{e_n}$), where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) of the listed qualities for our comprehensive quality model.
-Therefore, we achieve an overall gain 0.1433, which is calculated from a sum of a $SM$ gain (0.1467) and $QoS$ loss (-0.0034) using comprehensive quality model.
+Therefore, we achieve an overall gain 0.1433, which is calculated from a sum of a $SM$ gain (0.1467) and $QoS$ loss (-0.0034).
 To understand the improvement of semantic matchmaking quality from these numbers, we pick up $e_4$ that is associated with the smallest $\Delta Q$.
@@
 \ref{comparisontest} $(4)$.
-In addition, $Inst658772240$ is a required parameter of the $end$, and related to concept $Con2113572083$.
-Obviously, $Inst795998200$ is closer to user's required output $Inst658772240$ compared to $Inst582785907$.
-Consequently,  $Ser947554374$ is selected with a better semantic matchmaking quality compared to $Ser1640238160$.
+As $Inst658772240$ is a required parameter of the $end$, and related to concept $Con2113572083$, $Inst795998200$ is closer to the required output $Inst658772240$ compared to $Inst582785907$.
+Therefore,  $Ser947554374$ is selected with a better semantic matchmaking quality compared to $Ser1640238160$.
 \vspace{-0.6cm}
@@
 
-In this work, we propose an effective PSO-based approach to comprehensive quality-aware semantic web service composition, which has shown promise in achieving a better comprehensive quality in terms of a combination of semantic matchmaking quality and QoS compared to exisitng works.
+In this work, we propose an effective PSO-based approach to comprehensive quality-aware semantic web service composition, which also has shown promise in achieving a better comprehensive quality in terms of a combination of semantic matchmaking quality and QoS compared to exisitng works.
 Future works can investigate multi-objective EC techniques to produce a set of composition solutions for the situations when the quality preference is not known.

### 2017-04-02 paper.tex
update

@@
 Step 3 and Step 4: These two steps follow the standard PSO steps \cite{shi2001particle} except for some differences in particles mapping and decoding processes.
-In particular, these two differences are related to sorting a created service queue using serivce-to-index mapping for a particle' position vectors and evaluating the fitness of a particle after decoding this service queue into a $WG$ respectively.
+In particular, these two differences are related to sorting a created service queue using service-to-index mapping for a particle' position vectors and evaluating the fitness of a particle after decoding this service queue into a $WG$ respectively.
 Those differences are further addressed in Algorithms \ref{novelSteps} and \ref{graph_building} in \ref{POS-based_algomargin}.
@@
 
-In this work, we propose an effective PSO-based approach to comprehensive quality-aware semantic web service composition, which also has shown promise in achieving a better comprehensive quality in terms of a combination of semantic matchmaking quality and QoS compared to exisitng works.
+In this work, we propose an effective PSO-based approach to comprehensive quality-aware semantic web service composition, which also has shown promise in achieving a better comprehensive quality in terms of a combination of semantic matchmaking quality and QoS compared to existing works.
 Future works can investigate multi-objective EC techniques to produce a set of composition solutions for the situations when the quality preference is not known.

### 2017-04-02 paper.tex
update

@@
 \subsection{PSO-based Approach Algorithm}\label{POS-based_algomargin}
-The overall algorithm investigated here is made up of a PSO-based web service composition Algorithm \ref{novelSteps} and a decoding Algorithm \ref{graph_building}.
+The overall algorithm investigated here is made up of a PSO-based web service composition technique (Algorithm \ref{novelSteps}) and creating a WG from service queue (Algorithm \ref{graph_building}).
 In Algorithm \ref{novelSteps}, the  steps $4$, $5$, $6$ and $7$ are different from those of standard PSO: In step 4, the size of task-related service candidates generated by a greedy search determines the size of each particle's position.

### 2017-04-02 paper.tex
update

@@
 
-The \emph{semantic matchmaking quality} of the service composition can be obtained by aggregating over all edges in $E$ as follows:
+The \emph{semantic matchmaking quality} of the service composition can be obtained by aggregating overall edges in $E$ as follows:
 %\begin{equation}
@@
 For a service composition with services $ S_1, S_2, ...
-S_n$ we obtain the reliability $R=\prod\limits^n_{k=1}r_{S_k}$, the availability $A=\prod\limits^n_{k=1}a_{S_k}$, the cost $C=\sum\limits^n_{k=1}c_{S_k}$, and the response time $T$ is the time of most time-consumption path in the composition, i.e., $$T = MAX \{\sum\limits^{\ell_j}_{k=1}t_{S_k} | \text{ $j\in\{1,\ldots,m\}$ and $P_j$ is a path of length $\ell_j$}\}.$$
+S_n$ we obtain the reliability $R=\prod\limits^n_{k=1}r_{S_k}$, the availability $A=\prod\limits^n_{k=1}a_{S_k}$, the cost $C=\sum\limits^n_{k=1}c_{S_k}$, and the response time $T$ is the time of most time-consumption path in the composition, i.e., $$T = MAX \{\sum\limits^{\ell_j}_{k=1}t_{S_k} | \text{ $j\in\{1,\ldots,m\}$ and $\ell_j$ is the length of a path $P_j$}\}.$$
 
@@
 Fig.
-\ref{comparisontest} $(1)$ and $(2)$ show two $WGs$ as the best solutions obtained by employing the QoS model and the comprehensive quality model respectively.
+\ref{comparisontest} $(1)$ and $(2)$ show two $WGs$, $WG_1$ and $WG_2$ as the best solutions obtained by employing the QoS model and the comprehensive quality model respectively.
 Both $WGs$ have exactly the same service workflow structure, but some service vertices and edges denoted in red are different.
-To better understand these differences, we list the overall semantic matchmaking quality $SM$,  overall $QoS$ and semantic matchmaking quality associated to each edge in Fig.
+To better understand these differences, we list the overall semantic matchmaking quality $SM$,  overall $QoS$ and semantic matchmaking quality associated to these different edges in $WG_1$ and $WG_2$.
 \ref{comparisontest} $(3)$ (Note: $sm_{e_n} = 0.5type_{e_n} + 0.5 sim_{e_n}$), where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) of the listed qualities for our comprehensive quality model.
@@
 To understand the improvement of semantic matchmaking quality from these numbers, we pick up $e_4$ that is associated with the smallest $\Delta Q$.
-The $e_4$ of Fig.
-\ref{comparisontest} $(1)$ and Fig.
-\ref{comparisontest} $(2)$ has two different source service vertices, $Ser1640238160$ and $Ser947554374$, and two same $end$ vertices.
-$Ser1640238160$ and $Ser947554374$ are services with output parameters $Inst582785907$ and  $Inst795998200$ corresponds to two related concepts $Con2037585750$ and $Con103314376$ respectively in an ontology shown in Fig.
+The $e_4$ of $WG_1$ and $WG_2$ has two different source service vertices, $Ser1640238160$ and $Ser947554374$, and two the same $end$ vertices.
+$Ser1640238160$ and $Ser947554374$ are services with output parameters $Inst582785907$ and  $Inst795998200$ corresponds to two concepts $Con2037585750$ and $Con103314376$ respectively in the given ontology shown in Fig.
 \ref{comparisontest} $(4)$.

### 2017-04-02 paper.tex
update

@@
 To better understand these differences, we list the overall semantic matchmaking quality $SM$,  overall $QoS$ and semantic matchmaking quality associated to these different edges in $WG_1$ and $WG_2$.
-\ref{comparisontest} $(3)$ (Note: $sm_{e_n} = 0.5type_{e_n} + 0.5 sim_{e_n}$), where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) of the listed qualities for our comprehensive quality model.
+(Note: $sm_{e_n} = 0.5type_{e_n} + 0.5 sim_{e_n}$), where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) of the listed qualities for our comprehensive quality model.
 Therefore, we achieve an overall gain 0.1433, which is calculated from a sum of a $SM$ gain (0.1467) and $QoS$ loss (-0.0034).

### 2017-04-02 paper.tex
updagte

@@
 \subsection{PSO-based Approach Algorithm}\label{POS-based_algomargin}
-The overall algorithm investigated here is made up of a PSO-based web service composition technique (Algorithm \ref{novelSteps}) and creating a WG from service queue (Algorithm \ref{graph_building}).
+The overall algorithm investigated here is made up of a PSO-based web service composition technique (Algorithm \ref{novelSteps}) and a $WG$ creating technique from a service queue (Algorithm \ref{graph_building}).
 In Algorithm \ref{novelSteps}, the  steps $4$, $5$, $6$ and $7$ are different from those of standard PSO: In step 4, the size of task-related service candidates generated by a greedy search determines the size of each particle's position.

### 2017-04-02 paper.tex
update

--- 2017-04-02 paper.tex
@@
 \begin{abstract}
-Semantic web service composition has been a prevailing research area in recent years.
+Web service composition has been a prevailing research direction in recent years.
 There are two major challenges faced by researchers, semantic matchmaking and Quality of Service (QoS) optimisation.
 Semantic matchmaking aims to discover interoperable web services that can interact with each other by their resources described semantically.
-QoS optimisation aims to optimise the non-functional requirements of service users, e.g., minimum cost, maximal reliability.
-To meet users' requirements, one often needs to consider both semantic matchmaking quality and QoS simultaneously.
-Existing works on web service composition focus mainly on one single type of quality requirements.
-Therefore, we propose a comprehensive quality model considering semantic matchmaking quality and QoS simultaneously with an aim of achieving a more desirable balance on both sides.
-Further, we develop a PSO-based service composition approach with explicit support for the comprehensive model.
-We also conduct experiments to address the effectiveness of our PSO-based approach and a desirable balance achieved using our comprehensive quality model.
+QoS optimisation aims to optimise the non-functional requirements of service users, such as minimum cost and maximum reliability.
+To meet the requirements of service users, both semantic matchmaking quality and QoS should be considered simultaneously.
+Most existing works on web service composition, however, focus only on one of these two aspects.
+Therefore, we propose a comprehensive quality model that takes both semantic matchmaking quality and QoS into account with the aim of achieving a more desirable balance of both sides.
+Further, we develop a PSO-based service composition approach with explicit support for the proposed comprehensive quality model.
+We also conduct experiments to explore the effectiveness of our PSO-based approach and the desirable balance achieved by using our comprehensive quality model.
 
@@
 
-\textit{Web service composition} pertains to a chain of multiple web services to provide a value-added composite service that accommodates customers' complex requirements. 
+\textit{Web service composition} aims to loosely couple a set of web services to provide a value-added composite service that accommodates complex functional and non-functional requirements of service users.
 %This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems. 
@@
 The overall goal of this paper is to \textit{develop a PSO-based approach to comprehensive quality-aware automated semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}.
-Particularly, this paper extends existing works of QoS-aware service composition by considering jointly optimising QoS and semantic matchmaking quality, which is proposed as a comprehensive quality model.
+Particularly, this paper extends existing works on QoS-aware service composition by considering jointly optimising QoS and semantic matchmaking quality, which is proposed as a comprehensive quality model.
 We will achieve three objectives in this work:
@@
 \section{Related Work} \label{relatedWork}
-Substantial works on web service composition focus on either semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive}, However, only a few researchers address both semantic matchmaking quality and QoS for web service composition problems.
-To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some attempts on service composition that considers both aspects.
+While web service composition has attracted much research over the last decade, most efforts focus on either semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive}, Only very few works address both semantic matchmaking quality and QoS for web service composition problems.
+To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported about first attempts that consider both aspects together.
 
-Semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} captures the semantic descriptions of web services' parameters using some kind of logic (e.g., description logic) that ensures the interoperability of web services.
-In these approach, the number of web services or length of a graph representation for web service composition is minimised to reach the optimised composition solutions.
-However, this evaluation approach does not guarantee an optimised QoS of composition solutions.
+Semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} captures semantic descriptions of the parameters of web services using some kind of logic (i.e., description logic) to ensure the interoperability of web services.
+In these approaches, the goal is often to minimise the number of services or the size of a graph representation for a web service composition to obtain optimised composition solutions.
+However, these approaches do not guarantee an optimised QoS of service compositions.
 
-QoS-aware web service composition is studied using traditional approaches or EC techniques for finding near-optimised solutions.
-Qi et al.
-\cite{qi2010combining} propose a local optimisation and enumeration method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near optimal QoS.
+QoS-aware web service composition, on the other side, has been studied using classical optimisation techniques or EC techniques for finding near-optimised solutions.
+\cite{qi2010combining} proposes a local optimisation and enumeration method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near optimal QoS.
 EC techniques are widely used to automatically generate solutions with optimal QoS.
-Gupta et al.
-\cite{gupta2015optimization} employ a modified Genetic Algorithm (GA) using a binary string as an individual, which demands to be decoded into composition solutions.
-Yu et al.
-\cite{yu2013adaptive} use GP for finding near-optimal solutions that are reached by penalising infeasible solutions using a fitness function.
+\cite{gupta2015optimization} employs a modified Genetic Algorithm (GA) using a binary string as an individual, which demands to be decoded into composition solutions.
+\cite{yu2013adaptive} uses GP for finding near-optimal solutions that are reached by penalising infeasible solutions using a fitness function.
 A hybrid approach employing a greedy search and GP is introduced in \cite{ma2015hybrid} to generate functionally correct tree-based representations, which are transformed from graph-based representations.
-To eliminating the transformation process, a promising GraphEvol is proposed in \cite{da2015graphevol}, where graph-based evolutionary operators are employed.
-An indirect PSO-based approach was introduced in \cite{da2016particle}.
-An service queue is used as an indirect representation that is decoded into a \emph{directed acyclic graph} (DAG).
-These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality.
+\cite{da2015graphevol} introduces a promising graph-evolutionary approach to eliminate the transformation process.
+\cite{da2016particle} proposes an indirect PSO-based approach, where a service queue is used as an indirect representation that is decoded into a directed acyclic graph.
+However, these QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider the semantic matchmaking quality of service compositions.
 
 Only a few works \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} consider both semantic matchmaking quality and QoS simultaneously.
-Lecue et al.
-\cite{lecue2009optimizing} propose a semi-automated web service composition using GA to encode a given abstract service workflow, where the evaluation of semantic matchmaking quality requires a complete and formal definition of ontology using description logic, which is associated to the resources of web services.
+\cite{lecue2009optimizing} proposes a semi-automated web service composition using GA to encode a given abstract service workflow, where the evaluation of semantic matchmaking quality requires a complete and formal definition of ontology using description logic, which is associated to the resources of web services.
 Another GA-based approach \cite{fanjiang2014semantic} utilise process description language to encode pre-stored cases-based workflows, where workable services are composed to complete this workflow.
@@
 
-\section{Motivation and Problem Description}\label{Motivation and Problem Description}\label{Motivation}\label{problemDes}\label{qualityModel}\label{Comprehensive_Quality_Model}\label{qualityModel}
+\section{Problem Description and Comprehensive Quality Model}\label{Motivation and Problem Description}\label{Motivation}\label{problemDes}\label{qualityModel}\label{Comprehensive_Quality_Model}\label{qualityModel}
 
@@
 We consider a \emph{semantic web service} (\emph{service}, for short) as a tuple $S = (I_{S}, O_{S}, QoS_S)$ where $I_{S}$ is the set of service inputs that are consumed by $S$, $O_{S}$ the set of service outputs that are produced by $S$, and $QoS_{S}=\{t_S, c_S, r_S, a_S\}$ the set of non-functional attributes of $S$.
-The inputs in $I_{S}$ and the outputs in $O_{S}$ are concept-related parameters with the concepts in an ontology $\mathcal{O}$.
+The inputs in $I_{S}$ and outputs in $O_{S}$ are parameters that are related to concepts in an ontology $\mathcal{O}$.
 The attributes $t_S, c_S, r_S, a_S$ refer to the response time, cost, reliability, and availability of service $S$, respectively.
@@
 A \emph{service request} (also called \emph{composition task}) over $\mathcal{SR}$ is a tuple $T=(I_{T}, O_{T})$ where $I_{T}$ is the set of task inputs, and $O_{T}$ the set of task outputs.
-The inputs in $I_{T}$ and the outputs in $O_{T}$ are concept-related parameters with the concepts in the ontology $\mathcal{O}$.
+The inputs in $I_{T}$ and outputs in $O_{T}$ are parameters that are related to concepts in the ontology $\mathcal{O}$.
 
-A service composition is commonly represented as a DAG.
+A service composition is commonly represented as a \emph{directed acyclic graph} (DAG).
 It nodes correspond to the services in the composition.
@@
 As argued in \cite{lecue2009optimizing} $plugin$ matches are less preferable than $exact$ matches due to the overheads associated with data processing.
-We suggest to consider the semantic similarity of concepts when comparing different plugin types.
-For concepts $a, b$ in $\mathcal{O}$ the \emph{semantic similarity} $sim(a, b)$ is calculated based on the edge counting method defined in the formula (\ref{equation1}) from \cite{shet2012new}, where $N_a$, $N_b$ and $N_c$ measure the distances from concept $a$, concept $b$, and a closest common ancestor $c$ of $a$ and $b$ to the top concept of the ontology $\mathcal{O}$, respectively.
+We suggest to consider the semantic similarity of concepts when comparing different $plugin$ matches.
+For concepts $a, b$ in $\mathcal{O}$ the \emph{semantic similarity} $sim(a, b)$ is calculated based on the edge counting method defined in Eq.
+(\ref{equation1}) from \cite{shet2012new}, where $N_a$, $N_b$ and $N_c$ measure the distances from concept $a$, concept $b$, and a closest common ancestor $c$ of $a$ and $b$ to the top concept of the ontology $\mathcal{O}$, respectively.
 \vspace{-0.2cm}
@@
 
-\noindent with a suitable parameter $p, 0<p< 1$ to chosen, for discussion see \ref{PSO_based_approach}.
+\noindent with a suitable parameter $p, 0<p< 1$ to chosen, for discussion see Section \ref{PSO_based_approach}.
 However, if more than one pair of matched output and input exist from services $S$ and $S'$ respectively, $type_e$ and $sim_e$ will take on their average values.
@@
 
-%\textbf{Definition 6.} Given $full match(a \Rightarrow b)$, $sm(a,b)$ is a function for measuring semantic matchmaking quality between two concepts, which returns a pair of values consisting of $type(a, b)$ and $q_{sim}(a, b)$ defined in Formula (\ref{equation2}).
+%\textbf{Definition 6.} Given $full match(a \Rightarrow b)$, $sm(a,b)$ is a function for measuring semantic matchmaking quality between two concepts, which returns a pair of values consisting of $type(a, b)$ and $q_{sim}(a, b)$ defined in Eq.
+(\ref{equation2}).
 
@@
 %Since each $e$ defined in $E$ could have more than one $fullmatch(a \Rightarrow b)$ form a edge.
-Therefore, semantic matchmaking quality of one edge, denoted as $sm_e$ is defined in formula (\ref{equation3}), where $type_{e}$ and $sim_{e}$ are the average values of all involved $type(a, b)$ and $q_{sim}(a, b)$ respectively.
+Therefore, semantic matchmaking quality of one edge, denoted as $sm_e$ is defined in Eq.
+(\ref{equation3}), where $type_{e}$ and $sim_{e}$ are the average values of all involved $type(a, b)$ and $q_{sim}(a, b)$ respectively.
 
@@
 
-%Consequently, in Formula \ref{eqCQ}, the comprehensive quality $CQ$ consists of the aggregated semantic matchmaking quality $SM$ and the QoS calculation in DAG discussed before.
+%Consequently, in Eq. \ref{eqCQ}, the comprehensive quality $CQ$ consists of the aggregated semantic matchmaking quality $SM$ and the QoS calculation in DAG discussed before.
 \vspace{-0.1cm}
-\noindent When multiple quality criteria are involved into decision making, then the overall fitness of a solution is proposed as a \emph{comprehensive quality model}, which can be defined as a weighted sum of the individual criteria:
+\noindent When multiple quality criteria are involved into decision making, then the overall fitness of a solution can be defined as a weighted sum of the individual criteria: 
 \vspace{-0.2cm}
@@
 \end{equation}
-\noindent with $\sum_{k=1}^{6} w_k= 1$.
+\noindent with $\sum_{k=1}^{6} w_k= 1$. We call this objective function the \emph{comprehensive quality model} for service composition.
 The weights can be adjusted according to users' preferences.
 Herein, the individual criteria are normalised to a range between 0 to 1, where 1 means the best value and 0 means the worst.
-For this purpose, we normalise $MT$, $SIM$, $A$, $R$, $T$, and $C$ so that the function value falls within the range from 0 to 1 using formula (\ref{equation9}).
+For this purpose, we normalise $MT$, $SIM$, $A$, $R$, $T$, and $C$ so that the function value falls within the range from 0 to 1 using Eq.
+(\ref{equation9}).
 To simplify the presentation we also use the notation $(Q_1,Q_2,Q_3,Q_4,Q_5,Q_6) = (MT,SIM,A,R,T,C)$.
-$MT$ and $S$ have minimum value 0 and maximum value 1.
-The minimum and maximum value of $A$, $R$, $T$, and $C$ are calculated across all task-related candidates in the service repository $\mathcal{SR}$ using greedy search, for discussion see \ref{PSO_based_approach}.
+$MT$ and $SIM$ have minimum value 0 and maximum value 1.
+The minimum and maximum value of $A$, $R$, $T$, and $C$ are calculated across all task-related candidates in the service repository $\mathcal{SR}$ using greedy search, for details see Section \ref{PSO_based_approach}.
 
@@
 
-\noindent The composition task is to find the maximum value of objective function in (\ref{equation8}).
+\noindent To solve the composition task best possible the goal is to find the maximum value of the objective function in Eq. (\ref{equation8}).
 
@@
 \fbox{\includegraphics[scale=.4]{overview.pdf}}
- \caption{An overview of POS-based approach to comprehensive quality-aware automated semantic web service composition.}
+ \caption{An overview of our PSO-based approach to comprehensive quality-aware automated semantic web service composition.}
  \label{overview}
@@
 \vspace{-1.0cm}
-\subsection{An Overview to PSO-based Method}\label{PSO_based_approach}
+\subsection{An Overview of our PSO-based Approach}\label{PSO_based_approach}
 
@@
 
-Step 1: The composition process is triggered by a composition task, which is clearly defined in \ref{problemDes}.
+Step 1: The composition process is triggered by a composition task, which is clearly defined in Section \ref{problemDes}.
 
-Step 2: This composition task is used to discover all task-related service candidates using a greedy search algorithm adopted from \cite{ma2015hybrid}, which contributes to a shrunken service repository.
+Step 2: The composition task is used to discover all task-related service candidates using a greedy search algorithm adopted from \cite{ma2015hybrid}, which contributes to a shrunken service repository.
 This greedy search algorithm keeps adding outputs of the invoked services as available outputs (initialised with $I_{T}$) , and these available outputs are used to discover task-related services from a service repository and updated with the outputs of these discovered services.
@@
 In particular, these two differences are related to sorting a created service queue using service-to-index mapping for a particle' position vectors and evaluating the fitness of a particle after decoding this service queue into a $WG$ respectively.
-Those differences are further addressed in Algorithms \ref{novelSteps} and \ref{graph_building} in \ref{POS-based_algomargin}.
+Those differences are further addressed in Algorithms \ref{novelSteps} and \ref{graph_building} in Section \ref{POS-based_algomargin}.
 
-\subsection{PSO-based Approach Algorithm}\label{POS-based_algomargin}
-The overall algorithm investigated here is made up of a PSO-based web service composition technique (Algorithm \ref{novelSteps}) and creating a WG from service queue (Algorithm \ref{graph_building}).
+\subsection{The Algorithms for our PSO-based Approach}\label{POS-based_algomargin}
+The overall algorithm investigated here is made up of a PSO-based web service composition technique (Algorithm \ref{novelSteps}) and a $WG$ creating technique from a service queue (Algorithm \ref{graph_building}).
 In Algorithm \ref{novelSteps}, the  steps $4$, $5$, $6$ and $7$ are different from those of standard PSO: In step 4, the size of task-related service candidates generated by a greedy search determines the size of each particle's position.
@@
 In step 6, this sorted queue is used as one of the inputs of the forward decoding Algorithm \ref{graph_building} to create a $WG$.
-In step 7, the fitness value of the created $WG$ is the fitness value of the particle calculated by the comprehensive model discussed in \ref{Comprehensive_Quality_Model}.
+In step 7, the fitness value of the created $WG$ is the fitness value of the particle calculated by the comprehensive model discussed in Section \ref{Comprehensive_Quality_Model}.
 \vspace{-0.5cm}
@@
   \While {max. iterations not met}{
-     \ForEach{particles in the swarm}{
+     \ForEach{particle in the swarm}{
      Create a service candidates queue and map service candidates to a particle's position vectors\;
      Sort the service queue by position vectors' weights\;
-     Create a $WG$ from the service queue (Algorithm\ref{graph_building}) \;
+     Use Algorithm \ref{graph_building} to create a $WG$ from the service queue \;
      Calculate the $WG$ fitness value\;
@@
 Algorithm  \ref{graph_building} is a forward graph building algorithm extended from \cite{blum1997fast}.
-This algorithm take one input, a sorted service queue from step 5 of Algorithm \ref{novelSteps}.
+This algorithm takes one input, a sorted service queue from step 5 of Algorithm \ref{novelSteps}.
 Note that different service queues may lead to different $WGs$.
@@
  $OutputSet \leftarrow$ \{$I_{T}$\}\;
-  \While { $O_{T}$ do not satisfied by $OutputSet$}{
+  \While { $O_{T}$ not satisfied by $OutputSet$}{
      \ForEach{$S$ in $queue$}{
-      \uIf{all $I_{S}$ satisfied by $OutputSet$}{  
-        $V$ add $S$\;  
-        $OutputSet$ add \{$O_{S}$\}\;
+      \uIf{$I_{S}$ satisfied by $OutputSet$}{  
+        insert $S$ into $V$ \;  
+        adjoin $O_{S}$ to $OutputSet$\;
         $queue$.remove $S$\;   
         $e \leftarrow$ calculate $type_e$, $sim_e$ using $cache$\;
-        $E$ add $e$\;
+        insert $e$ into $E$\;
        }	
@@
   }
- remove $dangling$ $nodes$\; 
- remove $dangling$ $edges$\;
+ remove $dangling$ $nodes$ and $edges$ from $WG$\; 
  \KwRet $WG$\;
@@
 In this section, we employ a quantitative evaluation approach with a benchmark dataset used in \cite{ma2015hybrid,da2016genetic}, which is an augmented version of Web Service Challenge 2009 (WSC09) including QoS attributes.
-Two objectives of this evaluation are to: $(1)$ evaluate the effectiveness of our PSO-based approach, see comparison test in \ref{comparisonTestWithGP}.
+Two objectives of this evaluation are to: $(1)$ evaluate the effectiveness of our PSO-based approach, see comparison test in Section \ref{comparisonTestWithGP}.
 %To do this, we compare our PSO-based method with one existing GP-based approach \cite{ma2015hybrid}. 
-$(2)$ evaluate the effectiveness of our proposed comprehensive quality model to achieve a desirable balance on semantic matchmaking quality and QoS, see comparison test in \ref{comparisonTest}.
+$(2)$ evaluate the effectiveness of our proposed comprehensive quality model to achieve a desirable balance on semantic matchmaking quality and QoS, see comparison test in Section \ref{comparisonTest}.
 %To do this, we compare a widely used QoS model in QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol} with our comprehensive quality model using our PSO-based approach.
@@
 \vspace{-0.5cm}
-\subsection{Comparison Test for GP-based approach and PSO-based approach}\label{comparisonTestWithGP}
+\subsection{Comparison Test for GP-based vs. PSO-based approach}\label{comparisonTestWithGP}
 To evaluate the effectiveness of our proposed PSO-based approach, we compare our PSO-based method with one recent GP-based approach \cite{ma2015hybrid} using our proposed comprehensive quality model.
@@
 We employ independent-samples T tests to test the significant differences in mean fitness value.
-The results show that the PSO-based approach outperforms the existing GP-based approach in most cases except task 3.
-Note that all the p-values are consistently smaller than 0.01.
-In task 5, the PSO-based approach performs significantly better than the GP-based approach in finding optimal solutions.
+The results show that the PSO-based approach outperforms the existing GP-based approach in most cases except Task 3.
+Note that all $p$-values are consistently smaller than 0.01.
+In Task 5, the PSO-based approach performs significantly better than the GP-based approach in finding optimal solutions.
 It may be that the GP-based approach is stuck in local optima in a very large search space due to its evolutionary operators.
@@
 
-\subsection{Comparison Test for Comprehensive Quality Model and QoS Model}\label{comparisonTest}
+\subsection{Comparison Test for Comprehensive Quality Model vs. QoS Model}\label{comparisonTest}
 
@@
 We record and compare the mean values of both $SM$ ($SM = 0.5 \hat{MT} + 0.5 \hat{SIM}$) and $QoS$($QoS = 0.25 \hat{A} + 0.25 \hat{R} + 0.25(1 - \hat{T}) + 0.25(1 - \hat{C})$) of best solutions over 30 independent runs.
-To make a sense of the comparison, all these recorded values are normalised from 0 to 1, and compared using independent-samples T tests in Table \ref{decisionTable}.
+To make the comparison informative, all these recorded values have been normalised from 0 to 1, and compared using independent-samples t tests, see Table \ref{decisionTable}.
 
@@
 However, the mean value of $SM$ using the comprehensive quality model are significantly higher than those using the QoS model, while a slight trade-off in $QoS$ are observed in all tasks.
-In addition, our comprehensive model achieves a consistently higher comprehensive quality in terms of a combination of $SM$ and $QoS$, which is significantly better in task 1, 2, 3 and 4.
+In addition, our comprehensive model achieves a consistently higher comprehensive quality in terms of a combination of $SM$ and $QoS$, which is significantly better in Tasks 1, 2, 3 and 4.
 \vspace{-0.8cm}
@@
 \subsection{Further Discussion}\label{discuss1}
-To analyse the effectiveness of achieving a good comprehensive quality at the expense of slightly reduced QoS, we demonstrate two best solutions produced using task 3 as an example.
+To analyse the effectiveness of achieving a good comprehensive quality at the expense of slightly reduced QoS, we demonstrate two best solutions produced using Task 3 as an example.
 Fig.
-\ref{comparisontest} $(1)$ and $(2)$ show two $WGs$, $WG_1$ and $WG_2$ as the best solutions obtained by employing the QoS model and the comprehensive quality model respectively.
+\ref{comparisontest} $(1)$ and $(2)$ show two weighted DAGs $WG_1$ and $WG_2$ that have been obtained as the best service compositions solutions based on the QoS model and on the comprehensive quality model, respectively.
 Both $WGs$ have exactly the same service workflow structure, but some service vertices and edges denoted in red are different.
@@
 (Note: $sm_{e_n} = 0.5type_{e_n} + 0.5 sim_{e_n}$), where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) of the listed qualities for our comprehensive quality model.
-Therefore, we achieve an overall gain 0.1433, which is calculated from a sum of a $SM$ gain (0.1467) and $QoS$ loss (-0.0034).
+Therefore, we achieve a comprehensive quality gain of 0.1433, which is the result of a gain in semantic matchmaking quality (+0.1467) and a loss in $QoS$ (-0.0034).
 To understand the improvement of semantic matchmaking quality from these numbers, we pick up $e_4$ that is associated with the smallest $\Delta Q$.
-The $e_4$ of $WG_1$ and $WG_2$ has two different source service vertices, $Ser1640238160$ and $Ser947554374$, and two the same $end$ vertices.
+The $e_4$ of $WG_1$ and $WG_2$ has two different source nodes, $Ser1640238160$ and $Ser947554374$, and two the same end nodes.
 $Ser1640238160$ and $Ser947554374$ are services with output parameters $Inst582785907$ and  $Inst795998200$ corresponds to two concepts $Con2037585750$ and $Con103314376$ respectively in the given ontology shown in Fig.
 \ref{comparisontest} $(4)$.
-As $Inst658772240$ is a required parameter of the $end$, and related to concept $Con2113572083$, $Inst795998200$ is closer to the required output $Inst658772240$ compared to $Inst582785907$.
+As $Inst658772240$ is a required parameter of $End$, and related to concept $Con2113572083$, $Inst795998200$ is closer to the required output $Inst658772240$ than $Inst582785907$.
 Therefore,  $Ser947554374$ is selected with a better semantic matchmaking quality compared to $Ser1640238160$.
@@
 \includegraphics[scale=.29]{comparisontest.pdf}}}
- \caption{An example of comparison to best solutions for QoS model and comprehensive quality evluation model using Task 3.}
+ \caption{An example for the comparison of the best solutions obtained based on the QoS model and on the comprehensive quality model for Task 3.}
  \label{comparisontest}

### 2017-04-04 paper.tex
update

@@
 Note that all $p$-values are consistently smaller than 0.01.
-In Task 5, the PSO-based approach performs significantly better than the GP-based approach in finding optimal solutions.
+Using our PSO-based approach, small changes to sorted queues (particles in PSO) could lead to big changes to the composition solutions.
+This enables the PSO-based approach to escape from local optima more easily than the GP-based approach.
+%the PSO-based approach performs significantly better than the GP-based approach in finding optimal solutions.
 It may be that the GP-based approach is stuck in local optima in a very large search space due to its evolutionary operators.

### 2017-05-10 paper.tex
update

@@
 
-\section{Problem Description and Comprehensive Quality Model}\label{Motivation and Problem Description}\label{Motivation}\label{problemDes}\label{qualityModel}\label{Comprehensive_Quality_Model}\label{qualityModel}
+\section{Problem Description and Comprehensive Quality Model}\label{Motivation and Problem Description}
 
@@
 
-We consider a \emph{semantic web service} (\emph{service}, for short) as a tuple $S = (I_{S}, O_{S}, QoS_S)$ where $I_{S}$ is the set of service inputs that are consumed by $S$, $O_{S}$ the set of service outputs that are produced by $S$, and $QoS_{S}=\{t_S, c_S, r_S, a_S\}$ the set of non-functional attributes of $S$.
-The inputs in $I_{S}$ and outputs in $O_{S}$ are parameters that are related to concepts in an ontology $\mathcal{O}$.
+We consider a \emph{semantic web service} (\emph{service}, for short) as a tuple $S = (I_{S}, O_{S}, QoS_S)$ where $I_{S}$ is a set of service inputs that are consumed by $S$, $O_{S}$ is a set of service outputs that are produced by $S$, and $QoS_{S}=\{t_S, c_S, r_S, a_S\}$ is a set of non-functional attributes of $S$.
+The inputs in $I_{S}$ and outputs in $O_{S}$ are parameters modeled through concepts in a domain-specific ontology $\mathcal{O}$.
 The attributes $t_S, c_S, r_S, a_S$ refer to the response time, cost, reliability, and availability of service $S$, respectively.
 These four QoS attributes are most commonly used \cite{zeng2003quality}.
-% \textit{Response time} ($t_S$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.
-\textit{Cost} ($c_S$) is the amount of money that a service requester has to pay for executing the service.
-\textit{Reliability} ($r_S$) is the probability that a request is correctly responded within the maximum expected time frame, which is expressed as a number between 1 and 0.
-Similarly, \textit{availability} ($a_S$) is the probability that a service is accessible.
 
 A \emph{service repository} $\mathcal{SR}$ is a finite collection of services with a common ontology $\mathcal{O}$.
-A \emph{service request} (also called \emph{composition task}) over $\mathcal{SR}$ is a tuple $T=(I_{T}, O_{T})$ where $I_{T}$ is the set of task inputs, and $O_{T}$ the set of task outputs.
+A \emph{service request} (also called \emph{composition task}) over $\mathcal{SR}$ is a tuple $T=(I_{T}, O_{T})$ where $I_{T}$ is a set of task inputs, and $O_{T}$ is a set of task outputs.
 The inputs in $I_{T}$ and outputs in $O_{T}$ are parameters that are related to concepts in the ontology $\mathcal{O}$.
@@
 A service composition is commonly represented as a \emph{directed acyclic graph} (DAG).
-It nodes correspond to the services in the composition.
-Two services $S$ and $S'$ are connected by an edge $e$ if some output of $S$ serves as input for $S'$.
+Its nodes correspond to the services in the composition.
+Two services $S$ and $S'$ are connected by an edge $e$ if some outputs of $S$ service serve as inputs for $S'$.
 Apparently, such outputs and inputs must semantically match to ensure the correct execution of the service composition.
-%Moreover, the overall service inputs and outputs associated with the DAG must satisfy the composition requirements provided by users.
-%To answer a request from a user a suitable service composition is sought. 
 The mechanism to compose services relies on the semantic descriptions of inputs and outputs, which enables inputs of services to be matched by outputs of other services.
 The following \emph{matchmaking types} are often used to describe the level of a match \cite{paolucci2002semantic}: For concepts $a, b$ in $\mathcal{O}$ the \emph{matchmaking} returns $exact$ if $a$ and $b$ are equivalent ($a \equiv b$), $plugin$ if $a$ is a sub-concept of $b$ ($a \sqsubseteq b$), $subsume$ if $a$ is a super-concept of $b$ ($a \sqsupseteq b$), and $fail$ if none of previous matchmaking types is returned.
-%($a \perp b$)
+
 In this paper we are only interested in robust compositions where only $exact$ and $plugin$ matches are considered, see \cite{lecue2009optimizing}.
-%
 As argued in \cite{lecue2009optimizing} $plugin$ matches are less preferable than $exact$ matches due to the overheads associated with data processing.
@@
 For concepts $a, b$ in $\mathcal{O}$ the \emph{semantic similarity} $sim(a, b)$ is calculated based on the edge counting method defined in Eq.
-(\ref{equation1}) from \cite{shet2012new}, where $N_a$, $N_b$ and $N_c$ measure the distances from concept $a$, concept $b$, and a closest common ancestor $c$ of $a$ and $b$ to the top concept of the ontology $\mathcal{O}$, respectively.
+(\ref{equation1}) from \cite{shet2012new}, where $N_a$, $N_b$ and $N_c$ measure the distances from concept $a$, concept $b$, and the closest common ancestor $c$ of $a$ and $b$ to the top concept of the ontology $\mathcal{O}$, respectively.
 \vspace{-0.2cm}
@@
 \end{equation}
-\noindent For our purposes, $\lambda$ can be set to 0 as we do not measure the similarities of neighbourhood concepts, which is not the matching type considered in this paper. 
-%Thus, we obtain a combined function for measuring semantic matchmaking quality between two concepts:
-
-%\begin{equation}\label{equation2}sm(a, b) \stackrel{.}{=} ( type(a, b), \  sim(a, b) )\end{equation}
+\noindent For our purposes, $\lambda$ can be set to 0 as we do not measure the similarities of neighbourhood concepts, the matching type not considered in this paper.
 
@@
 $Start$ and $End$ are two special services defined as $Start = (\emptyset, I_T, \emptyset )$ and $End  = (O_T, \emptyset, \emptyset)$ that account for the input and output requirements given by the request.
-%Each edge $e$ between two services $S$ and $S'$ is associated with a set of incoming outputs produced by $S$ and a set of outgoing inputs consumed by $S'$.
 Each edge $e$ from a service $S$ to a service $S'$ means that service $S$ produces an output $a\in O_S$ that is matched ($exact$ or $plugin$) to an input $b\in I_{S'}$ to be consumed by service $S'$ in the composition.
-Based on the matchmaking type the \emph{semantic matchmaking quality} of edge $e$ can be defined as follows:
+Based on the matchmaking type, the \emph{semantic matchmaking quality} of edge $e$ can be defined as follows:
 \vspace{-0.2cm}
@@
 
-\noindent with a suitable parameter $p, 0<p< 1$ to chosen, for discussion see Section \ref{PSO_based_approach}.
-However, if more than one pair of matched output and input exist from services $S$ and $S'$ respectively, $type_e$ and $sim_e$ will take on their average values.
+\noindent with a suitable parameter $p, 0<p< 1$, see Section \ref{experiment_study}.
+However, if more than one pair of matched output and input exist from service $S$ to service $S'$, $type_e$ and $sim_e$ will take on their average values.
 
-%$e = \{ (O_{S_{src}} \cup I_{S_{src}}) \mid \forall o \in O_{S_{src}}, \exists i \in O_{S_{src}} \wedge fullmatch (o \Rightarrow i) \}$
-
-%\textbf{Definition 4.} Given $(a \in O^{C}_{S_m}) \vee (b \in I^{C}_{S_n}) \wedge (m \neq n) $, a $full match(a \Rightarrow b)$ holds if $type(a, b)$ returns $exact$ or $plugin$.
-The operator ``$ \Rightarrow$'' means $a$ is passed to $b$, and $b$ is fully satisfied by $a$.
-The full match is a guarantee of completely valid  ``$ \Rightarrow$'' operation, whereas, partial matches are not considered in this paper.
-
-%\textbf{Semantic matchmaking quality model}.
-Due to that the discretisational characteristics of different match types and values assigned to matching types driven by the cost of data manipulation \cite{lecue2009optimizing}, match types are considered to be one factor for the quality of matchmaking.
-For example, Exact matching type demands less time for computation compared to that of Plugin match.
-Another factor is concept similarity of two matched concepts.
-For example, two plugin types, $publication \sqsubseteq printedmaterial$ and $romanticnovel \sqsubseteq printedmaterial$, are associated with different similarities.
-
-%\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $sim(a, b)$ is a function that given a output-related concept $a$ of a service and a input-related concept $b$ of another service, it returns a concept similarity value between $a$ and $b$.
-
-%\textbf{Definition 6.} Given $full match(a \Rightarrow b)$, $sm(a,b)$ is a function for measuring semantic matchmaking quality between two concepts, which returns a pair of values consisting of $type(a, b)$ and $q_{sim}(a, b)$ defined in Eq.
-(\ref{equation2}).
-
-%\textbf{Weighted DAG composition model}.
-web service composition is considered to be a data workflow, where services are chained together by their inputs and outputs using the two models defined before.
-All these concepts are captured and tackled in a weighted DAG as $WG = (V, E)$ , where:
-
-%\textbf{Comprehensive quality model in a weighted DAG}.
-
-%Since each $e$ defined in $E$ could have more than one $fullmatch(a \Rightarrow b)$ form a edge.
-Therefore, semantic matchmaking quality of one edge, denoted as $sm_e$ is defined in Eq.
-(\ref{equation3}), where $type_{e}$ and $sim_{e}$ are the average values of all involved $type(a, b)$ and $q_{sim}(a, b)$ respectively.
-
-%\begin{equation}\label{equation3}sm_{e} \stackrel{.}{=} (type_ {e}, \  sim_ {e})\end{equation}
-
-The \emph{semantic matchmaking quality} of the service composition can be obtained by aggregating overall edges in $E$ as follows:
+The \emph{semantic matchmaking quality} of the service composition can be obtained by aggregating over all edges in $E$ as follows:
 %\begin{equation}
@@
 %\end{equation}
-The \emph{QoS} of the service composition can be obtained by aggregating the QoS values of the participating services.
+The \emph{QoS} of the service composition can be obtained by aggregating the QoS values of the participating services \cite{ma2015hybrid}.
 For a service composition with services $ S_1, S_2, ...
-S_n$ we obtain the reliability $R=\prod\limits^n_{k=1}r_{S_k}$, the availability $A=\prod\limits^n_{k=1}a_{S_k}$, the cost $C=\sum\limits^n_{k=1}c_{S_k}$, and the response time $T$ is the time of most time-consumption path in the composition, i.e., $$T = MAX \{\sum\limits^{\ell_j}_{k=1}t_{S_k} | \text{ $j\in\{1,\ldots,m\}$ and $\ell_j$ is the length of a path $P_j$}\}.$$
+S_n$ we obtain the reliability $R=\prod\limits^n_{k=1}r_{S_k}$, the availability $A=\prod\limits^n_{k=1}a_{S_k}$, the cost $C=\sum\limits^n_{k=1}c_{S_k}$, and the response time $T$ is the time of most time-consuming path in the composition, i.e., $$T = MAX \{\sum\limits^{\ell_j}_{k=1}t_{S_k} | \text{ $j\in\{1,\ldots,m\}$ and $\ell_j$ is the length of a path $P_j$}\}.$$
 
@@
 The weights can be adjusted according to users' preferences.
-Herein, the individual criteria are normalised to a range between 0 to 1, where 1 means the best value and 0 means the worst.
-For this purpose, we normalise $MT$, $SIM$, $A$, $R$, $T$, and $C$ so that the function value falls within the range from 0 to 1 using Eq.
+We normalise $MT$, $SIM$, $A$, $R$, $T$, and $C$ so that the function value falls within the range from 0 to 1 using Eq.
 (\ref{equation9}).
@@
 $MT$ and $SIM$ have minimum value 0 and maximum value 1.
-The minimum and maximum value of $A$, $R$, $T$, and $C$ are calculated across all task-related candidates in the service repository $\mathcal{SR}$ using greedy search, for details see Section \ref{PSO_based_approach}.
+The minimum and maximum value of $A$, $R$, $T$, and $C$ are calculated across all task-related candidates in the service repository $\mathcal{SR}$ using the greedy search in \cite{ma2015hybrid,da2016genetic}.
 
@@
 
-\noindent To solve the composition task best possible the goal is to find the maximum value of the objective function in Eq. (\ref{equation8}).
-
-%If the weights for $MT$ and $S$ are put to 0 we obtain the QoS-aware service composition approach \cite{ma2015hybrid,da2016particle,da2015graphevol} as a special case.
-To adequatley reflect the relevance of semantic quality it is recommended to choose he weights for $MT$ and $S$ strictly larger than 0.
+\noindent To solve the composition task satisfactorily our goal is to maximize the objective function in Eq. (\ref{equation8}).
 

### 2017-05-11 paper.tex
update

@@
 
-%where PSO optimise a queue of task-related services that is decoded into composition solutions.
-We compare the effectiveness of PSO-based method with one recent GP-based method using the proposed comprehensive quality model, and also compare the effectiveness of our proposed comprehensive quality model with one promising QoS model.
-
 \end{abstract}
@@
 The semantic dimension enables a better collaboration through ontology-based semantics, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}.
-\textit{Semantic web services composition} is distinguished from the syntactic service composition, the resources of semantic web services are described semantically to enable a better interoperability for chaining web services.
+\textit{Semantic web services composition} is distinguished from the syntactic service composition, as the resources of semantic web services are described semantically to enable a better interoperability for chaining web services.
 Another challenge is related to QoS optimisation.
@@
 Genetic Programming (GP) based approaches produce promising results, but these approaches often require repairing or penalising the solutions \cite{ma2015hybrid,yu2013adaptive}.
-However, Particle Swarm Optimisation (PSO) is considered to be an easy way to maintain the correctness of solutions in solving combinatorial optimisation problems \cite{da2016particle}.
+However, Particle Swarm Optimisation (PSO) is considered to be more efficient, as it simply updates particles' positions to move candidate particles across the searching space, rather than employing genetic operators to carry out searching process.
 All these works have enabled an \textit{automatic web service composition}, but do not optimise QoS and quality of semantic matchmaking simultaneously to achieve a desirable balance on both sides.
@@
 The overall goal of this paper is to \textit{develop a PSO-based approach to comprehensive quality-aware automated semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}.
-Particularly, this paper extends existing works on QoS-aware service composition by considering jointly optimising QoS and semantic matchmaking quality, which is proposed as a comprehensive quality model.
+Particularly, this paper extends existing works on QoS-aware service composition by considering jointly optimising the both quality aspects, which is proposed as a comprehensive quality model.
 We will achieve three objectives in this work:
@@
 \section{Related Work} \label{relatedWork}
-While web service composition has attracted much research over the last decade, most efforts focus on either semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive}, Only very few works address both semantic matchmaking quality and QoS for web service composition problems.
+While web service composition has attracted much research over the last decade, most efforts focus on either semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive}.
+Only very few works address both semantic matchmaking quality and QoS for web service composition problems.
 To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported about first attempts that consider both aspects together.
@@
 In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches, there is a lack of a fully automated semantic service composition approach to optimise semantic matchmaking quality and QoS simultaneously.
-%Therefore, we first propose an automated comprehensive quality-aware semantic web service composition approach.
-To do that, we will design a comprehensive quality model that considers both QoS and quality of semantic matchmaking between services.
-We will then propose a PSO-based approach to this semantic service composition using our proposed comprehensive quality model to evaluate candidate solutions.
 \vspace{-0.3cm}
 
-\section{Problem Description and Comprehensive Quality Model}\label{Motivation and Problem Description}
+\section{Problem Description and Comprehensive Quality Model}\label{problemDes}
 
@@
 Each edge $e$ from a service $S$ to a service $S'$ means that service $S$ produces an output $a\in O_S$ that is matched ($exact$ or $plugin$) to an input $b\in I_{S'}$ to be consumed by service $S'$ in the composition.
-Based on the matchmaking type, the \emph{semantic matchmaking quality} of edge $e$ can be defined as follows:
+Based on the matchmaking type ($type_e$), the \emph{semantic similarity} ($sim_e$) of edge $e$ can be defined as follows:
 \vspace{-0.2cm}
@@
 
-\noindent with a suitable parameter $p, 0<p< 1$, see Section \ref{experiment_study}.
+\noindent with a suitable parameter $p, 0<p< 1$.
+$p$ is determined by user's preference, see Section \ref{experiment_design}.
 However, if more than one pair of matched output and input exist from service $S$ to service $S'$, $type_e$ and $sim_e$ will take on their average values.
 
-The \emph{semantic matchmaking quality} of the service composition can be obtained by aggregating over all edges in $E$ as follows:
-%\begin{equation}
-%\label{eqSM}
-%SM \stackrel{.}{=} (MT, SIM)
-%\end{equation}
+The \emph{semantic matchmaking quality} of the service composition can be obtained by aggregating $type_e$ and $sim_e$, respectively, over all edges in $E$ as follows:
 \vspace{-0.2cm}
@@
 \vspace{-0.1cm}
-\noindent When multiple quality criteria are involved into decision making, then the overall fitness of a solution can be defined as a weighted sum of the individual criteria: 
+\noindent When multiple quality criteria are involved into decision making, then the overall fitness of a solution can be defined as a weighted sum of the individual criteria in Eq \ref{equation8}, assuming the preference of each quality criterion is known by users.
 \vspace{-0.2cm}
@@
 The weights can be adjusted according to users' preferences.
-We normalise $MT$, $SIM$, $A$, $R$, $T$, and $C$ so that the function value falls within the range from 0 to 1 using Eq.
+$\hat{MT}$, $\hat{SIM}$, $\hat{A}$, $\hat{R}$, $\hat{T}$, and $\hat{C}$ are normalised values calculated within the range from 0 to 1 using Eq.
 (\ref{equation9}).
 To simplify the presentation we also use the notation $(Q_1,Q_2,Q_3,Q_4,Q_5,Q_6) = (MT,SIM,A,R,T,C)$.
-$MT$ and $SIM$ have minimum value 0 and maximum value 1.
-The minimum and maximum value of $A$, $R$, $T$, and $C$ are calculated across all task-related candidates in the service repository $\mathcal{SR}$ using the greedy search in \cite{ma2015hybrid,da2016genetic}.
+$Q_1$ and $Q_2$ have minimum value 0 and maximum value 1.
+The minimum and maximum value of $Q_3$, $Q_4$, $Q_5$, and $Q_6$ are calculated across all task-related candidates in the service repository $\mathcal{SR}$ using the greedy search in \cite{ma2015hybrid,da2016genetic}.
 
@@
 \section{PSO-based Approach to Comprehensive Quality-Aware Automated Semantic Web Service Composition}\label{qswsc_approach}
-\vspace{-0.8cm}
+\subsection{An Overview of our PSO-based Approach}\label{PSO_based_approach}
+As PSO has shown promise in solving combinatorial optimisation problems, we propose a PSO-based approach to comprehensive quality-aware automated semantic web service composition.
+Fig.
+\ref{overview} shows an overview of our approach consisting of four steps:
 \begin{figure}[h]
@@
 \end{figure}
-\vspace{-1.0cm}
-\subsection{An Overview of our PSO-based Approach}\label{PSO_based_approach}
-
-As PSO has shown promise in solving combinatorial optimisation problems, we propose a PSO-based approach to comprehensive quality-aware automated semantic web service composition.
-Fig.
-\ref{overview} shows an overview of our approach consisting of four steps:
+\vspace{-0.5cm}
 
@@
 We record and compare the mean values of both $SM$ ($SM = 0.5 \hat{MT} + 0.5 \hat{SIM}$) and $QoS$($QoS = 0.25 \hat{A} + 0.25 \hat{R} + 0.25(1 - \hat{T}) + 0.25(1 - \hat{C})$) of best solutions over 30 independent runs.
-To make the comparison informative, all these recorded values have been normalised from 0 to 1, and compared using independent-samples t tests, see Table \ref{decisionTable}.
+To make the comparison informative, all these recorded values have been normalised from 0 to 1, and compared using independent-samples T tests, see Table \ref{decisionTable}.
+Note that p-values are smaller than 0.001 in the significance of the results.
 

### 2017-05-11 paper.tex
Camera-ready v1

@@
 We suggest to consider the semantic similarity of concepts when comparing different $plugin$ matches.
-For concepts $a, b$ in $\mathcal{O}$ the \emph{semantic similarity} $sim(a, b)$ is calculated based on the edge counting method defined in Eq.
-(\ref{equation1}) from \cite{shet2012new}, where $N_a$, $N_b$ and $N_c$ measure the distances from concept $a$, concept $b$, and the closest common ancestor $c$ of $a$ and $b$ to the top concept of the ontology $\mathcal{O}$, respectively.
-\vspace{-0.2cm}
-
+For concepts $a, b$ in $\mathcal{O}$ the \emph{semantic similarity} $sim(a, b)$ is calculated based on the edge counting method in a taxonomy like WorldNet or Ontology using Eq.
+(\ref{eq_sim}).
+This method \cite{shet2012new} has the advantages of simple calculation and good performance.
+In Eq.
+(\ref{eq_sim}), $N_a$, $N_b$ and $N_c$ measure the distances from concept $a$, concept $b$, and the closest common ancestor $c$ of $a$ and $b$ to the top concept of the ontology $\mathcal{O}$, respectively.
 \begin{equation}
 sim(a, b){=} \frac{2N_c \cdot e^{-\lambda L/D} }{N_{a}+N_{b}}
-\label{equation1}
+\label{eq_sim}
 \end{equation}
@@
 Each edge $e$ from a service $S$ to a service $S'$ means that service $S$ produces an output $a\in O_S$ that is matched ($exact$ or $plugin$) to an input $b\in I_{S'}$ to be consumed by service $S'$ in the composition.
-Based on the matchmaking type ($type_e$), the \emph{semantic similarity} ($sim_e$) of edge $e$ can be defined as follows:
-\vspace{-0.2cm}
-\begin{equation}
-\label{equation10}
+Based on the matchmaking type ($type_e$), the \emph{semantic similarity} ($sim_e$) of edge $e$ can be defined as follow:
+
+\begin{align*}
 type_e = 
 \begin{cases}
-	1 & \text{ if $a\equiv b$ ($exact$ match)},\\
+	1 & \text{ if $a\equiv b$ ($exact$ match)}\\
 	p & \text{ if $a \sqsubseteq b$ ($plugin$ match)}
 \end{cases}
-\end{equation}
-\begin{equation}
-\label{equation11}
+&&
 sim_e = sim(a,b) = \frac{2N_c}{N_{a}+N_{b}}
-\end{equation}
+\end{align*}
+
+%\begin{equation}
+%\label{equation10}
+%type_e = 
+%\begin{cases}
+%	1 & \text{ if $a\equiv b$ ($exact$ match)},\\
+%	p & \text{ if $a \sqsubseteq b$ ($plugin$ match)}
+%\end{cases}
+%\end{equation}
+%\begin{equation}
+%\label{equation11}
+%sim_e = sim(a,b) = \frac{2N_c}{N_{a}+N_{b}}
+%\end{equation}
 
@@
 
-The \emph{semantic matchmaking quality} of the service composition can be obtained by aggregating $type_e$ and $sim_e$, respectively, over all edges in $E$ as follows:
-\vspace{-0.2cm}
-\begin{equation}
-\label{equation6}
+The \emph{semantic matchmaking quality} of the service composition can be obtained by aggregating $type_e$ and $sim_e$, respectively, over all edges in $E$ as follow:
+\begin{align*}
 MT {=} \prod_{j=1}^{m} type_ {e_{j}}
-\end{equation}
-\begin{equation}
-\label{equation7}
+&&
 SIM {=} \frac{1}{m}\sum_{j=1}^m sim_ {e_{j}}
-\end{equation}
+\end{align*}
+
 %\begin{equation}
-%\label{eqCQ}
-%CQ \stackrel{.}{=} (MT, \  SIM, \  A,\  R,\  C,\  T)
+%\label{equation6}
+%MT {=} \prod_{j=1}^{m} type_ {e_{j}}
+%\end{equation}
+%\begin{equation}
+%\label{equation7}
+%SIM {=} \frac{1}{m}\sum_{j=1}^m sim_ {e_{j}}
 %\end{equation}
@@
 For a service composition with services $ S_1, S_2, ...
-S_n$ we obtain the reliability $R=\prod\limits^n_{k=1}r_{S_k}$, the availability $A=\prod\limits^n_{k=1}a_{S_k}$, the cost $C=\sum\limits^n_{k=1}c_{S_k}$, and the response time $T$ is the time of most time-consuming path in the composition, i.e., $$T = MAX \{\sum\limits^{\ell_j}_{k=1}t_{S_k} | \text{ $j\in\{1,\ldots,m\}$ and $\ell_j$ is the length of a path $P_j$}\}.$$
+S_n$ we obtain the reliability $R=\prod\limits^n_{k=1}r_{S_k}$, the availability $A=\prod\limits^n_{k=1}a_{S_k}$, the cost $C=\sum\limits^n_{k=1}c_{S_k}$, and the response time $T$ is the time of most time-consuming path in the composition, i.e., $$T = MAX \{\sum\limits^{\ell_n}_{k=1}t_{S_k} | \text{ $\ell_n$ is the length of a path $P_n$ and $n\in\{1,\ldots,n\}$}\}.$$
 
-%Consequently, in Eq. \ref{eqCQ}, the comprehensive quality $CQ$ consists of the aggregated semantic matchmaking quality $SM$ and the QoS calculation in DAG discussed before.
-\vspace{-0.1cm}
-\noindent When multiple quality criteria are involved into decision making, then the overall fitness of a solution can be defined as a weighted sum of the individual criteria in Eq \ref{equation8}, assuming the preference of each quality criterion is known by users.
-\vspace{-0.2cm}
+\noindent When multiple quality criteria are involved into decision making, then the overall fitness of a solution can be defined as a weighted sum of the individual criteria in Eq \ref{eq_fitness}, assuming the preference of each quality criterion is known by users.
 \begin{equation}
-\label{equation8}
+\label{eq_fitness}
 Fitness = w_1 \hat{MT} + w_2 \hat{SIM} + w_3 \hat{A} + w_4 \hat{R} + w_5(1 - \hat{T}) + w_6(1 - \hat{C})
@@
 $\hat{MT}$, $\hat{SIM}$, $\hat{A}$, $\hat{R}$, $\hat{T}$, and $\hat{C}$ are normalised values calculated within the range from 0 to 1 using Eq.
-(\ref{equation9}).
+(\ref{eq_normal}).
 To simplify the presentation we also use the notation $(Q_1,Q_2,Q_3,Q_4,Q_5,Q_6) = (MT,SIM,A,R,T,C)$.
@@
 \begin{equation}
-\label{equation9}
+\label{eq_normal}
 \hat{Q_k} = 
@@
 
-\noindent To solve the composition task satisfactorily our goal is to maximize the objective function in Eq. (\ref{equation8}).
+\noindent To solve the composition task satisfactorily our goal is to maximize the objective function in Eq. (\ref{eq_fitness}).
 
@@
 In step 6, this sorted queue is used as one of the inputs of the forward decoding Algorithm \ref{graph_building} to create a $WG$.
-In step 7, the fitness value of the created $WG$ is the fitness value of the particle calculated by the comprehensive model discussed in Section \ref{Comprehensive_Quality_Model}.
+In step 7, the fitness value of the created $WG$ is the fitness value of the particle calculated by the comprehensive model discussed in Section \ref{problemDes}.
 \vspace{-0.5cm}
@@
      Sort the service queue by position vectors' weights\;
-     Use Algorithm \ref{graph_building} to create a $WG$ from the service queue \;
+     Use Algorithm \ref{graph_building} to create a $WG$ from the service queue\;
      Calculate the $WG$ fitness value\;
@@
  $WG = (V, E)$\;
- $V \leftarrow$ \{$Start$, $End$ \} \;
+ $V \leftarrow$ \{$Start$, $End$ \}\;
  $OutputSet \leftarrow$ \{$I_{T}$\}\;
@@
       \uIf{$I_{S}$ satisfied by $OutputSet$}{  
-        insert $S$ into $V$ \;  
+        insert $S$ into $V$\;  
         adjoin $O_{S}$ to $OutputSet$\;

### 2017-05-11 paper.tex
cameral-ready-version 1.1

@@
 We consider a \emph{semantic web service} (\emph{service}, for short) as a tuple $S = (I_{S}, O_{S}, QoS_S)$ where $I_{S}$ is a set of service inputs that are consumed by $S$, $O_{S}$ is a set of service outputs that are produced by $S$, and $QoS_{S}=\{t_S, c_S, r_S, a_S\}$ is a set of non-functional attributes of $S$.
-The inputs in $I_{S}$ and outputs in $O_{S}$ are parameters modeled through concepts in a domain-specific ontology $\mathcal{O}$.
+The inputs in $I_{S}$ and outputs in $O_{S}$ are parameters modelled through concepts in a domain-specific ontology $\mathcal{O}$.
 The attributes $t_S, c_S, r_S, a_S$ refer to the response time, cost, reliability, and availability of service $S$, respectively.
@@
 In particular, these two differences are related to sorting a created service queue using service-to-index mapping for a particle' position vectors and evaluating the fitness of a particle after decoding this service queue into a $WG$ respectively.
-Those differences are further addressed in Algorithms \ref{novelSteps} and \ref{graph_building} in Section \ref{POS-based_algomargin}.
+Those differences are further addressed in Algorithms \ref{novelSteps} and \ref{graph_building} in Section \ref{PSO-based_algomargin}.
 
-\subsection{The Algorithms for our PSO-based Approach}\label{POS-based_algomargin}
+\subsection{The Algorithms for our PSO-based Approach}\label{PSO-based_algomargin}
 The overall algorithm investigated here is made up of a PSO-based web service composition technique (Algorithm \ref{novelSteps}) and a $WG$ creating technique from a service queue (Algorithm \ref{graph_building}).
@@
 Two objectives of this evaluation are to: $(1)$ evaluate the effectiveness of our PSO-based approach, see comparison test in Section \ref{comparisonTestWithGP}.
-%To do this, we compare our PSO-based method with one existing GP-based approach \cite{ma2015hybrid}. 
 $(2)$ evaluate the effectiveness of our proposed comprehensive quality model to achieve a desirable balance on semantic matchmaking quality and QoS, see comparison test in Section \ref{comparisonTest}.
-%To do this, we compare a widely used QoS model in QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol} with our comprehensive quality model using our PSO-based approach.
-
-%WSC09 is a benchmark dataset consisting of five composition tasks. These tasks are associated with an increasing number of services, and concepts in ontologies.
 
@@
 In general, weight settings and parameter $p$ are decided by users' preferences.
+
 \vspace{-0.5cm}
@@
 \bibliographystyle{splncs03}
-\bibliography{IEEEexample}
+\bibliography{bibliography}
 

### 2017-05-12 paper.tex
Camera-ready-version 1.2

@@
 \cite{lecue2009optimizing} proposes a semi-automated web service composition using GA to encode a given abstract service workflow, where the evaluation of semantic matchmaking quality requires a complete and formal definition of ontology using description logic, which is associated to the resources of web services.
-Another GA-based approach \cite{fanjiang2014semantic} utilise process description language to encode pre-stored cases-based workflows, where workable services are composed to complete this workflow.
+Another GA-based approach \cite{fanjiang2014semantic} utilise the structure of process description language to encode pre-stored cases-based workflows, where workable services are composed to complete this workflow.
 An automated immune-inspired web service composition approach \cite{pop2009immune} employs a clonal selection algorithm to proliferate decoded planning graphs, but this approach is only evaluated with some simple cases.
@@
 Both $WGs$ have exactly the same service workflow structure, but some service vertices and edges denoted in red are different.
-To better understand these differences, we list the overall semantic matchmaking quality $SM$,  overall $QoS$ and semantic matchmaking quality associated to these different edges in $WG_1$ and $WG_2$.
+To better understand these differences, we list the overall semantic matchmaking quality $SM$,  overall $QoS$ and semantic matchmaking quality $sm_{e_n}$ associated to these different edges in $WG_1$ and $WG_2$.
 (Note: $sm_{e_n} = 0.5type_{e_n} + 0.5 sim_{e_n}$), where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) of the listed qualities for our comprehensive quality model.

### 2017-05-12 paper.tex
format

@@
 (Note: $sm_{e_n} = 0.5type_{e_n} + 0.5 sim_{e_n}$), where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) of the listed qualities for our comprehensive quality model.
-Therefore, we achieve a comprehensive quality gain of 0.1433, which is the result of a gain in semantic matchmaking quality (+0.1467) and a loss in $QoS$ (-0.0034).
+Therefore, we achieve a comprehensive quality gain (+0.1433), a result of a gain in semantic matchmaking quality (+0.1467) and a loss in $QoS$ (-0.0034).
 To understand the improvement of semantic matchmaking quality from these numbers, we pick up $e_4$ that is associated with the smallest $\Delta Q$.

### 2017-05-16 paper.tex
update

@@
 Another challenge is related to QoS optimisation.
-This problem gives birth to \textit{QoS-aware service composition} that aims to find composition solutions with optimised QoS.
+This challenge gives birth to \textit{QoS-aware service composition} that aims to find composition solutions with optimised QoS.
 
@@
 In the past few years, many approaches \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive} to QoS-aware web service composition employ Evolutionary Computation (EC) techniques to automatically generate composition solutions.
-Genetic Programming (GP) based approaches produce promising results, but these approaches often require repairing or penalising the solutions \cite{ma2015hybrid,yu2013adaptive}.
-However, Particle Swarm Optimisation (PSO) is considered to be more efficient, as it simply updates particles' positions to move candidate particles across the searching space, rather than employing genetic operators to carry out searching process.
+Genetic Programming (GP) based approaches produce promising results, but these approaches often require repairing or penalising the solutions \cite{ma2015hybrid,yu2013adaptive}, which restrict their searching space.
+Particle Swarm Optimisation (PSO) based approaches are proposed to avoid producing invalid solutions to effectively search for near-optimal solutions \cite{da2016particle}.
 All these works have enabled an \textit{automatic web service composition}, but do not optimise QoS and quality of semantic matchmaking simultaneously to achieve a desirable balance on both sides.
 
-The overall goal of this paper is to \textit{develop a PSO-based approach to comprehensive quality-aware automated semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}.
+The overall goal of this paper is to \textit{develop a PSO-based approach to comprehensive quality-aware automated semantic web service composition that simultaneously optimises both QoS and semantic matchmaking quality}.
 Particularly, this paper extends existing works on QoS-aware service composition by considering jointly optimising the both quality aspects, which is proposed as a comprehensive quality model.
@@
 We suggest to consider the semantic similarity of concepts when comparing different $plugin$ matches.
-For concepts $a, b$ in $\mathcal{O}$ the \emph{semantic similarity} $sim(a, b)$ is calculated based on the edge counting method in a taxonomy like WorldNet or Ontology using Eq.
-(\ref{eq_sim}).
-This method \cite{shet2012new} has the advantages of simple calculation and good performance.
+For concepts $a, b$ in $\mathcal{O}$ the \emph{semantic similarity} $sim(a, b)$ is calculated based on an edge counting method in a taxonomy like WorldNet or Ontology using Eq.
+(\ref{eq_sim}) \cite{shet2012new}.
+This method has the advantages of simple calculation and good performance \cite{shet2012new}.
 In Eq.
@@
 \end{cases}
-&&
+,&&
 sim_e = sim(a,b) = \frac{2N_c}{N_{a}+N_{b}}
@@
 MT {=} \prod_{j=1}^{m} type_ {e_{j}}
-&&
+,&&
 SIM {=} \frac{1}{m}\sum_{j=1}^m sim_ {e_{j}}
@@
 For a service composition with services $ S_1, S_2, ...
-S_n$ we obtain the reliability $R=\prod\limits^n_{k=1}r_{S_k}$, the availability $A=\prod\limits^n_{k=1}a_{S_k}$, the cost $C=\sum\limits^n_{k=1}c_{S_k}$, and the response time $T$ is the time of most time-consuming path in the composition, i.e., $$T = MAX \{\sum\limits^{\ell_n}_{k=1}t_{S_k} | \text{ $\ell_n$ is the length of a path $P_n$ and $n\in\{1,\ldots,n\}$}\}.$$
-
-\noindent When multiple quality criteria are involved into decision making, then the overall fitness of a solution can be defined as a weighted sum of the individual criteria in Eq \ref{eq_fitness}, assuming the preference of each quality criterion is known by users.
+S_n$ we obtain the reliability $R=\prod\limits^n_{k=1}r_{S_k}$, the availability $A=\prod\limits^n_{k=1}a_{S_k}$, the cost $C=\sum\limits^n_{k=1}c_{S_k}$, and the response time $T$ is the time of the most time-consuming path in the composition, i.e., assuming $h$ is the number of path,
+$$T = MAX \{\sum\limits^{\ell_j}_{k=1}t_{S_k} | \text{ $j\in\{1,\ldots,h\}$,  and $\ell_j$ is the length of a path $P_j$}\}$$.
+\noindent When multiple quality criteria are involved into decision making, then the overall fitness of a solution can be defined as a weighted sum of the individual criteria in Eq \ref{eq_fitness}, assuming the preference of each quality criterion is provided by users.
 \begin{equation}
@@
 The $p$ of $type_e$ is set to 0.75 ($plugin$ match) according to \cite{lecue2009optimizing}.
-In general, weight settings and parameter $p$ are decided by users' preferences.
+In general, weight settings and parameter $p$ are decided according to users' preferences.
 
@@
 To make the comparison informative, all these recorded values have been normalised from 0 to 1, and compared using independent-samples T tests, see Table \ref{decisionTable}.
-Note that p-values are smaller than 0.001 in the significance of the results.
+Note that p-values are consistently smaller than 0.001 in the results with significant differences.
 
@@
 Fig.
-\ref{comparisontest} $(1)$ and $(2)$ show two weighted DAGs $WG_1$ and $WG_2$ that have been obtained as the best service compositions solutions based on the QoS model and on the comprehensive quality model, respectively.
+\ref{comparisontest} $(1)$ and $(2)$ show two weighted DAGs, $WG_1$ and $WG_2$, which have been obtained as the best service compositions solutions based on the QoS model and on the comprehensive quality model, respectively.
 Both $WGs$ have exactly the same service workflow structure, but some service vertices and edges denoted in red are different.

### 2017-05-17 paper.tex
final camera-ready

@@
 Genetic Programming (GP) based approaches produce promising results, but these approaches often require repairing or penalising the solutions \cite{ma2015hybrid,yu2013adaptive}, which restrict their searching space.
-Particle Swarm Optimisation (PSO) based approaches are proposed to avoid producing invalid solutions to effectively search for near-optimal solutions \cite{da2016particle}.
+Particle Swarm Optimisation (PSO) based approaches are therefore proposed to avoid producing invalid solutions to effectively search for near-optimal solutions \cite{da2016particle}.
 All these works have enabled an \textit{automatic web service composition}, but do not optimise QoS and quality of semantic matchmaking simultaneously to achieve a desirable balance on both sides.
@@
 S_n$ we obtain the reliability $R=\prod\limits^n_{k=1}r_{S_k}$, the availability $A=\prod\limits^n_{k=1}a_{S_k}$, the cost $C=\sum\limits^n_{k=1}c_{S_k}$, and the response time $T$ is the time of the most time-consuming path in the composition, i.e., assuming $h$ is the number of path,
-$$T = MAX \{\sum\limits^{\ell_j}_{k=1}t_{S_k} | \text{ $j\in\{1,\ldots,h\}$,  and $\ell_j$ is the length of a path $P_j$}\}$$.
-\noindent When multiple quality criteria are involved into decision making, then the overall fitness of a solution can be defined as a weighted sum of the individual criteria in Eq \ref{eq_fitness}, assuming the preference of each quality criterion is provided by users.
+$$T = MAX \{\sum\limits^{\ell_j}_{k=1}t_{S_k} | \text{ $j\in\{1,\ldots,h\}$,  and $\ell_j$ is the number of nodes in a path $P_j$}\}$$
+\noindent When multiple quality criteria are involved into decision making, then the overall fitness of a solution can be defined as a weighted sum of the individual criteria in Eq (\ref{eq_fitness}) that the preference of each quality criterion is provided by users.
 \begin{equation}
@@
 To make the comparison informative, all these recorded values have been normalised from 0 to 1, and compared using independent-samples T tests, see Table \ref{decisionTable}.
-Note that p-values are consistently smaller than 0.001 in the results with significant differences.
+Note that p-values are consistently smaller than 0.001 in the results indicating significant differences in performance.
 

### 2017-05-18 paper.tex
update Acknowledgement

@@
 In these works, huge efforts have been devoted to QoS-aware web service compositions assuming a pre-defined abstract workflow is given.
-This is generally considered as a \textit{semi-automated web service composition} approach.
+This is generally considered as a \textit{semi-automated web service composition}.
 Generating composition plans automatically in discovering and selecting suitable web services is a NP-hard problem \cite{moghaddam2014service}.
 In the past few years, many approaches \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive} to QoS-aware web service composition employ Evolutionary Computation (EC) techniques to automatically generate composition solutions.
-Genetic Programming (GP) based approaches produce promising results, but these approaches often require repairing or penalising the solutions \cite{ma2015hybrid,yu2013adaptive}, which restrict their searching space.
+Genetic Programming (GP) based approaches produce promising results, but often require repairing or penalising the solutions \cite{ma2015hybrid,yu2013adaptive}, which restrict their searching space.
 Particle Swarm Optimisation (PSO) based approaches are therefore proposed to avoid producing invalid solutions to effectively search for near-optimal solutions \cite{da2016particle}.
@@
 Only a few works \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} consider both semantic matchmaking quality and QoS simultaneously.
-\cite{lecue2009optimizing} proposes a semi-automated web service composition using GA to encode a given abstract service workflow, where the evaluation of semantic matchmaking quality requires a complete and formal definition of ontology using description logic, which is associated to the resources of web services.
-Another GA-based approach \cite{fanjiang2014semantic} utilise the structure of process description language to encode pre-stored cases-based workflows, where workable services are composed to complete this workflow.
+\cite{lecue2009optimizing} proposes a semi-automated web service composition using GA to encode a given abstract service workflow, where the evaluation of semantic matchmaking quality requires a complete and formal definition of ontology using description logic.
+Another GA-based approach \cite{fanjiang2014semantic} utilise the structure of process description languages to encode pre-stored cases-based workflows, where workable services are composed to complete this workflow.
 An automated immune-inspired web service composition approach \cite{pop2009immune} employs a clonal selection algorithm to proliferate decoded planning graphs, but this approach is only evaluated with some simple cases.
@@
 
-We consider a \emph{semantic web service} (\emph{service}, for short) as a tuple $S = (I_{S}, O_{S}, QoS_S)$ where $I_{S}$ is a set of service inputs that are consumed by $S$, $O_{S}$ is a set of service outputs that are produced by $S$, and $QoS_{S}=\{t_S, c_S, r_S, a_S\}$ is a set of non-functional attributes of $S$.
+We consider a \emph{semantic web service} (\emph{service}, for short) as a tuple $S = (I_{S}, O_{S}, QoS_S)$ where $I_{S}$ is a set of service inputs consumed by $S$, $O_{S}$ is a set of service outputs produced by $S$, and $QoS_{S}=\{t_S, c_S, r_S, a_S\}$ is a set of non-functional attributes of $S$.
 The inputs in $I_{S}$ and outputs in $O_{S}$ are parameters modelled through concepts in a domain-specific ontology $\mathcal{O}$.
@@
 Based on the matchmaking type ($type_e$), the \emph{semantic similarity} ($sim_e$) of edge $e$ can be defined as follow:
-
+\vspace{-0.2cm}
 \begin{align*}
@@
 \ref{overview} shows an overview of our approach consisting of four steps:
+\vspace{-0.5cm}
 \begin{figure}[h]
@@
 Those differences are further addressed in Algorithms \ref{novelSteps} and \ref{graph_building} in Section \ref{PSO-based_algomargin}.
-
+\vspace{-0.3cm}
 \subsection{The Algorithms for our PSO-based Approach}\label{PSO-based_algomargin}
@@
 
-\vspace{-1.2cm}
-
+\vspace{-1.1cm}
 \section{Experiment Study}\label{experiment_design}
@@
 
-\vspace{-0.5cm}
-\subsection{Comparison Test for GP-based vs. PSO-based approach}\label{comparisonTestWithGP}
+\vspace{-0.3cm}
+\subsection{GP-based vs. PSO-based approach}\label{comparisonTestWithGP}
 To evaluate the effectiveness of our proposed PSO-based approach, we compare our PSO-based method with one recent GP-based approach \cite{ma2015hybrid} using our proposed comprehensive quality model.
@@
 
-\subsection{Comparison Test for Comprehensive Quality Model vs. QoS Model}\label{comparisonTest}
+\subsection{Comprehensive Quality Model vs. QoS Model}\label{comparisonTest}
 
@@
 
-We observe an interesting pattern from Table \ref{decisionTable}.
-The mean values of $QoS$ using QoS model are significantly higher than those using comprehensive quality model for Tasks 2, 3, 4 and 5.
+In Table \ref{decisionTable}, the mean values of $QoS$ using QoS model are significantly higher than those using comprehensive quality model for Tasks 2, 3, 4 and 5.
 However, the mean value of $SM$ using the comprehensive quality model are significantly higher than those using the QoS model, while a slight trade-off in $QoS$ are observed in all tasks.
@@
 \end{table}
-\vspace{-0.8cm}
+\vspace{-1.0cm}
 \subsection{Further Discussion}\label{discuss1}
@@
 To understand the improvement of semantic matchmaking quality from these numbers, we pick up $e_4$ that is associated with the smallest $\Delta Q$.
-The $e_4$ of $WG_1$ and $WG_2$ has two different source nodes, $Ser1640238160$ and $Ser947554374$, and two the same end nodes.
+The $e_4$ of $WG_1$ and $WG_2$ has two different source nodes, $Ser1640238160$ and $Ser947554374$, and two the same $End$ nodes.
 $Ser1640238160$ and $Ser947554374$ are services with output parameters $Inst582785907$ and  $Inst795998200$ corresponds to two concepts $Con2037585750$ and $Con103314376$ respectively in the given ontology shown in Fig.
@@
 \vspace{-0.6cm}
-
 \begin{figure}[h]
@@
 \end{figure}
-\vspace{-1.0cm}
+\vspace{-1.5cm}
 
@@
 Future works can investigate multi-objective EC techniques to produce a set of composition solutions for the situations when the quality preference is not known.
-
-\vspace{-0.3cm}
+\vspace{-0.2cm}
+\section*{Acknowledgments} This research is supported by the Marsden fund council from Government funding, administered by the Royal Society of New Zealand.
+\vspace{-0.5cm}
 \bibliographystyle{splncs03}
